### 2019-07-23 icse/compile.tex
Initial ICSE paper format

\section{Algorithm Compiler}

\begin{itemize}
  \item Formal definition of Core language
    \begin{itemize}
      \item Syntax
      \item Semantics
    \end{itemize}
  \item Abstract algorithms
    \begin{itemize}
      \item syntax-directed / internal method
      \item Converted into Core
    \end{itemize}
\end{itemize}

### 2019-07-23 icse/eval.tex
Initial ICSE paper format

\section{Evaluation}

\begin{itemize}
  \item RQ1) Does ASE correctly extract semantics?
  \item RQ2) Is endurable size of manual portion in implementation of ASE?
  \item RQ3) Does ASE deal with annual updates from small changes?
  \item RQ4) How many specification errors are detected by ASE?
\end{itemize}

### 2019-07-23 icse/intro.tex
Initial ICSE paper format

\section{Introduction}

\begin{itemize}
  \item JavaScript is a essential programming language in client-sides.
  \item Because of its complicated semantics, it is not easy to understand JavaScript program behaviors.
  \item Several exisiting proposed formal semantics of JavaScript, but these have the following limitations.
    \begin{itemize}
      \item Fully manual implementation of parsers and interpreters.
      \item Supported only fixed version of ECMAScript (in most cases, ES 5.1).
    \end{itemize}
  \item We propose a way to automatically extract semantics from ECMAScript specifications and deal with its annual updates.
\end{itemize}

Our contributions are:
\begin{itemize}
  \item TODO
\end{itemize}

### 2019-07-23 icse/main.tex
Initial ICSE paper format

\documentclass[sigconf,review]{acmart}
\settopmatter{printacmref=false}

\input{fonts}
\input{macros}

\begin{document}

\title{Automatic Extraction of JavaScript Formal Semantics
from ECMAScript Specifications}

\author{Jihyeok Park}
\email{jhpark0223@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\author{Jihee Park}
\email{j31d0@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\author{Sukyoung Ryu}
\email{sryu.cs@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\maketitle

\begin{abstract}
\end{abstract}

% \keywords

\input{intro}
\input{background}
\input{overall}
\input{parser}
\input{compile}
\input{eval}
\input{related}
\input{conclusion}

% \bibliographystyle{ACM-Reference-Format}
% \bibliography{ref}

\end{document}

### 2019-07-23 icse/parser.tex
Initial ICSE paper format

\section{Parser Generation}

\subsection{Predictive Parsers vs Recursive Descent Parsers}
\begin{itemize}
  \item Predictive parser
    \begin{itemize}
      \item PROS: widely-used (Yacc), linear time, lookahead for predictions, no backtrack
      \item CONS: need to restructure CFG, not easy to implement ES-BNF features
    \end{itemize}
  \item Recursive descent parsers
    \begin{itemize}
      \item PROS: Scala-supported (Scala parser combinators), easily support ES-BNF features, no need to re-structure CFG
      \item CONS: PEG not CFG, exponential time for bactkracing.
    \end{itemize}
\end{itemize}

\subsection{Packrat Parsers with Lookaheads}
combination of recursive descent parsers with predictive parsers
implicit lookaheads

\subsection{Generating Parsers for \( \text{BNF}_\text{ES} \)}
How to handle each \( \text{BNF}_\text{ES} \) features

### 2019-07-23 icse/related.tex
Initial ICSE paper format

\section{Related Work}

\subsection{Parser Generation}
\subsection{Automatic Semantics Extraction}
\begin{itemize}
  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)
\end{itemize}

\subsection{Formal Semantics of JavaScript}
\begin{itemize}
  \item KJS: A complete formal semantics of JavaScript (PLDI'15)
  \item The Essence of JavaScript (ECOOP'10)
\end{itemize}

% A Trusted Mechanised JavaScript Specification (POPL'14)

### 2019-07-25 src/main/scala/kr/ac/kaist/ase/core/state/State.scala
add context and remove fixpoint at interp

@@ -2,11 +2,9 @@ package kr.ac.kaist.ase.core
 
 // CORE States
 case class State(
-    context: String = "<top-level>",
-    retValue: Option[Value] = None,
-    insts: List[Inst] = Nil,
+    context: Context = Context(),
+    ctxStack: List[Context] = List(),
     globals: Map[Id, Value] = Map(),
-    locals: Map[Id, Value] = Map(),
     heap: Heap = Heap()
 ) extends CoreNode {
   // getters
@@ -14,7 +12,7 @@ case class State(
   def apply(addr: Addr): Obj = heap(addr)
 
   // initialize local variables
-  def define(id: Id, value: Value): State = copy(locals = locals + (id -> value))
+  def define(id: Id, value: Value): State = copy(context = context.define(id, value))
 
   // setters
   def updated(refV: RefValue, value: Value): State = refV match {
@@ -24,14 +22,14 @@ case class State(
   }
   def updated(id: Id, value: Value): State =
     if (id.name.startsWith("GLOBAL_")) copy(globals = globals + (id -> value))
-    else copy(locals = locals + (id -> value))
+    else copy(context = context.define(id, value))
   def updated(addr: Addr, key: Value, value: Value): State =
     copy(heap = heap.updated(addr, key, value))
 
   // deletes
   def deleted(refV: RefValue): State = refV match {
     case RefValueId(id) =>
-      copy(locals = locals - id)
+      copy(context = context.deleted(id))
     case RefValueProp(addr, prop) =>
       copy(heap = heap.deleted(addr, prop))
     case _ => error(s"illegal reference delete: delete $refV")

### 2019-07-25 src/main/scala/kr/ac/kaist/ase/core/util/Beautifier.scala

@@ -254,18 +254,17 @@ object Beautifier {
 
     // states
     override def walk(st: State): Unit = oneDepth({
-      val State(context, retValue, insts, globals, locals, heap) = st
-      walk(indent); walk("Context: "); walk(context)
-      walk(indent); walk("Return Value: "); walkOpt[Value](retValue, walk)
+      val State(context, ctxStack, globals, heap) = st
+      walk(indent); walk("Context: "); walk(context.name)
       walk(indent); walk("Instructions: ");
       if (detail) {
-        walkList[Inst](insts, walk)
+        walkList[Inst](context.insts, walk)
         walk(indent); walk("GlobalVars: "); walkMap[Id, Value](globals, walk, walk)
       } else {
-        walkList[Inst](insts.slice(0, VISIBLE_LENGTH), walk)
-        if (insts.length > VISIBLE_LENGTH) oneDepth({ walk(indent); walk("...") })
+        walkList[Inst](context.insts.slice(0, VISIBLE_LENGTH), walk)
+        if (context.insts.length > VISIBLE_LENGTH) oneDepth({ walk(indent); walk("...") })
       }
-      walk(indent); walk("LocalVars: "); walkMap[Id, Value](locals, walk, walk)
+      walk(indent); walk("LocalVars: "); walkMap[Id, Value](context.locals, walk, walk)
       walk(indent); walk("Heap"); walk(heap)
     })
 

### 2019-07-25 src/main/scala/kr/ac/kaist/ase/core/util/Interp.scala

@@ -20,10 +20,13 @@ class Interp {
   def apply(st: State) = fixpoint(st)
 
   // perform transition until instructions are empty
-  def fixpoint(st: State): State = st.insts match {
-    case Nil => st
+  def fixpoint(st: State): State = st.context.insts match {
+    case Nil => st.ctxStack match {
+      case Nil => st
+      case ctx :: rest => fixpoint(st.copy(context = ctx.copy(locals = ctx.locals + (ctx.retId -> Absent)), ctxStack = rest))
+    }
     case inst :: rest =>
-      fixpoint(interp(inst)(st.copy(insts = rest)))
+      fixpoint(interp(inst)(st.copy(context = st.context.copy(insts = rest))))
   }
 
   // instructions
@@ -32,7 +35,7 @@ class Interp {
     if ((instCount % 10000 == 0) && (System.currentTimeMillis - startTime) > timeout) error("timeoutInst")
     if (DEBUG_INTERP) inst match {
       case ISeq(_) =>
-      case _ => println(s"${st.context}: ${beautify(inst)}")
+      case _ => println(s"${st.context.name}: ${beautify(inst)}")
     }
     inst match {
       case IExpr(expr) =>
@@ -67,22 +70,25 @@ class Interp {
         }
       case IReturn(expr) =>
         val (value, s0) = interp(expr)(st)
-        s0.copy(retValue = Some(value), insts = Nil)
+        s0.ctxStack match {
+          case Nil => s0.copy(context = s0.context.copy(locals = s0.context.locals + (s0.context.retId -> value), insts = Nil))
+          case ctx :: rest => s0.copy(context = ctx.copy(locals = ctx.locals + (ctx.retId -> value)), ctxStack = rest)
+        }
       case IIf(cond, thenInst, elseInst) =>
         val (v, s0) = interp(cond, true)(st)
         v match {
-          case Bool(true) => s0.copy(insts = thenInst :: s0.insts)
-          case Bool(false) => s0.copy(insts = elseInst :: s0.insts)
+          case Bool(true) => s0.copy(context = s0.context.copy(insts = thenInst :: s0.context.insts))
+          case Bool(false) => s0.copy(context = s0.context.copy(insts = elseInst :: s0.context.insts))
           case v => error(s"not a boolean: $v")
         }
       case IWhile(cond, body) =>
         val (v, s0) = interp(cond, true)(st)
         v match {
[…]

### 2019-07-25 src/main/scala/kr/ac/kaist/ase/generator/ModelGenerator.scala

@@ -47,10 +47,8 @@ object ModelGenerator {
     nf.println(s"""""")
     nf.println(s"""object Model {""")
     nf.println(s"""  lazy val initState: State = State(""")
-    nf.println(s"""    retValue = None,""")
-    nf.println(s"""    insts = Nil,""")
+    nf.println(s"""    context = Context(),""")
     nf.println(s"""    globals = initGlobal,""")
-    nf.println(s"""    locals = Map(),""")
     nf.println(s"""    heap = initHeap""")
     nf.println(s"""  )""")
     nf.println(s"""  lazy val initGlobal: Map[Id, Value] = BaseGlobal.get ++ Map(""")

### 2019-07-25 src/main/scala/kr/ac/kaist/ase/phase/Load.scala

@@ -16,10 +16,10 @@ case object Load extends PhaseObj[Script, LoadConfig, State] {
     aseConfig: ASEConfig,
     config: LoadConfig
   ): State = Model.initState.copy(
-    insts = List(Parser.parseInst("""{
+    context = Model.initState.context.copy(insts = List(Parser.parseInst("""{
       app __x0__ = (RunJobs)
       return __x0__
-    }""")),
+    }"""))),
     globals = Model.initState.globals + (Id("script") -> ASTVal(script))
   )
 

### 2019-07-25 src/main/scala/kr/ac/kaist/ase/phase/LoadCore.scala

@@ -15,7 +15,7 @@ case object LoadCore extends PhaseObj[Program, LoadCoreConfig, State] {
     pgm: Program,
     aseConfig: ASEConfig,
     config: LoadCoreConfig
-  ): State = Model.initState.copy(insts = pgm.insts)
+  ): State = Model.initState.copy(context = Model.initState.context.copy(insts = pgm.insts))
 
   def defaultConfig: LoadCoreConfig = LoadCoreConfig()
   val options: List[PhaseOption[LoadCoreConfig]] = List()

### 2019-07-25 src/test/scala/kr/ac/kaist/ase/JSTest.scala

@@ -22,7 +22,7 @@ class JSTest extends CoreTest {
   }
 
   // tests for js-interpreter
-  def evalJSTest(st: => State): Unit = st.retValue match {
+  def evalJSTest(st: => State): Unit = st.context.locals.get(st.context.retId) match {
     case Some(addr: Addr) => st.heap(addr, Str("Type")) match {
       case (addr: Addr) =>
         assert(addr == st.globals.getOrElse(Id("CONST_normal"), Absent))
@@ -52,7 +52,7 @@ class JSTest extends CoreTest {
       lazy val coreConfig = aseConfig.copy(fileNames = List(coreName))
 
       lazy val pgm = ParseCore((), coreConfig)
-      lazy val coreSt = EvalCore(st.copy(insts = pgm.insts), coreConfig)
+      lazy val coreSt = EvalCore(st.copy(context = st.context.copy(insts = pgm.insts)), coreConfig)
       check("JSCheck", name, {
         parseCoreTest(pgm)
         evalCoreTest(coreSt)

### 2019-07-25 src/test/scala/kr/ac/kaist/ase/Test262Test.scala

@@ -40,7 +40,7 @@ class Test262Test extends ASETest {
 
   // tests for js-interpreter
   def evalJSTest(st: => State): Unit = {
-    st.retValue match {
+    st.context.locals.get(st.context.retId) match {
       case Some(addr: Addr) => st.heap(addr, Str("Type")) match {
         case (addr: Addr) =>
           assert(addr == st.globals.getOrElse(Id("CONST_normal"), Absent))

### 2019-07-25 icse/related.tex
Added related works

@@
 \subsection{Parser Generation}
+\begin{itemize}
+  \item Packrat parsing:: simple, powerful, lazy, linear time, functional pearl (ICFP'02)~\cite{packrat}
+\end{itemize}
+
 \subsection{Automatic Semantics Extraction}
 \begin{itemize}
-  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)
+  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)~\cite{javadoc}
 \end{itemize}
@@
 \begin{itemize}
-  \item KJS: A complete formal semantics of JavaScript (PLDI'15)
-  \item The Essence of JavaScript (ECOOP'10)
+  \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
+  \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
+  \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
 \end{itemize}
-
-% A Trusted Mechanised JavaScript Specification (POPL'14)

### 2019-07-26 icse/parser.tex
Added BNF_ES explanation
Temporal updates for parsers

@@
 
+In this section, we introduce a way to automatically generate JavaScript parsers
+from given ECMAScript specifications. First, we explain \( \bnfes \), an extension
+of BNF used in ECMAScript to describe lexical and syntactic grammars of JavaScript.
+We defined a recursive descent parser generator to support \( \bnfes \) notations.
+We implemented our idea by extending the basic Scala parser combinator.
+The implementation also support the automatic semicolon insertion,
+one of the most distinct parsing feautres in ECMAScript.
+
+\subsection{\( \bnfes \): Grammars for ECMAScripts}
+
+ECMAScript supports their lexical and syntactic grammars based on
+their own Backus-Naur form(BNF), we call it as \( \bnfes \).
+It provides five additional notations:
+\begin{itemize}
+  \item \( \code{T}_\code{opt} \)
+    - the (non-)terminal \( \term \) is optional
+  \item \( \code{T but not T'} \):
+    - the (non-)terminal \( \term \) should be not the (non-)terminal \( \code{T'} \)
+  \item \( \code{[lookahead} = \code{T]} \)
+    - it checks that remain inputs are possible to be parsed using \( \code{T} \)
+    but does not consume any inputs.
+  \item \( \code{[lookahead} \neq \code{T]} \)
+    - it checks that remain inputs are not possible to be parsed using \( \code{T} \)
+    but does not consume any inputs.
+    % \code{T[P}^\code{*}\code{]} & \text{parameters}
+    % \\\hline
+    % \begin{itemize}
+    %   \item \code{?P} & \text{passing argument} \code{P}
+    %   \item \code{+P} & \kwtrue
+    %   \item \code{\textasciitilde}\code{P} &  \kwfalse
+    % \end{itemize}
+    % \code{[+P] T} & \text{if} \; \code{P} \; \text{is} \; \kwtrue \;\text{, added} \; \code{T}
+    % \\\hline
+    % \code{[\textasciitilde}\code{P] T} & if  \code{P}  is  \kwfalse , added  \code{T}
+    % \\\hline
+\end{itemize}
+
+Our goal is to automatically generate parsers from grammars written in \( \bnfes \).
+
+% There are two different parsing approaches:
+% ``top-down'' approach (LL-style parsing) and
+% ``bottom-up'' approach (LR-style parsing).
+% Top-down approach support 
+% 
+% There are two different kinds of parsers: top-down parsing, bottom-up parsing.
+% 
+% 
+% 
+% Such features could be easily represented in Parsing Expression Grammars (PEGs).
+% 
+% 
+% 
+% Backus–Naur form(BNF)에 다섯 가지의 방식을 추가한 형태로 lexical 및 syntactic grammar를 제공한다.
+% 각각의
+
 \subsection{Predictive Parsers vs Recursive Descent Parsers}
-\begin{itemize}
-  \item Predictive parser
-    \begin{itemize}
-      \item PROS: widely-used (Yacc), linear time, lookahead for predictions, no backtrack
-      \item CONS: need to restructure CFG, not easy to implement ES-BNF features
-    \end{itemize}
-  \item Recursive descent parsers
-    \begin{itemize}
-      \item PROS: Scala-supported (Scala parser combinators), easily support ES-BNF features, no need to re-structure CFG
-      \item CONS: PEG not CFG, exponential time for bactkracing.
-    \end{itemize}
-\end{itemize}
 
@@
 
-\subsection{Generating Parsers for \( \text{BNF}_\text{ES} \)}
-How to handle each \( \text{BNF}_\text{ES} \) features
+\subsection{Generating Parsers for \( \bnfes \)}
+How to handle each \( \bnfes \) features
+% \begin{table}
+%   \centering
+%   \[
+%     \begin{array}{l|l}
+%       \bnfes & \peg
+%       \\\hline
+%       \code{T}_\code{opt} & \code{T?}
+%       \\\hline
+%       \code{T but not T'} & \code{-T'} \; \code{\textasciitilde} \; \code{T}
+%       \\\hline
+%       \code{[lookahead} = \code{T]} & \code{+T}
+%       \\\hline
+%       \code{[lookahead} \neq \code{T]} & \code{-T}
+%       \\\hline
+%       % \code{T[P}^\code{*}\code{]} & \text{parameters}
+%       % \\\hline
+%       % \begin{itemize}
+%       %   \item \code{?P} & \text{passing argument} \code{P}
+%       %   \item \code{+P} & \kwtrue
+%       %   \item \code{\textasciitilde}\code{P} &  \kwfalse
+%       % \end{itemize}
+%       % \code{[+P] T} & \text{if} \; \code{P} \; \text{is} \; \kwtrue \;\text{, added} \; \code{T}
+%       % \\\hline
+%       % \code{[\textasciitilde}\code{P] T} & if  \code{P}  is  \kwfalse , added  \code{T}
+%       % \\\hline
+%     \end{array}
+%   \]
+%   \caption{Conversion from \( \bnfes \) into \( \peg \)}
+%   \label{table:bnfes}
+% \end{table}

### 2019-07-27 icse/parser.tex
Temporal update for parsers

@@
 
-ECMAScript supports their lexical and syntactic grammars based on
-their own Backus-Naur form(BNF), we call it as \( \bnfes \).
-It provides five additional notations:
+ECMAScript provides their lexical and syntactic grammars as grammars
+based on \( \bnfes \), an extension of Backus-Naur form for ECMAScript.
+\( \bnfes \) consists of a number of \textit{productions}
+with the following forms:
+\[
+  \nt(\param_1, \cdots, \param_k) ::=
+  (\cond_1 \Rightarrow)^? \rhs_1 \mid
+  \cdots \mid
+  (\cond_n \Rightarrow)^? \rhs_n
+\]
+The left-hand side represents a parametric nonterminal \( \nt \) with
+multiple boolean parameters \( \param_1, \cdots, \param_n \).
+A production has multiple right-hand sides with optional conditions.
+The condition \( \cond \) is either \( \param_i \) or \( ! \param_i \),
+the negation of \( \param_i \).
+For example, consider the following production:
+\[
+  \nt(\param) ::= \param \Rightarrow \code{a}
+  \mid \; !\param \Rightarrow \code{b}
+  \mid  \code{c}
+\]
+Then, \( \nt(\kwt) \) means \( \code{a} \mid \code{c} \)
+and \( \nt(\kwf) \) means \( \code{b} \mid \code{c} \).
+
+Each right-hand side \( \rhs \) is a sequence of the following symbols:
 \begin{itemize}
-  \item \( \code{T}_\code{opt} \)
-    - the (non-)terminal \( \term \) is optional
-  \item \( \code{T but not T'} \):
-    - the (non-)terminal \( \term \) should be not the (non-)terminal \( \code{T'} \)
-  \item \( \code{[lookahead} = \code{T]} \)
-    - it checks that remain inputs are possible to be parsed using \( \code{T} \)
-    but does not consume any inputs.
-  \item \( \code{[lookahead} \neq \code{T]} \)
-    - it checks that remain inputs are not possible to be parsed using \( \code{T} \)
-    but does not consume any inputs.
-    % \code{T[P}^\code{*}\code{]} & \text{parameters}
-    % \\\hline
-    % \begin{itemize}
-    %   \item \code{?P} & \text{passing argument} \code{P}
-    %   \item \code{+P} & \kwtrue
-    %   \item \code{\textasciitilde}\code{P} &  \kwfalse
-    % \end{itemize}
-    % \code{[+P] T} & \text{if} \; \code{P} \; \text{is} \; \kwtrue \;\text{, added} \; \code{T}
-    % \\\hline
-    % \code{[\textasciitilde}\code{P] T} & if  \code{P}  is  \kwfalse , added  \code{T}
-    % \\\hline
+  \item \( \boxed{\symb} \):
+    basic symbols; terminal \( \code{x} \) or
+    non-terminal \( \nt(\argument_1, \cdots, \argument_k) \)
+  \item \( \boxed{\symb?} \): optional symbols
+  \item \( \boxed{\pm \symb} \): positive/negative lookahead symbols
+  \item \( \boxed{\symb \butnot \symb'} \): exclusive symbols
+  \item \( \boxed{\nolt} \): no line terminator symbols
 \end{itemize}
 
-Our goal is to automatically generate parsers from grammars written in \( \bnfes \).
+Basic symbols are either terminal or non-terminal.
+A non-terminal symbol \( \nt(\argument_1, \cdots, \argument_k) \)
+has multiple parameters and each argument \( \argument_i \) is
+a boolean value \( \kwt \), \( \kwf \) or a parameter \( \param_i \).
+An optional symbol \( \symb? \) is same with \( \epsilon \mid \symb \)
+where \( \epsilon \) denotes the empty sequence.
+A positive(negative) lookahead symbol \( +\symb \)(\( -\symb \))
+checks that the symbol \( \symb \) succeeds(fails) and
+\textit{never consumes any input}.
+The exclusive symbols \( \symb \butnot \symb' \)
+first checks that the symbol \( \symb \) succeeds
+and then checks that the result does not correspond to \( \symb' \).
+The no line terminal symbol \( \nolt \) is a special symbol
+that restricts the white spaces between two other symbols.
+
+\subsection{First/Follow Packrat Parsing}
+
+Our goal is to automatically generate JavaScript parsers from ECMAScript
+grammars written in \( \bnfes \). However, there are several problems
+to use traditional lex/yacc style parser generator.
+\begin{itemize}
+  \item \textbf{Context-Sensitive Tokens} ECMAScript tokens are context-sensitive
+    because of the regular expressions and template strings.
+    For example, the code \( \code{/x/g} \) might be a regular expression token
+    or four tokens to represent divided by the variable \( \code{x} \) and \( \code{g} \).
+\end{itemize}
 
@@
 % 각각의 
+combination of recursive descent parsers with predictive parsers
 
-\subsection{Predictive Parsers vs Recursive Descent Parsers}
-
-\subsection{Packrat Parsers with Lookaheads}
-combination of recursive descent parsers with predictive parsers
-implicit lookaheads
+first terms and follow terms
 
 \subsection{Generating Parsers for \( \bnfes \)}
-How to handle each \( \bnfes \) features
+how to handle each \( \bnfes \) features
 % \begin{table}
@@
 % \end{table}
+
+% \begin{figure}
+%   \centering
+%   \[
+%     \begin{array}{rcrcl}
+%       Call[Await] &::=& 
+%       A(p, q, r) &::=& && a A(p, \kwt, \kwf)\\
+%                  &\mid& p &Rightarrow& b\\
+%     \end{array}
+%   \]
+%   \caption{Example of \( \bnfes \)}
+%   \label{figure:bnfes}
+% \end{figure}
+
+% code size 줄이기 위해서 모두 풀어헤치지 않고 함수로 변환했다.
+
+% PEG를 그대로 사용하면 backtrack을 이미 성공한 곳에서는 하지 않기 때문에
+% 생기는 문제를 CFG로 적혀있는 것을 해결하기 위해서 lookahead를 추가함
+% Lexical Grammar는 context-sensitive하기 때문에 먼저 lexer를 돌리지 못함
+% gll에서 비슷하게 first/follow를 한 것을 보고 PEG parser를 extend함

### 2019-07-28 icse/parser.tex
Temporal update for parsers

@@
 
-ECMAScript provides their lexical and syntactic grammars as grammars
-based on \( \bnfes \), an extension of Backus-Naur form for ECMAScript.
+ECMAScript provides their lexical and syntactic grammars using \( \bnfes \),
+an extension of Backus-Naur form for ECMAScript.
 \( \bnfes \) consists of a number of \textit{productions}
@@
 A non-terminal symbol \( \nt(\argument_1, \cdots, \argument_k) \)
-has multiple parameters and each argument \( \argument_i \) is
+takes multiple arguments and each of them \( \argument_i \) is
 a boolean value \( \kwt \), \( \kwf \) or a parameter \( \param_i \).
@@
 first checks that the symbol \( \symb \) succeeds
-and then checks that the result does not correspond to \( \symb' \).
+and then checks that the parsing result does not correspond to \( \symb' \).
 The no line terminal symbol \( \nolt \) is a special symbol
@@
 
-\subsection{First/Follow Packrat Parsing}
+\subsection{SFDF-Backtrack Parsing}
 
-Our goal is to automatically generate JavaScript parsers from ECMAScript
-grammars written in \( \bnfes \). However, there are several problems
-to use traditional lex/yacc style parser generator.
+Our goal is to automatically generate readable JavaScript parsers from ECMAScript
+grammars written in \( \bnfes \). There are several options for existing paraser generators.
+Among them, we decide to extend Packrat parsers~\cite{packrat} 
+with 
+to support \( \bnfes \) Packrat parsers are first proposed by
+
+assumptions:
+
+Unambiguous
+
 \begin{itemize}
@@
     For example, the code \( \code{/x/g} \) might be a regular expression token
-    or four tokens to represent divided by the variable \( \code{x} \) and \( \code{g} \).
+    or four tokens that represent division by variables \( \code{x} \) and \( \code{g} \),
+    depends on enclosing contexts. Thus, tokenizers should be evaluated during the parser
+    not before the parser.
+  \item \textbf{\( \bnfes \) Symbols} Several symbols notations in \( \bnfes \) are
+    not trivial to be converted into normal BNF rules. 
 \end{itemize}
+
+%  Thus, we extend
 
@@
 
-first terms and follow terms
+static first terms and dynamic follow terms
 
-\subsection{Generating Parsers for \( \bnfes \)}
-how to handle each \( \bnfes \) features
-% \begin{table}
-%   \centering
-%   \[
-%     \begin{array}{l|l}
-%       \bnfes & \peg
-%       \\\hline
-%       \code{T}_\code{opt} & \code{T?}
-%       \\\hline
-%       \code{T but not T'} & \code{-T'} \; \code{\textasciitilde} \; \code{T}
-%       \\\hline
-%       \code{[lookahead} = \code{T]} & \code{+T}
-%       \\\hline
-%       \code{[lookahead} \neq \code{T]} & \code{-T}
-%       \\\hline
-%       % \code{T[P}^\code{*}\code{]} & \text{parameters}
-%       % \\\hline
-%       % \begin{itemize}
-%       %   \item \code{?P} & \text{passing argument} \code{P}
-%       %   \item \code{+P} & \kwtrue
-%       %   \item \code{\textasciitilde}\code{P} &  \kwfalse
-%       % \end{itemize}
-%       % \code{[+P] T} & \text{if} \; \code{P} \; \text{is} \; \kwtrue \;\text{, added} \; \code{T}
-%       % \\\hline
-%       % \code{[\textasciitilde}\code{P] T} & if  \code{P}  is  \kwfalse , added  \code{T}
-%       % \\\hline
-%     \end{array}
-%   \]
-%   \caption{Conversion from \( \bnfes \) into \( \peg \)}
-%   \label{table:bnfes}
-% \end{table}
+\paragraph{Static-first dynamic-follow}
+% PEG를 그대로 사용하면 backtrack을 이미 성공한 곳에서는 하지 않기 때문에 lookahead를 추가함
 
-% \begin{figure}
-%   \centering
-%   \[
-%     \begin{array}{rcrcl}
-%       Call[Await] &::=& 
-%       A(p, q, r) &::=& && a A(p, \kwt, \kwf)\\
-%                  &\mid& p &Rightarrow& b\\
-%     \end{array}
-%   \]
-%   \caption{Example of \( \bnfes \)}
-%   \label{figure:bnfes}
-% \end{figure}
+% LL(1)-parser의 정의에서 사용하는 first / follow 개념을 확장하여
 
-% code size 줄이기 위해서 모두 풀어헤치지 않고 함수로 변환했다.
+% static한 first를 구하고 dynamic하게 오는 follow를 통해 결정함
 
-% PEG를 그대로 사용하면 backtrack을 이미 성공한 곳에서는 하지 않기 때문에
-% 생기는 문제를 CFG로 적혀있는 것을 해결하기 위해서 lookahead를 추가함
-% Lexical Grammar는 context-sensitive하기 때문에 먼저 lexer를 돌리지 못함
-% gll에서 비슷하게 first/follow를 한 것을 보고 PEG parser를 extend함
+\subsection{Implementation}
+
+% - 실제 EMCAScript production(필요?) -> Our definition -> AST / Parser
+% - code size 줄이기 위해서 모두 풀어헤치지 않고 함수로 변환했다.
+% - autmoatic semicolon insertion도 해주는데 fail한 token 중에 가장 나중에 나오는 부분을 찾아서
+%   offending token으로 지정하고 이를 기반으로 semicolon insertion을 진행
+%   => 넣었을 때 안넣었을 때 test262 parsing 성공률 비교하면 좋을 듯

### 2019-07-29 icse/compile.tex
section 5

@@
-\section{Algorithm Compiler}
+\section{Semantic generation}
+
+\subsection{Core language}
+실행 가능한 specification을 만들기 위한 langauge.
+algorithm들의 공통된 행동을 실행할 수 있게 잘 설계함
+ex) let X be ... => let X = ...
+
+\subsubsection{다른 rewriting system 또는 compiler와 다른 점}
+특징으로는 Parser에서 만들어진 AST를 하나의 값으로 들고 다니면서 관련 함수를 호출하거나 subAST를 가져올수 있게 만들어짐. 이는 Syntax function 실행을 위해선데 이후 initial state organization에서 설명 
+또한 ES specification에서 공통적으로 동작하는 복잡한 연산을 expression으로 지원함, 특히 문서에 covered by에 있는 것처럼 AST Value를 Goal symbol로 다시 parse해야 하는 경우도 있고, eval이나 Class creation 관련 함수에서처럼 string을 AST로 parse해야하는 경우도 있음.
+그런 경우를 parse-syntax 를 넣어서 처리할 수 있게
+해줌.
+
+\subsection{semantic 컴파일하기 위해 하는 것 + specification 구조}
+기본적인 원칙 :
+\begin{itemize} 
+\item 자바스크립트로 알고리즘 이름이랑 파라미터, 스텝을 가져와서 코어의 글로벌 ID에 매치 시켜줌
+\item initial Heap을 생성해줌
+\end{itemize}
+매치를 시킨다는 뜻은 코어의 글로벌 ID에 코어 함수 형태로 알고리즘을 넣는 것임
+
+\begin{itemize}
+\item Default Algorithm
+\item Type-dependent algorithm
+\item Object-dependent algorithm
+\item Syntax-dependent algorithm
+\item Object layout
+\end{itemize}
+
+일단 (Type, Object, Syntax)-dependent algorithm 구역을 나누는건 manual
+
+Convert to
+\begin{itemize}
+\item algorithm => Function (AlgoCompiler)
+\item algorithm name => Global Id (generator)
+\item Builtin Object => Heap NamedAddr as Object (manual)
+\item Builtin Object function name => Heap Object .Code (generator)
+\item Type name => Internal Map object (generator)
+\item Type function name => Internal Map field (generator)
+\item Syntax => AST (parser)
+\item Syntax function name => Internal AST semantics field (generator)
+\end{itemize}
+
+\subsection{함수의 의미 번역 (algorithm => Function)}
+Function은 parameter와 body로 나뉨
+\subsubsection{parameter extraction} : HTML에 써있음 + 여러 특별한 말들 (with parameter * )
+Builtin function의 경우 specification 내에서 implicit하게 전해지는 parameter들이 있는데, (thisValue, newTarget) 이것을
+core에서 모두 명시적으로 받게 (지금은 javascript 단에서) 자동으로 고쳐준다.
+
+\subsubsection{body extraction ( AlgoCompiler )} : 이부분이 Human resource 많이 들어감
+여기서 rule에 따라 step을 만들어줌
+나눌 수도 있을 것 같은데 지금은 일단 instruction, expression, condition, type, value, reference을 나타내는 position을 분리하고 거기에 맞춰서 case별로 parser를 짬
+근데 똑같은 의미도 여러 다른 말로 표현하기 떄문에 지금은 모든 경우를 하나씩 써놓음
+또 같은 말도 context에 따라 의미가 다른 경우가 있음 (Return할때), 지금은 알고리즘의 종류에만 dependent하므로 알고리즘에 flag를 둬서 구분
+
+간단하지 않은 알고리즘의 경우는 1) core 내에서 표현될 수 있는 경우 Function을 만들어 모델링하거나 
+2) 지원하지 않는 경우가 있다
+
+\subsection{ Initial state configuration ( generator ) }
+기본적으로 함수는 모두 Global Id로 넣어놓고 필요할때 호출하는데, 필요한 함수가 정적이지 않고
+context-dependent하게 호출될 필요가 있음 ( Type, Syntax의 경우는 말 그대로 호출할 함수가
+스펙 내에서 context-dependent하고, Builtin object의 경우는 유저가 호출할 수 있게 Builtin function object로 넣으라고 써있음) 이 문제를 해결하는 3가지 방법 :
+1. Type의 경우 Core에 Type을 넣고 Type name => internal property를 자동 생성
+
+Internal method를 그 타입 이름과 같이 등록해서 그 타입 Obj를 생성할때 자동으로 field에 넣어줌
+Global Object를 만들기 위해 힙 만들어 줌 그 안에는 Field와 Function들이
+
+2. Syntax의 경우 Core에 ASTVal을 넣고 semantic을 쓸수 있게 해줌
+Syntax - directed algorithm을 실제 AST와 매칭 (AST node를 대상으로 실행해야 하는 알고리즘이 있으면 그 알고리즘을 찾아서 실행해 주는 것)
+specification을 보면 알고리즘 이름과 Syntax가 붙어 있기 떄문에 자동으로 뽑아낼 수 있음
+그 알고리즘을 실행할 떄 subAST 이름을 지칭하면서 사용하는데, 이를 subAST이름을 가진 argument를 넘겨줌으로써 실행할 수 있게 함
+있음
+
+3. Builtin Object의 경우 매뉴얼하게 initial heap에 유저가 접근할 수 있게 넣어줌
+
+\subsubsection{Js script evaluation}
+
+최종적으로 parse된 AST Value를 initial state의 global variable로 가지고 정해진 함수 (RunJobs)를 불러 ECMAScript를 실행한다
 

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/generator/ParserGenerator.scala
Reverted / Refactored parsers

@@ -78,7 +78,7 @@ object ParserGenerator {
       val pre = "lazy val"
       val llpre = if (LLs.isEmpty) "" else "resolveLL"
       val post = s"[$name] = memo {" + LINE_SEP +
-        s"""    case args @ List(${params.mkString(", ")}) => $llpre("""
+        s"""    case args @ List(${params.mkString(", ")}) => log($llpre("""
       nf.println(s"""  $pre $name: ESParser$post""")
       nf.print(noLLs.map {
         case (rhs, i) => getParsers(name, rhs.tokens, rhs.cond, i, false)
@@ -87,7 +87,7 @@ object ParserGenerator {
         case (rhs, i) => getParsers(name, rhs.tokens.drop(1), rhs.cond, i, true)
       }.mkString("," + LINE_SEP, " |" + LINE_SEP, ""))
       nf.println
-      nf.println(s"""    )""")
+      nf.println(s"""    ))("$name")""")
       nf.println(s"""    case v => throw WrongNumberOfParserParams(v)""")
       nf.println(s"""  }""")
     }
@@ -107,7 +107,7 @@ object ParserGenerator {
       })
 
       if (cond != "") parser = s"""(if (${cond}) ${parser} else MISMATCH)"""
-      s"""      $parser"""
+      s"""      log($parser)("$astName")"""
     }
 
     def appendParser(base: String, token: Token): String = token match {

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/package.scala

@@ -39,5 +39,5 @@ package object ase {
   val DEBUG_INTERP: Boolean = false
 
   // display progress in tests
-  val DISPLAY_TEST_PROGRESS = true
+  val DISPLAY_TEST_PROGRESS = false
 }

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/parser/Containers.scala

@@ -1,0 +1,20 @@
+package kr.ac.kaist.ase.parser
+
+import scala.util.parsing.combinator.Parsers
+import scala.util.parsing.input.{ Reader, Position }
+
+trait Containers { this: Parsers =>
+  type Container
+  def emptyContainer: Container
+  class ContainerReader[T](reader: Reader[T]) extends Reader[T] { outer =>
+    val container = emptyContainer
+    override def source = reader.source
+    override def offset = reader.offset
+    def first: T = reader.first
+    def rest: Reader[T] = new ContainerReader(reader.rest) {
+      override val container = outer.container
+    }
+    def pos: Position = reader.pos
+    def atEnd: Boolean = reader.atEnd
+  }
+}

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/parser/ESParsers.scala

@@ -1,19 +1,20 @@
 package kr.ac.kaist.ase.parser
 
-import kr.ac.kaist.ase.error.TooManySemicolonInsertion
-import kr.ac.kaist.ase.model.{ AST, Script }
-import kr.ac.kaist.ase.util.Useful.cached
 import kr.ac.kaist.ase.{ DEBUG_PARSER, DEBUG_SEMI_INSERT, LINE_SEP }
+import kr.ac.kaist.ase.model.{ AST, Script }
+import kr.ac.kaist.ase.util.Useful._
 import scala.collection.mutable
+import scala.util.matching.Regex
+import scala.util.parsing.combinator._
 import scala.util.parsing.input._
 
 trait ESParsers extends LAParsers {
-  // data containers
+  // container with cache for LAParser and right-most failed positions
+  def emptyContainer: Container = Container()
   case class Container(
-    val cache: mutable.Map[ParseCase[_], ParseResult[_]] = mutable.Map.empty,
+    var cache: Map[ParseCase[_], ParseResult[_]] = Map(),
     var rightmostFailedPos: Option[Position] = None
   )
-  def emptyContainer = Container()
 
   // automatic semicolon insertion
   def insertSemicolon(reader: ContainerReader[Char]): Option[String] = {
@@ -81,27 +82,31 @@ trait ESParsers extends LAParsers {
 
   // parser that supports automatic semicolon insertions
   override def parse[T](p: LAParser[T], in: Reader[Char]): ParseResult[T] = {
-    val MAX_ADDITION = 100
-    val init: (Option[ParseResult[T]], Reader[Char]) = (None, in)
-    (init /: (0 until MAX_ADDITION)) {
-      case ((None, in), _) =>
-        val reader = new ContainerReader(in)
-        p(emptyFirst, reader) match {
-          case (f: Failure) => insertSemicolon(reader) match {
-            case Some(str) => (None, new CharSequenceReader(str))
-            case None => (Some(f), reader)
-          }
-          case r => (Some(r), reader)
-        }
-      case (res, _) => res
-    } match {
-      case (Some(res), _) => res
-      case _ => throw TooManySemicolonInsertion(MAX_ADDITION)
+    val reader = new ContainerReader(in)
+    p(emptyFirst, reader) match {
+      case (f: Failure) => insertSemicolon(reader) match {
[…]

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/parser/LAParsers.scala

@@ -6,90 +6,38 @@ import scala.collection.mutable
 import scala.language.reflectiveCalls
 import scala.util.parsing.input._
 
-trait LAParsers extends Lexer {
-  val fail = failure("")
+trait LAParsers extends Lexer with Containers {
+  // failed parser
+  val failed: Parser[Nothing] = failure("")
+
+  // added cache for containers
   type Container <: {
-    val cache: mutable.Map[ParseCase[_], ParseResult[_]]
-  }
-
-  // Lookahaed parsers
-  class LAParser[+T](
-      val parser: FirstTerms => Parser[T],
-      val first: FirstTerms
-  ) {
-    def ~[U](_that: => LAParser[U]): LAParser[~[T, U]] = {
-      lazy val that = _that
-      new LAParser(
-        follow => this.parser(that.first ~ follow) ~ that.parser(follow),
-        this.first ~ that.first
-      )
-    }
-
-    def ~>[U](_that: => LAParser[U]): LAParser[U] = {
-      lazy val that = _that
-      new LAParser(
-        follow => this.parser(that.first ~ follow) ~> that.parser(follow),
-        this.first ~ that.first
-      )
-    }
-
-    def <~[U](_that: => LAParser[U]): LAParser[T] = {
-      lazy val that = _that
-      new LAParser(
-        follow => this.parser(that.first ~ follow) <~ that.parser(follow),
-        this.first ~ that.first
-      )
-    }
-
-    def |[U >: T](that: LAParser[U]): LAParser[U] = if (that eq MISMATCH) this else new LAParser(
-      follow => this.parser(follow) ||| that.parser(follow),
-      this.first + that.first
-    )
-
-    def ^^[U](f: T => U): LAParser[U] = new LAParser(
-      follow => this.parser(follow) ^^ f,
-      this.first
-    )
-
-    def ^^^[U](_v: => U): LAParser[U] = {
-      lazy val v = _v
-      new LAParser(
-        follow => this.parser(follow) ^^^ v,
-        this.first
-      )
-    }
-
-    def apply(follow: FirstTerms, in: ContainerReader[Char]): ParseResult[T] = parser(follow)(in)
-
-    def unary_-(): LAParser[Unit] = new LAParser(
-      follow => not(parser(follow)),
-      emptyFirst
-    )
-
-    def unary_+(): LAParser[T] = new LAParser(
-      follow => guard(parser(follow)),
[…]

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/parser/Lexer.scala

@@ -5,13 +5,13 @@ import scala.util.matching.Regex
 import scala.util.parsing.combinator.RegexParsers
 import scala.util.parsing.input.{ Reader, Position }
 
-trait Lexer extends RegexParsers with PackratParsers with UnicodeRegex {
+trait Lexer extends RegexParsers with UnicodeRegex {
   // not skip white spaces
   override def skipWhitespace = false
 
   // lexer type
-  type Lexer = PackratParser[String]
-  type FLexer = PackratParser[String => String]
+  type Lexer = Parser[String]
+  type FLexer = Parser[String => String]
   implicit def str2lexer(str: String): Lexer = literal(str)
   implicit def regex2lexer(r: Regex): Lexer = regex(r)
 
@@ -71,7 +71,7 @@ trait Lexer extends RegexParsers with PackratParsers with UnicodeRegex {
   lazy val Skip: Lexer = ((WhiteSpace | LineTerminator | Comment)*) ^^ { _.mkString }
 
   // no LineTerminator lexer
-  lazy val strNoLineTerminator: Lexer = +memo(Skip.filter(s => lines.findFirstIn(s).isEmpty))
+  lazy val strNoLineTerminator: Lexer = +Skip.filter(s => lines.findFirstIn(s).isEmpty)
 
   // resolve left recursions
   def resolveLL(f: Lexer, s: FLexer): Lexer = {

### 2019-07-31 src/main/scala/kr/ac/kaist/ase/parser/PackratParsers.scala

@@ -1,168 +1,0 @@
-package kr.ac.kaist.ase.parser
-
-import scala.util.parsing.combinator.Parsers
-import scala.collection.mutable
-import scala.language.implicitConversions
-import scala.util.parsing.input.{ Reader, Position }
-
-trait PackratParsers extends Parsers {
-  type Container
-  protected def emptyContainer: Container
-  class ContainerReader[+T](underlying: Reader[T]) extends Reader[T] { outer =>
-    val container: Container = emptyContainer
-    private[PackratParsers] val cache = mutable.HashMap.empty[(Parser[_], Position), MemoEntry[_]]
-    private[PackratParsers] def getFromCache[T](p: Parser[T]): Option[MemoEntry[T]] = {
-      cache.get((p, pos)).asInstanceOf[Option[MemoEntry[T]]]
-    }
-    private[PackratParsers] def updateCacheAndGet[T](p: Parser[T], w: MemoEntry[T]): MemoEntry[T] = {
-      cache.put((p, pos), w)
-      w
-    }
-    private[PackratParsers] val recursionHeads: mutable.HashMap[Position, Head] = mutable.HashMap.empty
-    private[PackratParsers] var lrStack: List[LR] = Nil
-    override def source: java.lang.CharSequence = underlying.source
-    override def offset: Int = underlying.offset
-    def first: T = underlying.first
-    def rest: Reader[T] = new ContainerReader(underlying.rest) {
-      override val container: Container = outer.container
-      override private[PackratParsers] val cache = outer.cache
-      override private[PackratParsers] val recursionHeads = outer.recursionHeads
-      lrStack = outer.lrStack
-    }
-    def pos: Position = underlying.pos
-    def atEnd: Boolean = underlying.atEnd
-  }
-  override def phrase[T](p: Parser[T]) = {
-    val q = super.phrase(p)
-    new PackratParser[T] {
-      def apply(in: Input) = in match {
-        case in: ContainerReader[_] => q(in)
-        case in => q(new ContainerReader(in))
-      }
-    }
-  }
-  private def getPosFromResult(r: ParseResult[_]): Position = r.next.pos
-  private case class MemoEntry[+T](var r: Either[LR, ParseResult[_]]) {
-    def getResult: ParseResult[T] = r match {
-      case Left(LR(res, _, _)) => res.asInstanceOf[ParseResult[T]]
[…]

### 2019-07-31 icse/compile.tex

@@
 
-\begin{itemize}
-\item Default Algorithm
-\item Type-dependent algorithm
-\item Object-dependent algorithm
-\item Syntax-dependent algorithm
-\item Object layout
-\end{itemize}
-
-일단 (Type, Object, Syntax)-dependent algorithm 구역을 나누는건 manual
-
-Convert to
-\begin{itemize}
-\item algorithm => Function (AlgoCompiler)
-\item algorithm name => Global Id (generator)
-\item Builtin Object => Heap NamedAddr as Object (manual)
-\item Builtin Object function name => Heap Object .Code (generator)
-\item Type name => Internal Map object (generator)
-\item Type function name => Internal Map field (generator)
-\item Syntax => AST (parser)
-\item Syntax function name => Internal AST semantics field (generator)
-\end{itemize}
-
 \subsection{함수의 의미 번역 (algorithm => Function)}
@@
 
-\subsection{ Initial state configuration ( generator ) }
-기본적으로 함수는 모두 Global Id로 넣어놓고 필요할때 호출하는데, 필요한 함수가 정적이지 않고
-context-dependent하게 호출될 필요가 있음 ( Type, Syntax의 경우는 말 그대로 호출할 함수가
-스펙 내에서 context-dependent하고, Builtin object의 경우는 유저가 호출할 수 있게 Builtin function object로 넣으라고 써있음) 이 문제를 해결하는 3가지 방법 :
-1. Type의 경우 Core에 Type을 넣고 Type name => internal property를 자동 생성
-
-Internal method를 그 타입 이름과 같이 등록해서 그 타입 Obj를 생성할때 자동으로 field에 넣어줌
-Global Object를 만들기 위해 힙 만들어 줌 그 안에는 Field와 Function들이
-
-2. Syntax의 경우 Core에 ASTVal을 넣고 semantic을 쓸수 있게 해줌
-Syntax - directed algorithm을 실제 AST와 매칭 (AST node를 대상으로 실행해야 하는 알고리즘이 있으면 그 알고리즘을 찾아서 실행해 주는 것)
-specification을 보면 알고리즘 이름과 Syntax가 붙어 있기 떄문에 자동으로 뽑아낼 수 있음
-그 알고리즘을 실행할 떄 subAST 이름을 지칭하면서 사용하는데, 이를 subAST이름을 가진 argument를 넘겨줌으로써 실행할 수 있게 함
-있음
-
-3. Builtin Object의 경우 매뉴얼하게 initial heap에 유저가 접근할 수 있게 넣어줌
-
-\subsubsection{Js script evaluation}
-
-최종적으로 parse된 AST Value를 initial state의 global variable로 가지고 정해진 함수 (RunJobs)를 불러 ECMAScript를 실행한다
-
 \begin{itemize}
@@
 \end{itemize}
+
+\section{ Initial state configuration ( generator ) }
+
+위와 같은 방법으로 언어의 AST와 파서, 그리고 언어의 명세에서 필요한 절차들을 실행 가능한 형태로 얻을 수 있다.
+그러나, 대부분의 언어는 실행을 하기 위해 초기 환경이 필요하며, 이러한 환경은 절차들과는 다른 형식으로 기술되어 있다.
+때로는 긴 문장 형식으로 설명되어 있기도 하고, 경우에 따라 암묵적으로 정의되기도 한다.
+따라서, 오버뷰에서 블랙박스로 표현되는 language dependent part에서는 실제 언어를 실행하기 위해 언어의 초기 환경을 구성한다.
+
+Convert to
+\begin{itemize}
+\item algorithm => Function (AlgoCompiler)
+\item algorithm name => Global Id (generator)
+\item Builtin Object => Heap NamedAddr as Object (manual)
+\item Builtin Object function name => Heap Object .Code (generator)
+\item Type name => Internal Map object (generator)
+\item Type function name => Internal Map field (generator)
+\item Syntax => AST (parser)
+\item Syntax function name => Internal AST semantics field (generator)
+\end{itemize}
+
+ ECMAScript 명세에서의 경우, 초기 환경은 Global Object와 source Script (AST), Intrinsic Object, 그리고 절차들을 적절한 context에서 참조하기 위한 binding environment로 구성된다.
+절차를 참조하여 실행하기 위한 방법은 크게 세 가지가 있다.
+첫 번째로 이름을 탑 레벨에서 불러 실행할 수 있고, 두 번째로 Object에 종속적인 절차를 이름으로 부를 수 있다.
+Object에 종속적인 절차는 Type에 종속적인 절차 또는 AST의 모양에 종속적인 절차로 나뉜다.
+ 우리는 각각의 경우를 처리할 수 있게 만들었다.
+
+ Global Object
+
+ 글로벌 오브젝트 안에는 빌트인 오브젝트들이 들어있으며, 각각의 빌트인 오브젝트는 빌트인 함수들과 field가 있다.
+빌트인 함수는 명세에 써있는 특정 절차들을 호출한다.
+글로벌 오브젝트를 지원하기 위해 간단하게 빌트인 오브젝트의 모양(가지고 있는 빌트인 함수 이름과 property)를 작성하면 자동으로 빌트인 함수 이름과 절차를 대응시켜 Core Heap에 할당해 넣어주었다.
+
+ Intrinsic Object
+
+ Intrinsic Object은 Specification 내에서 Global Object 하위에 있는 특정 Object를 참조할 때 사용하는 별칭이다.
+Intrinsic Object를 지칭하는 이름과 실제 Object의 위치가 specification 내에서 table로 설명되어 있으므로, HTML table을 파싱하여 Intrinsic Object의 별칭과 실제 Object의 주소가 대응되게 자동으로 넣었다.
+
+ Binding environment
+
+기본적으로 함수는 모두 Global Id로 넣어놓고 필요할때 호출하는데, 필요한 함수가 정적이지 않고
+context-dependent하게 호출될 필요가 있다.
+
+\begin{itemize}
+  \item Default Algorithm
+  \item Type-dependent algorithm
+  \item Syntax-dependent algorithm
+  \end{itemize}
+
+일단 (Type, Object, Syntax)-dependent algorithm 구역을 나누는건 manual
+
+Type에 종속적인 절차와 AST 모양에 종속적인 절차가 기술된 범위를 수동으로 지정하고, 이후 자동으로 그 Type과 AST 구조를 추출해서 각각 필요한 시점에 불릴 수 있게 할 수 있었다.
+AST 모양에 종속적인 절차를 예로 들면, 그 절차의 이름에 AST 모양을 serialization한 값을 붙여 유일한 이름을 만들고, AST에서 특정 절차를 수행할 때 그 모양을 serialization한 것과 이름을 합하여 그 AST에 종속적인 절차를 가져온다.
+Type의 경우도 같은 방법으로 절차를 가져올 수 있다.
+
+1. Type의 경우 Core에 Type을 넣고 Type name => internal property를 자동 생성
+
+Internal method를 그 타입 이름과 같이 등록해서 그 타입 Obj를 생성할때 자동으로 field에 넣어줌
+
+2. Syntax의 경우 Core에 ASTVal을 넣고 semantic을 쓸수 있게 해줌
+Syntax - directed algorithm을 실제 AST와 매칭 (AST node를 대상으로 실행해야 하는 알고리즘이 있으면 그 알고리즘을 찾아서 실행해 주는 것)
+specification을 보면 알고리즘 이름과 Syntax가 붙어 있기 떄문에 자동으로 뽑아낼 수 있음
+그 알고리즘을 실행할 떄 subAST 이름을 지칭하면서 사용하는데, 이를 subAST이름을 가진 argument를 넘겨줌으로써 실행할 수 있게 함
+있음
+
+\subsubsection{Js script evaluation}
+ 마지막으로 Parser를 통해 만들어진 AST를 참조할 수 있는 Id를 Core의 초기 환경에 추가한 후 실제 ECMAScript를 실행하기 위한 RunJobs 절차를 최초 실행 절차로 설정해 놓으면 실행하기 위한 모든 환경 설정이 끝난다.

### 2019-07-31 icse/compile.tex
write a paragraph

@@
 
-위와 같은 방법으로 언어의 AST와 파서, 그리고 언어의 명세에서 필요한 절차들을 실행 가능한 형태로 얻을 수 있다.
-그러나, 대부분의 언어는 실행을 하기 위해 초기 환경이 필요하며, 이러한 환경은 절차들과는 다른 형식으로 기술되어 있다.
-때로는 긴 문장 형식으로 설명되어 있기도 하고, 경우에 따라 암묵적으로 정의되기도 한다.
-따라서, 오버뷰에서 블랙박스로 표현되는 language dependent part에서는 실제 언어를 실행하기 위해 언어의 초기 환경을 구성한다.
+By above techniques, we can get the programming language's AST, Parser, and executable steps to run the abstract algorithm in the specification.
+But, to run the program with these primitives, Many languages need initial environment to run the program.
+It is mostly about initialization of builtin types, and it also includes specifying entry point of the program (fetch main function and fill arguments in Java, C, ..)
+These environments are sometimes described as steps of algorithm, but mostly it is not. 
+In our diagram, we categorized these part as language-dependent environment.
+It is hard to generate environment automatically, but it is relativly not too heavy to model it compared to modeling numerous algorithms used in runtime.
+In this section, we describre how to generate initial environment for ECMAScript to run defined semantics.
 
@@
 \begin{itemize}
-\item algorithm => Function (AlgoCompiler)
-\item algorithm name => Global Id (generator)
-\item Builtin Object => Heap NamedAddr as Object (manual)
-\item Builtin Object function name => Heap Object .Code (generator)
-\item Type name => Internal Map object (generator)
-\item Type function name => Internal Map field (generator)
-\item Syntax => AST (parser)
-\item Syntax function name => Internal AST semantics field (generator)
+\item algorithm name => Global Id
+\item Builtin Object function name => Heap Object .Code
+\item Type function name => Internal Map field
+\item Syntax function name => Internal AST semantics field
 \end{itemize}
@@
   \item Syntax-dependent algorithm
+  \item Builtin object algorithm
   \end{itemize}

### 2019-08-01 icse/compile.tex
convert a paragrah in section 6

@@
 
- ECMAScript 명세에서의 경우, 초기 환경은 Global Object와 source Script (AST), Intrinsic Object, 그리고 절차들을 적절한 context에서 참조하기 위한 binding environment로 구성된다.
-절차를 참조하여 실행하기 위한 방법은 크게 세 가지가 있다.
-첫 번째로 이름을 탑 레벨에서 불러 실행할 수 있고, 두 번째로 Object에 종속적인 절차를 이름으로 부를 수 있다.
-Object에 종속적인 절차는 Type에 종속적인 절차 또는 AST의 모양에 종속적인 절차로 나뉜다.
- 우리는 각각의 경우를 처리할 수 있게 만들었다.
+For ECMAScript Specification, initial environment consists of the builtin objects, Intrinsinc objects, and mapping from specification steps to corresponding reference.
 
@@
 
- 글로벌 오브젝트 안에는 빌트인 오브젝트들이 들어있으며, 각각의 빌트인 오브젝트는 빌트인 함수들과 field가 있다.
-빌트인 함수는 명세에 써있는 특정 절차들을 호출한다.
-글로벌 오브젝트를 지원하기 위해 간단하게 빌트인 오브젝트의 모양(가지고 있는 빌트인 함수 이름과 property)를 작성하면 자동으로 빌트인 함수 이름과 절차를 대응시켜 Core Heap에 할당해 넣어주었다.
+ In ECMAScript, there is a initial object which have references of builtin object. Each Builtin Object provides fields and function, just as ordinary object. But when its function is called,
+ the corresponding step specified in document should be called.
+To support global object, we make shape of builtin object and its attributes, and then we autoamtically match the step in specification to corresponding field in object by considering its function name.
 
@@
 
- Intrinsic Object은 Specification 내에서 Global Object 하위에 있는 특정 Object를 참조할 때 사용하는 별칭이다.
-Intrinsic Object를 지칭하는 이름과 실제 Object의 위치가 specification 내에서 table로 설명되어 있으므로, HTML table을 파싱하여 Intrinsic Object의 별칭과 실제 Object의 주소가 대응되게 자동으로 넣었다.
+ While Global Object is used for reference in ECMAScript language, It is also frequently used in ECMAScript specification. But Global Object layout is
+ formed for reference in Host language, it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
+ Correspondence between Intrinsic name and Builtin objects are shown in table, so we parse this table to generate global ID to object.
 
  Binding environment
+
+ 절차를 참조하여 실행하기 위한 방법은 크게 세 가지가 있다. 첫 번째로 이름을 탑 레벨에서 불러 실행할 수 있고, 두 번째로 Object에 종속적인 절차를 이름으로 부를 수 있다. Object에 종속적인 절차는 Type에 종속적인 절차 또는 AST의 모양에 종속적인 절차로 나뉜다.
 

### 2019-08-01 icse/compile.tex
edit section 6

@@
 
-For ECMAScript Specification, initial environment consists of the builtin objects, Intrinsinc objects, and mapping from specification steps to corresponding reference.
+For ECMAScript Specification, initial environment consists of the builtin objects, Intrinsincs, and binding environment of specification steps.
 
- Global Object
+Builtin objects
 
@@
 
- Intrinsic Object
+ Intrinsics
 
- While Global Object is used for reference in ECMAScript language, It is also frequently used in ECMAScript specification. But Global Object layout is
- formed for reference in Host language, it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
+ While Builtin objects can be used to refer itself in ECMAScript language, It is also frequently used in ECMAScript specification. But name of builtin objects
+ are defiend for reference in Host language, it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
  Correspondence between Intrinsic name and Builtin objects are shown in table, so we parse this table to generate global ID to object.
@@
 
- 절차를 참조하여 실행하기 위한 방법은 크게 세 가지가 있다. 첫 번째로 이름을 탑 레벨에서 불러 실행할 수 있고, 두 번째로 Object에 종속적인 절차를 이름으로 부를 수 있다. Object에 종속적인 절차는 Type에 종속적인 절차 또는 AST의 모양에 종속적인 절차로 나뉜다.
-
- 기본적으로 함수는 모두 Global Id로 넣어놓고 필요할때 호출하는데, 필요한 함수가 정적이지 않고
-context-dependent하게 호출될 필요가 있다.
-
+ In specification, All algorithm has name to refer it, but some algorithms have same names and they are called in context-dependent way.
  \begin{itemize}
-  \item Default Algorithm
+  \item Global Algorithm
   \item Type-dependent algorithm
@@
 
-일단 (Type, Object, Syntax)-dependent algorithm 구역을 나누는건 manual
+ There is four types of algorithm. 
+ First is global algorithm that can be called by just name, 
+ second is set of algorithms which are bounded in specific type of object, 
+ third is set of algorithms which are bounded in AST,
+ and forth is set of algorithms which correspond to builtin object function.
 
-Type에 종속적인 절차와 AST 모양에 종속적인 절차가 기술된 범위를 수동으로 지정하고, 이후 자동으로 그 Type과 AST 구조를 추출해서 각각 필요한 시점에 불릴 수 있게 할 수 있었다.
-AST 모양에 종속적인 절차를 예로 들면, 그 절차의 이름에 AST 모양을 serialization한 값을 붙여 유일한 이름을 만들고, AST에서 특정 절차를 수행할 때 그 모양을 serialization한 것과 이름을 합하여 그 AST에 종속적인 절차를 가져온다.
-Type의 경우도 같은 방법으로 절차를 가져올 수 있다.
+ We set builtin object function algorithms when initialzing builtin object, so we descibe about rest three algorithms.
 
-1. Type의 경우 Core에 Type을 넣고 Type name => internal property를 자동 생성
+First, we categorized sections by types of algorithm. Builtin object has several own sections to describe its functions,
+so it is easy to extract builtin object algorithms. Type-dependent algorithms and syntax-dependent algorithms has their own layout, so it
+can be extracted. Rest algorithms are considered as global algorithm.
 
-Internal method를 그 타입 이름과 같이 등록해서 그 타입 Obj를 생성할때 자동으로 field에 넣어줌
+We just convert global algorithms to function, and bind global identifier to that function to call it by algorithm name.
 
-2. Syntax의 경우 Core에 ASTVal을 넣고 semantic을 쓸수 있게 해줌
-Syntax - directed algorithm을 실제 AST와 매칭 (AST node를 대상으로 실행해야 하는 알고리즘이 있으면 그 알고리즘을 찾아서 실행해 주는 것)
-specification을 보면 알고리즘 이름과 Syntax가 붙어 있기 떄문에 자동으로 뽑아낼 수 있음
-그 알고리즘을 실행할 떄 subAST 이름을 지칭하면서 사용하는데, 이를 subAST이름을 가진 argument를 넘겨줌으로써 실행할 수 있게 함
-있음
+For type-denpendent algorithms, we organized map from algorithm name to function for each type,
+ and we insert functions as propertiy of object when such type of object is created.
 
-\subsubsection{Js script evaluation}
- 마지막으로 Parser를 통해 만들어진 AST를 참조할 수 있는 Id를 Core의 초기 환경에 추가한 후 실제 ECMAScript를 실행하기 위한 RunJobs 절차를 최초 실행 절차로 설정해 놓으면 실행하기 위한 모든 환경 설정이 끝난다.
+For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call AST-dependent algorithm which requires AST Value and algorithm name.
+To insert functions, we gather which AST can be applied to a function. Also, to use subAST structure, we passes subAST in function as argument.

### 2019-08-01 icse/compile.tex

@@
 
-By above techniques, we can get the programming language's AST, Parser, and executable steps to run the abstract algorithm in the specification.
-But, to run the program with these primitives, Many languages need initial environment to run the program.
-It is mostly about initialization of builtin types, and it also includes specifying entry point of the program (fetch main function and fill arguments in Java, C, ..)
-These environments are sometimes described as steps of algorithm, but mostly it is not. 
+In this section, we describre how to generate initial environment for ECMAScript to run defined semantics. 
+We can extract programming language's AST, Parser, and executable algorithm in the specification with minimal human effort.
+With these primitives, we can build entire system for evaluating target language.
+
+Initial environment of language is mostly about initialization of builtin types, or entry point of the program, etc.
 In our diagram, we categorized these part as language-dependent environment.
-It is hard to generate environment automatically, but it is relativly not too heavy to model it compared to modeling numerous algorithms used in runtime.
-In this section, we describre how to generate initial environment for ECMAScript to run defined semantics.
+For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs, and Algorithm scope. We will describe how to generate each component.
 
-Convert to
-\begin{itemize}
-\item algorithm name => Global Id
-\item Builtin Object function name => Heap Object .Code
-\item Type function name => Internal Map field
-\item Syntax function name => Internal AST semantics field
-\end{itemize}
+\subsection{Builtin objects}
 
-For ECMAScript Specification, initial environment consists of the builtin objects, Intrinsincs, and binding environment of specification steps.
+ In ECMAScript, there is the object which have references of builtin object. Each Builtin Object provides fields and function, just as ordinary object. When its function is called,
+ the corresponding algorithm specified in the document should be called.
+To support builtin object, we make structure of builtin object and its attributes, and then we autoamtically map corresponding field to the algorithm in specification by matching its function name.
 
-Builtin objects
+ \subsection{Intrinsics}
 
- In ECMAScript, there is a initial object which have references of builtin object. Each Builtin Object provides fields and function, just as ordinary object. But when its function is called,
- the corresponding step specified in document should be called.
-To support global object, we make shape of builtin object and its attributes, and then we autoamtically match the step in specification to corresponding field in object by considering its function name.
+ While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently refered in specification. But name of builtin objects
+ are defiend for reference in Host language, so it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
+ Map between Intrinsic name and Builtin objects are available in speicificaion as table form , so we parse this table to generate global identifier to object.
 
- Intrinsics
-
- While Builtin objects can be used to refer itself in ECMAScript language, It is also frequently used in ECMAScript specification. But name of builtin objects
- are defiend for reference in Host language, it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
- Correspondence between Intrinsic name and Builtin objects are shown in table, so we parse this table to generate global ID to object.
-
- Binding environment
+ \subsection{Algorithm scope}
 
  In specification, All algorithm has name to refer it, but some algorithms have same names and they are called in context-dependent way.
+ There is four types of algorithm. 
  \begin{itemize}
-  \item Global Algorithm
-  \item Type-dependent algorithm
-  \item Syntax-dependent algorithm
-  \item Builtin object algorithm
+  \item Global algorithm: they can be called by name in any context
+  \item Type-dependent algorithm: they are bounded in specific type of object
+  \item Syntax-dependent algorithm: they are bounded in AST
+  \item Builtin function algorithm: they correspond to builtin function
   \end{itemize}
-
- There is four types of algorithm. 
- First is global algorithm that can be called by just name, 
- second is set of algorithms which are bounded in specific type of object, 
- third is set of algorithms which are bounded in AST,
- and forth is set of algorithms which correspond to builtin object function.
-
- We set builtin object function algorithms when initialzing builtin object, so we descibe about rest three algorithms.
 
@@
 
+We mapped builtin function algorithms in environment when initialzing builtin object, so we descibe about rest three algorithms.
+
+\subsubsection{Global algorithm}
+
 We just convert global algorithms to function, and bind global identifier to that function to call it by algorithm name.
+
+\subsubsection{Type-dependent algorithm}
 
@@
 
+ \subsubsection{Syntax-dependent algorithm}
 For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call AST-dependent algorithm which requires AST Value and algorithm name.

### 2019-08-01 icse/compile.tex
edit section 6

@@
 
-\section{ Initial state configuration ( generator ) }
+\section{ Building entire system to evaluate code }
 
-In this section, we describre how to generate initial environment for ECMAScript to run defined semantics. 
-We can extract programming language's AST, Parser, and executable algorithm in the specification with minimal human effort.
-With these primitives, we can build entire system for evaluating target language.
+In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
+environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript langauge.
 
-Initial environment of language is mostly about initialization of builtin types, or entry point of the program, etc.
-In our diagram, we categorized these part as language-dependent environment.
-For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs, and Algorithm scope. We will describe how to generate each component.
+\subsection{Extracting specification}
+First step is to collect language specification and extract component that we can process autoamtically. For our target langauge, ECMAScript, has HTML format of specification in their website, and
+in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
+We get these information by parsing HTML document, and passing these result to our previous moudle to get AST, Parser, and executable algorithms automatically.
 
-\subsection{Builtin objects}
+Rest part is initial environment of language such as initialization of builtin types, or entry point of the program, etc.
+
+\subsection{Generating initial environment for evaluating}
+For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs. We will describe how to generate each component.
+
+\subsubsection{Builtin objects}
 
@@
 
- \subsection{Intrinsics}
+ \subsubsection{Intrinsics}
 
@@
 
+In ECMAScript specification, there are some objects which has similar interface, but they have different algorithms.
+
+For Example, Object Environment Record and Declarative Environment Record is different object in specification, but they have same name of algorithm(i.e. HasBinding(N))
+
+In this case, algorithm is called in context of calling Object(i.e. x.HasBinding(N)). We name it type-dependent algorithm.
 For type-denpendent algorithms, we organized map from algorithm name to function for each type,
@@
  \subsubsection{Syntax-dependent algorithm}
-For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call AST-dependent algorithm which requires AST Value and algorithm name.
-To insert functions, we gather which AST can be applied to a function. Also, to use subAST structure, we passes subAST in function as argument.
+
+ Like type-dependent algorithm, there are many AST Value (in specification, it is called Parse Node) which uses same name of algorithm but the content is differnt.
+The most frequent example is Evaluation of the AST Value. every Evaluation algorithm has same name, but each algorithm can be applied for specific syntax. We name it syntax-dependent algorithm.
+For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call syntax-dependent algorithm which requires AST Value and algorithm name.
+We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

### 2019-08-01 icse/main.tex
add kotex (temporal)
Added related works
Fill in contents of parsers

@@
 \documentclass[sigconf,review]{acmart}
+
+\usepackage{kotex}
+\usepackage[T1]{fontenc}
+\usepackage{beramono}
+\usepackage{listings}
+\usepackage{xcolor}
+\usepackage{qtree}
+\usepackage{ulem}
+\usepackage{graphicx}
+\usepackage{listings}
+
+% removed ACM references
 \settopmatter{printacmref=false}
 
-\input{fonts}
+% scala code style
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+\lstdefinestyle{myScalastyle}{
+  frame=tb,
+  language=scala,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  frame=single,
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3,
+}
+
+% load macros
 \input{macros}
@@
 \maketitle
-
 \begin{abstract}
@@
 
-% \keywords
+% TODO \keywords
 
@@
 
-% \bibliographystyle{ACM-Reference-Format}
-% \bibliography{ref}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{ref}
 

### 2019-08-01 icse/parser.tex
Fill in contents of parsers

@@
-\section{Parser Generation}
+\section{Parser Generator}
 
@@
 from given ECMAScript specifications. First, we explain \( \bnfes \), an extension
-of BNF used in ECMAScript to describe lexical and syntactic grammars of JavaScript.
-We defined a recursive descent parser generator to support \( \bnfes \) notations.
-We implemented our idea by extending the basic Scala parser combinator.
-The implementation also support the automatic semicolon insertion,
-one of the most distinct parsing feautres in ECMAScript.
+of Backus-Naur form(BNF) used in ECMAScript to describe lexical and
+syntactic grammars of JavaScript. We propose a recursive descent parser generator
+that both supports backtracking and lookahead tokens to correctly support
+\( \bnfes \) notations. We implement our idea by extending Scala parser combinators.
+The implementation also supports the automatic semicolon insertion,
+one of the most distinctive parsing features in ECMAScript.
 
@@
 
+Backus-Naur form(BNF) is proposed to represent context-free grammars(CFGs).
 ECMAScript provides their lexical and syntactic grammars using \( \bnfes \),
-an extension of Backus-Naur form for ECMAScript.
-\( \bnfes \) consists of a number of \textit{productions}
-with the following forms:
+an extension of BNF for ECMAScript.
+It consists of a number of \textit{productions} with the following forms:
 \[
-  \nt(\param_1, \cdots, \param_k) ::=
+  \NT{A}(\param_1, \cdots, \param_k) ::=
   (\cond_1 \Rightarrow)^? \rhs_1 \mid
@@
 \]
-The left-hand side represents a parametric nonterminal \( \nt \) with
+The left-hand side represents a parametric non-terminal \( \NT{A} \) with
 multiple boolean parameters \( \param_1, \cdots, \param_n \).
+If a non-terminal takes no parameters, parenthesis are omitted for the brevity.
 A production has multiple right-hand sides with optional conditions.
-The condition \( \cond \) is either \( \param_i \) or \( ! \param_i \),
-the negation of \( \param_i \).
+A condition \( \cond \) is either a boolean parameter \( \param \)
+or its negation \( ! \param \).
 For example, consider the following production:
 \[
-  \nt(\param) ::= \param \Rightarrow \code{a}
-  \mid \; !\param \Rightarrow \code{b}
-  \mid  \code{c}
+  \NT{A}(\param) ::= \param \Rightarrow \T{a}
+  \mid \; !\param \Rightarrow \T{b}
+  \mid  \T{c}
 \]
-Then, \( \nt(\kwt) \) means \( \code{a} \mid \code{c} \)
-and \( \nt(\kwf) \) means \( \code{b} \mid \code{c} \).
+Then, \( \NT{A}(\kwt) \) means \( \T{a} \mid \T{c} \)
+and \( \NT{A}(\kwf) \) means \( \T{b} \mid \T{c} \).
 
@@
 \begin{itemize}
-  \item \( \boxed{\symb} \):
-    basic symbols; terminal \( \code{x} \) or
-    non-terminal \( \nt(\argument_1, \cdots, \argument_k) \)
+  \item \( \boxed{\epsilon} \): empty sequence
+  \item \( \boxed{\T{a}} \): terminal symbols
+  \item \( \boxed{\NT{A}(\argument_1, \cdots, \argument_k)} \): non-terminal symbols
   \item \( \boxed{\symb?} \): optional symbols
@@
   \item \( \boxed{\symb \butnot \symb'} \): exclusive symbols
-  \item \( \boxed{\nolt} \): no line terminator symbols
+  \item \( \boxed{\nolt} \): no line-terminator symbols
 \end{itemize}
 
-Basic symbols are either terminal or non-terminal.
-A non-terminal symbol \( \nt(\argument_1, \cdots, \argument_k) \)
+The empty sequence \( \epsilon \) passes without any conditions
+and a terminal symbol is any token.
+A non-terminal symbol \( \NT{A}(\argument_1, \cdots, \argument_k) \)
 takes multiple arguments and each of them \( \argument_i \) is
 a boolean value \( \kwt \), \( \kwf \) or a parameter \( \param_i \).
-An optional symbol \( \symb? \) is same with \( \epsilon \mid \symb \)
-where \( \epsilon \) denotes the empty sequence.
+An optional symbol \( \symb? \) is same with \( \symb \mid \epsilon \).
 A positive(negative) lookahead symbol \( +\symb \)(\( -\symb \))
@@
 and then checks that the parsing result does not correspond to \( \symb' \).
-The no line terminal symbol \( \nolt \) is a special symbol
+The no-line terminal symbol \( \nolt \) is a special symbol
 that restricts the white spaces between two other symbols.
 
-\subsection{SFDF-Backtrack Parsing}
+\subsection{Lookahead Parsers}
 
-Our goal is to automatically generate readable JavaScript parsers from ECMAScript
-grammars written in \( \bnfes \). There are several options for existing paraser generators.
-Among them, we decide to extend Packrat parsers~\cite{packrat} 
-with 
-to support \( \bnfes \) Packrat parsers are first proposed by
-
-assumptions:
-
-Unambiguous
+Our goal is to automatically generate JavaScript parsers from ECMAScript
+grammars written in \( \bnfes \). There are several options for parser generators;
+ANTLR, Lex/Yacc, Bison, and PEG. Among them, we decided to use
+Scala parser combinators defined under \textit{parsing expression grammars(PEG)}.
+PEG follows top-down (LL-style) parsing approaches and there are two different
+categories; predictive parser and recursive descent with backtracking.
+Predictive parsers are widely used in general and LL(k) parsers are typical
+examples of predictive top-down parsers.
+They choose a right-hand sides based on predicting the next tokens in deterministic
+manners. In the other hand, PEG is a recursive descent parser with
+\textit{backtracking}. It visits each right-hand side in order and backtrack
+into the previous rules when parsing fails.
+Thus, it is possible to use each production itself as a parser
+in PEG. Moreover, There are several reasons why we extend Scala parser combinator
+to deal with ECMAScript lexers and grammars written in \( \bnfes \):
 
@@
   \item \textbf{Context-Sensitive Tokens} ECMAScript tokens are context-sensitive
-    because of the regular expressions and template strings.
-    For example, the code \( \code{/x/g} \) might be a regular expression token
-    or four tokens that represent division by variables \( \code{x} \) and \( \code{g} \),
-    depends on enclosing contexts. Thus, tokenizers should be evaluated during the parser
-    not before the parser.
-  \item \textbf{\( \bnfes \) Symbols} Several symbols notations in \( \bnfes \) are
-    not trivial to be converted into normal BNF rules. 
+    because of the JavaScript regular expressions and template strings.
+    For example, the code \( \code{/x/g} \) might be a single regular expression token
+    or four tokens that represent division by variables \( \code{x} \) and \( \code{g} \)
+    depending on enclosing contexts. Thus, lexers should be evaluated during the parser
+    not before the parser. Scala parser combinators also treat lexers as parsers thus
+    it is possible to use appropriate lexers depending on the parsing contexts.
+  \item \textbf{\( \bnfes \) Symbols} PEG is suitable grammars to represent
+    \( \bnfes \) symbols. We will explain detailed conversion from
+    \( \bnfes \) grammars into Scala parser combinators in section~\ref{sec:convert-bnfes}.
+  \item \textbf{Multiple Starting Non-terminals} After ECMAScript 6, grammars support
+    both scripts and modules as starting point of parsers. In Scala parser combinators,
+    it is possible to parse input string using any non-terminals as parsers.
+  \item \textbf{Parsing in Run-time} JavaScript supports \( \code{eval} \)
+    function that parses given JavaScript String values into codes and evaluates them.
+    Moreover, there is special phrases ``the \( N \) that is \textit{covered by}
+    \( P \)'' in syntax-directed abstract algorithms.
+    It means that the syntax tree \( P \) is parsed with generalized parsers because
+    it needs evaluation contexts to correctly choose specific parsers.
+    When the interpreter meets the above phrase, the specific parsers are now
+    decided into \( N \) thus we should parse again the given syntax tree \( P \) with
+    the non-terminal \( N \) in run time.
 \end{itemize}
 
-%  Thus, we extend
+\subsubsection{Prioritized choices}
+However, unfortunately, there is fundamental problem in PEG-based parsers;
+\textit{prioritized choices}.
+In PEG, the pipe operator ( \( \mid \) ) denotes a prioritized choice,
+unlike CFG that deals with it in non-deterministic manners.
+It means that PEG always pick the first success right-hand side even though
+there exist other success choices in remaining right-hand sides.
+While ECMAScript grammars are deterministic languages, some non-terminals
+accepts multiple right-hand sides for a given input strings.
+It distort the meaning of ECMAScript grammars.
+For example, consider the following simplified grammars for JavaScript expressions:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \NT{A} &::=& \NT{T} \T{;} \mid \NT{A} \; \T{+} \; \NT{T} \T{;} \\
+    \NT{T} &::=& \T{a} \mid \T{a} \T{(} \T{b} \T{)}\\
+  \end{array}
+\]
+While it represents deterministic grammar, the non-terminal \( \NT{T} \)
+should accept both right-hand sides if the given string is \( \code{a(b);} \).
+However, PEG-based parser fails to parse it
+because the first right-hand side \( \T{a} \) is always tried
+first in the non-terminal \( \NT{T} \).
+Thus, the latter one \( \T{a} \T{(} \T{b} \T{)} \) is not reachable in PEG.
+A simple solution is to change the order of right-hand sides;
+\( \NT{T} ::= \T{a} \T{(} \T{b} \T{)} \mid \T{a} \).
+However, it is not easy to ensure which order is correct
+because their inclusion relationship should be calculated.
+Moreover, some productions are not possible to resolve them
+by simply re-ordering right-hand sides:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \NT{A} &::=& \NT{B} \; \T{b}\\
+    \NT{B} &::=& \T{a} \mid \T{a} \; \T{b}\\
+  \end{array}
+\]
+The non-terminal \( \NT{A} \) should successfully parse two strings \( \code{ab} \)
+and \( \code{abb} \). However, the non-terminal \( \NT{A} \) accepts only
+\( \code{ab} \) and it accepts only \( \code{abb} \) when \( \NT{B} \) has
+reversed order. It means that we should re-structure
+the above rules to accept both strings in traditional PEG grammars.
 
-% There are two different parsing approaches:
-% ``top-down'' approach (LL-style parsing) and
-% ``bottom-up'' approach (LR-style parsing).
-% Top-down approach support 
-% 
-% There are two different kinds of parsers: top-down parsing, bottom-up parsing.
-% 
-% 
-% 
-% Such features could be easily represented in Parsing Expression Grammars (PEGs).
-% 
-% 
-% 
-% Backus–Naur form(BNF)에 다섯 가지의 방식을 추가한 형태로 lexical 및 syntactic grammar를 제공한다.
-% 각각의 
-combination of recursive descent parsers with predictive parsers
+\subsubsection{Lookahead tokens}
+To alleviate such problems, we propose \textit{lookahead parsers},
+which is extended recursive descent parsers with backtracking and
+\textit{lookahead tokens}.
+It keeps track of the next possible tokens using statically
+calculated first tokens of each symbols using algorithm in
+Figure~\ref{fig:first-tokens}. For example, the following steps explain
+how to utilize lookahead tokens during parsing processes with
+the input \( \code{a(b);} \):
 
-static first terms and dynamic follow terms
+\begin{figure}
+\centering
+\[
+  \begin{array}{l@{~}c@{~}l}
+    \rhsfirst{\symb_1 \cdots \symb_n} &=& \symbfirst{\symb_1} \firstplus
+    \symbfirst{\symb_2 \cdots \symb_n}\\
+    && \text{where} \; x \firstplus y = \left\{
+    \begin{array}{ll}
+      x \cup y & \text{if} \; \emptyfirst \in x\\
+      x & \text{otherwise}\\
+    \end{array}
+    \right.\\
+    \symbfirst{\epsilon} &=& \{ \emptyfirst \}\\
+    \symbfirst{\T{a}} &=& \{ \T{a} \} \\
+    \symbfirst{\NT{A}(\argument_1, \cdots, \argument_k)} &=&
+    \rhsfirst{\rhs_1} \cup \cdots \cup \rhsfirst{\rhs_n}\\
+    && \text{where} \; \NT{A}(\argument_1, \cdots, \argument_k) =
+    \rhs_1 \mid \cdots \mid \rhs_n\\
+    \symbfirst{\symb?} &=& \symbfirst{\symb} \cup \{ \emptyfirst \}\\
+    \symbfirst{+\symb} &=& \symbfirst{\symb}\\
+    \symbfirst{-\symb} &=& \{ \emptyfirst \}\\
+    \symbfirst{\symb \butnot \symb'} &=& \symbfirst{\symb}\\
+    \symbfirst{\nolt} &=& \{ \emptyfirst \}\\
+  \end{array}
+\]
+\caption{Over-approximated first tokens of \( \bnfes \) symbols}
+\label{fig:first-tokens}
+\end{figure}
 
-\paragraph{Static-first dynamic-follow}
-% PEG를 그대로 사용하면 backtrack을 이미 성공한 곳에서는 하지 않기 때문에 lookahead를 추가함
+\Tree[.\(\NT{A}[\emptyfirst]\)
+[.\(\NT{T}\T{;}[\emptyfirst]\)
+[.\(\NT{T}[\T{;}]\)
+\sout{\(\T{a}[\T{;}]\)}
+[.\(\T{a}\T{(}\T{b}\T{)}[\T{;}]\)
+[.\(\T{a}[\T{(}]\) \(\boxed{\T{a}}\) ]
+[.\(\T{(}\T{b}\T{)}[\T{;}]\)
+[.\(\T{(}[\T{b}]\) \(\boxed{\T{(}}\) ]
+[.\(\T{b}\T{)}[\T{;}]\)
+[.\(\T{b}[\T{)}]\) \(\boxed{\T{b}}\) ]
+[.\(\T{b}\T{)}[\T{;}]\)
+[.\(\T{)}[\T{;}]\) \(\boxed{\T{)}}\) ] ] ] ] ] ]
+[.\(\T{;}[\emptyfirst]\)
+\(\boxed{\T{;}}\) ] ] ]
 
-% LL(1)-parser의 정의에서 사용하는 first / follow 개념을 확장하여
+Each node \( \symb^*[\la] \) denotes a sequence of symbols \( \symb^* \) with
+lookahead tokens \( \la \), which is the set of tokens.
+The parsing process follows pre-order traversals.
+It starts from the starting non-terminal \( \NT{A} \) with the special
+lookahead \( \emptyfirst \), which denotes the end of inputs.
+Then, it visits the first right-hand side \( \NT{T} \T{;} \) with the same lookahead.
+Each symbol will be visited with the corresponding lookahead, that is the
+first tokens of the right next symbol.
+For example, for the symbol \( \NT{T} \), the next symbol is \( \T{;} \)
+and its first token is itself. Thus, the parser visits \( \NT{T} \)
+with the lookahead \( \T{;} \). The most important point in this parsing process
+is the first right hand side \( \T{a} \) of the non-terminal \( \NT{T} \).
+It is visited with the lookahead \( \T{;} \) but the next token of the input string
+\( \code{a(b);} \) is \( \code{(} \) not \( \code{;} \).
+Thus, it fails to parse the input string even though the current token is
+same with the terminal \( \T{a} \).
+Thus, the parser could visit the next right-hand side \( \T{a}\T{(}\T{b}\T{)} \)
+and finally the input \( \code{a(b);} \) is successfully parsed.
 
-% static한 first를 구하고 dynamic하게 오는 follow를 통해 결정함
+We formally define semantics of lookahead parsers
+in Figure~\ref{fig:laparser} by converting them into the given parsers.
+The helper function \( \getlap{\la} \) generates a parser by combining all
+tokens in the lookahead \( \la \) using prioritized choices.
+In this case, the order does not change the semantics of lookahead parsers
+because \( \getlap{\la} \) just check whether it contains the given token or not.
+
+\begin{figure}
+\centering
+\[
+  \begin{array}{l@{~}c@{~}l}
+    (\symb_1 \cdots \symb_n)[\la] &=&
+    \symb_1[\symbfirst{\symb_2 \cdots \symb_n} \firstplus \la] \;
+    (\symb_1 \cdots \symb_n)[\la]\\
+    \epsilon[\la] &=& +\getlap{\la}\\
+    \T{a}[\la] &=& \T{a} \; +\getlap{\la} \\
+    \NT{A}(\argument_1, \cdots, \argument_k)[\la] &=&
+    \rhs_1[\la] \mid \cdots \mid \rhs_n[\la]\\
+    && \text{where} \; \NT{A}(\argument_1, \cdots, \argument_k) =
+    \rhs_1 \mid \cdots \mid \rhs_n\\
+
+    \symb?[\la] &=& \symb[\la] \mid \epsilon[\la]\\
+    (\pm\symb)[\la] &=& \pm(\symb[\la]) \\
+    (\symb \butnot \symb')[\la] &=& \symb[\la] \butnot \symb'\\
+    \nolt &=& \nolt \; +\getlap{\la}\\
+  \end{array}
+\]
+\caption{Formal semantics of lookahead parsers}
+\label{fig:laparser}
+\end{figure}
 
@@
 
-% - 실제 EMCAScript production(필요?) -> Our definition -> AST / Parser
-% - code size 줄이기 위해서 모두 풀어헤치지 않고 함수로 변환했다.
-% - autmoatic semicolon insertion도 해주는데 fail한 token 중에 가장 나중에 나오는 부분을 찾아서
-%   offending token으로 지정하고 이를 기반으로 semicolon insertion을 진행
-%   => 넣었을 때 안넣었을 때 test262 parsing 성공률 비교하면 좋을 듯
+We implement lookahead parsers by extending Scala parser combinators.
+We define \( \code{LAparser} \) trait to represent lookahead parser
+and it has two members; first tokens and a function from lookahead tokens into parsers
+described in Figure~\ref{fig:first-tokens} and Figure~\ref{fig:laparser}, respectively.
+There exists two different issues in implementing the lookahead parsers in Scala
+to treat ECMAScript syntax written in \( \bnfes \).
+
+\paragraph{Performances} One of critical weak points of recursive descent parsing
+with backtracking is its performance. Basically, it needs exponential time related
+to the input size because of the backtracking mechanism. Fortunately,
+Ford et al~\cite{packrat} proposed Packrat parsing that provides linear
+time complexity based on memoization technique. The main idea is that it treats
+each parser as a function from the current input position into the parsing result.
+Thus, it just memoizes each parser based on input positions. It dramatically reduces
+the redundant parsing trials. In a similar way, we treat each lookahead parser as
+a function from a pair of lookahead tokens and input positions into parsing results.
+
+\paragraph{Left Recursions} The other issue is that recursive descent parsers
+does not support left recursions in grammars. If a grammar has left recursions,
+the parser falls into an infinite loop. To resolve this problem,
+Warth et al~\cite{packrat-lr} proposed a way to support not only direct left
+recursions but also indirect ones in Packrat parsing.
+The basic idea is extends the memoization technique to support grow the parsing
+results. We believe that it is conceptually possible to support direct and indirect
+left recursions by applying the Warth's approach.
+\inred{However, fortunately, it is not necessary to handle indirect left
+recursions in order to deal with ECMAScript syntax because the all
+versions of ECMAScript only have direct left recursions.}
+Thus, we decided to just remove direct left recursions by defining sub productions
+and carefully build the abstract syntax trees.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=6em]{img/array_literal.png}
+  \[
+    \begin{array}{l}
+      \NT{ArrayLiteral}(Yield, Await) ::=\\
+      \qquad \T{[} \; Elision? \; \T{]}\\
+      \qquad \T{[} \; ElementList(Yield, Await) \; \T{]}\\
+      \qquad \T{[} \; ElementList(Yield, Await) \; \T{,} Elision? \; \T{]}\\
+    \end{array}
+  \]
+  \caption{Array literals defined in ES2019 and its \( \bnfes \)}
+  \label{fig:array-literal}
+\end{figure}
+
+\subsubsection{AST generations}
+We first automatically generate abstract syntax tree(AST) as Scala case classes
+from the given \( \bnfes \) grammar that represents a version of ECMAScript.
+For lexical grammars, their structures are not used in ECMAScript semantics
+thus we gives them String types. For parser grammars, we need to
+automatically synthesize a Scala file that has classes of syntax trees.
+For each production \(
+  \NT{A}(\param_1, \cdots, \param_k) ::=
+  (\cond_1 \Rightarrow)^? \rhs_1 \mid
+  \cdots \mid
+  (\cond_n \Rightarrow)^? \rhs_n
+\), the AST generator defines the \( \code{A} \) trait and
+multiple sub classes \( \code{Ai} \) of \( \code{A} \) for right-hand sides.
+Each class \( \code{Ai} \) has non-terminals as member variables and
+its type is the corresponding non-terminal type. Additionally, only optional
+non-terminal symbol has \( \code{Option[\_]} \) types.
+For instance, the \( ArrayLiteral \) production
+in~Figure\ref{fig:array-literal} automatically translated into the following
+Scala classes:
+\begin{lstlisting}[style=myScalastyle]
+trait ArrayLiteral extends AST
+case class ArrayLiteral0(x1: Option[Elision])
+case class ArrayLiteral1(x1: ElementList)
+case class ArrayLiteral2(x1: ElementList, x3: Option[Elision])
+\end{lstlisting}
+
+\subsubsection{Parser generations}\label{sec:convert-bnfes}
+The next step is to automatically extract parsers from the given \( \bnfes \) grammar.
+The conversion from \( \bnfes \) symbols into Scala codes is defined as follows:
+\[
+  \begin{array}{c|c}
+    \bnfes \; \text{symbols} & \text{Scala codes}\\\hline\hline
+    \epsilon & \code{MATCH}\\\hline
+    \T{a} & \code{"a"}\\\hline
+    \NT{A}(\argument_1, \argument_n) & \code{A(a1, .. , an)}\\\hline
+    \symb? & \code{opt(s)}\\\hline
+    \symb \butnot \symb' & \code{s\textbackslash s'}\\\hline
+    \nolt & \code{NoLineTerminator}\\\hline
+  \end{array}
+\]
+The \( \code{MATCH} \) denotes the empty sequence of lookahead parsers.
+Each String literals are implicitly converted into lookahead parsers
+through Scala implicit conversions. The \( \code{opt(s)} \) funciton
+is same with \( \code{s | MATCH} \). We also define \( \code{\textbackslash} \)
+opertor between parsers to support exclusive parsers.
+Finally, we support the \( \code{NoLineTerminator} \) parser.
+It is a little bit tricky because it should hook the whitespace parsers
+and check whether it contains line terminators.
+However, it is possible in our approach because
+we also automatically generates lexers not only parsers of ECMAScript syntax.
+For the final result, the automatically synthesized parser from the
+production \( ArrayLiteral \) in Figure~\ref{fig:array-literal} is defined as follows:
+\begin{lstlisting}[style=myScalastyle]
+lazy val ArrayLiteral: List[Boolean] => LAParser[ArrayLiteral] = memo {
+  case args @ List(Yield, Await) =>
+    ((MATCH <~ "[") ~ opt(Elision) <~ "]") ^^ {
+      case _ ~ x0 => ArrayLiteral0(x0)
+    } | ((MATCH <~ "[") ~ ElementList(Yield, Await) <~ "]") ^^ {
+      case _ ~ x0 => ArrayLiteral1(x0)
+    } | (((MATCH <~ "[") ~ ElementList(Yield, Await) <~ ",") ~ opt(Elision) <~ "]") ^^ {
+      case _ ~ x0 ~ x1 => ArrayLiteral2(x0, x1)
+    }
+}
+\end{lstlisting}
+
+Moreover, we support automatic semicolon insertion algorihtms as well.
+It is the most distinctive parsing feautres in ECMAScript to parse more programs.
+We extend our parser implementation to keep track of the right-most position
+that fails to be parsed in the given input. In ECMAScript, the token at that
+position is defined as \textit{offending token} and automatic semicolon insertion
+algorithms are defined with such tokens. The algorithm is quite easy when we
+already have the position offending tokens, because there are only three simple
+rules. Thus, we just manually support them by following the rule in ECMAScript 2019.
+Moreover, the rule is rarely changed because the only one sub-rule is added
+after ECMAScript 5.1 written in 2011.

### 2019-08-05 icse/related.tex
Added more small comment in related works
update bib

@@
 
+Our technique is closely related by these fields: Parser generation, Automatic model generation, and Formal semantics of JavaScript.
 \subsection{Parser Generation}
@@
   \item Packrat parsing:: simple, powerful, lazy, linear time, functional pearl (ICFP'02)~\cite{packrat}
+    % left recursion 잘 안됨 / memoization으로 memory가 엄청 커짐
+    % GLL - follow가 아닌 prediction으로 사용함 / 이 방법을 적용하면 중간중간 발생하는 nondeterministic한 경우를 모두 keeping해야됨.
+    % context-sensitive token이기에 미리 parsing을 한 token이 존재하지 않기 때문에 그 다음 token이 뭔지 알 수 없어서 prediction도 하지 못함
 \end{itemize}
 
-\subsection{Automatic Semantics Extraction}
-\begin{itemize}
-  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)~\cite{javadoc}
-\end{itemize}
+\subsection{Automatic Model Generation}
+There is similiar problems in many fields. Not only langauge semantics, many specification is not constructed formally, so many researcheres are trying to
+extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
+formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses javadoc comments of target API function with NLP techniques and various
+heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
+to find correct modeling.
+Unlike their approaches, we provides specification translation assistant to support future language update, and to provide correct meaning of specification, which also can applicable when
+testing for each primitive is unavailable so we cannot decide correct semantics automatically.
+
+% \begin{itemize}
+%  \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)~\cite{javadoc}
+% \end{itemize}
 
 \subsection{Formal Semantics of JavaScript}
+Building formal semantics of JavaScript language is 
 \begin{itemize}
+  \item JsVert: \cite{javert}
   \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}

### 2019-08-05 icse/related.tex
add related work

@@
 \subsection{Formal Semantics of JavaScript}
-Building formal semantics of JavaScript language is 
-\begin{itemize}
-  \item JsVert: \cite{javert}
-  \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
-  \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
-  \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
-\end{itemize}
+Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
+web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many reseraches to define formal semantics of JavaScript and
+using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugraing. Their method can
+work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
+which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaSciprt based on ECMAScript specification, and they manually convert from specification
+to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verifiaction and analysis. Similarly, JaVerT coverts specification
+to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
+convertion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.
+
+% \begin{itemize}
+%   \item JaVerT: JavaScript verification toolchain (POPL'18)~\cite{javert}
+%   \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
+%   \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
+%   \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
+% \end{itemize}

### 2019-08-05 icse/converter.tex
temporal update

\section{Algorithm Converter}

There are several efforts to extract formal ECMAScript semantics for static analysis
or verifications of JavaScript programs~\cite{???}. However, existing researches
manually extract the semantics and only target specific version of
EMCAScript specifications, mostly ECMAScript 5.1.
It is the critical problem to treat real-world JavaScript programs
because ECMAScript specifications are annually updated after 2015.

To alleviate such problems, we propose to automatically extract semantics from
ECMAScript specifications. Their semantics are provided as \textit{abstract algorithms}
written in structural natural langauges. Our main idea is to convert such algorithms
into our small core languages. The algorithm converter consits of multiple rules
for each layer. Moreover, we provide \textit{rule generation assistant}.
It diagnoses root causes of failed conversions and suggests
that which layer of rules should be extended for them.

\subsection{Abstract Algorithms}

Abstract algorithms in ECMAScript specifications are written in structural
natural languages. For example, Figure~\ref{fig:to-primitive} describes
the \( \code{ToPrimitive} \) abstract algorithm. It takes two parameters
\( \code{input} \) and \( \code{PreferredType} \) and evaluates its body
with given arguments. Its body consits of multiple steps and each step could
have multiple sub-steps as well. While it is not easy to infer exact meaning
of natural languages, fortunately, there is additional HTML tags are attached
into several tokens in abstract algorithms. For example, all the paramters
and newly defined local identifiers have \( \code{<var>} \) tags.
We utilize such information to construct more precise semantics.
The following table describes the list of HTML tags we utilize
and their meaning:

\[
  \begin{array}{c|l}

    \text{tags} & \text{descriptions}\\\hline\hline
    \code{<code>} & \text{ECMAScript codes}\\\hline
    \code{<emu-const>} & \text{constant values}\\\hline
    \code{<emu-grammar>} & \text{productions}\\\hline
    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
    \code{<emu-val>} & \text{values}\\\hline
    \code{<ol>} & \text{ordered sub-steps}\\\hline
    \code{<sup>} & \text{superscripts}\\\hline
    \code{<ul>} & \text{unordered sub-steps}\\\hline
    \code{<var>} & \text{variables}\\\hline
  \end{array}
\]

\subsection{Layered Rule-based Conversions}

We convert abstract algorithms

\subsubsection{Layered Rules}

% 각각의 layer를 어떻게 나누었나를 설명
% 가장 많이 match하는 경우? 중복되는 경우?
% 예시 보여주기

\subsubsection{Core Language for ECMAScript}

% core의 특성을 정리해서 보여주기 formal?
% data와 type을 어떤 식으로 다루는 지 알려주기
% 예시 보여주기

\subsection{Rule Generation Assistant}

% 각 module들 설명하기

\inred{
\subsection{Core language}
실행 가능한 specification을 만들기 위한 langauge.
algorithm들의 공통된 행동을 실행할 수 있게 잘 설계함
ex) let X be ... => let X = ...

\subsubsection{다른 rewriting system 또는 compiler와 다른 점}
특징으로는 Parser에서 만들어진 AST를 하나의 값으로 들고 다니면서 관련 함수를 호출하거나 subAST를 가져올수 있게 만들어짐. 이는 Syntax function 실행을 위해선데 이후 initial state organization에서 설명 
또한 ES specification에서 공통적으로 동작하는 복잡한 연산을 expression으로 지원함, 특히 문서에 covered by에 있는 것처럼 AST Value를 Goal symbol로 다시 parse해야 하는 경우도 있고, eval이나 Class creation 관련 함수에서처럼 string을 AST로 parse해야하는 경우도 있음. 그런 경우를 parse-syntax 를 넣어서 처리할 수 있게
해줌.

\subsection{함수의 의미 번역 (algorithm => Function)}
Function은 parameter와 body로 나뉨
\subsubsection{parameter extraction} : HTML에 써있음 + 여러 특별한 말들 (with parameter * )
Builtin function의 경우 specification 내에서 implicit하게 전해지는 parameter들이 있는데, (thisValue, newTarget) 이것을
core에서 모두 명시적으로 받게 (지금은 javascript 단에서) 자동으로 고쳐준다.

\subsubsection{body extraction ( AlgoCompiler )} : 이부분이 Human resource 많이 들어감
여기서 rule에 따라 step을 만들어줌
나눌 수도 있을 것 같은데 지금은 일단 instruction, expression, condition, type, value, reference을 나타내는 position을 분리하고 거기에 맞춰서 case별로 parser를 짬
근데 똑같은 의미도 여러 다른 말로 표현하기 떄문에 지금은 모든 경우를 하나씩 써놓음
또 같은 말도 context에 따라 의미가 다른 경우가 있음 (Return할때), 지금은 알고리즘의 종류에만 dependent하므로 알고리즘에 flag를 둬서 구분

간단하지 않은 알고리즘의 경우는 1) core 내에서 표현될 수 있는 경우 Function을 만들어 모델링하거나 
2) 지원하지 않는 경우가 있다

\begin{itemize}
  \item Formal definition of Core language
    \begin{itemize}
      \item Syntax
      \item Semantics
    \end{itemize}
  \item Abstract algorithms
    \begin{itemize}
      \item syntax-directed / internal method
      \item Converted into Core
    \end{itemize}
\end{itemize}
}

\begin{figure}
  \centering
  \includegraphics[height=18em]{img/to_primitive.png}
  \begin{lstlisting}[style=myCorestyle]
"ToPrimitive" (input, PreferredType) => {
  if (= (Type input) "Object") {
    if (= PreferredType absent) let hint = "default"
    else if (= PreferredType "String") let hint = "string"
    else let hint = "number"
    let exoticToPrim = ? (GetMethod input SYMBOL_toPrimitive)
    if (! (= exoticToPrim undefined)) {
      let result = ? (Call exoticToPrim input (new [hint]))
      if (! (= (Type result) "Object")) return result
      return (Throw INTRINSIC_TypeErrorPrototype)
    }
    if (= hint "default") hint = "number"
    return ? (OrdinaryToPrimitive input hint)
  }
  return input
}
  \end{lstlisting}
  \caption{\( \code{ToPrimitive} \) abstract algorithms}
  \label{fig:to-primitive}
\end{figure}

% HTML tag based token / structure 그대로 살림
% Parameter를 뽑는 방법들
% Context dependent한 return과 함수가 아닌 macro에 해당하는 returnifabrupt등을 설명

### 2019-08-05 icse/framework.tex
temporal update

--- 2019-08-01 icse/compile.tex
@@
-\section{Semantic generation}
-
-\subsection{Core language}
-실행 가능한 specification을 만들기 위한 langauge.
-algorithm들의 공통된 행동을 실행할 수 있게 잘 설계함
-ex) let X be ... => let X = ...
-
-\subsubsection{다른 rewriting system 또는 compiler와 다른 점}
-특징으로는 Parser에서 만들어진 AST를 하나의 값으로 들고 다니면서 관련 함수를 호출하거나 subAST를 가져올수 있게 만들어짐. 이는 Syntax function 실행을 위해선데 이후 initial state organization에서 설명 
-또한 ES specification에서 공통적으로 동작하는 복잡한 연산을 expression으로 지원함, 특히 문서에 covered by에 있는 것처럼 AST Value를 Goal symbol로 다시 parse해야 하는 경우도 있고, eval이나 Class creation 관련 함수에서처럼 string을 AST로 parse해야하는 경우도 있음.
-그런 경우를 parse-syntax 를 넣어서 처리할 수 있게
-해줌.
-
-\subsection{semantic 컴파일하기 위해 하는 것 + specification 구조}
-기본적인 원칙 :
-\begin{itemize} 
-\item 자바스크립트로 알고리즘 이름이랑 파라미터, 스텝을 가져와서 코어의 글로벌 ID에 매치 시켜줌
-\item initial Heap을 생성해줌
-\end{itemize}
-매치를 시킨다는 뜻은 코어의 글로벌 ID에 코어 함수 형태로 알고리즘을 넣는 것임
-
-\subsection{함수의 의미 번역 (algorithm => Function)}
-Function은 parameter와 body로 나뉨
-\subsubsection{parameter extraction} : HTML에 써있음 + 여러 특별한 말들 (with parameter * )
-Builtin function의 경우 specification 내에서 implicit하게 전해지는 parameter들이 있는데, (thisValue, newTarget) 이것을
-core에서 모두 명시적으로 받게 (지금은 javascript 단에서) 자동으로 고쳐준다.
-
-\subsubsection{body extraction ( AlgoCompiler )} : 이부분이 Human resource 많이 들어감
-여기서 rule에 따라 step을 만들어줌
-나눌 수도 있을 것 같은데 지금은 일단 instruction, expression, condition, type, value, reference을 나타내는 position을 분리하고 거기에 맞춰서 case별로 parser를 짬
-근데 똑같은 의미도 여러 다른 말로 표현하기 떄문에 지금은 모든 경우를 하나씩 써놓음
-또 같은 말도 context에 따라 의미가 다른 경우가 있음 (Return할때), 지금은 알고리즘의 종류에만 dependent하므로 알고리즘에 flag를 둬서 구분
-
-간단하지 않은 알고리즘의 경우는 1) core 내에서 표현될 수 있는 경우 Function을 만들어 모델링하거나 
-2) 지원하지 않는 경우가 있다
-
-\begin{itemize}
-  \item Formal definition of Core language
-    \begin{itemize}
-      \item Syntax
-      \item Semantics
-    \end{itemize}
-  \item Abstract algorithms
-    \begin{itemize}
-      \item syntax-directed / internal method
-      \item Converted into Core
-    \end{itemize}
-\end{itemize}
-
-\section{ Building entire system to evaluate code }
+\section{Building entire system to evaluate code}
 
@@
 We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.
+
+% \begin{itemize}
+%   \item \textbf{Global Algorithms} Global algorithms are possible to be accessed
+%     by any other algorithms. The top-level algorithm \( \code{RunJobs} \) is also global.
+%   \item \textbf{Type-dependent Algorithms} Several algorithms have different
+%     bodies dependent on types of their owner data. In ECMAScript specifications,
+%     there are two different data types; language types and specification types.
+%     The language types are explicitly used in JavaScript languages such as
+%     \( \code{Boolean}, \code{Number}, \code{String} \), and \( \code{Object} \).
+%     However, specification types are only used in specifications such as
+%     Lists, Records, and Lexical Environments. Among them, some data types
+%     have their own member algorithms. For example, language type \( \code{Object} \)
+%     has several internal methods described in abstract algorithms. It depends
+%     on 
+% 
+%     several data types have their own member algorithms. For example, 
+%     
+%     For example, the internal method
+%     \( \code{[[Call]]} \) has different semantics dependent on its owner object.
+%     Moreover, the owner objects are used in the body of algorithms as well.
+%     Thus, we extend the parameters to accept its owner object as an implicit argument.
+%   \item \textbf{Syntax-directed Algorithms} The semantics of each JavaScript syntax
+%     are written in 
+% \end{itemize}
+
+% \subsection{semantic 컴파일하기 위해 하는 것 + specification 구조}
+% 기본적인 원칙 :
+% \begin{itemize} 
+% \item 자바스크립트로 알고리즘 이름이랑 파라미터, 스텝을 가져와서 코어의 글로벌 ID에 매치 시켜줌
+% \item initial Heap을 생성해줌
+% \end{itemize}
+% 매치를 시킨다는 뜻은 코어의 글로벌 ID에 코어 함수 형태로 알고리즘을 넣는 것임
+%

### 2019-08-05 icse/main.tex
temporal update

@@
   language=scala,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  frame=single,
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3,
+}
+\lstdefinestyle{myCorestyle}{
+  frame=tb,
   aboveskip=3mm,
@@
 \input{intro}
-\input{background}
-\input{overall}
+\input{overview}
 \input{parser}
-\input{compile}
+\input{converter}
+\input{framework}
 \input{eval}

### 2019-08-05 icse/overview.tex
temporal update

\section{Overview}

% TODO
% \begin{figure}
%   \centering
%   \includegraphics[height=6em]{img/???}
%   \caption{}
%   \label{fig:array-literal}
% \end{figure}

\begin{itemize}
  \item Sytnax: automatically generate parser from ES-BNF
    \begin{itemize}
      \item ES-BNF features
      \item Packrat Parsers with 1-lookahead
      \item Example
    \end{itemize}
  \item Semantics: automatically convert abstract algorithms into Core programs
    \begin{itemize}
      \item Abstract algorithms
      \item Example
    \end{itemize}
\end{itemize}
\begin{itemize}
  \item Figure of overall structure
  \item Explanation of each module
\end{itemize}

### 2019-08-06 icse/compiler.tex
Renamed converter -> compiler

--- 2019-08-05 icse/converter.tex
@@
-\section{Algorithm Converter}
+\section{Algorithm Compiler}
 
-There are several efforts to extract formal ECMAScript semantics for static analysis
-or verifications of JavaScript programs~\cite{???}. However, existing researches
-manually extract the semantics and only target specific version of
-EMCAScript specifications, mostly ECMAScript 5.1.
-It is the critical problem to treat real-world JavaScript programs
-because ECMAScript specifications are annually updated after 2015.
+In this section, we propose a compiler from abstract algorithms
+into our core language for ECMAScript specifications.
+We first convert a given abstract algorithm into a list of
+tokens based on HTML tags. Then, we
 
-To alleviate such problems, we propose to automatically extract semantics from
-ECMAScript specifications. Their semantics are provided as \textit{abstract algorithms}
-written in structural natural langauges. Our main idea is to convert such algorithms
-into our small core languages. The algorithm converter consits of multiple rules
-for each layer. Moreover, we provide \textit{rule generation assistant}.
-It diagnoses root causes of failed conversions and suggests
-that which layer of rules should be extended for them.
+use \textit{compiler assistant}
+to generate compiler rules.
+
+o
+In this section, we propose our core languages for ECMAScript
+and explain how to convert abstract algorithms into the core programs.
+We first explain the pre-processing to extract abstract algorithms
+as lists of tagged tokens from ECMAScript specifications written in HTML.
+Then, we introduce main features of the core languages and
 
@@
 the \( \code{ToPrimitive} \) abstract algorithm. It takes two parameters
-\( \code{input} \) and \( \code{PreferredType} \) and evaluates its body
-with given arguments. Its body consits of multiple steps and each step could
-have multiple sub-steps as well. While it is not easy to infer exact meaning
-of natural languages, fortunately, there is additional HTML tags are attached
+\( \code{input} \) and \( \code{PreferredType} \). The body consits of
+multiple steps and each step might have multiple sub-steps as well.
+While it is not easy to infer exact meaning of natural languages,
+fortunately, there is additional HTML tags are attached
 into several tokens in abstract algorithms. For example, all the paramters
-and newly defined local identifiers have \( \code{<var>} \) tags.
-We utilize such information to construct more precise semantics.
-The following table describes the list of HTML tags we utilize
-and their meaning:
+and local identifiers have \( \code{<var>} \) tags. We utilize such information
+to construct more precise semantics. The following table describes
+the list of HTML tags we utilize and their meaning:
 
@@
   \begin{array}{c|l}
-
     \text{tags} & \text{descriptions}\\\hline\hline
@@
 
-We convert abstract algorithms
+We use multi-layer rules to convert abstract algorithms.
+Each layer of rules denotes same level of expressiveness.
+We define six different layers; statements, expressions,
+conditions, types, values, references.
+
+\paragraph{Statements}
 
@@
   \end{lstlisting}
-  \caption{\( \code{ToPrimitive} \) abstract algorithms}
+  \caption{\( \code{ToPrimitive} \) abstract algorithms
+  and its generated core program.}
   \label{fig:to-primitive}

### 2019-08-06 icse/compiler.tex
More writing for algorithm compiler

@@
 
-In this section, we propose a compiler from abstract algorithms
-into our core language for ECMAScript specifications.
-We first convert a given abstract algorithm into a list of
-tokens based on HTML tags. Then, we
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{img/algo_compiler.png}
+  \caption{Overall structure of the algorithm compiler.}
+  \label{fig:algo-compiler}
+\end{figure}
 
-use \textit{compiler assistant}
-to generate compiler rules.
+In this section, we propose the \textit{algorithm compiler}
+that compiles abstract algorithms into \( \ires \) functions
+and its overall structure is described in Figure~\ref{fig:algo-compiler}.
+Before compiling abstract algorithms,
+the tokenizer first tokenizes each abstract algorithm into
+a list of tagged tokens. Then, the token parser constructs
+syntactic parse tree of the given token list.
+Finally, the \( \ires \) function generator constructs the coressponding
+\( \ires \) function from the given parse tree.
+The parser and the generator is dependent on conversion rules
+and we define the general conversion rules for abstract algorithms in
+ECMAScript specifications. Like Coq, a proof assistant, we also provide
+the \textit{rule generation assistant} to make easy write conversion rules.
+It diagnoses root causes of failed parsing tokens
+and suggests new conversion rules based on
+statistical analysis of algorithm steps that failed to be parsed.
 
-o
-In this section, we propose our core languages for ECMAScript
-and explain how to convert abstract algorithms into the core programs.
-We first explain the pre-processing to extract abstract algorithms
-as lists of tagged tokens from ECMAScript specifications written in HTML.
-Then, we introduce main features of the core languages and
+\subsection{Tokenizer}
 
-\subsection{Abstract Algorithms}
-
-Abstract algorithms in ECMAScript specifications are written in structural
-natural languages. For example, Figure~\ref{fig:to-primitive} describes
-the \( \code{ToPrimitive} \) abstract algorithm. It takes two parameters
-\( \code{input} \) and \( \code{PreferredType} \). The body consits of
-multiple steps and each step might have multiple sub-steps as well.
-While it is not easy to infer exact meaning of natural languages,
-fortunately, there is additional HTML tags are attached
-into several tokens in abstract algorithms. For example, all the paramters
-and local identifiers have \( \code{<var>} \) tags. We utilize such information
-to construct more precise semantics. The following table describes
-the list of HTML tags we utilize and their meaning:
-
+Abstract algorithms in ECMAScript specifications are written in structured
+natural languages in HTML files. An algorithm consists of ordered steps
+and it might contain sub-steps as well. For example,
+the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive}
+has three steps and second step has seven sub-steps.
+Moreover, the tokens of each step has its own HTML tag and each tag
+has the following meaning:
 \[
   \begin{array}{c|l}
-    \text{tags} & \text{descriptions}\\\hline\hline
+    \text{HTML tags} & \text{meanings}\\\hline\hline
+    \code{<var>} & \text{variables}\\\hline
+    \code{<emu-grammar>} & \text{productions}\\\hline
+    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
     \code{<code>} & \text{ECMAScript codes}\\\hline
     \code{<emu-const>} & \text{constant values}\\\hline
-    \code{<emu-grammar>} & \text{productions}\\\hline
-    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
     \code{<emu-val>} & \text{values}\\\hline
     \code{<ol>} & \text{ordered sub-steps}\\\hline
+    \code{<ul>} & \text{unordered sub-steps}\\\hline
     \code{<sup>} & \text{superscripts}\\\hline
-    \code{<ul>} & \text{unordered sub-steps}\\\hline
-    \code{<var>} & \text{variables}\\\hline
+    \text{otheriwse} & \text{simple texts}\\\hline
+  \end{array}
+\]
+We try to keep the tag information for each token to generate more
+precise conversion rules. For example, if and only if a token has a tag
+\( \code{<var>} \), it is a parameter or a local variable.
+Thus, it is possible to construct a conversion rule precisly discriminates
+identifiers and other components.
+
+The tokenizer first recognizes the overall structures of steps.
+Then, it divides each step into sequence of tagged tokens.
+If an HTML element has a explicit tag, it is converted into a single token
+with the tag. Otherwise, it is splitted into multiple tokens and each token
+should be a sequence of alphanumeric characters or a single
+non-alphanumeric character. For example, in the \( \code{ToPrimitive} \)algorithm,
+\( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
+and \( \code{@@toPrimitive} \) is splitted into three text tokens
+\( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).
+
+For the linear structures, the tokenizer flatten the structured steps into
+a single list. Some conversion rules should handle multiple steps such as
+the conditional statements (if-then-else). Thus, we decide to break down
+structured algorithms using three special tokens;
+\( \tend \) denotes the end of a single step,
+\( \tin \) and \( \tout \) the start and the end of nested steps, respectively.
+For example, the \( \code{ToPrimitive} \) algorithm is tokenized as follows.
+\[
+  \begin{array}{l}
+    \code{Assert} \cdots \tend\\
+    \code{If} \cdots \tin \code{If} \cdots \tend
+    \cdots \code{Return} \cdots \tend \tout \tend\\
+    \code{Return} \cdots \tend\\
   \end{array}
@@
 
-\subsection{Layered Rule-based Conversions}
+\subsection{Token Parser}
 
-We use multi-layer rules to convert abstract algorithms.
-Each layer of rules denotes same level of expressiveness.
-We define six different layers; statements, expressions,
-conditions, types, values, references.
+The token parser parses a given list of tokens into a syntactic parse tree.
+It depends on the given \textit{conversion rules} that consists of
+two parts parsing rules and mapping from parsing rules into corresponding
+\( \ires \) components.
+A parsing rule consists of basic token matchers and other parsing rules
+including itself. For example, the following parsing rule is simplifed version for
+sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
+\begin{lstlisting}[style=myScalastyle]
+// statements
+val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "."
+// expressions
+val Expr = (
+  // identifiers
+  varT |
+  // return if abrupt
+  "?" ~ Expr |
+  // function calls
+  textT ~ "(" ~ repsep(varT, ",") ~ ")" |
+  // lists
+  "<<" ~ repsep(Expr, ",") ~ ">>"
+)
+\end{lstlisting}
 
-\paragraph{Statements}
+Each parsing rule is written in extended Scala parser combinators.
+We modify the meaning of altenative composition operator ( \( | \) ) to collect
+all longest matched results. If the parser detects that a step cannot be
+parsed with the given parsing rules. It reports that a step is not possible
+to be parsed under the given rules into the rule generation assistant.
+Moreover, even though the parser could parse a step, it will be also reported
+if it could be parsed in not a single but multiple ways.
+Each string literal is a token matcher for tokens without any tags and checks
+that the token has same string value with the sring literal.
+The \( \code{varT} \) and \( \code{textT} \) is also token matchers
+for token with the tag \( \code{<var>} \) and no tags.
+The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
+defined with our extended parser combinators.
+Morevoer, it supports all helpers functions defined in Scala parser combinators.
+For example, the helper function \( \code{repsep(p, q)} \) generates a new
+parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
+using another parsing rule \( \code{q} \) as separators.
+Finally, the token parser with the above rules parses sub-step \( i \) in the
+\( \code{ToPrimitive} \) into the following syntactic parse tree:
+\includegraphics[width=0.5\textwidth]{img/parse_tree.png}
 
-\subsubsection{Layered Rules}
+\subsection{\( \ires \) Function Generator}
 
-% 각각의 layer를 어떻게 나누었나를 설명
-% 가장 많이 match하는 경우? 중복되는 경우?
-% 예시 보여주기
+The \( \ires \) function generator takes a parse tree from the token parser
+and generates an \( \ires \) function. The given conversion rules describe
+the mapping from each parsing rule into corresponding \( \ires \) components.
+The \( \ires \) is an imperative style programming languages that we proposed
+in order to represent each step of abstract algorithms in ECMAScript specifications.
 
-\subsubsection{Core Language for ECMAScript}
-
-% core의 특성을 정리해서 보여주기 formal?
-% data와 type을 어떤 식으로 다루는 지 알려주기
-% 예시 보여주기
+% IR_ES 더 설명하기
 
 \subsection{Rule Generation Assistant}
-
-% 각 module들 설명하기
-
-\inred{
-\subsection{Core language}
-실행 가능한 specification을 만들기 위한 langauge.
-algorithm들의 공통된 행동을 실행할 수 있게 잘 설계함
-ex) let X be ... => let X = ...
-
-\subsubsection{다른 rewriting system 또는 compiler와 다른 점}
-특징으로는 Parser에서 만들어진 AST를 하나의 값으로 들고 다니면서 관련 함수를 호출하거나 subAST를 가져올수 있게 만들어짐. 이는 Syntax function 실행을 위해선데 이후 initial state organization에서 설명 
-또한 ES specification에서 공통적으로 동작하는 복잡한 연산을 expression으로 지원함, 특히 문서에 covered by에 있는 것처럼 AST Value를 Goal symbol로 다시 parse해야 하는 경우도 있고, eval이나 Class creation 관련 함수에서처럼 string을 AST로 parse해야하는 경우도 있음.
-그런 경우를 parse-syntax 를 넣어서 처리할 수 있게
-해줌.
-
-\subsection{함수의 의미 번역 (algorithm => Function)}
-Function은 parameter와 body로 나뉨
-\subsubsection{parameter extraction} : HTML에 써있음 + 여러 특별한 말들 (with parameter * )
-Builtin function의 경우 specification 내에서 implicit하게 전해지는 parameter들이 있는데, (thisValue, newTarget) 이것을
-core에서 모두 명시적으로 받게 (지금은 javascript 단에서) 자동으로 고쳐준다.
-
-\subsubsection{body extraction ( AlgoCompiler )} : 이부분이 Human resource 많이 들어감
-여기서 rule에 따라 step을 만들어줌
-나눌 수도 있을 것 같은데 지금은 일단 instruction, expression, condition, type, value, reference을 나타내는 position을 분리하고 거기에 맞춰서 case별로 parser를 짬
-근데 똑같은 의미도 여러 다른 말로 표현하기 떄문에 지금은 모든 경우를 하나씩 써놓음
-또 같은 말도 context에 따라 의미가 다른 경우가 있음 (Return할때), 지금은 알고리즘의 종류에만 dependent하므로 알고리즘에 flag를 둬서 구분
-
-간단하지 않은 알고리즘의 경우는 1) core 내에서 표현될 수 있는 경우 Function을 만들어 모델링하거나 
-2) 지원하지 않는 경우가 있다
-
-\begin{itemize}
-  \item Formal definition of Core language
-    \begin{itemize}
-      \item Syntax
-      \item Semantics
-    \end{itemize}
-  \item Abstract algorithms
-    \begin{itemize}
-      \item syntax-directed / internal method
-      \item Converted into Core
-    \end{itemize}
-\end{itemize}
-}
-
-\begin{figure}
-  \centering
-  \includegraphics[height=18em]{img/to_primitive.png}
-  \begin{lstlisting}[style=myCorestyle]
-"ToPrimitive" (input, PreferredType) => {
-  if (= (Type input) "Object") {
-    if (= PreferredType absent) let hint = "default"
-    else if (= PreferredType "String") let hint = "string"
-    else let hint = "number"
-    let exoticToPrim = ? (GetMethod input SYMBOL_toPrimitive)
-    if (! (= exoticToPrim undefined)) {
-      let result = ? (Call exoticToPrim input (new [hint]))
-      if (! (= (Type result) "Object")) return result
-      return (Throw INTRINSIC_TypeErrorPrototype)
-    }
-    if (= hint "default") hint = "number"
-    return ? (OrdinaryToPrimitive input hint)
-  }
-  return input
-}
-  \end{lstlisting}
-  \caption{\( \code{ToPrimitive} \) abstract algorithms
-  and its generated core program.}
-  \label{fig:to-primitive}
-\end{figure}
-
-% HTML tag based token / structure 그대로 살림
-% Parameter를 뽑는 방법들
-% Context dependent한 return과 함수가 아닌 macro에 해당하는 returnifabrupt등을 설명

### 2019-08-06 icse/main.tex
Renamed converter -> compiler
More writing for algorithm compiler

--- 2019-08-01 icse/main.tex
@@
   showstringspaces=false,
-  columns=flexible,
-  basicstyle={\small\ttfamily},
+  columns=fixed,
+  basicstyle={\footnotesize\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  frame=single,
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3,
+}
+\lstdefinestyle{myCorestyle}{
+  frame=tb,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=fixed,
+  basicstyle={\footnotesize\ttfamily},
   numbers=none,
@@
 \input{intro}
-\input{background}
-\input{overall}
+\input{overview}
 \input{parser}
-\input{compile}
+\input{compiler}
+\input{framework}
 \input{eval}

### 2019-08-06 icse/overview.tex
More writing for algorithm compiler

@@
 
-% TODO
-% \begin{figure}
-%   \centering
-%   \includegraphics[height=6em]{img/???}
-%   \caption{}
-%   \label{fig:array-literal}
-% \end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[height=18em]{img/to_primitive.png}
+  \begin{lstlisting}[style=myCorestyle]
+"ToPrimitive" (input, PreferredType) => {
+  if (= (Type input) "Object") {
+    if (= PreferredType absent) let hint = "default"
+    else if (= PreferredType "String") let hint = "string"
+    else let hint = "number"
+    let exoticToPrim = ? (GetMethod input SYMBOL_toPrimitive)
+    if (! (= exoticToPrim undefined)) {
+      let result = ? (Call exoticToPrim input (new [hint]))
+      if (! (= (Type result) "Object")) return result
+      return (Throw INTRINSIC_TypeErrorPrototype)
+    }
+    if (= hint "default") hint = "number"
+    return ? (OrdinaryToPrimitive input hint)
+  }
+  return input
+}
+  \end{lstlisting}
+  \caption{\( \code{ToPrimitive} \) abstract algorithms
+  and its generated core program.}
+  \label{fig:to-primitive}
+\end{figure}
 

### 2019-08-06 icse/framework.tex

@@
 in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
-We get these information by parsing HTML document, and passing these result to our previous moudle to get AST, Parser, and executable algorithms automatically.
+We get these information by parsing HTML document, and passing these result to our previous moudle to get AST, Parser, and executable algorithms.
 
-Rest part is initial environment of language such as initialization of builtin types, or entry point of the program, etc.
+To organize these primitives and running the program, we have to model initial environment of language such as initialization of builtin types, or entry point of the program, etc.
 
@@
 
- In ECMAScript, there is the object which have references of builtin object. Each Builtin Object provides fields and function, just as ordinary object. When its function is called,
+ Builtin object is pre-defined object with many built-in functions. For example, In ECMAScript \( \code{Array} \) refers an object which can generate an array by
+ calling it. Each Builtin Object provides fields and function, just as ordinary object. When its function is called,
  the corresponding algorithm specified in the document should be called.
-To support builtin object, we make structure of builtin object and its attributes, and then we autoamtically map corresponding field to the algorithm in specification by matching its function name.
+
+ In specification, a built-in function object usually matches to abstract algorithm. Its algorithm name
+ describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
+ we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as attribute. 
+ To support builtin object, we make structure of builtin object and its attributes.
+ After we correctly organizes structure, then we made algorithm that autoamtically map corresponding field to the abstract algorithm in specification by matching its function name.
 
@@
  While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently refered in specification. But name of builtin objects
- are defiend for reference in Host language, so it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
- Map between Intrinsic name and Builtin objects are available in speicificaion as table form , so we parse this table to generate global identifier to object.
+ are defiend for reference in Host language, so it needs another name to refer it in specification langauge. For example, \( \code{Array} \) is a name for
+ ECMAScript reference, so abstract algorithm should call \\
+ \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm intorduces intrinsics, which
+are alias for built-in objects. For example it is refred as \( \code{\%Array\%} \) to refer Array Object.
+ Map between Intrinsic name and Builtin objects are available in speicificaion as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.
 
@@
  In specification, All algorithm has name to refer it, but some algorithms have same names and they are called in context-dependent way.
- There is four types of algorithm. 
+In "5.2 Algorithm Conventions", it defines three types of abstract operation.
  \begin{itemize}
-  \item Global algorithm: they can be called by name in any context
-  \item Type-dependent algorithm: they are bounded in specific type of object
-  \item Syntax-dependent algorithm: they are bounded in AST
-  \item Builtin function algorithm: they correspond to builtin function
+  \item Abstract operation: they can be called by name in any context
+  \item Method-like abstract operation: algorithm dispatch depends on receiver object
+  \item Syntax-directed operation: algorithm dispatch depends on receiver AST
   \end{itemize}
 
-  First, we categorized sections by types of algorithm. Builtin object has several own sections to describe its functions,
-so it is easy to extract builtin object algorithms. Type-dependent algorithms and syntax-dependent algorithms has their own layout, so it
-can be extracted. Rest algorithms are considered as global algorithm.
+First, we categorized sections by types of algorithm.
+Method-like abstract operation has seperate sections to describe it, so we manually add these sections to treat differently.
+Also Syntax-directed operations are described in distinct sections, so both case is easy to extract it.
+Rest algorithms are considered as ordinary Abstract operation.
 
-We mapped builtin function algorithms in environment when initialzing builtin object, so we descibe about rest three algorithms.
+\subsubsection{Abstract operation}
 
-\subsubsection{Global algorithm}
+We just convert abstract operations to function, and bind global identifier to that function to call it by algorithm name.
 
-We just convert global algorithms to function, and bind global identifier to that function to call it by algorithm name.
-
-\subsubsection{Type-dependent algorithm}
+\subsubsection{Method-like abstract operation}
 
@@
 
-For Example, Object Environment Record and Declarative Environment Record is different object in specification, but they have same name of algorithm(i.e. HasBinding(N))
+For Example, Ordinary Object and String Exotic Object is different object in specification, but they have same name of algorithm(i.e. \( \code{[[getOwnProperty]](N)} \))
 
-In this case, algorithm is called in context of calling Object(i.e. x.HasBinding(N)). We name it type-dependent algorithm.
-For type-denpendent algorithms, we organized map from algorithm name to function for each type,
- and we insert functions as propertiy of object when such type of object is created.
+In this case, algorithm dispatching should consider receiver Object(i.e. \( \code{x.[[GetOwnProperty]](N)} \)).
+For method-like abstract operation, we organized map from algorithm name to function for each type,
+ and we insert functions as propertiy of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
+ then we insert attributes with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.
 
- \subsubsection{Syntax-dependent algorithm}
+ \subsubsection{Syntax-directed operation}
 
- Like type-dependent algorithm, there are many AST Value (in specification, it is called Parse Node) which uses same name of algorithm but the content is differnt.
-The most frequent example is Evaluation of the AST Value. every Evaluation algorithm has same name, but each algorithm can be applied for specific syntax. We name it syntax-dependent algorithm.
-For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call syntax-dependent algorithm which requires AST Value and algorithm name.
+ Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is differnt.
+The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Nonterminal
+\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some nonterminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
+(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the subcomponent of AST can be used as values. For example, In the
+Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer subcomponent of AST.
+ For Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
 We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

### 2019-08-07 icse/compiler.tex
More writing for algorithm compiler

@@
 
-The \( \ires \) function generator takes a parse tree from the token parser
-and generates an \( \ires \) function. The given conversion rules describe
-the mapping from each parsing rule into corresponding \( \ires \) components.
-The \( \ires \) is an imperative style programming languages that we proposed
-in order to represent each step of abstract algorithms in ECMAScript specifications.
+We define \( \ires \) language to give semantics into syntactic parse tree of
+abstract algorithm steps. It has the following language features:
 
-% IR_ES 더 설명하기
+\begin{itemize}
+\item \textbf{Dynamic Typing} We decide to use dynamic typing for \( \ires \)
+because each variables in abstract algorithms are not statically typed.
+Thus, variables do not have its own static types while each value of \( \ires \)
+has its dynamic type.
+
+\item \textbf{Imparative Style} \( \ires \) represents algorithm steps
+as statements. Each statement changes the current state
+that consists of environments and a heap.
+
+\item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
+lambda functions as values but it has only restricted scopes. In each function,
+only global variables, parameter, and newly defined local variables are accessible.
+It means that the function closure does not capture the the current environemnt.
+We use such restricted scopes becuase it is enough to represent abstract algorithms.
+
+\item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
+the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
+are defined in \( \ires \); numbers, strings, booleans, undefined, and null.
+Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
+the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
+of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive} might be
+not present in some function calls. Then, the parameter has the \( \code{absent} \) value
+to represent its absence.
+
+\item \textbf{Abstract Data Types} \( \ires \) only supports three abstract data types;
+\( \code{Record} \) for mapping from some values into other value,
+\( \code{List} \) for sequenital data types,
+and \( \code{Singletone} \) for singleton data types.
+They are stored in corresponding addresses in the heap structure.
+For example, ECMAScript environment records are represented as \( \code{Record} \) data types
+from String values for identifier names into addresses.
+The addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings.
+We treat a ECMAScript constants such as \( \code{empty} \) and primitive symbols as singleton
+data types in \( \ires \).
+\end{itemize}
+
+To generate the corresponding \( \ires \) function from syntactic parse tree,
+we describe the mapping from each parsing rule into the corresponding \( \ires \) components.
+For example, we describe the following mapping for the previous example parsing rules:
+\begin{lstlisting}[style=myScalastyle]
+// statements
+val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ { case _ ~ x ~ _ ~ y => ESLet(x, y) }
+// expressions
+val Expr = (
+  // identifiers
+  varT |
+  // return if abrupt
+  "?" ~ Expr ^^ { _ ~ e => ESReturnIfAbrupt(e) } |
+  // function calls
+  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ { case x ~ _ ~ y ~ _ => ESCall(x, y) } |
+  // lists
+  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ { case _ ~ x ~ _ => ESList(e) }
+)
+\end{lstlisting}
+Finally, sub-step \( i \) in the \( \code{ToPrimitive} \) is converted
+into the following instructions:
+\begin{lstlisting}[style=myCorestyle]
+let result = ? (Call exoticToPrim input (new [hint]))
+\end{lstlisting}
 
 \subsection{Rule Generation Assistant}
+
+To make easy write conversion rules, we support \textit{rule generation assistant}.
+It consists of several helper functions to show the specific statistics of
+the not yet convertable abstract algorithm steps. It make easy not only construct
+conversion reuls from the scratch but also update existing conversion rules
+for updated specifications. We explain each helper function and how to utilize
+it to construct conversion rules.
+
+\subsubsection{Statement format suggestions}
+
+\inred{TODO}
+
+\subsubsection{Fault localizations based on \( \tstar \) tokens}
+
+\inred{TODO}

### 2019-08-07 icse/compiler.tex
Written intro

@@
 // statements
-val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "."
+val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
 // expressions
@@
   // identifiers
-  varT |
+  varT ^^ ... |
   // return if abrupt
-  "?" ~ Expr |
+  "?" ~ Expr ^^ ... |
   // function calls
-  textT ~ "(" ~ repsep(varT, ",") ~ ")" |
+  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
   // lists
-  "<<" ~ repsep(Expr, ",") ~ ">>"
+  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ ...
 )
@@
 // statements
-val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ { case _ ~ x ~ _ ~ y => ESLet(x, y) }
+val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ESLet(x, y) }
 // expressions
@@
   // identifiers
-  varT |
+  ... ^^ { x => x } |
   // return if abrupt
-  "?" ~ Expr ^^ { _ ~ e => ESReturnIfAbrupt(e) } |
+  ... ^^ { _ ~ e => ESReturnIfAbrupt(e) } |
   // function calls
-  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ { case x ~ _ ~ y ~ _ => ESCall(x, y) } |
+  ... ^^ { case x ~ _ ~ y ~ _ => ESCall(x, y) } |
   // lists
-  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ { case _ ~ x ~ _ => ESList(e) }
+  ... ^^ { case _ ~ x ~ _ => ESList(e) }
 )
@@
 into the following instructions:
-\begin{lstlisting}[style=myCorestyle]
+\begin{lstlisting}[style=ires]
 let result = ? (Call exoticToPrim input (new [hint]))

### 2019-08-07 icse/intro.tex
Temporal updates
Written intro

@@
 
+JavaScript is one of widely used programming languages not only for client-sides
+but also for server-side programming~\cite{???} and even operating systems~\cite{???}.
+However, developers suffer from the intricate semantics of JavaScript and
+such complexities cause security vulnerabilities. For example, the following JavaScript
+code seems to be tautology:
+\begin{lstlisting}[style=myJSstyle]
+function f(x) { return x == !x; }
+\end{lstlisting}
+Unfortunately, it returns \( \code{false} \) when the argument is an empty array
+\( \code{[]} \). To correctly understand such situations, the understanding of
+formal semantics of JavaScript is necessary.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{img/previous.png}
+  \caption{Previous approaches of semantics extractions for ECMAScript}
+  \label{fig:previous}
+\end{figure}
+
+However, the existing JavaScript foraml semantics are fully manually written
+by researchers based on ECMAScript specifications. ECMAScript is a standardized language
+of JavaScript and its specifications formally define its syntax and semantics.
+As described in Figure~\ref{fig:previous}, former researchers implement parser and
+describe semantics using their own intermediate representation (IR) according to the ECMAScript
+specifications. However, their approaches are fully manual thus excessively labor-intensive
+to handle full semantics.
+
+Moreover, it is not suitable approach to cope with the updates of ECMAScript specifications.
+Most of full formal semantics of ECMAScript only supports ECMAScript 5.1 that was
+released in December 2009. Until 2014 years, it was not big deal because ECMAScript
+specifications are rarely updated. However, in late 2014, The Ecma Technical
+Committee 39 (TC39) decided to release ECMAScript on a yearly cadence. From the
+ECMAScript 6, officially ECMAScript 2015, they updated specifications every years
+in June. Now, no researches correctly deal with recent ECMAScript features;
+lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \),
+classes, for-of operators, async functions, or generators.
+
+To alleviate such problems, we propose \textit{Automatic Semantics Extractor (ASE)}
+for ECMAScript specifications. The tool automatically generates JavaScript parser
+from syntax provided by ECMAScript specifications. It also extracts formal
+JavaScript semantics in semi-automatic ways. It is semi-automatic because
+it depends on manually defined \textit{conversion rules}. Each rule describes how abstract
+algorithms in specifications are converted into functions of our core language \( \ires \).
+However, to save the labor of defininig such rules, we also propose \textit{rule generation assistant}
+that suggests new conversion rules based on not yet convertable algorithms.
+The assistant help us deal with changed or newly introduced algorithms defined in new version of
+ECMAScript specifications as well.
+
+Our main contribution is our tool ASE that mechanizes extraction of JavaScript syntax and semantics
+from ECMAScript specifications:
 \begin{itemize}
-  \item JavaScript is a essential programming language in client-sides.
-  \item Because of its complicated semantics, it is not easy to understand JavaScript program behaviors.
-  \item Several exisiting proposed formal semantics of JavaScript, but these have the following limitations.
-    \begin{itemize}
-      \item Fully manual implementation of parsers and interpreters.
-      \item Supported only fixed version of ECMAScript (in most cases, ES 5.1).
+  \item ASE enables to extract the syntax and semantics of ECMAScript 2019,
+    which is the latest released version of ECMAScript in June 2019.
+    Moreover, we successfully applied our tool into the next proposed version,
+    ECMAScript 2020. The official conformance test suite, test262, provides
+    \inred{XXXXX} tests for ECMAScript 2020 and we passed \inred{XXXXX} tests
+    among them.
+  \item ASE is also applicable in-process proposed langauge features in a modular way.
+    ECMAScript specifications are open-source based documentations. Thus, anyone
+    could propose some new language feautres. Then, the committee carefully inspects
+    such proposals and adds them into specifications. Each in-process proposed language
+    feature has its own specification and tests. Thus, we apply ASE into the specification
+    and evalute the corresponding tests. Among \inred{XX} proposals, we successfully
+    pass all the tests in \inred{XX} proposals and partially pass the tests in \inred{XX}
+    proposals.
+  \item Moreover, all extraction mechanisms in ASE is automatic thus we could use this tool
+    to find possible specification errors. We found \inred{X} possible specification errors
+    in ECMAScript 2019 and reported them into TC39, which is the Ecma Technical Committee.
+    We confirm that all of them are real specification errors.
 \end{itemize}
-  \item We propose a way to automatically extract semantics from ECMAScript specifications and deal with its annual updates.
-\end{itemize}
-
-Our contributions are:
-\begin{itemize}
-  \item TODO
-\end{itemize}

### 2019-08-07 icse/main.tex
Written intro

--- 2019-08-01 icse/main.tex
@@
 
-% scala code style
+% Scala code style
 \definecolor{dkgreen}{rgb}{0,0.6,0}
@@
   showstringspaces=false,
-  columns=flexible,
-  basicstyle={\small\ttfamily},
+  columns=fixed,
+  basicstyle={\footnotesize\ttfamily},
   numbers=none,
-  numberstyle=\tiny\color{gray},
   keywordstyle=\color{blue},
@@
   tabsize=3,
+}
+
+% 
+\lstdefinestyle{ires}{
+  frame=tb,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=fixed,
+  basicstyle={\footnotesize\ttfamily},
+  numbers=none,
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  frame=single,
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3,
+}
+
+% JavaScript code style
+\lstdefinelanguage{JavaScript}{
+  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
+  keywordstyle=\color{blue}\bfseries,
+  ndkeywords={class, export, boolean, throw, implements, import, this},
+  ndkeywordstyle=\color{darkgray}\bfseries,
+  identifierstyle=\color{black},
+  sensitive=false,
+  comment=[l]{//},
+  morecomment=[s]{/*}{*/},
+  commentstyle=\color{purple}\ttfamily,
+  stringstyle=\color{red}\ttfamily,
+  morestring=[b]',
+  morestring=[b]"
+}
+
+\lstdefinestyle{myJSstyle}{
+  language=JavaScript,
+  extendedchars=true,
+  basicstyle=\footnotesize\ttfamily,
+  showstringspaces=false,
+  showspaces=false,
+  numbers=none,
+  tabsize=2,
+  breaklines=true,
+  showtabs=false,
+  captionpos=b
 }

### 2019-08-07 icse/overview.tex
More writing for algorithm compiler
Written intro

@@
   \centering
+  \includegraphics[width=0.5\textwidth]{img/overview.png}
+  \caption{Overall structure of Automatic Semantics Extractor (ASE)}
+  \label{fig:overview}
+\end{figure}
+
+\begin{figure}
+  \centering
   \includegraphics[height=18em]{img/to_primitive.png}
-  \begin{lstlisting}[style=myCorestyle]
+  \begin{lstlisting}[style=ires]
 "ToPrimitive" (input, PreferredType) => {

### 2019-08-08 src/main/scala/kr/ac/kaist/ase/generator/ASTGenerator.scala
create StringWrapper for lexer NT and use it for exist check

@@ -17,6 +17,7 @@ object ASTGenerator {
       nf.println(s"""package kr.ac.kaist.ase.model""")
       nf.println
       nf.println(s"""import kr.ac.kaist.ase.core._""")
+      nf.println(s"""import kr.ac.kaist.ase.parser.StringWrapper""")
       nf.println(s"""import kr.ac.kaist.ase.error.UnexpectedSemantics""")
       nf.println(s"""import scala.collection.immutable.{ Set => SSet }""")
       nf.println
@@ -53,6 +54,7 @@ object ASTGenerator {
           }
           val paramPairs = params.map(_._1) zip (handleParams(params.map(_._2)))
           val listString = ("Nil" /: paramPairs) { case (str, (x, t)) => s"""l("$t", $x, $str)""" }
+          val listWrapper = ("Nil" /: paramPairs) { case (str, (x, t)) => s"""w("$t", $x, $str)""" }
 
           val maxK = (0 /: params) {
             case (k, (_, t)) => if (t.startsWith("Option[")) k * 2 + 1 else k
@@ -64,6 +66,7 @@ object ASTGenerator {
           nf.println(s"""  }""")
           nf.println(s"""  val k: Int = ${("0" /: params) { case (str, (x, _)) => s"d($x, $str)" }}""")
           nf.println(s"""  val fullList: List[(String, Value)] = $listString.reverse""")
+          nf.println(s"""  val wrapperList: List[String] = $listWrapper.reverse""")
           nf.println(s"""  val info: ASTInfo = $name$i""")
           nf.println(s"""}""")
           nf.println(s"""object $name$i extends ASTInfo {""")
@@ -103,7 +106,7 @@ object ASTGenerator {
     def getParamTypes(rhs: Rhs): List[String] = for {
       (token, i) <- rhs.tokens.zipWithIndex
       paramType = getType(token)
-    } yield if (lexNames contains paramType) "String" else paramType
+    } yield if (lexNames contains paramType) "StringWrapper" else paramType
 
     def getString(rhs: Rhs): String = (for {
       (token, i) <- rhs.tokens.zipWithIndex

### 2019-08-08 src/main/resources/es2020/manual/AlgoCompiler.scala
edit for WeakMap and Map

@@ -1125,6 +1125,8 @@ trait AlgoCompilerHelper extends TokenParsers {
           pair(List(parseInst(s"app $tempP = (IsAccessorDescriptor $x)")), ERef(RefId(Id(tempP))))
       } | name <~ "does not have all of the internal slots of a String Iterator Instance (21.1.5.3)" ^^ {
         case x => pair(Nil, parseExpr(s"""(|| (= $x.IteratedString absent) (= $x.StringIteratorNextIndex absent))"""))
+      } | (ref <~ "is" ~ ("not present" | "absent") <~ ", or is either") ~ (valueExpr <~ "or") ~ valueExpr ~ subCond ^^ {
+        case (i0 ~ r) ~ e1 ~ e2 ~ f => concat(i0, f(EBOp(OOr, EBOp(OOr, EUOp(ONot, exists(r)), EBOp(OEq, ERef(r), e1)), EBOp(OEq, ERef(r), e2))))
       } | (ref <~ "is" ~ ("not present" | "absent")) ~ subCond ^^ {
         case (i0 ~ r) ~ f => concat(i0, f(EUOp(ONot, exists(r))))
       } | expr <~ "is an abrupt completion" ^^ {

### 2019-08-08 icse/compiler.tex
Written overview

@@
 and it might contain sub-steps as well. For example,
-the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive}
+the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es}
 has three steps and second step has seven sub-steps.
@@
 the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
-of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive} might be
+of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es} might be
 not present in some function calls. Then, the parameter has the \( \code{absent} \) value
@@
 Finally, sub-step \( i \) in the \( \code{ToPrimitive} \) is converted
-into the following instructions:
+into the following instruction:
 \begin{lstlisting}[style=ires]

### 2019-08-08 icse/intro.tex
Written overview

@@
 such complexities cause security vulnerabilities. For example, the following JavaScript
-code seems to be tautology:
+code seems to always return \( \code{false} \):
 \begin{lstlisting}[style=myJSstyle]
@@
 \end{lstlisting}
-Unfortunately, it returns \( \code{false} \) when the argument is an empty array
+Unfortunately, it returns \( \code{true} \) when the argument is an empty array
 \( \code{[]} \). To correctly understand such situations, the understanding of
@@
 Most of full formal semantics of ECMAScript only supports ECMAScript 5.1 that was
-released in December 2009. Until 2014 years, it was not big deal because ECMAScript
+released in December 2009. Until 2014, it was not big deal because ECMAScript
 specifications are rarely updated. However, in late 2014, The Ecma Technical
@@
 in June. Now, no researches correctly deal with recent ECMAScript features;
-lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \),
+lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \)),
 classes, for-of operators, async functions, or generators.
@@
 algorithms in specifications are converted into functions of our core language \( \ires \).
-However, to save the labor of defininig such rules, we also propose \textit{rule generation assistant}
-that suggests new conversion rules based on not yet convertable algorithms.
-The assistant help us deal with changed or newly introduced algorithms defined in new version of
+However, to save the labor of defininig such rules, we also propose \textit{rule generation assistant}.
+It suggests new conversion rules based on statistical analysis of not yet convertable algorithms.
+The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
 ECMAScript specifications as well.

### 2019-08-08 icse/overview.tex
Written overview

@@
 \section{Overview}
+
+In this section, we introduce the overall structure of ASE and the outline of
+this paper. Figure~\ref{fig:overview} depicts the overall structure of ASE.
+It mechanizes to extract syntax and semantics of ECMAScript using
+two main module; the \textit{parser generator} and the \textit{algorithm compiler}.
+If first extracts information via the spec extractor.
+ECMAScript specifications are provided as a readable HTML file.
+Thus, we develop the spec extractor in JavaScript to automatically
+extract their contents.
 
@@
   \includegraphics[width=0.5\textwidth]{img/overview.png}
-  \caption{Overall structure of Automatic Semantics Extractor (ASE)}
+  \caption{Overall structure of Automatic Semantics Extractor (ASE)
+  for ECMAScript specifications}
   \label{fig:overview}
@@
 
+ECMAScript specifications describe their lexical and syntactic grammars
+based on their own extension of Backus-Naur Form (BNF).
+We call it as \( \bnfes \), BNF for ECMAScript specifications.
+It supports additional notations for parametric productions, conditional
+right-hand sides, optional symbols, positive/negative lookaheads,
+exclusive symbols, and no line-terminator symbols. We first formally define
+\( \bnfes \) and build the spec extractor to extract grammars written in \( \bnfes \).
+Then, we carefully construct the \textit{parser generator} for them by extending
+the Scala parser combinators. Moreover, we propose \textit{lookahead parsers}
+to parse \( \bnfes \) for correct and fast parsing.
+A lookahead parser keeps track of its lookahead, which is the set of
+possible next tokens. With lookahead parsers,
+the parser generator automatically generate parsers for ECMAScript grammars.
+The generated parsers are readable and one-to-one corresponds to each
+grammar components.
+For example, Firugre~\ref{fig:array-literal-es} is ArrayLiteral production in
+ECMAScript 2019 specification and Figure~\ref{fig:array-literal-parser}
+is the generated parser of the algorithm written in Scala.
+In the first right-hand side, the optional \( Elision \) token
+is represented as \( \code{opt(Elision)} \).
+The parametric non-terminal \( ElementList \) with arguments \( Yield \)
+and \( Await \) is represented as \( \code{ElementList(Yield, Await)} \).
+
 \begin{figure}
   \centering
-  \includegraphics[height=18em]{img/to_primitive.png}
+  \begin{subfigure}[t]{0.4\textwidth}
+    \includegraphics[width=\textwidth]{img/array_literal.png}
+    \caption{ArrayLiteral production in ECMAScript 2019 specification.}
+    \label{fig:array-literal-es}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myScalastyle]
+type P[T] = List[Boolean] => LAParser[T]
+lazy val ArrayLiteral: P[ArrayLiteral] = memo {
+  case List(Yield, Await) =>
+  "[" ~ opt(Elision) ~ "]" ^^ ArrayLiteral0 |
+  "[" ~ ElementList(Yield, Await) ~ "]" ^^ ArrayLiteral1 |
+  "[" ~ ElementList(Yield, Await) ~ "," ~ opt(Elision) ~ "]" ^^ ArrayLiteral2
+}
+    \end{lstlisting}
+    \caption{The generated parser for ArrayLiteral production.}
+    \label{fig:array-literal-parser}
+  \end{subfigure}
+  \caption{ArrayLiteral grammar production in ECMAScript 2019.}
+  \label{fig:array-literal}
+\end{figure}
+
+The semantics in ECMAScript specifications are described as
+abstract algorithms. They are written in structured natural languages
+with ordered steps and tagged tokens. For example, Figure~\ref{fig:to-primitive-es}
+is an example abstract algorithm for \( \code{ToPrimitive} \) in
+ECMAScript 2019. The spec extractor extracts each abstract algorithm
+with HTML tags because we utilize tag information to discriminate
+different kinds of tokens. Then, the \textit{algorithm compiler} converts
+given abstract algorithms into funcitons of our core language \( \ires \).
+The compilation is dependent on manually defined conversion rules
+that consists of two parts; parsing rules and mapping from each rule into \( \ires \)
+component. We carefully define \( \ires \) to directly match instructions with
+the corresponding algorithm steps. For example, Figure~\ref{fig:to-primitive-ires}
+describes the generated \( \ires \) function for the \( \code{ToPrimitive} \)
+algorithm. Each instruction of the generated \( \ires \) function
+is easily matched with the corresponding algorithm step
+and also they have similar silhouettes.
+
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}{0.4\textwidth}
+    \includegraphics[width=\textwidth]{img/to_primitive.png}
+    \subcaption{\( \code{ToPrimitive} \) abstract algorithm in ES2019.}
+    \label{fig:to-primitive-es}
+  \end{subfigure}
+  \qquad
+  \begin{subfigure}{0.48\textwidth}
     \begin{lstlisting}[style=ires]
@@
     \end{lstlisting}
+    \subcaption{The \( \ires \) funciton for \( \code{ToPrimitive} \)
+    abstract algorithm.}
+    \label{fig:to-primitive-ires}
+  \end{subfigure}
   \caption{\( \code{ToPrimitive} \) abstract algorithms
@@
   \label{fig:to-primitive}
-\end{figure}
+\end{figure*}
 
-\begin{itemize}
-  \item Sytnax: automatically generate parser from ES-BNF
-    \begin{itemize}
-      \item ES-BNF features
-      \item Packrat Parsers with 1-lookahead
-      \item Example
-    \end{itemize}
-  \item Semantics: automatically convert abstract algorithms into Core programs
-    \begin{itemize}
-      \item Abstract algorithms
-      \item Example
-    \end{itemize}
-\end{itemize}
-\begin{itemize}
-  \item Figure of overall structure
-  \item Explanation of each module
-\end{itemize}
+Finally, the generated \( \ires \) functions with mannual initial settings
+are applied into the \( \ires \) interpreter. We could parse a
+given JavaScript program using the generated JavaScript parser
+to get the abstract syntax tree (AST). Then, the \( \ires \) interpreter
+evaluates the given AST and provides evaluation results.
+
+From now, we describe the detailed techniques of ASE.
+Section 3 formallly defines \( \bnfes \) and how to automatically
+generate parsers from given \( \bnfes \) using lookahead parsers.
+Section 4 explains abstract algorithms with tagged tokens
+and how to compile them into \( \ires \) functions based on
+given conversion rules. Section 5 describes the implemented details
+about initial settings to evaluate JavaScript programs. Section 6
+discusses the effectiveness of ASE with four research questions.
+Section 7 discusses related work and Section 8 concludes.

### 2019-08-08 icse/parser.tex
Written overview

@@
 that restricts the white spaces between two other symbols.
+
+\begin{figure}
+  \centering
+  \[
+    \begin{array}{l}
+      \NT{ArrayLiteral}(Yield, Await) ::=\\
+      \qquad \T{[} \; Elision? \; \T{]}\\
+      \qquad \T{[} \; ElementList(Yield, Await) \; \T{]}\\
+      \qquad \T{[} \; ElementList(Yield, Await) \; \T{,} Elision? \; \T{]}\\
+    \end{array}
+  \]
+  \caption{ArrayLiteral production in \( \bnfes \).}
+  \label{fig:array-literal-bnfes}
+\end{figure}
+
+For example,
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[height=6em]{img/array_literal.png}
-  \[
-    \begin{array}{l}
-      \NT{ArrayLiteral}(Yield, Await) ::=\\
-      \qquad \T{[} \; Elision? \; \T{]}\\
-      \qquad \T{[} \; ElementList(Yield, Await) \; \T{]}\\
-      \qquad \T{[} \; ElementList(Yield, Await) \; \T{,} Elision? \; \T{]}\\
-    \end{array}
-  \]
-  \caption{Array literals defined in ES2019 and its \( \bnfes \)}
-  \label{fig:array-literal}
-\end{figure}
-
 \subsubsection{AST generations}
@@
 For the final result, the automatically synthesized parser from the
-production \( ArrayLiteral \) in Figure~\ref{fig:array-literal} is defined as follows:
-\begin{lstlisting}[style=myScalastyle]
-lazy val ArrayLiteral: List[Boolean] => LAParser[ArrayLiteral] = memo {
-  case args @ List(Yield, Await) =>
-    ((MATCH <~ "[") ~ opt(Elision) <~ "]") ^^ {
-      case _ ~ x0 => ArrayLiteral0(x0)
-    } | ((MATCH <~ "[") ~ ElementList(Yield, Await) <~ "]") ^^ {
-      case _ ~ x0 => ArrayLiteral1(x0)
-    } | (((MATCH <~ "[") ~ ElementList(Yield, Await) <~ ",") ~ opt(Elision) <~ "]") ^^ {
-      case _ ~ x0 ~ x1 => ArrayLiteral2(x0, x1)
-    }
-}
-\end{lstlisting}
+production \( ArrayLiteral \) in Figure~\ref{fig:array-literal} is defined
+as the parsers defined in Figure~\ref{fig:array-literal}.
 

### 2019-08-08 icse/eval.tex
Comments in evaluation

@@
 \begin{itemize}
-  \item RQ1) Does ASE correctly extract semantics?
-  \item RQ2) Is endurable size of manual portion in implementation of ASE?
-  \item RQ3) Does ASE deal with annual updates from small changes?
-  \item RQ4) How many specification errors are detected by ASE?
+  \item RQ1) Does ASE correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
+    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
+  \item RQ2) Is endurable size of manual portion in implementation of ASE? \inred{refactoring for conversion rules / get statistics of conversion rules}
+    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
+  \item RQ3) Does ASE deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
+    각 feature name / 의미 / compile 성공률 / 결과 test
+  \item RQ4) How many specification errors are detected by ASE? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
 \end{itemize}

### 2019-08-15 icse/compiler.tex
Written abstract

@@
 syntactic parse tree of the given token list.
-Finally, the \( \ires \) function generator constructs the coressponding
+Finally, the \( \ires \) function generator constructs the corresponding
 \( \ires \) function from the given parse tree.
@@
     \code{<sup>} & \text{superscripts}\\\hline
-    \text{otheriwse} & \text{simple texts}\\\hline
+    \text{otherwise} & \text{simple texts}\\\hline
   \end{array}
@@
 \( \code{<var>} \), it is a parameter or a local variable.
-Thus, it is possible to construct a conversion rule precisly discriminates
+Thus, it is possible to construct a conversion rule precisely discriminates
 identifiers and other components.
@@
 If an HTML element has a explicit tag, it is converted into a single token
-with the tag. Otherwise, it is splitted into multiple tokens and each token
+with the tag. Otherwise, it is divided into multiple tokens and each token
 should be a sequence of alphanumeric characters or a single
@@
 \( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
-and \( \code{@@toPrimitive} \) is splitted into three text tokens
+and \( \code{@@toPrimitive} \) is divided into three text tokens
 \( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).
@@
 A parsing rule consists of basic token matchers and other parsing rules
-including itself. For example, the following parsing rule is simplifed version for
+including itself. For example, the following parsing rule is simplified version for
 sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
@@
 Each parsing rule is written in extended Scala parser combinators.
-We modify the meaning of altenative composition operator ( \( | \) ) to collect
+We modify the meaning of alternative composition operator ( \( | \) ) to collect
 all longest matched results. If the parser detects that a step cannot be
@@
 Each string literal is a token matcher for tokens without any tags and checks
-that the token has same string value with the sring literal.
+that the token has same string value with the string literal.
 The \( \code{varT} \) and \( \code{textT} \) is also token matchers
@@
 defined with our extended parser combinators.
-Morevoer, it supports all helpers functions defined in Scala parser combinators.
+Moreover, it supports all helpers functions defined in Scala parser combinators.
 For example, the helper function \( \code{repsep(p, q)} \) generates a new
@@
 
-\item \textbf{Imparative Style} \( \ires \) represents algorithm steps
+\item \textbf{Imperative Style} \( \ires \) represents algorithm steps
 as statements. Each statement changes the current state
@@
 only global variables, parameter, and newly defined local variables are accessible.
-It means that the function closure does not capture the the current environemnt.
-We use such restricted scopes becuase it is enough to represent abstract algorithms.
+It means that the function closure does not capture the the current environment.
+We use such restricted scopes because it is enough to represent abstract algorithms.
 
@@
 the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
-are defined in \( \ires \); numbers, strings, booleans, undefined, and null.
+are defined in \( \ires \); numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
 Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
@@
 \( \code{Record} \) for mapping from some values into other value,
-\( \code{List} \) for sequenital data types,
-and \( \code{Singletone} \) for singleton data types.
+\( \code{List} \) for sequential data types,
+and \( \code{Singleton} \) for singleton data types.
 They are stored in corresponding addresses in the heap structure.
@@
 It consists of several helper functions to show the specific statistics of
-the not yet convertable abstract algorithm steps. It make easy not only construct
-conversion reuls from the scratch but also update existing conversion rules
+the not yet convertible abstract algorithm steps. It make easy not only construct
+conversion rules from the scratch but also update existing conversion rules
 for updated specifications. We explain each helper function and how to utilize
@@
 
-\subsubsection{Fault localizations based on \( \tstar \) tokens}
+\subsubsection{Fault localization based on \( \tstar \) tokens}
 

### 2019-08-15 icse/eval.tex
Written abstract

@@
 \begin{itemize}
-  \item RQ1) Does ASE correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
+  \item RQ1) Does JSSET correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
     test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
-  \item RQ2) Is endurable size of manual portion in implementation of ASE? \inred{refactoring for conversion rules / get statistics of conversion rules}
+  \item RQ2) Is endurable size of manual portion in implementation of JSSET? \inred{refactoring for conversion rules / get statistics of conversion rules}
     개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
-  \item RQ3) Does ASE deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
+  \item RQ3) Does JSSET deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
     각 feature name / 의미 / compile 성공률 / 결과 test
-  \item RQ4) How many specification errors are detected by ASE? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
+  \item RQ4) How many specification errors are detected by JSSET? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
 \end{itemize}

### 2019-08-15 icse/framework.tex
Written abstract

@@
 In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
-environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript langauge.
+environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript language.
 
 \subsection{Extracting specification}
-First step is to collect language specification and extract component that we can process autoamtically. For our target langauge, ECMAScript, has HTML format of specification in their website, and
+First step is to collect language specification and extract component that we can process automatically. For our target language, ECMAScript, has HTML format of specification in their website, and
 in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
-We get these information by parsing HTML document, and passing these result to our previous moudle to get AST, Parser, and executable algorithms.
+We get these information by parsing HTML document, and passing these result to our previous module to get AST, Parser, and executable algorithms.
 
@@
 \subsection{Generating initial environment for evaluating}
-For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs. We will describe how to generate each component.
+For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsic objects. We will describe how to generate each component.
 
@@
  To support builtin object, we make structure of builtin object and its attributes.
- After we correctly organizes structure, then we made algorithm that autoamtically map corresponding field to the abstract algorithm in specification by matching its function name.
+ After we correctly organizes structure, then we made algorithm that automatically map corresponding field to the abstract algorithm in specification by matching its function name.
 
- \subsubsection{Intrinsics}
+ \subsubsection{Intrinsic objects}
 
- While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently refered in specification. But name of builtin objects
- are defiend for reference in Host language, so it needs another name to refer it in specification langauge. For example, \( \code{Array} \) is a name for
+ While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently referred in specification. But name of builtin objects
+ are defined for reference in Host language, so it needs another name to refer it in specification language. For example, \( \code{Array} \) is a name for
  ECMAScript reference, so abstract algorithm should call \\
- \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm intorduces intrinsics, which
-are alias for built-in objects. For example it is refred as \( \code{\%Array\%} \) to refer Array Object.
- Map between Intrinsic name and Builtin objects are available in speicificaion as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.
+ \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm introduces Intrinsic objects, which
+are alias for built-in objects. For example it is referred as \( \code{\%Array\%} \) to refer Array Object.
+ Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.
 
@@
 First, we categorized sections by types of algorithm.
-Method-like abstract operation has seperate sections to describe it, so we manually add these sections to treat differently.
+Method-like abstract operation has separate sections to describe it, so we manually add these sections to treat differently.
 Also Syntax-directed operations are described in distinct sections, so both case is easy to extract it.
@@
 For method-like abstract operation, we organized map from algorithm name to function for each type,
- and we insert functions as propertiy of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
+ and we insert functions as property of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
  then we insert attributes with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.
@@
 
- Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is differnt.
-The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Nonterminal
-\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some nonterminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
-(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the subcomponent of AST can be used as values. For example, In the
-Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer subcomponent of AST.
+ Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is different.
+The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Non-terminal
+\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some non-terminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
+(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
+Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer sub-component of AST.
  For Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.

### 2019-08-15 icse/intro.tex
Written abstract

@@
 
-However, the existing JavaScript foraml semantics are fully manually written
+However, the existing JavaScript formal semantics are fully manually written
 by researchers based on ECMAScript specifications. ECMAScript is a standardized language
@@
 lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \)),
-classes, for-of operators, async functions, or generators.
+classes, for-of operators, asynchronous functions \( \code{async} \), or generators.
 
-To alleviate such problems, we propose \textit{Automatic Semantics Extractor (ASE)}
-for ECMAScript specifications. The tool automatically generates JavaScript parser
+To alleviate such problems, we propose JavaScript Semantics Extraction Toolchain (JSSET)
+based on ECMAScript specifications. The tool automatically generates JavaScript parser
 from syntax provided by ECMAScript specifications. It also extracts formal
@@
 algorithms in specifications are converted into functions of our core language \( \ires \).
-However, to save the labor of defininig such rules, we also propose \textit{rule generation assistant}.
-It suggests new conversion rules based on statistical analysis of not yet convertable algorithms.
+However, to save the labor of defining such rules, we also propose \textit{rule generation assistant}.
+It suggests new conversion rules based on statistical analysis of not yet convertible algorithms.
 The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
@@
 
-Our main contribution is our tool ASE that mechanizes extraction of JavaScript syntax and semantics
+Our main contribution is our tool JSSET that mechanizes extraction of JavaScript syntax and semantics
 from ECMAScript specifications:
 \begin{itemize}
-  \item ASE enables to extract the syntax and semantics of ECMAScript 2019,
+  \item JSSET enables to extract the syntax and semantics of ECMAScript 2019,
     which is the latest released version of ECMAScript in June 2019.
@@
     among them.
-  \item ASE is also applicable in-process proposed langauge features in a modular way.
+  \item JSSET is also applicable in-process proposed language features in a modular way.
     ECMAScript specifications are open-source based documentations. Thus, anyone
-    could propose some new language feautres. Then, the committee carefully inspects
+    could propose some new language features. Then, the committee carefully inspects
     such proposals and adds them into specifications. Each in-process proposed language
-    feature has its own specification and tests. Thus, we apply ASE into the specification
-    and evalute the corresponding tests. Among \inred{XX} proposals, we successfully
+    feature has its own specification and tests. Thus, we apply JSSET into the specification
+    and evaluate the corresponding tests. Among \inred{XX} proposals, we successfully
     pass all the tests in \inred{XX} proposals and partially pass the tests in \inred{XX}
     proposals.
-  \item Moreover, all extraction mechanisms in ASE is automatic thus we could use this tool
+  \item Moreover, all extraction mechanisms in JSSET is automatic thus we could use this tool
     to find possible specification errors. We found \inred{X} possible specification errors

### 2019-08-15 icse/main.tex
Written overview
Written abstract

@@
-\documentclass[sigconf,review]{acmart}
+\documentclass[sigconf,review,anonymous=true]{acmart}
 
@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{listings}
@@
 
-% 
+% ECMAScript Intermediate Reprentations
 \lstdefinestyle{ires}{
@@
 
-\title{Automatic Extraction of JavaScript Formal Semantics
-from ECMAScript Specifications}
+\title{JSSET: JavaScript Semantics Extraction Toolchain}
 
@@
 
-\maketitle
 \begin{abstract}
+While JavaScript is initially invented for client-side in web browsers,
+JavaScript engines are now embedded in many other types of host software.
+Despite its popularity, JavaScript semantics are complicated because of its
+dynamic nature. Thus, the formal analysis and verification of JavaScript programs
+require its formal semantics. Several researches proposed formal semantics
+of JavaScript based on ECMAScript, the official specifications of JavaScript.
+However, the existing approaches are fully manual and only target ECMAScript 5.1.
+It is a critical problem to understand recent JavaScript programs
+because ECMAScript is annually updated from 2015. Thus, already five more updates
+after ECMAScript 5.1.
+
+To alleviate such problems, we propose JSSET, a JavaScript Semantics Extraction
+Toolchain. It automatically extracts JavaScript formal semantics from ECMAScript
+specifications. JSSET generates JavaScript parser for the given grammar written
+in \( \bnfes \), an extended BNF used in ECMAScript specifications.
+Our tool also converts each abstract algorithm written in structured natural
+languages into functions written in \( \ires \), an Intermediate Representation
+for ECMAScript specifications. The conversion from algorithms to \( \ires \) functions
+is defined with \textit{conversion rules}. We apply JSSET into the next proposed
+version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
+in test262, the official ECMAScript conformance test suite.
+Moreover, JSSET also successfully extracts semantics for \inred{XX} proposed features
+by adding only \inred{XX} minor conversion rules.
 \end{abstract}
 
-% TODO \keywords
+\keywords{
+  JavaScript,
+  mechanized formal semantics,
+  recursive descent parsing
+}
+
+\maketitle
 

### 2019-08-15 icse/overview.tex
Written abstract

@@
 
-In this section, we introduce the overall structure of ASE and the outline of
-this paper. Figure~\ref{fig:overview} depicts the overall structure of ASE.
+In this section, we introduce the overall structure of JSSET and the outline of
+this paper. Figure~\ref{fig:overview} depicts the overall structure of JSSET.
 It mechanizes to extract syntax and semantics of ECMAScript using
@@
   \includegraphics[width=0.5\textwidth]{img/overview.png}
-  \caption{Overall structure of Automatic Semantics Extractor (ASE)
-  for ECMAScript specifications}
+  \caption{Overall structure of JavaScript Semantics Extraction Toolchain (JSSET)}
   \label{fig:overview}
@@
 
-From now, we describe the detailed techniques of ASE.
+From now, we describe the detailed techniques of JSSET.
 Section 3 formallly defines \( \bnfes \) and how to automatically
@@
 about initial settings to evaluate JavaScript programs. Section 6
-discusses the effectiveness of ASE with four research questions.
+discusses the effectiveness of JSSET with four research questions.
 Section 7 discusses related work and Section 8 concludes.

### 2019-08-15 icse/parser.tex
Written abstract

@@
 Each String literals are implicitly converted into lookahead parsers
-through Scala implicit conversions. The \( \code{opt(s)} \) funciton
+through Scala implicit conversions. The \( \code{opt(s)} \) function
 is same with \( \code{s | MATCH} \). We also define \( \code{\textbackslash} \)
-opertor between parsers to support exclusive parsers.
+operator between parsers to support exclusive parsers.
 Finally, we support the \( \code{NoLineTerminator} \) parser.
-It is a little bit tricky because it should hook the whitespace parsers
+It is a little bit tricky because it should hook the white space parsers
 and check whether it contains line terminators.
@@
 
-Moreover, we support automatic semicolon insertion algorihtms as well.
-It is the most distinctive parsing feautres in ECMAScript to parse more programs.
+Moreover, we support automatic semicolon insertion algorithms as well.
+It is the most distinctive parsing features in ECMAScript to parse more programs.
 We extend our parser implementation to keep track of the right-most position

### 2019-08-15 icse/related.tex
More writing for algorithm compiler
Written abstract

@@
 \subsection{Automatic Model Generation}
-There is similiar problems in many fields. Not only langauge semantics, many specification is not constructed formally, so many researcheres are trying to
+There is similar problems in many fields. Not only language semantics, many specification is not constructed formally, so many researches are trying to
 extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
-formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses javadoc comments of target API function with NLP techniques and various
+formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses Javadoc comments of target API function with NLP techniques and various
 heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
@@
 testing for each primitive is unavailable so we cannot decide correct semantics automatically.
+
+% TODO pseudo code의 형태와 natural language의 결합이다.
+% TODO moudular test로 guide를 받을 수 없어서 user defined rule을 사용. 대신, statistical analysis를 기반으로 guide해줌
 
@@
 Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
-web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many reseraches to define formal semantics of JavaScript and
-using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugraing. Their method can
+web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
+using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
 work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
-which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaSciprt based on ECMAScript specification, and they manually convert from specification
-to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verifiaction and analysis. Similarly, JaVerT coverts specification
+which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaScript based on ECMAScript specification, and they manually convert from specification
+to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verification and analysis. Similarly, JaVerT coverts specification
 to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
-convertion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.
+conversion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.
 

### 2019-08-15 icse/intro.tex
Updated introduction

@@
 
-JavaScript is one of widely used programming languages not only for client-sides
-but also for server-side programming~\cite{???} and even operating systems~\cite{???}.
-However, developers suffer from the intricate semantics of JavaScript and
-such complexities cause security vulnerabilities. For example, the following JavaScript
+JavaScript is one of widely used programming languages not only for client-side
+but also for server-side programming~\cite{nodejs, meanjs}
+and even small embedded systems~\cite{espruino, tessel2}.
+According to W3Techs\footnote{https://w3techs.com/technologies/details/cp-javascript/all/all},
+95.2\% of websites use JavaScript as the client-side programming language.
+Moreover, JavaScript is the top-ranked language used in active GitHub repositories
+\footnote{https://githut.info/}.
+Despite its popularity, JavaScript developers often suffer from its intricate semantics
+and it may causes security vulnerabilities. For example, the following JavaScript
 code seems to always return \( \code{false} \):
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{img/previous.png}
-  \caption{Previous approaches of semantics extractions for ECMAScript}
-  \label{fig:previous}
+  \includegraphics[width=0.48\textwidth]{img/existing.png}
+  \caption{Existing approaches of semantics extractions for ECMAScript}
+  \label{fig:existing}
 \end{figure}
 
-However, the existing JavaScript formal semantics are fully manually written
-by researchers based on ECMAScript specifications. ECMAScript is a standardized language
-of JavaScript and its specifications formally define its syntax and semantics.
-As described in Figure~\ref{fig:previous}, former researchers implement parser and
-describe semantics using their own intermediate representation (IR) according to the ECMAScript
-specifications. However, their approaches are fully manual thus excessively labor-intensive
-to handle full semantics.
+There have been several researches~\cite{lambdajs, kjs, javert} to define formal semantics of JavaScript
+for formal verification or program analysis. As illustrated in Figure~\ref{fig:existing},
+they define their own Intermediate Representations (IR) to represent JavaScript
+program semantics. They develop a parser for JavaScript programs and
+an AST-IR translator to convert JavaScript AST into their own IR.
+This approach helps us focus on IR to construct program analysis and formal verifications.
+It reduces the effort to handle the diverse and enormous features of JavaScript languages.
+We define such methodology that mechanizes to translate given AST into a treatable IR
+as \textit{IR-based semantics extractions}.
 
-Moreover, it is not suitable approach to cope with the updates of ECMAScript specifications.
-Most of full formal semantics of ECMAScript only supports ECMAScript 5.1 that was
-released in December 2009. Until 2014, it was not big deal because ECMAScript
+However, existing IR-based semantics extractions of JavaScript are not easy to
+handle recent JavaScript programs because they manually extract semantics.
+The JavaScript syntax and semantics are described in ECMAScript specifications.
+ECMAScript is a standardized language of JavaScript and written in structured natural languages.
+However, the problem is the amount of JavaScript syntax and semantics are huge.
+The most recent version of ECMAScript 2019 consists of 798 pages.
+Thus, it is excessively labor-intensive to handle full semantics and also error-prone.
+
+Moreover, it is not a suitable approach to cope with the updates of ECMAScript specifications.
+Most of formal semantics of ECMAScript supports only ECMAScript 5.1 that was
+released in December 2009. Until 2014, it was not a big deal because ECMAScript
 specifications are rarely updated. However, in late 2014, The Ecma Technical
@@
 lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \)),
-classes, for-of operators, asynchronous functions \( \code{async} \), or generators.
+classes, \( \code{for-of} \) operators, \( \code{async} \) functions, or generators.
 
-To alleviate such problems, we propose JavaScript Semantics Extraction Toolchain (JSSET)
-based on ECMAScript specifications. The tool automatically generates JavaScript parser
-from syntax provided by ECMAScript specifications. It also extracts formal
+In this paper, we propose JavaScript Syntax and Semantics Extraction Toolchain (JSSET)
+based on ECMAScript specifications. The tool automatically extracts JavaScript
+syntax and semantics from ECMAScript specifications. It generates JavaScript parser
+from the syntax provided by ECMAScript specifications. It also extracts formal
 JavaScript semantics in semi-automatic ways. It is semi-automatic because
-it depends on manually defined \textit{conversion rules}. Each rule describes how abstract
+it depends on manually defined \textit{conversion rules}. Each conversion rule describes how abstract
 algorithms in specifications are converted into functions of our core language \( \ires \).
-However, to save the labor of defining such rules, we also propose \textit{rule generation assistant}.
+However, to save the labor of defining such rules, we also propose a \textit{rule generation assistant}.
 It suggests new conversion rules based on statistical analysis of not yet convertible algorithms.
@@
 \begin{itemize}
-  \item JSSET enables to extract the syntax and semantics of ECMAScript 2019,
-    which is the latest released version of ECMAScript in June 2019.
+  \item JSSET enables to extract the syntax and semantics of ECMAScript 2020,
+    which is the next released version of ECMAScript in June 2020.
     Moreover, we successfully applied our tool into the next proposed version,
@@
     to find possible specification errors. We found \inred{X} possible specification errors
-    in ECMAScript 2019 and reported them into TC39, which is the Ecma Technical Committee.
+    in ECMAScript 2020 and reported them into TC39, which is the Ecma Technical Committee.
     We confirm that all of them are real specification errors.

### 2019-08-15 icse/main.tex
Updated introduction

@@
 
-\title{JSSET: JavaScript Semantics Extraction Toolchain}
+\title{JSSET: JavaScript Syntax and Semantics Extraction Toolchain}
 
@@
 
-To alleviate such problems, we propose JSSET, a JavaScript Semantics Extraction
-Toolchain. It automatically extracts JavaScript formal semantics from ECMAScript
+To alleviate such problems, we propose JSSET, a JavaScript Syntax and Semantics
+Extraction Toolchain. It automatically extracts JavaScript syntax and semantics from ECMAScript
 specifications. JSSET generates JavaScript parser for the given grammar written

### 2019-08-16 icse/framework.tex
fix section 5.2 and 7

@@
 
-In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
-environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript language.
+In this section, we demonstrate how our idea can be implemented for target language. Although it is hard to generalize the process because the format of specification or
+environment of the programming language is varying, We shows the possibility to build entire system to extract target language specification and interpreting it with minimal human effort by giving end-to-end example of ECMAScript language.
 
@@
 
-\subsection{Generating initial environment for evaluating}
-For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsic objects. We will describe how to generate each component.
+\subsection{Generating initial environment for execution}
+For ECMAScript Specification, initial environment consists of the Builtin objects, and Intrinsic objects. We describe how to generate each component.
 
@@
 
- Builtin object is pre-defined object with many built-in functions. For example, In ECMAScript \( \code{Array} \) refers an object which can generate an array by
- calling it. Each Builtin Object provides fields and function, just as ordinary object. When its function is called,
- the corresponding algorithm specified in the document should be called.
+ Builtin object is a pre-defined object with many built-in functions. For example, In ECMAScript \( \code{Array} \) corresponds to an object which can generate an array by
+ calling it. Each builtin object provides data property and functions, just as ordinary object. When its function is called,
+ its algorithm specified in the document should be called.
 
- In specification, a built-in function object usually matches to abstract algorithm. Its algorithm name
+ In specification, a builtin function object usually matches to abstract algorithm. Its algorithm name
  describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
- we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as attribute. 
- To support builtin object, we make structure of builtin object and its attributes.
+ we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as property.
+ To support builtin object, we make structure of builtin object and its properties.
  After we correctly organizes structure, then we made algorithm that automatically map corresponding field to the abstract algorithm in specification by matching its function name.
@@
 
- While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently referred in specification. But name of builtin objects
- are defined for reference in Host language, so it needs another name to refer it in specification language. For example, \( \code{Array} \) is a name for
- ECMAScript reference, so abstract algorithm should call \\
- \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm introduces Intrinsic objects, which
-are alias for built-in objects. For example it is referred as \( \code{\%Array\%} \) to refer Array Object.
+ In specification, "Well-known intrinsics are built-in objects that are explicitly referenced by the algorithms".
+ Abstract algorithm uses name like "\%name\%", which are alias for builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
  Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.
@@
  and we insert functions as property of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
- then we insert attributes with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.
+ then we insert property with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.
 

### 2019-08-16 icse/related.tex
fix section 5.2 and 7

@@
 \subsection{Formal Semantics of JavaScript}
-Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
-web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
-using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
+
+% Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
+% web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
+% using it to formal verification or program analysis.
+There are also many researches to define formal semantics of JavaScript. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
 work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,

### 2019-08-16 icse/eval.tex
Revised intro & overview

--- 2019-08-08 icse/eval.tex
@@
-\section{Evaluation}
+\section{Evaluation}\label{sec:eval}
 
 \begin{itemize}
-  \item RQ1) Does ASE correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
+  \item RQ1) Does \( \tool \) correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
     test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
-  \item RQ2) Is endurable size of manual portion in implementation of ASE? \inred{refactoring for conversion rules / get statistics of conversion rules}
+  \item RQ2) Is endurable size of manual portion in implementation of \( \tool \)? \inred{refactoring for conversion rules / get statistics of conversion rules}
     개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
-  \item RQ3) Does ASE deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
+  \item RQ3) Does \( \tool \) deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
     각 feature name / 의미 / compile 성공률 / 결과 test
-  \item RQ4) How many specification errors are detected by ASE? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
+  \item RQ4) How many specification errors are detected by \( \tool \)? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
 \end{itemize}

### 2019-08-16 icse/intro.tex
Revised intro & overview

@@
   \includegraphics[width=0.48\textwidth]{img/existing.png}
-  \caption{Existing approaches of semantics extractions for ECMAScript}
+  \caption{Existing approaches of IR-based semantics extractions for ECMAScript}
   \label{fig:existing}
@@
 
-In this paper, we propose JavaScript Syntax and Semantics Extraction Toolchain (JSSET)
+In this paper, we propose JavaScript IR-based Semantics Extraction Toolchain (\( \tool \))
 based on ECMAScript specifications. The tool automatically extracts JavaScript
 syntax and semantics from ECMAScript specifications. It generates JavaScript parser
-from the syntax provided by ECMAScript specifications. It also extracts formal
-JavaScript semantics in semi-automatic ways. It is semi-automatic because
-it depends on manually defined \textit{conversion rules}. Each conversion rule describes how abstract
-algorithms in specifications are converted into functions of our core language \( \ires \).
+from the syntax provided by ECMAScript specifications. It also automatically extracts
+formal JavaScript semantics with given \textit{conversion rules}. Each conversion
+rule describes how abstract algorithms in specifications are converted into
+functions of our intermediate representation \( \ires \) for ECMAScript.
 However, to save the labor of defining such rules, we also propose a \textit{rule generation assistant}.
@@
 
-Our main contribution is our tool JSSET that mechanizes extraction of JavaScript syntax and semantics
+Our main contribution is our tool \( \tool \) that mechanizes extraction of JavaScript syntax and semantics
 from ECMAScript specifications:
 \begin{itemize}
-  \item JSSET enables to extract the syntax and semantics of ECMAScript 2020,
+  \item \( \tool \) enables to extract the syntax and semantics of ECMAScript 2020,
     which is the next released version of ECMAScript in June 2020.
@@
     among them.
-  \item JSSET is also applicable in-process proposed language features in a modular way.
+  \item \( \tool \) is also applicable in-process proposed language features in a modular way.
     ECMAScript specifications are open-source based documentations. Thus, anyone
@@
     such proposals and adds them into specifications. Each in-process proposed language
-    feature has its own specification and tests. Thus, we apply JSSET into the specification
+    feature has its own specification and tests. Thus, we apply \( \tool \) into the specification
     and evaluate the corresponding tests. Among \inred{XX} proposals, we successfully
@@
     proposals.
-  \item Moreover, all extraction mechanisms in JSSET is automatic thus we could use this tool
+  \item Moreover, all extraction mechanisms in \( \tool \) is automatic thus we could use this tool
     to find possible specification errors. We found \inred{X} possible specification errors

### 2019-08-16 icse/main.tex
Revised intro & overview

@@
 
-\title{JSSET: JavaScript Syntax and Semantics Extraction Toolchain}
+\title{\( \tool \): JavaScript IR-based Semantics Extraction Toolchain}
 
@@
 
-To alleviate such problems, we propose JSSET, a JavaScript Syntax and Semantics
+To alleviate such problems, we propose \( \tool \), a JavaScript IR-based Semantics
 Extraction Toolchain. It automatically extracts JavaScript syntax and semantics from ECMAScript
-specifications. JSSET generates JavaScript parser for the given grammar written
+specifications. \( \tool \) generates JavaScript parser for the given grammar written
 in \( \bnfes \), an extended BNF used in ECMAScript specifications.
@@
 for ECMAScript specifications. The conversion from algorithms to \( \ires \) functions
-is defined with \textit{conversion rules}. We apply JSSET into the next proposed
+is defined with \textit{conversion rules}. We apply \( \tool \) into the next proposed
 version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
 in test262, the official ECMAScript conformance test suite.
-Moreover, JSSET also successfully extracts semantics for \inred{XX} proposed features
+Moreover, \( \tool \) also successfully extracts semantics for \inred{XX} proposed features
 by adding only \inred{XX} minor conversion rules.

### 2019-08-16 icse/overview.tex
Revised intro & overview

--- 2019-08-07 icse/overview.tex
@@
   \includegraphics[width=0.5\textwidth]{img/overview.png}
-  \caption{Overall structure of Automatic Semantics Extractor (ASE)}
+  \caption{Overall structure of JavaScript IR-based Semantics Extraction Toolchain (\( \tool \))}
   \label{fig:overview}
@@
 
+In this section, we introduce the overall structure of \( \tool \) and the outline of
+this paper. The main motivation of automatically extracting syntax and semantics of JavaScript
+from ECMAScript specifications is that they are provided as HTML files in well-organized ways.
+We utilize such well-organized structures and HTML tag information to extract
+syntax and semantics of JavaScript. The overall structure of \( \tool \) is depicted
+in Figure~\ref{fig:overview}. For the first step, we develop the spec extractor
+in JavaScript to extract syntax and semantics in JSON formats from
+the ECMAScript specification HTML file.
+
 \begin{figure}
   \centering
-  \includegraphics[height=18em]{img/to_primitive.png}
+  \begin{subfigure}[t]{0.4\textwidth}
+    \includegraphics[width=\textwidth]{img/array_literal.png}
+    \caption{ArrayLiteral production in ECMAScript 2019 specification.}
+    \label{fig:array-literal-es}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.48\textwidth}
+    \begin{lstlisting}[style=myScalastyle]
+type P[T] = List[Boolean] => LAParser[T]
+lazy val ArrayLiteral: P[ArrayLiteral] = memo {
+  case List(Yield, Await) =>
+  "[" ~ opt(Elision) ~ "]" ^^ ArrayLiteral0 |
+  "[" ~ ElementList(Yield, Await) ~ "]" ^^ ArrayLiteral1 |
+  "[" ~ ElementList(Yield, Await) ~ "," ~ opt(Elision) ~ "]" ^^ ArrayLiteral2
+}
+    \end{lstlisting}
+    \caption{The generated parser for ArrayLiteral production.}
+    \label{fig:array-literal-parser}
+  \end{subfigure}
+  \caption{ArrayLiteral grammar production in ECMAScript 2019.}
+  \label{fig:array-literal}
+\end{figure}
+
+ECMAScript specifications provide their lexical and syntactic grammars in Appendix A
+using their own extended Backus-Naur Form (BNF) for ECMAScript.
+We call it as \( \bnfes \) and formally define it in Section~\ref{sec:parser}.
+The spec extractor to extract grammars written in \( \bnfes \) into JSON files.
+For example, Figure~\ref{fig:array-literal-es} denotes the \( ArrayLiteral \) production
+in ECMAScript 2020 specification. It takes two boolean parameters
+\( Yield \) and \( Await \) and consists of three right-hand sides.
+the first right-hand side consists of three symbols; two terminal symbols \( \code{[} \) and
+\( \code{]} \), one non-terminal symbol \( Elision_{opt} \). The \( opt \)
+subscript denotes that it is optional. In the second and third right-hand sides,
+\( ElementList[?Yield, ?Await] \) denotes the parametric non-terminal symbol
+with the parameters \( Yield \) and \( Await \) of \( ArrayLiteral \) as two arguments.
+The prefix \( ? \) denotes that the given parameter is passed as an argument.
+
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}{0.4\textwidth}
+    \includegraphics[width=\textwidth]{img/to_primitive.png}
+    \subcaption{\( \code{ToPrimitive} \) abstract algorithm in ES2019.}
+    \label{fig:to-primitive-es}
+  \end{subfigure}
+  \qquad
+  \begin{subfigure}{0.48\textwidth}
     \begin{lstlisting}[style=ires]
@@
   \label{fig:to-primitive}
-\end{figure}
+\end{figure*}
 
-\begin{itemize}
-  \item Sytnax: automatically generate parser from ES-BNF
-    \begin{itemize}
-      \item ES-BNF features
-      \item Packrat Parsers with 1-lookahead
-      \item Example
-    \end{itemize}
-  \item Semantics: automatically convert abstract algorithms into Core programs
-    \begin{itemize}
-      \item Abstract algorithms
-      \item Example
-    \end{itemize}
-\end{itemize}
-\begin{itemize}
-  \item Figure of overall structure
-  \item Explanation of each module
-\end{itemize}
+To generate JavaScript parser from the given \( \bnfes \) grammar,
+we construct the \textit{parser generator} in Scala.
+It synthesizes a JavaScript parser in Scala according to the given \( \bnfes \)
+and the generated parser is defined with Scala parser combinators~\cite{scala-parser-combinators}.
+Moreover, we propose \textit{lookahead parsers} for correct and fast parsing.
+A lookahead parser keeps track of its lookahead, which is the set of
+the possible next tokens. With lookahead parsers, the generated parsers are
+readable and one-to-one corresponds to each grammar components.
+For example, Figure~\ref{fig:array-literal-parser} is the generated parser of
+the \( ArrayLiteral \) production in Figure~\ref{fig:array-literal-es}.
+Each parser has the \( \code{List[Boolean] => LAParser[T]} \) type because
+each production in \( \bnfes \) is parametric with boolean values.
+The \( \code{memo} \) is a memoization function for pairs of boolean parameters and result parsers.
+for optimizations. The lazy value \( \code{ArrayLiteral} \) corresponds to the \( ArrayLiteral \)
+production. In the parser, each String literal such as \( \code{"["} \) or \( \code{"]"} \)
+denotes a parser for a terminal symbol. The \( \code{opt} \) helper function creates
+optional parsers. The parametric non-terminal \( ElementList \) with arguments \( Yield \)
+and \( Await \) is represented as a function call \( \code{ElementList(Yield, Await)} \).
+The \( \code{\textasciitilde} \) operator combines two parsers
+and the \( \code{\^{}\^{}} \) operator denotes how to construct the abstract syntax trees (AST).
+The right side of \( \code{\^{}\^{}} \) is the constructor of AST and each constructor
+has the number to denote the order between right-hand sides. For example,
+The \( \code{ArrayLiteral0} \) constructor denotes that the first right-hand side of
+the \( ArrayLiteral \) production.
+
+The semantics in ECMAScript specifications are described as
+abstract algorithms. They are written in structured natural languages
+with ordered steps and tagged tokens. The spec extractor extracts each abstract algorithm
+with HTML tags because we utilize tag information to discriminate different kinds of tokens.
+For example, Figure~\ref{fig:to-primitive-es} is the \( \code{ToPrimitive} \)
+abstract algorithm in ECMAScript 2020. It has three steps and
+second step consists of seven sub-steps. Each parameter or local variable such as
+\( \code{input} \) or \( \code{PreferredType} \) is written with \( \code{<var>} \) HTML tags
+and each value is tagged with \( \code{<code>} \).
+
+To extract such abstract algorithms into treatable representations,
+we define \( \ires \), a specialized intermediate representation
+for ECMAScript abstract algorithms. Then, we develop the \textit{algorithm compiler}
+in Scala using also Scala parser combinators to convert given abstract algorithms
+into \( \ires \) functions. It is dependent on the conversion rules that consists of two parts;
+parsing rules and mapping from each rule into \( \ires \) component.
+We explain detailed role of conversion rules in Section~\ref{sec:compiler}.
+Thus, each abstract algorithm is converted into a function written in \( \ires \)
+through the algorithm compiler. For example, Figure~\ref{fig:to-primitive-ires}
+describes the generated \( \ires \) function for the \( \code{ToPrimitive} \)
+algorithm. The \( \code{input} \) and \( \code{PreferredType} \) are parameters
+of the \( \code{ToPrimitive} \) function. The parameter \( \code{PreferredType} \)
+is might be optional but we handle such cases with a special value \( \code{absent} \).
+The \( \code{absent} \) value denotes that it is not present.
+Thus, the condition of the step 2-a is converted into
+the equality check with the \( \code{absent} \).
+For the assertions, we omit in this paper but we believe that it could be handled in
+the same approach. The specific keywords will be represented as string values.
+For instance, the hint Number or the hint String converted into \( \code{"Number"} \)
+and \( \code{"String"} \). Moreover, the algorithm compiler modifies prefixes of
+symbols from @@ to \( \code{SYMBOL\_} \) and handle exceptions with the corresponding
+intrinsic error objects.
+
+Finally, the AST-\( \ires \) translator is constructed with the given \( \ires \)
+functions with manually specified global settings. The global settings have
+minor but necessary information to evaluate given JavaScript programs.
+For example, structure of builtin objects, name aliases for intrinsic objects,
+and types of abstract algorithms. Then, we could translate a given JavaScript program
+into \( \ires \) through the generated JavaScript parser and AST-\( \ires \) translator
+via \( \tool \).
+
+From now, we describe the detailed techniques of \( \tool \).
+Section~\ref{sec:parser} formallly defines \( \bnfes \) and how to automatically
+generate parsers from given \( \bnfes \) using lookahead parsers.
+Section~\ref{sec:compiler} explains abstract algorithms with tagged tokens
+and how to compile them into \( \ires \) functions based on
+given conversion rules. Moreover, we introduce the rule generation assistant
+to easily construct conversion rules. Section~\ref{sec:framework} describes
+the implemented details including global settings to evaluate JavaScript programs.
+Section~\ref{sec:eval} discusses the effectiveness of \( \tool \) with
+four research questions.
+Section~\ref{sec:related} discusses related work and Section 8 concludes.

### 2019-08-16 icse/compiler.tex
Revised intro & overview
Updated images

@@
-\section{Algorithm Compiler}
+\section{Algorithm Compiler}\label{sec:compiler}
 
@@
 the \textit{rule generation assistant} to make easy write conversion rules.
-It diagnoses root causes of failed parsing tokens
-and suggests new conversion rules based on
-statistical analysis of algorithm steps that failed to be parsed.
+It suggests new conversion rules based on
+statistical analysis of algorithm steps that failed to be parsed
+and also diagnoses root causes of parsing failures.
 
@@
 \( \code{ToPrimitive} \) into the following syntactic parse tree:
-\includegraphics[width=0.5\textwidth]{img/parse_tree.png}
+\includegraphics[width=0.5\textwidth]{img/token_ast.png}
 
@@
 
+\inred{
 To make easy write conversion rules, we support \textit{rule generation assistant}.
-It consists of several helper functions to show the specific statistics of
-the not yet convertible abstract algorithm steps. It make easy not only construct
-conversion rules from the scratch but also update existing conversion rules
-for updated specifications. We explain each helper function and how to utilize
-it to construct conversion rules.
+It consists of two helper functions; the \textit{rule recommender} and
+the \textit{fault localizer}. The
 
-\subsubsection{Statement format suggestions}
+It makes easy not only construct conversion rules from the scratch
+but also updates existing conversion rules to handle specification updates.
+We explain each helper function and how to utilize it to construct conversion rules.
 
-\inred{TODO}
+\subsubsection{Statistics Monitor}
 
-\subsubsection{Fault localization based on \( \tstar \) tokens}
+TODO
 
-\inred{TODO}
+\subsubsection{Fault localizer}
+
+TODO
+}

### 2019-08-16 icse/compiler.tex
Revised section 4 except 4.4

@@
 a list of tagged tokens. Then, the token parser constructs
-syntactic parse tree of the given token list.
-Finally, the \( \ires \) function generator constructs the corresponding
-\( \ires \) function from the given parse tree.
-The parser and the generator is dependent on conversion rules
-and we define the general conversion rules for abstract algorithms in
+abstract syntax tree (AST) of the given token list.
+Finally, the \( \ires \) matcher constructs the corresponding
+\( \ires \) function from the given token AST.
+The parser and the matcher are dependent on compile rules
+and we define the general compile rules for abstract algorithms in
 ECMAScript specifications. Like Coq, a proof assistant, we also provide
-the \textit{rule generation assistant} to make easy write conversion rules.
-It suggests new conversion rules based on
-statistical analysis of algorithm steps that failed to be parsed
-and also diagnoses root causes of parsing failures.
+the \textit{rule assistant} to make easy write compile rules.
+It suggests new compile rules based on
+statistical analysis of failed algorithm steps to be parsed
+and also diagnoses root causes of parsing failures
+for updated abstract algorithms.
 
@@
 and it might contain sub-steps as well. For example,
-the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es}
+the ToPrimitive algorithm in Figure~\ref{fig:to-primitive-es}
 has three steps and second step has seven sub-steps.
@@
 We try to keep the tag information for each token to generate more
-precise conversion rules. For example, if and only if a token has a tag
+precise compile rules. For example, if and only if a token has a tag
 \( \code{<var>} \), it is a parameter or a local variable.
-Thus, it is possible to construct a conversion rule precisely discriminates
+Thus, it is possible to construct a compile rule precisely discriminates
 identifiers and other components.
@@
 should be a sequence of alphanumeric characters or a single
-non-alphanumeric character. For example, in the \( \code{ToPrimitive} \)algorithm,
-\( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
+non-alphanumeric character. For example, in the ToPrimitive algorithm,
+\( \textbf{\code{"default"}} \) is a single token with the HTML tag \( \code{<code>} \)
 and \( \code{@@toPrimitive} \) is divided into three text tokens
@@
 
-For the linear structures, the tokenizer flatten the structured steps into
-a single list. Some conversion rules should handle multiple steps such as
-the conditional statements (if-then-else). Thus, we decide to break down
-structured algorithms using three special tokens;
-\( \tend \) denotes the end of a single step,
+Moreover, the tokenizer flattens the structured steps into
+a single token list to easily handle multi-step statements.
+Several statements in abstract algorithms consists of multilple steps.
+For example, an if-then-else statement often consists of two steps;
+one step for the then-branch and another step for the else-branh.
+For linear structures, we introduce three special tokens to break down structured
+algorithms; \( \tend \) denotes the end of a single step,
 \( \tin \) and \( \tout \) the start and the end of nested steps, respectively.
-For example, the \( \code{ToPrimitive} \) algorithm is tokenized as follows.
+For example, the ToPrimitive algorithm is tokenized as follows.
 \[
@@
 
-\subsection{Token Parser}
+After tokenizing abstract algorithms, the algorithm compiler compiles token lists
+into \( \ires \) functions. It consists of two modules; the token list parser and
+the token AST converter. They are dependent on compile rules and each compile rule
+consists of a \textit{parsing rule} and a \textit{conversion rule}:
+\begin{lstlisting}[style=myScalastyle]
+val CompileRule = ParsingRule ^^ ConversionRule
+\end{lstlisting}
+For the compile rule \( \code{CompileRule} \), the parsing rule
+\( \code{ParsingRule} \) describes how to parse the given token list into structured
+token AST. The conversion rule \( \code{ConversionRule} \) describes how to
+convert the given token AST structure into an \( \ires \) component.
+Now, we explain the token list parser and token AST converter with
+parsing rules and conversion rules, respectively.
 
-The token parser parses a given list of tokens into a syntactic parse tree.
-It depends on the given \textit{conversion rules} that consists of
-two parts parsing rules and mapping from parsing rules into corresponding
-\( \ires \) components.
-A parsing rule consists of basic token matchers and other parsing rules
-including itself. For example, the following parsing rule is simplified version for
-sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
+\subsection{Token List Parser}
+
+The token list parser is dependent on the given parsing rules.
+Each parsing rule is written in extended Scala parser combinators.
+We modify the meaning of alternative composition operator ( \( | \) ) to collect
+all longest matched results. If the parser detects that a step cannot be
+parsed with the given parsing rules. It reports that the step is not possible
+to be parsed under the given rules into the rule assistant.
+Moreover, even though the parser could parse the step, it will be also reported
+if it could be parsed in not a single but multiple ways.
+We basically use Packrat parsing~\cite{packrat}, the parsing rule could support
+not only non-left recursive but also left recursive parsing rules.
+
+We support two kinds of basic token parsers; tag-based parsers and
+content-based parsers. A tag-based parser just checks that the next
+token has the given tag. For example, the tag-based parser \( \code{varT} \)
+checks that the next token has the tag \( \code{<var>} \). A content-based parser
+checks that the next token is text token and its content passes the given condition.
+For example, the String literal \( \code{"Let"} \) denotes the content parser
+that checks whether the next token is text token with the content \( \code{Let} \).
+Moreover, we provide two content parsers \( \code{word} \) and \( \code{number} \)
+that checks the content consists of only alphabets or numbers, respectively.
+In the parsing rule, any helper functions defined in Scala parser combinators
+are available. For example, the helper function \( \code{repsep(p, q)} \) generates a new
+parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
+using another parsing rule \( \code{q} \) as the separator.
+
+For example, the following parsing rule is simplified version for
+the step 2-e-i of the ToPrimitive algorithm.
 \begin{lstlisting}[style=myScalastyle]
@@
   // function calls
-  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
+  word ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
   // lists
@@
 \end{lstlisting}
+The \( \code{Stmt} \) denotes the compile rule for statements with one
+parsing rule. The \( \code{Expr} \) represents the compile rule for expressions
+with four different parsing rules. Finally, the token parser with the above rules
+parses the step 2-e-i in the ToPrimitive into the following
+token AST:
+\begin{center}
+\includegraphics[width=0.5\textwidth]{img/token_ast.png}
+\end{center}
 
-Each parsing rule is written in extended Scala parser combinators.
-We modify the meaning of alternative composition operator ( \( | \) ) to collect
-all longest matched results. If the parser detects that a step cannot be
-parsed with the given parsing rules. It reports that a step is not possible
-to be parsed under the given rules into the rule generation assistant.
-Moreover, even though the parser could parse a step, it will be also reported
-if it could be parsed in not a single but multiple ways.
-Each string literal is a token matcher for tokens without any tags and checks
-that the token has same string value with the string literal.
-The \( \code{varT} \) and \( \code{textT} \) is also token matchers
-for token with the tag \( \code{<var>} \) and no tags.
-The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
-defined with our extended parser combinators.
-Moreover, it supports all helpers functions defined in Scala parser combinators.
-For example, the helper function \( \code{repsep(p, q)} \) generates a new
-parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
-using another parsing rule \( \code{q} \) as separators.
-Finally, the token parser with the above rules parses sub-step \( i \) in the
-\( \code{ToPrimitive} \) into the following syntactic parse tree:
-\includegraphics[width=0.5\textwidth]{img/token_ast.png}
+\subsection{Token AST Converter}
 
-\subsection{\( \ires \) Function Generator}
-
-We define \( \ires \) language to give semantics into syntactic parse tree of
-abstract algorithm steps. It has the following language features:
+We define \( \ires \) to represent abstract algorithms as its functions.
+The following bullets explain the reason of our language design choices
+for \( \ires \).
 
@@
 \item \textbf{Dynamic Typing} We decide to use dynamic typing for \( \ires \)
-because each variables in abstract algorithms are not statically typed.
+because each variable in abstract algorithms are not statically typed.
 Thus, variables do not have its own static types while each value of \( \ires \)
@@
 \item \textbf{Imperative Style} \( \ires \) represents algorithm steps
-as statements. Each statement changes the current state
-that consists of environments and a heap.
+as imperative-style instructions. Each instruction changes the current state
+that consists of an environment and a heap.
 
 \item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
-lambda functions as values but it has only restricted scopes. In each function,
-only global variables, parameter, and newly defined local variables are accessible.
-It means that the function closure does not capture the the current environment.
+lambda functions as values but they have only restricted scopes. In each function,
+only global variables, parameters, and newly defined local variables are available.
+It means that the function closure does not capture the current environment.
 We use such restricted scopes because it is enough to represent abstract algorithms.
@@
 \item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
-the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
-are defined in \( \ires \); numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
+the symbols that is newly introduced after ECMAScript 6. In JavaScript, symbols are
+primitive values but it is much easier to treat them as singleton objects.
+Thus, only five ECMAScript primitives are defined in \( \ires \);
+numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
 Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
 the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
-of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es} might be
+of ToPrimitive algorithm in Figure~\ref{fig:to-primitive-es} might be
 not present in some function calls. Then, the parameter has the \( \code{absent} \) value
@@
 For example, ECMAScript environment records are represented as \( \code{Record} \) data types
-from String values for identifier names into addresses.
-The addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings.
-We treat a ECMAScript constants such as \( \code{empty} \) and primitive symbols as singleton
-data types in \( \ires \).
+String values as keys and addresses as values. Each key String value represents an identifier
+name and each address represents an ECMAScript binding object.
+Thus, the addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings
+in the heap. We treat not only symbols but also constants used in ECMAScript specifications,
+such as \( \code{empty} \) or \( \code{normal} \), as singleton data types in \( \ires \).
 \end{itemize}
 
-To generate the corresponding \( \ires \) function from syntactic parse tree,
-we describe the mapping from each parsing rule into the corresponding \( \ires \) components.
-For example, we describe the following mapping for the previous example parsing rules:
+To generate the corresponding \( \ires \) function from the given token AST,
+the token AST converter uses the given coversion rules. Each conversion rule is
+defined with the corresponding parsing rule and it is a function from given token AST
+into an \( \ires \) component. For basic token parsers, their conversion rules
+always return the String value of the content in the parsed token.
+For example, the following conversion rules are for the previous example
+parsing rules:
 \begin{lstlisting}[style=myScalastyle]
 // statements
-val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ESLet(x, y) }
+val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
 // expressions
@@
   // identifiers
-  ... ^^ { x => x } |
+  ... ^^ { x => EId(x) } |
   // return if abrupt
-  ... ^^ { _ ~ e => ESReturnIfAbrupt(e) } |
+  ... ^^ { _ ~ e => EReturnIfAbrupt(e) } |
   // function calls
-  ... ^^ { case x ~ _ ~ y ~ _ => ESCall(x, y) } |
+  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) } |
   // lists
-  ... ^^ { case _ ~ x ~ _ => ESList(e) }
+  ... ^^ { case _ ~ x ~ _ => EList(e) }
 )
 \end{lstlisting}
-Finally, sub-step \( i \) in the \( \code{ToPrimitive} \) is converted
-into the following instruction:
+The conversion rule of the compile rule \( \code{Stmt} \) takes
+only second and fourth sub trees and convert them into \( \ires \) components.
+The second sub-tree is converted into a String value because it was
+constructed via basic the token parser \( \code{varT} \).
+The fourth sub-tree is converted into an \( \ires \) expression
+because the conversion rules of the \( \code{Expr} \) compile rule
+constructs \( \ires \) expressions.
+Then, the conversion rule of \( \code{Stmt} \) constructs the
+lexical binding instruction \( \code{ILet} \) with the String value
+and the \( \ires \) expression. Finally, sub-step 2-e-i in the ToPrimitive
+is converted into the following instruction:
 \begin{lstlisting}[style=ires]
@@
 \inred{
-To make easy write conversion rules, we support \textit{rule generation assistant}.
+To make easy write compile rules, we support \textit{rule generation assistant}.
 It consists of two helper functions; the \textit{rule recommender} and
@@
 
-It makes easy not only construct conversion rules from the scratch
-but also updates existing conversion rules to handle specification updates.
-We explain each helper function and how to utilize it to construct conversion rules.
+It makes easy not only construct compile rules from the scratch
+but also updates existing compile rules to handle specification updates.
+We explain each helper function and how to utilize it to construct compile rules.
 

### 2019-08-16 icse/eval.tex
Revised section 4 except 4.4

@@
     test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
-  \item RQ2) Is endurable size of manual portion in implementation of \( \tool \)? \inred{refactoring for conversion rules / get statistics of conversion rules}
+  \item RQ2) Is endurable size of manual portion in implementation of \( \tool \)? \inred{refactoring for compile rules / get statistics of compile rules}
     개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
-  \item RQ3) Does \( \tool \) deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
+  \item RQ3) Does \( \tool \) deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of compile rules}
     각 feature name / 의미 / compile 성공률 / 결과 test

### 2019-08-16 icse/intro.tex
Revised section 4 except 4.4

@@
 from the syntax provided by ECMAScript specifications. It also automatically extracts
-formal JavaScript semantics with given \textit{conversion rules}. Each conversion
+formal JavaScript semantics with given \textit{compile rules}. Each compile
 rule describes how abstract algorithms in specifications are converted into
@@
 However, to save the labor of defining such rules, we also propose a \textit{rule generation assistant}.
-It suggests new conversion rules based on statistical analysis of not yet convertible algorithms.
+It suggests new compile rules based on statistical analysis of not yet convertible algorithms.
 The assistant helps us deal with changed or newly introduced algorithms defined in new versions of

### 2019-08-16 icse/main.tex
Revised section 4 except 4.4

@@
 languages into functions written in \( \ires \), an Intermediate Representation
-for ECMAScript specifications. The conversion from algorithms to \( \ires \) functions
-is defined with \textit{conversion rules}. We apply \( \tool \) into the next proposed
+for ECMAScript specifications. The compilation from algorithms to \( \ires \) functions
+is defined with \textit{compile rules}. We apply \( \tool \) into the next proposed
 version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
@@
 Moreover, \( \tool \) also successfully extracts semantics for \inred{XX} proposed features
-by adding only \inred{XX} minor conversion rules.
+by adding only \inred{XX} minor compile rules.
 \end{abstract}

### 2019-08-16 icse/overview.tex
Fixed small errors
Revised section 4 except 4.4

@@
     \includegraphics[width=\textwidth]{img/array_literal.png}
-    \caption{ArrayLiteral production in ECMAScript 2019 specification.}
+    \caption{\( ArrayLiteral \) production.}
     \label{fig:array-literal-es}
@@
     \end{lstlisting}
-    \caption{The generated parser for ArrayLiteral production.}
+    \caption{The generated parser for \( ArrayLiteral \) production.}
     \label{fig:array-literal-parser}
   \end{subfigure}
-  \caption{ArrayLiteral grammar production in ECMAScript 2019.}
+  \caption{\( ArrayLiteral \) production in ECMAScript 2020 specification and its generated parser.}
   \label{fig:array-literal}
@@
     \includegraphics[width=\textwidth]{img/to_primitive.png}
-    \subcaption{\( \code{ToPrimitive} \) abstract algorithm in ES2019.}
+    \subcaption{The ToPrimitive abstract algorithm.}
     \label{fig:to-primitive-es}
@@
     \end{lstlisting}
-    \subcaption{The \( \ires \) funciton for \( \code{ToPrimitive} \)
-    abstract algorithm.}
+    \subcaption{The \( \ires \) funciton for the ToPrimitive algorithm.}
     \label{fig:to-primitive-ires}
   \end{subfigure}
-  \caption{\( \code{ToPrimitive} \) abstract algorithms
-  and its generated core program.}
+  \caption{ToPrimitive abstract algorithm in ECMAScript 2020 specification and its generated \( \ires \) function.}
   \label{fig:to-primitive}
@@
 with HTML tags because we utilize tag information to discriminate different kinds of tokens.
-For example, Figure~\ref{fig:to-primitive-es} is the \( \code{ToPrimitive} \)
+For example, Figure~\ref{fig:to-primitive-es} is the ToPrimitive
 abstract algorithm in ECMAScript 2020. It has three steps and
@@
 in Scala using also Scala parser combinators to convert given abstract algorithms
-into \( \ires \) functions. It is dependent on the conversion rules that consists of two parts;
+into \( \ires \) functions. It is dependent on the compile rules that consists of two parts;
 parsing rules and mapping from each rule into \( \ires \) component.
-We explain detailed role of conversion rules in Section~\ref{sec:compiler}.
+We explain detailed role of compile rules in Section~\ref{sec:compiler}.
 Thus, each abstract algorithm is converted into a function written in \( \ires \)
 through the algorithm compiler. For example, Figure~\ref{fig:to-primitive-ires}
-describes the generated \( \ires \) function for the \( \code{ToPrimitive} \)
+describes the generated \( \ires \) function for the ToPrimitive
 algorithm. The \( \code{input} \) and \( \code{PreferredType} \) are parameters
@@
 and how to compile them into \( \ires \) functions based on
-given conversion rules. Moreover, we introduce the rule generation assistant
-to easily construct conversion rules. Section~\ref{sec:framework} describes
+given compile rules. Moreover, we introduce the rule generation assistant
+to easily construct compile rules. Section~\ref{sec:framework} describes
 the implemented details including global settings to evaluate JavaScript programs.

### 2019-08-16 icse/compiler.tex
Written 4.4 Rule Assistant

@@
 
-\subsection{Rule Generation Assistant}
+\subsection{Rule Assistant}
 
-\inred{
-To make easy write compile rules, we support \textit{rule generation assistant}.
-It consists of two helper functions; the \textit{rule recommender} and
-the \textit{fault localizer}. The
+To make easy write compile rules, we support \textit{rule assistant}.
+It takes currently not yet convertible steps as arguments
+and we call them as failed steps. For each failed step,
+The rule assistant diagnosis the root cause of parsing failures.
+The basic idea is to check that it becomes possible to be parsed
+with assumption that a speicific sub-sequence of failed steps is
+successfully parsed. We define the approach to find such sub-sequences of
+failed steps as \textit{fault localizations}. The rule assistant recommend
+new compile rules for failed steps via fault localizations.
+Moreover, it also helps us update existing compile rules for new version
+of specifications.
 
-It makes easy not only construct compile rules from the scratch
-but also updates existing compile rules to handle specification updates.
-We explain each helper function and how to utilize it to construct compile rules.
+The fault localization algorithm is evaluated with the special token \( \tstar \).
+The special token \( \tstar \) represents a sub-sequence of a failed step.
+The rule assistant substitues a specific sub-sequence \( T[i..j] \) of the
+failed step \( T \) into a single star token \( \tstar \). For each compile rule,
+the parsing rule  \( \code{starT} \) is implicitely added to utilize it in the
+rule assistant. The \( \code{starT} \) is a special basic token parser
+that just checks whether the given token is the special token \( \tstar \).
+Its corresponding conversion rule is a function that returns a dummy
+\( \ires \) component \( \code{Dummy} \) with the String value of the
+compile rule name. For example, the compile rules in the previous example are
+acutally defined as follows:
+\begin{lstlisting}[style=myScalastyle]
+// statements
+val Stmt = ... | starT ^^ { case x => Dummy("Stmt") }
+// expressions
+val Expr = ... | starT ^^ { case x => Dummy("Expr") }
+\end{lstlisting}
+Then, the rule assistant evaluates the \textsc{FaultLocalize} algorithm
+with the failed step to find the set of most specific suggestions.
+\begin{algorithm}
+  \caption{Fault Localization}
+  \begin{algorithmic}[1]
+    \Function{FaultLocalize}{$T,n$}\Comment{$T$ - failed step, $n$ - size}
+    \State $S = \varnothing$
+    \For{$i = 0$ to $n - 1$}
+    \For{$j = i$ to $n - 1$}
+    \State $T'$ = a copy of $T$
+    \State Substitue $T'[i..j]$ into $\tstar$
+    \If{Parse($T'$) containing $\code{Dummy(}x \code{)}$}
+    \State Insert $(x, i, j)$ into $S$
+    \EndIf
+    \EndFor
+    \EndFor
+    \While{$s = (x, i, j) \in S$}
+    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
+    \State Remove $s \in S$
+    \EndIf
+    \EndWhile
+    \State \Return $S$
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
 
-\subsubsection{Statistics Monitor}
-
-TODO
-
-\subsubsection{Fault localizer}
-
-TODO
-}
+For example, assume that the expression compile rule for lists is removed.
+Then, the step 2-e-i of the ToPrimitive algorithm becomes a failed step.
+The fault localization algorithm first find one suggestion for statements
+and four suggestions for expressions as follows:
+\[
+  \begin{array}{c}
+    (\code{"Stmt"}, 0, 14), \;
+    (\code{"Expr"}, 3, 13), \;
+    (\code{"Expr"}, 4, 13), \;\\
+    (\code{"Expr"}, 6, 12), \;
+    (\code{"Expr"}, 10, 12)
+  \end{array}
+\]
+However, first four suggestions are removed because the last one is the most
+specific sub-sequence. Finally, the rule assistant suggests to define
+another expression compile rule for the token list \hint{}.

### 2019-08-16 icse/related.tex
Revised intro & overview
Updated images
Written related work for parsers

@@
-\section{Related Work}
+\section{Related Work}\label{sec:related}
 
-Our technique is closely related by these fields: Parser generation, Automatic model generation, and Formal semantics of JavaScript.
-\subsection{Parser Generation}
-\begin{itemize}
-  \item Packrat parsing:: simple, powerful, lazy, linear time, functional pearl (ICFP'02)~\cite{packrat}
-    % left recursion 잘 안됨 / memoization으로 memory가 엄청 커짐
-    % GLL - follow가 아닌 prediction으로 사용함 / 이 방법을 적용하면 중간중간 발생하는 nondeterministic한 경우를 모두 keeping해야됨.
-    % context-sensitive token이기에 미리 parsing을 한 token이 존재하지 않기 때문에 그 다음 token이 뭔지 알 수 없어서 prediction도 하지 못함
-\end{itemize}
+Our technique is closely related by these fields: parser generation, automatic model generation, and formal semantics of JavaScript.
 
-\subsection{Automatic Model Generation}
+From Packrat parsing~\cite{packrat} with parsing expression grammars (PEG (PEG))~\cite{peg},
+the recursive-descent parsers with backtracking supports linear-time parsing.
+However, it suffers from the fundamental problem of ordered choices;
+\( ab \) is silently unmatched in \( a \mid ab \) quirk.
+The Generalized LL (GLL) parsing~\cite{gll} is basically recursive-descent with backtracking
+but it could support general context-free grammars (CFG) even including ambiguous grammars.
+However, it takes \( O(n^3) \) parsing time when the input size is \( n \) in worst cases.
+While it could be reduced into almost linear time on most real grammars,
+it should keep all intermediate possible parsing results during parsing mechanisms.
+Unlike GLL parsing, our lookahead parsing is not applicable into general context-free grammar.
+However, we experimentally show that JavaScript parsers could be generated via lookahead parsers.
+Lookahead parsers take \( O(kn) \) where \( n \) is the length of inputs and \( k \)
+is the number of tokens. In JavaScript parser, it has only constant number of tokens
+thus the generated JavaScript parsers with lookahead parsers take linear time.
+
 There is similar problems in many fields. Not only language semantics, many specification is not constructed formally, so many researches are trying to
@@
 % \end{itemize}
-
-\subsection{Formal Semantics of JavaScript}
 

### 2019-08-18 icse/intro.tex
Till Sec. 1

--- 2019-08-15 icse/intro.tex
@@
 \section{Introduction}
+JavaScript is one of the widely used programming languages not only for client-side
+but also for server-side programming~\cite{nodejs, meanjs}
+and even for small embedded systems~\cite{espruino, tessel2}.
+It is the top-ranked language used in active GitHub
+repositories\footnote{https://githut.info/}, and \#7 in the TIOBE
+Programming Community index\footnote{https://www.tiobe.com/tiobe-index/}.
+According to W3Techs\footnote{https://w3techs.com/technologies/details/cp-javascript/all/all},
+95.2\% of websites use JavaScript as their client-side programming language.
 
-JavaScript is one of widely used programming languages not only for client-side
-but also for server-side programming~\cite{nodejs, meanjs}
-and even small embedded systems~\cite{espruino, tessel2}.
-According to W3Techs\footnote{https://w3techs.com/technologies/details/cp-javascript/all/all},
-95.2\% of websites use JavaScript as the client-side programming language.
-Moreover, JavaScript is the top-ranked language used in active GitHub repositories
-\footnote{https://githut.info/}.
-Despite its popularity, JavaScript developers often suffer from its intricate semantics
-and it may causes security vulnerabilities. For example, the following JavaScript
-code seems to always return \( \code{false} \):
+Despite its popularity, JavaScript developers often suffer from its intricate semantics,
+which may cause security vulnerabilities.  For example, calling the following JavaScript
+function seems to always return \( \code{false} \):
 \begin{lstlisting}[style=myJSstyle]
@@
 \end{lstlisting}
-Unfortunately, it returns \( \code{true} \) when the argument is an empty array
-\( \code{[]} \). To correctly understand such situations, the understanding of
-formal semantics of JavaScript is necessary.
+Unfortunately, it returns \( \code{true} \) when its argument is an empty array
+\( \code{[]} \).  To correctly understand and reason about such complex
+behaviors, the formal semantics of JavaScript is necessary.
 
@@
   \includegraphics[width=0.48\textwidth]{img/existing.png}
-  \caption{Existing approaches of semantics extractions for ECMAScript}
+\vspace*{-2em}
+  \caption{Existing approaches: Manual extraction of IR-based semantics for ECMAScript}
   \label{fig:existing}
+\vspace*{-1em}
 \end{figure}
 
-There have been several researches~\cite{lambdajs, kjs, javert} to define formal semantics of JavaScript
-for formal verification or program analysis. As illustrated in Figure~\ref{fig:existing},
-they define their own Intermediate Representations (IR) to represent JavaScript
-program semantics. They develop a parser for JavaScript programs and
-an AST-IR translator to convert JavaScript AST into their own IR.
-This approach helps us focus on IR to construct program analysis and formal verifications.
-It reduces the effort to handle the diverse and enormous features of JavaScript languages.
-We define such methodology that mechanizes to translate given AST into a treatable IR
-as \textit{IR-based semantics extractions}.
+Researchers have defined various JavaScript formal
+semantics~\cite{aplas08,lambdajs,kjs,javert} and developed several static
+analyzers on top of them~\cite{jsai,tajs,wala,safe}.  As illustrated
+in Figure~\ref{fig:existing}, they defined their own Intermediate
+Representations (IRs) to represent JavaScript program semantics.  They
+built parsers to construct Abstract Syntax Trees (ASTs) from
+programs and AST-IR translators to convert ASTs
+to their own IRs.  This approach helps researchers focus on IRs
+without worrying about diverse and enormous features of JavaScript in
+developing new techniques for program analysis and formal verification.
+We dub such a methodology that manipulates language semantics by first
+translating given programs to IRs that are suitable for analysis and
+verification \textit{IR-based semantics extraction}.
 
-However, existing IR-based semantics extractions of JavaScript are not easy to
-handle recent JavaScript programs because they manually extract semantics.
-The JavaScript syntax and semantics are described in ECMAScript specifications.
-ECMAScript is a standardized language of JavaScript and written in structured natural languages.
-However, the problem is the amount of JavaScript syntax and semantics are huge.
-The most recent version of ECMAScript 2019 consists of 798 pages.
-Thus, it is excessively labor-intensive to handle full semantics and also error-prone.
+However, existing approaches to JavaScript IR-based semantics
+extraction have difficulties in manipulating recent JavaScript
+programs, because they all extract the semantics \textit{manually}.
+The JavaScript syntax and semantics are described in the ECMAScript
+specification, written in English in a clearly structured and
+organized manner.  Unfortunately, manually implementing parsers and
+translators for JavaScript from the specification is tedious,
+labor-intensive, and error-prone especially because the language is
+huge.  The most recent specification, ECMAScript 2019, has 798 pages.
 
-Moreover, it is not a suitable approach to cope with the updates of ECMAScript specifications.
-Most of formal semantics of ECMAScript supports only ECMAScript 5.1 that was
-released in December 2009. Until 2014, it was not a big deal because ECMAScript
-specifications are rarely updated. However, in late 2014, The Ecma Technical
-Committee 39 (TC39) decided to release ECMAScript on a yearly cadence. From the
-ECMAScript 6, officially ECMAScript 2015, they updated specifications every years
-in June. Now, no researches correctly deal with recent ECMAScript features;
-lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \)),
-classes, \( \code{for-of} \) operators, \( \code{async} \) functions, or generators.
+Moreover, manual extraction does not scale for frequent updates of the
+specification.  While most existing formal semantics and analyzers of
+JavaScript support only ECMAScript 5.1 released in December 2009,
+from ECMAScript 6, officially dubbed ECMAScript 2015, the 
+ECMAScript specification is updated every year.  Focusing on
+ECMAScript 5.1 was reasonable until 2014, because the
+specification was rarely updated.  However, in late 2014, The Ecma
+Technical Committee 39 (TC39)~\cite{tc39} decided to release the
+specification annually.  Currently, no formal semantics
+nor analyzers for JavaScript correctly deal with recent ECMAScript
+features such as lexical binding via \( \code{let} \), the spread
+\( \code{...} \) operator, classes, the \( \code{for-of} \) operator,
+the \( \code{async} \) functions, and generators.
 
-In this paper, we propose JavaScript Syntax and Semantics Extraction Toolchain (JSSET)
-based on ECMAScript specifications. The tool automatically extracts JavaScript
-syntax and semantics from ECMAScript specifications. It generates JavaScript parser
-from the syntax provided by ECMAScript specifications. It also extracts formal
-JavaScript semantics in semi-automatic ways. It is semi-automatic because
-it depends on manually defined \textit{conversion rules}. Each conversion rule describes how abstract
-algorithms in specifications are converted into functions of our core language \( \ires \).
-However, to save the labor of defining such rules, we also propose a \textit{rule generation assistant}.
-It suggests new conversion rules based on statistical analysis of not yet convertible algorithms.
-The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
-ECMAScript specifications as well.
+In this paper, we propose JavaScript IR-based Semantics Extraction
+Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
+syntax and semantics from the ECMAScript specification.  It
+automatically generates a JavaScript parser from the syntax defined in
+the ECMAScript specification.  It also automatically extracts the
+formal semantics of JavaScript with given \textit{compile rules}.
+Each compile rule describes how abstract algorithms in the
+specification written in a natural language are converted into
+functions of our intermediate representation \( \ires \).  In
+addition, to save the labor of defining such compile rules, we also
+present a \textit{rule generation assistant}, which suggests new
+compile rules based on statistical analysis of not yet convertible
+algorithms.  The assistant helps us deal with changed or newly
+introduced algorithms defined in new versions of the ECMAScript
+specification as well.
 
-Our main contribution is our tool JSSET that mechanizes extraction of JavaScript syntax and semantics
-from ECMAScript specifications:
-\begin{itemize}
-  \item JSSET enables to extract the syntax and semantics of ECMAScript 2020,
-    which is the next released version of ECMAScript in June 2020.
-    Moreover, we successfully applied our tool into the next proposed version,
-    ECMAScript 2020. The official conformance test suite, test262, provides
-    \inred{XXXXX} tests for ECMAScript 2020 and we passed \inred{XXXXX} tests
-    among them.
-  \item JSSET is also applicable in-process proposed language features in a modular way.
-    ECMAScript specifications are open-source based documentations. Thus, anyone
-    could propose some new language features. Then, the committee carefully inspects
-    such proposals and adds them into specifications. Each in-process proposed language
-    feature has its own specification and tests. Thus, we apply JSSET into the specification
-    and evaluate the corresponding tests. Among \inred{XX} proposals, we successfully
-    pass all the tests in \inred{XX} proposals and partially pass the tests in \inred{XX}
-    proposals.
-  \item Moreover, all extraction mechanisms in JSSET is automatic thus we could use this tool
-    to find possible specification errors. We found \inred{X} possible specification errors
-    in ECMAScript 2020 and reported them into TC39, which is the Ecma Technical Committee.
-    We confirm that all of them are real specification errors.
+The main contribution of this paper is \( \tool \):
+\begin{itemize}[leftmargin=0.5cm]
+\item We successfully applied \( \tool \) to ECMAScript 2020, the next
+ECMAScript version scheduled to be released in June 2020.  The
+automatically extracted semantics passed the official conformance test
+suite, test262~\cite{test262}; out of \inred{XXXXX} tests for
+ECMAScript 2020 it passed \inred{XXXXX} tests.
+\item \( \tool \) is also applicable to new language features proposed
+for a future release to aid language development in a modular way.
+Because ECMAScript is an open standard language, various proposals are
+available with their own specification changes and tests.  We applied
+\( \tool \) to such proposals; out of \inred{XX} proposals, the tool
+passed all the tests in \inred{XX} proposals and partially passed the
+tests in \inred{XX} proposals.
+\item Moreover, since the extraction mechanism of \( \tool \) is fully
+automatic, we can use it to find possible specification errors.  We
+indeed found \inred{X} possible specification errors in ECMAScript
+2020; we reported them to TC39 and \inred{X} errors were confirmed and
+the remaining \inred{X} errors are under review.
 \end{itemize}

### 2019-08-18 icse/main.tex
Written 4.4 Rule Assistant

@@
 \usepackage{listings}
+\usepackage[noend]{algorithm,algpseudocode}
+\usepackage{enumitem}
 
@@
 \begin{abstract}
-While JavaScript is initially invented for client-side in web browsers,
-JavaScript engines are now embedded in many other types of host software.
-Despite its popularity, JavaScript semantics are complicated because of its
-dynamic nature. Thus, the formal analysis and verification of JavaScript programs
-require its formal semantics. Several researches proposed formal semantics
-of JavaScript based on ECMAScript, the official specifications of JavaScript.
-However, the existing approaches are fully manual and only target ECMAScript 5.1.
-It is a critical problem to understand recent JavaScript programs
-because ECMAScript is annually updated from 2015. Thus, already five more updates
-after ECMAScript 5.1.
+JavaScript was initially designed for client-side code in web browsers,
+but its engine is now embedded in various kinds of host software.
+Despite its popularity, since the JavaScript semantics is complex
+especially due to its dynamic nature, understanding and reasoning
+about JavaScript programs are challenging tasks.  Thus,
+researchers have proposed several attempts to define the formal semantics
+of JavaScript based on ECMAScript, the official JavaScript specification.
+However, the existing approaches are manual, labor-intensive, and
+error-prone, and they all target only the ECMAScript 5.1 version.
+This problem is critical in understanding recent JavaScript programs
+because ECMAScript has been annually released since 2015, which made
+already five updates after ECMAScript 5.1.
 
-To alleviate such problems, we propose \( \tool \), a JavaScript IR-based Semantics
-Extraction Toolchain. It automatically extracts JavaScript syntax and semantics from ECMAScript
-specifications. \( \tool \) generates JavaScript parser for the given grammar written
-in \( \bnfes \), an extended BNF used in ECMAScript specifications.
-Our tool also converts each abstract algorithm written in structured natural
-languages into functions written in \( \ires \), an Intermediate Representation
-for ECMAScript specifications. The compilation from algorithms to \( \ires \) functions
-is defined with \textit{compile rules}. We apply \( \tool \) into the next proposed
-version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
+To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
+Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
+semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
+parser for a given grammar written in \( \bnfes \), an extended BNF
+used in ECMAScript specifications.  It also converts each
+abstract algorithm written in a structured natural language into
+functions written in \( \ires \), an Intermediate Representation
+for ECMAScript specifications.  The compilation from algorithms to
+\( \ires \) functions is defined with \textit{compile rules}.
+We applied \( \tool \) to the next proposed version, ECMAScript 2020,
+and the automatically extracted semantics passed all \inred{XXXXX} tests 
 in test262, the official ECMAScript conformance test suite.
-Moreover, \( \tool \) also successfully extracts semantics for \inred{XX} proposed features
-by adding only \inred{XX} minor compile rules.
+\inred{Moreover, \( \tool \) also successfully extracts
+semantics for \inred{XX} proposed features by adding only \inred{XX}
+minor compile rules.}
 \end{abstract}

### 2019-08-18 icse/overview.tex
Till Sec. 1
Till Sec. 2

--- 2019-08-15 icse/overview.tex
@@
 \section{Overview}
-
-In this section, we introduce the overall structure of JSSET and the outline of
-this paper. Figure~\ref{fig:overview} depicts the overall structure of JSSET.
-It mechanizes to extract syntax and semantics of ECMAScript using
-two main module; the \textit{parser generator} and the \textit{algorithm compiler}.
-If first extracts information via the spec extractor.
-ECMAScript specifications are provided as a readable HTML file.
-Thus, we develop the spec extractor in JavaScript to automatically
-extract their contents.
-
 \begin{figure}
@@
   \includegraphics[width=0.5\textwidth]{img/overview.png}
-  \caption{Overall structure of JavaScript Semantics Extraction Toolchain (JSSET)}
+  \caption{Overall structure of \( \tool \): Automatic extraction of
+IR-based semantics for ECMAScript}
   \label{fig:overview}
+\vspace*{-1em}
 \end{figure}
 
-ECMAScript specifications describe their lexical and syntactic grammars
-based on their own extension of Backus-Naur Form (BNF).
-We call it as \( \bnfes \), BNF for ECMAScript specifications.
-It supports additional notations for parametric productions, conditional
-right-hand sides, optional symbols, positive/negative lookaheads,
-exclusive symbols, and no line-terminator symbols. We first formally define
-\( \bnfes \) and build the spec extractor to extract grammars written in \( \bnfes \).
-Then, we carefully construct the \textit{parser generator} for them by extending
-the Scala parser combinators. Moreover, we propose \textit{lookahead parsers}
-to parse \( \bnfes \) for correct and fast parsing.
-A lookahead parser keeps track of its lookahead, which is the set of
-possible next tokens. With lookahead parsers,
-the parser generator automatically generate parsers for ECMAScript grammars.
-The generated parsers are readable and one-to-one corresponds to each
-grammar components.
-For example, Firugre~\ref{fig:array-literal-es} is ArrayLiteral production in
-ECMAScript 2019 specification and Figure~\ref{fig:array-literal-parser}
-is the generated parser of the algorithm written in Scala.
-In the first right-hand side, the optional \( Elision \) token
-is represented as \( \code{opt(Elision)} \).
-The parametric non-terminal \( ElementList \) with arguments \( Yield \)
-and \( Await \) is represented as \( \code{ElementList(Yield, Await)} \).
+In this section, we introduce the overall structure of \( \tool \)
+depicted in Figure~\ref{fig:overview} and the outline of the paper.
+Compared to the existing approaches shown in
+Figure~\ref{fig:existing}, \( \tool \) automatically generates
+{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} from the
+ECMAScript specification.  Inside \( \tool \), {\sf Spec Extractor}
+extracts the JavaScript syntax to build the parser and its semantics
+to build the translator.
+
+The motivation of automatically extracting syntax and semantics
+of JavaScript from the ECMAScript specification is twofold: 1) the
+natural language used in the specification follows well-organized
+specific patterns, and 2) the specification is available as HTML files
+using various HTML tags.  As the first step, we developed {\sf Spec Extractor}
+in JavaScript, which extracts the syntax and semantics from the
+ECMAScript specification in HTML into JSON format.
 
@@
     \includegraphics[width=\textwidth]{img/array_literal.png}
-    \caption{ArrayLiteral production in ECMAScript 2019 specification.}
+    \caption{The \textit{ArrayLiteral} production in ECMAScript 2020}
     \label{fig:array-literal-es}
   \end{subfigure}
-  \begin{subfigure}[t]{0.5\textwidth}
+  \begin{subfigure}[t]{0.46\textwidth}
     \begin{lstlisting}[style=myScalastyle]
@@
     \end{lstlisting}
-    \caption{The generated parser for ArrayLiteral production.}
+    \caption{The generated parser for the \textit{ArrayLiteral} production}
     \label{fig:array-literal-parser}
   \end{subfigure}
-  \caption{ArrayLiteral grammar production in ECMAScript 2019.}
+  \caption{The \textit{ArrayLiteral} production in the ECMAScript 2020 specification and its generated parser}
   \label{fig:array-literal}
@@
 
-The semantics in ECMAScript specifications are described as
-abstract algorithms. They are written in structured natural languages
-with ordered steps and tagged tokens. For example, Figure~\ref{fig:to-primitive-es}
-is an example abstract algorithm for \( \code{ToPrimitive} \) in
-ECMAScript 2019. The spec extractor extracts each abstract algorithm
-with HTML tags because we utilize tag information to discriminate
-different kinds of tokens. Then, the \textit{algorithm compiler} converts
-given abstract algorithms into funcitons of our core language \( \ires \).
-The compilation is dependent on manually defined conversion rules
-that consists of two parts; parsing rules and mapping from each rule into \( \ires \)
-component. We carefully define \( \ires \) to directly match instructions with
-the corresponding algorithm steps. For example, Figure~\ref{fig:to-primitive-ires}
-describes the generated \( \ires \) function for the \( \code{ToPrimitive} \)
-algorithm. Each instruction of the generated \( \ires \) function
-is easily matched with the corresponding algorithm step
-and also they have similar silhouettes.
+\smallskip
+
+\textbf{Syntax.} The ECMAScript specification provides the lexical and
+syntactic grammars in Appendix A using their own extended Backus-Naur
+Form (BNF) for ECMAScript.  We dub it \( \bnfes \) and formally define
+it in Section~\ref{sec:parser}.  Our {\sf Spec Extractor} reads the
+grammars written in \( \bnfes \) and converts them into JSON files.
+For example, Figure~\ref{fig:array-literal}(a) shows the
+\textit{ArrayLiteral} production in the ECMAScript 2020
+specification.  It takes two boolean parameters \textsf{Yield} and
+\textsf{Await} and has three alternatives.  The first alternative
+consists of three symbols: two terminal symbols \( \code{[} \) and
+\( \code{]} \) and one non-terminal symbol \textit{Elision}$_{\mbox{\footnotesize opt}}$.
+The {\small opt} subscript denotes that it is optional.  In the second
+and third alternatives, \textit{ElementList}$_{\mbox{\footnotesize\sf [?Yield, ?Await]}}$
+denotes a parametric non-terminal symbol \textit{ElementList}
+with the parameters \textsf{Yield} and \textsf{Await} of
+\textit{ArrayLiteral} as its two arguments. The prefix \textsf{\small ?}
+of a symbol denotes that the symbol is passed as an argument.
 
@@
     \includegraphics[width=\textwidth]{img/to_primitive.png}
-    \subcaption{\( \code{ToPrimitive} \) abstract algorithm in ES2019.}
+    \subcaption{The \textbf{ToPrimitive} algorithm in ECMAScript 2020}
     \label{fig:to-primitive-es}
@@
     \end{lstlisting}
-    \subcaption{The \( \ires \) funciton for \( \code{ToPrimitive} \)
-    abstract algorithm.}
+    \subcaption{The generated \( \ires \) function for the \textbf{ToPrimitive} algorithm}
     \label{fig:to-primitive-ires}
   \end{subfigure}
-  \caption{\( \code{ToPrimitive} \) abstract algorithms
-  and its generated core program.}
+  \caption{The \textbf{ToPrimitive} abstract algorithm in the ECMAScript 2020 specification and its generated \( \ires \) function}
   \label{fig:to-primitive}
@@
 
-Finally, the generated \( \ires \) functions with mannual initial settings
-are applied into the \( \ires \) interpreter. We could parse a
-given JavaScript program using the generated JavaScript parser
-to get the abstract syntax tree (AST). Then, the \( \ires \) interpreter
-evaluates the given AST and provides evaluation results.
+To generate {\sf JavaScript Parser} from a given \( \bnfes \) grammar, we
+construct \textsf{JS Parser Generator} in Scala.  It synthesizes a
+JavaScript parser according to the given \( \bnfes \), and the
+generated parser is defined with Scala parser combinators~\cite{scala-parser-combinators}.
+Moreover, in order to parse \( \bnfes \) grammars correctly and
+efficiently, we propose \textit{lookahead parsers}, which keep track
+of lookaheads, sets of possible next tokens.  With lookahead parsers,
+generated parsers become more readable and have one-to-one
+mapping to their corresponding grammar productions.
+For example, Figure~\ref{fig:array-literal}(b) shows the generated
+parser for the \textit{ArrayLiteral} production in Figure~\ref{fig:array-literal}(a).
+Each parser has the \( \code{List[Boolean] => LAParser[T]} \) type
+because  each production in \( \bnfes \) is parametric with boolean values.
+The \( \code{memo} \) is a memoization function for pairs of boolean
+parameters and resulting parsers for performance optimization.
+The lazy value \( \code{ArrayLiteral} \) corresponds to the
+\textit{ArrayLiteral} production.  In the parser, each string literal
+such as \( \code{"["} \) or \( \code{"]"} \) denotes a parser for a
+terminal symbol.  The \( \code{opt} \) helper function creates
+optional parsers.  The parametric non-terminal \textit{ElementList}
+with arguments \textsf{Yield} and \textsf{Await} is represented as a
+function call \( \code{ElementList(Yield, Await)} \).
+The \( \code{\textasciitilde} \) operator combines two parsers
+and the \( \code{\^{}\^{}} \) operator describes how to construct ASTs.
+When the left-hand side of \( \code{\^{}\^{}} \) is matched, its
+right-hand side shows a corresponding AST constructor, where each
+constructor has a number denoting the order among right-hand sides.
+For example, the \( \code{ArrayLiteral0} \) constructor corresponds to
+the first right-hand side of the \textit{ArrayLiteral} production.
 
-From now, we describe the detailed techniques of JSSET.
-Section 3 formallly defines \( \bnfes \) and how to automatically
-generate parsers from given \( \bnfes \) using lookahead parsers.
-Section 4 explains abstract algorithms with tagged tokens
-and how to compile them into \( \ires \) functions based on
-given conversion rules. Section 5 describes the implemented details
-about initial settings to evaluate JavaScript programs. Section 6
-discusses the effectiveness of JSSET with four research questions.
-Section 7 discusses related work and Section 8 concludes.
+\smallskip
+
+\textbf{Semantics.}
+The ECMAScript specification describes the language semantics as
+abstract algorithms in English.  While they are written in a natural
+language, the writing style is well-organized with ordered steps and
+tagged tokens.  Our {\sf Spec Extractor} reads each abstract algorithm
+with HTML tags and converts them into JSON files.  For example,
+Figure~\ref{fig:to-primitive}(a) presents the \textbf{ToPrimitive}
+abstract algorithm in ECMAScript 2020.  It has three steps and the
+second step consists of seven sub-steps.  In the HTML files describing
+the abstract algorithms, each parameter or local variable such as
+\textit{input} or \textit{PreferredType} has the \( \code{<var>} \)
+HTML tag and each value has the \( \code{<code>} \) tag.
+
+%because we utilize tag information to discriminate different kinds of tokens.
+To translate such abstract algorithms into representations that are
+suitable for manipulation, we define \( \ires \), a specialized
+intermediate representation for ECMAScript abstract algorithms.  Then,
+we develop \textsf{Algorithm Compiler} in Scala using Scala parser
+combinators again to convert given abstract algorithms to \( \ires \)
+functions.  It also takes \textsf{Compile Rules} as another input,
+which has two parts: parsing rules and mapping from each rule to its
+corresponding \( \ires \) component.  They are \textit{manually} specified for
+the ECMAScript specification; we explain them in detail in
+Section~\ref{sec:compiler}.  Thus, each abstract algorithm is
+converted into a function written in \( \ires \) via \textsf{Algorithm Compiler}.
+For example, Figure~\ref{fig:to-primitive}(b) presents the generated
+\( \ires \) function for the \textbf{ToPrimitive} abstract algorithm.
+The \( \code{ToPrimitive} \) function takes two parameters:
+\( \code{input} \) and \( \code{PreferredType} \).  The optional
+\( \code{PreferredType} \) parameter in the abstract algorithm has
+a special value \( \code{absent} \) in the generated \( \ires \) function.
+Thus, we convert the condition of the 2-a step,
+``If \textit{PreferredType} is not present,'' into the equality check
+with \( \code{absent} \): \( \code{if (= PreferredType absent)} \).
+In this paper, we omit assertions for presentation brevity; we believe
+that they can be handled similarly.  Some specific keywords are
+represented as string values.  For instance, ``hint Number'' and
+``hint String'' are converted into \( \code{"Number"} \) and
+\( \code{"String"} \), respectively.  In addition,
+\textsf{Algorithm Compiler} modifies prefixes of symbols from
+\( \code{@@} \) to \( \code{SYMBOL\_} \) and handles exceptions with
+their corresponding intrinsic error objects.
+
+Finally, \( \tool \) constructs {\sf AST-\( \ires \) Translator} with
+the given \( \ires \) functions and \textit{manually} specified
+{\sf Global Setting}, which have minor but necessary information to
+evaluate JavaScript programs described in the ECMAScript specification.
+For example, they include the structure of the standard built-in
+objects, name aliases for intrinsic objects, and types of abstract
+algorithms.
+
+Putting them all together, we can translate a given JavaScript program
+into \( \ires \) via generated {\sf JavaScript Parser} and
+{\sf AST-\( \ires \) Translator} by \( \tool \).
+Once \( \tool \) provides the entire infrastructure, supporting yet
+another ECMAScript version would not require much manual efforts;
+the only additional efforts may be possible changes in \textsf{Compile Rules}
+and {\sf Global Setting}.
+
+\smallskip
+
+\textbf{Outline.}
+In the remainder of this paper, we describe the detailed techniques of
+\( \tool \).  We first formally define \( \bnfes \) and how to
+automatically generate parsers from given \( \bnfes \) using lookahead
+parsers (Section~\ref{sec:parser}).  Then, we explain how to compile
+abstract algorithms with tagged tokens into \( \ires \) functions using
+compile rules, and introduce a rule generation assistant to
+easily construct compile rules (Section~\ref{sec:compiler}).  After
+describing implementation details (Section~\ref{sec:framework}),
+we evaluate the effectiveness of \( \tool \)
+(Section~\ref{sec:eval}), discuss related work
+(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclude}).

### 2019-08-18 icse/eval.tex
Temporal update for evaluation

@@
 
+We evaluate \( \tool \) based on the following four research questions:
 \begin{itemize}
-  \item RQ1) Does \( \tool \) correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
-    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
-  \item RQ2) Is endurable size of manual portion in implementation of \( \tool \)? \inred{refactoring for compile rules / get statistics of compile rules}
-    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
-  \item RQ3) Does \( \tool \) deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of compile rules}
-    각 feature name / 의미 / compile 성공률 / 결과 test
-  \item RQ4) How many specification errors are detected by \( \tool \)? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
+  \item RQ2) \textbf{Effectiveness} Is \( \tool \) effective to extract syntax and
+    semantics of existing ECMAScript specifications?
+  \item RQ1) \textbf{Correctness} Does \( \tool \) correctly extract JavaScript syntax
+    and semantics from ECMAScript 2020 speicification?
+  \item RQ3) \textbf{Adaptability} Does \( \tool \) deal with future proposed features?
+  \item RQ4) \textbf{Specification Error Detection} What specification errors
+    are detected by \( \tool \)?
 \end{itemize}
+
+\subsection{Effectiveness}
+
+\begin{figure}[t]
+  \centering
+  \begin{subfigure}{0.23\textwidth}
+    \includegraphics[width=\textwidth]{img/all-version-syntax.png}
+    \caption{The parser generator.}
+    \label{fig:syntax-all-version}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.23\textwidth}
+    \includegraphics[width=\textwidth]{img/all-version-sem.png}
+    \caption{The algorithm compiler.}
+    \label{fig:semantics-all-version}
+  \end{subfigure}
+  \caption{The result of the parser generator and the algorithm compiler for
+  ECMAScript specifications from 2016 to 2020.}
+  \label{fig:all-version}
+\end{figure}
+
+We disucss the effectiveness of \( \tool \) by checking that the parser generator
+and the algorithm compiler are able to handle existing ECMAScript specifications.
+Figure~\ref{fig:all-version} shows the result of \( \tool \) from ECMAScript 2016
+to 2020. While ECMAScript 5.1 is the first version that officially supports
+the specification in HTML. However, two oldest versions ECMAScript 5.1 and 2015 are written
+in quite different styles with recent versions including HTML tags used in abstract algorithms.
+Thus, we evaluate only five recent versions from ECMAScript 2016 to 2020.
+We first apply \( \tool \) into ECMAScript 2016 and counts how many productions in syntax
+and algorithm steps in semantics are automatically extracted. For ECMAScript 2017 to 2020,
+we consider only newly added productions and algorithm steps in ecah version.
+For syntax, the parser generator successfully generates parsers for all \inred{XXX} productions
+in ECMAScript 2016 and \inred{XXX} new productions in ECMAScript 2017 to 2020.
+For semantics, the algorithm compilear successfully compiles \inred{XXXX} of \inred{XXXX} steps
+into \( \ires \) instructions for ECMAScript 2016, and \inred{XXXX} of \inred{XXXX} newly added
+steps are compiled in ECMAScript 2017 to 2020.
+
+\subsection{Correctness}
+
+\begin{table}[] \centering
+  \begin{tabular}{lr}\toprule
+    \belowrulesepcolor{gainsboro}
+    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794} \\
+    \aboverulesepcolor{gainsboro}\midrule
+    Annexes/Internationalisation & 1,774\\ \hdashline
+    In-process features & \inred{XXXX} \\\midrule
+    Module tests & \inred{XXXX} \\\hdashline
+    Non-strict tests & \inred{XXXX} \\\hdashline
+    \belowrulesepcolor{gainsboro}
+    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Strict Script Tests} & \textbf{\inred{XXXXX}} \\
+    \aboverulesepcolor{gainsboro}\midrule
+    Not supported features & \inred{XXXX} \\\midrule
+    \belowrulesepcolor{gainsboro}
+    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}} \\
+    \aboverulesepcolor{gainsboro}\midrule
+    Passed tests & \inred{XXXX} \\\hdashline
+    Failed tests & \inred{XXXX} \\\bottomrule
+  \end{tabular}
+  \caption{The syntax testing results of ECMAScript 2020 with test262.}
+  \label{table:test262}
+\end{table}
+
+To check that \( \tool \) correctly extracts semantics, we apply our tool into ECMAScript 2020
+specification. It is the next version of ECMAScript that is actively updated in GitHub~\ref{es2020}
+to be released in the next year. Ecma Technical Committee 39 (TC39) officially provides
+the conformance test suite, test262, for ECMAScript 2020. Thus, we develop \( \ires \)
+interpreter to evaluate the \( \ires \) compiled from tests in test262.
+However, test262 also provides tests for in-process features and other extensions
+such as web browsers and internationalisation.
+Thus, we exclude such tests from test262 test suite for evaluations.
+Figure~\ref{table:test262} describes how to break down tests and the test results for parsers
+and interpreters. We fixed the version of ECMAScript 2020 and test262 in August in 2019.
+In that version, the test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
+for extensions and in-process features. Then, we focus on only strict script not non-strict
+or module codes thus we remove \inred{XXXX} tests. Finally, we have \inred{XXXX}
+
+Then, we filter out tests having not supported features explained in Section~\ref{sec:framework}.
+Table~\ref{table:}
+We first exclude tests about not-yet applied proposed features,
+
+\subsection{Adaptability}
+\subsection{Specification Error Detection}
+
+% test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
+% \inred{refactoring for compile rules / get statistics of compile rules}
+% 개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
+% \inred{proposed language features / related tests in test262 / diff of compile rules}
+% 각 feature name / 의미 / compile 성공률 / 결과 test
+% \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}

### 2019-08-18 icse/img/all-version-sem.R

@@ -1,0 +1,30 @@
+library(plotly)
+
+ECMAScript_Version <- c(2016, 2017, 2018, 2019, 2020)
+existing <- c(0, 4000, 4110, 5140, 5400)
+auto <- c(5000, 1800, 2070, 2090, 2300)
+manual <- c(200, 50, 100, 30, 20)
+data <- data.frame(ECMAScript_Version, existing, auto, manual)
+
+p <- plot_ly(
+  data,
+  x = ~ECMAScript_Version,
+  y = ~existing,
+  type = 'bar',
+  name = 'existing',
+  marker = list(color = 'black'),
+  dtick = 1
+) %>% add_trace(
+  y = ~auto,
+  name = 'auto',
+  marker = list(color = '#0070DE')
+) %>% add_trace(
+  y = ~manual,
+  name = 'manual',
+  marker = list(color = '#FE1A13')
+) %>% layout(
+  yaxis = list(title = '# of Steps'),
+  xaxis = list(title = 'ECMAScript Versions', dtick = 1),
+  barmode = 'stack'
+)
+p

### 2019-08-18 icse/img/all-version-syntax.R

@@ -1,0 +1,29 @@
+library(plotly)
+
+ECMAScript_Version <- c(2016, 2017, 2018, 2019, 2020)
+existing <- c(0, 270, 290, 300, 325)
+auto <- c(280, 30, 20, 30, 10)
+manual <- c(3, 0, 0, 0, 0)
+data <- data.frame(ECMAScript_Version, existing, auto, manual)
+
+p <- plot_ly(
+  data,
+  x = ~ECMAScript_Version,
+  y = ~existing,
+  type = 'bar',
+  name = 'existing',
+  marker = list(color = 'black')
+) %>% add_trace(
+  y = ~auto,
+  name = 'auto',
+  marker = list(color = '#0070DE')
+) %>% add_trace(
+  y = ~manual,
+  name = 'manual',
+  marker = list(color = '#FE1A13')
+) %>% layout(
+  yaxis = list(title = '# of Productions'),
+  xaxis = list(title = 'ECMAScript Versions', dtick = 1),
+  barmode = 'stack'
+)
+p

### 2019-08-19 icse/intro.tex
Reflected Jihyeok's comments

@@
 developing new techniques for program analysis and formal verification.
-We dub such a methodology that manipulates language semantics by first
+We dub such a methodology that manipulates language semantics by
 translating given programs to IRs that are suitable for analysis and
@@
 present a \textit{rule generation assistant}, which suggests new
-compile rules based on statistical analysis of not yet convertible
+compile rules based on fault localization of not yet convertible
 algorithms.  The assistant helps us deal with changed or newly
@@
 indeed found \inred{X} possible specification errors in ECMAScript
-2020; we reported them to TC39 and \inred{X} errors were confirmed and
-the remaining \inred{X} errors are under review.
+2020.  They were all confirmed by TC39 and will be fixed in the next
+release.
 \end{itemize}

### 2019-08-19 icse/eval.tex
Temporal update for evaluations

@@
 
-We disucss the effectiveness of \( \tool \) by checking that the parser generator
-and the algorithm compiler are able to handle existing ECMAScript specifications.
+We discuss the effectiveness of \( \tool \) by applying it into existing ECMAScript specifications.
+The evaluation focuses on how many productions and abstract algorithms are covered by
+our tool 1) in each version, and 2) in each difference between adjacent versions.
 Figure~\ref{fig:all-version} shows the result of \( \tool \) from ECMAScript 2016
@@
 Thus, we evaluate only five recent versions from ECMAScript 2016 to 2020.
-We first apply \( \tool \) into ECMAScript 2016 and counts how many productions in syntax
-and algorithm steps in semantics are automatically extracted. For ECMAScript 2017 to 2020,
-we consider only newly added productions and algorithm steps in ecah version.
-For syntax, the parser generator successfully generates parsers for all \inred{XXX} productions
-in ECMAScript 2016 and \inred{XXX} new productions in ECMAScript 2017 to 2020.
-For semantics, the algorithm compilear successfully compiles \inred{XXXX} of \inred{XXXX} steps
-into \( \ires \) instructions for ECMAScript 2016, and \inred{XXXX} of \inred{XXXX} newly added
-steps are compiled in ECMAScript 2017 to 2020.
+As described in Figure~\ref{fig:all-version}, \( \tool \) suceeds to generate parsers
+from all versions. For semantics, the algorithm compiler has \inred{XX\%} success rates
+in average. Moreover, \( \tool \) are also effective to update existing semantics
+because \inred{XX\%} of newly defined algorithms are automatically compiled into \( \ires \)
+functions.
 
@@
 
-\begin{table}[] \centering
+\begin{table}
+  \centering
   \begin{tabular}{lr}\toprule
@@
     Annexes/Internationalisation & 1,774\\ \hdashline
-    In-process features & \inred{XXXX} \\\midrule
+    In-process features & \inred{XXXX} \\\hdashline
     Module tests & \inred{XXXX} \\\hdashline
-    Non-strict tests & \inred{XXXX} \\\hdashline
+    Non-strict tests & \inred{XXXX} \\\midrule
     \belowrulesepcolor{gainsboro}
@@
   \end{tabular}
-  \caption{The syntax testing results of ECMAScript 2020 with test262.}
+  \caption{The results of tests in the test262 for ECMAScript 2020.}
   \label{table:test262}
@@
 
-To check that \( \tool \) correctly extracts semantics, we apply our tool into ECMAScript 2020
-specification. It is the next version of ECMAScript that is actively updated in GitHub~\ref{es2020}
-to be released in the next year. Ecma Technical Committee 39 (TC39) officially provides
-the conformance test suite, test262, for ECMAScript 2020. Thus, we develop \( \ires \)
-interpreter to evaluate the \( \ires \) compiled from tests in test262.
-However, test262 also provides tests for in-process features and other extensions
-such as web browsers and internationalisation.
-Thus, we exclude such tests from test262 test suite for evaluations.
-Figure~\ref{table:test262} describes how to break down tests and the test results for parsers
-and interpreters. We fixed the version of ECMAScript 2020 and test262 in August in 2019.
-In that version, the test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
-for extensions and in-process features. Then, we focus on only strict script not non-strict
-or module codes thus we remove \inred{XXXX} tests. Finally, we have \inred{XXXX}
-
-Then, we filter out tests having not supported features explained in Section~\ref{sec:framework}.
-Table~\ref{table:}
-We first exclude tests about not-yet applied proposed features,
+To evaluate that \( \tool \) correctly extracts semantics, we extract semantics of ECMAScript
+2020 via our tool. Above automatically extracted parts of semantics, we manually implement
+\inred{XX} \( \ires \) functions for failed to be automatically compiled abstract algorithms.
+Moreover, we fill in global setting based on ECMAScript 2020 specification as described
+in Section~\ref{sec:framework}. The ECMAScript 2020 version is actively updated in
+GitHub~\ref{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
+officially provides the conformance test suite, test262, for ECMAScript 2020.
+Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
+However, the test262 also provides tests for in-process features and other extensions
+such as web browsers and internationalisation. Thus, we exclude them from our target tests.
+Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
+semantics. We use test262 written in \inred{August 6, 2019}. In that version,
+test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
+for extensions and in-process features. Then, we remove tests for non-strict mode because
+we focus on only JavaScript codes in strict mode
+as described in Section~\ref{sec:framework}. Finally, we remove the \inred{XXXX} tests
+for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
+We test our extracted semantics for \inred{XXXXX} applicable tests and pass \inred{XXXX} tests.
+There are several reasons of test failures; \inred{...}.
 
 \subsection{Adaptability}
+
+\begin{table}
+  \centering
+  \[
+    \begin{array}{l|r|r|r|r} \hline
+      \text{features} &
+      \multicolumn{1}{c|}{\text{\#prods}} &
+      \multicolumn{1}{c|}{\text{\#steps}} &
+      \multicolumn{1}{c|}{\Delta\text{CR}} &
+      \multicolumn{1}{c}{\text{tests}}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
+      \hline
+      \text{total} & \inred{XX} & \inred{XXX} & \inred{XX} & \inred{XXX/XXX}\\\hline
+    \end{array}
+  \]
+  \caption{The result of \( \tool \) for in-process language features}
+  \label{table:in-process}
+\end{table}
+
+We also check that \( \tool \) deals with future language features for adaptability.
+ECMAScript specifications are managed as open-sources and proposals of in-process language
+features follow the TC39 process and are tracked in the separated repository~\ref{proposals}.
+Thare are five stages for proposals; Stage 0, Stage 1, active, finished or inactive proposals.
+Each proposal starts from Stage 0 and is promoted to an active proposal through Stage 1.
+Then, the committee (TC39) regularly examins the active proposal and changes the stage into
+finished if they want to apply the proposed language features, otherwise, changes it
+into inactive stage.
+
+% We also check that \( \tool \) deals with future language features based on in-process language
+% features. Each in-process language feature has its own specification, and the test262 supports
+% tests for them. We extract semantics of \inred{XX} language features via \( \tool \) and test extracted
+% semantics based on tests in test262. Table~\ref{table:in-process} describes the result and
+% \( \tool \) successfully generates parsers of total \inred{XX} productions.
+% For semantics, \( \tool \) successfully compiles \inred{XXX} algorithm steps by adding
+% \inred{XX} more compile rules. Above the semantics, \inred{XXX} tests passes among \inred{XXX}
+% tests for \inred{XX} in-process language features.
+
 \subsection{Specification Error Detection}
+
+We found four specification errors in ECMAScript 2020. All of them
 

### 2019-08-19 icse/img/all-version-sem-delta.R

@@ -1,8 +1,8 @@
 library(plotly)
 
-ECMAScript_Version <- c(2016, 2017, 2018, 2019, 2020)
-auto <- c(930, 1140, 1200, 1290, 1400)
-manual <- c(100, 102, 103, 109, 120)
+ECMAScript_Version <- c("2015-16", "2016-17", "2017-18", "2019-20")
+auto <- c(160, 100, 240, 180)
+manual <- c(10, 3, 7, 8)
 data <- data.frame(ECMAScript_Version, auto, manual)
 
 p <- plot_ly(

### 2019-08-19 icse/framework.tex
Revised intro & overview

@@
-\section{Building entire system to evaluate code}
+\section{Building entire system to extract semantics}\label{sec:framework}
 
@@
  In specification, "Well-known intrinsics are built-in objects that are explicitly referenced by the algorithms".
- Abstract algorithm uses name like "\%name\%", which are alias for builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
+ Abstract algorithm uses identifiers like "\%name\%" to point builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
  Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.
@@
 
- Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is different.
-The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Non-terminal
-\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some non-terminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
-(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
-Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer sub-component of AST.
- For Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
+ Like method-like abstract operation, many AST objects have similar interface, but they have different algorithm.
+The most frequent example is "Evaluation" algorithm of AST Values. Many non-terminal symbol have different algorithm with name "Evaluation", and
+when specification requires "the result of evaluating \textit{variable}", then it should apply "Evaluation" of non-terminal symbol which matches to \textit{variable}.
+It is assumed that \textit{variable} is a AST value. Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
+Evaluation algorithm of \textit{CallExpression} : \textit{CallExpression} \textit{Arguments}, algorithm can uses \textit{CallExpression} or \textit{Arguments} to refer sub-component of AST.
+ To support Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
 We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

### 2019-08-19 icse/overview.tex
Updated overview image

@@
   \centering
-  \includegraphics[width=0.5\textwidth]{img/overview.png}
+  \includegraphics[width=0.48\textwidth]{img/overview.png}
   \caption{Overall structure of \( \tool \): Automatic extraction of
@@
 right-hand side shows a corresponding AST constructor, where each
-constructor has a number denoting the order among right-hand sides.
+constructor has a number denoting the order among alternatives.
 For example, the \( \code{ArrayLiteral0} \) constructor corresponds to
-the first right-hand side of the \textit{ArrayLiteral} production.
+the first alternative of the \textit{ArrayLiteral} production.
 
@@
 functions.  It also takes \textsf{Compile Rules} as another input,
-which has two parts: parsing rules and mapping from each rule to its
+which has two parts: parsing rules and conversion rules from each rule to its
 corresponding \( \ires \) component.  They are \textit{manually} specified for

### 2019-08-19 icse/eval.tex
Evaluation except last quetion

@@
     Annexes/Internationalisation & 1,774\\ \hdashline
-    In-process features & \inred{XXXX} \\\hdashline
+    In-progress features & \inred{XXXX} \\\hdashline
     Module tests & \inred{XXXX} \\\hdashline
@@
 2020 via our tool. Above automatically extracted parts of semantics, we manually implement
-\inred{XX} \( \ires \) functions for failed to be automatically compiled abstract algorithms.
+\inred{XX} \( \ires \) functions for abstract algorithms failed to be automatically compiled.
 Moreover, we fill in global setting based on ECMAScript 2020 specification as described
 in Section~\ref{sec:framework}. The ECMAScript 2020 version is actively updated in
-GitHub~\ref{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
+GitHub~\cite{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
 officially provides the conformance test suite, test262, for ECMAScript 2020.
 Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
-However, the test262 also provides tests for in-process features and other extensions
+However, the test262 also provides tests for in-progress features and other extensions
 such as web browsers and internationalisation. Thus, we exclude them from our target tests.
@@
 test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
-for extensions and in-process features. Then, we remove tests for non-strict mode because
+for extensions and in-progres features. Then, we remove tests for non-strict mode because
 we focus on only JavaScript codes in strict mode
@@
 
-\begin{table}
-  \centering
-  \[
-    \begin{array}{l|r|r|r|r} \hline
-      \text{features} &
-      \multicolumn{1}{c|}{\text{\#prods}} &
-      \multicolumn{1}{c|}{\text{\#steps}} &
-      \multicolumn{1}{c|}{\Delta\text{CR}} &
-      \multicolumn{1}{c}{\text{tests}}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
-      \hline
-      \text{total} & \inred{XX} & \inred{XXX} & \inred{XX} & \inred{XXX/XXX}\\\hline
-    \end{array}
-  \]
-  \caption{The result of \( \tool \) for in-process language features}
-  \label{table:in-process}
-\end{table}
+We also check that \( \tool \) deals with future language features for adaptability.
+ECMAScript specifications are managed as open-sources and proposals of in-progress language
+features follow the TC39 process and are tracked in the separated repository~\cite{proposals}.
+Thare are five stages for proposals; Stage from 0 to 3, and finished or inactive proposals.
+The committee (TC39) regularly examins the proposals in Stage 3 and changes the stage into
+finished if its members decide to apply it into official specifications. Otherwise, the committee
+changes the stage of proposal into inactive. Our tool \( \tool \) is also applicable into
+not yet finished proposals and we advance \inred{a case study for a proposal} in Stage 3.
+We decide to study on proposals in Stage 3 because test262 supports tests for several
+proposals in Stage 3.
 
-We also check that \( \tool \) deals with future language features for adaptability.
-ECMAScript specifications are managed as open-sources and proposals of in-process language
-features follow the TC39 process and are tracked in the separated repository~\ref{proposals}.
-Thare are five stages for proposals; Stage 0, Stage 1, active, finished or inactive proposals.
-Each proposal starts from Stage 0 and is promoted to an active proposal through Stage 1.
-Then, the committee (TC39) regularly examins the active proposal and changes the stage into
-finished if they want to apply the proposed language features, otherwise, changes it
-into inactive stage.
-
-% We also check that \( \tool \) deals with future language features based on in-process language
-% features. Each in-process language feature has its own specification, and the test262 supports
-% tests for them. We extract semantics of \inred{XX} language features via \( \tool \) and test extracted
-% semantics based on tests in test262. Table~\ref{table:in-process} describes the result and
-% \( \tool \) successfully generates parsers of total \inred{XX} productions.
-% For semantics, \( \tool \) successfully compiles \inred{XXX} algorithm steps by adding
-% \inred{XX} more compile rules. Above the semantics, \inred{XXX} tests passes among \inred{XXX}
-% tests for \inred{XX} in-process language features.
+\inred{...}
 
@@
 
-We found four specification errors in ECMAScript 2020. All of them
+We found four specification errors in ECMAScript 2020 via \( \tool \).
+They were all confirmed by TC39 and will be fixed in the next release.
+
+\paragraph{Ambiguous \textbf{VarScopedDeclarations} for \textit{IterationStatement}}
 

### 2019-08-19 icse/eval.tex
Updated evaluation

@@
 We found four specification errors in ECMAScript 2020 via \( \tool \).
-They were all confirmed by TC39 and will be fixed in the next release.
+We fixed them and sent pull requests into the official GitHub repository of
+ECMAScript specification~\cite{es2020}. They were all confirmed by TC39
+and will be fixed in the next release.
 
-\paragraph{Ambiguous \textbf{VarScopedDeclarations} for \textit{IterationStatement}}
+First, we found that \textbf{VarScopedDeclarations} syntax-directed algorithms of
+specific cases of \textit{IterationStatement} are ambigious.
+The \textbf{VarScopedDeclarations} algorithm is used to initially define
+the variable declarations before entering speicific scopes. However, the iteration syntax
+\( \code{for await (} \; \textit{LeftHandSideExpression} \; \code{of} \;
+\textit{AssignmentExpression} \; \code{)} \; \textit{Statement} \)
+has two different \textbf{VarScopedDeclarations} algorithms.
+In \( \tool \), the spec extractor detects such duplications.
 
-% test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
-% \inred{refactoring for compile rules / get statistics of compile rules}
-% 개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
-% \inred{proposed language features / related tests in test262 / diff of compile rules}
-% 각 feature name / 의미 / compile 성공률 / 결과 test
-% \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
+For the \textbf{ExpectedArgumentCount} syntax-directed algorithm, we found that
+there are missing cases for some syntax. This algorithm counts the number of
+expected arugments of a specific parameters. However, it does not cover all
+the cases. For example, if there exists only one formal parameter,
+the ECMAScript 2020 specification does not provide any semantics.
+We detect this error during evaluations of test262 tests under
+the extracted semantics via \( \tool \). It throws an error that there
+is no \textbf{ExpectedArgumentCount} algorithm for specific tests.
+
+Moreover, we found an error in \textsf{Ecmarkup}, a toolchain used to specify ECMAScript
+and render the raw specification HTML files.
+At the first time, we though that we found a missing case for the \textbf{IsFunctionDefinition}
+algorithm of unnamed function expressions. However, in the raw specification HTML file,
+there are no missing cases. We investigate why it happens and realize that \textsf{Ecmarkup}
+itself has a bug to silently remove the {\small opt} subscript in
+\( \code{collapsed} \) syntax mode. Thus, unnamed functions are not described
+in the rendered HTML file.
+
+\inred{- completion records??}
+% The last issue is about the \textit{completion record type}, which is one of controversial features
+% in ECMAScript specifications. They are used to describe the propagation of control
+% flows and values in abstract algorithms. They are implicitly constructed
+% in steps that return values that are not completion records in runtime semantics.
+% Moreover, 
+% It confuses the type of return values

### 2019-08-19 icse/img/all-version-sem-delta.R
Updated images in evaluation

@@ -1,24 +1,25 @@
 library(plotly)
 
 ECMAScript_Version <- c("2015-16", "2016-17", "2017-18", "2019-20")
-auto <- c(160, 100, 240, 180)
-manual <- c(10, 3, 7, 8)
+auto <- c(256, 123, 121, 155)
+manual <- c(217, 139, 108, 280)
 data <- data.frame(ECMAScript_Version, auto, manual)
 
 p <- plot_ly(
   data,
-  x = ~ECMAScript_Version,
-  y = ~auto,
+  y = ~ECMAScript_Version,
+  x = ~auto,
   type = 'bar',
   name = 'auto',
-  marker = list(color = '#0070DE')
+  marker = list(color = '#0070DE'),
+  orientation = 'h'
 ) %>% add_trace(
-  y = ~manual,
+  x = ~manual,
   name = 'manual',
   marker = list(color = '#FE1A13')
 ) %>% layout(
-  yaxis = list(title = '# of Steps'),
-  xaxis = list(title = 'ECMAScript Versions', dtick = 1),
+  xaxis = list(title = '# of Steps'),
+  yaxis = list(title = '', showticklabels = FALSE),
   barmode = 'stack'
 )
 p

### 2019-08-19 icse/img/all-version-sem.R

@@ -1,24 +1,25 @@
 library(plotly)
 
 ECMAScript_Version <- c(2016, 2017, 2018, 2019, 2020)
-auto <- c(930, 1140, 1200, 1290, 1400)
-manual <- c(100, 102, 103, 109, 120)
+auto <- c(938, 1055, 1109, 1127, 1145)
+manual <- c(475, 436, 446, 474, 456)
 data <- data.frame(ECMAScript_Version, auto, manual)
 
 p <- plot_ly(
   data,
-  x = ~ECMAScript_Version,
-  y = ~auto,
+  y = ~ECMAScript_Version,
+  x = ~auto,
   type = 'bar',
   name = 'auto',
-  marker = list(color = '#0070DE')
+  marker = list(color = '#0070DE'),
+  orientation = 'h'
 ) %>% add_trace(
-  y = ~manual,
+  x = ~manual,
   name = 'manual',
   marker = list(color = '#FE1A13')
 ) %>% layout(
-  yaxis = list(title = '# of Steps'),
-  xaxis = list(title = 'ECMAScript Versions', dtick = 1),
+  xaxis = list(title = '# of Steps', autorange = "reversed"),
+  yaxis = list(title = 'ECMAScript Versions', side = "right", dtick = 1),
   barmode = 'stack'
 )
 p

### 2019-08-19 icse/conclusion.tex
Written conclusion

\section{Conclusion}\label{sec:conclude}

We indiciate the problem that existing JavaScript semantics are not suitable for
annually updated cadence of ECMAScript specifications. We propose a tool \( \tool \),
JavaScript IR-based Semantics Extraction Toolchain to mechanize extracting syntax
and semantics from ECMAScript specifications. The most important modules are
the parser generator and the algorithm compiler. The parser generator generates
parsers from given \( \bnfes \) in lookahead parsers we proposed. the algorithm
compiler compiles given abstract algorithm written in structured natural language
into \( \ires \) functions. It is dependent on given compile rules and we provide
general compile rules for existing ECMAScript specifications. Moroever, we also
develop the rule assistant to diagnose root causes of not yet convertible algorithms.
It aids to modify compile rules for specification updates. We evaluate \( \tool \)
based on the next version of ECMAScript specification (2020) with the official conformance test
suite (test262). The extracted semantics passed all \inred{XXXXX} tests in test262
and we show that the tool is alo applicable into in-progress language features
by a case study. Moreover, we found \inred{four} real specification errors via \( \tool \)
and TC39 confirms all of them.

### 2019-08-19 icse/parser.tex
Revised intro & overview
Fixed small errors
Updated images
Fixed small typo
Till Sec. 3

--- 2019-08-08 icse/parser.tex
@@
-\section{Parser Generator}
+\section{Parser Generator}\label{sec:parser}
+In this section, we explain how to automatically generate JavaScript
+parsers from a given ECMAScript specification.
 
-In this section, we introduce a way to automatically generate JavaScript parsers
-from given ECMAScript specifications. First, we explain \( \bnfes \), an extension
-of Backus-Naur form(BNF) used in ECMAScript to describe lexical and
-syntactic grammars of JavaScript. We propose a recursive descent parser generator
-that both supports backtracking and lookahead tokens to correctly support
-\( \bnfes \) notations. We implement our idea by extending Scala parser combinators.
-The implementation also supports the automatic semicolon insertion,
-one of the most distinctive parsing features in ECMAScript.
-
-\subsection{\( \bnfes \): Grammars for ECMAScripts}
-
-Backus-Naur form(BNF) is proposed to represent context-free grammars(CFGs).
-ECMAScript provides their lexical and syntactic grammars using \( \bnfes \),
-an extension of BNF for ECMAScript.
-It consists of a number of \textit{productions} with the following forms:
+\subsection{\( \bnfes \): Grammar for ECMAScript}
+The ECMAScript specification describes the JavaScript syntax using an
+extension of the BNF notation.  We formally define the notation and
+dub it \( \bnfes \).  It consists of a number of \textit{productions}
+with the following form:
 \[
@@
 \]
-The left-hand side represents a parametric non-terminal \( \NT{A} \) with
-multiple boolean parameters \( \param_1, \cdots, \param_n \).
-If a non-terminal takes no parameters, parenthesis are omitted for the brevity.
-A production has multiple right-hand sides with optional conditions.
+The left-hand side of $::=$ represents a parametric non-terminal \( \NT{A} \)
+with multiple boolean parameters \( \param_1, \cdots, \param_k \).
+If a non-terminal takes no parameter, parentheses are omitted for brevity.
+A production has multiple alternatives separated by $\mid$ with optional conditions.
 A condition \( \cond \) is either a boolean parameter \( \param \)
-or its negation \( ! \param \).
+or its negation \( ! \param \).  An alternative \( \rhs \) is a sequence
+of symbols, where a symbol \( \symb \) is one of the following:
+\begin{itemize}[leftmargin=0.5cm]
+\item \( \epsilon \): the empty sequence, which passes without any conditions
+\item \( \T{a} \): a terminal, which is any token
+\item \( \NT{A}(\argument_1, \cdots, \argument_k) \): a non-terminal,
+which takes multiple arguments where each argument \( \argument_i \) is
+either a boolean value \( \kwt \) or \( \kwf \), or a parameter \( \param_i \)
+\item \( \symb? \): option, which is the same with \( \symb \mid \epsilon \)
+\item \( +\symb \) (\( -\symb \)) : positive (negative) lookahead,
+which checks whether \( \symb \) succeeds (fails) and
+\textit{never consumes any input}
+\item \( \symb \butnot \symb' \): exclusion, which
+first checks whether \( \symb \) succeeds
+and then checks whether the parsing result does not correspond to \( \symb' \)
+\item \( \nolt \): no line-terminator, which is a special symbol
+that restricts the white spaces between two different symbols
+\end{itemize}
 For example, consider the following production:
@@
 
-Each right-hand side \( \rhs \) is a sequence of the following symbols:
-\begin{itemize}
-  \item \( \boxed{\epsilon} \): empty sequence
-  \item \( \boxed{\T{a}} \): terminal symbols
-  \item \( \boxed{\NT{A}(\argument_1, \cdots, \argument_k)} \): non-terminal symbols
-  \item \( \boxed{\symb?} \): optional symbols
-  \item \( \boxed{\pm \symb} \): positive/negative lookahead symbols
-  \item \( \boxed{\symb \butnot \symb'} \): exclusive symbols
-  \item \( \boxed{\nolt} \): no line-terminator symbols
+\subsection{Lookahead Parsers}
+To support \( \bnfes \) correctly, we propose a recursive descent
+parser generator that handles both backtracking and lookahead tokens.
+
+\smallskip
+
+\textbf{Approach.} 
+Our goal is to automatically generate a JavaScript parser from a given
+ECMAScript grammar written in \( \bnfes \).  Among various parser
+generators, we chose Scala parser combinators defined in
+\textit{Parsing Expression Grammar (PEG)}~\cite{peg}.
+PEG is a top-down (LL-style) recursive descent parser with
+\textit{backtracking}.  It visits each alternative of a production in
+order and backtracks to its previous production when parsing fails.
+We chose Scala parser combinators because of the following reasons:
+
+\begin{itemize}[leftmargin=0.5cm]
+\item \textbf{Context-sensitive tokens:} ECMAScript tokens are
+context-sensitive because of JavaScript regular expressions and
+template strings.  For example, \( \code{/x/g} \) could be a single
+regular expression token or four tokens that represent division by
+variables \( \code{x} \) and \( \code{g} \) depending on enclosing
+contexts.  Thus, lexers should be evaluated during parsing not before
+parsing.  Since Scala parser combinators also treat lexers as parsers,
+we can use appropriate lexers depending on parsing contexts.
+\item \textbf{\( \bnfes \) symbols:} PEG can represent \( \bnfes \)
+symbols intuitively as we explain in Section~\ref{sec:convert-bnfes}.
+\item \textbf{Multiple starting non-terminals:} Since ECMAScript 6,
+both scripts and modules serve as starting points of parsers.  Scala
+parser combinators allow to use any non-terminals as parsers.
+\item \textbf{Parsing at run-time:} JavaScript supports the \( \code{eval} \)
+function that parses a given JavaScript string value to code and
+evaluates it.  Moreover, syntax-directed abstract algorithms use special
+phrases like ``the \( N \) that is \textit{covered by} \( P \),'' which
+means that a generalized parser parses the syntax tree \( P \) because
+finding a specific parser to correctly parse it requires its
+evaluation context.  When a JavaScript interpreter encounters such a
+phrase, it decides a specific parser to \( N \) and parses the given
+syntax tree \( P \) with the non-terminal \( N \) again at run time.
 \end{itemize}
 
-The empty sequence \( \epsilon \) passes without any conditions
-and a terminal symbol is any token.
-A non-terminal symbol \( \NT{A}(\argument_1, \cdots, \argument_k) \)
-takes multiple arguments and each of them \( \argument_i \) is
-a boolean value \( \kwt \), \( \kwf \) or a parameter \( \param_i \).
-An optional symbol \( \symb? \) is same with \( \symb \mid \epsilon \).
-A positive(negative) lookahead symbol \( +\symb \)(\( -\symb \))
-checks that the symbol \( \symb \) succeeds(fails) and
-\textit{never consumes any input}.
-The exclusive symbols \( \symb \butnot \symb' \)
-first checks that the symbol \( \symb \) succeeds
-and then checks that the parsing result does not correspond to \( \symb' \).
-The no-line terminal symbol \( \nolt \) is a special symbol
-that restricts the white spaces between two other symbols.
+\smallskip
 
-\begin{figure}
-  \centering
-  \[
-    \begin{array}{l}
-      \NT{ArrayLiteral}(Yield, Await) ::=\\
-      \qquad \T{[} \; Elision? \; \T{]}\\
-      \qquad \T{[} \; ElementList(Yield, Await) \; \T{]}\\
-      \qquad \T{[} \; ElementList(Yield, Await) \; \T{,} Elision? \; \T{]}\\
-    \end{array}
-  \]
-  \caption{ArrayLiteral production in \( \bnfes \).}
-  \label{fig:array-literal-bnfes}
-\end{figure}
-
-For example,
-
-\subsection{Lookahead Parsers}
-
-Our goal is to automatically generate JavaScript parsers from ECMAScript
-grammars written in \( \bnfes \). There are several options for parser generators;
-ANTLR, Lex/Yacc, Bison, and PEG. Among them, we decided to use
-Scala parser combinators defined under \textit{parsing expression grammars(PEG)}.
-PEG follows top-down (LL-style) parsing approaches and there are two different
-categories; predictive parser and recursive descent with backtracking.
-Predictive parsers are widely used in general and LL(k) parsers are typical
-examples of predictive top-down parsers.
-They choose a right-hand sides based on predicting the next tokens in deterministic
-manners. In the other hand, PEG is a recursive descent parser with
-\textit{backtracking}. It visits each right-hand side in order and backtrack
-into the previous rules when parsing fails.
-Thus, it is possible to use each production itself as a parser
-in PEG. Moreover, There are several reasons why we extend Scala parser combinator
-to deal with ECMAScript lexers and grammars written in \( \bnfes \):
-
-\begin{itemize}
-  \item \textbf{Context-Sensitive Tokens} ECMAScript tokens are context-sensitive
-    because of the JavaScript regular expressions and template strings.
-    For example, the code \( \code{/x/g} \) might be a single regular expression token
-    or four tokens that represent division by variables \( \code{x} \) and \( \code{g} \)
-    depending on enclosing contexts. Thus, lexers should be evaluated during the parser
-    not before the parser. Scala parser combinators also treat lexers as parsers thus
-    it is possible to use appropriate lexers depending on the parsing contexts.
-  \item \textbf{\( \bnfes \) Symbols} PEG is suitable grammars to represent
-    \( \bnfes \) symbols. We will explain detailed conversion from
-    \( \bnfes \) grammars into Scala parser combinators in section~\ref{sec:convert-bnfes}.
-  \item \textbf{Multiple Starting Non-terminals} After ECMAScript 6, grammars support
-    both scripts and modules as starting point of parsers. In Scala parser combinators,
-    it is possible to parse input string using any non-terminals as parsers.
-  \item \textbf{Parsing in Run-time} JavaScript supports \( \code{eval} \)
-    function that parses given JavaScript String values into codes and evaluates them.
-    Moreover, there is special phrases ``the \( N \) that is \textit{covered by}
-    \( P \)'' in syntax-directed abstract algorithms.
-    It means that the syntax tree \( P \) is parsed with generalized parsers because
-    it needs evaluation contexts to correctly choose specific parsers.
-    When the interpreter meets the above phrase, the specific parsers are now
-    decided into \( N \) thus we should parse again the given syntax tree \( P \) with
-    the non-terminal \( N \) in run time.
-\end{itemize}
-
-\subsubsection{Prioritized choices}
-However, unfortunately, there is fundamental problem in PEG-based parsers;
-\textit{prioritized choices}.
-In PEG, the pipe operator ( \( \mid \) ) denotes a prioritized choice,
-unlike CFG that deals with it in non-deterministic manners.
-It means that PEG always pick the first success right-hand side even though
-there exist other success choices in remaining right-hand sides.
-While ECMAScript grammars are deterministic languages, some non-terminals
-accepts multiple right-hand sides for a given input strings.
-It distort the meaning of ECMAScript grammars.
-For example, consider the following simplified grammars for JavaScript expressions:
+\textbf{Problem: Prioritized Choices.} While PEG provides all the
+features we discussed so far, it has one fundamental problem:
+\textit{prioritized choices}.  In PEG, the pipe \( \mid \) operator
+denotes a prioritized choice; even when multiple alternatives are
+applicable, PEG always picks the first success alternative.  However,
+some non-terminals of the ECMAScript grammar accept multiple
+alternatives for given input strings.  For example, consider the
+following simplified grammar of the JavaScript expressions:
 \[
@@
 \]
-While it represents deterministic grammar, the non-terminal \( \NT{T} \)
-should accept both right-hand sides if the given string is \( \code{a(b);} \).
-However, PEG-based parser fails to parse it
-because the first right-hand side \( \T{a} \) is always tried
-first in the non-terminal \( \NT{T} \).
-Thus, the latter one \( \T{a} \T{(} \T{b} \T{)} \) is not reachable in PEG.
-A simple solution is to change the order of right-hand sides;
-\( \NT{T} ::= \T{a} \T{(} \T{b} \T{)} \mid \T{a} \).
-However, it is not easy to ensure which order is correct
-because their inclusion relationship should be calculated.
-Moreover, some productions are not possible to resolve them
-by simply re-ordering right-hand sides:
+The non-terminal \( \NT{T} \) should accept both alternatives for
+\( \code{a(b);} \), but PEG-based parsers fail to parse it because the
+first alternative \( \T{a} \) succeeds first and the second alternative
+\( \T{a} \T{(} \T{b} \T{)} \) is not reachable.  A simple solution is
+to change the order of alternatives like \( \NT{T} ::= \T{a} \T{(} \T{b} \T{)} \mid \T{a} \),
+but ensuring correct order is not trivial because it requires
+calculation of their inclusion relationship.  Moreover, simple
+reordering does not work for some productions:
 \[
@@
 \]
-The non-terminal \( \NT{A} \) should successfully parse two strings \( \code{ab} \)
-and \( \code{abb} \). However, the non-terminal \( \NT{A} \) accepts only
-\( \code{ab} \) and it accepts only \( \code{abb} \) when \( \NT{B} \) has
-reversed order. It means that we should re-structure
-the above rules to accept both strings in traditional PEG grammars.
+The non-terminal \( \NT{A} \) should successfully parse two strings
+\( \code{ab} \) and \( \code{abb} \),  but it accepts only \( \code{ab} \),
+and it accepts only \( \code{abb} \) if \( \NT{B} ::= \T{a} \; \T{b} \mid \T{a} \).
+Hence, we should re-structure the above rules to accept both strings
+in traditional PEG grammars.
 
-\subsubsection{Lookahead tokens}
-To alleviate such problems, we propose \textit{lookahead parsers},
-which is extended recursive descent parsers with backtracking and
-\textit{lookahead tokens}.
-It keeps track of the next possible tokens using statically
-calculated first tokens of each symbols using algorithm in
-Figure~\ref{fig:first-tokens}. For example, the following steps explain
-how to utilize lookahead tokens during parsing processes with
-the input \( \code{a(b);} \):
-
-\begin{figure}
+\begin{figure}[t]
 \centering
+\small
 \[
@@
     \symbfirst{\symb \butnot \symb'} &=& \symbfirst{\symb}\\
-    \symbfirst{\nolt} &=& \{ \emptyfirst \}\\
+    \symbfirst{\nolt} &=& \{ \emptyfirst \}
   \end{array}
 \]
+\vspace*{-1em}
 \caption{Over-approximated first tokens of \( \bnfes \) symbols}
@@
 
-\Tree[.\(\NT{A}[\emptyfirst]\)
-[.\(\NT{T}\T{;}[\emptyfirst]\)
-[.\(\NT{T}[\T{;}]\)
-\sout{\(\T{a}[\T{;}]\)}
-[.\(\T{a}\T{(}\T{b}\T{)}[\T{;}]\)
-[.\(\T{a}[\T{(}]\) \(\boxed{\T{a}}\) ]
-[.\(\T{(}\T{b}\T{)}[\T{;}]\)
-[.\(\T{(}[\T{b}]\) \(\boxed{\T{(}}\) ]
-[.\(\T{b}\T{)}[\T{;}]\)
-[.\(\T{b}[\T{)}]\) \(\boxed{\T{b}}\) ]
-[.\(\T{b}\T{)}[\T{;}]\)
-[.\(\T{)}[\T{;}]\) \(\boxed{\T{)}}\) ] ] ] ] ] ]
-[.\(\T{;}[\emptyfirst]\)
-\(\boxed{\T{;}}\) ] ] ]
+\smallskip
 
-Each node \( \symb^*[\la] \) denotes a sequence of symbols \( \symb^* \) with
-lookahead tokens \( \la \), which is the set of tokens.
-The parsing process follows pre-order traversals.
-It starts from the starting non-terminal \( \NT{A} \) with the special
-lookahead \( \emptyfirst \), which denotes the end of inputs.
-Then, it visits the first right-hand side \( \NT{T} \T{;} \) with the same lookahead.
-Each symbol will be visited with the corresponding lookahead, that is the
-first tokens of the right next symbol.
+\textbf{Solution: Lookahead Tokens.}
+To alleviate the problem, we propose \textit{lookahead parsers},
+which are recursive descent parsers extended with backtracking and
+\textit{lookahead tokens}.  They keep track of the next possible
+tokens by statically calculating first tokens of each symbol using the
+algorithm in Figure~\ref{fig:first-tokens}.  For example, the
+following steps explain how to utilize lookahead tokens during parsing
+with the input \( \code{a(b);} \):
+\begin{center}
+  \includegraphics[width=0.3\textwidth]{img/laparser.png}
+\end{center}
+Each node \( \symb^*[\la] \) denotes a sequence of symbols \( \symb^* \)
+with a set of lookahead tokens \( \la \).  The parsing process follows
+a pre-order traversal.  It starts from the starting non-terminal \( \NT{A} \)
+with the special lookahead \( \emptyfirst \), which denotes the end of
+inputs.  Then, it visits the first alternative \( \NT{T} \T{;} \) with
+the same lookahead.  Each symbol is visited with its corresponding
+lookahead, which is the first tokens of the right next symbol.
 For example, for the symbol \( \NT{T} \), the next symbol is \( \T{;} \)
 and its first token is itself.  Thus, the parser visits \( \NT{T} \)
-with the lookahead \( \T{;} \). The most important point in this parsing process
-is the first right hand side \( \T{a} \) of the non-terminal \( \NT{T} \).
-It is visited with the lookahead \( \T{;} \) but the next token of the input string
-\( \code{a(b);} \) is \( \code{(} \) not \( \code{;} \).
-Thus, it fails to parse the input string even though the current token is
-same with the terminal \( \T{a} \).
-Thus, the parser could visit the next right-hand side \( \T{a}\T{(}\T{b}\T{)} \)
-and finally the input \( \code{a(b);} \) is successfully parsed.
+with the lookahead \( \T{;} \).  The most important point here
+is the first alternative \( \T{a} \) of the
+non-terminal \( \NT{T} \).  The parser visits it with the lookahead \( \T{;} \)
+but the next token of the input string \( \code{a(b);} \) is \( \code{(} \)
+rather than \( \code{;} \).  Hence, it fails to parse the input string
+even though the current token is the same with the terminal \( \T{a} \).
+Therefore, the parser can visit the next alternative \( \T{a}\T{(}\T{b}\T{)} \)
+and successfully parsers the input \( \code{a(b);} \).
 
-We formally define semantics of lookahead parsers
-in Figure~\ref{fig:laparser} by converting them into the given parsers.
-The helper function \( \getlap{\la} \) generates a parser by combining all
-tokens in the lookahead \( \la \) using prioritized choices.
-In this case, the order does not change the semantics of lookahead parsers
-because \( \getlap{\la} \) just check whether it contains the given token or not.
-
-\begin{figure}
+\begin{figure}[t]
 \centering
+\small
 \[
@@
 \]
+\vspace*{-1em}
 \caption{Formal semantics of lookahead parsers}
 \label{fig:laparser}
+\vspace*{-1em}
 \end{figure}
 
-\subsection{Implementation}
+We formally define the semantics of lookahead parsers in Figure~\ref{fig:laparser}.
+The helper function \( \getlap{\la} \) generates a parser by combining all
+tokens in the lookahead \( \la \) using prioritized choices.
+In this case, the order does not change the semantics of lookahead parsers
+because \( \getlap{\la} \) just checks the existence of a given token.
 
-We implement lookahead parsers by extending Scala parser combinators.
-We define \( \code{LAparser} \) trait to represent lookahead parser
-and it has two members; first tokens and a function from lookahead tokens into parsers
-described in Figure~\ref{fig:first-tokens} and Figure~\ref{fig:laparser}, respectively.
-There exists two different issues in implementing the lookahead parsers in Scala
-to treat ECMAScript syntax written in \( \bnfes \).
+\subsection{Implementation}\label{sec:convert-bnfes}
+We implemented lookahead parsers by extending Scala parser combinators
+with two functions corresponding to Figure~\ref{fig:first-tokens} and
+Figure~\ref{fig:laparser}.
 
-\paragraph{Performances} One of critical weak points of recursive descent parsing
-with backtracking is its performance. Basically, it needs exponential time related
-to the input size because of the backtracking mechanism. Fortunately,
-Ford et al~\cite{packrat} proposed Packrat parsing that provides linear
-time complexity based on memoization technique. The main idea is that it treats
-each parser as a function from the current input position into the parsing result.
-Thus, it just memoizes each parser based on input positions. It dramatically reduces
-the redundant parsing trials. In a similar way, we treat each lookahead parser as
-a function from a pair of lookahead tokens and input positions into parsing results.
+\smallskip
 
-\paragraph{Left Recursions} The other issue is that recursive descent parsers
-does not support left recursions in grammars. If a grammar has left recursions,
-the parser falls into an infinite loop. To resolve this problem,
-Warth et al~\cite{packrat-lr} proposed a way to support not only direct left
-recursions but also indirect ones in Packrat parsing.
-The basic idea is extends the memoization technique to support grow the parsing
-results. We believe that it is conceptually possible to support direct and indirect
-left recursions by applying the Warth's approach.
-\inred{However, fortunately, it is not necessary to handle indirect left
-recursions in order to deal with ECMAScript syntax because the all
-versions of ECMAScript only have direct left recursions.}
-Thus, we decided to just remove direct left recursions by defining sub productions
-and carefully build the abstract syntax trees.
-
-\subsubsection{AST generations}
-We first automatically generate abstract syntax tree(AST) as Scala case classes
-from the given \( \bnfes \) grammar that represents a version of ECMAScript.
-For lexical grammars, their structures are not used in ECMAScript semantics
-thus we gives them String types. For parser grammars, we need to
-automatically synthesize a Scala file that has classes of syntax trees.
-For each production \(
+\textbf{AST Generation.}
+We first automatically generate ASTs as Scala case classes from a
+given \( \bnfes \) grammar.  Because lexical grammars do not affect
+the ECMAScript semantics, we represent them as string values.
+For parser grammars, we automatically synthesize a Scala file that has
+classes of syntax trees.  For each production \(
   \NT{A}(\param_1, \cdots, \param_k) ::=
@@
   (\cond_n \Rightarrow)^? \rhs_n
-\), the AST generator defines the \( \code{A} \) trait and
-multiple sub classes \( \code{Ai} \) of \( \code{A} \) for right-hand sides.
-Each class \( \code{Ai} \) has non-terminals as member variables and
-its type is the corresponding non-terminal type. Additionally, only optional
-non-terminal symbol has \( \code{Option[\_]} \) types.
-For instance, the \( ArrayLiteral \) production
-in~Figure\ref{fig:array-literal} automatically translated into the following
-Scala classes:
-\begin{lstlisting}[style=myScalastyle]
+\), the AST generator defines the \( \code{A} \) trait and multiple
+subclasses \( \code{A}_i \) of \( \code{A} \) for \(1 \le i \le n\)
+that represents its alternatives.  Each class \( \code{A}_i \) has
+non-terminals in its corresponding alternative as its fields.
+For instance, the \( ArrayLiteral \) production in Figure~\ref{fig:array-literal}
+gets automatically translated to the following Scala classes:
+\begin{lstlisting}[style=smallScalastyle]
 trait ArrayLiteral extends AST
@@
 
-\subsubsection{Parser generations}\label{sec:convert-bnfes}
-The next step is to automatically extract parsers from the given \( \bnfes \) grammar.
-The conversion from \( \bnfes \) symbols into Scala codes is defined as follows:
+\smallskip
+
+\textbf{Parser Generation.}
+The next step is to automatically extract parsers from the given \(
+\bnfes \) grammar.  The conversion from \( \bnfes \) symbols into
+Scala code is as follows:
 \[
-  \begin{array}{c|c}
-    \bnfes \; \text{symbols} & \text{Scala codes}\\\hline\hline
-    \epsilon & \code{MATCH}\\\hline
-    \T{a} & \code{"a"}\\\hline
-    \NT{A}(\argument_1, \argument_n) & \code{A(a1, .. , an)}\\\hline
-    \symb? & \code{opt(s)}\\\hline
-    \symb \butnot \symb' & \code{s\textbackslash s'}\\\hline
-    \nolt & \code{NoLineTerminator}\\\hline
+\small
+  \begin{array}{ccc}
+%    \bnfes \; \text{symbols} &\Rightarrow& \text{Scala codes}\\\hline
+    \epsilon &\Rightarrow& \scode{MATCH}\\
+    \T{a} &\Rightarrow& \scode{"a"}\\
+    \NT{A}(\argument_1, \cdots, \argument_n) &\Rightarrow& \scode{A(a1, .. , an)}\\
+    \symb? &\Rightarrow& \scode{opt(s)}\\
+    \pm\symb &\Rightarrow& \pm\scode{\symb} \\
+    \symb \butnot \symb' &\Rightarrow& \scode{s\textbackslash s'}\\
+    \nolt &\Rightarrow& \scode{NoLineTerminator}\\
   \end{array}
 \]
-The \( \code{MATCH} \) denotes the empty sequence of lookahead parsers.
-Each String literals are implicitly converted into lookahead parsers
-through Scala implicit conversions. The \( \code{opt(s)} \) funciton
-is same with \( \code{s | MATCH} \). We also define \( \code{\textbackslash} \)
-opertor between parsers to support exclusive parsers.
-Finally, we support the \( \code{NoLineTerminator} \) parser.
-It is a little bit tricky because it should hook the whitespace parsers
-and check whether it contains line terminators.
-However, it is possible in our approach because
-we also automatically generates lexers not only parsers of ECMAScript syntax.
-For the final result, the automatically synthesized parser from the
-production \( ArrayLiteral \) in Figure~\ref{fig:array-literal} is defined
-as the parsers defined in Figure~\ref{fig:array-literal}.
+where \( \code{MATCH} \) denotes the empty sequence of lookahead parsers.
+Each string literal gets implicitly converted to a lookahead parser via
+Scala implicit conversion.  The \( \code{opt(s)} \) function is the
+same with \( \code{s | MATCH} \).  We also define the \( \code{\textbackslash} \) 
+operator between parsers to support exclusive parsers.
+Finally, we provide the \( \code{NoLineTerminator} \) parser, which uses
+the white space parsers to check the existence of line terminators.
+Our approach can support such a parser because we also automatically
+generate lexers not only parsers of the ECMAScript syntax.  Then, the 
+automatically synthesized parser from the production \textit{ArrayLiteral}
+in Figure~\ref{fig:array-literal}(a) is the one in Figure~\ref{fig:array-literal}(b).
 
-Moreover, we support automatic semicolon insertion algorihtms as well.
-It is the most distinctive parsing feautres in ECMAScript to parse more programs.
-We extend our parser implementation to keep track of the right-most position
-that fails to be parsed in the given input. In ECMAScript, the token at that
-position is defined as \textit{offending token} and automatic semicolon insertion
-algorithms are defined with such tokens. The algorithm is quite easy when we
-already have the position offending tokens, because there are only three simple
-rules. Thus, we just manually support them by following the rule in ECMAScript 2019.
-Moreover, the rule is rarely changed because the only one sub-rule is added
-after ECMAScript 5.1 written in 2011.
+We support the automatic semicolon insertion algorithm, which
+is the most distinctive parsing feature in ECMAScript.  We extended
+our parser implementation to keep track of the right-most position
+that fails to be parsed in a given input.  In ECMAScript, the token at that
+position is defined as an \textit{offending token} and the automatic
+semicolon insertion algorithm is defined with such tokens.  The
+algorithm is simple when we already have the positions of offending
+tokens.  Thus, we just manually supported them by following the rules
+in ECMAScript 2020.  In addition, the rules rarely change; since
+ECMAScript 5.1 written in 2011, only one sub-rule was added.
+
+\smallskip
+
+\textbf{Discussion.}
+While implementing lookahead parsers in Scala, we resolved two issues.
+
+First, one of the critical weak points of recursive descent parsing
+with backtracking is its performance.  To support backtracking, it
+requires exponential time relative to the input size.  Luckily, Ford
+et al~\cite{packrat} proposed Packrat parsing that provides linear 
+time complexity using memoization.  By treating each parser as a
+function from the current input position to a parsing result, it just
+memoizes each parser using input positions, which dramatically reduces
+redundant parsing trials.  In a similar way, we treat each lookahead
+parser as a function from a pair of lookahead tokens and input
+positions to a parsing result.
+
+The second issue is that recursive descent parsers do not support left
+recursion in grammars.  If a grammar has a left recursion, its parser
+falls into an infinite loop.  To resolve this problem, Warth et
+al~\cite{packrat-lr} proposed a mechanism to support not only direct
+left recursion but also indirect one in Packrat parsing.  While we can
+adopt the mechanism, we found that the ECMAScript 2020 syntax does not
+use indirect left recursion.  Thus, we decided to just remove direct
+left recursion by defining sub productions.

### 2019-08-19 src/main/resources/es2020_prop/manual/AlgoCompiler.scala
support proposal: Optional Chaining

@@ -1,0 +1,1617 @@
+package kr.ac.kaist.ase.model
+
+import kr.ac.kaist.ase.algorithm
+import algorithm.{ AlgoKind, Algorithm, Token, StaticSemantics }
+import algorithm.{ Method, Grammar, AlgoCompilers, Text }
+import kr.ac.kaist.ase.core.Parser._
+import kr.ac.kaist.ase.core._
+import kr.ac.kaist.ase.LINE_SEP
+import scala.util.{ Try, Success, Failure }
+
+import kr.ac.kaist.ase.error.UnexpectedShift
+import kr.ac.kaist.ase.parser.TokenParsers
+import kr.ac.kaist.ase.util.Useful._
+
+case class AlgoCompiler(algoName: String, algo: Algorithm) extends AlgoCompilerHelper {
+  val kind = algo.kind
+  lazy val result: (Func, Map[Int, List[Token]]) = {
+    val (params, varparam) = handleParams(algo.params)
+    val func = Func(
+      name = algoName,
+      params = params,
+      varparam = varparam,
+      body = normalizeTempIds(flatten(ISeq(parseAll(stmts, algo.toTokenList) match {
+        case Success(res, _) => res
+        case f @ NoSuccess(_, reader) => error(s"[AlgoCompilerFailed] ${algo.filename}")
+      })))
+    )
+    (func, failed)
+  }
+}
+
+trait AlgoCompilerHelper extends AlgoCompilers {
+  val algo: Algorithm
+  val algoName: String
+  val kind: AlgoKind
+
+  // execution context stack string
+  val executionStack = "GLOBAL_executionStack"
+  val context = "GLOBAL_context"
+  val realm = "REALM"
+  val jobQueue = "GLOBAL_jobQueue"
+  val retcont = "__ret__"
+
+  ////////////////////////////////////////////////////////////////////////////////
+  // Instructions
+  ////////////////////////////////////////////////////////////////////////////////
+  lazy val stmt: P[Inst] = {
+    etcStmt | (
+      innerStmt |||
+      returnStmt |||
+      returnContStmt |||
+      letStmt |||
+      ifStmt |||
[…]

### 2019-08-19 src/main/resources/es2020_prop/manual/algorithm/RegExpCreate.scala

@@ -1,0 +1,10 @@
+package kr.ac.kaist.ase.model
+
+import kr.ac.kaist.ase.core.Parser._
+import kr.ac.kaist.ase.core._
+
+object RegExpCreate {
+  val func: Func = parseFunc(""""RegExpCreate" (pattern, flags) => {
+    !!! "RegularExpression"
+  }""")
+}

### 2019-08-19 src/main/resources/es2020_prop/manual/algorithm/floor.scala

@@ -1,0 +1,10 @@
+package kr.ac.kaist.ase.model
+
+import kr.ac.kaist.ase.core.Parser._
+import kr.ac.kaist.ase.core._
+
+object floor {
+  val func: Func = parseFunc(""""floor" (a) => {
+    return (- a (% a 1))
+  }""")
+}

### 2019-08-19 icse/main.tex
Temporal update for evaluation

@@
 \usepackage{qtree}
+\usepackage{colortbl}
 \usepackage{ulem}
@@
 \usepackage{listings}
-\usepackage[noend]{algorithm,algpseudocode}
 \usepackage{enumitem}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\usepackage{booktabs}
+
+% color
+\definecolor{gainsboro}{rgb}{0.86, 0.86, 0.86}
+\newcommand*{\belowrulesepcolor}[1]{%
+  \noalign{%
+    \kern-\belowrulesep
+    \begingroup
+      \color{#1}%
+      \hrule height\belowrulesep
+    \endgroup
+  }%
+}
+\newcommand*{\aboverulesepcolor}[1]{%
+  \noalign{%
+    \begingroup
+      \color{#1}%
+      \hrule height\aboverulesep
+    \endgroup
+    \kern-\aboverulesep
+  }%
+}
+
+% dashed line
+\usepackage{array}
+\usepackage{arydshln}
+\setlength\dashlinedash{0.2pt}
+\setlength\dashlinegap{1.5pt}
+\setlength\arrayrulewidth{0.3pt}
 
@@
   basicstyle={\footnotesize\ttfamily},
+  numbers=none,
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  frame=single,
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3,
+}
+\lstdefinestyle{smallScalastyle}{
+  frame=tb,
+  language=scala,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=fixed,
+  basicstyle={\scriptsize\ttfamily},
   numbers=none,

### 2019-08-20 icse/eval.tex
Updated images in evaluation
Changed tag

@@
   \centering
-  \begin{subfigure}{0.23\textwidth}
-    \includegraphics[width=\textwidth]{img/all-version-syntax.png}
+  \begin{subfigure}{0.48\textwidth}
+    \[
+      \begin{array}{c|r|r|r|r|r}
+        \hline
+        \text{version}
+        & \multicolumn{1}{c|}{2016}
+        & \multicolumn{1}{c|}{2017}
+        & \multicolumn{1}{c|}{2018}
+        & \multicolumn{1}{c|}{2019}
+        & \multicolumn{1}{c}{2020}\\\hline
+        \text{\#prods}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}\\\hline
+        \Delta
+        & \multicolumn{1}{c|}{\text{-}}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}
+        & \text{\inred{XXX}}\\\hline
+      \end{array}
+    \]
     \caption{The parser generator.}
@@
   \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.23\textwidth}
+  \begin{subfigure}{0.48\textwidth}
     \includegraphics[width=\textwidth]{img/all-version-sem.png}
@@
 Moreover, we fill in global setting based on ECMAScript 2020 specification as described
-in Section~\ref{sec:framework}. The ECMAScript 2020 version is actively updated in
+in Section~\ref{sec:impl}. The ECMAScript 2020 version is actively updated in
 GitHub~\cite{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
@@
 we focus on only JavaScript codes in strict mode
-as described in Section~\ref{sec:framework}. Finally, we remove the \inred{XXXX} tests
+as described in Section~\ref{sec:impl}. Finally, we remove the \inred{XXXX} tests
 for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
@@
 in the rendered HTML file.
-
-\inred{- completion records??}
-% The last issue is about the \textit{completion record type}, which is one of controversial features
-% in ECMAScript specifications. They are used to describe the propagation of control
-% flows and values in abstract algorithms. They are implicitly constructed
-% in steps that return values that are not completion records in runtime semantics.
-% Moreover, 
-% It confuses the type of return values

### 2019-08-20 icse/overview.tex
Changed tag

@@
 easily construct compile rules (Section~\ref{sec:compiler}).  After
-describing implementation details (Section~\ref{sec:framework}),
+describing implementation details (Section~\ref{sec:impl}),
 we evaluate the effectiveness of \( \tool \)

### 2019-08-20 icse/impl.tex
Changed filename framework.tex -> impl.tex
Edited implementation section

--- 2019-08-19 icse/framework.tex
@@
-\section{Building entire system to extract semantics}\label{sec:framework}
+\section{Implementation}\label{sec:impl}
 
-In this section, we demonstrate how our idea can be implemented for target language. Although it is hard to generalize the process because the format of specification or
-environment of the programming language is varying, We shows the possibility to build entire system to extract target language specification and interpreting it with minimal human effort by giving end-to-end example of ECMAScript language.
+In this section, we demonstrate the implementation detail of \( \tool \).
+We target to extract JavaScript syntax and semantics from
+ECMAScript 2020 specification. It is the next ECMAScript version
+that is actively updated in GitHub repository~\cite{es2020}
+to be released in the next year. Moreover, Ecma Technical Committee 39 (TC39)
+officially provides the conformance test suite, test262, for ECMAScript 2020.
 
-\subsection{Extracting specification}
-First step is to collect language specification and extract component that we can process automatically. For our target language, ECMAScript, has HTML format of specification in their website, and
-in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
-We get these information by parsing HTML document, and passing these result to our previous module to get AST, Parser, and executable algorithms.
+\subsection{Excluded Language Features}
+We decide to not support several language features in ECMAScript 2020:
 
-To organize these primitives and running the program, we have to model initial environment of language such as initialization of builtin types, or entry point of the program, etc.
+\paragraph{No-Strict Mode}
+Since ECMAScript 5, JavaScript introduced strict mode to \textit{intentianally} provide
+slightly different semantics. It provides more stable semantics by preventing
+unsafe actions or throwing originally ignored errors.
+However, ECMAScript specification says:
+``Strict mode does not restrict or modify any aspect of the ECMAScript semantics
+that must operate consistently across multiple source text units.''
+Thus, we decide to only support strict mode JavaScript to reduce the labors.
 
-\subsection{Generating initial environment for execution}
-For ECMAScript Specification, initial environment consists of the Builtin objects, and Intrinsic objects. We describe how to generate each component.
+\paragraph{Intricate Built-ins}
+JavaScript provides various built-in object to support helper functions in standard.
+However, several built-in libraries are orthogonal but labor-intensive
+to be manually modeled. Thus, we decide to not support
+four orgothonoal libraries; \( \code{Math} \), \( \code{Date} \),
+\( \code{RegExp} \), and \( \code{JSON} \).
 
-\subsubsection{Builtin objects}
+\paragraph{Modules}
+Moreover, we also do not support modules introduced since ES6 (ECMAScript 2015).
+With the \( \code{import} \) keyword, a JavaScript program
+imports other JavaScript components defined with the \( \code{export} \)
+keyword in modules. In order to support modules in semantics, we should
+model the functionality to communicate with file system to access
+JavaScript module files. However, modules do not critically affect
+the overall semantics. Thus, we decide to not support modules.
 
- Builtin object is a pre-defined object with many built-in functions. For example, In ECMAScript \( \code{Array} \) corresponds to an object which can generate an array by
- calling it. Each builtin object provides data property and functions, just as ordinary object. When its function is called,
- its algorithm specified in the document should be called.
+\subsection{Comple Rules for ECMAScript}
 
- In specification, a builtin function object usually matches to abstract algorithm. Its algorithm name
- describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
- we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as property.
- To support builtin object, we make structure of builtin object and its properties.
- After we correctly organizes structure, then we made algorithm that automatically map corresponding field to the abstract algorithm in specification by matching its function name.
+\begin{table}
+  \centering
+  \[
+    \begin{array}{c|r|r|r|r|r|r|r}
+      \text{name}
+      & \multicolumn{1}{c|}{\code{Stmt}}
+      & \multicolumn{1}{c|}{\code{Expr}}
+      & \multicolumn{1}{c|}{\code{Cond}}
+      & \multicolumn{1}{c|}{\code{Value}}
+      & \multicolumn{1}{c|}{\code{Ty}}
+      & \multicolumn{1}{c|}{\code{Ref}}
+      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
+      \text{\# rules}
+      & \inred{XX}
+      & \inred{XX}
+      & \inred{XX}
+      & \inred{XX}
+      & \inred{XX}
+      & \inred{XX}
+      & \inred{XX}\\\hline
+    \end{array}
+  \]
+  \caption{The compile rules for ECMAScript specifications.}
+  \label{table:rules}
+\end{table}
 
- \subsubsection{Intrinsic objects}
+The \textsf{Algorithm Compiler} requires compile rules to compile
+given abstract algorithms into \( \ires \) functions.
+We define compiler rules for ECMAScript specifications
+and Table~\ref{table:rules} describes them.
+The statement compile rule \( \code{Stmt} \) contains
+\inred{XX} compile rules and generates \( \ires \) instructions.
+The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \)
+compile rules denote expressions, conditions, and values, respectively.
+While all of them generates \( \ires \) expressions,
+we discriminate them because they have different use cases.
+The \( \code{Ty} \) denotes type names and generates
+string primitives in \( \ires \). The \( \code{Ref} \)
+represents the references including identifiers lookups or
+member accesses of map-like structures. It generates
+\( \ires \) reference expressions.
+Finally, the Section number \( \code{SecNo} \) compile rule
+represents sections numbers such as \( \code{9.4.1.1} \),
+and it converts such numbers into the corresponding name strings
+such as \( \code{"BoundFunctionObject.Call"} \).
 
- In specification, "Well-known intrinsics are built-in objects that are explicitly referenced by the algorithms".
- Abstract algorithm uses identifiers like "\%name\%" to point builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
- Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.
+\subsection{Global Setting}
 
-\subsection{Algorithm scope}
+We manually implemented \textsf{Global Setting} for ECMAScript 2020.
+It consists of the structure of built-in objects and ECMAScript data types.
 
- In specification, All algorithm has name to refer it, but some algorithms have same names and they are called in context-dependent way.
-In "5.2 Algorithm Conventions", it defines three types of abstract operation.
- \begin{itemize}
-  \item Abstract operation: they can be called by name in any context
-  \item Method-like abstract operation: algorithm dispatch depends on receiver object
-  \item Syntax-directed operation: algorithm dispatch depends on receiver AST
-  \end{itemize}
+\subsubsection{ECMAScript Data Types}
 
-First, we categorized sections by types of algorithm.
-Method-like abstract operation has separate sections to describe it, so we manually add these sections to treat differently.
-Also Syntax-directed operations are described in distinct sections, so both case is easy to extract it.
-Rest algorithms are considered as ordinary Abstract operation.
+In ECMAScript, the Section \textsf{6 ECMAScript Data Types and Values} describes
+data types used in ECMAScript specifications. They not only represent
+data types explicitely exposed into JavaScript evaluations, but also
+represent all internal data types used in the specification.
+For example, the Environement Records are record types from identifiers
+into bindings for values. They are not explicitely accessed in JavaScript
+programs but defined internally in the specification.
 
-\subsubsection{Abstract operation}
+Each ECMAScript data type consists of several fields to store relevant values.
+Thus, we should implement such structures to correctly evaluate JavaScript
+programs. Moreover, some fields of ECMAScript data types might be
+abstract algorithms. We call them as \textit{method-like abstract algorithms}
+and they have implicitly get reciever object as an argument.
+In order to mimic such implicit behaviors, we added a special variable
+\( \code{this} \) as the first parameter. And we modify algorithm compiler
+to detect cases and pass the receiver object into the method-like abstract
+algorithms. For example, an Environement Record has the \textsf{DeleteBinding (N)}
+abstract algorithm as one of its fields. Then, it has two parameters the special
+parameter \( \code{this} \) and normal one \( \code{N} \).
+The following algorithm step is compiled into the \( \ires \) instruction
+\( \code{return DclRec.DeleteBinding(DclRec, N)} \).
+\begin{center}
+  \includegraphics[width=0.3\textwidth]{img/method-like-example.png}
+\end{center}
 
-We just convert abstract operations to function, and bind global identifier to that function to call it by algorithm name.
+\subsubsection{Built-in Objects}
+In ECMAScript, built-in objects are pre-defined functions with several
+built-in functions. For example, the array object \( \code{Array} \)
+is the constructor of array objects, and its prototype property
+\( \code{Array.prototype} \) has built-in functions for array objects.
+For example, \( \code{[1,2,3].flat()} \) calls the
+\( \code{Array.prototype.flat} \) built-in function with the array
+\( \code{[1,2,3]} \). Built-in functions are also abstract algorithms
+thus each of them is automatically converted into an \( \ires \) function.
+However, the structured of built-in objects should be implemented manually.
+Thus, we implement built-in objects in Scala and connect their properties
+with the extracted \( \ires \) functions.
 
-\subsubsection{Method-like abstract operation}
-
-In ECMAScript specification, there are some objects which has similar interface, but they have different algorithms.
-
-For Example, Ordinary Object and String Exotic Object is different object in specification, but they have same name of algorithm(i.e. \( \code{[[getOwnProperty]](N)} \))
-
-In this case, algorithm dispatching should consider receiver Object(i.e. \( \code{x.[[GetOwnProperty]](N)} \)).
-For method-like abstract operation, we organized map from algorithm name to function for each type,
- and we insert functions as property of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
- then we insert property with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.
-
- \subsubsection{Syntax-directed operation}
-
- Like method-like abstract operation, many AST objects have similar interface, but they have different algorithm.
-The most frequent example is "Evaluation" algorithm of AST Values. Many non-terminal symbol have different algorithm with name "Evaluation", and
-when specification requires "the result of evaluating \textit{variable}", then it should apply "Evaluation" of non-terminal symbol which matches to \textit{variable}.
-It is assumed that \textit{variable} is a AST value. Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
-Evaluation algorithm of \textit{CallExpression} : \textit{CallExpression} \textit{Arguments}, algorithm can uses \textit{CallExpression} or \textit{Arguments} to refer sub-component of AST.
- To support Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
-We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.
-
-% \begin{itemize}
-%   \item \textbf{Global Algorithms} Global algorithms are possible to be accessed
-%     by any other algorithms. The top-level algorithm \( \code{RunJobs} \) is also global.
-%   \item \textbf{Type-dependent Algorithms} Several algorithms have different
-%     bodies dependent on types of their owner data. In ECMAScript specifications,
-%     there are two different data types; language types and specification types.
-%     The language types are explicitly used in JavaScript languages such as
-%     \( \code{Boolean}, \code{Number}, \code{String} \), and \( \code{Object} \).
-%     However, specification types are only used in specifications such as
-%     Lists, Records, and Lexical Environments. Among them, some data types
-%     have their own member algorithms. For example, language type \( \code{Object} \)
-%     has several internal methods described in abstract algorithms. It depends
-%     on 
-% 
-%     several data types have their own member algorithms. For example, 
-%     
-%     For example, the internal method
-%     \( \code{[[Call]]} \) has different semantics dependent on its owner object.
-%     Moreover, the owner objects are used in the body of algorithms as well.
-%     Thus, we extend the parameters to accept its owner object as an implicit argument.
-%   \item \textbf{Syntax-directed Algorithms} The semantics of each JavaScript syntax
-%     are written in 
-% \end{itemize}
-
-% \subsection{semantic 컴파일하기 위해 하는 것 + specification 구조}
-% 기본적인 원칙 :
-% \begin{itemize} 
-% \item 자바스크립트로 알고리즘 이름이랑 파라미터, 스텝을 가져와서 코어의 글로벌 ID에 매치 시켜줌
-% \item initial Heap을 생성해줌
-% \end{itemize}
-% 매치를 시킨다는 뜻은 코어의 글로벌 ID에 코어 함수 형태로 알고리즘을 넣는 것임
-%
+Some built-in objects are named as intrinsic objects when they are
+are explicitly referenced in abstrat algorithms.
+Intrinsic objects have their own names as aliases in the table
+of the Section \textsf{6.1.7.4 Well-known Intrinsic Objects}.
+Thus, we extract such alias information into \textsf{Global Setting}
+to utilize it during evaluations.

### 2019-08-20 icse/compiler.tex
Fixed error of code in algorithm copiler section

--- 2019-08-16 icse/compiler.tex
@@
 \section{Algorithm Compiler}\label{sec:compiler}
-
 \begin{figure}
@@
   \includegraphics[width=0.5\textwidth]{img/algo_compiler.png}
-  \caption{Overall structure of the algorithm compiler.}
+  \caption{Overall structure of {\sf Algorithm Compiler}}
   \label{fig:algo-compiler}
@@
 
-In this section, we propose the \textit{algorithm compiler}
-that compiles abstract algorithms into \( \ires \) functions
-and its overall structure is described in Figure~\ref{fig:algo-compiler}.
-Before compiling abstract algorithms,
-the tokenizer first tokenizes each abstract algorithm into
-a list of tagged tokens. Then, the token parser constructs
-syntactic parse tree of the given token list.
-Finally, the \( \ires \) function generator constructs the corresponding
-\( \ires \) function from the given parse tree.
-The parser and the generator is dependent on conversion rules
-and we define the general conversion rules for abstract algorithms in
-ECMAScript specifications. Like Coq, a proof assistant, we also provide
-the \textit{rule generation assistant} to make easy write conversion rules.
-It suggests new conversion rules based on
-statistical analysis of algorithm steps that failed to be parsed
-and also diagnoses root causes of parsing failures.
+In this section, we explain {\sf Algorithm Compiler} that compiles
+abstract algorithms to \( \ires \) functions as illustrated in
+Figure~\ref{fig:algo-compiler}.
 
 \subsection{Tokenizer}
+Before compiling abstract algorithms, {\sf Tokenizer} first tokenizes
+each abstract algorithm into a list of tagged tokens.  An algorithm
+consists of ordered steps and it may contain sub-steps as well.
+For example, the \textbf{\small ToPrimitive} algorithm in
+Figure~\ref{fig:to-primitive}(a) has three steps and the second step
+has seven sub-steps.  Moreover, the tokens of each step have their own
+HTML tags and each tag has a meaning.  For instance, \code{<var>}
+denotes variables, \code{<emu-grammar>} denotes productions, and
+\code{<code>} denotes ECMAScript code.
+% \[
+%   \begin{array}{c|l}
+%     \text{HTML tags} & \text{meanings}\\\hline\hline
+%     \code{<var>} & \text{variables}\\\hline
+%     \code{<emu-grammar>} & \text{productions}\\\hline
+%     \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
+%     \code{<code>} & \text{ECMAScript codes}\\\hline
+%     \code{<emu-const>} & \text{constant values}\\\hline
+%     \code{<emu-val>} & \text{values}\\\hline
+%     \code{<ol>} & \text{ordered sub-steps}\\\hline
+%     \code{<ul>} & \text{unordered sub-steps}\\\hline
+%     \code{<sup>} & \text{superscripts}\\\hline
+%     \text{otherwise} & \text{simple texts}\\\hline
+%   \end{array}
+% \]
+We keep such HTML tag information for each token to generate more precise
+{\sf Compile Rules}.  For example, because if and only if a token has
+a tag \( \code{<var>} \), it is a parameter or a local variable, we can
+construct {\sf Compile Rules} that precisely distinguish identifiers
+from other components.
 
-Abstract algorithms in ECMAScript specifications are written in structured
-natural languages in HTML files. An algorithm consists of ordered steps
-and it might contain sub-steps as well. For example,
-the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es}
-has three steps and second step has seven sub-steps.
-Moreover, the tokens of each step has its own HTML tag and each tag
-has the following meaning:
-\[
-  \begin{array}{c|l}
-    \text{HTML tags} & \text{meanings}\\\hline\hline
-    \code{<var>} & \text{variables}\\\hline
-    \code{<emu-grammar>} & \text{productions}\\\hline
-    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
-    \code{<code>} & \text{ECMAScript codes}\\\hline
-    \code{<emu-const>} & \text{constant values}\\\hline
-    \code{<emu-val>} & \text{values}\\\hline
-    \code{<ol>} & \text{ordered sub-steps}\\\hline
-    \code{<ul>} & \text{unordered sub-steps}\\\hline
-    \code{<sup>} & \text{superscripts}\\\hline
-    \text{otherwise} & \text{simple texts}\\\hline
-  \end{array}
-\]
-We try to keep the tag information for each token to generate more
-precise conversion rules. For example, if and only if a token has a tag
-\( \code{<var>} \), it is a parameter or a local variable.
-Thus, it is possible to construct a conversion rule precisely discriminates
-identifiers and other components.
-
-The tokenizer first recognizes the overall structures of steps.
-Then, it divides each step into sequence of tagged tokens.
-If an HTML element has a explicit tag, it is converted into a single token
+The {\sf Tokenizer} module recognizes the structure of each step,
+and divides the step into a sequence of tagged tokens.
+If an HTML element has an explicit tag, it is converted to a single token
 with the tag.  Otherwise, it is divided into multiple tokens and each token
-should be a sequence of alphanumeric characters or a single
-non-alphanumeric character. For example, in the \( \code{ToPrimitive} \)algorithm,
-\( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
+becomes a sequence of alphanumeric characters or a single non-alphanumeric
+character.  For example, in the \textbf{\small ToPrimitive} algorithm,
+\( \textbf{\code{"default"}} \) is a single token with the HTML tag \( \code{<code>} \)
 and \( \code{@@toPrimitive} \) is divided into three text tokens
@@
 
-For the linear structures, the tokenizer flatten the structured steps into
-a single list. Some conversion rules should handle multiple steps such as
-the conditional statements (if-then-else). Thus, we decide to break down
-structured algorithms using three special tokens;
-\( \tend \) denotes the end of a single step,
-\( \tin \) and \( \tout \) the start and the end of nested steps, respectively.
-For example, the \( \code{ToPrimitive} \) algorithm is tokenized as follows.
+Moreover, {\sf Tokenizer} flattens a structured step to a single token
+list to handle multi-step statements easily.  Some statements in
+abstract algorithms consist of multiple steps.  For example, the
+\( \code{if}\!-\!\code{then}\!-\!\code{else} \) statement often consists of
+two steps: one for the \( \code{then} \)-branch and another
+for the \( \code{else} \)-branch.  To treat them as a linear structure,
+we introduce three special tokens to break down structured algorithms:
+\( \tend \) denotes the end of a single step, and \( \tin \) and
+\( \tout \) denote the start and the end of nested steps, respectively.
+For example, the \textbf{\small ToPrimitive} algorithm is tokenized as follows.
 \[
@@
 
-\subsection{Token Parser}
+After tokenizing abstract algorithms, {\sf Algorithm Compiler}
+compiles token lists into \( \ires \) functions using
+{\sf Token List Parser} and {\sf Token AST Converter}.
+They depend on {\sf Compile Rules} and each compile rule
+consists of a \textit{parsing rule} and a \textit{conversion rule}:
+\begin{lstlisting}[style=myScalastyle]
+val CompileRule = ParsingRule ^^ ConversionRule
+\end{lstlisting}
+For each compile rule, its parsing rule describes how to parse a given
+token list into a structured token AST, and its conversion rule describes
+how to convert the given token AST structure into an \( \ires \) component.
+Now, we explain the token list parser and token AST converter with
+parsing rules and conversion rules, respectively.
 
-The token parser parses a given list of tokens into a syntactic parse tree.
-It depends on the given \textit{conversion rules} that consists of
-two parts parsing rules and mapping from parsing rules into corresponding
-\( \ires \) components.
-A parsing rule consists of basic token matchers and other parsing rules
-including itself. For example, the following parsing rule is simplified version for
-sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
+\subsection{Token List Parser}
+Parsing rules determine the token list parser, and each parsing rule
+is written in extended Scala parser combinators.  We modified the
+meaning of the alternative composition operator ( \( | \) ) to collect
+all the longest matched results.  If a parser detects a step that
+cannot be parsed with given parsing rules, it reports the step into
+{\sf Rule Assistant}.  Even when a parser parses a step successfully,
+it also reports the step if it can parse the step in multiple ways.
+We use Packrat parsing~\cite{packrat} for parsing rules, which
+support left recursion.
+
+We provide two kinds of basic token parsers: tag-based parsers and
+content-based parsers.  A tag-based parser just checks whether the next
+token has a given tag.  For example, the tag-based parser \( \code{varT} \)
+checks whether the next token has the tag \( \code{<var>} \).  A
+content-based parser checks whether the next token is a text token and
+its content passes a given condition.  For example, the string literal
+\( \code{"Let"} \) denotes a content-based parser that checks whether
+the next token is a text token with the content \( \code{Let} \).
+We also provide two content-based parsers \( \code{word} \) and
+\( \code{number} \) that check whether the content of the next token
+consists of only alphabets or numbers, respectively.  In parsing
+rules, all the helper functions defined in Scala parser combinators
+are available.  For instance, the helper function \( \code{repsep(p, q)} \)
+generates a new parsing rule that denotes zero or more repetition of the
+parsing rule \( \code{p} \) using another parsing rule \( \code{q} \) as
+a separator.
+
+Consider the following example parsing rule, which is a simplified
+version for the step 2-e-i of the \textbf{ToPrimitive} algorithm.
 \begin{lstlisting}[style=myScalastyle]
@@
 val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
-// expressions
-val Expr = (
-  // identifiers
-  varT ^^ ... |
-  // return if abrupt
-  "?" ~ Expr ^^ ... |
+val Expr = (          // expressions
+  varT ^^ ... |       // identifiers
+  "?" ~ Expr ^^ ... | // return if abrupt
                       // function calls
-  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
-  // lists
-  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ ...
+  word ~ "(" ~ repsep(Expr, ",") ~ ")" ^^ ... |
+  "<<" ~ repsep(varT, ",") ~ ">>" ^^ ...  // lists
 )
 \end{lstlisting}
+The \( \code{Stmt} \) compile rule describes how to compile statements
+with one parsing rule and its conversion rule is omitted for now for
+brevity.  The \( \code{Expr} \) compile rule describes how to compile
+expressions with four parsing rules.  A token parser with the above
+rules parses the step 2-e-i of \textbf{ToPrimitive} to the following
+token AST:
+\begin{center}
+\includegraphics[width=0.5\textwidth]{img/token_ast.png}
+\end{center}
 
-Each parsing rule is written in extended Scala parser combinators.
-We modify the meaning of alternative composition operator ( \( | \) ) to collect
-all longest matched results. If the parser detects that a step cannot be
-parsed with the given parsing rules. It reports that a step is not possible
-to be parsed under the given rules into the rule generation assistant.
-Moreover, even though the parser could parse a step, it will be also reported
-if it could be parsed in not a single but multiple ways.
-Each string literal is a token matcher for tokens without any tags and checks
-that the token has same string value with the string literal.
-The \( \code{varT} \) and \( \code{textT} \) is also token matchers
-for token with the tag \( \code{<var>} \) and no tags.
-The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
-defined with our extended parser combinators.
-Moreover, it supports all helpers functions defined in Scala parser combinators.
-For example, the helper function \( \code{repsep(p, q)} \) generates a new
-parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
-using another parsing rule \( \code{q} \) as separators.
-Finally, the token parser with the above rules parses sub-step \( i \) in the
-\( \code{ToPrimitive} \) into the following syntactic parse tree:
-\includegraphics[width=0.5\textwidth]{img/token_ast.png}
-
-\subsection{\( \ires \) Function Generator}
-
-We define \( \ires \) language to give semantics into syntactic parse tree of
-abstract algorithm steps. It has the following language features:
-
-\begin{itemize}
-\item \textbf{Dynamic Typing} We decide to use dynamic typing for \( \ires \)
-because each variables in abstract algorithms are not statically typed.
-Thus, variables do not have its own static types while each value of \( \ires \)
-has its dynamic type.
-
-\item \textbf{Imperative Style} \( \ires \) represents algorithm steps
-as statements. Each statement changes the current state
-that consists of environments and a heap.
-
-\item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
-lambda functions as values but it has only restricted scopes. In each function,
-only global variables, parameter, and newly defined local variables are accessible.
-It means that the function closure does not capture the the current environment.
-We use such restricted scopes because it is enough to represent abstract algorithms.
-
-\item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
-the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
-are defined in \( \ires \); numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
-Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
-the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
-of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es} might be
-not present in some function calls. Then, the parameter has the \( \code{absent} \) value
-to represent its absence.
-
-\item \textbf{Abstract Data Types} \( \ires \) only supports three abstract data types;
-\( \code{Record} \) for mapping from some values into other value,
-\( \code{List} \) for sequential data types,
-and \( \code{Singleton} \) for singleton data types.
-They are stored in corresponding addresses in the heap structure.
-For example, ECMAScript environment records are represented as \( \code{Record} \) data types
-from String values for identifier names into addresses.
-The addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings.
-We treat a ECMAScript constants such as \( \code{empty} \) and primitive symbols as singleton
-data types in \( \ires \).
-\end{itemize}
-
-To generate the corresponding \( \ires \) function from syntactic parse tree,
-we describe the mapping from each parsing rule into the corresponding \( \ires \) components.
-For example, we describe the following mapping for the previous example parsing rules:
+\subsection{Token AST Converter}
+Conversion rules describe how to generate an \( \ires \) function for a
+given token AST.  Each conversion rule is defined with its
+corresponding parsing rule.  For basic token parsers, their conversion
+rules always return the string values of the contents in parsed tokens.
+For example, the following conversion rules are the omitted parts
+in the previous example for the step 2-e-i of \textbf{ToPrimitive}:
 \begin{lstlisting}[style=myScalastyle]
 // statements
-val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ESLet(x, y) }
-// expressions
-val Expr = (
-  // identifiers
-  ... ^^ { x => x } |
+val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
+val Expr = (               // expressions
+  ... ^^ { x => EId(x) } | // identifiers
                            // return if abrupt
-  ... ^^ { _ ~ e => ESReturnIfAbrupt(e) } |
+  ... ^^ { _ ~ e => EReturnIfAbrupt(e) } |
                            // function calls
-  ... ^^ { case x ~ _ ~ y ~ _ => ESCall(x, y) } |
-  // lists
-  ... ^^ { case _ ~ x ~ _ => ESList(e) }
+  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) } |
+  ... ^^ { case _ ~ x ~ _ => EList(e) } // lists
 )
 \end{lstlisting}
-Finally, sub-step \( i \) in the \( \code{ToPrimitive} \) is converted
-into the following instruction:
+The conversion rule of the compile rule \( \code{Stmt} \) uses only
+the second and fourth sub trees and converts them to \( \ires \)
+components.  The second sub-tree is converted to a string value
+because it was constructed via the basic token parser \( \code{varT} \).
+The fourth sub-tree is converted to an \( \ires \) expression
+because the conversion rules of the \( \code{Expr} \) compile rule
+construct \( \ires \) expressions.  Then, the conversion rule of
+\( \code{Stmt} \) constructs the lexical binding instruction \( \code{ILet} \)
+with the string value and the \( \ires \) expression.  In this way,
+the step 2-e-i of \textbf{ToPrimitive} is converted to the following
+instruction:
 \begin{lstlisting}[style=ires]
@@
 
-\subsection{Rule Generation Assistant}
+We define \( \ires \) to represent abstract algorithms as its
+functions with the following design choices:
 
-\inred{
-To make easy write conversion rules, we support \textit{rule generation assistant}.
-It consists of two helper functions; the \textit{rule recommender} and
-the \textit{fault localizer}. The
+\begin{itemize}[leftmargin=0.5cm]
+\item \textbf{Dynamic typing:} Because each variable in abstract
+algorithms is not statically typed, variables do not have their own
+static types while each value of \( \ires \) has its dynamic type.
 
-It makes easy not only construct conversion rules from the scratch
-but also updates existing conversion rules to handle specification updates.
-We explain each helper function and how to utilize it to construct conversion rules.
+\item \textbf{Imperative style:} \( \ires \) represents algorithm steps
+as imperative instructions in the sense that each instruction changes
+the current state consisting of an environment and a heap.
 
-\subsubsection{Statistics Monitor}
+\item \textbf{Higher-order functions with restricted scopes:}
+In each function of \( \ires \), only global variables, parameters,
+and its local variables are available, which means that a function
+closure does not capture its current environment.  We use such
+restricted scopes because they are enough to represent abstract
+algorithms.
 
-TODO
+\item \textbf{Primitive values:} \( \ires \) supports ECMAScript
+primitive values except ``symbols'' because symbols can be represented
+as singleton objects.  Also, \( \ires \) provides the unique \(
+\code{absent} \) value to represent the absence of parameters.  For
+example, when the optional second parameter \( \code{PreferredType} \)
+of \textbf{ToPrimitive} in Figure~\ref{fig:to-primitive}(a) is absent,
+the parameter has the \( \code{absent} \) value.
 
-\subsubsection{Fault localizer}
+\item \textbf{Abstract data types:} \( \ires \) supports only three
+abstract data types: \( \code{Record} \) for mappings from some values
+to other values, \( \code{List} \) for sequential data, and
+\( \code{Singleton} \) for singleton data.  For example, ECMAScript
+environment records are represented as \( \code{Record} \)
+with string values as keys and addresses as values.  Each key
+represents an identifier name and its corresponding address represents
+an ECMAScript object.  We also represent constants in the ECMAScript
+specification such as \( \code{empty} \) and \( \code{normal} \) as
+\( \code{Singleton} \) data types in \( \ires \).
+\end{itemize}
 
-TODO
-}
+\subsection{Rule Assistant}
+\begin{algorithm}[t]
+  \caption{Fault Localization}\label{alg:fault}
+  \begin{algorithmic}[1]
+    \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
+    \State $S = \varnothing$
+    \For{$i = 0$ to $n - 1$}
+    \For{$j = i$ to $n - 1$}
+    \State $T'$ = a copy of $T$
+    \State Substitute $T'[i..j]$ with $\tstar$
+    \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
+    \State Insert $(x, i, j)$ into $S$
+    \EndIf
+    \EndFor
+    \EndFor
+    \While{$s = (x, i, j) \in S$}
+    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
+    \State Remove $s$ from $S$
+    \EndIf
+    \EndWhile
+    \State \Return $S$
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+To make it easy to write compile rules, we support a \textit{rule assistant},
+which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
+For each failed step, the rule assistant diagnoses a root cause of the
+parsing failure.  The basic idea is to check whether we can parse the
+failed input with the assumption that a specific sub-sequence of the
+failed step is successfully parsed.  We define an approach to find
+such sub-sequences of failed steps as \textit{fault localization}.
+This approach was actually helpful for us when we update existing
+compile rules for new versions of the specification.
+
+The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
+For a given failed step $T$ and the size of a failed input $n$, it
+attempts to find a set of the most specific suggestions.  It
+substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
+special token \( \tstar \), which represents some sub-sequence of a
+failed step.  It collects a set of possible suggestions, and then
+removes more general ones than existing suggestions.  To support this
+process, we added a parsing rule  \( \code{starT} \) to each compile
+rule as follows:
+\begin{lstlisting}[style=myScalastyle]
+// statements
+val Stmt = ... | starT ^^ { case x => Dummy("Stmt") }
+// expressions
+val Expr = ... | starT ^^ { case x => Dummy("Expr") }
+\end{lstlisting}
+where \( \code{starT} \) is a special basic token parser that just
+checks whether a given token is the special token \( \tstar \). 
+Its corresponding conversion rule is a function that returns a dummy
+\( \ires \) component \( \code{Dummy} \) with a string value that
+represents the name of its compile rule.
+
+For example, let us assume that the \( \code{Expr} \) compile rule
+does not have the alternative for lists:
+\begin{lstlisting}[style=myScalastyle]
+  "<<" ~ repsep(varT, ",") ~ ">>" ^^
+       { case _ ~ x ~ _ => EList(e) } // lists
+\end{lstlisting}
+Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
+When we use the fault localization algorithm with the failed step and
+its size 15, it first finds one suggestion for statements and four
+suggestions for expressions as follows:
+\[
+\footnotesize
+\! \! \! \!
+  \begin{array}{c}
+    (\scode{"Stmt"}, 0, 14), \;
+    (\scode{"Expr"}, 3, 13), \;
+    (\scode{"Expr"}, 4, 13), \;
+    (\scode{"Expr"}, 6, 12), \;
+    (\scode{"Expr"}, 10, 12)
+  \end{array}
+\]
+In the \textbf{\small while} loop on lines 9--11, because the last one
+is the most specific sub-sequence, it removes the other four
+suggestions. Finally, the rule assistant suggests to define another
+expression compile rule for the token list \hint{}.

### 2019-08-20 icse/compiler.tex
Small changed for Section 4

@@
 is written in extended Scala parser combinators.  We modified the
-meaning of the alternative composition operator ( \( | \) ) to collect
+meaning of the alternative composition operator ( \( ||| \) ) to collect
 all the longest matched results.  If a parser detects a step that
@@
 val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
-val Expr = (          // expressions
-  varT ^^ ... |       // identifiers
-  "?" ~ Expr ^^ ... | // return if abrupt
+// expressions
+val Expr =
+  // identifiers        // return if abrupt
+  varT      ^^ ... |||  "?" ~ Expr      ^^ ... |||
   // function calls
-  word ~ "(" ~ repsep(Expr, ",") ~ ")" ^^ ... |
-  "<<" ~ repsep(varT, ",") ~ ">>" ^^ ...  // lists
-)
+  word ~ "(" ~ repsep(Expr, ",") ~ ")"  ^^ ... |||
+  // lists
+  "<<" ~ repsep(varT, ",") ~ ">>"       ^^ ...
 \end{lstlisting}
@@
 val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
-val Expr = (               // expressions
-  ... ^^ { x => EId(x) } | // identifiers
-                           // return if abrupt
-  ... ^^ { _ ~ e => EReturnIfAbrupt(e) } |
+// expressions
+val Expr =
+  // identifiers   // return if abrupt
+  ... ^^ EId |||   ... ^^ { _ ~ e => EAbrupt(e) } |||
   // function calls
-  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) } |
-  ... ^^ { case _ ~ x ~ _ => EList(e) } // lists
+  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }    |||
+  // lists
+  ... ^^ { case _ ~ x ~ _ => EList(e) }
 )
@@
 environment records are represented as \( \code{Record} \)
-with string values as keys and addresses as values.  Each key
-represents an identifier name and its corresponding address represents
-an ECMAScript object.  We also represent constants in the ECMAScript
-specification such as \( \code{empty} \) and \( \code{normal} \) as
-\( \code{Singleton} \) data types in \( \ires \).
+from string values into addresses that represents other type of
+\( \code{Record} \) for bindings.  We also represent constants
+in the ECMAScript specification such as \( \code{empty} \)
+and \( \code{normal} \) as \( \code{Singleton} \) data types
+in \( \ires \).
 \end{itemize}
@@
 // statements
-val Stmt = ... | starT ^^ { case x => Dummy("Stmt") }
+val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
 // expressions
-val Expr = ... | starT ^^ { case x => Dummy("Expr") }
+val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
 \end{lstlisting}

### 2019-08-20 icse/compiler.tex
Typo fixes

@@
 each abstract algorithm into a list of tagged tokens.  An algorithm
-consists of ordered steps and it may contain sub-steps as well.
+consists of ordered steps, and a step may contain sub-steps as well.
 For example, the \textbf{\small ToPrimitive} algorithm in
@@
 the second and fourth sub trees and converts them to \( \ires \)
-components.  The second sub-tree is converted to a string value
+instructions.  The second sub-tree is converted to a string value
 because it was constructed via the basic token parser \( \code{varT} \).
@@
 the step 2-e-i of \textbf{ToPrimitive} is converted to the following
-instruction:
+\( \ires \) instruction:
 \begin{lstlisting}[style=ires]
@@
 environment records are represented as \( \code{Record} \)
-from string values into addresses that represents other type of
+from string values into addresses that represent other types of
 \( \code{Record} \) for bindings.  We also represent constants

### 2019-08-20 icse/eval.tex
Written Section 6

@@
 \begin{figure}[t]
-  \centering
-  \begin{subfigure}{0.48\textwidth}
   \[
-      \begin{array}{c|r|r|r|r|r}
+    \begin{array}{c|r|r|r|r|r|r}
       \hline
-        \text{version}
-        & \multicolumn{1}{c|}{2016}
-        & \multicolumn{1}{c|}{2017}
-        & \multicolumn{1}{c|}{2018}
-        & \multicolumn{1}{c|}{2019}
-        & \multicolumn{1}{c}{2020}\\\hline
-        \text{\#prods}
+      \textbf{version}
+      & \multicolumn{1}{c|}{\textbf{2016}}
+      & \multicolumn{1}{c|}{\textbf{2017}}
+      & \multicolumn{1}{c|}{\textbf{2018}}
+      & \multicolumn{1}{c|}{\textbf{2019}}
+      & \multicolumn{1}{c|}{\textbf{2020}}
+      & \multicolumn{1}{c}{\textbf{avg.}}\\\hline
+      \text{\# lexical prod.}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}\\\hline
+      \text{\# syntactic prod.}
       & \text{\inred{XXX}}
       & \text{\inred{XXX}}
-        & \text{\inred{XXX}}
-        & \text{\inred{XXX}}
-        & \text{\inred{XXX}}\\\hline
-        \Delta
-        & \multicolumn{1}{c|}{\text{-}}
       & \text{\inred{XXX}}
@@
   \]
-    \caption{The parser generator.}
+  \[
+    \begin{array}{c|r|r|r|r|r}
+      \hline
+      \textbf{old version}
+      & \multicolumn{1}{c|}{\textbf{2016}}
+      & \multicolumn{1}{c|}{\textbf{2017}}
+      & \multicolumn{1}{c|}{\textbf{2018}}
+      & \multicolumn{1}{c|}{\textbf{2019}}
+      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
+      \textbf{new version}
+      & \multicolumn{1}{c|}{\textbf{2017}}
+      & \multicolumn{1}{c|}{\textbf{2018}}
+      & \multicolumn{1}{c|}{\textbf{2019}}
+      & \multicolumn{1}{c|}{\textbf{2020}}
+      & \\\hline
+      \Delta \; \text{\# lexical prod.}
+      & \text{\inred{X}}
+      & \text{\inred{X}}
+      & \text{\inred{X}}
+      & \text{\inred{X}}
+      & \text{\inred{X}}\\\hline
+      \Delta \; \text{\# syntactic prod.}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}
+      & \text{\inred{XX}}\\\hline
+    \end{array}
+  \]
+  \caption{The number of productions for lexical and
+  syntactic grammars in ECMAScript specifications.}
   \label{fig:syntax-all-version}
-  \end{subfigure}
-  \begin{subfigure}{0.48\textwidth}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \begin{subfigure}{0.23\textwidth}
     \includegraphics[width=\textwidth]{img/all-version-sem.png}
-    \caption{The algorithm compiler.}
+    \caption{Evaluation results for each version}
     \label{fig:semantics-all-version}
   \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.20\textwidth}
+    \includegraphics[width=\textwidth]{img/all-version-sem-delta.png}
+    \caption{Evaluation results for each difference of adjacent versions}
+    \label{fig:semantics-all-version-delta}
+  \end{subfigure}
   \caption{The result of the parser generator and the algorithm compiler for
-  ECMAScript specifications from 2016 to 2020.}
+  ECMAScript specifications.}
   \label{fig:all-version}
@@
 Thus, we evaluate only five recent versions from ECMAScript 2016 to 2020.
-As described in Figure~\ref{fig:all-version}, \( \tool \) suceeds to generate parsers
-from all versions. For semantics, the algorithm compiler has \inred{XX\%} success rates
-in average. Moreover, \( \tool \) are also effective to update existing semantics
-because \inred{XX\%} of newly defined algorithms are automatically compiled into \( \ires \)
-functions.
+
+First, we evaluate that the \textsf{Parser Generator} in \( \tool \) successfully generate
+parsers from all target versions of ECMAScript specifications. As described in
+Figure~\ref{fig:syntax-all-version}, lexical and syntactic grammars
+have \inred{XX} and \inred{XXX} productions in average, respectively.
+Moreover, JavaScript syntax are annually updated of \inred{X} productions for lexical grammars
+and \inred{XX} productions for syntactic grammars in average.
+
+Figure~\ref{fig:all-version} shows the evaluation results for semantics.
+The \textsf{Algorithm Compiler} with the compile rules described in Section~\ref{sec:impl}
+has \inred{XX\%} success rates for existing specifications in average. Moreover,
+\( \tool \) are also effective to update existing semantics
+because \inred{XX\%} of changed or newly defined algorithms are automatically
+compiled into \( \ires \) functions. Thus, we believe that \( \tool \) effectively
+reduce the effort to extract syntax and semantics of JavaScript
+not only when developing them from the scratch, but also updating existing syntax and semantics.
 
@@
     Annexes/Internationalisation & 1,774\\ \hdashline
-    In-progress features & \inred{XXXX} \\\hdashline
-    Module tests & \inred{XXXX} \\\hdashline
-    Non-strict tests & \inred{XXXX} \\\midrule
+    In-progress features & \inred{XXXX} \\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Strict Script Tests} & \textbf{\inred{XXXXX}} \\
+    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{\inred{XXXXX}} \\
     \aboverulesepcolor{gainsboro}\midrule
-    Not supported features & \inred{XXXX} \\\midrule
+    Non-strict codes & \inred{XXXX}\\\hdashline
+    \code{Math}, \code{Date}, \code{RegExp}, and \code{JSON} & \inred{XXXX} \\\hdashline
+    Modules & \inred{XXXX} \\\midrule
     \belowrulesepcolor{gainsboro}
@@
     \aboverulesepcolor{gainsboro}\midrule
+    Not-yet modeled & \inred{XXXX} \\\hdashline
     Passed tests & \inred{XXXX} \\\hdashline
@@
 
-To evaluate that \( \tool \) correctly extracts semantics, we extract semantics of ECMAScript
-2020 via our tool. Above automatically extracted parts of semantics, we manually implement
-\inred{XX} \( \ires \) functions for abstract algorithms failed to be automatically compiled.
-Moreover, we fill in global setting based on ECMAScript 2020 specification as described
-in Section~\ref{sec:impl}. The ECMAScript 2020 version is actively updated in
-GitHub~\cite{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
-officially provides the conformance test suite, test262, for ECMAScript 2020.
-Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
-However, the test262 also provides tests for in-progress features and other extensions
-such as web browsers and internationalisation. Thus, we exclude them from our target tests.
+To evaluate that \( \tool \) correctly extracts semantics, we develop the JavaScript
+interpreter based on the extracted syntax and semantics from ECMAScript 2020.
+Among \inred{XXXX} algorithms in ECMAScript 2020, \inred{XXX} algorithms
+are related to the not-supported language features. And \inred{XXXX} algorithms
+are automatically compiled into \( \ires \) functions via the \textsf{Algorithm Compiler}.
+Among remaining \inred{XXX} algorithms, we select \inred{XX} algorithms
+essential parts of overall semantics and manually implement corresponding \( \ires \)
+functions. As described in Section~\ref{sec:impl}, we also
+carefully implement \textsf{Global Setting}.
+
+We test our JavaScript interpreter based on test262, the conformance test suite
+that is officially provided by the committee TC39. However, the current version of
+test262 also provides tests for other extensions or in-progress features.
+Thus, we exclude them to focus on only the semantics of ECMAScript 2020.
 Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
@@
 test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
-for extensions and in-progres features. Then, we remove tests for non-strict mode because
-we focus on only JavaScript codes in strict mode
-as described in Section~\ref{sec:impl}. Finally, we remove the \inred{XXXX} tests
-for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
-We test our extracted semantics for \inred{XXXXX} applicable tests and pass \inred{XXXX} tests.
-There are several reasons of test failures; \inred{...}.
+for extensions and in-progres features. We also remove \inred{XXXX} tests for
+not-supported features; non-strict codes, intricate built-in objects, and modules.
+Finally, we tested \inred{XXXXX} applicable tests with our JavaScript interpreter.
+Among them, \inred{XXXXX} tests are successfully passed and all other tests are
+not passed just because of not yet modeled abstract algorithms. It means that
+all semantics extracted from \( \tool \) are perfectly correct.
+
+% TODO if some tests are failed, categorize them and explain why they are failed.
 
@@
 ECMAScript specifications are managed as open-sources and proposals of in-progress language
-features follow the TC39 process and are tracked in the separated repository~\cite{proposals}.
-Thare are five stages for proposals; Stage from 0 to 3, and finished or inactive proposals.
-The committee (TC39) regularly examins the proposals in Stage 3 and changes the stage into
-finished if its members decide to apply it into official specifications. Otherwise, the committee
-changes the stage of proposal into inactive. Our tool \( \tool \) is also applicable into
-not yet finished proposals and we advance \inred{a case study for a proposal} in Stage 3.
-We decide to study on proposals in Stage 3 because test262 supports tests for several
-proposals in Stage 3.
+features by following the TC39 process. Such proposals are tracked in the separated repository~\cite{proposals}
+and thare are six different stages for them; Stage from 0 to 3, and finished or inactive proposals.
+Each proposal starts with Stage 0 and is promoted into Stage 3 through Stage 1 and 2.
+The committee (TC39) regularly examins the Stage 3 proposals to decide their next stages.
+If the proposals are confirmed, the committee changes their stages into finished
+and integrate them into the next version of ECMAScript specification.
+Otherwise, the committee changes them into inactive. Our tool \( \tool \) is also applicable
+into not yet finished proposals and we advance a case study for a Stage 3 proposal.
 
-\inred{...}
+The optional chain syntax (\( \code{?.} \)) is one of Stage 3 proposals that removes the
+boilerplate codes; \( \code{x \&\& x.p} \). The code first checks that the value of
+the variable \( \code{x} \) is not \( \code{undefined} \) and then access its
+property \( \code{p} \). With the optional chain syntax, we could redece the code size
+by implementing as \( \code{x?.p} \). We apply this proposal into ECMAScript 2020 specification
+and evaluate \( \tool \) to extract the semantics from the extended specification.
+For the extended speicification, the \textsf{Parser Generator} successfully handle
+three updated lexical productions and three updated syntactic productions.
+For semantics, there 22 updated abstract algorithms. At the first attempt,
+the \textsf{Algorithm Compiler} suceedes to compile only 10 algorithms.
+However, we notice that several algorithm steps have diffrent styles with
+the existing ECMAScript specifications. Thus, we revise them into the original
+writing styles and report the revision into the GitHub repository of the proposal.
+The authors of this proposal approved and accepted our pull requests.
+After revisions, 21 of 22 algorithms are successfully compiled and we manually
+compile only one algorithm. In the test262, there are 33 tests related to the optional chain
+syntax and six tests of them are semantics tests. The semantics extracted with
+the optional chain proposal successfully pass all the six semantics tests.
+This case study shows the adaptability of \( \tool \) for future language features
+and also \( \tool \) might be possible to be used as a specification writing guidance.
 
@@
 
-We found four specification errors in ECMAScript 2020 via \( \tool \).
+We found three specification errors in ECMAScript 2020 via \( \tool \).
 We fixed them and sent pull requests into the official GitHub repository of
@@
 The \textbf{VarScopedDeclarations} algorithm is used to initially define
-the variable declarations before entering speicific scopes. However, the iteration syntax
-\( \code{for await (} \; \textit{LeftHandSideExpression} \; \code{of} \;
-\textit{AssignmentExpression} \; \code{)} \; \textit{Statement} \)
-has two different \textbf{VarScopedDeclarations} algorithms.
-In \( \tool \), the spec extractor detects such duplications.
+the variable declarations before entering speicific scopes.
+However, the following iteration syntax has two different
+\textbf{VarScopedDeclarations} algorithms:
+\[
+  \code{for await (} \; \textit{LeftHandSideExpression} \; \code{of} \;
+\textit{AssignmentExpression} \; \code{)} \; \textit{Statement}
+\]
+The \textsf{Spec Extractor} of \( \tool \) detects its duplicated
+semantics during automatically extracting abstract algorithms into JSON files.
 
-For the \textbf{ExpectedArgumentCount} syntax-directed algorithm, we found that
+For the \textbf{ExpectedArgumentCount} algorithm, we found that
 there are missing cases for some syntax. This algorithm counts the number of
@@
 
-Moreover, we found an error in \textsf{Ecmarkup}, a toolchain used to specify ECMAScript
-and render the raw specification HTML files.
-At the first time, we though that we found a missing case for the \textbf{IsFunctionDefinition}
-algorithm of unnamed function expressions. However, in the raw specification HTML file,
-there are no missing cases. We investigate why it happens and realize that \textsf{Ecmarkup}
-itself has a bug to silently remove the {\small opt} subscript in
-\( \code{collapsed} \) syntax mode. Thus, unnamed functions are not described
-in the rendered HTML file.
+Moreover, we found an error in \textsf{Ecmarkup}, a toolchain used to
+specify ECMAScript and beautify a raw speicification HTML file
+into a more visible HTML file. At the first time, we though that
+we found a missing case for the \textbf{IsFunctionDefinition}
+algorithm of unnamed function expressions. However, in the
+raw specification HTML file, there are no missing cases. We investigate
+why it happens and realize that \textsf{Ecmarkup} itself has
+a bug to silently remove the {\small opt} subscript in \( \code{collapsed} \)
+syntax mode. It is already discovered bug but our tool found this bug
+in a mechanical way.

### 2019-08-20 icse/impl.tex
Till Sec. 5

@@
 \section{Implementation}\label{sec:impl}
+In this section, we describe the implementation detail of \( \tool \),
+which is an open-source project\footnote{The URL of the tool is anonymized
+due to a double-blind review process.}.
 
-In this section, we demonstrate the implementation detail of \( \tool \).
-We target to extract JavaScript syntax and semantics from
+Our goal is to extract the JavaScript syntax and semantics from the
 ECMAScript 2020 specification.  It is the next ECMAScript version
-that is actively updated in GitHub repository~\cite{es2020}
+that is actively updated in its GitHub repository~\cite{es2020}
 to be released in the next year.  Moreover, Ecma Technical Committee 39 (TC39)
@@
 \subsection{Excluded Language Features}
-We decide to not support several language features in ECMAScript 2020:
+We decided not to support the following language features in ECMAScript 2020:
 
 \paragraph{No-Strict Mode}
-Since ECMAScript 5, JavaScript introduced strict mode to \textit{intentianally} provide
-slightly different semantics. It provides more stable semantics by preventing
-unsafe actions or throwing originally ignored errors.
-However, ECMAScript specification says:
-``Strict mode does not restrict or modify any aspect of the ECMAScript semantics
-that must operate consistently across multiple source text units.''
-Thus, we decide to only support strict mode JavaScript to reduce the labors.
+Since ECMAScript 5, JavaScript introduced strict mode to
+\textit{intentionally} provide slightly different semantics.  It
+provides more stable semantics by preventing unsafe actions or
+throwing originally ignored errors.  However, the ECMAScript
+specification states that ``Strict mode does not restrict or modify
+any aspect of the ECMAScript semantics that must operate consistently
+across multiple source text units.''  Thus, we decided to support only
+strict mode of JavaScript to focus on the main contribution of this
+paper.
 
-\paragraph{Intricate Built-ins}
-JavaScript provides various built-in object to support helper functions in standard.
-However, several built-in libraries are orthogonal but labor-intensive
-to be manually modeled. Thus, we decide to not support
-four orgothonoal libraries; \( \code{Math} \), \( \code{Date} \),
+\paragraph{Intricate Built-in Objects}
+JavaScript provides various standard built-in objects to support
+helper functions.  However, several built-in libraries require
+labor-intensive manual modeling without adding any technical
+contribution to this paper.  Thus, we decided not to support
+four such libraries: \( \code{Math} \), \( \code{Date} \),
 \( \code{RegExp} \), and \( \code{JSON} \).
@@
 \paragraph{Modules}
-Moreover, we also do not support modules introduced since ES6 (ECMAScript 2015).
-With the \( \code{import} \) keyword, a JavaScript program
-imports other JavaScript components defined with the \( \code{export} \)
-keyword in modules. In order to support modules in semantics, we should
-model the functionality to communicate with file system to access
-JavaScript module files. However, modules do not critically affect
-the overall semantics. Thus, we decide to not support modules.
+Moreover, we do not support modules that were introduced since ES6
+(ECMAScript 2015).  With the \( \code{import} \) keyword, a JavaScript
+program can import other JavaScript components defined with the \(
+\code{export} \) keyword in their modules.  In order to support
+modules in our automatically generated semantics, we should model the
+functionality to communicate with file systems to access JavaScript
+module files.  Because modules do not affect the overall JavaScript
+semantics critically, we decided not to support modules.
 
-\subsection{Comple Rules for ECMAScript}
+\subsection{Compile Rules for ECMAScript}
 
-\begin{table}
+\begin{table}[t]
   \centering
+  \caption{Compile rules in ECMAScript 2020}
+  \label{table:rules}
+\vspace*{-1em}
   \[
@@
   \]
-  \caption{The compile rules for ECMAScript specifications.}
-  \label{table:rules}
 \end{table}
 
-The \textsf{Algorithm Compiler} requires compile rules to compile
-given abstract algorithms into \( \ires \) functions.
-We define compiler rules for ECMAScript specifications
-and Table~\ref{table:rules} describes them.
-The statement compile rule \( \code{Stmt} \) contains
-\inred{XX} compile rules and generates \( \ires \) instructions.
-The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \)
-compile rules denote expressions, conditions, and values, respectively.
-While all of them generates \( \ires \) expressions,
-we discriminate them because they have different use cases.
-The \( \code{Ty} \) denotes type names and generates
-string primitives in \( \ires \). The \( \code{Ref} \)
-represents the references including identifiers lookups or
-member accesses of map-like structures. It generates
-\( \ires \) reference expressions.
-Finally, the Section number \( \code{SecNo} \) compile rule
-represents sections numbers such as \( \code{9.4.1.1} \),
-and it converts such numbers into the corresponding name strings
-such as \( \code{"BoundFunctionObject.Call"} \).
+As we discussed in Section~\ref{sec:compiler}, \textsf{Algorithm Compiler}
+requires compile rules to compile given abstract algorithms to \( \ires \)
+functions.  In order to cover the entire ECMAScript 2020 specification,
+we defined compile rules for only seven kinds as summarized in
+Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
+contains \inred{XX} compile rules and generates \( \ires \) instructions.
+The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \) compile
+rules denote expressions, conditions, and values, respectively.  While
+all of them generate \( \ires \) expressions, they represent different
+contexts in the ECMAScript specification.  For example,
+\( \code{Expr} \) represents a context where any expression can appear,
+\( \code{Cond} \) denotes a context where any boolean-valued expression
+can appear, and \( \code{Value} \) represents a context where a fully
+evaluated value can appear.  The \( \code{Ty} \) compile rule denotes
+type names and generates string primitives in \( \ires \).  The \( \code{Ref} \)
+represents references such as identifier lookup and member accesses of
+map-like structures.  It generates \( \ires \) reference expressions.
+Finally, the \( \code{SecNo} \) compile rule denotes section numbers
+like \( \code{9.4.1.1} \), and it converts such numbers to
+corresponding name strings like \( \code{"BoundFunctionExoticObject.Call"} \):
+\begin{lstlisting}[style=myScalastyle]
+lazy val section: P[String] = (
+  "9.4.1.1" ^^^ "BoundFunctionExoticObject.Call" |
+  ...
+) ^^ { getScalaName(_) }
+\end{lstlisting}
 
 \subsection{Global Setting}
+We manually implemented \textsf{Global Setting} for ECMAScript 2020,
+which has two parts: ECMAScript data types and built-in objects.
 
-We manually implemented \textsf{Global Setting} for ECMAScript 2020.
-It consists of the structure of built-in objects and ECMAScript data types.
+\paragraph{ECMAScript Data Types}
+In ECMAScript 2020, Section 6 \textsf{ECMAScript Data Types and Values}
+describes data types used in the specification.  It describes not only
+data types explicitly exposed for JavaScript evaluation, but also all
+the internal data types used in the specification.  For example, the
+Environment Records are record types from identifiers to bindings for
+values.  They are not explicitly accessible in JavaScript programs
+but defined and used internally in the specification.
 
-\subsubsection{ECMAScript Data Types}
+Each ECMAScript data type has several fields to store their relevant values.
+We should implement such structures in order to correctly evaluate JavaScript
+programs, but fields of ECMAScript data types could be abstract algorithms.
+We call them \textit{method-like abstract algorithms} because they
+implicitly get their receiver objects as arguments at callsites.
+To mimic such implicit behaviors, we added a special variable
+\( \code{this} \) as the first parameter of a method-like abstract algorithm,
+and passed a receiver object at its callsite by modifying
+\textsf{Algorithm Compiler}.  For example, an Environment Record has
+the \textsf{DeleteBinding (N)} abstract algorithm as one of its fields.
+Then, it gets two parameters, the special parameter \( \code{this} \)
+and normal one \( \code{N} \).  Thus, the following algorithm step:
+\begin{center}
+  \includegraphics[width=0.22\textwidth]{img/method-like-example.png}
+\end{center}
+is compiled into the following \( \ires \) instruction:
+\begin{lstlisting}[style=ires]
+return DclRec.DeleteBinding(DclRec, N)
+\end{lstlisting}
 
-In ECMAScript, the Section \textsf{6 ECMAScript Data Types and Values} describes
-data types used in ECMAScript specifications. They not only represent
-data types explicitely exposed into JavaScript evaluations, but also
-represent all internal data types used in the specification.
-For example, the Environement Records are record types from identifiers
-into bindings for values. They are not explicitely accessed in JavaScript
-programs but defined internally in the specification.
+\vspace*{-.5em}
+\paragraph{Built-in Objects}
+In ECMAScript, built-in objects are pre-defined functions with several
+built-in functions.  For example, \( \code{Array} \)
+is the constructor of array objects, and its prototype
+\( \code{Array.prototype} \) has built-in functions for array objects.
+For instance, \( \code{[1,2,3].flat()} \) calls the
+\( \code{Array.prototype.flat} \) built-in function with the array
+\( \code{[1,2,3]} \).  Because built-in functions are also abstract
+algorithms, each of them is automatically converted to an \( \ires \)
+function.  However, the structures of built-in objects should be
+manually implemented.  Thus, we implemented built-in objects in Scala
+and connected their properties with the extracted \( \ires \) functions.
 
-Each ECMAScript data type consists of several fields to store relevant values.
-Thus, we should implement such structures to correctly evaluate JavaScript
-programs. Moreover, some fields of ECMAScript data types might be
-abstract algorithms. We call them as \textit{method-like abstract algorithms}
-and they have implicitly get reciever object as an argument.
-In order to mimic such implicit behaviors, we added a special variable
-\( \code{this} \) as the first parameter. And we modify algorithm compiler
-to detect cases and pass the receiver object into the method-like abstract
-algorithms. For example, an Environement Record has the \textsf{DeleteBinding (N)}
-abstract algorithm as one of its fields. Then, it has two parameters the special
-parameter \( \code{this} \) and normal one \( \code{N} \).
-The following algorithm step is compiled into the \( \ires \) instruction
-\( \code{return DclRec.DeleteBinding(DclRec, N)} \).
-\begin{center}
-  \includegraphics[width=0.3\textwidth]{img/method-like-example.png}
-\end{center}
-
-\subsubsection{Built-in Objects}
-In ECMAScript, built-in objects are pre-defined functions with several
-built-in functions. For example, the array object \( \code{Array} \)
-is the constructor of array objects, and its prototype property
-\( \code{Array.prototype} \) has built-in functions for array objects.
-For example, \( \code{[1,2,3].flat()} \) calls the
-\( \code{Array.prototype.flat} \) built-in function with the array
-\( \code{[1,2,3]} \). Built-in functions are also abstract algorithms
-thus each of them is automatically converted into an \( \ires \) function.
-However, the structured of built-in objects should be implemented manually.
-Thus, we implement built-in objects in Scala and connect their properties
-with the extracted \( \ires \) functions.
-
-Some built-in objects are named as intrinsic objects when they are
-are explicitly referenced in abstrat algorithms.
-Intrinsic objects have their own names as aliases in the table
-of the Section \textsf{6.1.7.4 Well-known Intrinsic Objects}.
-Thus, we extract such alias information into \textsf{Global Setting}
-to utilize it during evaluations.
+Some built-in objects that are explicitly referenced in abstract
+algorithms are intrinsic objects.  Intrinsic objects have their own
+aliased names summarized in Table 7 of Section 6.1.7.4
+\textsf{Well-Known Intrinsic Objects}.  We extracted the alias
+information into \textsf{Global Setting} to utilize it during evaluation.

### 2019-08-21 icse/impl.tex
Updated section number code

@@
 Finally, the \( \code{SecNo} \) compile rule denotes section numbers
-like \( \code{9.4.1.1} \), and it converts such numbers to
-corresponding name strings like \( \code{"BoundFunctionExoticObject.Call"} \):
+like \( \code{9.5.12} \), and it converts such numbers to
+corresponding name strings like \( \code{"ProxyExoticObject.Call"} \):
 \begin{lstlisting}[style=myScalastyle]
-lazy val section: P[String] = (
-  "9.4.1.1" ^^^ "BoundFunctionExoticObject.Call" |
+lazy val SecNo =
+  "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
   ...
-) ^^ { getScalaName(_) }
 \end{lstlisting}

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/package.scala
Changed default version into es2020_full

@@ -31,7 +31,7 @@ package object ase {
   val CUR_DIR = System.getProperty("user.dir")
 
   // ECMAScript model
-  val VERSION = "es2020"
+  val VERSION = "es2020_full"
 
   val DIFFLIST = List("es2016", "es2017", "es2018", "es2019", "es2020")
 

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/generator/ParserGenerator.scala
Defined getArgsN helper function

@@ -77,11 +77,9 @@ object ParserGenerator {
 
       val pre = "lazy val"
       val llpre = if (LLs.isEmpty) "" else "resolveLL"
-      val post = s"[$name] = memo {" + LINE_SEP +
-        (if (params.isEmpty)
-          s"""    case args => log($llpre("""
-        else
-          s"""    case args @ ${(params :+ "rest").mkString(" :: ")} => log($llpre(""")
+      val post = s"[$name] = memo(args => {" + LINE_SEP + (if (params.isEmpty) "" else {
+        s"""    val List(${params.mkString(", ")}) = getArgsN("$name", args, ${params.length})""" + LINE_SEP
+      }) + s"""    log($llpre("""
       nf.println(s"""  $pre $name: ESParser$post""")
       nf.print(noLLs.map {
         case (rhs, i) => getParsers(name, rhs.tokens, rhs.cond, i, false)
@@ -91,11 +89,11 @@ object ParserGenerator {
       }.mkString("," + LINE_SEP, " |" + LINE_SEP, ""))
       nf.println
       nf.println(s"""    ))("$name")""")
-      if (!params.isEmpty)
-        nf.println(s"""    case v => throw WrongNumberOfParserParams("$name", v)""")
-      nf.println(s"""  }""")
+      nf.println(s"""  })""")
     }
 
+    lazy val paramMap: Map[String, List[String]] =
+      prods.map(prod => prod.lhs.name -> prod.lhs.params).toMap
     def getParsers(name: String, tokens: List[Token], cond: String, idx: Int, isSub: Boolean): String = {
       var parser = ("MATCH" /: tokens)(appendParser(_, _)) + " ^^ { case "
       val count = tokens.count(_ match {
@@ -139,7 +137,6 @@ object ParserGenerator {
     nf.println(s"""import kr.ac.kaist.ase.AST""")
     nf.println(s"""import kr.ac.kaist.ase.core._""")
     nf.println(s"""import kr.ac.kaist.ase.parser.ESParsers""")
-    nf.println(s"""import kr.ac.kaist.ase.error.WrongNumberOfParserParams""")
     nf.println
     nf.println(s"""object Parser extends ESParsers {""")
     lexProds.foreach(getStrParser)

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/parser/ESParsers.scala

@@ -1,8 +1,9 @@
 package kr.ac.kaist.ase.parser
 
-import kr.ac.kaist.ase.{ AST, Lexical, DEBUG_PARSER, DEBUG_SEMI_INSERT, LINE_SEP }
+import kr.ac.kaist.ase.error.WrongNumberOfParserParams
 import kr.ac.kaist.ase.model.{ Script }
 import kr.ac.kaist.ase.util.Useful._
+import kr.ac.kaist.ase.{ AST, Lexical, DEBUG_PARSER, DEBUG_SEMI_INSERT, LINE_SEP }
 import scala.collection.mutable
 import scala.util.matching.Regex
 import scala.util.parsing.combinator._
@@ -152,4 +153,10 @@ trait ESParsers extends LAParsers {
 
   // all rules
   val rules: Map[String, ESParser[AST]]
+
+  // get fixed length arguments
+  def getArgsN(name: String, args: List[Boolean], n: Int): List[Boolean] = {
+    if (args.length == n) args
+    else throw WrongNumberOfParserParams(name, args)
+  }
 }

### 2019-08-21 icse/impl.tex
Revised Sec. 5

@@
 
-\paragraph{Intricate Built-in Objects}
+\paragraph{Orthogonal Built-in Objects}
 JavaScript provides various standard built-in objects to support
-helper functions.  However, several built-in libraries require
-labor-intensive manual modeling without adding any technical
-contribution to this paper.  Thus, we decided not to support
-four such libraries: \( \code{Math} \), \( \code{Date} \),
-\( \code{RegExp} \), and \( \code{JSON} \).
+helper functions.  However, several built-in libraries are orthogonal
+to the JavaScript semantics but support extra functionalities such as
+\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
+\( \code{JSON} \).  Thus, we decided not to support the four libraries.
 

### 2019-08-21 src/main/resources/es2020_full/manual/BuiltinHeap.scala
more corret modeling of builtinHeap

@@ -32,7 +32,8 @@ object BuiltinHeap {
     ("GLOBAL.String.prototype.toLocaleLowerCase", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleLowerCase")))),
     ("GLOBAL.String.prototype.toLocaleUpperCase", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleUpperCase")))),
     ("GLOBAL.Number.prototype.toLocaleString", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleString")))),
-    ("GLOBAL.Array.prototype.sort", 1, Func("", List(), None, IExpr(ENotSupported("sort"))))
+    ("GLOBAL.Array.prototype.sort", 1, Func("", List(), None, IExpr(ENotSupported("sort")))),
+    ("GLOBAL.INTRINSIC_ThrowTypeError", 0, INTRINSIC_ThrowTypeError.func)
   )
 
   private def addDesc(
@@ -240,7 +241,22 @@ object BuiltinHeap {
       nmap = NMap(
         "length" -> DataProperty(Num(0.0), F, F, T),
         "name" -> DataProperty(Str(""), F, F, T),
-        "constructor" -> DataProperty(NamedAddr("GLOBAL.Function"), T, F, T)
+        "constructor" -> DataProperty(NamedAddr("GLOBAL.Function"), T, F, T),
+        "caller" -> AccessorProperty(NamedAddr("GLOBAL.INTRINSIC_ThrowTypeError"), NamedAddr("GLOBAL.INTRINSIC_ThrowTypeError"), F, T),
+        "arguments" -> AccessorProperty(NamedAddr("GLOBAL.INTRINSIC_ThrowTypeError"), NamedAddr("GLOBAL.INTRINSIC_ThrowTypeError"), F, T)
+      ) ++ Map(
+          NamedAddr("GLOBAL.Symbol.hasInstance") -> DataProperty(NamedAddr("GLOBAL.Function.prototype[#GLOBAL.Symbol.hasInstance]"), F, F, F)
+        )
+    ),
+   "GLOBAL.Function.prototype[#GLOBAL.Symbol.hasInstance]" -> Struct(
+      typeName = "BuiltinFunctionObject",
+      imap = IMap(
+        "Prototype" -> NamedAddr("GLOBAL.Function.prototype"),
+        "Code" -> GLOBALDOTFunctionDOTprototypeDOTSYMBOL_hasInstance.func
+      ),
[…]

### 2019-08-21 src/test/scala/kr/ac/kaist/ase/GrammarDiffTest.scala
Added helper for counting grammars

@@ -1,0 +1,43 @@
+package kr.ac.kaist.ase
+
+import java.io._
+import kr.ac.kaist.ase.model._
+import kr.ac.kaist.ase.spec._
+import kr.ac.kaist.ase.util.Useful._
+import org.scalatest._
+import scala.util.Random.shuffle
+import scala.util.{ Failure, Success, Try }
+
+class GrammarDiffTest extends CoreTest {
+  // tag name
+  val tag: String = "grammarDiffTest"
+
+  def getDiffSize[A, B](old: Map[A, B], cur: Map[A, B]): Int = (0 /: cur) {
+    case (count, (k, v)) => old.get(k) match {
+      case Some(oldV) => if (oldV == v) count else count + 1
+      case None => count + 1
+    }
+  }
+
+  // registration
+  def init: Unit = {
+    val m = Map[String, Production]()
+    ((m, m) /: DIFFLIST) {
+      case ((prevLexMap, prevSynMap), version) =>
+        val spec = Spec(s"$RESOURCE_DIR/$version/auto/spec.json")
+        val Grammar(lexProds, synProds) = spec.grammar
+
+        val lexMap = lexProds.map(prod => prod.lhs.name -> prod).toMap
+        val synMap = synProds.map(prod => prod.lhs.name -> prod).toMap
+
+        val diffLexSize = getDiffSize(prevLexMap, lexMap)
+        val diffSynSize = getDiffSize(prevSynMap, synMap)
+
+        println(s"diff : $diffLexSize, $diffSynSize")
+        println(s"$version : ${lexMap.size}, ${synMap.size}")
+
+        (lexMap, synMap)
+    }
+  }
+  init
+}

### 2019-08-21 icse/eval.tex
Updated the number of grammars

@@
   \[
-    \begin{array}{c|r|r|r|r|r|r}
+    \begin{array}{c|r|r|r|r|r?r}
       \hline
@@
       & \multicolumn{1}{c|}{\textbf{2019}}
-      & \multicolumn{1}{c|}{\textbf{2020}}
+      & \multicolumn{1}{c?}{\textbf{2020}}
       & \multicolumn{1}{c}{\textbf{avg.}}\\\hline
       \text{\# lexical prod.}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}\\\hline
+      & \text{78}
+      & \text{78}
+      & \text{78}
+      & \text{81}
+      & \text{81}
+      & \text{79.2}\\\hline
       \text{\# syntactic prod.}
-      & \text{\inred{XXX}}
-      & \text{\inred{XXX}}
-      & \text{\inred{XXX}}
-      & \text{\inred{XXX}}
-      & \text{\inred{XXX}}
-      & \text{\inred{XXX}}\\\hline
+      & \text{157}
+      & \text{167}
+      & \text{167}
+      & \text{174}
+      & \text{175}
+      & \text{168}\\\hline
     \end{array}
@@
   \[
-    \begin{array}{c|r|r|r|r|r}
+    \begin{array}{c|r|r|r|r?r}
       \hline
@@
       & \multicolumn{1}{c|}{\textbf{2018}}
-      & \multicolumn{1}{c|}{\textbf{2019}}
+      & \multicolumn{1}{c?}{\textbf{2019}}
       & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
@@
       & \multicolumn{1}{c|}{\textbf{2019}}
-      & \multicolumn{1}{c|}{\textbf{2020}}
+      & \multicolumn{1}{c?}{\textbf{2020}}
       & \\\hline
       \Delta \; \text{\# lexical prod.}
-      & \text{\inred{X}}
-      & \text{\inred{X}}
-      & \text{\inred{X}}
-      & \text{\inred{X}}
-      & \text{\inred{X}}\\\hline
+      & \text{3}
+      & \text{5}
+      & \text{6}
+      & \text{0}
+      & \text{4.7}\\\hline
       \Delta \; \text{\# syntactic prod.}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}
-      & \text{\inred{XX}}\\\hline
+      & \text{140}
+      & \text{15}
+      & \text{8}
+      & \text{2}
+      & \text{55}\\\hline
     \end{array}

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/package.scala
Reverted es2016 -> es2020_full

@@ -31,7 +31,7 @@ package object ase {
   val CUR_DIR = System.getProperty("user.dir")
 
   // ECMAScript model
-  val VERSION = "es2016"
+  val VERSION = "es2020_full"
 
   val DIFFLIST = List("es2016", "es2017", "es2018", "es2019", "es2020")
 

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/package.scala
Turn off the parser debugger

@@ -37,7 +37,7 @@ package object ase {
 
   // Debugging mode
   val DEBUG_SEMI_INSERT: Boolean = false
-  val DEBUG_PARSER: Boolean = true
+  val DEBUG_PARSER: Boolean = false
   val DEBUG_INTERP: Boolean = false
 
   // display progress in tests

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/phase/FilterMeta.scala
Show filtered tests

@@ -105,75 +105,46 @@ case object FilterMeta extends PhaseObj[Unit, FilterMetaConfig, Unit] {
       "well-formed-json-stringify"
     )
 
-  lazy val test262configSummary: Test262ConfigSummary = {
-    val test262Dir = s"$TEST_DIR/test262"
-    val dir = new File(test262Dir)
-    val (normalL, errorL) = walkTree(dir).toList.filter(
-      (file) => jsFilter(file.getName)
-    ).map((x) => MetaParser(x.toString, dir.toString)).filter((x) => filter(x)).map {
-        case MetaData(name, n, _, i, _, _) => Test262Config(name, n, i)
-      }.partition(_.negative.isEmpty)
-    Test262ConfigSummary(
-      normalL.map((x) => NormalTestConfig(x.name, x.includes)),
-      errorL.collect { case Test262Config(name, Some(n), in) => ErrorTestConfig(name, n, in) }
-    )
-  }
+  val test262Dir = new File(s"$TEST_DIR/test262/test")
+  val allTests = TestList(
+    walkTree(test262Dir)
+      .toList
+      .filter(f => jsFilter(f.getName))
+      .map(x => MetaParser(x.toString, test262Dir.toString))
+  )
 
-  lazy val test262propconfigSummary: Test262ConfigSummary = {
-    val test262Dir = s"$TEST_DIR/test262"
-    val dir = new File(test262Dir)
-    val (normalL, errorL) = walkTree(dir).toList.filter(
-      (file) => jsFilter(file.getName)
-    ).map((x) => MetaParser(x.toString, dir.toString)).filter((x) => filterprop(x)).map {
-        case MetaData(name, n, _, i, _, _) => Test262Config(name, n, i)
-      }.partition(_.negative.isEmpty)
-    Test262ConfigSummary(
-      normalL.map((x) => NormalTestConfig(x.name, x.includes)),
-      errorL.collect { case Test262Config(name, Some(n), in) => ErrorTestConfig(name, n, in) }
-    )
-  }
+  def getSummary(features: List[String]): Test262ConfigSummary = allTests
+    .remove("harness", _.name startsWith "/harness")
+    .remove("internationalisation", _.name startsWith "/intl")
+    .remove("annex", _.name startsWith "/annex")
+    .remove("in-progress features", !_.features.forall(features contains _))
+    .remove("non-strict codes", m => (m.flags contains "noStrict") || (m.flags contains "raw"))
+    .remove("modules", m => (
[…]

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/util/TestConfigJsonProtocol.scala

@@ -1,4 +1,6 @@
 package kr.ac.kaist.ase.util
+
+import kr.ac.kaist.ase.parser.{ MetaParser, MetaData }
 import spray.json._
 
 case class Test262Config(name: String, negative: Option[String], includes: List[String])
@@ -13,4 +15,26 @@ object TestConfigJsonProtocol extends DefaultJsonProtocol {
   implicit val normalTestConfigFormat = jsonFormat2(NormalTestConfig)
   implicit val errorTestConfigFormat = jsonFormat3(ErrorTestConfig)
   implicit val test262ConfigFormat = jsonFormat2(Test262ConfigSummary)
+}
+
+case class TestList(list: List[MetaData]) {
+  def length: Int = list.length
+  def remove(desc: String, f: MetaData => Boolean): TestList = {
+    val (filtered, removed) = ((List[MetaData](), 0) /: list) {
+      case ((l, count), meta) =>
+        if (f(meta)) (l, count + 1)
+        else (meta :: l, count)
+    }
+    println(f"$desc%-30s: $removed tests are removed")
+    TestList(filtered.reverse)
+  }
+  def getSummary: Test262ConfigSummary = {
+    val (normalL, errorL) = list.map {
+      case MetaData(name, n, _, i, _, _) => Test262Config(name, n, i)
+    }.partition(_.negative.isEmpty)
+    Test262ConfigSummary(
+      normalL.map(x => NormalTestConfig(x.name, x.includes)),
+      errorL.collect { case Test262Config(name, Some(n), in) => ErrorTestConfig(name, n, in) }
+    )
+  }
 }

### 2019-08-21 icse/eval.tex
Updated table

@@
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794} \\
+    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Annexes/Internationalisation & 1,774\\ \hdashline
-    In-progress features & \inred{XXXX} \\\midrule
+    Annexes/Internationalisation & 1,774\\\hdashline
+    In-progress features & 5,803\\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{\inred{XXXXX}} \\
+    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict codes & \inred{XXXX}\\\hdashline
-    \code{Math}, \code{Date}, \code{RegExp}, and \code{JSON} & \inred{XXXX} \\\hdashline
-    Modules & \inred{XXXX} \\\midrule
+    Non-strict codes & 1,136\\\hdashline
+    Modules & 918 \\\hdashline
+    Negative tests & 2,280\\\hdashline
+    \code{Math}, \code{Date}, \code{RegExp}, and \code{JSON} & \inred{XXXX}\\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}} \\
+    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
     \aboverulesepcolor{gainsboro}\midrule

### 2019-08-21 icse/eval.tex
Changed Table 2

@@
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict codes & 1,136\\\hdashline
-    Modules & 918 \\\hdashline
+    Non-strict tests & 1,136\\\hdashline
+    Module tests& 918 \\\hdashline
     Negative tests & 2,280\\\hdashline
-    \code{Math}, \code{Date}, \code{RegExp}, and \code{JSON} & \inred{XXXX}\\\midrule
+    Inessential built-in objects tests & \inred{XXXX}\\\hdashline
+    Tests for not yet modeled semantics & \inred{XXXX} \\\midrule
     \belowrulesepcolor{gainsboro}
@@
     \aboverulesepcolor{gainsboro}\midrule
-    Not-yet modeled & \inred{XXXX} \\\hdashline
     Passed tests & \inred{XXXX} \\\hdashline

### 2019-08-21 icse/eval.tex
Re-order negative tests

@@
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict tests & 1,136\\\hdashline
-    Module tests& 918 \\\hdashline
-    Negative tests & 2,280\\\hdashline
+    Negative tests & 2,628\\\hdashline
+    Non-strict tests & 1,064\\\hdashline
+    Module tests& 642 \\\hdashline
     Inessential built-in objects tests & \inred{XXXX}\\\hdashline

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/phase/FilterMeta.scala

@@ -118,8 +118,9 @@ case object FilterMeta extends PhaseObj[Unit, FilterMetaConfig, Unit] {
     .remove("internationalisation", _.name startsWith "/intl")
     .remove("annex", _.name startsWith "/annex")
     .remove("in-progress features", !_.features.forall(features contains _))
-    .remove("non-strict codes", m => (m.flags contains "noStrict") || (m.flags contains "raw"))
-    .remove("modules", m => (
+    .remove("negative", !_.negative.isEmpty)
+    .remove("non-strict", m => (m.flags contains "noStrict") || (m.flags contains "raw"))
+    .remove("module", m => (
       (m.flags contains "module") ||
       (m.name startsWith "/language/module-code/") ||
       (m.name startsWith "/language/expressions/dynamic-import/") ||

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/core/syntax/Expr.scala
Removed ENotYetImpl

@@ -46,9 +46,6 @@ case class EConvert(source: Expr, target: COp, flags: List[Expr]) extends Expr
 case class EContains(list: Expr, elem: Expr) extends Expr
 case class ECopy(obj: Expr) extends Expr
 case class EKeys(mobj: Expr) extends Expr
-case class ENotYetImpl(msg: String) extends Expr {
-  override def toString: String = s"""ENotYetImpl("$msg")"""
-}
 case class ENotSupported(msg: String) extends Expr {
   override def toString: String = s"""ENotSupported("$msg")"""
 }

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/core/util/Interp.scala

@@ -405,7 +405,6 @@ class Interp {
         case (addr: Addr) => s0.keys(addr)
         case v => error(s"not an address: $v")
       }
-    case ENotYetImpl(msg) => error(s"[NotYetImpl]:${st.context.name}: $msg")
     case ENotSupported(msg) => throw NotSupported(msg)
   }
 

### 2019-08-21 src/main/scala/kr/ac/kaist/ase/algorithm/GeneralAlgoCompiler.scala
Refactored conditions

@@ -450,22 +450,17 @@ trait GeneralAlgoCompilerHelper extends AlgoCompilers {
   ////////////////////////////////////////////////////////////////////////////////
   lazy val cond: P[I[Expr]] = _cond <~ guard("," | in) | etcCond
   lazy val _cond: P[I[Expr]] = (
-    expr ~ condBOp ~ expr ^^ {
-      case (i0 ~ x) ~ ((b, n, r)) ~ (i1 ~ y) => pair(i0 ++ i1, calc(n, r, b, x, y))
-    } ||| _cond ~ (condOp <~ opt("if")) ~ _cond ^^ {
-      case (i ~ l) ~ ((op, _)) ~ (i1 ~ r) if isEmptyInsts(i1) => pair(i, EBOp(op, l, r))
-      case (i0 ~ l) ~ ((op, f)) ~ (i1 ~ r) =>
-        val temp = getTempId
-        val (t, e) = f(ISeq(i1 :+ IAssign(toRef(temp), r)))
-        pair(i0 ++ List(ILet(temp, l), IIf(toERef(temp), t, e)), toERef(temp))
-    } ||| expr ~ rep1sep(rhs, sep("or")) ^^ {
-      case (i ~ r) ~ fs => pair(i, fs.map(_(r)).reduce(EBOp(OOr, _, _)))
-    } ||| expr <~ "is strict mode code" ^^^ {
-      pair(Nil, EBool(true)) // TODO : support strict mode code
-    } | (id <~ "does not have" ~ ("a" | "an")) ~ internalName <~ ("field" | "internal slot") ^^ {
-      case x ~ y => pair(Nil, EBOp(OEq, toERef(x, y), EAbsent))
-    } ||| containsExpr
+    bopCond |||
+    condOpCond |||
+    rhsCond |||
+    strictModeCond |||
+    containsCond
   )
+
+  // binary operator conditions
+  lazy val bopCond: P[I[Expr]] = expr ~ condBOp ~ expr ^^ {
+    case (i0 ~ x) ~ ((b, n, r)) ~ (i1 ~ y) => pair(i0 ++ i1, calc(n, r, b, x, y))
+  }
   lazy val condBOp: P[(BOp, Boolean, Boolean)] = (
     ("=" | "equals") ^^^ (OEq, false, false) |||
     ("≠" | "is different from") ^^^ (OEq, true, false) |||
[…]

### 2019-08-21 icse/conclusion.tex
Till Sec. 6

@@
 based on the next version of ECMAScript specification (2020) with the official conformance test
-suite (test262). The extracted semantics passed all \inred{XXXXX} tests in test262
+suite (Test262). The extracted semantics passed all \inred{XXXXX} tests in Test262
 and we show that the tool is alo applicable into in-progress language features
-by a case study. Moreover, we found \inred{four} real specification errors via \( \tool \)
+by a case study. Moreover, we found three real specification errors via \( \tool \)
 and TC39 confirms all of them.

### 2019-08-21 icse/eval.tex
Till Sec. 6

@@
 We evaluate \( \tool \) based on the following four research questions:
-\begin{itemize}
-  \item RQ2) \textbf{Effectiveness} Is \( \tool \) effective to extract syntax and
-    semantics of existing ECMAScript specifications?
-  \item RQ1) \textbf{Correctness} Does \( \tool \) correctly extract JavaScript syntax
-    and semantics from ECMAScript 2020 speicification?
-  \item RQ3) \textbf{Adaptability} Does \( \tool \) deal with future proposed features?
-  \item RQ4) \textbf{Specification Error Detection} What specification errors
-    are detected by \( \tool \)?
+\begin{itemize}[leftmargin=0.5cm]
+\item RQ1. \textbf{Effectiveness:} Does \( \tool \) effectively reduce
+manual efforts in extracting the syntax and semantics from existing
+ECMAScript specifications? 
+\item RQ2. \textbf{Correctness:} Do the extracted syntax and semantics
+from ECMAScript 2020 behave correctly?
+\item RQ3. \textbf{Adaptability:} Is \( \tool \) applicable to
+incomplete feature proposals?
+\item RQ4. \textbf{Usefulness:} Does \( \tool \) detect any
+specification errors?
 \end{itemize}
@@
   \[
-    \begin{array}{c|r|r|r|r|r?r}
-      \hline
-      \textbf{version}
+    \begin{array}{c?r|r|r|r|r?r}
+      \textbf{Version}
       & \multicolumn{1}{c|}{\textbf{2016}}
@@
       & \multicolumn{1}{c?}{\textbf{2020}}
-      & \multicolumn{1}{c}{\textbf{avg.}}\\\hline
-      \text{\# lexical prod.}
+      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
+      \text{\# Lexical prod.}
       & \text{78}
@@
       & \text{79.2}\\\hline
-      \text{\# syntactic prod.}
+      \text{\# Syntactic prod.}
       & \text{157}
@@
       & \text{175}
-      & \text{168}\\\hline
+      & \text{168}\\
     \end{array}
@@
     \begin{array}{c|r|r|r|r?r}
-      \hline
-      \textbf{old version}
+      \textbf{Old version}
       & \multicolumn{1}{c|}{\textbf{2016}}
@@
       & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
-      \textbf{new version}
+      \textbf{New version}
       & \multicolumn{1}{c|}{\textbf{2017}}
@@
       & \multicolumn{1}{c?}{\textbf{2020}}
-      & \\\hline
-      \Delta \; \text{\# lexical prod.}
+      & \\\toprule
+      \Delta \; \text{\# Lexical prod.}
       & \text{3}
@@
       & \text{4.7}\\\hline
-      \Delta \; \text{\# syntactic prod.}
+      \Delta \; \text{\# Syntactic prod.}
       & \text{140}
@@
       & \text{2}
-      & \text{55}\\\hline
+      & \text{55}\\
     \end{array}
   \]
-  \caption{The number of productions for lexical and
-  syntactic grammars in ECMAScript specifications.}
+  \caption{Number of productions in specifications,
+from \textit{all} of which \( \tool \) automatically generated parsers}
   \label{fig:syntax-all-version}
@@
     \includegraphics[width=\textwidth]{img/all-version-sem.png}
-    \caption{Evaluation results for each version}
+    \caption{Results for different versions}
     \label{fig:semantics-all-version}
@@
     \includegraphics[width=\textwidth]{img/all-version-sem-delta.png}
-    \caption{Evaluation results for each difference of adjacent versions}
+    \caption{Results for differences between versions}
     \label{fig:semantics-all-version-delta}
   \end{subfigure}
-  \caption{The result of the parser generator and the algorithm compiler for
-  ECMAScript specifications.}
+  \caption{Number of abstract algorithms in specifications, from which
+\( \tool \) generated the JavaScript semantics}
   \label{fig:all-version}
@@
 
-We discuss the effectiveness of \( \tool \) by applying it into existing ECMAScript specifications.
-The evaluation focuses on how many productions and abstract algorithms are covered by
-our tool 1) in each version, and 2) in each difference between adjacent versions.
-Figure~\ref{fig:all-version} shows the result of \( \tool \) from ECMAScript 2016
-to 2020. While ECMAScript 5.1 is the first version that officially supports
-the specification in HTML. However, two oldest versions ECMAScript 5.1 and 2015 are written
-in quite different styles with recent versions including HTML tags used in abstract algorithms.
-Thus, we evaluate only five recent versions from ECMAScript 2016 to 2020.
+We evaluate the effectiveness of \( \tool \) by applying it to the
+most recent five versions of the ECMAScript specifications, ECMAScript
+2016 to 2020.  We measured for how many grammar productions and
+abstract algorithms \( \tool \) automatically generates parsers and
+semantics, respectively, in two respects: 1) in each version and 2) in
+each difference between adjacent versions.
 
-First, we evaluate that the \textsf{Parser Generator} in \( \tool \) successfully generate
-parsers from all target versions of ECMAScript specifications. As described in
-Figure~\ref{fig:syntax-all-version}, lexical and syntactic grammars
-have \inred{XX} and \inred{XXX} productions in average, respectively.
-Moreover, JavaScript syntax are annually updated of \inred{X} productions for lexical grammars
-and \inred{XX} productions for syntactic grammars in average.
+For syntax, we measured the number of grammar productions for which
+\textsf{Parser Generator} automatically generated parsers.  As summarized in
+Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
+syntactic grammar productions are \inred{XX} and \inred{XXX}, respectively.
+In addition, the average numbers of annually updated lexical and
+syntactic grammar productions between adjacent versions are \inred{X}
+and \inred{XX}, respectively.  We report that \( \tool \)
+automatically generated parsers for \textit{all} the productions.
 
-Figure~\ref{fig:all-version} shows the evaluation results for semantics.
-The \textsf{Algorithm Compiler} with the compile rules described in Section~\ref{sec:impl}
-has \inred{XX\%} success rates for existing specifications in average. Moreover,
-\( \tool \) are also effective to update existing semantics
-because \inred{XX\%} of changed or newly defined algorithms are automatically
-compiled into \( \ires \) functions. Thus, we believe that \( \tool \) effectively
-reduce the effort to extract syntax and semantics of JavaScript
-not only when developing them from the scratch, but also updating existing syntax and semantics.
+For semantics, we measured the number of abstract algorithms that
+\textsf{Algorithm Compiler} with the compile rules described in
+Section~\ref{sec:impl} automatically covered.
+Figure~\ref{fig:all-version} shows that \( \tool \) could
+automatically extract semantics with the \inred{XX\%} success rate on
+average for existing specifications, and \inred{XX\%} for changed or
+newly defined algorithms.  Thus, we believe that \( \tool \) effectively
+reduces the efforts to extract the syntax and semantics of JavaScript
+not only for developing them from scratch, but also for updating
+existing ones.
 
 \subsection{Correctness}
-
-\begin{table}
+\begin{table}[t]
   \centering
+  \caption{Testing results of Test262 for ECMAScript 2020}
+  \label{table:test262}
   \begin{tabular}{lr}\toprule
@@
     \aboverulesepcolor{gainsboro}\midrule
-    Negative tests & 2,628\\\hdashline
-    Non-strict tests & 1,064\\\hdashline
+    Non-strict mode tests & 1,064\\\hdashline
     Module tests& 642 \\\hdashline
-    Inessential built-in objects tests & \inred{XXXX}\\\hdashline
-    Tests for not yet modeled semantics & \inred{XXXX} \\\midrule
+    Inessential built-in object tests & \inred{XXXX}\\\hdashline
+    Non-standard negative tests & 2,628\\\midrule
     \belowrulesepcolor{gainsboro}
@@
   \end{tabular}
-  \caption{The results of tests in the test262 for ECMAScript 2020.}
-  \label{table:test262}
 \end{table}
 
-To evaluate that \( \tool \) correctly extracts semantics, we develop the JavaScript
-interpreter based on the extracted syntax and semantics from ECMAScript 2020.
-Among \inred{XXXX} algorithms in ECMAScript 2020, \inred{XXX} algorithms
-are related to the not-supported language features. And \inred{XXXX} algorithms
-are automatically compiled into \( \ires \) functions via the \textsf{Algorithm Compiler}.
-Among remaining \inred{XXX} algorithms, we select \inred{XX} algorithms
-essential parts of overall semantics and manually implement corresponding \( \ires \)
-functions. As described in Section~\ref{sec:impl}, we also
-carefully implement \textsf{Global Setting}.
+To evaluate the correctness of \( \tool \), we developed a JavaScript
+interpreter based on the extracted syntax and semantics from
+ECMAScript 2020.  Among 1,601 algorithms in ECMAScript 2020,
+\inred{XXX} algorithms are relevant to the excluded language features
+discussed in Section~\ref{sec:exclusion}, and \inred{XXXX} algorithms
+are automatically compiled via \textsf{Algorithm Compiler}.
+Among the remaining \inred{XXX} algorithms, we selected \inred{XX}
+algorithms that are essential to the core semantics and manually
+implemented their corresponding \( \ires \) functions.
 
-We test our JavaScript interpreter based on test262, the conformance test suite
-that is officially provided by the committee TC39. However, the current version of
-test262 also provides tests for other extensions or in-progress features.
-Thus, we exclude them to focus on only the semantics of ECMAScript 2020.
-Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
-semantics. We use test262 written in \inred{August 6, 2019}. In that version,
-test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
-for extensions and in-progres features. We also remove \inred{XXXX} tests for
-not-supported features; non-strict codes, intricate built-in objects, and modules.
-Finally, we tested \inred{XXXXX} applicable tests with our JavaScript interpreter.
-Among them, \inred{XXXXX} tests are successfully passed and all other tests are
-not passed just because of not yet modeled abstract algorithms. It means that
-all semantics extracted from \( \tool \) are perfectly correct.
+We tested the interpreter using Test262, the official conformance test
+suite provided by TC39, as of \inred{August 6, 2019}.  Because Test262
+contains tests for extensions and in-progress features, we excluded
+them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
+Test262 consists of 36,794 tests and we excluded 7,577 tests for
+extensions and in-progress features.  We also excluded \inred{XXXX}
+tests for excluded features and non-standard negative tests.
+Finally, we tested \inred{XXXXX} applicable tests with our JavaScript
+interpreter and they all successfully passed, which means that all the
+semantics extracted from \( \tool \) are perfectly correct.
 
-% TODO if some tests are failed, categorize them and explain why they are failed.
+% TODO if some tests failed, categorize them and explain why they failed.
 
 \subsection{Adaptability}
+We show the adaptability of \( \tool \) with one case study: applying
+it to an incomplete feature proposal.  Because ECMAScript is an open
+standard language, various proposals are available with their own
+specification changes and tests by following the TC39 process.  A
+separate repository~\cite{proposals} maintains such proposals with six
+different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
+proposal starts with Stage 0, and the TC39 committee regularly
+examines Stage 3 proposals to decide their next stages.  If a proposal
+is confirmed, the committee changes its stage to Finished and
+integrates it into the next version of the ECMAScript specification.
+Otherwise, the committee changes its stage to Inactive.  Thus, we
+applied \( \tool \) to one Stage 3 proposal.
+%https://github.com/tc39/proposal-optional-chaining
 
-We also check that \( \tool \) deals with future language features for adaptability.
-ECMAScript specifications are managed as open-sources and proposals of in-progress language
-features by following the TC39 process. Such proposals are tracked in the separated repository~\cite{proposals}
-and thare are six different stages for them; Stage from 0 to 3, and finished or inactive proposals.
-Each proposal starts with Stage 0 and is promoted into Stage 3 through Stage 1 and 2.
-The committee (TC39) regularly examins the Stage 3 proposals to decide their next stages.
-If the proposals are confirmed, the committee changes their stages into finished
-and integrate them into the next version of ECMAScript specification.
-Otherwise, the committee changes them into inactive. Our tool \( \tool \) is also applicable
-into not yet finished proposals and we advance a case study for a Stage 3 proposal.
+The optional chaining operator (\( \code{?.} \)) is one of Stage 3
+proposals that removes specific boilerplate code.  It detects a code
+pattern like \( \code{x \&\& x.p} \), which first checks that the
+value of \( \code{x} \) is not \( \code{undefined} \) and then
+accesses its property \( \code{p} \).  With the optional chaining
+operator, we can reduce code size by implementing it as \( \code{x?.p} \).
+We extended ECMAScript 2020 with this proposal and applied \( \tool \)
+to the extended specification.  We found that \textsf{Parser Generator}
+successfully handled three updated lexical productions and three
+updated syntactic productions.  For semantics, the proposal had 22
+updated abstract algorithms.  At the first attempt,
+\textsf{Algorithm Compiler} succeeded compiling only 10 algorithms.
+However, we noticed that several algorithm steps have different styles
+from existing ECMAScript specifications.  Thus, we revised them to the
+original style, sent three pull requests to the GitHub repository
+of the proposal, and the authors of the proposal accepted our pull
+requests\footnote{The URL of three pull requests are anonymized 
+due to a double-blind review process.}.  After revision, 21 of 22
+algorithms are successfully compiled and we manually compiled only one
+algorithm.  Test262 has 33 tests for the optional chaining operator
+and six of them are semantics tests.  The semantics extracted with the
+optional chaining operator proposal successfully passed all the six
+semantics tests.  This case study shows that \( \tool \) is applicable
+to future language features and it could be useful as a specification
+writing guide.
 
-The optional chain syntax (\( \code{?.} \)) is one of Stage 3 proposals that removes the
-boilerplate codes; \( \code{x \&\& x.p} \). The code first checks that the value of
-the variable \( \code{x} \) is not \( \code{undefined} \) and then access its
-property \( \code{p} \). With the optional chain syntax, we could redece the code size
-by implementing as \( \code{x?.p} \). We apply this proposal into ECMAScript 2020 specification
-and evaluate \( \tool \) to extract the semantics from the extended specification.
-For the extended speicification, the \textsf{Parser Generator} successfully handle
-three updated lexical productions and three updated syntactic productions.
-For semantics, there 22 updated abstract algorithms. At the first attempt,
-the \textsf{Algorithm Compiler} suceedes to compile only 10 algorithms.
-However, we notice that several algorithm steps have diffrent styles with
-the existing ECMAScript specifications. Thus, we revise them into the original
-writing styles and report the revision into the GitHub repository of the proposal.
-The authors of this proposal approved and accepted our pull requests.
-After revisions, 21 of 22 algorithms are successfully compiled and we manually
-compile only one algorithm. In the test262, there are 33 tests related to the optional chain
-syntax and six tests of them are semantics tests. The semantics extracted with
-the optional chain proposal successfully pass all the six semantics tests.
-This case study shows the adaptability of \( \tool \) for future language features
-and also \( \tool \) might be possible to be used as a specification writing guidance.
+\subsection{Usefulness}
+We show the usefulness of \( \tool \) with one case study:
+specification error detection.  While applying \( \tool \) to
+ECMAScript 2020, we found three specification errors.  We fixed them
+and sent pull requests to the official GitHub repository of
+ECMAScript~\cite{es2020}.  They were all confirmed by TC39
+and will be fixed in the next release \footnote{The URL of three pull
+requests are anonymized due to a double-blind review process.}.
 
-\subsection{Specification Error Detection}
+% https://github.com/tc39/ecma262/pull/1661
+% https://github.com/tc39/ecma262/pull/1662
+% https://github.com/tc39/ecma262/pull/1663
+The first error we found is an ambiguous production for
+\textit{IterationStatement}.  For some
+specific cases, the syntax-directed algorithm for
+\textbf{VarScopedDeclarations} is ambiguous.
+Our \( \tool \) detected the duplicated semantics while automatically
+extracting the abstract algorithms in JSON files.
 
-We found three specification errors in ECMAScript 2020 via \( \tool \).
-We fixed them and sent pull requests into the official GitHub repository of
-ECMAScript specification~\cite{es2020}. They were all confirmed by TC39
-and will be fixed in the next release.
+The second error is that the \textbf{ExpectedArgumentCount} algorithm
+has missing cases.  While this algorithm counts
+the number of expected arguments of given formal parameters, it does
+not cover the case with only one formal parameter in the sense that it
+does not provide any semantics for the case.  We found this error
+during evaluation of the Test262 tests under the extracted semantics
+via \( \tool \).  The interpreter threw an error because for specific
+tests no \textbf{ExpectedArgumentCount} algorithm was available.
 
-First, we found that \textbf{VarScopedDeclarations} syntax-directed algorithms of
-specific cases of \textit{IterationStatement} are ambigious.
-The \textbf{VarScopedDeclarations} algorithm is used to initially define
-the variable declarations before entering speicific scopes.
-However, the following iteration syntax has two different
-\textbf{VarScopedDeclarations} algorithms:
-\[
-  \code{for await (} \; \textit{LeftHandSideExpression} \; \code{of} \;
-\textit{AssignmentExpression} \; \code{)} \; \textit{Statement}
-\]
-The \textsf{Spec Extractor} of \( \tool \) detects its duplicated
-semantics during automatically extracting abstract algorithms into JSON files.
-
-For the \textbf{ExpectedArgumentCount} algorithm, we found that
-there are missing cases for some syntax. This algorithm counts the number of
-expected arugments of a specific parameters. However, it does not cover all
-the cases. For example, if there exists only one formal parameter,
-the ECMAScript 2020 specification does not provide any semantics.
-We detect this error during evaluations of test262 tests under
-the extracted semantics via \( \tool \). It throws an error that there
-is no \textbf{ExpectedArgumentCount} algorithm for specific tests.
-
-Moreover, we found an error in \textsf{Ecmarkup}, a toolchain used to
-specify ECMAScript and beautify a raw speicification HTML file
-into a more visible HTML file. At the first time, we though that
-we found a missing case for the \textbf{IsFunctionDefinition}
-algorithm of unnamed function expressions. However, in the
-raw specification HTML file, there are no missing cases. We investigate
-why it happens and realize that \textsf{Ecmarkup} itself has
-a bug to silently remove the {\small opt} subscript in \( \code{collapsed} \)
-syntax mode. It is already discovered bug but our tool found this bug
-in a mechanical way.
+The third error is in \textsf{Ecmarkup}~\cite{ecmarkup}, a
+toolchain that specifies ECMAScript and beautifies an HTML file with
+raw specification to a more readable one.  At first, we though we
+found a missing case for the \textbf{IsFunctionDefinition} algorithm
+of unnamed function expressions.  However, the HTML file with raw
+specification contained the corresponding case.  We investigated the
+issue and realized that \textsf{Ecmarkup} itself had a bug that
+silently removed the {\small opt} subscript in the \( \code{collapsed} \)
+syntax mode.  It was already reported in another pull request but
+\( \tool \) detected it in a mechanical way.

### 2019-08-21 icse/impl.tex
Updated table
Till Sec. 6

@@
 to be released in the next year.  Moreover, Ecma Technical Committee 39 (TC39)
-officially provides the conformance test suite, test262, for ECMAScript 2020.
+officially provides the conformance test suite, Test262, for ECMAScript 2020.
 
-\subsection{Excluded Language Features}
+\subsection{Excluded Language Features}\label{sec:exclusion}
 We decided not to support the following language features in ECMAScript 2020:
 
-\paragraph{No-Strict Mode}
+\paragraph{Non-Strict Mode}
 Since ECMAScript 5, JavaScript introduced strict mode to
@@
 paper.
-
-\paragraph{Orthogonal Built-in Objects}
-JavaScript provides various standard built-in objects to support
-helper functions.  However, several built-in libraries are orthogonal
-to the JavaScript semantics but support extra functionalities such as
-\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
-\( \code{JSON} \).  Thus, we decided not to support the four libraries.
 
@@
 
+\paragraph{Inessential Built-in Objects}
+JavaScript provides various standard built-in objects to support
+helper functions.  However, several built-in libraries are not essential
+to the core JavaScript semantics but support extra functionalities such as
+\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
+\( \code{JSON} \).  Thus, we decided not to support such libraries
+following the tradition of KJS~\cite{kjs}.
+
 \subsection{Compile Rules for ECMAScript}
-
 \begin{table}[t]
@@
   \[
-    \begin{array}{c|r|r|r|r|r|r|r}
-      \text{name}
+    \begin{array}{c?r|r|r|r|r|r|r}
+      \text{Name}
       & \multicolumn{1}{c|}{\code{Stmt}}
@@
       & \multicolumn{1}{c}{\code{SecNo}}\\\hline
-      \text{\# rules}
+      \text{\# Rules}
       & \inred{XX}
@@
       & \inred{XX}
-      & \inred{XX}\\\hline
+      & \inred{XX}
     \end{array}

### 2019-08-21 icse/intro.tex
Till Sec. 6

@@
 automatically extracted semantics passed the official conformance test
-suite, test262~\cite{test262}; out of \inred{XXXXX} tests for
+suite, Test262~\cite{test262}; out of \inred{XXXXX} tests for
 ECMAScript 2020 it passed \inred{XXXXX} tests.

### 2019-08-21 icse/main.tex
Changed filename framework.tex -> impl.tex
Written Section 6
Updated the number of grammars
Till Sec. 6

@@
 \usepackage{qtree}
+\usepackage{multirow}
 \usepackage{colortbl}
@@
 
+% thicker vertical line
+\newcolumntype{?}{!{\vrule width 1pt}}
+
 % load macros
@@
 and the automatically extracted semantics passed all \inred{XXXXX} tests 
-in test262, the official ECMAScript conformance test suite.
+in Test262, the official ECMAScript conformance test suite.
 \inred{Moreover, \( \tool \) also successfully extracts
@@
 \input{compiler}
-\input{framework}
+\input{impl}
 \input{eval}

### 2019-08-22 icse/conclusion.tex
First draft

@@
 \section{Conclusion}\label{sec:conclude}
-
-We indiciate the problem that existing JavaScript semantics are not suitable for
-annually updated cadence of ECMAScript specifications. We propose a tool \( \tool \),
-JavaScript IR-based Semantics Extraction Toolchain to mechanize extracting syntax
-and semantics from ECMAScript specifications. The most important modules are
-the parser generator and the algorithm compiler. The parser generator generates
-parsers from given \( \bnfes \) in lookahead parsers we proposed. the algorithm
-compiler compiles given abstract algorithm written in structured natural language
-into \( \ires \) functions. It is dependent on given compile rules and we provide
-general compile rules for existing ECMAScript specifications. Moroever, we also
-develop the rule assistant to diagnose root causes of not yet convertible algorithms.
-It aids to modify compile rules for specification updates. We evaluate \( \tool \)
-based on the next version of ECMAScript specification (2020) with the official conformance test
-suite (Test262). The extracted semantics passed all \inred{XXXXX} tests in Test262
-and we show that the tool is alo applicable into in-progress language features
-by a case study. Moreover, we found three real specification errors via \( \tool \)
-and TC39 confirms all of them.
+The annual updates of the ECMAScript specification makes it difficult to
+build program analysis or formal verification of JavaScript due to the
+required human efforts in modeling a moving target.  In this paper,
+we proposed a tool \( \tool \), which \emph{automatically} extracts the
+syntax and semantics specified in the ECMAScript specification.  The tool
+generates a parser from a language grammar written in \( \bnfes \), and
+compiles abstract algorithms written in English to \( \ires \) functions.
+The only parts that require manual efforts are compile rules and
+language-specific global setting, which we provide for ECMAScript
+as an example case study.  We also support a rule assistant to guide
+how to convert new abstract algorithms.  We evaluated \( \tool \) by
+applying it to ECMAScript 2020 with Test262.  The extracted semantics
+passed all \inred{XXXXX} applicable tests in Test262 and we showed
+that the tool is also applicable to an incomplete language proposal as
+a case study.  The tool also detected six confirmed errors from the
+specification and the proposal. The implementation of the tool is
+publicly available as an open-source project.

### 2019-08-22 icse/intro.tex
First draft

@@
 Because ECMAScript is an open standard language, various proposals are
-available with their own specification changes and tests.  We applied
-\( \tool \) to such proposals; out of \inred{XX} proposals, the tool
-passed all the tests in \inred{XX} proposals and partially passed the
-tests in \inred{XX} proposals.
+available with their own specification changes and tests.  As a case
+study, we applied \( \tool \) to such a proposal, during which the tool
+found some errors in the proposal.  The reported errors were all confirmed
+and the tool passed all the tests.
 \item Moreover, since the extraction mechanism of \( \tool \) is fully

### 2019-08-22 icse/main.tex
First draft

@@
 \( \ires \) functions is defined with \textit{compile rules}.
-We applied \( \tool \) to the next proposed version, ECMAScript 2020,
-and the automatically extracted semantics passed all \inred{XXXXX} tests 
-in Test262, the official ECMAScript conformance test suite.
-\inred{Moreover, \( \tool \) also successfully extracts
-semantics for \inred{XX} proposed features by adding only \inred{XX}
-minor compile rules.}
+We applied \( \tool \) to ECMAScript 2020,
+and the automatically extracted semantics passed all \inred{XXXXX}
+applicable tests in Test262, the official ECMAScript conformance test
+suite.  The tool also extracted the semantics of an incomplete proposal,
+and it detected confirmed errors in both the specification and the proposal.
 \end{abstract}

### 2019-08-22 icse/related.tex
First draft

--- 2019-08-16 icse/related.tex
@@
-\section{Related Work}
+\section{Related Work}\label{sec:related}
+Our technique is closely related to three fields: parser generation,
+automatic model generation, and formal semantics of JavaScript.
 
-Our technique is closely related by these fields: Parser generation, Automatic model generation, and Formal semantics of JavaScript.
-\subsection{Parser Generation}
-\begin{itemize}
-  \item Packrat parsing:: simple, powerful, lazy, linear time, functional pearl (ICFP'02)~\cite{packrat}
-    % left recursion 잘 안됨 / memoization으로 memory가 엄청 커짐
-    % GLL - follow가 아닌 prediction으로 사용함 / 이 방법을 적용하면 중간중간 발생하는 nondeterministic한 경우를 모두 keeping해야됨.
-    % context-sensitive token이기에 미리 parsing을 한 token이 존재하지 않기 때문에 그 다음 token이 뭔지 알 수 없어서 prediction도 하지 못함
-\end{itemize}
+From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
+parsers with backtracking support linear-time parsing.  However, it
+has the fundamental problem of ordered choices: \( ab \) is silently
+unmatched with \( a \mid ab \).  While Generalized LL (GLL) parsing~\cite{gll}
+is basically recursive-descent with backtracking that can support general
+context-free grammars (CFGs) even in the presence of ambiguous grammars,
+its worst-time complexity is \( O(n^3) \) for the input size \( n \).
+Unlike GLL parsing, our lookahead parsing is not applicable to general CFGs,
+but we experimentally showed that it can generate JavaScript parsers.
+The complexity of lookahead parsing is \( O(k \cdot n) \) for the input size
+\( n \) and the constant number of tokens \( k \).
 
-\subsection{Automatic Model Generation}
-There is similar problems in many fields. Not only language semantics, many specification is not constructed formally, so many researches are trying to
-extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
-formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses Javadoc comments of target API function with NLP techniques and various
-heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
-to find correct modeling.
-Unlike their approaches, we provides specification translation assistant to support future language update, and to provide correct meaning of specification, which also can applicable when
-testing for each primitive is unavailable so we cannot decide correct semantics automatically.
+In the field of automatic model generation, the closest related work to
+ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
+for API functions.  Using NLP techniques and various heuristic methods,
+it produces several candidate code tests them with actual implementation
+of the API functions to find correct modeling.  Unlike their approach, we
+support a specification translation assistant to support future language
+updates and to provide correct meaning of specification, which is
+applicable for testing even when the actual implementation is not available.
 
@@
 
-\subsection{Formal Semantics of JavaScript}
-
 % Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
@@
 % using it to formal verification or program analysis.
-There are also many researches to define formal semantics of JavaScript. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
-work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
-which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaScript based on ECMAScript specification, and they manually convert from specification
-to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verification and analysis. Similarly, JaVerT coverts specification
-to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
-conversion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.
+
+Several approaches have defined the formal semantics of JavaScript.
+\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
+rest as desugaring.  While it presents the core JavaScript semantics in
+an extension of the $\lambda$ calculus, it does not show the semantics
+correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
+JaVerT\citet{javert} defined formal semantics of JavaScript by manually converting
+the ECMAScript specification to their own formal languages.  KJS mapped
+ECMAScript 5 in the K framework~\cite{kframework}, which can be used
+for program verification and analysis.  Similarly, JaVerT converts the
+specification to their own IR called JSIL to make further analysis.
+Our approach provides a framework to generate converters from the
+specification to IR with a conversion assistant and layered translation
+techniques, which reduces human efforts significantly.
 

### 2019-08-23 icse/eval.tex
Updated evaluation

@@
 
-\begin{figure}[t]
+\begin{table}[t]
+  \caption{Number of productions in specifications,
+from \textit{all} of which \( \tool \) automatically generated parsers}
+  \label{fig:syntax-all-version}
   \[
@@
   \]
-  \caption{Number of productions in specifications,
-from \textit{all} of which \( \tool \) automatically generated parsers}
-  \label{fig:syntax-all-version}
-\end{figure}
+\end{table}
 
@@
   \centering
-  \begin{subfigure}{0.23\textwidth}
-    \includegraphics[width=\textwidth]{img/all-version-sem.png}
-    \caption{Results for different versions}
+  \begin{subfigure}{0.46\textwidth}
+    \includegraphics[width=\textwidth]{img/sem-all.png}
+    \caption{Results for existing versions}
     \label{fig:semantics-all-version}
@@
   \hfill
-  \begin{subfigure}{0.20\textwidth}
-    \includegraphics[width=\textwidth]{img/all-version-sem-delta.png}
-    \caption{Results for differences between versions}
+  \begin{subfigure}{0.48\textwidth}
+    \includegraphics[width=\textwidth]{img/sem-delta.png}
+    \caption{Results for differences between adjacent versions}
     \label{fig:semantics-all-version-delta}
   \end{subfigure}
-  \caption{Number of abstract algorithms in specifications, from which
+  \caption{Number of steps for abstract algorithms in specifications, from which
 \( \tool \) generated the JavaScript semantics}
@@
 2016 to 2020.  We measured for how many grammar productions and
-abstract algorithms \( \tool \) automatically generates parsers and
+steps in abstract algorithms \( \tool \) automatically generates parsers and
 semantics, respectively, in two respects: 1) in each version and 2) in
@@
 Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
-syntactic grammar productions are \inred{XX} and \inred{XXX}, respectively.
+syntactic grammar productions are 79.2 and 168, respectively.
 In addition, the average numbers of annually updated lexical and
-syntactic grammar productions between adjacent versions are \inred{X}
-and \inred{XX}, respectively.  We report that \( \tool \)
+syntactic grammar productions between adjacent versions are 4.7
+and 55, respectively.  We report that \( \tool \)
 automatically generated parsers for \textit{all} the productions.
 
-For semantics, we measured the number of abstract algorithms that
+For semantics, we measured the number of steps in abstract algorithms that
 \textsf{Algorithm Compiler} with the compile rules described in
@@
 Figure~\ref{fig:all-version} shows that \( \tool \) could
-automatically extract semantics with the \inred{XX\%} success rate on
-average for existing specifications, and \inred{XX\%} for changed or
-newly defined algorithms.  Thus, we believe that \( \tool \) effectively
+automatically extract semantics with the 91.60\% success rate on
+average for existing specifications, and 90.43\% for changed or
+newly defined steps.  Moreover, we found that algorithm steps in
+built-in libraries are less covered than other language semantics
+with 86.98\% success rates (86.09\% for updates).
+It is due to the diverse writing styles to represent
+their own specific functionalities.
+However, steps in core language semantics are covered
+with higher success rates 95.35\% (95.25\% for updates).
+
+According to this evaluation, we believe that \( \tool \) effectively
 reduces the efforts to extract the syntax and semantics of JavaScript

### 2019-08-23 icse/impl.tex
First draft
Updated number in implementation

@@
 \( \code{JSON} \).  Thus, we decided not to support such libraries
-following the tradition of KJS~\cite{kjs}.
+following the tradition of KJS~\cite{kjs}, which is a complete
+formal semantics of JavaScript.
 
@@
       \text{\# Rules}
-      & \inred{XX}
-      & \inred{XX}
-      & \inred{XX}
-      & \inred{XX}
-      & \inred{XX}
-      & \inred{XX}
-      & \inred{XX}
+      & 17
+      & 16
+      & 8
+      & 11
+      & 33
+      & 7
+      & 21
     \end{array}

### 2019-08-23 src/main/resources/es2020_full/manual/BaseGlobal.scala
fix error of ThrowTypeError Intrinsic

@@ -38,6 +38,7 @@ object BaseGlobal {
     "GetTypeOf" -> GetTypeOf.func,
     "IsArrayIndex" -> IsArrayIndex.func,
     "IsAbruptCompletion" -> IsAbruptCompletion.func,
+    "INTRINSIC_ThrowTypeError" -> NamedAddr("GLOBAL.INTRINSIC_ThrowTypeError"),
     "GLOBAL_executionStack" -> NamedAddr("executionStack"),
     "GLOBAL_jobQueue" -> NamedAddr("jobQueue"),
     "GLOBAL_context" -> Null,

### 2019-08-23 src/main/resources/es2020_full/manual/BuiltinHeap.scala

@@ -32,8 +32,7 @@ object BuiltinHeap {
     ("GLOBAL.String.prototype.toLocaleLowerCase", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleLowerCase")))),
     ("GLOBAL.String.prototype.toLocaleUpperCase", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleUpperCase")))),
     ("GLOBAL.Number.prototype.toLocaleString", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleString")))),
-    ("GLOBAL.Array.prototype.sort", 1, Func("", List(), None, IExpr(ENotSupported("sort")))),
-    ("GLOBAL.INTRINSIC_ThrowTypeError", 0, INTRINSIC_ThrowTypeError.func)
+    ("GLOBAL.Array.prototype.sort", 1, Func("", List(), None, IExpr(ENotSupported("sort"))))
   )
 
   private def addDesc(
@@ -265,6 +264,16 @@ object BuiltinHeap {
       nmap = NMap(
         "length" -> DataProperty(Num(1.0), F, F, T),
         "name" -> DataProperty(Str("[Symbol.hasInstance]"), F, F, T)
+      )
+    ),
+   "GLOBAL.INTRINSIC_ThrowTypeError" -> Struct(
+      typeName = "BuiltinFunctionObject",
+      imap = IMap(
+        "Code" -> INTRINSIC_ThrowTypeError.func
+      ),
+      nmap = NMap(
+        "length" -> DataProperty(Num(0.0), F, F, F),
+        "name" -> DataProperty(Str(""), F, F, F)
       )
     ),
     "GLOBAL.Boolean" -> Struct(

### 2019-08-23 src/main/scala/kr/ac/kaist/ase/generator/ModelGenerator.scala

@@ -51,7 +51,7 @@ object ModelGenerator {
     nf.println(s"""    globals = initGlobal,""")
     nf.println(s"""    heap = initHeap""")
     nf.println(s"""  )""")
-    nf.println(s"""  lazy val initGlobal: Map[Id, Value] = BaseGlobal.get ++ Map(""")
+    nf.println(s"""  lazy val initGlobal: Map[Id, Value] = Map(""")
     symbols.foreach {
       case (k, v) =>
         nf.println(s"""    Id("${getScalaName(k)}") -> NamedAddr("GLOBAL.$v"),""")
@@ -65,7 +65,7 @@ object ModelGenerator {
     nf.println(s"""  ) ++ Map(""")
     nf.println(consts.map(i =>
       s"""    Id("CONST_$i") -> NamedAddr("CONST_$i")""").mkString("," + LINE_SEP))
-    nf.println(s"""  )""")
+    nf.println(s"""  ) ++ BaseGlobal.get""")
     nf.println(s"""  lazy val builtinMethods: List[(String, Int, Func)] = List(""")
     nf.println(builtinMethods.map(x => {
       val obj = getScalaName(x)

### 2019-08-23 icse/conclusion.tex
Replaced \emph with \textit

@@
 required human efforts in modeling a moving target.  In this paper,
-we proposed a tool \( \tool \), which \emph{automatically} extracts the
+we proposed a tool \( \tool \), which \textit{automatically} extracts the
 syntax and semantics specified in the ECMAScript specification.  The tool

### 2019-08-23 src/main/scala/kr/ac/kaist/ase/parser/Containers.scala
Fixed error in automatic semicolon insertion

@@ -8,11 +8,13 @@ trait Containers { this: Parsers =>
   def emptyContainer: Container
   class ContainerReader[T](reader: Reader[T]) extends Reader[T] { outer =>
     val container = emptyContainer
+    val rev = List[T]()
     override def source = reader.source
     override def offset = reader.offset
     def first: T = reader.first
     def rest: Reader[T] = new ContainerReader(reader.rest) {
       override val container = outer.container
+      override val rev = outer.first :: outer.rev
     }
     def pos: Position = reader.pos
     def atEnd: Boolean = reader.atEnd

### 2019-08-23 src/main/scala/kr/ac/kaist/ase/parser/ESParsers.scala

@@ -14,20 +14,20 @@ trait ESParsers extends LAParsers {
   def emptyContainer: Container = Container()
   case class Container(
     var cache: Map[ParseCase[_], ParseResult[_]] = Map(),
-    var rightmostFailedPos: Option[Position] = None
+    var rightmostFailedPos: Option[(Position, List[Char])] = None
   )
 
   // automatic semicolon insertion
   def insertSemicolon(reader: ContainerReader[Char]): Option[String] = {
     reader.container.rightmostFailedPos match {
-      case Some(pos) =>
+      case Some((pos, rev)) =>
         val source = reader.source.toString
         val line = pos.line - 1
         val column = pos.column - 1
-        val lines = source.split('\n')
+        val lines = source.split(Array('\n', '\r'))
+        val revStr = rev.mkString
 
         if (DEBUG_SEMI_INSERT) {
-          println(source)
           lines.zipWithIndex.foreach {
             case (x, i) => println(f"$i%4d: $x")
           }
@@ -59,10 +59,7 @@ trait ESParsers extends LAParsers {
 
         // 1-1. The offending token is separated from the previous token
         //      by at least one LineTerminator
-        if (parseAll(rep(WhiteSpace), curLine.splitAt(column)._1).successful &&
-          line > 0 && !lines.splitAt(line)._1.forall {
-            case line => parseAll(rep(WhiteSpace), line).successful
-          }) return insert
+        if (!parse(strNoLineTerminator, revStr).successful) return insert
 
         // 1-2. The offending token is '}'
         if (curChar == '}') return insert
@@ -142,10 +139,10 @@ trait ESParsers extends LAParsers {
     val container = in.container
     val res = parser(in)
     (res, container.rightmostFailedPos) match {
-      case (f @ Failure(_, cur), Some(origPos)) if origPos < cur.pos =>
-        container.rightmostFailedPos = Some(cur.pos)
-      case (f @ Failure(_, cur), None) =>
-        container.rightmostFailedPos = Some(cur.pos)
+      case (f @ Failure(_, cur: ContainerReader[_]), Some((origPos, _))) if origPos < cur.pos =>
+        container.rightmostFailedPos = Some((cur.pos, cur.rev))
+      case (f @ Failure(_, cur: ContainerReader[_]), None) =>
+        container.rightmostFailedPos = Some((cur.pos, cur.rev))
       case _ =>
     }
     res

### 2019-08-23 icse20/eval.tex
Renamed directory icse -> icse20

--- 2019-08-23 icse/eval.tex
@@
   \label{fig:syntax-all-version}
+\vspace*{-1em}
+\small
   \[
@@
   \end{subfigure}
-  \caption{Number of steps for abstract algorithms in specifications, from which
+  \caption{Number of abstract algorithm steps in specifications, from which
 \( \tool \) generated the JavaScript semantics}
   \label{fig:all-version}
+\vspace*{-1em}
 \end{figure}
@@
 
-For syntax, we measured the number of grammar productions for which
-\textsf{Parser Generator} automatically generated parsers.  As summarized in
-Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
-syntactic grammar productions are 79.2 and 168, respectively.
-In addition, the average numbers of annually updated lexical and
-syntactic grammar productions between adjacent versions are 4.7
-and 55, respectively.  We report that \( \tool \)
-automatically generated parsers for \textit{all} the productions.
+%For syntax, we measured the number of grammar productions for which
+%\textsf{Parser Generator} automatically generated parsers.  
+%Table~\ref{fig:syntax-all-version} shows the number of grammar productions
 
-For semantics, we measured the number of steps in abstract algorithms that
-\textsf{Algorithm Compiler} with the compile rules described in
-Section~\ref{sec:impl} automatically covered.
-Figure~\ref{fig:all-version} shows that \( \tool \) could
-automatically extract semantics with the 91.60\% success rate on
-average for existing specifications, and 90.43\% for changed or
-newly defined steps.  Moreover, we found that algorithm steps in
-built-in libraries are less covered than other language semantics
-with 86.98\% success rates (86.09\% for updates).
-It is due to the diverse writing styles to represent
-their own specific functionalities.
-However, steps in core language semantics are covered
-with higher success rates 95.35\% (95.25\% for updates).
+For syntax, \( \tool \) automatically generated parsers for
+\textit{all} the productions.  As Table~\ref{fig:syntax-all-version} shows,
+the average numbers of lexical and syntactic productions are 79.2 and 168, respectively.
+Also, the average numbers of annually updated lexical and
+syntactic productions between adjacent versions are 4.7 and 55, respectively.
 
-According to this evaluation, we believe that \( \tool \) effectively
-reduces the efforts to extract the syntax and semantics of JavaScript
-not only for developing them from scratch, but also for updating
-existing ones.
+For semantics, Figure~\ref{fig:all-version} shows that \( \tool \)
+automatically extracted semantics with the 91.60\% success rate on
+average for existing specifications, and 90.43\% for updates.
+We found that algorithm steps in
+built-in libraries have lower success rates (86.98\% for specifications
+and 86.09\% for updates) than core language semantics (95.35\%  for specifications
+and 95.25\% for updates) because of diverse writing styles in
+describing their own specific functionalities.
+
+This results show that \( \tool \) effectively reduces the efforts to
+extract the syntax and semantics of JavaScript not only for developing
+them from scratch, but also for updating existing ones.
 
@@
   \label{table:test262}
+\vspace*{-.5em}
+\small
   \begin{tabular}{lr}\toprule
@@
   \end{tabular}
+\vspace*{-1em}
 \end{table}
@@
 standard language, various proposals are available with their own
-specification changes and tests by following the TC39 process.  A
+specification changes and tests.  A
 separate repository~\cite{proposals} maintains such proposals with six

### 2019-08-23 icse20/impl.tex
Renamed directory icse -> icse20

--- 2019-08-23 icse/impl.tex
@@
 \section{Implementation}\label{sec:impl}
-In this section, we describe the implementation detail of \( \tool \),
-which is an open-source project\footnote{The URL of the tool is anonymized
-due to a double-blind review process.}.
-
-Our goal is to extract the JavaScript syntax and semantics from the
-ECMAScript 2020 specification.  It is the next ECMAScript version
-that is actively updated in its GitHub repository~\cite{es2020}
-to be released in the next year.  Moreover, Ecma Technical Committee 39 (TC39)
-officially provides the conformance test suite, Test262, for ECMAScript 2020.
+This section describes the implementation detail of our open-source
+tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
+double-blind review process.}.  We target
+%aim to extract the syntax and semantics from 
+ECMAScript 2020, which is actively updated in its
+GitHub repository~\cite{es2020} to be released in the next year.
 
 \subsection{Excluded Language Features}\label{sec:exclusion}
-We decided not to support the following language features in ECMAScript 2020:
+We decided not to support the following ECMAScript 2020 features:
 
@@
 across multiple source text units.''  Thus, we decided to support only
-strict mode of JavaScript to focus on the main contribution of this
-paper.
+strict mode to focus on the main contribution of this paper.
 
@@
   \]
+\vspace*{-2em}
 \end{table}
@@
 Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
-contains \inred{XX} compile rules and generates \( \ires \) instructions.
+contains 17 compile rules and generates \( \ires \) instructions.
 The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \) compile
@@
 like \( \code{9.5.12} \), and it converts such numbers to
-corresponding name strings like \( \code{"ProxyExoticObject.Call"} \):
-\begin{lstlisting}[style=myScalastyle]
-lazy val SecNo =
-  "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
-  ...
-\end{lstlisting}
+corresponding name strings like \( \code{"ProxyExoticObject.Call"} \).
+% \begin{lstlisting}[style=myScalastyle]
+% lazy val SecNo =
+%   "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
+%   ...
+% \end{lstlisting}
 
@@
 \begin{center}
-  \includegraphics[width=0.22\textwidth]{img/method-like-example.png}
+  \includegraphics[width=0.2\textwidth]{img/method-like-example.png}
 \end{center}
@@
 
-\vspace*{-.5em}
+\vspace*{-1em}
 \paragraph{Built-in Objects}
@@
 and connected their properties with the extracted \( \ires \) functions.
-
+%
 Some built-in objects that are explicitly referenced in abstract
-algorithms are intrinsic objects.  Intrinsic objects have their own
+algorithms are intrinsic objects, which have their own
 aliased names summarized in Table 7 of Section 6.1.7.4
 \textsf{Well-Known Intrinsic Objects}.  We extracted the alias
-information into \textsf{Global Setting} to utilize it during evaluation.
+into \textsf{Global Setting} to utilize it during evaluation.

### 2019-08-23 icse20/parser.tex
Renamed directory icse -> icse20

--- 2019-08-19 icse/parser.tex
@@
 Therefore, the parser can visit the next alternative \( \T{a}\T{(}\T{b}\T{)} \)
-and successfully parsers the input \( \code{a(b);} \).
+and successfully parses the input \( \code{a(b);} \).
 
@@
 \), the AST generator defines the \( \code{A} \) trait and multiple
-subclasses \( \code{A}_i \) of \( \code{A} \) for \(1 \le i \le n\)
+subclasses \( \code{A}_i \) of \( \code{A} \) for \(0 \le i \le n-1\)
 that represents its alternatives.  Each class \( \code{A}_i \) has

### 2019-08-23 icse20/related.tex
Renamed directory icse -> icse20

--- 2019-08-22 icse/related.tex
@@
 correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
-JaVerT\citet{javert} defined formal semantics of JavaScript by manually converting
+JaVerT~\citet{javert} defined formal semantics of JavaScript by manually converting
 the ECMAScript specification to their own formal languages.  KJS mapped
-ECMAScript 5 in the K framework~\cite{kframework}, which can be used
+ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
 for program verification and analysis.  Similarly, JaVerT converts the
 specification to their own IR called JSIL to make further analysis.
-Our approach provides a framework to generate converters from the
-specification to IR with a conversion assistant and layered translation
-techniques, which reduces human efforts significantly.
+Our approach provides a framework to generate syntactic parsers and
+semantics compilers from the specification to \( \ires \)
+with a conversion assistant, which reduces human efforts significantly.
 

### 2019-08-23 icse20/intro.tex
Revised references

--- 2019-08-22 icse/intro.tex
@@
 specification.  While most existing formal semantics and analyzers of
-JavaScript support only ECMAScript 5.1 released in December 2009,
+JavaScript support only ECMAScript 5.1~\cite{ecma5} released in December 2009,
 from ECMAScript 6, officially dubbed ECMAScript 2015, the 
@@
 automatic, we can use it to find possible specification errors.  We
-indeed found \inred{X} possible specification errors in ECMAScript
-2020.  They were all confirmed by TC39 and will be fixed in the next
-release.
+indeed found 3 specification errors in ECMAScript 2020.  They were all
+confirmed by TC39 and will be fixed in the next release.
 \end{itemize}

### 2019-08-23 src/main/resources/es2020_full/manual/BuiltinHeap.scala
fix Construct field error

@@ -13,7 +13,7 @@ object BuiltinHeap {
     case (m, (name, Struct(ty, imap, nmap))) => ((m ++ Map(
       NamedAddr(s"$name") -> CoreMap(
         Ty(ty),
-        Model.tyMap.getOrElse(ty, Map()) ++
+        (Model.tyMap.getOrElse(ty, Map()) - Str("Construct")) ++
           imap.map +
           (Str("SubMap") -> NamedAddr(s"$name.SubMap"))
       ),
@@ -31,6 +31,7 @@ object BuiltinHeap {
     ("GLOBAL.String.prototype.toUpperCase", 0, Func("", List(), None, IExpr(ENotSupported("toUpperCase")))),
     ("GLOBAL.String.prototype.toLocaleLowerCase", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleLowerCase")))),
     ("GLOBAL.String.prototype.toLocaleUpperCase", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleUpperCase")))),
+    ("GLOBAL.String.prototype.localeCompare", 1, Func("", List(), None, IExpr(ENotSupported("localeCompare")))),
     ("GLOBAL.Number.prototype.toLocaleString", 0, Func("", List(), None, IExpr(ENotSupported("toLocaleString")))),
     ("GLOBAL.Array.prototype.sort", 1, Func("", List(), None, IExpr(ENotSupported("sort"))))
   )
@@ -115,7 +116,8 @@ object BuiltinHeap {
       imap = IMap(
         "Extensible" -> Bool(true),
         "Prototype" -> NamedAddr("GLOBAL.Error"),
-        "Code" -> errFunc
+        "Code" -> errFunc,
+        "Construct" -> BuiltinFunctionObjectDOTConstruct.func
       ),
       nmap = NMap(
         "name" -> DataProperty(Str(errName), F, F, T),
@@ -208,7 +210,8 @@ object BuiltinHeap {
       imap = IMap(
         "Extensible" -> Bool(true),
         "Prototype" -> NamedAddr("GLOBAL.Function.prototype"),
-        "Code" -> GLOBALDOTObject.func
+        "Code" -> GLOBALDOTObject.func,
+        "Construct" -> BuiltinFunctionObjectDOTConstruct.func
       ),
       nmap = NMap(
         "length" -> DataProperty(Num(1.0), F, F, T),
@@ -281,7 +284,8 @@ object BuiltinHeap {
[…]

### 2019-08-23 src/main/scala/kr/ac/kaist/ase/generator/ModelGenerator.scala

@@ -76,7 +76,7 @@ object ModelGenerator {
     nf.println(consts.map(i =>
       s"""    NamedAddr("CONST_$i") -> CoreSymbol(Str("CONST_$i"))""").mkString("," + LINE_SEP))
     nf.println(s"""  ) match {""")
-    nf.println(s"""    case m => ModelHelper.addBuiltin(m, builtinMethods ++ BuiltinHeap.builtinMethods)""")
+    nf.println(s"""    case m => ModelHelper.addBuiltin(m, BuiltinHeap.builtinMethods ++ builtinMethods)""")
     nf.println(s"""  })""")
     nf.println(s"""  lazy val tyMap: Map[String, Map[Value, Value]] = Map(""")
     nf.println(tys.map {

### 2019-08-23 lib/spec_extractor/es2020.js
fix length and prototype errors

@@ -77,6 +77,8 @@ SpecExtractor.loadSpec(() => {
         data.steps[6].tokens[2] = '|';
         addMethod('BitwiseORExpression1Evaluation0', length, data);
         return;
+      } else if (name == 'GLOBAL.Array.prototype.push' || name == 'GLOBAL.Array.prototype.concat' || name == 'GLOBAL.Array.prototype.unshift' || name == 'GLOBAL.Number.prototype.toString') {
+        length = 1;
       } else if (name == 'GLOBAL.Array.from') {
         data.steps[7].tokens[7].steps[4].tokens[2].steps[5].tokens[6].steps.length = 2;
       } else if (name == 'GLOBAL.Array.prototype.sort') {

### 2019-08-23 src/main/resources/es2020_full/manual/BuiltinHeap.scala

@@ -272,6 +272,8 @@ object BuiltinHeap {
    "GLOBAL.INTRINSIC_ThrowTypeError" -> Struct(
       typeName = "BuiltinFunctionObject",
       imap = IMap(
+        "Extensible" -> Bool(true),
+        "Prototype" -> NamedAddr("GLOBAL.Function.prototype"),
         "Code" -> INTRINSIC_ThrowTypeError.func
       ),
       nmap = NMap(

### 2019-08-23 icse20/eval.tex
Removed Promised.allSettled / updated numbers in Table 3

@@
     Annexes/Internationalisation & 1,774\\\hdashline
-    In-progress features & 5,803\\\midrule
+    In-progress features & 5,895\\\midrule
     \belowrulesepcolor{gainsboro}
@@
     Inessential built-in object tests & \inred{XXXX}\\\hdashline
-    Non-standard negative tests & 2,628\\\midrule
+    Non-standard negative tests & 2,280\\\midrule
     \belowrulesepcolor{gainsboro}
@@
 them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
-Test262 consists of 36,794 tests and we excluded 7,577 tests for
+Test262 consists of 36,794 tests and we excluded 7,669 tests for
 extensions and in-progress features.  We also excluded \inred{XXXX}

### 2019-08-23 src/main/scala/kr/ac/kaist/ase/phase/FilterMeta.scala

@@ -91,7 +91,6 @@ case object FilterMeta extends PhaseObj[Unit, FilterMetaConfig, Unit] {
     "WeakMap",
     "WeakSet"
   ) ++ List(
-      "Promise.allSettled",
       "Object.fromEntries",
       "dynamic-import",
       "Array.prototype.flat",
@@ -118,7 +117,6 @@ case object FilterMeta extends PhaseObj[Unit, FilterMetaConfig, Unit] {
     .remove("internationalisation", _.name startsWith "/intl")
     .remove("annex", _.name startsWith "/annex")
     .remove("in-progress features", !_.features.forall(features contains _))
-    .remove("negative", !_.negative.isEmpty)
     .remove("non-strict", m => (m.flags contains "noStrict") || (m.flags contains "raw"))
     .remove("module", m => (
       (m.flags contains "module") ||
@@ -129,6 +127,7 @@ case object FilterMeta extends PhaseObj[Unit, FilterMetaConfig, Unit] {
       (m.flags contains "CanBlockIsFalse") ||
       (m.flags contains "CanBlockIsTrue")
     )).remove("locale", !_.locales.isEmpty)
+    .remove("negative", !_.negative.isEmpty)
     .getSummary
 
   lazy val test262configSummary = getSummary(standardFeatures)

### 2019-08-23 src/main/scala/kr/ac/kaist/ase/parser/ESParsers.scala
Fixed error for line terminator

@@ -24,7 +24,7 @@ trait ESParsers extends LAParsers {
         val source = reader.source.toString
         val line = pos.line - 1
         val column = pos.column - 1
-        val lines = source.split(Array('\n', '\r'))
+        val lines = source.replace("\r\n", "\n").split(Array('\n', '\r'))
         val revStr = rev.mkString
 
         if (DEBUG_SEMI_INSERT) {

### 2019-08-23 icse20/eval.tex
Updated numbers in Table 3

@@
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
+    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict mode tests & 1,064\\\hdashline
-    Module tests& 642 \\\hdashline
+    Non-strict mode tests & 1,136\\\hdashline
+    Module tests& 918 \\\hdashline
     Inessential built-in object tests & \inred{XXXX}\\\hdashline

### 2019-08-23 icse20/eval.tex
Slight updates in evaluation

@@
 interpreter based on the extracted syntax and semantics from
-ECMAScript 2020.  Among 1,601 algorithms in ECMAScript 2020,
-\inred{XXX} algorithms are relevant to the excluded language features
-discussed in Section~\ref{sec:exclusion}, and \inred{XXXX} algorithms
-are automatically compiled via \textsf{Algorithm Compiler}.
-Among the remaining \inred{XXX} algorithms, we selected \inred{XX}
-algorithms that are essential to the core semantics and manually
-implemented their corresponding \( \ires \) functions.
+ECMAScript 2020.  Among 9,657 steps in ECMAScript 2020,
+8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
+Among the remaining 731 steps, we selected 381 steps
+that are essential to the core semantics and manually
+implemented their corresponding \( \ires \) functions
+via the rule assistant introduced in Section~\ref{sec:assistant}.
+Moreover, we implement the \textsf{Global Setting} except
+the excluded language features discussed in Section~\ref{sec:exclusion}.
 
 We tested the interpreter using Test262, the official conformance test
-suite provided by TC39, as of \inred{August 6, 2019}.  Because Test262
+suite provided by TC39, as of August 6, 2019.  Because Test262
 contains tests for extensions and in-progress features, we excluded

### 2019-08-24 src/main/resources/es2020_full/manual/algorithm/EnumerateObjectPropertiesHelper.scala
Fix minor bug in EnumerateObjectPropertiesHelper

@@ -5,7 +5,7 @@ import kr.ac.kaist.ase.core._
 
 object EnumerateObjectPropertiesHelper {
   val func: Func = parseFunc(""""EnumerateObjectPropertiesHelper" ( O , listAll, listEnum ) => {
-    let a = (map-keys O["SubMap"])
+    app a = (O.OwnPropertyKeys O)
     let __x0__ = 0i
     while (< __x0__ a.length) {
       let c = a[__x0__]

### 2019-08-24 icse20/conclusion.tex
Updated final numbers

--- 2019-08-23 icse/conclusion.tex
@@
 applying it to ECMAScript 2020 with Test262.  The extracted semantics
-passed all \inred{XXXXX} applicable tests in Test262 and we showed
+passed 19,220 of 19,282 applicable tests in Test262 and we showed
 that the tool is also applicable to an incomplete language proposal as

### 2019-08-24 icse20/eval.tex
Updated final numbers

@@
     Module tests& 918 \\\hdashline
-    Inessential built-in object tests & \inred{XXXX}\\\hdashline
-    Non-standard negative tests & 2,280\\\midrule
+    Early error tests & 1,316\\\hdashline
+    Inessential built-in object tests & 6,473\\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
+    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Passed tests & \inred{XXXX} \\\hdashline
-    Failed tests & \inred{XXXX} \\\bottomrule
+    Passed tests & 19,220 \\\hdashline
+    Failed tests & 62 \\\bottomrule
   \end{tabular}
@@
 Test262 consists of 36,794 tests and we excluded 7,669 tests for
-extensions and in-progress features.  We also excluded \inred{XXXX}
-tests for excluded features and non-standard negative tests.
-Finally, we tested \inred{XXXXX} applicable tests with our JavaScript
-interpreter and they all successfully passed, which means that all the
-semantics extracted from \( \tool \) are perfectly correct.
+extensions and in-progress features.  We also filtered out
+tests for excluded features described in Section~\ref{sec:impl}.
+Finally, we tested 19,282 applicable tests with our JavaScript
+interpreter and only 62 tests are failed. Among them, 54 tests
+utilize implementation-dependent features and 3 tests are timeout
+and 5 tests are wrong tests. Thus, we believe that all the
+semantics extracted from \( \tool \) are correct.
 

### 2019-08-24 icse20/impl.tex
Updated final numbers

@@
 semantics critically, we decided not to support modules.
+
+\paragraph{Early Errors}
+ECMAScript specifications declare their syntax not only using
+\( \bnfes \) but also using Early Error Rule to violate invalid codes
+before evaluations. For example, an Early Error Rule checks whether
+functions have duplicated parameters in strict mode. However,
+there are written in natural languages with differenet styles
+with abstract algorithms. Thus, we do not support Early Error Rules.
 

### 2019-08-24 icse20/intro.tex
Updated final numbers

@@
 automatically extracted semantics passed the official conformance test
-suite, Test262~\cite{test262}; out of \inred{XXXXX} tests for
-ECMAScript 2020 it passed \inred{XXXXX} tests.
+suite, Test262~\cite{test262}; out of 19,282 tests for
+ECMAScript 2020 it passed 19,220 tests.
 \item \( \tool \) is also applicable to new language features proposed

### 2019-08-24 icse20/main.tex
Renamed directory icse -> icse20
Updated final numbers

--- 2019-08-22 icse/main.tex
@@
 We applied \( \tool \) to ECMAScript 2020,
-and the automatically extracted semantics passed all \inred{XXXXX}
+and the automatically extracted semantics passed 19,220 of 19,282
 applicable tests in Test262, the official ECMAScript conformance test
 suite.  The tool also extracted the semantics of an incomplete proposal,
-and it detected confirmed errors in both the specification and the proposal.
+and it detected three errors from the specification and they were all
+confirmed.
 \end{abstract}
@@
 
+\normalem
 \bibliographystyle{ACM-Reference-Format}

### 2019-08-24 src/test/scala/kr/ac/kaist/ase/Test262Test.scala
remove println in test262Test

@@ -95,7 +95,6 @@ class Test262Test extends ASETest {
       if ((!(noParseSet contains name)) && ((!PREVDIFF) || (failedSet contains name.replace("//", "/").split("test/").last))) check("Test262Eval", name, {
         val jsConfig = aseConfig.copy(fileNames = List(jsName))
 
-        println(name)
         val ast = Parse((), jsConfig)
         ModelHelper.checkSupported(ast)
 

### 2019-08-24 icse20/conclusion.tex
First submission

@@
 passed 19,220 of 19,282 applicable tests in Test262 and we showed
-that the tool is also applicable to an incomplete language proposal as
-a case study.  The tool also detected six confirmed errors from the
+that the tool is also applicable to an incomplete language proposal.
+The tool also detected six confirmed errors from the
 specification and the proposal.  The implementation of the tool is

### 2019-08-24 icse20/eval.tex
First submission

@@
 \vspace*{-.5em}
-\small
+\footnotesize
   \begin{tabular}{lr}\toprule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
+    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
     \aboverulesepcolor{gainsboro}\midrule
@@
 tests for excluded features described in Section~\ref{sec:impl}.
-Finally, we tested 19,282 applicable tests with our JavaScript
-interpreter and only 62 tests are failed. Among them, 54 tests
-utilize implementation-dependent features and 3 tests are timeout
-and 5 tests are wrong tests. Thus, we believe that all the
+Finally, we tested 19,282 applicable tests and only 62 tests failed.
+Among them, 54 tests utilize implementation-dependent features,
+three are timeout with 20 minutes due to enormous computation,
+and five are wrong tests.  Thus, we believe that all the
 semantics extracted from \( \tool \) are correct.

### 2019-08-24 icse20/impl.tex
First submission

--- 2019-08-23 icse20/impl.tex
@@
 \section{Implementation}\label{sec:impl}
-This section describes the implementation detail of our open-source
+We describe the implementation detail of our open-source
 tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
-double-blind review process.}.  We target
-%aim to extract the syntax and semantics from 
-ECMAScript 2020, which is actively updated in its
-GitHub repository~\cite{es2020} to be released in the next year.
+double-blind review process.}, which targets
+ECMAScript 2020~\cite{es2020}.
+
+%We describe how we implement an open-source \( \tool \)\footnote{
+%The URL of the tool is anonymized due to a double-blind review process.},
+%which targets ECMAScript 2020~\cite{es2020}.
 
@@
 
+\vspace*{-.5em}
 \paragraph{Non-Strict Mode}
 Since ECMAScript 5, JavaScript introduced strict mode to
-\textit{intentionally} provide slightly different semantics.  It
+provide different semantics.  It
 provides more stable semantics by preventing unsafe actions or
@@
 across multiple source text units.''  Thus, we decided to support only
-strict mode to focus on the main contribution of this paper.
+strict mode.
 
+\vspace*{-.5em}
 \paragraph{Modules}
-Moreover, we do not support modules that were introduced since ES6
-(ECMAScript 2015).  With the \( \code{import} \) keyword, a JavaScript
-program can import other JavaScript components defined with the \(
-\code{export} \) keyword in their modules.  In order to support
+Moreover, we do not support modules that were introduced since ES6.
+With the \( \code{import} \) keyword, a JavaScript
+program can import other JavaScript components.  To support
 modules in our automatically generated semantics, we should model the
@@
 
+\vspace*{-.5em}
+\paragraph{Early Errors}
+ECMAScript specifications use Early Error Rules to preclude invalid code
+before evaluation. For example, an Early Error Rule checks whether
+functions have duplicated parameters in strict mode.
+Because they are written in differenet styles from abstract algorithms,
+we do not support Early Error Rules.
+
+\vspace*{-.5em}
 \paragraph{Inessential Built-in Objects}
-JavaScript provides various standard built-in objects to support
-helper functions.  However, several built-in libraries are not essential
-to the core JavaScript semantics but support extra functionalities such as
-\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
-\( \code{JSON} \).  Thus, we decided not to support such libraries
-following the tradition of KJS~\cite{kjs}, which is a complete
-formal semantics of JavaScript.
+JavaScript provides various standard built-in objects but some of them
+are not essential to core JavaScript but support extra functionalities such as
+\( \code{RegExp} \) and \( \code{JSON} \).  Thus, we decided not to
+support such libraries following the tradition of KJS~\cite{kjs},
+which is a complete formal semantics of JavaScript.
 
@@
 
+\vspace*{-.5em}
 \paragraph{ECMAScript Data Types}

### 2019-08-24 icse20/intro.tex
temporal update

@@
 \section{Introduction}
-JavaScript is one of the widely used programming languages not only for client-side
+JavaScript is one of the most widely used programming languages not only for client-side
 but also for server-side programming~\cite{nodejs, meanjs}
@@
 Despite its popularity, JavaScript developers often suffer from its intricate semantics,
-which may cause security vulnerabilities.  For example, calling the following JavaScript
+which may cause unexpected behavior.  For example, calling the following JavaScript
 function seems to always return \( \code{false} \):
@@
 \( \code{[]} \).  To correctly understand and reason about such complex
-behaviors, the formal semantics of JavaScript is necessary.
+behavior, the formal semantics of JavaScript is necessary.
 
@@
 Moreover, manual extraction does not scale for frequent updates of the
-specification.  While most existing formal semantics and analyzers of
-JavaScript support only ECMAScript 5.1~\cite{ecma5} released in December 2009,
-from ECMAScript 6, officially dubbed ECMAScript 2015, the 
-ECMAScript specification is updated every year.  Focusing on
-ECMAScript 5.1 was reasonable until 2014, because the
+specification.  Most existing formal semantics and analyzers of
+JavaScript support only ECMAScript 5.1~\cite{ecma5} released in June 2011.
+Focusing on ECMAScript 5.1 was reasonable until 2014, because the
 specification was rarely updated.  However, in late 2014, The Ecma

### 2019-08-24 icse20/main.tex
temporal update

@@
 To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
-Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
-semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
+Extraction Toolchain. It \textit{synthesizes} a JavaScript
 parser for a given grammar written in \( \bnfes \), an extended BNF
-used in ECMAScript specifications.  It also converts each
-abstract algorithm written in a structured natural language into
-functions written in \( \ires \), an Intermediate Representation
-for ECMAScript specifications.  The compilation from algorithms to
-\( \ires \) functions is defined with \textit{compile rules}.
-We applied \( \tool \) to ECMAScript 2020,
-and the automatically extracted semantics passed 19,220 of 19,282
-applicable tests in Test262, the official ECMAScript conformance test
-suite.  The tool also extracted the semantics of an incomplete proposal,
-and it detected three errors from the specification and they were all
-confirmed.
+used in ECMAScript. It also \textit{automatically} extracts
+semantics based on rule-based compilations. Each \textit{compile rule}
+describes how to convert each abstract algorithm written in a structured natural language
+into functions written in \( \ires \), an Intermediate Representation
+for ECMAScript. \( \tool \) successfully synthesizes
+parsers and compiles 91.60\% of algorithm steps for five recent
+ECMAScript versions. We tested the extracted semantics from the next version
+ECMAScript 2020 using Test262, the official ECMAScript conformance test
+suite. It passed 19,220 of 19,282 tests and we found three specification errors
+using our tool. Moreover, we check the adaptability of \( \tool \)
+via a case study for an incomplete proposal.
 \end{abstract}
@@
   mechanized formal semantics,
-  recursive descent parsing
+  program synthesis
 }

### 2019-08-24 icse20/overview.tex
temporal update

--- 2019-08-20 icse/overview.tex
@@
 consists of three symbols: two terminal symbols \( \code{[} \) and
-\( \code{]} \) and one non-terminal symbol \textit{Elision}$_{\mbox{\footnotesize opt}}$.
+\( \code{]} \), and one non-terminal symbol \textit{Elision}$_{\mbox{\footnotesize opt}}$.
 The {\small opt} subscript denotes that it is optional.  In the second
@@
 the given \( \ires \) functions and \textit{manually} specified
-{\sf Global Setting}, which have minor but necessary information to
+{\sf Global Setting}, which has minor but necessary information to
 evaluate JavaScript programs described in the ECMAScript specification.
-For example, they include the structure of the standard built-in
-objects, name aliases for intrinsic objects, and types of abstract
-algorithms.
+They consists of the structure of the standard built-in
+objects and ECMAScript data types.
 

### 2019-08-24 icse20/main.tex
Revised abstract

@@
 used in ECMAScript. It also \textit{automatically} extracts
-semantics based on rule-based compilations. Each \textit{compile rule}
+semantics using rule-based compilation. Each \textit{compile rule}
 describes how to convert each abstract algorithm written in a structured natural language
 into functions written in \( \ires \), an Intermediate Representation
-for ECMAScript. \( \tool \) successfully synthesizes
-parsers and compiles 91.60\% of algorithm steps for five recent
-ECMAScript versions. We tested the extracted semantics from the next version
-ECMAScript 2020 using Test262, the official ECMAScript conformance test
-suite. It passed 19,220 of 19,282 tests and we found three specification errors
-using our tool. Moreover, we check the adaptability of \( \tool \)
-via a case study for an incomplete proposal.
+for ECMAScript. \( \tool \) synthesizes parsers from all \( \bnfes \) productions
+and extracts semantics from 91.60\% of algorithm steps for five recent
+ECMAScript versions. We manually extend one of the extracted semantics for
+the next version of ECMAScript 2020. It passed 19,220 of 19,282 applicable tests
+in Test262, the official ECMAScript conformance test suite. While extracting
+the semantics using \( \tool \), we found three specification errors
+and all of them are confirmed by TC 39. Moreover, we succeed to apply
+our tool into an incomplete proposal as a case study.
 \end{abstract}

### 2019-08-24 icse20/overview.tex
Revised abstract

@@
 {\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} from the
-ECMAScript specification.  Inside \( \tool \), {\sf Spec Extractor}
-extracts the JavaScript syntax to build the parser and its semantics
-to build the translator.
+ECMAScript specification.
 
@@
 using various HTML tags.  As the first step, we developed {\sf Spec Extractor}
-in JavaScript, which extracts the syntax and semantics from the
-ECMAScript specification in HTML into JSON format.
+to simply collect and save both syntax and semantics into JSON format.
+It is written in JavaScript because the ECMAScript specifications are
+provided as HTML files.
 

### 2019-08-24 icse20/compiler.tex
Slight updates in evaluation
assitant -> fault localizer

--- 2019-08-20 icse/compiler.tex
@@
 cannot be parsed with given parsing rules, it reports the step into
-{\sf Rule Assistant}.  Even when a parser parses a step successfully,
+{\sf Fault Localizer}.  Even when a parser parses a step successfully,
 it also reports the step if it can parse the step in multiple ways.
@@
 
-\subsection{Rule Assistant}
+\subsection{Fault Localizer}\label{sec:localizer}
 \begin{algorithm}[t]
@@
 
-To make it easy to write compile rules, we support a \textit{rule assistant},
+To diagnose the root cause of parsing failures, we support a \textsf{Fault Localizer},
 which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
-For each failed step, the rule assistant diagnoses a root cause of the
-parsing failure.  The basic idea is to check whether we can parse the
-failed input with the assumption that a specific sub-sequence of the
-failed step is successfully parsed.  We define an approach to find
-such sub-sequences of failed steps as \textit{fault localization}.
-This approach was actually helpful for us when we update existing
+The basic idea is to check whether we can parse the failed algorithm step
+with the assumption that a specific sub-sequence of the
+failed step is successfully parsed.  We define a \textit{rule suggestion}
+as such sub-sequence of failed steps with the name of an existing compile rule.
+\textsf{Fault Localizer} refines candidates of rule suggestions into
+most specific ones. This approach was actually helpful for us when we update existing
 compile rules for new versions of the specification.
@@
 For a given failed step $T$ and the size of a failed input $n$, it
-attempts to find a set of the most specific suggestions.  It
+attempts to find a set of the most specific rule suggestions.  It
 substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
 special token \( \tstar \), which represents some sub-sequence of a
-failed step.  It collects a set of possible suggestions, and then
+failed step.  It collects a set of possible rule suggestions, and then
 removes more general ones than existing suggestions.  To support this
@@
 When we use the fault localization algorithm with the failed step and
-its size 15, it first finds one suggestion for statements and four
-suggestions for expressions as follows:
+its size 15, it first finds one rule suggestion for statements and four
+rule suggestions for expressions as follows:
 \[
@@
 is the most specific sub-sequence, it removes the other four
-suggestions. Finally, the rule assistant suggests to define another
-expression compile rule for the token list \hint{}.
+rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
+another expression compile rule for the token list \hint{}.

### 2019-08-24 icse20/conclusion.tex
assitant -> fault localizer

@@
 language-specific global setting, which we provide for ECMAScript
-as an example case study.  We also support a rule assistant to guide
-how to convert new abstract algorithms.  We evaluated \( \tool \) by
-applying it to ECMAScript 2020 with Test262.  The extracted semantics
-passed 19,220 of 19,282 applicable tests in Test262 and we showed
-that the tool is also applicable to an incomplete language proposal.
-The tool also detected six confirmed errors from the
-specification and the proposal.  The implementation of the tool is
-publicly available as an open-source project.
+as an example case study.  We also support \textsf{Fault Localizer} to
+adapt updates of ECMAScript specification by suggesting new rules.
+We evaluated \( \tool \) by applying it to ECMAScript 2020 with Test262.
+The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.
+The tool also detected three confirmed errors from the specification.
+Moreover, we showed that the tool is also applicable to an incomplete
+language proposal. The implementation of the tool is publicly available
+as an open-source project.

### 2019-08-24 icse20/eval.tex
Fixed typos
assitant -> fault localizer

@@
     \aboverulesepcolor{gainsboro}\midrule
-    Annexes/Internationalisation & 1,774\\\hdashline
+    Annexes/Internationalization & 1,774\\\hdashline
     In-progress features & 5,895\\\midrule
@@
 implemented their corresponding \( \ires \) functions
-via the rule assistant introduced in Section~\ref{sec:assistant}.
+via the \textsf{Fault Localizer} introduced in Section~\ref{sec:localizer}.
 Moreover, we implement the \textsf{Global Setting} except

### 2019-08-24 icse20/related.tex
assitant -> fault localizer

@@
 of the API functions to find correct modeling.  Unlike their approach, we
-support a specification translation assistant to support future language
-updates and to provide correct meaning of specification, which is
+introduce a fault localization algorithm to support future language
+updates and to provide correct meaning of specification. Our tool is also
 applicable for testing even when the actual implementation is not available.
@@
 specification to their own IR called JSIL to make further analysis.
-Our approach provides a framework to generate syntactic parsers and
-semantics compilers from the specification to \( \ires \)
-with a conversion assistant, which reduces human efforts significantly.
+Our approach provides a mechanized framework to synthesize syntactic parsers and
+to automatically extract semantics from the specification to \( \ires \)
+using rule-based compilation technique. It significantly reduces human
+efforts and also flexible for future specification updates.
 

### 2019-08-24 icse20/main.tex
Rewording

@@
 and extracts semantics from 91.60\% of algorithm steps for five recent
-ECMAScript versions. We manually extend one of the extracted semantics for
-the next version of ECMAScript 2020. It passed 19,220 of 19,282 applicable tests
+ECMAScript versions.  We implemented a JavaScript interpreter for ECMAScript 2020
+using the extracted semantics.  It passed 19,220 of 19,282 applicable tests
 in Test262, the official ECMAScript conformance test suite. While extracting
 the semantics using \( \tool \), we found three specification errors
-and all of them are confirmed by TC 39. Moreover, we succeed to apply
-our tool into an incomplete proposal as a case study.
+and all of them were confirmed by TC 39. Moreover, we also successfully applied
+our tool to an incomplete proposal as a case study.
 \end{abstract}

### 2019-08-24 icse20/related.tex
Rewording

@@
 an extension of the $\lambda$ calculus, it does not show the semantics
-correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
-JaVerT~\citet{javert} defined formal semantics of JavaScript by manually converting
+correspondence defined in the ECMAScript specification.  KJS~\cite{kjs} and
+JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
 the ECMAScript specification to their own formal languages.  KJS mapped
@@
 Our approach provides a mechanized framework to synthesize syntactic parsers and
-to automatically extract semantics from the specification to \( \ires \)
+to automatically extract semantics
 using rule-based compilation technique. It significantly reduces human

### 2019-08-24 icse20/compiler.tex
Updated image for fault localizer
fix to fault localizer
Second submission

@@
   \centering
-  \includegraphics[width=0.5\textwidth]{img/algo_compiler.png}
+  \includegraphics[width=0.48\textwidth]{img/algo_compiler.png}
   \caption{Overall structure of {\sf Algorithm Compiler}}
@@
 
-To diagnose the root cause of parsing failures, we support a \textsf{Fault Localizer},
+To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
 which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
@@
 failed step is successfully parsed.  We define a \textit{rule suggestion}
-as such sub-sequence of failed steps with the name of an existing compile rule.
-\textsf{Fault Localizer} refines candidates of rule suggestions into
-most specific ones. This approach was actually helpful for us when we update existing
+as such a sub-sequence of failed steps with the name of an existing compile rule.
+\textsf{Fault Localizer} refines candidates of rule suggestions into the
+most specific ones. It helped us when we update existing
 compile rules for new versions of the specification.

### 2019-08-24 icse20/related.tex
Second submission

@@
 to automatically extract semantics
-using rule-based compilation technique. It significantly reduces human
-efforts and also flexible for future specification updates.
+using a rule-based compilation technique, which significantly reduces human
+efforts.
 

### 2019-12-16 ase20/impl.tex
IEEETran format for ASE'20

--- 2019-08-24 icse20/impl.tex
@@
 functions have duplicated parameters in strict mode.
-Because they are written in differenet styles from abstract algorithms,
+Because they are written in different styles from abstract algorithms,
 we do not support Early Error Rules.
@@
 implicitly get their receiver objects as arguments at callsites.
-To mimic such implicit behaviors, we added a special variable
+To mimic such implicit behavior, we added a special variable
 \( \code{this} \) as the first parameter of a method-like abstract algorithm,

### 2019-12-16 ase20/intro.tex
IEEETran format for ASE'20

--- 2019-08-24 icse20/intro.tex
@@
 addition, to save the labor of defining such compile rules, we also
-present a \textit{rule generation assistant}, which suggests new
+present a \textsf{Fault Localizer}, which suggests new
 compile rules based on fault localization of not yet convertible
-algorithms.  The assistant helps us deal with changed or newly
+algorithms.  It helps us deal with changed or newly
 introduced algorithms defined in new versions of the ECMAScript

### 2019-12-16 ase20/main.tex
IEEETran format for ASE'20

--- 2019-08-24 icse20/main.tex
@@
-\documentclass[sigconf,review,anonymous=true]{acmart}
+\documentclass[10pt,conference,anonymous=true]{IEEEtran}
 
+\usepackage{url}
+\usepackage{amsmath, amssymb}
+\usepackage{natbib}
 \usepackage{kotex}
@@
 \setlength\arrayrulewidth{0.3pt}
-
-% removed ACM references
-\settopmatter{printacmref=false}
 
@@
 
-\author{Jihyeok Park}
-\email{jhpark0223@kaist.ac.kr}
-\affiliation{\institution{KAIST}}
+\author{\IEEEauthorblockN{Jihyeok Park}
+  \IEEEauthorblockA{\textit{KAIST}}
+  Daejeon, South Korea \\
+  jhpark0223@kaist.ac.kr
 
-\author{Jihee Park}
-\email{j31d0@kaist.ac.kr}
-\affiliation{\institution{KAIST}}
+  \and
 
-\author{Sukyoung Ryu}
-\email{sryu.cs@kaist.ac.kr}
-\affiliation{\institution{KAIST}}
+  \IEEEauthorblockN{Jihee Park}
+  \IEEEauthorblockA{\textit{KAIST}}
+  Daejeon, South Korea \\
+  j31d0@kaist.ac.kr
+
+  \and
+
+  \IEEEauthorblockN{Sukyoung Ryu}
+  \IEEEauthorblockA{\textit{KAIST}}
+  Daejeon, South Korea \\
+  sryu.cs@kaist.ac.kr
+}
+
+\maketitle
 
@@
 
-\keywords{
+\begin{IEEEkeywords}
   JavaScript,
@@
   program synthesis
-}
-
-\maketitle
+\end{IEEEkeywords}
 

### 2019-12-16 ase20/overview.tex
IEEETran format for ASE'20

--- 2019-08-24 icse20/overview.tex
@@
 abstract algorithms with tagged tokens into \( \ires \) functions using
-compile rules, and introduce a rule generation assistant to
+compile rules, and introduce a fault localization algorithm to
 easily construct compile rules (Section~\ref{sec:compiler}).  After

### 2019-12-16 ase20/img/all-version-sem-delta.R

@@ -1,0 +1,30 @@
+library(plotly)
+
+ECMAScript_Version <- c("2015-16", "2016-17", "2017-18", "2019-20")
+auto <- c(256, 123, 121, 155)
+manual <- c(217, 139, 108, 280)
+data <- data.frame(ECMAScript_Version, auto, manual)
+
+p <- plot_ly(
+  data,
+  x = ~ECMAScript_Version,
+  y = ~auto,
+  type = 'bar',
+  name = 'auto',
+  text = auto,
+  textposition = 'auto',
+  marker = list(color = '#0070DE')
+  # orientation = 'h'
+) %>% add_trace(
+  y = ~manual,
+  name = 'manual',
+  text = manual,
+  textposition = 'auto',
+  marker = list(color = '#FE1A13')
+) %>% layout(
+  yaxis = list(title = '# of Steps', dtick = 50),
+  xaxis = list(title = 'Δ ECMAScript Version'), #, showticklabels = FALSE),
+  legend = list(orientation = 'h', x = 0.1, y = 1.05, bgcolor='rgba(0,0,0,0)'),
+  barmode = 'stack'
+)
+p

### 2019-12-16 ase20/img/all-version-sem.R

@@ -1,0 +1,30 @@
+library(plotly)
+
+ECMAScript_Version <- c(2016, 2017, 2018, 2019, 2020)
+auto <- c(938, 1055, 1109, 1127, 1145)
+manual <- c(475, 436, 446, 474, 456)
+data <- data.frame(ECMAScript_Version, auto, manual)
+
+p <- plot_ly(
+  data,
+  x = ~ECMAScript_Version,
+  y = ~auto,
+  type = 'bar',
+  name = 'auto',
+  text = auto,
+  textposition = 'auto',
+  marker = list(color = '#0070DE')
+  # orientation = 'h'
+) %>% add_trace(
+  y = ~manual,
+  name = 'manual',
+  text = manual,
+  textposition = 'auto',
+  marker = list(color = '#FE1A13')
+) %>% layout(
+  yaxis = list(title = '# of Steps', dtick = 200), # , autorange = "reversed"),
+  xaxis = list(title = 'ECMAScript Versions', side = "right", dtick = 1),
+  legend = list(orientation = 'h', x = 0.1, y = 1.05, bgcolor='rgba(0,0,0,0)'),
+  barmode = 'stack'
+)
+p

### 2020-03-23 ase20/compiler.tex
[ASE] Removed FaultLocalizer part

--- 2019-08-24 icse20/compiler.tex
@@
 
-\subsection{Fault Localizer}\label{sec:localizer}
-\begin{algorithm}[t]
-  \caption{Fault Localization}\label{alg:fault}
-  \begin{algorithmic}[1]
-    \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
-    \State $S = \varnothing$
-    \For{$i = 0$ to $n - 1$}
-    \For{$j = i$ to $n - 1$}
-    \State $T'$ = a copy of $T$
-    \State Substitute $T'[i..j]$ with $\tstar$
-    \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
-    \State Insert $(x, i, j)$ into $S$
-    \EndIf
-    \EndFor
-    \EndFor
-    \While{$s = (x, i, j) \in S$}
-    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
-    \State Remove $s$ from $S$
-    \EndIf
-    \EndWhile
-    \State \Return $S$
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
-which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
-The basic idea is to check whether we can parse the failed algorithm step
-with the assumption that a specific sub-sequence of the
-failed step is successfully parsed.  We define a \textit{rule suggestion}
-as such a sub-sequence of failed steps with the name of an existing compile rule.
-\textsf{Fault Localizer} refines candidates of rule suggestions into the
-most specific ones. It helped us when we update existing
-compile rules for new versions of the specification.
-
-The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
-For a given failed step $T$ and the size of a failed input $n$, it
-attempts to find a set of the most specific rule suggestions.  It
-substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
-special token \( \tstar \), which represents some sub-sequence of a
-failed step.  It collects a set of possible rule suggestions, and then
-removes more general ones than existing suggestions.  To support this
-process, we added a parsing rule  \( \code{starT} \) to each compile
-rule as follows:
-\begin{lstlisting}[style=myScalastyle]
-// statements
-val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
-// expressions
-val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
-\end{lstlisting}
-where \( \code{starT} \) is a special basic token parser that just
-checks whether a given token is the special token \( \tstar \). 
-Its corresponding conversion rule is a function that returns a dummy
-\( \ires \) component \( \code{Dummy} \) with a string value that
-represents the name of its compile rule.
-
-For example, let us assume that the \( \code{Expr} \) compile rule
-does not have the alternative for lists:
-\begin{lstlisting}[style=myScalastyle]
-  "<<" ~ repsep(varT, ",") ~ ">>" ^^
-       { case _ ~ x ~ _ => EList(e) } // lists
-\end{lstlisting}
-Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
-When we use the fault localization algorithm with the failed step and
-its size 15, it first finds one rule suggestion for statements and four
-rule suggestions for expressions as follows:
-\[
-\footnotesize
-\! \! \! \!
-  \begin{array}{c}
-    (\scode{"Stmt"}, 0, 14), \;
-    (\scode{"Expr"}, 3, 13), \;
-    (\scode{"Expr"}, 4, 13), \;
-    (\scode{"Expr"}, 6, 12), \;
-    (\scode{"Expr"}, 10, 12)
-  \end{array}
-\]
-In the \textbf{\small while} loop on lines 9--11, because the last one
-is the most specific sub-sequence, it removes the other four
-rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
-another expression compile rule for the token list \hint{}.
+% XXX removed
+% \subsection{Fault Localizer}\label{sec:localizer}
+% \begin{algorithm}[t]
+%   \caption{Fault Localization}\label{alg:fault}
+%   \begin{algorithmic}[1]
+%     \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
+%     \State $S = \varnothing$
+%     \For{$i = 0$ to $n - 1$}
+%     \For{$j = i$ to $n - 1$}
+%     \State $T'$ = a copy of $T$
+%     \State Substitute $T'[i..j]$ with $\tstar$
+%     \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
+%     \State Insert $(x, i, j)$ into $S$
+%     \EndIf
+%     \EndFor
+%     \EndFor
+%     \While{$s = (x, i, j) \in S$}
+%     \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
+%     \State Remove $s$ from $S$
+%     \EndIf
+%     \EndWhile
+%     \State \Return $S$
+%     \EndFunction
+%   \end{algorithmic}
+% \end{algorithm}
+% 
+% To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
+% which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
+% The basic idea is to check whether we can parse the failed algorithm step
+% with the assumption that a specific sub-sequence of the
+% failed step is successfully parsed.  We define a \textit{rule suggestion}
+% as such a sub-sequence of failed steps with the name of an existing compile rule.
+% \textsf{Fault Localizer} refines candidates of rule suggestions into the
+% most specific ones. It helped us when we update existing
+% compile rules for new versions of the specification.
+% 
+% The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
+% For a given failed step $T$ and the size of a failed input $n$, it
+% attempts to find a set of the most specific rule suggestions.  It
+% substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
+% special token \( \tstar \), which represents some sub-sequence of a
+% failed step.  It collects a set of possible rule suggestions, and then
+% removes more general ones than existing suggestions.  To support this
+% process, we added a parsing rule  \( \code{starT} \) to each compile
+% rule as follows:
+% \begin{lstlisting}[style=myScalastyle]
+% // statements
+% val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
+% // expressions
+% val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
+% \end{lstlisting}
+% where \( \code{starT} \) is a special basic token parser that just
+% checks whether a given token is the special token \( \tstar \). 
+% Its corresponding conversion rule is a function that returns a dummy
+% \( \ires \) component \( \code{Dummy} \) with a string value that
+% represents the name of its compile rule.
+% 
+% For example, let us assume that the \( \code{Expr} \) compile rule
+% does not have the alternative for lists:
+% \begin{lstlisting}[style=myScalastyle]
+%   "<<" ~ repsep(varT, ",") ~ ">>" ^^
+%        { case _ ~ x ~ _ => EList(e) } // lists
+% \end{lstlisting}
+% Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
+% When we use the fault localization algorithm with the failed step and
+% its size 15, it first finds one rule suggestion for statements and four
+% rule suggestions for expressions as follows:
+% \[
+% \footnotesize
+% \! \! \! \!
+%   \begin{array}{c}
+%     (\scode{"Stmt"}, 0, 14), \;
+%     (\scode{"Expr"}, 3, 13), \;
+%     (\scode{"Expr"}, 4, 13), \;
+%     (\scode{"Expr"}, 6, 12), \;
+%     (\scode{"Expr"}, 10, 12)
+%   \end{array}
+% \]
+% In the \textbf{\small while} loop on lines 9--11, because the last one
+% is the most specific sub-sequence, it removes the other four
+% rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
+% another expression compile rule for the token list \hint{}.

### 2020-03-24 ase20/intro.tex
[ASE] revised intro

@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/existing.png}
+  \includegraphics[width=0.48\textwidth]{img/existing.pdf}
 \vspace*{-2em}
-  \caption{Existing approaches: Manual extraction of IR-based semantics for ECMAScript}
+  \caption{Existing approaches: Manually implemented parsers and AST-IR
+  translators for IR-based semantics of JavaScript programs}
   \label{fig:existing}
@@
 Researchers have defined various JavaScript formal
-semantics~\cite{aplas08,lambdajs,kjs,javert} and developed several static
-analyzers on top of them~\cite{jsai,tajs,wala,safe}.  As illustrated
-in Figure~\ref{fig:existing}, they defined their own Intermediate
-Representations (IRs) to represent JavaScript program semantics.  They
-built parsers to construct Abstract Syntax Trees (ASTs) from
-programs and AST-IR translators to convert ASTs
-to their own IRs.  This approach helps researchers focus on IRs
-without worrying about diverse and enormous features of JavaScript in
-developing new techniques for program analysis and formal verification.
-We dub such a methodology that manipulates language semantics by
-translating given programs to IRs that are suitable for analysis and
-verification \textit{IR-based semantics extraction}.
+semantics~\cite{aplas08,lambdajs,kjs,javert} suitable for static
+analysis~\cite{jsai,tajs,wala,safe} and formal verification~\cite{javert} by
+referring to ECMAScript specification.  ECMAScript specification officially
+describes JavaScript syntax using a variant of extended BNF notation, and its
+semantics using abstract algorithms written in English in a clearly and
+structured manner.  As illustrated in Figure~\ref{fig:existing}, they built
+parsers that constructs Abstract Syntax Trees (ASTs) of given JavaScript
+programs, and AST-IR translators to convert ASTs to their own Intermediate
+Representations (IRs). This approach helps researchers focus on IRs without
+worrying about diverse and enormous features of JavaScript in developing new
+techniques for program analysis and formal verification.  We dub such
+methodology that manipulates language semantics by translating given programs to
+IRs \textit{IR-based semantics extraction}.
 
-However, existing approaches to JavaScript IR-based semantics
-extraction have difficulties in manipulating recent JavaScript
-programs, because they all extract the semantics \textit{manually}.
-The JavaScript syntax and semantics are described in the ECMAScript
-specification, written in English in a clearly structured and
-organized manner.  Unfortunately, manually implementing parsers and
-translators for JavaScript from the specification is tedious,
-labor-intensive, and error-prone especially because the language is
-huge.  The most recent specification, ECMAScript 2019, has 798 pages.
+However, to the best of our knowledge, all existing approaches to JavaScript
+IR-based semantics extraction \textit{manually} build parsers and translators.
+The manual approach is tedious, labor-intensive, and error-prone.  For example,
+KJS~\cite{kjs} is one of formal semantics for traditional JavaScript described
+in ECMAScript 5.1 specification~\cite{ecma5} (ES5.1, 2011) and it is defined on top of \(
+\kframework \), which is a framework for defining language semantics.  According
+to an author of KJS, it took \textit{four months} to implement AST-IR translator
+for 1,370 lines out of 2,932 lines in 368 abstract algorithms. However, modern
+JavaScript becomes much more massive than traditional one and the most recent
+version of ECMAScript specification (ES10, 2019) has 1,731 abstract algorithms
+consisting of 10,068 lines.  It means that it is not scalable to build AST-IR
+translator for modern JavaScript.  Thus, most of JavaScript formal semantics
+targets for ES5.1 and no formal semantics deals with modern JavaScript features
+such as lexical binding via \( \code{let} \), the spread \( \code{...} \)
+operator, classes, the \( \code{for-of} \) operator, the \( \code{async} \)
+functions, and generators.
 
-Moreover, manual extraction does not scale for frequent updates of the
-specification.  Most existing formal semantics and analyzers of
-JavaScript support only ECMAScript 5.1~\cite{ecma5} released in June 2011.
-Focusing on ECMAScript 5.1 was reasonable until 2014, because the
-specification was rarely updated.  However, in late 2014, The Ecma
-Technical Committee 39 (TC39)~\cite{tc39} decided to release the
-specification annually.  Currently, no formal semantics
-nor analyzers for JavaScript correctly deal with recent ECMAScript
-features such as lexical binding via \( \code{let} \), the spread
-\( \code{...} \) operator, classes, the \( \code{for-of} \) operator,
-the \( \code{async} \) functions, and generators.
+Moreover, JavaScript syntax and semantics is annually updated.  Until ECMAScript
+5.1 specification, JavaScript is quite stable language because the specification
+has been rarely updated.  However, The Ecma Technical Committee 39
+(TC39)~\cite{tc39} decided to release the specification annually in late 2014.
+The first specification (ES6, 2015) after this official announcement includes
+various modern JavaScript languages features. In every year, several syntax and
+roughly 1,000 to 3,000 lines of abstract algorithms are modified or newly added
+in the specification. Thus, we need to update JavaScript parser every year while
+existing work does not care about parser itself because the stable parser for
+traditional JavaScript (ES5.1) already existed. Besides, the manual approach
+does not scale for AST-IR translators to deal with this frequent and massive
+updates of ECMAScript specification.
 
-In this paper, we propose JavaScript IR-based Semantics Extraction
-Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
-syntax and semantics from the ECMAScript specification.  It
-automatically generates a JavaScript parser from the syntax defined in
-the ECMAScript specification.  It also automatically extracts the
-formal semantics of JavaScript with given \textit{compile rules}.
-Each compile rule describes how abstract algorithms in the
-specification written in a natural language are converted into
-functions of our intermediate representation \( \ires \).  In
-addition, to save the labor of defining such compile rules, we also
-present a \textsf{Fault Localizer}, which suggests new
-compile rules based on fault localization of not yet convertible
-algorithms.  It helps us deal with changed or newly
-introduced algorithms defined in new versions of the ECMAScript
-specification as well.
+To alleviate this problem, we proposed a technique to \textit{automatically
+synthesize} parsers and AST-IR translators directly from ECMAScript
+specifications. There are several technical challenges in synthesizing parsers
+and translators. For syntax, ECMAScript specifications utilize their own special
+variant of extended BNF with parametric non-terminals, conditional
+alternatives, and various special terminal symbols. Thus, no existing parser
+generation technique is directly applicable for this variant. Moreover,
+JavaScript provides automatic semicolon insertion in parsing algorithm not in
+lexer with several complex rules. For semantics, abstract algorithms in
+ECMAScript specifications are written in English and no reference interpreter to
+check the synthesized AST-IR translators for future specifications.  Moreover,
+the general representation of abstract algorithms is necessary for the forward
+compatibility of our technique.
 
-The main contribution of this paper is \( \tool \):
+Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
+Toolchain:
 \begin{itemize}[leftmargin=0.5cm]
-\item We successfully applied \( \tool \) to ECMAScript 2020, the next
-ECMAScript version scheduled to be released in June 2020.  The
-automatically extracted semantics passed the official conformance test
-suite, Test262~\cite{test262}; out of 19,282 tests for
-ECMAScript 2020 it passed 19,220 tests.
-\item \( \tool \) is also applicable to new language features proposed
-for a future release to aid language development in a modular way.
-Because ECMAScript is an open standard language, various proposals are
-available with their own specification changes and tests.  As a case
-study, we applied \( \tool \) to such a proposal, during which the tool
-found some errors in the proposal.  The reported errors were all confirmed
-and the tool passed all the tests.
-\item Moreover, since the extraction mechanism of \( \tool \) is fully
-automatic, we can use it to find possible specification errors.  We
-indeed found 3 specification errors in ECMAScript 2020.  They were all
-confirmed by TC39 and will be fixed in the next release.
+  \item \( \tool \) \textit{first} automatically synthesizes parsers and AST-IR
+    translators for modern JavaScript directly from ECMAScript specifications.
+    For syntax, we first formalize \( \bnfes \), the variant of extended BNF
+    used in the specification, and propose the parser generation technique for
+    \( \bnfes \) with automatic semicolon insertion.  While parsers are
+    generated in a fully automatic way, synthesis of AST-IR translators are
+    semi-automatic assisted by \textit{compile rules} because of the difficulty
+    to deal with semantics written in natural language. Each compile rule
+    describes how each line of abstract algorithms is converted into our
+    intermediate representation \( \ires \) designed for ECMAScript
+    specifications.
+  \item We first define formal semantics of modern JavaScript via \( \tool \).
+    We applied our tool to the next version of specification (ES11) scheduled to
+    be released in June 2020.  The synthesized parser and translator passed the
+    official conformance test suite, Test262~\cite{test262}; out of
+    \inred{XX,XXX} applicable tests for ES11 it passed \inred{XX,XXX}
+    tests.  Moreover, we found a 3 specification errors in ES11 by
+    using the synthesized parsers and translators.  They were all confirmed by
+    TC39 and will be fixed in the next release.
+  \item \( \tool \) is also adaptable for new language features will be proposed
+    in future ECMAScript specifications.  TC39 manages proposals for new
+    language features in an open source
+    project\footnote{https://github.com/tc39/proposals}. As a case study, we
+    applied \( \tool \) to feature proposals in Stage 3 and we found some errors
+    in the language feature \inred{XXX} and \inred{XXX}. The reported errors
+    were all confirmed as real bugs.
 \end{itemize}

### 2020-03-26 ase20/abstract.tex
[ASE] revised abstract

\begin{abstract}
JavaScript was initially designed for client-side programming in web browsers,
but its engine is now embedded in various kinds of host software.  Despite the
popularity, since the JavaScript semantics is complex especially due to its
dynamic nature, understanding and reasoning about JavaScript programs are
challenging tasks.  Thus, researchers have proposed several attempts to define
the formal semantics of JavaScript based on ECMAScript, the official JavaScript
specification.  However, the existing approaches are manual, labor-intensive,
and error-prone and all formal semantics target former versions of ECMAScript
5.1 (ES5.1).  It is critical in understanding modern JavaScript language
features introduced after ECMAScript 6 (ES6). Moreover, ECMAScript has been
annually released since 2015, which made already five updates after ES5.1.

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based
Semantics Extraction Toolchain. It is the first tool that \textit{automatically
synthesizes} parsers and AST-IR translators directly from a given ECMAScript.
For syntax, we develop a parser generation technique with \textit{lookahead
parsing} for \( \bnfes \), a variant of the extended BNF used in ECMAScript.
For semantics, \( \tool \) synthesizes AST-IR translators using \textit{forward
compatible} rule-based compilation. Each \textit{compile rule} describes how to
convert each step of abstract algorithms written in structured natural language
into \( \ires \), an Intermediate Representation that we designed for
ECMAScript. For the five most recent ECMAScript versions, \( \tool \) succeeds
to synthesize parsers for all versions, and to compile \inred{XX.XX}\% of
algorithm steps in average. We manually complete the core part of formal
semantics of the next version of ECMAScript (ES11) based on the extracted
semantics and it passed all \inred{XX,XXX} applicable tests. Based on the formal
semantics, we found \inred{X} specification errors in ES11 and all of them were
confirmed by TC 39.  Furthermore, we also successfully applied \( \tool \) to
\inred{X} feature proposals in Stage 3.
\end{abstract}

### 2020-03-26 ase20/main.tex
Applied ASE 2020 format
[ASE] revised abstract

--- 2019-08-24 icse20/main.tex
@@
-\documentclass[sigconf,review,anonymous=true]{acmart}
+\documentclass[sigconf,review,anonymous]{acmart}
 
+\usepackage{url}
+\usepackage{amsmath, amssymb}
+\usepackage{natbib}
 \usepackage{kotex}
@@
 \usepackage{booktabs}
+
+% remove ACM Reference format
+\settopmatter{printacmref=false}
 
@@
 \author{Jihyeok Park}
+\affiliation{%
+  \institution{KAIST}
+  \department{School of Computing}
+  \city{Daejeon}
+  \country{South Korea}
+}
 \email{jhpark0223@kaist.ac.kr}
-\affiliation{\institution{KAIST}}
 
 \author{Jihee Park}
+\affiliation{%
+  \institution{KAIST}
+  \department{School of Computing}
+  \city{Daejeon}
+  \country{South Korea}
+}
 \email{j31d0@kaist.ac.kr}
-\affiliation{\institution{KAIST}}
 
 \author{Sukyoung Ryu}
+\affiliation{%
+  \institution{KAIST}
+  \department{School of Computing}
+  \city{Daejeon}
+  \country{South Korea}
+}
 \email{sryu.cs@kaist.ac.kr}
-\affiliation{\institution{KAIST}}
 
-\begin{abstract}
-JavaScript was initially designed for client-side code in web browsers,
-but its engine is now embedded in various kinds of host software.
-Despite its popularity, since the JavaScript semantics is complex
-especially due to its dynamic nature, understanding and reasoning
-about JavaScript programs are challenging tasks.  Thus,
-researchers have proposed several attempts to define the formal semantics
-of JavaScript based on ECMAScript, the official JavaScript specification.
-However, the existing approaches are manual, labor-intensive, and
-error-prone, and they all target only the ECMAScript 5.1 version.
-This problem is critical in understanding recent JavaScript programs
-because ECMAScript has been annually released since 2015, which made
-already five updates after ECMAScript 5.1.
-
-To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
-Extraction Toolchain. It \textit{synthesizes} a JavaScript
-parser for a given grammar written in \( \bnfes \), an extended BNF
-used in ECMAScript. It also \textit{automatically} extracts
-semantics using rule-based compilation. Each \textit{compile rule}
-describes how to convert each abstract algorithm written in a structured natural language
-into functions written in \( \ires \), an Intermediate Representation
-for ECMAScript. \( \tool \) synthesizes parsers from all \( \bnfes \) productions
-and extracts semantics from 91.60\% of algorithm steps for five recent
-ECMAScript versions. We manually extend one of the extracted semantics for
-the next version of ECMAScript 2020. It passed 19,220 of 19,282 applicable tests
-in Test262, the official ECMAScript conformance test suite. While extracting
-the semantics using \( \tool \), we found three specification errors
-and all of them are confirmed by TC 39. Moreover, we succeed to apply
-our tool into an incomplete proposal as a case study.
-\end{abstract}
-
-\keywords{
-  JavaScript,
-  mechanized formal semantics,
-  program synthesis
-}
-
+\input{abstract}
+\keywords{JavaScript, mechanized formal semantics, program synthesis}
 \maketitle

### 2020-03-28 ase20/abstract.tex
[ASE] Revised abstract / intro

@@
 specification.  However, the existing approaches are manual, labor-intensive,
-and error-prone and all formal semantics target former versions of ECMAScript
-5.1 (ES5.1).  It is critical in understanding modern JavaScript language
-features introduced after ECMAScript 6 (ES6). Moreover, ECMAScript has been
-annually released since 2015, which made already five updates after ES5.1.
+and error-prone and all formal semantics targeted ECMAScript 5.1 (ES5.1, 2011)
+or more former versions.  It is critical in understanding modern JavaScript
+language features introduced by ECMAScript 6 (ES6, 2015).  Moreover, ECMAScript
+has been annually released since 2015, which made already five updates after
+ES5.1.
 
@@
 algorithm steps in average.  We manually complete the core part of formal
-semantics of the next version of ECMAScript (ES11) based on the extracted
-semantics and it passed all \inred{XX,XXX} applicable tests. Based on the formal
-semantics, we found \inred{X} specification errors in ES11 and all of them were
-confirmed by TC 39.  Furthermore, we also successfully applied \( \tool \) to
-\inred{X} feature proposals in Stage 3.
+semantics of the draft of the next ECMAScript (ES11, 2020) based on the
+extracted semantics and it passed all \inred{XX,XXX} applicable tests.  Based on
+the formal semantics, we found \inred{X} specification errors in ES11 and all of
+them were confirmed by TC 39.  Furthermore, we also successfully applied \(
+\tool \) to \inred{X} feature proposals in Stage 3 to check the forward
+compatibility of \( \tool \).
 \end{abstract}

### 2020-03-28 ase20/intro.tex
[ASE] Revised abstract / intro

--- 2019-12-16 ase20/intro.tex
@@
 \section{Introduction}
-JavaScript is one of the most widely used programming languages not only for client-side
-but also for server-side programming~\cite{nodejs, meanjs}
-and even for small embedded systems~\cite{espruino, tessel2}.
-It is the top-ranked language used in active GitHub
-repositories\footnote{https://githut.info/}, and \#7 in the TIOBE
-Programming Community index\footnote{https://www.tiobe.com/tiobe-index/}.
-According to W3Techs\footnote{https://w3techs.com/technologies/details/cp-javascript/all/all},
-95.2\% of websites use JavaScript as their client-side programming language.
+JavaScript is one of the most widely used programming languages not only for
+client-side but also for server-side programming~\cite{nodejs, meanjs} and even
+for small embedded systems~\cite{espruino, tessel2}.  It is the top-ranked
+language used in active GitHub repositories\footnote{https://githut.info/}, and
+\#7 in the TIOBE Programming Community
+index\footnote{https://www.tiobe.com/tiobe-index/}.  According to
+W3Techs\footnote{https://w3techs.com/technologies/details/cp-javascript/all/all},
+95.0\% of websites use JavaScript as their client-side programming language.
 
-Despite its popularity, JavaScript developers often suffer from its intricate semantics,
-which may cause unexpected behavior.  For example, calling the following JavaScript
-function seems to always return \( \code{false} \):
+Despite its popularity, JavaScript developers often suffer from its intricate
+semantics, which may cause unexpected behaviors.  For example, calling the
+following JavaScript function seems to always return \( \code{false} \):
 \begin{lstlisting}[style=myJSstyle]
@@
 \end{lstlisting}
-Unfortunately, it returns \( \code{true} \) when its argument is an empty array
-\( \code{[]} \).  To correctly understand and reason about such complex
-behavior, the formal semantics of JavaScript is necessary.
+Unfortunately, it returns \( \code{true} \) when its argument
+is an empty array \( \code{[]} \).  To correctly understand and reason about
+such a complex behavior, the formal semantics of JavaScript is necessary.
 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/existing.png}
+  \includegraphics[width=0.48\textwidth]{img/existing.pdf}
 \vspace*{-2em}
-  \caption{Existing approaches: Manual extraction of IR-based semantics for ECMAScript}
+  \caption{Existing approaches: Manually built parsers and AST-IR
+  translators for JavaScript IR-based semantics}
   \label{fig:existing}
@@
 Researchers have defined various JavaScript formal
-semantics~\cite{aplas08,lambdajs,kjs,javert} and developed several static
-analyzers on top of them~\cite{jsai,tajs,wala,safe}.  As illustrated
-in Figure~\ref{fig:existing}, they defined their own Intermediate
-Representations (IRs) to represent JavaScript program semantics.  They
-built parsers to construct Abstract Syntax Trees (ASTs) from
-programs and AST-IR translators to convert ASTs
-to their own IRs.  This approach helps researchers focus on IRs
-without worrying about diverse and enormous features of JavaScript in
-developing new techniques for program analysis and formal verification.
-We dub such a methodology that manipulates language semantics by
-translating given programs to IRs that are suitable for analysis and
-verification \textit{IR-based semantics extraction}.
+semantics~\cite{aplas08,lambdajs,kjs,javert} suitable for static
+analysis~\cite{jsai,tajs,wala,safe} and formal verification~\cite{javert} by
+referring to ECMAScript.  ECMAScript is the official specification that
+describes JavaScript syntax using a variant of the extended BNF (EBNF) notation,
+and its semantics using abstract algorithms written in English in a clear and
+structured manner.  \textit{IR-based semantics extraction} is a typical way to
+define the formal semantics by building a compiler from programs to Intermediate
+Representations (IRs) to indirectly represent the semantics of given programs.
+As illustrated in Figure~\ref{fig:existing}, the compiler consists of a parser
+that constructs Abstract Syntax Trees (ASTs) of given JavaScript programs, and
+an AST-IR translator that converts ASTs to their own IRs.  This approach helps
+researchers focus on IRs without worrying about diverse and enormous features of
+JavaScript in developing new techniques for static analysis and formal
+verification.
 
-However, existing approaches to JavaScript IR-based semantics
-extraction have difficulties in manipulating recent JavaScript
-programs, because they all extract the semantics \textit{manually}.
-The JavaScript syntax and semantics are described in the ECMAScript
-specification, written in English in a clearly structured and
-organized manner.  Unfortunately, manually implementing parsers and
-translators for JavaScript from the specification is tedious,
-labor-intensive, and error-prone especially because the language is
-huge.  The most recent specification, ECMAScript 2019, has 798 pages.
+However, to the best of our knowledge, all existing approaches to JavaScript
+IR-based semantics extraction \textit{manually} build parsers and translators.
+Although it was reasonable approach until ECMAScript 5.1 (ES5.1,
+2011)~\cite{es5}, the manual approach is too tedious, labor-intensive, and
+error-prone to deal with the large size of modern JavaScript since ECMAScript 6
+(ES6, 2015)~\cite{es6}. ES6 introduced lots of significantly new features such
+as lexical binding via \( \code{let} \), the spread \( \code{...} \) operator,
+classes, the \( \code{for-of} \) operator, the \( \code{async} \) functions, and
+generators.  KJS~\cite{kjs} is one of formal semantics of ECMAScript 5.1 (ES5.1,
+2011) and it is defined on top of \( \kframework \), which is a framework for
+defining language semantics.  According to an author of KJS, it took
+\textit{four months} to implement AST-IR translator for 1,370 steps out of 2,932
+steps in 368 abstract algorithms. However, the most recent version of ECMAScript
+(ES10, 2019)~\cite{es10} has 1,731 abstract algorithms consisting of 10,068
+steps. Thus, it is not scalable to build AST-IR translator for modern JavaScript
+and no formal semantics exists for ES6 to ES10.
 
-Moreover, manual extraction does not scale for frequent updates of the
-specification.  Most existing formal semantics and analyzers of
-JavaScript support only ECMAScript 5.1~\cite{ecma5} released in June 2011.
-Focusing on ECMAScript 5.1 was reasonable until 2014, because the
-specification was rarely updated.  However, in late 2014, The Ecma
-Technical Committee 39 (TC39)~\cite{tc39} decided to release the
-specification annually.  Currently, no formal semantics
-nor analyzers for JavaScript correctly deal with recent ECMAScript
-features such as lexical binding via \( \code{let} \), the spread
-\( \code{...} \) operator, classes, the \( \code{for-of} \) operator,
-the \( \code{async} \) functions, and generators.
+Moreover, JavaScript syntax and semantics are annually updated.  Until
+ECMAScript 5.1, JavaScript was a stable language because the specification was
+rarely updated.  However, The Ecma Technical Committee 39 (TC39)~\cite{tc39}
+decided to release the specification annually in late 2014.  After this official
+announcement, several syntax features and roughly 1,000 to 3,000 steps of
+abstract algorithms are modified or newly added in the specification every year.
+To deal with these frequent and massive updates of ECMAScript, researchers
+should manually update parsers and AST-IR translators by putting a lot of
+effort.
 
-In this paper, we propose JavaScript IR-based Semantics Extraction
-Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
-syntax and semantics from the ECMAScript specification.  It
-automatically generates a JavaScript parser from the syntax defined in
-the ECMAScript specification.  It also automatically extracts the
-formal semantics of JavaScript with given \textit{compile rules}.
-Each compile rule describes how abstract algorithms in the
-specification written in a natural language are converted into
-functions of our intermediate representation \( \ires \).  In
-addition, to save the labor of defining such compile rules, we also
-present a \textsf{Fault Localizer}, which suggests new
-compile rules based on fault localization of not yet convertible
-algorithms.  It helps us deal with changed or newly
-introduced algorithms defined in new versions of the ECMAScript
-specification as well.
+To alleviate this problem, we propose a technique to \textit{automatically
+synthesize} parsers and AST-IR translators directly from ECMAScript with
+\textit{forward compatibility}. There are several technical challenges in
+synthesizing parsers and translators. For syntax, ECMAScript utilize their own
+special variant of the EBNF with parametric non-terminals, conditional
+alternatives, and various special terminal symbols.  Thus, no existing parser
+generation technique is directly applicable for this variant.  Moreover,
+JavaScript provides automatic semicolon insertion in its parsing algorithm with
+several complex rules not in a lexer. For semantics, abstract algorithms in
+ECMAScript are written in English.  Besides, general and forward compatible
+representation of abstract algorithms is necessary for future version of
+ECMAScript.
 
-The main contribution of this paper is \( \tool \):
+Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
+Toolchain:
 \begin{itemize}[leftmargin=0.5cm]
-\item We successfully applied \( \tool \) to ECMAScript 2020, the next
-ECMAScript version scheduled to be released in June 2020.  The
-automatically extracted semantics passed the official conformance test
-suite, Test262~\cite{test262}; out of 19,282 tests for
-ECMAScript 2020 it passed 19,220 tests.
-\item \( \tool \) is also applicable to new language features proposed
-for a future release to aid language development in a modular way.
-Because ECMAScript is an open standard language, various proposals are
-available with their own specification changes and tests.  As a case
-study, we applied \( \tool \) to such a proposal, during which the tool
-found some errors in the proposal.  The reported errors were all confirmed
-and the tool passed all the tests.
-\item Moreover, since the extraction mechanism of \( \tool \) is fully
-automatic, we can use it to find possible specification errors.  We
-indeed found 3 specification errors in ECMAScript 2020.  They were all
-confirmed by TC39 and will be fixed in the next release.
+  \item \( \tool \) is the \textit{first} tool that can automatically synthesize
+    parsers and AST-IR translators for modern JavaScript directly from
+    ECMAScript.  For syntax, we formalize the variant of EBNF as \( \bnfes \)
+    for the first time, and propose a parser generation technique with
+    \textit{lookahead parsing} for \( \bnfes \) with automatic semicolon
+    insertion. For Semantics, synthesis of AST-IR translators are semi-automatic
+    assisted by \textit{compile rules} because of the difficulty in dealing with
+    the semantics written in a natural language.  Compile rules describe how
+    each step of abstract algorithms is converted into our intermediate
+    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
+    for the five most recent ECMAScript versions including the draft of the next
+    version (ES6 to ES11).  We succeed to generate parsers for all versions, and
+    to automatically cover \inred{XX.X}\% of steps in abstract algorithms in
+    average.
+  \item Based on \( \tool \), we define the first IR-based formal semantics of
+    modern JavaScript.  The semantics targets the core part of the draft of next
+    version of ECMAScript (ES11), and our tool successfully synthesizes its
+    parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
+    algorithm steps.  We manually complete the missing parts of the AST-IR
+    translator (\inred{XXX} steps) in \inred{XX} days.  To check the correctness
+    of the formal semantics, we evaluated Test262~\cite{test262}, the official
+    conformance test suite, and the semantics passed all \inred{XX,XXX}
+    applicable tests.  Moreover, we found \inred{X} specification errors in ES11
+    based on the formal semantics.  They were all confirmed by TC39 and will be
+    fixed in the next release.
+  \item \( \tool \) is also forward compatible with new language features
+    proposed for future ECMAScript specifications.  TC39 manages proposals of
+    new language features in an open source
+    project\footnote{https://github.com/tc39/proposals}.  There are five stages
+    of proposals (from Stage 0 to Stage 4).  All proposals in Stage 4 (Finished)
+    are applied in the draft of the next ECMAScript, Stage 3 (Candidate) is the
+    last stage before Stage 3.  For evaluation of forward compatibility of \(
+    \tool \), we applied our tool to all \inred{XX} Stage 3 proposals. It
+    succeeded to synthesize parsers for all proposals, and to convert \inred{XX}
+    out of \inred{XX} algorithm steps for all proposals. After completing all
+    missing parts, each semantics passed all \inred{XX} tests.
 \end{itemize}

### 2020-03-30 ase20/abstract.tex
Revised Intro

--- 2020-03-26 ase20/abstract.tex
@@
 specification.  However, the existing approaches are manual, labor-intensive,
-and error-prone and all formal semantics target former versions of ECMAScript
-5.1 (ES5.1).  It is critical in understanding modern JavaScript language
-features introduced after ECMAScript 6 (ES6). Moreover, ECMAScript has been
-annually released since 2015, which made already five updates after ES5.1.
+and error-prone and all of their formal semantics target ECMAScript 5.1 (ES5.1, 2011)
+or its former versions.  Therefore, they are not suitable for understanding
+\textit{modern JavaScript} language features introduced since
+ECMAScript 6 (ES6, 2015).  Moreover, ECMAScript has been annually updated since ES6,
+which made already five releases after ES5.1.
 
@@
 Semantics Extraction Toolchain.  It is the first tool that \textit{automatically
-synthesizes} parsers and AST-IR translators directly from a given ECMAScript.
+synthesizes} parsers and AST-IR translators directly from a given
+language specification, ECMAScript.
 For syntax, we develop a parser generation technique with \textit{lookahead
@@
 For semantics, \( \tool \) synthesizes AST-IR translators using \textit{forward
-compatible} rule-based compilation. Each \textit{compile rule} describes how to
-convert each step of abstract algorithms written in structured natural language
+compatible} rule-based compilation.  \textit{Compile rules} describe how to
+convert each step of abstract algorithms written in a structured natural language
 into \( \ires \), an Intermediate Representation that we designed for
-ECMAScript. For the five most recent ECMAScript versions, \( \tool \) succeeds
-to synthesize parsers for all versions, and to compile \inred{XX.XX}\% of
-algorithm steps in average. We manually complete the core part of formal
-semantics of the next version of ECMAScript (ES11) based on the extracted
-semantics and it passed all \inred{XX,XXX} applicable tests. Based on the formal
-semantics, we found \inred{X} specification errors in ES11 and all of them were
-confirmed by TC 39.  Furthermore, we also successfully applied \( \tool \) to
-\inred{X} feature proposals in Stage 3.
+ECMAScript.  For the five most recent ECMAScript versions and the
+current draft of the next ECMAScript (ES11, 2020), \( \tool \) automatically
+synthesized parsers for all versions, and compiled \inred{XX.XX}\% of the
+algorithm steps on average.  After we complete the missing parts manually,
+the extracted core semantics of ES11 passed all \inred{XX,XXX} applicable tests.
+Using this \textit{first formal semantics of modern JavaScript}, we found
+\inred{X} specification errors in ES11, which were all confirmed by
+the Ecma Technical Committee 39.  Furthermore, we also successfully
+applied \( \tool \) to \inred{X} feature proposals that are candidates
+for inclusion in ECMAScript, which shows the forward compatibility of \( \tool \).
 \end{abstract}

### 2020-03-30 ase20/intro.tex
Revised Intro
Revised Sec. 1

@@
 referring to ECMAScript.  ECMAScript is the official specification that
-describes JavaScript syntax using a variant of the extended BNF (EBNF) notation,
+describes the JavaScript syntax using a variant of the extended BNF (EBNF) notation,
 and its semantics using abstract algorithms written in English in a clear and
-structured manner.  \textit{IR-based semantics extraction} is a typical way to
-define the formal semantics by building a compiler from programs to Intermediate
+structured manner.  \textit{IR-based semantics extraction} is a traditional way to
+define the formal semantics of a language by building a compiler front-end
+that takes programs and produces their Intermediate
 Representations (IRs) to indirectly represent the semantics of given programs.
-As illustrated in Figure~\ref{fig:existing}, the compiler consists of a parser
+As illustrated in Figure~\ref{fig:existing}, the compiler front-end consists of a parser
 that constructs Abstract Syntax Trees (ASTs) of given JavaScript programs, and
@@
 IR-based semantics extraction \textit{manually} build parsers and translators.
-Although it was reasonable approach until ECMAScript 5.1 (ES5.1,
+Although it was a reasonable approach until ECMAScript 5.1 (ES5.1,
 2011)~\cite{es5}, the manual approach is too tedious, labor-intensive, and
-error-prone to deal with the large size of modern JavaScript since ECMAScript 6
-(ES6, 2015)~\cite{es6}. ES6 introduced lots of significantly new features such
+error-prone to deal with the large size of \textit{modern JavaScript} since ECMAScript 6
+(ES6, 2015)~\cite{es6}. ES6 introduced numerous significantly new features such
 as lexical binding via \( \code{let} \), the spread \( \code{...} \) operator,
 classes, the \( \code{for-of} \) operator, the \( \code{async} \) functions, and
-generators.  KJS~\cite{kjs} is one of formal semantics of ECMAScript 5.1 (ES5.1,
-2011) and it is defined on top of \( \kframework \), which is a framework for
+generators.  For example, consider KJS~\cite{kjs}.
+KJS is one of formal semantics of ES5.1
+and it is defined on top of \( \kframework \), which is a framework for
 defining language semantics.  According to an author of KJS, it took
-\textit{four months} to implement AST-IR translator for 1,370 steps out of 2,932
+\textit{four months} to implement an AST-IR translator for 1,370 steps out of 2,932
 steps in 368 abstract algorithms. However, the most recent version of ECMAScript
 (ES10, 2019)~\cite{es10} has 1,731 abstract algorithms consisting of 10,068
-steps. Thus, it is not scalable to build AST-IR translator for modern JavaScript
-and no formal semantics exists for ES6 to ES10.
+steps. Thus, the manual approach does not seem to be scalable enough to build
+an AST-IR translator for modern JavaScript
+and indeed no formal semantics exists for ES6 to ES10.
 
 Moreover, JavaScript syntax and semantics are annually updated.  Until
-ECMAScript 5.1, JavaScript was a stable language because the specification was
-rarely updated.  However, The Ecma Technical Committee 39 (TC39)~\cite{tc39}
+ES 5.1, JavaScript was a stable language because the specification was
+rarely updated.  However, the Ecma Technical Committee 39 (TC39)~\cite{tc39}
 decided to release the specification annually in late 2014.  After this official
 announcement, several syntax features and roughly 1,000 to 3,000 steps of
-abstract algorithms are modified or newly added in the specification every year.
-To deal with these frequent and massive updates of ECMAScript, researchers
-should manually update parsers and AST-IR translators by putting a lot of
-effort.
+abstract algorithms have been modified or newly added in the specification every year.
+To handle these frequent and massive updates of ECMAScript,
+the manual approach requires researchers to manually update parsers and AST-IR translators,
+which incurs tremendous efforts.
 
@@
 \textit{forward compatibility}. There are several technical challenges in
-synthesizing parsers and translators. For syntax, ECMAScript utilize their own
+synthesizing parsers and translators. For syntax, ECMAScript utilizes its own
 special variant of the EBNF with parametric non-terminals, conditional
@@
 JavaScript provides automatic semicolon insertion in its parsing algorithm with
-several complex rules not in a lexer. For semantics, abstract algorithms in
-ECMAScript are written in English.  Besides, general and forward compatible
-representation of abstract algorithms is necessary for future version of
-ECMAScript.
+several complex rules, not in a lexer. For semantics, abstract algorithms in
+ECMAScript are written in English.  Besides, a general and forward compatible
+representation of abstract algorithms is necessary to support future
+versions of ECMAScript.
 
@@
 \begin{itemize}[leftmargin=0.5cm]
-  \item \( \tool \) is the \textit{first} tool that can automatically synthesize
-    parsers and AST-IR translators for modern JavaScript directly from
-    ECMAScript.  For syntax, we formalize the variant of EBNF as \( \bnfes \)
-    for the first time, and propose a parser generation technique with
-    \textit{lookahead parsing} for \( \bnfes \) with automatic semicolon
-    insertion. For Semantics, synthesis of AST-IR translators are semi-automatic
-    assisted by \textit{compile rules} because of the difficulty in dealing with
-    the semantics written in a natural language.  Compile rules describe how
+  \item \textbf{\( \tool \) is the \textit{first tool that can automatically synthesize}
+    parsers and AST-IR translators directly from a language specification,
+    ECMAScript.}  For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
+    and propose a parser generation technique with
+    lookahead parsing for \( \bnfes \), which supports automatic semicolon
+    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
+    translators assisted by compile rules because of the
+    difficulty in handling the semantics written in a natural language.  Compile rules describe how
     each step of abstract algorithms is converted into our intermediate
     representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
-    for the five most recent ECMAScript versions including the draft of the next
-    version (ES6 to ES11).  We succeed to generate parsers for all versions, and
-    to automatically cover \inred{XX.X}\% of steps in abstract algorithms in
-    average.
-  \item Based on \( \tool \), we define the first IR-based formal semantics of
-    modern JavaScript.  The semantics targets the core part of the draft of next
-    version of ECMAScript (ES11), and our tool successfully synthesizes its
+    with the five most recent ECMAScript versions and the current draft of the next
+    ECMAScript (ES6 to ES11).   \( \tool \) automatically generated
+    parsers for all versions, and automatically compiled
+    \inred{XX.X}\% of the steps in abstract algorithms on average.
+  \item \textbf{ Using \( \tool \), we could define the \textit{first IR-based
+    formal semantics of modern JavaScript}.}  The semantics targets the
+    core of ES11, and \( \tool \) successfully synthesizes its
     parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
-    algorithm steps.  We manually complete the missing parts of the AST-IR
-    translator (\inred{XXX} steps) in \inred{XX} days.  To check the correctness
-    of the formal semantics, we evaluated Test262~\cite{test262}, the official
+    algorithm steps.  We manually completed the missing parts of the AST-IR
+    translator (\inred{XXX} steps) in \inred{XX} days.  We evaluated the correctness
+    of the formal semantics using Test262~\cite{test262}, the official
     conformance test suite, and the semantics passed all \inred{XX,XXX}
     applicable tests.  Moreover, we found \inred{X} specification errors in ES11
-    based on the formal semantics.  They were all confirmed by TC39 and will be
+    thanks to the formal semantics.  They were all confirmed by TC39 and will be
     fixed in the next release.
-  \item \( \tool \) is also forward compatible with new language features
-    proposed for future ECMAScript specifications.  TC39 manages proposals of
+  \item \textbf{\( \tool \) is also \textit{forward compatible} with new language features
+    proposed for future ECMAScript specifications.}  TC39 manages proposals of
     new language features in an open source
-    project\footnote{https://github.com/tc39/proposals}.  There are five stages
-    of proposals (from Stage 0 to Stage 4).  All proposals in Stage 4 (Finished)
-    are applied in the draft of the next ECMAScript, Stage 3 (Candidate) is the
-    last stage before Stage 3.  For evaluation of forward compatibility of \(
-    \tool \), we applied our tool to all \inred{XX} Stage 3 proposals. It
-    succeeded to synthesize parsers for all proposals, and to convert \inred{XX}
-    out of \inred{XX} algorithm steps for all proposals. After completing all
-    missing parts, each semantics passed all \inred{XX} tests.
+    project\footnote{https://github.com/tc39/proposals}.  Out of five stages
+    of proposals (from Stage 0 to Stage 4), proposals in Stage 4 (Finished)
+    are ready for inclusiong in the next ECMAScript, and proposals in
+    Stage 3 (Candidate) are in the last stage before finished.  We
+    evaluated the forward compatibility of \( \tool \) by appling it
+    to all \inred{XX} proposals in Stage 3. It successfully
+    synthesized parsers for all proposals, and automatically
+    compiled \inred{XX} out of \inred{XX} algorithm steps for all
+    proposals.  After completion of the missing parts,
+    each semantics passed all \inred{XX} tests.
 \end{itemize}

### 2020-03-30 ase20/intro.tex
[ASE] Fixed typos in intro

@@
     of proposals (from Stage 0 to Stage 4), proposals in Stage 4 (Finished)
-    are ready for inclusiong in the next ECMAScript, and proposals in
+    are ready for inclusion in the next ECMAScript, and proposals in
     Stage 3 (Candidate) are in the last stage before finished.  We
-    evaluated the forward compatibility of \( \tool \) by appling it
+    evaluated the forward compatibility of \( \tool \) by applying it
     to all \inred{XX} proposals in Stage 3. It successfully

### 2020-03-31 ase20/overview.tex
[ASE] Revised overview

--- 2019-08-24 icse20/overview.tex
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/overview.png}
-  \caption{Overall structure of \( \tool \): Automatic extraction of
-IR-based semantics for ECMAScript}
+  \includegraphics[width=0.48\textwidth]{img/overview.pdf}
+  \caption{Overall structure of \( \tool \): Automatically synthesized {\sf
+    JavaScript Parser} and {\sf AST-\( \ires \) Translator} for JavaScript
+    IR-based semantics}
   \label{fig:overview}
@@
 Compared to the existing approaches shown in
-Figure~\ref{fig:existing}, \( \tool \) automatically generates
-{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} from the
-ECMAScript specification.
+Figure~\ref{fig:existing}, \( \tool \) automatically synthesizes
+{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} directly from
+ECMAScript.
 
-The motivation of automatically extracting syntax and semantics
-of JavaScript from the ECMAScript specification is twofold: 1) the
-natural language used in the specification follows well-organized
-specific patterns, and 2) the specification is available as HTML files
-using various HTML tags.  As the first step, we developed {\sf Spec Extractor}
-to simply collect and save both syntax and semantics into JSON format.
-It is written in JavaScript because the ECMAScript specifications are
-provided as HTML files.
+The motivation of automatically extracting syntax and semantics of JavaScript
+from the ECMAScript is twofold: 1) ECMAScript is written in a well-organized
+style, and 2) it is available as HTML files using various HTML tags.  As the
+first step, we developed {\sf Spec Extractor} to simply collect and save both
+syntax and semantics into JSON format.  We implemented {\sf Spec Extractor} in
+JavaScript to easily manipulate ECMAScript written in HTML.
 
@@
   \begin{subfigure}[t]{0.4\textwidth}
-    \includegraphics[width=\textwidth]{img/array_literal.png}
-    \caption{The \textit{ArrayLiteral} production in ECMAScript 2020}
+    \includegraphics[width=\textwidth]{img/arrayliteral-syntax.pdf}
+    \caption{The \textit{ArrayLiteral} production in ES10}
     \label{fig:array-literal-es}
   \end{subfigure}
-  \begin{subfigure}[t]{0.46\textwidth}
+  \begin{subfigure}[t]{0.48\textwidth}
     \begin{lstlisting}[style=myScalastyle]
-type P[T] = List[Boolean] => LAParser[T]
-lazy val ArrayLiteral: P[ArrayLiteral] = memo {
+val ArrayLiteral: List[Boolean] => LAParser[T] = memo {
   case List(Yield, Await) =>
   "[" ~ opt(Elision) ~ "]"             ^^ ArrayLiteral0 |
-  "[" ~ ElementList(Yield, Await) ~ "]" ^^ ArrayLiteral1 |
-  "[" ~ ElementList(Yield, Await) ~ "," ~ opt(Elision) ~ "]" ^^ ArrayLiteral2
+  "[" ~ ElementList(Yield,Await) ~ "]" ^^ ArrayLiteral1 |
+  "[" ~ ElementList(Yield,Await) ~ ","
+      ~ opt(Elision)~ "]"              ^^ ArrayLiteral2
 }
     \end{lstlisting}
+    \vspace*{-1em}
     \caption{The generated parser for the \textit{ArrayLiteral} production}
@@
   \end{subfigure}
-  \caption{The \textit{ArrayLiteral} production in the ECMAScript 2020 specification and its generated parser}
+  \caption{The \textit{ArrayLiteral} production in the ES10 and its generated parser}
   \label{fig:array-literal}
+  \vspace*{-1em}
 \end{figure}
@@
 
-\textbf{Syntax.} The ECMAScript specification provides the lexical and
-syntactic grammars in Appendix A using their own extended Backus-Naur
-Form (BNF) for ECMAScript.  We dub it \( \bnfes \) and formally define
-it in Section~\ref{sec:parser}.  Our {\sf Spec Extractor} reads the
-grammars written in \( \bnfes \) and converts them into JSON files.
-For example, Figure~\ref{fig:array-literal}(a) shows the
-\textit{ArrayLiteral} production in the ECMAScript 2020
-specification.  It takes two boolean parameters \textsf{Yield} and
+\textbf{Syntax.} ECMAScript provides the lexical and syntactic grammars in
+Appendix A using a variant of EBNF for ECMAScript.  We dub it \( \bnfes \) and
+formally define it in Section~\ref{sec:parser}.  Our {\sf Spec Extractor} reads
+the grammars written in \( \bnfes \) and converts them into JSON files.
+For example, Figure~\ref{fig:array-literal}(a) shows the \textit{ArrayLiteral}
+production in ES10.  It takes two boolean parameters \textsf{Yield} and
 \textsf{Await} and has three alternatives.  The first alternative
@@
 
-\begin{figure*}[t]
-  \centering
-  \begin{subfigure}{0.4\textwidth}
-    \includegraphics[width=\textwidth]{img/to_primitive.png}
-    \subcaption{The \textbf{ToPrimitive} algorithm in ECMAScript 2020}
-    \label{fig:to-primitive-es}
-  \end{subfigure}
-  \qquad
-  \begin{subfigure}{0.48\textwidth}
-    \begin{lstlisting}[style=ires]
-"ToPrimitive" (input, PreferredType) => {
-  if (= (Type input) "Object") {
-    if (= PreferredType absent) let hint = "default"
-    else if (= PreferredType "String") let hint = "string"
-    else let hint = "number"
-    let exoticToPrim = ? (GetMethod input SYMBOL_toPrimitive)
-    if (! (= exoticToPrim undefined)) {
-      let result = ? (Call exoticToPrim input (new [hint]))
-      if (! (= (Type result) "Object")) return result
-      return (Throw INTRINSIC_TypeErrorPrototype)
-    }
-    if (= hint "default") hint = "number"
-    return ? (OrdinaryToPrimitive input hint)
-  }
-  return input
-}
-    \end{lstlisting}
-    \subcaption{The generated \( \ires \) function for the \textbf{ToPrimitive} algorithm}
-    \label{fig:to-primitive-ires}
-  \end{subfigure}
-  \caption{The \textbf{ToPrimitive} abstract algorithm in the ECMAScript 2020 specification and its generated \( \ires \) function}
-  \label{fig:to-primitive}
-\end{figure*}
-
 To generate {\sf JavaScript Parser} from a given \( \bnfes \) grammar, we
-construct \textsf{JS Parser Generator} in Scala.  It synthesizes a
+construct \textsf{Parser Generator} in Scala.  It synthesizes a
 JavaScript parser according to the given \( \bnfes \), and the
@@
 
-\smallskip
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.43\textwidth}
+    \includegraphics[width=\textwidth]{img/arrayliteral-eval.pdf}
+    \subcaption{\textbf{Evaluation} abstract algorithm for the third alternative}
+    \label{fig:array-literal-eval-es}
+  \end{subfigure}
+  \qquad
+  \begin{subfigure}{0.46\textwidth}
+    \begin{lstlisting}[style=ires]
+ArrayLiteral[2].Evaluation (ElementList, Elision) => {
+  let array = ! (ArrayCreate 0)
+  let len = (ElementList.ArrayAccumulation array 0)
+  ? len
+  if (= Elision absent) let padding = 0
+  else let padding = Elision.ElisionWidth
+  (Set array "length" (ToUint32 (+ padding len)) false)
+  return array
+}
+    \end{lstlisting}
+    \vspace*{-1em}
+    \subcaption{The generated \( \ires \) function}
+    \label{fig:array-literal-eval-ires}
+  \end{subfigure}
+  \vspace{-1em}
+  \caption{\textbf{Evaluation} abstract algorithm for the third alternative of
+    \textit{ArrayLiteral} in ES10 and its generated \( \ires \)
+    function}
+  \label{fig:array-literal-eval}
+  \vspace{-1em}
+\end{figure}
 
 \textbf{Semantics.}
-The ECMAScript specification describes the language semantics as
-abstract algorithms in English.  While they are written in a natural
-language, the writing style is well-organized with ordered steps and
-tagged tokens.  Our {\sf Spec Extractor} reads each abstract algorithm
-with HTML tags and converts them into JSON files.  For example,
-Figure~\ref{fig:to-primitive}(a) presents the \textbf{ToPrimitive}
-abstract algorithm in ECMAScript 2020.  It has three steps and the
-second step consists of seven sub-steps.  In the HTML files describing
-the abstract algorithms, each parameter or local variable such as
-\textit{input} or \textit{PreferredType} has the \( \code{<var>} \)
-HTML tag and each value has the \( \code{<code>} \) tag.
+ECMAScript describes the language semantics as abstract algorithms in English.
+While they are written in a natural language, the writing style is
+well-organized with ordered steps and tagged tokens.  Our {\sf Spec Extractor}
+reads each abstract algorithm with HTML tags and converts them into JSON files.
+For example, Figure~\ref{fig:array-literal-eval}(a) presents the
+\textbf{Evaluation} abstract algorithm of the third alternative of the
+\textit{ArrayLiteral} production in ES10, and it has seven steps.  In the HTML
+files describing the abstract algorithms, each non-terminal symbol
+(i.e. \textit{ElementList}), local variable (i.e. \textit{array}), code (i.e. \(
+\code{"length"} \)), or value (i.e. \textbf{false}) has the \( \code{<nt>} \),
+\( \code{<var>} \), \( \code{<code>} \), or \( \code{<emu-val>} \) tag,
+respectively.
 
-%because we utilize tag information to discriminate different kinds of tokens.
 To translate such abstract algorithms into representations that are
@@
 functions.  It also takes \textsf{Compile Rules} as another input,
-which has two parts: parsing rules and conversion rules from each rule to its
-corresponding \( \ires \) component.  They are \textit{manually} specified for
-the ECMAScript specification; we explain them in detail in
-Section~\ref{sec:compiler}.  Thus, each abstract algorithm is
+which has two parts: parsing rules and conversion rules.  They are
+\textit{manually} specified for ECMAScript; we explain them in
+detail in Section~\ref{sec:compiler}.  Thus, each abstract algorithm is
 converted into a function written in \( \ires \) via \textsf{Algorithm Compiler}.
-For example, Figure~\ref{fig:to-primitive}(b) presents the generated
-\( \ires \) function for the \textbf{ToPrimitive} abstract algorithm.
-The \( \code{ToPrimitive} \) function takes two parameters:
-\( \code{input} \) and \( \code{PreferredType} \).  The optional
-\( \code{PreferredType} \) parameter in the abstract algorithm has
-a special value \( \code{absent} \) in the generated \( \ires \) function.
-Thus, we convert the condition of the 2-a step,
-``If \textit{PreferredType} is not present,'' into the equality check
-with \( \code{absent} \): \( \code{if (= PreferredType absent)} \).
-In this paper, we omit assertions for presentation brevity; we believe
-that they can be handled similarly.  Some specific keywords are
-represented as string values.  For instance, ``hint Number'' and
-``hint String'' are converted into \( \code{"Number"} \) and
-\( \code{"String"} \), respectively.  In addition,
-\textsf{Algorithm Compiler} modifies prefixes of symbols from
-\( \code{@@} \) to \( \code{SYMBOL\_} \) and handles exceptions with
-their corresponding intrinsic error objects.
+For example, Figure~\ref{fig:array-literal-eval}(b) presents the generated
+\( \ires \) function for the \textbf{Evaluation} abstract algorithm described in
+Figure~\ref{fig:array-literal-eval}(a).
+The \( \code{ArrayLiteral[2].Evaluation} \) function takes two parameters for
+two non-terminal symbols: \( \code{ElementList} \) and \( \code{Elision} \).
+The parameter \( \code{Elision} \) has a special value \( \code{absent} \) when
+the non-terminal symbols \textit{Elision}$_{\mbox{\footnotesize opt}}$ is not
+present.  Thus, we convert the condition in the step 4,
+``if \textit{Elision} is not present,'' into the equality check with \(
+\code{absent} \): \( \code{if (= Elision absent)} \).  Codes are represented as
+string values and values are represented as corresponding \( \ires \) values.
+For instance, the code \texttt{"length"} and the value \textbf{false} are
+converted into the string value \( \code{"length"} \) and the boolean value
+\( \code{false} \), respectively.
 
-Finally, \( \tool \) constructs {\sf AST-\( \ires \) Translator} with
-the given \( \ires \) functions and \textit{manually} specified
-{\sf Global Setting}, which has minor but necessary information to
-evaluate JavaScript programs described in the ECMAScript specification.
-They consists of the structure of the standard built-in
-objects and ECMAScript data types.
-
-Putting them all together, we can translate a given JavaScript program
-into \( \ires \) via generated {\sf JavaScript Parser} and
-{\sf AST-\( \ires \) Translator} by \( \tool \).
-Once \( \tool \) provides the entire infrastructure, supporting yet
-another ECMAScript version would not require much manual efforts;
-the only additional efforts may be possible changes in \textsf{Compile Rules}
-and {\sf Global Setting}.
+Finally, \( \tool \) constructs {\sf AST-\( \ires \) Translator} with the given
+\( \ires \) functions and \textit{manually} specified {\sf Global Setting},
+which has minor but necessary information to evaluate JavaScript programs
+described in ECMAScript.  They consists of the structure of the standard
+built-in objects and ECMAScript data types. Putting them all together, we can
+translate a given JavaScript program into \( \ires \) via generated {\sf
+JavaScript Parser} and {\sf AST-\( \ires \) Translator} by \( \tool \).  Even
+though \( \tool \) is not fully automatic because of {\sf Compile Rules} and
+{\sf Global Setting}, it could dramatically reduce the efforts to building
+parsers and translators from the scratch.
 
@@
 abstract algorithms with tagged tokens into \( \ires \) functions using
-compile rules, and introduce a rule generation assistant to
-easily construct compile rules (Section~\ref{sec:compiler}).  After
-describing implementation details (Section~\ref{sec:impl}),
-we evaluate the effectiveness of \( \tool \)
-(Section~\ref{sec:eval}), discuss related work
-(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclude}).
+compile rules (Section~\ref{sec:compiler}).  After describing implementation
+details (Section~\ref{sec:impl}), we evaluate our tool \( \tool \)
+(Section~\ref{sec:eval}), discuss related work (Section~\ref{sec:related}), and
+conclude (Section~\ref{sec:conclude}).

### 2020-04-01 src/main/scala/kr/ac/kaist/jiset/algorithm/GeneralAlgoCompiler.scala
update AlgoCompiler for 2019

@@ -382,10 +382,10 @@ trait GeneralAlgoCompilerHelper extends AlgoCompilers {
     secno ~ "for the" ~> intrinsicName <~ "function" ^^ {
       ("", 0, _)
     } |||
-    "ListIterator next ()" ^^^ ("next", 0, "ListIteratornext") |||
+    "ListIterator" ~ code.filter(_ == "next") ~ "(" ~ secno ~ ")" ^^^ ("next", 0, "ListIteratornext") |||
     "GetCapabilitiesExecutor Functions" ^^^ ("", 2, "GLOBALDOTGetCapabilitiesExecutorFunctions") |||
-    "Promise Resolve Functions" ^^^ ("", 1, "GLOBALDOTPromiseResolveFunctions") |||
-    "Promise Reject Functions" ^^^ ("", 1, "GLOBALDOTPromiseRejectFunctions") |||
+    "Promise Resolve Functions (" <~ secno <~ ")" ^^^ ("", 1, "GLOBALDOTPromiseResolveFunctions") |||
+    "Promise Reject Functions (" <~ secno <~ ")" ^^^ ("", 1, "GLOBALDOTPromiseRejectFunctions") |||
     "Await Fulfilled Functions" ^^^ ("", 1, "GLOBALDOTAwaitFulfilledFunctions") |||
     "Await Rejected Functions" ^^^ ("", 1, "GLOBALDOTAwaitRejectedFunctions") |||
     "Async-from-Sync Iterator Value Unwrap Functions" ^^^ ("", 1, "GLOBALDOTAsyncfromSyncIteratorValueUnwrapFunctions")
@@ -590,7 +590,7 @@ trait GeneralAlgoCompilerHelper extends AlgoCompilers {
   }
   lazy val condBOp: P[(BOp, Boolean, Boolean)] = (
     ("=" | "equals") ^^^ (OEq, false, false) |||
-    ("≠" | "is different from") ^^^ (OEq, true, false) |||
+    ("≠" | "is not equal to" | "is different from") ^^^ (OEq, true, false) |||
     ("<" | "is less than") ^^^ (OLt, false, false) |||
     "≥" ^^^ (OLt, true, false) |||
     (">" | "is greater than") ^^^ (OLt, false, true) |||
@@ -673,7 +673,7 @@ trait GeneralAlgoCompilerHelper extends AlgoCompilers {
     "the code matching the syntactic production that is being evaluated is contained in strict mode code" |||
[…]

### 2020-04-01 src/main/scala/kr/ac/kaist/jiset/model/AlgoCompiler.scala

@@ -173,7 +173,7 @@ trait AlgoCompilerHelper extends GeneralAlgoCompilerHelper {
       }
     } | "resume the context that is now on the top of the execution context stack as the running execution context" ^^^ {
       parseInst(s"""$context = $executionStack[(- $executionStack.length 1i)]""")
-    } | "let" ~> name <~ "be a newly created ecmascript function object with the internal slots listed in table 27." ^^ {
+    } | "let" ~> name <~ "be a newly created ecmascript function object with the internal slots listed in table 27. All of those internal slots are initialized to" <~ value <~ "." ^^ {
       case x => parseInst(s"""{
         let $x = (new ECMAScriptFunctionObject("SubMap" -> (new SubMap())))
         delete $x.Call
@@ -293,12 +293,13 @@ trait AlgoCompilerHelper extends GeneralAlgoCompilerHelper {
       "If IsCallable (" ~ id ~ ") is" ~ value ~ ", set" ~ id ~ "to the intrinsic function % ObjProto_toString % ." |
       "If IsDataDescriptor (" ~ id ~ ") is" ~ value ~ "and" ~ id ~ "has attribute values { [ [ Writable ] ] :" ~ value ~ ", [ [ Enumerable ] ] :" ~ value ~ "} , return" ~ value ~ "." |
       "If any element of the BoundNames of" ~ id ~ "also occurs in the LexicallyDeclaredNames of" ~ id ~ ", throw a" ~ value ~ "exception ." |
-      "If any static semantics errors are detected for" ~ id ~ "or" ~ id ~ ", throw a" ~ value ~ "exception ." ~ rest |
+      "If any static semantics errors are detected for" ~ id ~ "or" ~ id ~ ", throw a" ~ value ~ "or a" ~ value ~ "exception ," ~ rest |
       "If neither" ~ id ~ "nor any prefix of" ~ id ~ "satisfies the syntax of a StrDecimalLiteral ( see 7 . 1 . 3 . 1 ) , return" ~ value ~ "." |
       "If only one argument was passed , return" ~ id ~ "." |
       "If the Directive Prologue of FunctionStatementList contains a Use Strict Directive , return" ~ value ~ "; otherwise , return" ~ value ~ "." |
       "If the binding for" ~ id ~ "in" ~ id ~ "cannot be deleted , return" ~ value ~ "." |
[…]

### 2020-04-01 ase20/compiler.tex
[ASE] Revised about the word: ECMAScript

@@
 \( \code{Record} \) for bindings.  We also represent constants
-in the ECMAScript specification such as \( \code{empty} \)
+in ECMAScript such as \( \code{empty} \)
 and \( \code{normal} \) as \( \code{Singleton} \) data types

### 2020-04-01 ase20/conclusion.tex
[ASE] Revised about the word: ECMAScript

--- 2019-08-24 icse20/conclusion.tex
@@
 \section{Conclusion}\label{sec:conclude}
-The annual updates of the ECMAScript specification makes it difficult to
+The annual updates of the ECMAScript makes it difficult to
 build program analysis or formal verification of JavaScript due to the
@@
 we proposed a tool \( \tool \), which \textit{automatically} extracts the
-syntax and semantics specified in the ECMAScript specification.  The tool
+syntax and semantics specified in ECMAScript.  The tool
 generates a parser from a language grammar written in \( \bnfes \), and
@@
 as an example case study.  We also support \textsf{Fault Localizer} to
-adapt updates of ECMAScript specification by suggesting new rules.
-We evaluated \( \tool \) by applying it to ECMAScript 2020 with Test262.
+adapt updates of ECMAScript by suggesting new rules.
+We evaluated \( \tool \) by applying it to ES10 with Test262.
 The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.

### 2020-04-01 ase20/eval.tex
[ASE] Revised about the word: ECMAScript

--- 2019-08-24 icse20/eval.tex
@@
 \item RQ2. \textbf{Correctness:} Do the extracted syntax and semantics
-from ECMAScript 2020 behave correctly?
+from ES10 behave correctly?
 \item RQ3. \textbf{Adaptability:} Is \( \tool \) applicable to
@@
 We evaluate the effectiveness of \( \tool \) by applying it to the
-most recent five versions of the ECMAScript specifications, ECMAScript
-2016 to 2020.  We measured for how many grammar productions and
+most recent five versions of ECMAScript, ES6 to ES10.
+We measured for how many grammar productions and
 steps in abstract algorithms \( \tool \) automatically generates parsers and
@@
   \centering
-  \caption{Testing results of Test262 for ECMAScript 2020}
+  \caption{Testing results of Test262 for ES10}
   \label{table:test262}
@@
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
+    \rowcolor{gainsboro} \textbf{ES10 Tests} & \textbf{29,125}\\
     \aboverulesepcolor{gainsboro}\midrule
@@
 To evaluate the correctness of \( \tool \), we developed a JavaScript
-interpreter based on the extracted syntax and semantics from
-ECMAScript 2020.  Among 9,657 steps in ECMAScript 2020,
+interpreter based on the extracted syntax and semantics from ES10.
+Among 9,657 steps in ES10,
 8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
@@
 contains tests for extensions and in-progress features, we excluded
-them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
+them to focus on the semantics of ES10.  As Table~\ref{table:test262} shows,
 Test262 consists of 36,794 tests and we excluded 7,669 tests for
@@
 is confirmed, the committee changes its stage to Finished and
-integrates it into the next version of the ECMAScript specification.
+integrates it into the next version of ECMAScript.
 Otherwise, the committee changes its stage to Inactive.  Thus, we
@@
 operator, we can reduce code size by implementing it as \( \code{x?.p} \).
-We extended ECMAScript 2020 with this proposal and applied \( \tool \)
+We extended ES10 with this proposal and applied \( \tool \)
 to the extended specification.  We found that \textsf{Parser Generator}
@@
 However, we noticed that several algorithm steps have different styles
-from existing ECMAScript specifications.  Thus, we revised them to the
+from existing ECMAScript.  Thus, we revised them to the
 original style, sent three pull requests to the GitHub repository
@@
 specification error detection.  While applying \( \tool \) to
-ECMAScript 2020, we found three specification errors.  We fixed them
+ES10, we found three specification errors.  We fixed them
 and sent pull requests to the official GitHub repository of

### 2020-04-01 ase20/impl.tex
[ASE] Revised about the word: ECMAScript

@@
 tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
-double-blind review process.}, which targets
-ECMAScript 2020~\cite{es2020}.
+double-blind review process.}, which targets ES10~\cite{es10}.
 
@@
 %The URL of the tool is anonymized due to a double-blind review process.},
-%which targets ECMAScript 2020~\cite{es2020}.
+%which targets ES10~\cite{es10}.
 
 \subsection{Excluded Language Features}\label{sec:exclusion}
-We decided not to support the following ECMAScript 2020 features:
+We decided not to support the following ES10 features:
 
@@
 \paragraph{Non-Strict Mode}
-Since ECMAScript 5, JavaScript introduced strict mode to
+Since ES5.1, JavaScript introduced strict mode to
 provide different semantics.  It
 provides more stable semantics by preventing unsafe actions or
-throwing originally ignored errors.  However, the ECMAScript
-specification states that ``Strict mode does not restrict or modify
+throwing originally ignored errors.  However, ECMAScript
+states that ``Strict mode does not restrict or modify
 any aspect of the ECMAScript semantics that must operate consistently
@@
 \paragraph{Early Errors}
-ECMAScript specifications use Early Error Rules to preclude invalid code
+ECMAScript uses Early Error Rules to preclude invalid code
 before evaluation. For example, an Early Error Rule checks whether
@@
   \centering
-  \caption{Compile rules in ECMAScript 2020}
+  \caption{Compile rules in ES10}
   \label{table:rules}
@@
 requires compile rules to compile given abstract algorithms to \( \ires \)
-functions.  In order to cover the entire ECMAScript 2020 specification,
+functions.  In order to cover the entire ES10,
 we defined compile rules for only seven kinds as summarized in
@@
 all of them generate \( \ires \) expressions, they represent different
-contexts in the ECMAScript specification.  For example,
+contexts in ECMAScript.  For example,
 \( \code{Expr} \) represents a context where any expression can appear,
@@
 \subsection{Global Setting}
-We manually implemented \textsf{Global Setting} for ECMAScript 2020,
+We manually implemented \textsf{Global Setting} for ES10,
 which has two parts: ECMAScript data types and built-in objects.
@@
 \paragraph{ECMAScript Data Types}
-In ECMAScript 2020, Section 6 \textsf{ECMAScript Data Types and Values}
+In ES10, Section 6 \textsf{ECMAScript Data Types and Values}
 describes data types used in the specification.  It describes not only

### 2020-04-01 ase20/parser.tex
[ASE] Revised about the word: ECMAScript

--- 2019-08-23 icse20/parser.tex
@@
 In this section, we explain how to automatically generate JavaScript
-parsers from a given ECMAScript specification.
+parsers from a given ECMAScript.
 
 \subsection{\( \bnfes \): Grammar for ECMAScript}
-The ECMAScript specification describes the JavaScript syntax using an
+ECMAScript describes the JavaScript syntax using an
 extension of the BNF notation.  We formally define the notation and
@@
 tokens.  Thus, we just manually supported them by following the rules
-in ECMAScript 2020.  In addition, the rules rarely change; since
-ECMAScript 5.1 written in 2011, only one sub-rule was added.
+in ES10.  In addition, the rules rarely change; since
+ES5.1 written in 2011, only one sub-rule was added.
 
@@
 left recursion but also indirect one in Packrat parsing.  While we can
-adopt the mechanism, we found that the ECMAScript 2020 syntax does not
+adopt the mechanism, we found that the ES10 syntax does not
 use indirect left recursion.  Thus, we decided to just remove direct

### 2020-04-01 ase20/related.tex
[ASE] Revised about the word: ECMAScript

--- 2019-08-24 icse20/related.tex
@@
 an extension of the $\lambda$ calculus, it does not show the semantics
-correspondence defined in the ECMAScript specification.  KJS~\cite{kjs} and
+correspondence defined in ECMAScript.  KJS~\cite{kjs} and
 JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
-the ECMAScript specification to their own formal languages.  KJS mapped
-ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
+ECMAScript to their own formal languages.  KJS mapped
+ES5.1 in the K framework~\cite{kframework}, which can be used
 for program verification and analysis.  Similarly, JaVerT converts the

### 2020-04-01 ase20/abstract.tex
Revised Abstract and Introduction

@@
 ECMAScript 6 (ES6, 2015).  Moreover, ECMAScript has been annually updated since ES6,
-which made already five releases after ES5.1.
+which already made five releases after ES5.1.
 
@@
 into \( \ires \), an Intermediate Representation that we designed for
-ECMAScript.  For the five most recent ECMAScript versions and the
-current draft of the next ECMAScript (ES11, 2020), \( \tool \) automatically
+ECMAScript.  For the five most recent ECMAScript versions, \( \tool \) automatically
 synthesized parsers for all versions, and compiled \inred{XX.XX}\% of the
 algorithm steps on average.  After we complete the missing parts manually,
-the extracted core semantics of ES11 passed all \inred{XX,XXX} applicable tests.
+the extracted core semantics of the latest ECMAScript version (ES10, 2019)
+passed all \inred{XX,XXX} applicable tests.
 Using this \textit{first formal semantics of modern JavaScript}, we found
-\inred{X} specification errors in ES11, which were all confirmed by
+\inred{X} specification errors in ES10, which were all confirmed by
 the Ecma Technical Committee 39.  Furthermore, we also successfully
-applied \( \tool \) to \inred{X} feature proposals that are candidates
-for inclusion in ECMAScript, which shows the forward compatibility of \( \tool \).
+applied \( \tool \) to the current draft of the next ECMAScript (ES11, 2020),
+which shows the forward compatibility of \( \tool \).
 \end{abstract}

### 2020-04-01 ase20/intro.tex
Revised Abstract and Introduction

@@
 that takes programs and produces their Intermediate
-Representations (IRs) to indirectly represent the semantics of given programs.
-As illustrated in Figure~\ref{fig:existing}, the compiler front-end consists of a parser
+Representations (IRs) to indirectly represent the semantics of the given programs.
+As illustrated in Figure~\ref{fig:existing}, a compiler front-end consists of a parser
 that constructs Abstract Syntax Trees (ASTs) of given JavaScript programs, and
-an AST-IR translator that converts ASTs to their own IRs.  This approach helps
+an AST-IR translator that converts ASTs to their own IRs.  It helps
 researchers focus on IRs without worrying about diverse and enormous features of
@@
 IR-based semantics extraction \textit{manually} build parsers and translators.
-Although it was a reasonable approach until ECMAScript 5.1 (ES5.1,
-2011)~\cite{es5}, the manual approach is too tedious, labor-intensive, and
+Although manually building them was reasonable until ECMAScript 5.1 (ES5.1,
+2011)~\cite{es5}, it is too tedious, labor-intensive, and
 error-prone to deal with the large size of \textit{modern JavaScript} since ECMAScript 6
@@
 \textit{four months} to implement an AST-IR translator for 1,370 steps out of 2,932
-steps in 368 abstract algorithms. However, the most recent version of ECMAScript
+steps in 368 abstract algorithms~\cite{kjsslides}. However, the most recent version of ECMAScript
 (ES10, 2019)~\cite{es10} has 1,731 abstract algorithms consisting of 10,068
-steps. Thus, the manual approach does not seem to be scalable enough to build
-an AST-IR translator for modern JavaScript
+steps. Thus, the manual approaches do not seem to be scalable enough to build
+an AST-IR translator for modern JavaScript,
 and indeed no formal semantics exists for ES6 to ES10.
@@
 To handle these frequent and massive updates of ECMAScript,
-the manual approach requires researchers to manually update parsers and AST-IR translators,
+the manual approaches require researchers to manually update parsers and AST-IR translators,
 which incurs tremendous efforts.
@@
 synthesizing parsers and translators. For syntax, ECMAScript utilizes its own
-special variant of the EBNF with parametric non-terminals, conditional
+special variant of EBNF with parametric non-terminals, conditional
 alternatives, and various special terminal symbols.  Thus, no existing parser
@@
     representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
-    with the five most recent ECMAScript versions and the current draft of the next
-    ECMAScript (ES6 to ES11).   \( \tool \) automatically generated
+    with the five most recent ECMAScript versions (ES6 to ES10).   \( \tool \) automatically generated
     parsers for all versions, and automatically compiled
@@
     formal semantics of modern JavaScript}.}  The semantics targets the
-    core of ES11, and \( \tool \) successfully synthesizes its
+    core of ES10, and \( \tool \) successfully synthesizes its
     parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
@@
     conformance test suite, and the semantics passed all \inred{XX,XXX}
-    applicable tests.  Moreover, we found \inred{X} specification errors in ES11
+    applicable tests.  Moreover, we found \inred{X} specification errors in ES10
     thanks to the formal semantics.  They were all confirmed by TC39 and will be
@@
   \item \textbf{\( \tool \) is also \textit{forward compatible} with new language features
-    proposed for future ECMAScript specifications.}  TC39 manages proposals of
-    new language features in an open source
-    project\footnote{https://github.com/tc39/proposals}.  Out of five stages
-    of proposals (from Stage 0 to Stage 4), proposals in Stage 4 (Finished)
-    are ready for inclusion in the next ECMAScript, and proposals in
-    Stage 3 (Candidate) are in the last stage before finished.  We
-    evaluated the forward compatibility of \( \tool \) by applying it
-    to all \inred{XX} proposals in Stage 3. It successfully
-    synthesized parsers for all proposals, and automatically
-    compiled \inred{XX} out of \inred{XX} algorithm steps for all
-    proposals.  After completion of the missing parts,
-    each semantics passed all \inred{XX} tests.
+    proposed for future ECMAScript specifications.}  
+    We evaluated the forward compatibility of \( \tool \) by applying it
+    to the current draft of the next ECMAScript (ES11, 2020).  It successfully
+    synthesized a parser and automatically
+    compiled \inred{XX} out of \inred{XX} algorithm steps for ES11.
+    After completion of the missing parts, the extracted semantics passed all \inred{XX} tests.
 \end{itemize}

### 2020-04-01 ase20/parser.tex
[ASE] Revised Section 3 (Parser Generator)

@@
 \subsection{\( \bnfes \): Grammar for ECMAScript}
-ECMAScript describes the JavaScript syntax using an
-extension of the BNF notation.  We formally define the notation and
-dub it \( \bnfes \).  It consists of a number of \textit{productions}
-with the following form:
+ECMAScript describes the JavaScript syntax using a variant of the extended BNF.
+We formally define the notation and dub it \( \bnfes \).  It consists of a
+number of \textit{productions} with the following form:
 \[
@@
 
-\subsection{Lookahead Parsers}
-To support \( \bnfes \) correctly, we propose a recursive descent
-parser generator that handles both backtracking and lookahead tokens.
+\subsection{Lookahead Parsing}
+To support \( \bnfes \) correctly, we extend PEG-based parser generation
+techniques with lookahead parsing.
 
@@
 
-\textbf{Approach.} 
-Our goal is to automatically generate a JavaScript parser from a given
-ECMAScript grammar written in \( \bnfes \).  Among various parser
-generators, we chose Scala parser combinators defined in
-\textit{Parsing Expression Grammar (PEG)}~\cite{peg}.
-PEG is a top-down (LL-style) recursive descent parser with
-\textit{backtracking}.  It visits each alternative of a production in
-order and backtracks to its previous production when parsing fails.
-We chose Scala parser combinators because of the following reasons:
+\textbf{Background (Parsing Expression Grammar).}
+Most parser generators target context-free languages with specific parsing
+algorithms for Context-Free Grammar (CFG): JavaCC with LL(k)~\inred{\cite{llk}},
+Bison with GLR~\inred{\cite{glr}}, and ANTLR with
+ALL(*)~\inred{\cite{all-star}}.  However, they are not directly applicable for
+ECMAScript syntax because ECMAScript lexical and syntactic grammars require
+context-sensitive lexers and parsers:
+\begin{itemize}[leftmargin=0.5cm]
+  \item \textbf{Context-sensitive tokens:}
+    ECMAScript tokens are context-sensitive because of JavaScript regular
+    expressions and template strings.  For example, \( \code{/x/g} \) could be a
+    single regular expression token or four tokens that represent division by
+    variables \( \code{x} \) and \( \code{g} \) depending on enclosing contexts.
+    Thus, lexers should be evaluated during parsing not before parsing.
+  \item \textbf{Context-sensitive \( \bnfes \) symbols:}
+    \( \bnfes \) supports context-sensitive symbols: positive (negative)
+    lookahead \( +\symb \) (\( -\symb \)), exclusion \( \symb \butnot \symb' \),
+    and no line-terminator \( \nolt \).  They have highly expressive power. It
+    could even represent the classic non-context-free language \( \{ a^n b^n c^n
+    : n \geq 1 \} \) with the following productions:
+    \[
+      \begin{array}{r@{~}c@{~}lr@{~}c@{~}l}
+        \NT{S} &::=& +(\NT{X}~\T{c})~\NT{A}~\NT{Y}&
+        \NT{X} &::=& \T{a}~\NT{X}?~\T{b}\\
+        \NT{A} &::=& \T{a}~\NT{A}?&
+        \NT{Y} &::=& \T{b}~\NT{Y}?~\T{c}\\
+      \end{array}
+    \]
+    It is not trivial to support such \( \bnfes \) symbols in CFG-based
+    parser generators.
+\end{itemize}
 
-\begin{itemize}[leftmargin=0.5cm]
-\item \textbf{Context-sensitive tokens:} ECMAScript tokens are
-context-sensitive because of JavaScript regular expressions and
-template strings.  For example, \( \code{/x/g} \) could be a single
-regular expression token or four tokens that represent division by
-variables \( \code{x} \) and \( \code{g} \) depending on enclosing
-contexts.  Thus, lexers should be evaluated during parsing not before
-parsing.  Since Scala parser combinators also treat lexers as parsers,
-we can use appropriate lexers depending on parsing contexts.
-\item \textbf{\( \bnfes \) symbols:} PEG can represent \( \bnfes \)
-symbols intuitively as we explain in Section~\ref{sec:convert-bnfes}.
-\item \textbf{Multiple starting non-terminals:} Since ECMAScript 6,
-both scripts and modules serve as starting points of parsers.  Scala
-parser combinators allow to use any non-terminals as parsers.
-\item \textbf{Parsing at run-time:} JavaScript supports the \( \code{eval} \)
-function that parses a given JavaScript string value to code and
-evaluates it.  Moreover, syntax-directed abstract algorithms use special
-phrases like ``the \( N \) that is \textit{covered by} \( P \),'' which
-means that a generalized parser parses the syntax tree \( P \) because
-finding a specific parser to correctly parse it requires its
-evaluation context.  When a JavaScript interpreter encounters such a
-phrase, it decides a specific parser to \( N \) and parses the given
-syntax tree \( P \) with the non-terminal \( N \) again at run time.
-\end{itemize}
+Unlike CFG-based parser generators, parser generators based on \textit{Parsing
+Expression Grammar (PEG)}~\cite{peg} can easily resolve these problems.  PEGs
+are defined with a top-down (LL-style) recursive descent parser with
+\textit{backtracking}.  It visits each alternative of a production in order and
+backtracks to its previous production when parsing fails.  PEG-based parser
+generators treat lexers as parsers thus we can use appropriate lexers depending
+on parsing contexts.  Moreover, PEGs support \textit{and-predicate} (\&) and
+\textit{not-predicate} (!) operators that denote the same meaning of the
+positive and negative lookahead symbols in \( \bnfes \), respectively. Thus, we
+could easily support context-sensitive tokens and \( \bnfes \) symbols in
+PEG-based parser generators.
 
@@
 
-\textbf{Problem: Prioritized Choices.} While PEG provides all the
-features we discussed so far, it has one fundamental problem:
-\textit{prioritized choices}.  In PEG, the pipe \( \mid \) operator
-denotes a prioritized choice; even when multiple alternatives are
-applicable, PEG always picks the first success alternative.  However,
-some non-terminals of the ECMAScript grammar accept multiple
-alternatives for given input strings.  For example, consider the
-following simplified grammar of the JavaScript expressions:
-\[
+\textbf{Problem: Prioritized Choices.}
+While PEG-based parser generators support the context-sensitivity,
+PEGs have one fundamental difference with \( \bnfes \): \textit{prioritized
+choices}.  PEGs use prioritized choice operator `\( / \)' instead of the unordered
+pipe operator `\( \mid \)' in \( \bnfes \); even when multiple alternatives are
+applicable, PEGs always pick the first success alternative.  For example,
+consider the following simplified PEG for the JavaScript expressions:
+\begin{equation}
   \begin{array}{r@{~}c@{~}l}
-    \NT{A} &::=& \NT{T} \T{;} \mid \NT{A} \; \T{+} \; \NT{T} \T{;} \\
-    \NT{T} &::=& \T{a} \mid \T{a} \T{(} \T{b} \T{)}\\
+    \NT{S} &::=& \NT{E} ~ \T{+} ~ \NT{E}\\
+    \NT{E} &::=& \T{x} ~/~ \T{x} \T{.} \T{p}\\
   \end{array}
-\]
-The non-terminal \( \NT{T} \) should accept both alternatives for
-\( \code{a(b);} \), but PEG-based parsers fail to parse it because the
-first alternative \( \T{a} \) succeeds first and the second alternative
-\( \T{a} \T{(} \T{b} \T{)} \) is not reachable.  A simple solution is
-to change the order of alternatives like \( \NT{T} ::= \T{a} \T{(} \T{b} \T{)} \mid \T{a} \),
-but ensuring correct order is not trivial because it requires
-calculation of their inclusion relationship.  Moreover, simple
-reordering does not work for some productions:
-\[
+  \label{eq:simple-js}
+\end{equation}
+If it is written in \( \bnfes \), the string \( \code{x+x.p} \) is in this
+language. However, in this PEG, the first alternative \( \T{x} \) of \( \NT{E}
+\) is always taken if the input string starts with \( \code{x} \). Thus, the
+second alternative \( \T{x}\T{.}\T{p} \) of \( \NT{E} \) is unreachable and \(
+\code{x+x.p} \) is not in the language.  A simple solution is just to change the
+order of alternatives of \( \NT{E} \) like \( \NT{E} ::= \T{x} \T{.} \T{p} ~/~
+\T{x} \).  However, simple reordering is not the solution for all cases:
+\begin{equation}
   \begin{array}{r@{~}c@{~}l}
-    \NT{A} &::=& \NT{B} \; \T{b}\\
-    \NT{B} &::=& \T{a} \mid \T{a} \; \T{b}\\
+    \NT{S} &::=& \NT{A} ~ \T{b}\\
+    \NT{A} &::=& \T{a} ~/~ \T{a} \T{b}\\
   \end{array}
-\]
-The non-terminal \( \NT{A} \) should successfully parse two strings
-\( \code{ab} \) and \( \code{abb} \),  but it accepts only \( \code{ab} \),
-and it accepts only \( \code{abb} \) if \( \NT{B} ::= \T{a} \; \T{b} \mid \T{a} \).
-Hence, we should re-structure the above rules to accept both strings
-in traditional PEG grammars.
+\end{equation}
+If it is written in \( \bnfes \), both strings \( \code{ab} \) and \( \code{abb}
+\) is in this language. However, this PEG only accepts the string \( \code{ab}
+\), and another PEG with the reordered production \( \NT{A} ::= \T{a} \T{b}
+~/~ \T{a} \) only accepts \( \code{abb} \).
 
@@
     \rhsfirst{\symb_1 \cdots \symb_n} &=& \symbfirst{\symb_1} \firstplus
-    \symbfirst{\symb_2 \cdots \symb_n}\\
+    \rhsfirst{\symb_2 \cdots \symb_n}\\
     && \text{where} \; x \firstplus y = \left\{
@@
 \label{fig:first-tokens}
+\vspace{-1em}
 \end{figure}
@@
 \textbf{Solution: Lookahead Tokens.}
-To alleviate the problem, we propose \textit{lookahead parsers},
-which are recursive descent parsers extended with backtracking and
-\textit{lookahead tokens}.  They keep track of the next possible
-tokens by statically calculating first tokens of each symbol using the
-algorithm in Figure~\ref{fig:first-tokens}.  For example, the
-following steps explain how to utilize lookahead tokens during parsing
-with the input \( \code{a(b);} \):
+To alleviate the problem, we propose \textit{lookahead parsing}, which is an
+extended parsing algorithm for PEGs with \textit{lookahead tokens}.  The key
+idea of lookahead parsing is to keep track of the next possible tokens by
+statically calculating first tokens of each symbol using the algorithm in
+Figure~\ref{fig:first-tokens}.  For example, the following steps explain how to
+utilize lookahead tokens during parsing of the string \( \code{x+x.p} \) with
+the PEG in Equation~(1): %\ref{eq:simple-js}:
 \begin{center}
-  \includegraphics[width=0.3\textwidth]{img/laparser.png}
+  \includegraphics[width=0.3\textwidth]{img/laparser.pdf}
 \end{center}
-Each node \( \symb^*[\la] \) denotes a sequence of symbols \( \symb^* \)
-with a set of lookahead tokens \( \la \).  The parsing process follows
-a pre-order traversal.  It starts from the starting non-terminal \( \NT{A} \)
-with the special lookahead \( \emptyfirst \), which denotes the end of
-inputs.  Then, it visits the first alternative \( \NT{T} \T{;} \) with
-the same lookahead.  Each symbol is visited with its corresponding
-lookahead, which is the first tokens of the right next symbol.
-For example, for the symbol \( \NT{T} \), the next symbol is \( \T{;} \)
-and its first token is itself.  Thus, the parser visits \( \NT{T} \)
-with the lookahead \( \T{;} \).  The most important point here
-is the first alternative \( \T{a} \) of the
-non-terminal \( \NT{T} \).  The parser visits it with the lookahead \( \T{;} \)
-but the next token of the input string \( \code{a(b);} \) is \( \code{(} \)
-rather than \( \code{;} \).  Hence, it fails to parse the input string
-even though the current token is the same with the terminal \( \T{a} \).
-Therefore, the parser can visit the next alternative \( \T{a}\T{(}\T{b}\T{)} \)
-and successfully parses the input \( \code{a(b);} \).
+Each node \( \symb[\la] \) denotes a symbol \( \symb \) with a set of lookahead
+tokens \( \la \).  The underlined character in the string of each node denotes
+the current position in parsing process that follows a pre-order traversal.  It
+starts from the starting non-terminal \( \NT{S} \) with the special lookahead \(
+\emptyfirst \), which denotes the end of inputs.  Then, it visits the first
+alternative \( \NT{E}~\T{+}~\NT{E} \) with the same lookahead \( \emptyfirst \).
+Each symbol is visited with its corresponding lookahead, which is the first
+tokens of the right next symbol.  For example, for the second symbol \( \T{+} \)
+in \( \NT{E}~\T{+}~\NT{E} \), the next symbol is \( \NT{E} \) and its first
+tokens are:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \symbfirst{\NT{E}} &=& \rhsfirst{\T{x}} \cup \rhsfirst{\T{x.p}}\\
+                       &=& \symbfirst{\T{x}} \cup (\symbfirst{\T{x}} \firstplus
+    \rhsfirst{\T{.p}}) = \{ \T{x} \}\\
+  \end{array}
+\]
+Thus, the parser visits \( \T{+} \) with the lookahead \( \T{x} \).
+The most important point here is the difference between two visits of the
+non-terminal \( \NT{E} \) in \( \NT{E}~\T{+}~\NT{E} \).  The first visit of \(
+\NT{E} \) has the lookahead \( \T{+} \) and the actual next character after
+matching \( \T{x} \) is also \( \T{+} \). Thus, the first alternative \( \T{x}
+\) of \( \NT{E} \) is taken for the first visit.  However, in the second visit
+of \( \NT{E} \), the lookahead is the end of inputs \( \emptyfirst \) but the
+next character after matching \( \T{x} \) is the dot character (\( \T{.} \))
+instead of the end of inputs.  Thus, the second alternative \( \T{x.p} \) is
+taken in the second visit and the parser successfully parses the input \(
+\code{x+x.p} \) now.
+
+We formally define the semantics of lookahead parsers in Figure~\ref{fig:laparser}.
+The helper function \( \getlap{\la} \) generates a parser by combining all
+tokens in the lookahead \( \la \) using prioritized choices.
+In this case, the order does not change the semantics of lookahead parsers
+because \( \getlap{\la} \) just checks the existence of a given token.
+
+\subsection{Implementation}\label{sec:convert-bnfes}
+We implemented lookahead parsing technique by extending Scala parser combinators
+library, which is a Scala library for PEG-based parser generations.  We
+developed {\sf Parser Generator} to synthesize PEG-based parsers with
+lookahead parsing for \( \bnfes \).
 
@@
 
-We formally define the semantics of lookahead parsers in Figure~\ref{fig:laparser}.
-The helper function \( \getlap{\la} \) generates a parser by combining all
-tokens in the lookahead \( \la \) using prioritized choices.
-In this case, the order does not change the semantics of lookahead parsers
-because \( \getlap{\la} \) just checks the existence of a given token.
-
-\subsection{Implementation}\label{sec:convert-bnfes}
-We implemented lookahead parsers by extending Scala parser combinators
-with two functions corresponding to Figure~\ref{fig:first-tokens} and
-Figure~\ref{fig:laparser}.
-
 \smallskip
@@
 \textbf{AST Generation.}
-We first automatically generate ASTs as Scala case classes from a
-given \( \bnfes \) grammar.  Because lexical grammars do not affect
-the ECMAScript semantics, we represent them as string values.
-For parser grammars, we automatically synthesize a Scala file that has
-classes of syntax trees.  For each production \(
+{\sf Parser Generator} first automatically synthesizes ASTs as Scala case classes
+from a given \( \bnfes \) grammar.  Because structure of lexical productions do
+not affect the ECMAScript semantics, we represent lexical non-terminals as
+string values.  For each syntactic production \(
   \NT{A}(\param_1, \cdots, \param_k) ::=
@@
   (\cond_n \Rightarrow)^? \rhs_n
-\), the AST generator defines the \( \code{A} \) trait and multiple
+\), the generator synthesizes the \( \code{A} \) trait and multiple
 subclasses \( \code{A}_i \) of \( \code{A} \) for \(0 \le i \le n-1\)
@@
 \textbf{Parser Generation.}
-The next step is to automatically extract parsers from the given \(
-\bnfes \) grammar.  The conversion from \( \bnfes \) symbols into
-Scala code is as follows:
-\[
-\small
-  \begin{array}{ccc}
-%    \bnfes \; \text{symbols} &\Rightarrow& \text{Scala codes}\\\hline
-    \epsilon &\Rightarrow& \scode{MATCH}\\
-    \T{a} &\Rightarrow& \scode{"a"}\\
-    \NT{A}(\argument_1, \cdots, \argument_n) &\Rightarrow& \scode{A(a1, .. , an)}\\
-    \symb? &\Rightarrow& \scode{opt(s)}\\
-    \pm\symb &\Rightarrow& \pm\scode{\symb} \\
-    \symb \butnot \symb' &\Rightarrow& \scode{s\textbackslash s'}\\
-    \nolt &\Rightarrow& \scode{NoLineTerminator}\\
-  \end{array}
-\]
-where \( \code{MATCH} \) denotes the empty sequence of lookahead parsers.
-Each string literal gets implicitly converted to a lookahead parser via
-Scala implicit conversion.  The \( \code{opt(s)} \) function is the
-same with \( \code{s | MATCH} \).  We also define the \( \code{\textbackslash} \) 
-operator between parsers to support exclusive parsers.
-Finally, we provide the \( \code{NoLineTerminator} \) parser, which uses
-the white space parsers to check the existence of line terminators.
-Our approach can support such a parser because we also automatically
-generate lexers not only parsers of the ECMAScript syntax.  Then, the 
-automatically synthesized parser from the production \textit{ArrayLiteral}
-in Figure~\ref{fig:array-literal}(a) is the one in Figure~\ref{fig:array-literal}(b).
+The next step is to automatically synthesizes parsers for each production in \(
+\bnfes \).  We extended Scala parser combinators to support lookahead parsing
+and \( \bnfes \) notations. For example, the synthesized parser from the
+production \textit{ArrayLiteral} in Figure~\ref{fig:array-literal}(a) is the one
+in Figure~\ref{fig:array-literal}(b).  The naive implementation of lookahead
+parsing has exponential parsing time because of backtracking.  To reduce the
+complexity to linear time, we applied the memoization technique introduced in
+Packrat parsing~\cite{packrat} proposed by Ford et al.  \inred{Moreover, we also
+implemented the \textit{growing the seed} technique presented by Warth et
+al~\cite{packrat-lr} to support direct and even indirect left recursive
+productions.  It helps to synthesize parsers without changing the structure of
+each production in \( \bnfes \).}
 
-We support the automatic semicolon insertion algorithm, which
-is the most distinctive parsing feature in ECMAScript.  We extended
-our parser implementation to keep track of the right-most position
-that fails to be parsed in a given input.  In ECMAScript, the token at that
-position is defined as an \textit{offending token} and the automatic
-semicolon insertion algorithm is defined with such tokens.  The
-algorithm is simple when we already have the positions of offending
-tokens.  Thus, we just manually supported them by following the rules
-in ES10.  In addition, the rules rarely change; since
+The synthesized parsers also support the automatic semicolon insertion
+algorithm, which is one of the most distinctive parsing features in ECMAScript.
+We extended our parsing algorithm to keep track of the right-most position that
+fails to be parsed in a given input.  In ECMAScript, the token at that position
+is defined as an \textit{offending token} and the automatic semicolon insertion
+algorithm is defined with such tokens.  The algorithm is simple when we already
+have the positions of offending tokens.  Thus, we just manually supported them
+by following the rules defined in Section
+11.9\footnote{https://www.ecma-international.org/ecma-262/\#sec-automatic-semicolon-insertion}
+in ES10.  The rules about automatic semicolon insertion rarely change; since
 ES5.1 written in 2011, only one sub-rule was added.
-
-\smallskip
-
-\textbf{Discussion.}
-While implementing lookahead parsers in Scala, we resolved two issues.
-
-First, one of the critical weak points of recursive descent parsing
-with backtracking is its performance.  To support backtracking, it
-requires exponential time relative to the input size.  Luckily, Ford
-et al~\cite{packrat} proposed Packrat parsing that provides linear 
-time complexity using memoization.  By treating each parser as a
-function from the current input position to a parsing result, it just
-memoizes each parser using input positions, which dramatically reduces
-redundant parsing trials.  In a similar way, we treat each lookahead
-parser as a function from a pair of lookahead tokens and input
-positions to a parsing result.
-
-The second issue is that recursive descent parsers do not support left
-recursion in grammars.  If a grammar has a left recursion, its parser
-falls into an infinite loop.  To resolve this problem, Warth et
-al~\cite{packrat-lr} proposed a mechanism to support not only direct
-left recursion but also indirect one in Packrat parsing.  While we can
-adopt the mechanism, we found that the ES10 syntax does not
-use indirect left recursion.  Thus, we decided to just remove direct
-left recursion by defining sub productions.

### 2020-04-02 ase20/abstract.tex
Forward compatibility by Stage 4 proposals not by ES11

@@
 the Ecma Technical Committee 39.  Furthermore, we also successfully
-applied \( \tool \) to the current draft of the next ECMAScript (ES11, 2020),
+applied \( \tool \) to \inred{X} feature proposals that are ready
+for inclusion in the next ECMAScript, 
 which shows the forward compatibility of \( \tool \).

### 2020-04-02 ase20/intro.tex
Forward compatibility by Stage 4 proposals not by ES11

@@
 Despite its popularity, JavaScript developers often suffer from its intricate
-semantics, which may cause unexpected behaviors.  For example, calling the
-following JavaScript function seems to always return \( \code{false} \):
+semantics, which may cause unexpected behaviors.  For example, the
+following function may seem to always return \( \code{false} \):
 \begin{lstlisting}[style=myJSstyle]
@@
 classes, the \( \code{for-of} \) operator, the \( \code{async} \) functions, and
-generators.  For example, consider KJS~\cite{kjs}.
-KJS is one of formal semantics of ES5.1
-and it is defined on top of \( \kframework \), which is a framework for
-defining language semantics.  According to an author of KJS, it took
+generators.  For example, consider KJS~\cite{kjs},
+one of formal semantics of ES5.1 defined on top of \( \kframework \), which is
+a framework for defining language semantics.
+According to an author of KJS, it took
 \textit{four months} to implement an AST-IR translator for 1,370 steps out of 2,932
@@
 synthesizing parsers and translators. For syntax, ECMAScript utilizes its own
-special variant of EBNF with parametric non-terminals, conditional
+variant of EBNF with parametric non-terminals, conditional
 alternatives, and various special terminal symbols.  Thus, no existing parser
@@
     insertion. For semantics, we propose semi-automatic synthesis of AST-IR
-    translators assisted by compile rules because of the
-    difficulty in handling the semantics written in a natural language.  Compile rules describe how
-    each step of abstract algorithms is converted into our intermediate
+    translators assisted by compile rules due to the
+    difficulty in handling the semantics written in a natural language.  Compile rules describe
+    how to convert each step of abstract algorithms into our intermediate
     representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
@@
      We evaluated the forward compatibility of \( \tool \) by applying it
-    to the current draft of the next ECMAScript (ES11, 2020).  It successfully
-    synthesized a parser and automatically
-    compiled \inred{XX} out of \inred{XX} algorithm steps for ES11.
+     to all \inred{XX} proposals that are ready for inclusion in the next ECMAScript  (ES11, 2020).
+    It automatically synthesized parsers and
+    compiled \inred{XX} out of \inred{XX} algorithm steps for all the proposals.
     After completion of the missing parts, the extracted semantics passed all \inred{XX} tests.

### 2020-04-03 ase20/overview.tex
Revised Sec. 2

@@
 In this section, we introduce the overall structure of \( \tool \)
-depicted in Figure~\ref{fig:overview} and the outline of the paper.
+depicted in Figure~\ref{fig:overview}.
 Compared to the existing approaches shown in
@@
 The motivation of automatically extracting syntax and semantics of JavaScript
-from the ECMAScript is twofold: 1) ECMAScript is written in a well-organized
-style, and 2) it is available as HTML files using various HTML tags.  As the
-first step, we developed {\sf Spec Extractor} to simply collect and save both
-syntax and semantics into JSON format.  We implemented {\sf Spec Extractor} in
-JavaScript to easily manipulate ECMAScript written in HTML.
+from ECMAScript is twofold: 1) ECMAScript is written in a well-organized
+style, and 2) it is available as HTML files using various HTML tags.
+To easily manipulate ECMAScript written in HTML, we developed
+{\sf Spec Extractor} in JavaScript to extract the syntax and semantics in JSON format.
 
@@
     \includegraphics[width=\textwidth]{img/arrayliteral-syntax.pdf}
-    \caption{The \textit{ArrayLiteral} production in ES10}
+    \caption{\textit{ArrayLiteral} production in ES10}
     \label{fig:array-literal-es}
@@
     \vspace*{-1em}
-    \caption{The generated parser for the \textit{ArrayLiteral} production}
+    \caption{Generated parser for the \textit{ArrayLiteral} production}
     \label{fig:array-literal-parser}
   \end{subfigure}
-  \caption{The \textit{ArrayLiteral} production in the ES10 and its generated parser}
+  \vspace*{-1em}
+  \caption{\textit{ArrayLiteral} production in ES10 and its parser}
   \label{fig:array-literal}
-  \vspace*{-1em}
 \end{figure}
@@
 efficiently, we propose \textit{lookahead parsers}, which keep track
-of lookaheads, sets of possible next tokens.  With lookahead parsers,
-generated parsers become more readable and have one-to-one
-mapping to their corresponding grammar productions.
+of lookaheads, sets of possible next tokens.  With lookahead parsing,
+generated parsers now have one-to-one mapping to their corresponding
+grammar productions, improving readability.
 For example, Figure~\ref{fig:array-literal}(b) shows the generated
@@
 parameters and resulting parsers for performance optimization.
-The lazy value \( \code{ArrayLiteral} \) corresponds to the
+The value \( \code{ArrayLiteral} \) corresponds to the
 \textit{ArrayLiteral} production.  In the parser, each string literal
@@
 When the left-hand side of \( \code{\^{}\^{}} \) is matched, its
-right-hand side shows a corresponding AST constructor, where each
-constructor has a number denoting the order among alternatives.
+right-hand side shows a corresponding AST constructor, where the name
+of each constructor has a number denoting the order among alternatives.
 For example, the \( \code{ArrayLiteral0} \) constructor corresponds to
@@
 While they are written in a natural language, the writing style is
-well-organized with ordered steps and tagged tokens.  Our {\sf Spec Extractor}
-reads each abstract algorithm with HTML tags and converts them into JSON files.
+well-organized with ordered steps and tagged tokens.  {\sf Spec Extractor}
+reads abstract algorithms with HTML tags and converts them into JSON files.
 For example, Figure~\ref{fig:array-literal-eval}(a) presents the
@@
 files describing the abstract algorithms, each non-terminal symbol
-(i.e. \textit{ElementList}), local variable (i.e. \textit{array}), code (i.e. \(
-\code{"length"} \)), or value (i.e. \textbf{false}) has the \( \code{<nt>} \),
+(e.g. \textit{ElementList}), local variable (e.g. \textit{array}), code (e.g. \(
+\code{"length"} \)), or value (e.g. \textbf{false}) has the \( \code{<nt>} \),
 \( \code{<var>} \), \( \code{<code>} \), or \( \code{<emu-val>} \) tag,
@@
 
-To translate such abstract algorithms into representations that are
+To translate such abstract algorithms into representations
 suitable for manipulation, we define \( \ires \), a specialized
-intermediate representation for ECMAScript abstract algorithms.  Then,
+intermediate representation for ECMAScript.  Then,
 we develop \textsf{Algorithm Compiler} in Scala using Scala parser
@@
 For example, Figure~\ref{fig:array-literal-eval}(b) presents the generated
-\( \ires \) function for the \textbf{Evaluation} abstract algorithm described in
+\( \ires \) function for the \textbf{Evaluation} abstract algorithm shown in
 Figure~\ref{fig:array-literal-eval}(a).
@@
 The parameter \( \code{Elision} \) has a special value \( \code{absent} \) when
-the non-terminal symbols \textit{Elision}$_{\mbox{\footnotesize opt}}$ is not
-present.  Thus, we convert the condition in the step 4,
+the non-terminal symbol \textit{Elision}$_{\mbox{\footnotesize opt}}$ is not
+present.  Thus, we convert the condition in step 4,
 ``if \textit{Elision} is not present,'' into the equality check with \(
@@
 string values and values are represented as corresponding \( \ires \) values.
-For instance, the code \texttt{"length"} and the value \textbf{false} are
+For instance, the code \texttt{\small "length"} and the value \textbf{false} are
 converted into the string value \( \code{"length"} \) and the boolean value
@@
 which has minor but necessary information to evaluate JavaScript programs
-described in ECMAScript.  They consists of the structure of the standard
+described in ECMAScript such as the structure of the standard
 built-in objects and ECMAScript data types. Putting them all together, we can
@@
 {\sf Global Setting}, it could dramatically reduce the efforts to building
-parsers and translators from the scratch.
+parsers and translators from scratch.
 
-\smallskip
-
-\textbf{Outline.}
-In the remainder of this paper, we describe the detailed techniques of
-\( \tool \).  We first formally define \( \bnfes \) and how to
-automatically generate parsers from given \( \bnfes \) using lookahead
-parsers (Section~\ref{sec:parser}).  Then, we explain how to compile
-abstract algorithms with tagged tokens into \( \ires \) functions using
-compile rules (Section~\ref{sec:compiler}).  After describing implementation
-details (Section~\ref{sec:impl}), we evaluate our tool \( \tool \)
+In the remainder of this paper, we explain the details of how to
+automatically generate parsers (Section~\ref{sec:parser}) and how to compile
+abstract algorithms (Section~\ref{sec:compiler}).  After describing implementation
+details (Section~\ref{sec:impl}), we evaluate \( \tool \)
 (Section~\ref{sec:eval}), discuss related work (Section~\ref{sec:related}), and

### 2020-04-03 ase20/parser.tex
Revised Sec. 3

@@
 of symbols, where a symbol \( \symb \) is one of the following:
-\begin{itemize}[leftmargin=0.5cm]
+\begin{itemize}%[leftmargin=0.5cm]
 \item \( \epsilon \): the empty sequence, which passes without any conditions
@@
 
-\textbf{Background (Parsing Expression Grammar).}
+\textbf{Background: Parsing Expression Grammar.}
 Most parser generators target context-free languages with specific parsing
@@
 Bison with GLR~\inred{\cite{glr}}, and ANTLR with
-ALL(*)~\inred{\cite{all-star}}.  However, they are not directly applicable for
+ALL(*)~\inred{\cite{all-star}}.  However, they are not directly applicable for the
 ECMAScript syntax because ECMAScript lexical and syntactic grammars require
 context-sensitive lexers and parsers:
-\begin{itemize}[leftmargin=0.5cm]
+\begin{itemize}%[leftmargin=0.5cm]
   \item \textbf{Context-sensitive tokens:}
@@
   \item \textbf{Context-sensitive \( \bnfes \) symbols:}
-    \( \bnfes \) supports context-sensitive symbols: positive (negative)
+    \( \bnfes \) supports context-sensitive symbols, which are positive (negative)
     lookahead \( +\symb \) (\( -\symb \)), exclusion \( \symb \butnot \symb' \),
-    and no line-terminator \( \nolt \).  They have highly expressive power. It
-    could even represent the classic non-context-free language \( \{ a^n b^n c^n
+    and no line-terminator \( \nolt \).  They are highly expressive
+    and they can even represent the classic non-context-free language \( \{ a^n b^n c^n
     : n \geq 1 \} \) with the following productions:
@@
     \]
-    It is not trivial to support such \( \bnfes \) symbols in CFG-based
+    However, it is not trivial to support such \( \bnfes \) symbols in CFG-based
     parser generators.
@@
 backtracks to its previous production when parsing fails.  PEG-based parser
-generators treat lexers as parsers thus we can use appropriate lexers depending
+generators treat lexers as parsers, thus we can use appropriate lexers depending
 on parsing contexts.  Moreover, PEGs support \textit{and-predicate} (\&) and
 \textit{not-predicate} (!) operators that denote the same meaning of the
-positive and negative lookahead symbols in \( \bnfes \), respectively. Thus, we
-could easily support context-sensitive tokens and \( \bnfes \) symbols in
+positive and negative lookahead symbols in \( \bnfes \), respectively. Therefore, we
+can easily support context-sensitive tokens and \( \bnfes \) symbols in
 PEG-based parser generators.
@@
 PEGs have one fundamental difference with \( \bnfes \): \textit{prioritized
-choices}.  PEGs use prioritized choice operator `\( / \)' instead of the unordered
+choices}.  PEGs use the prioritized choice operator `\( / \)' instead of the unordered
 pipe operator `\( \mid \)' in \( \bnfes \); even when multiple alternatives are
-applicable, PEGs always pick the first success alternative.  For example,
-consider the following simplified PEG for the JavaScript expressions:
+applicable, PEGs always pick the first successful alternative.  For example,
+consider the following \( \bnfes \):
+\begin{equation}
+  \begin{array}{r@{~}c@{~}l}
+    \NT{S} &::=& \NT{E} ~ \T{+} ~ \NT{E}\\
+    \NT{E} &::=& \T{x} \, \mid\, \T{x} \T{.} \T{p}\\
+  \end{array}
+  \label{eq:simple-js}
+\end{equation}
+As expected, this grammar accepts the string \( \code{x+x.p} \).
+However, the following PEG:
 \begin{equation}
@@
 \end{equation}
-If it is written in \( \bnfes \), the string \( \code{x+x.p} \) is in this
-language. However, in this PEG, the first alternative \( \T{x} \) of \( \NT{E}
-\) is always taken if the input string starts with \( \code{x} \). Thus, the
-second alternative \( \T{x}\T{.}\T{p} \) of \( \NT{E} \) is unreachable and \(
-\code{x+x.p} \) is not in the language.  A simple solution is just to change the
-order of alternatives of \( \NT{E} \) like \( \NT{E} ::= \T{x} \T{.} \T{p} ~/~
-\T{x} \).  However, simple reordering is not the solution for all cases:
+does not accept the same string \( \code{x+x.p} \).
+Because the first alternative \( \T{x} \) of \( \NT{E} \) is chosen
+whenever an input string starts with \( \code{x} \),
+the second alternative \( \T{x}\T{.}\T{p} \) of \( \NT{E} \) is always unreachable.
+A simple solution to accept the string is just to change the
+order of alternatives of \( \NT{E} \) like \( \NT{E} ::= \T{x} \T{.} \T{p} ~/~ \T{x} \).
+
+Unfortunately, simple reordering is not a general solution for all
+cases.  Consider the following \( \bnfes \):
+\begin{equation}
+  \begin{array}{r@{~}c@{~}l}
+    \NT{S} &::=& \NT{A} ~ \T{b}\\
+    \NT{A} &::=& \T{a} \,\mid\, \T{a} \T{b}\\
+  \end{array}
+\end{equation}
+It accepts both strings \( \code{ab} \) and \( \code{abb} \).
+However, the following PEG:
 \begin{equation}
@@
 \end{equation}
-If it is written in \( \bnfes \), both strings \( \code{ab} \) and \( \code{abb}
-\) is in this language. However, this PEG only accepts the string \( \code{ab}
-\), and another PEG with the reordered production \( \NT{A} ::= \T{a} \T{b}
-~/~ \T{a} \) only accepts \( \code{abb} \).
+accepts only \( \code{ab} \), and another PEG with reordered
+productions as follows:
+\begin{equation}
+  \begin{array}{r@{~}c@{~}l}
+    \NT{S} &::=& \NT{A} ~ \T{b}\\
+    \NT{A} &::=& \T{a} \T{b} ~/~ \T{a}\\
+  \end{array}
+\end{equation}
+accepts only \( \code{abb} \).
 
@@
     \rhsfirst{\symb_1 \cdots \symb_n} &=& \symbfirst{\symb_1} \firstplus
-    \rhsfirst{\symb_2 \cdots \symb_n}\\
+    \rhsfirst{\symb_2 \cdots \symb_n}\\[.1em]
     && \text{where} \; x \firstplus y = \left\{
     \begin{array}{ll}
-      x \cup y & \text{if} \; \emptyfirst \in x\\
-      x & \text{otherwise}\\
+      x \cup y & \text{if} \; \emptyfirst \in x\\[.1em]
+      x & \text{otherwise}\\[.2em]
     \end{array}
-    \right.\\
-    \symbfirst{\epsilon} &=& \{ \emptyfirst \}\\
-    \symbfirst{\T{a}} &=& \{ \T{a} \} \\
+    \right.\\[.1em]
+    \symbfirst{\epsilon} &=& \{ \emptyfirst \}\\[.1em]
+    \symbfirst{\T{a}} &=& \{ \T{a} \} \\[.1em]
     \symbfirst{\NT{A}(\argument_1, \cdots, \argument_k)} &=&
-    \rhsfirst{\rhs_1} \cup \cdots \cup \rhsfirst{\rhs_n}\\
+    \rhsfirst{\rhs_1} \cup \cdots \cup \rhsfirst{\rhs_n}\\[.1em]
     && \text{where} \; \NT{A}(\argument_1, \cdots, \argument_k) =
-    \rhs_1 \mid \cdots \mid \rhs_n\\
-    \symbfirst{\symb?} &=& \symbfirst{\symb} \cup \{ \emptyfirst \}\\
-    \symbfirst{+\symb} &=& \symbfirst{\symb}\\
-    \symbfirst{-\symb} &=& \{ \emptyfirst \}\\
-    \symbfirst{\symb \butnot \symb'} &=& \symbfirst{\symb}\\
+    \rhs_1 \mid \cdots \mid \rhs_n\\[.2em]
+    \symbfirst{\symb?} &=& \symbfirst{\symb} \cup \{ \emptyfirst \}\\[.1em]
+    \symbfirst{+\symb} &=& \symbfirst{\symb}\\[.1em]
+    \symbfirst{-\symb} &=& \{ \emptyfirst \}\\[.1em]
+    \symbfirst{\symb \butnot \symb'} &=& \symbfirst{\symb}\\[.1em]
     \symbfirst{\nolt} &=& \{ \emptyfirst \}
@@
 \]
-\vspace*{-1em}
+%\vspace*{-1em}
 \caption{Over-approximated first tokens of \( \bnfes \) symbols}
@@
 idea of lookahead parsing is to keep track of the next possible tokens by
-statically calculating first tokens of each symbol using the algorithm in
+statically calculating a set of first tokens for each symbol using the algorithm in
 Figure~\ref{fig:first-tokens}.  For example, the following steps explain how to
 utilize lookahead tokens during parsing of the string \( \code{x+x.p} \) with
-the PEG in Equation~(1): %\ref{eq:simple-js}:
+the PEG in Equation~(1):\\[-.5em]
 \begin{center}
-  \includegraphics[width=0.3\textwidth]{img/laparser.pdf}
+  \includegraphics[width=0.33\textwidth]{img/laparser.pdf}
 \end{center}
+
+\smallskip
+\noindent
 Each node \( \symb[\la] \) denotes a symbol \( \symb \) with a set of lookahead
 tokens \( \la \).  The underlined character in the string of each node denotes
-the current position in parsing process that follows a pre-order traversal.  It
-starts from the starting non-terminal \( \NT{S} \) with the special lookahead \(
+the current position in the parsing process that follows a pre-order traversal.
+The parser starts from the starting non-terminal \( \NT{S} \) with the special lookahead \(
 \emptyfirst \), which denotes the end of inputs.  Then, it visits the first
@@
 matching \( \T{x} \) is also \( \T{+} \). Thus, the first alternative \( \T{x}
-\) of \( \NT{E} \) is taken for the first visit.  However, in the second visit
+\) of \( \NT{E} \) is chosen for the first visit.  However, in the second visit
 of \( \NT{E} \), the lookahead is the end of inputs \( \emptyfirst \) but the
 next character after matching \( \T{x} \) is the dot character (\( \T{.} \))
-instead of the end of inputs.  Thus, the second alternative \( \T{x.p} \) is
-taken in the second visit and the parser successfully parses the input \(
-\code{x+x.p} \) now.
+instead of the end of inputs.  Therefore, the second alternative \( \T{x.p} \) is
+chosen in the second visit and the parser now successfully parses the input \(
+\code{x+x.p} \).
 
@@
 \subsection{Implementation}\label{sec:convert-bnfes}
-We implemented lookahead parsing technique by extending Scala parser combinators
-library, which is a Scala library for PEG-based parser generations.  We
+We implemented the lookahead parsing technique
+by extending the Scala parser combinators
+library, which is a Scala library for PEG-based parser generation.  We
 developed {\sf Parser Generator} to synthesize PEG-based parsers with
@@
     \symb_1[\symbfirst{\symb_2 \cdots \symb_n} \firstplus \la] \;
-    (\symb_1 \cdots \symb_n)[\la]\\
-    \epsilon[\la] &=& +\getlap{\la}\\
-    \T{a}[\la] &=& \T{a} \; +\getlap{\la} \\
+    (\symb_1 \cdots \symb_n)[\la]\\[.1em]
+    \epsilon[\la] &=& +\getlap{\la}\\[.1em]
+    \T{a}[\la] &=& \T{a} \; +\getlap{\la} \\[.1em]
     \NT{A}(\argument_1, \cdots, \argument_k)[\la] &=&
-    \rhs_1[\la] \mid \cdots \mid \rhs_n[\la]\\
+    \rhs_1[\la] \mid \cdots \mid \rhs_n[\la]\\[.1em]
     && \text{where} \; \NT{A}(\argument_1, \cdots, \argument_k) =
-    \rhs_1 \mid \cdots \mid \rhs_n\\
+    \rhs_1 \mid \cdots \mid \rhs_n\\[.2em]
 
-    \symb?[\la] &=& \symb[\la] \mid \epsilon[\la]\\
-    (\pm\symb)[\la] &=& \pm(\symb[\la]) \\
-    (\symb \butnot \symb')[\la] &=& \symb[\la] \butnot \symb'\\
-    \nolt &=& \nolt \; +\getlap{\la}\\
+    \symb?[\la] &=& \symb[\la] \mid \epsilon[\la]\\[.1em]
+    (\pm\symb)[\la] &=& \pm(\symb[\la]) \\[.1em]
+    (\symb \butnot \symb')[\la] &=& \symb[\la] \butnot \symb'\\[.1em]
+    \nolt &=& \nolt \; +\getlap{\la}
   \end{array}
 \]
-\vspace*{-1em}
+%\vspace*{-1em}
 \caption{Formal semantics of lookahead parsers}
@@
 \textbf{AST Generation.}
-{\sf Parser Generator} first automatically synthesizes ASTs as Scala case classes
-from a given \( \bnfes \) grammar.  Because structure of lexical productions do
+{\sf Parser Generator} first automatically synthesizes ASTs as Scala classes
+from a given \( \bnfes \) grammar.  Because the structure of lexical productions do
 not affect the ECMAScript semantics, we represent lexical non-terminals as
@@
   (\cond_n \Rightarrow)^? \rhs_n
-\), the generator synthesizes the \( \code{A} \) trait and multiple
-subclasses \( \code{A}_i \) of \( \code{A} \) for \(0 \le i \le n-1\)
-that represents its alternatives.  Each class \( \code{A}_i \) has
+\), the generator synthesizes a trait \( \code{A} \) and its multiple
+subclasses \( \code{A}_i \) for \(0 \le i \le n-1\)
+that represent its alternatives.  Each class \( \code{A}_i \) has
 non-terminals in its corresponding alternative as its fields.
@@
 production \textit{ArrayLiteral} in Figure~\ref{fig:array-literal}(a) is the one
-in Figure~\ref{fig:array-literal}(b).  The naive implementation of lookahead
-parsing has exponential parsing time because of backtracking.  To reduce the
-complexity to linear time, we applied the memoization technique introduced in
-Packrat parsing~\cite{packrat} proposed by Ford et al.  \inred{Moreover, we also
-implemented the \textit{growing the seed} technique presented by Warth et
-al~\cite{packrat-lr} to support direct and even indirect left recursive
-productions.  It helps to synthesize parsers without changing the structure of
+in Figure~\ref{fig:array-literal}(b).  A na\"{i}ve implementation of lookahead
+parsing would take exponential time because of backtracking.  To reduce it
+to linear time, we applied the memoization technique introduced in
+Packrat parsing~\cite{packrat}.  \inred{Moreover, we also
+implemented the \textit{growing the seed} technique presented
+by~\citet{packrat-lr} to support direct and even indirect left recursive
+productions.  It enables the synthesis of parsers without changing the structure of
 each production in \( \bnfes \).}
@@
 11.9\footnote{https://www.ecma-international.org/ecma-262/\#sec-automatic-semicolon-insertion}
-in ES10.  The rules about automatic semicolon insertion rarely change; since
+in ES10.  The automatic semicolon insertion rules rarely change; since
 ES5.1 written in 2011, only one sub-rule was added.

### 2020-04-09 ase20/parser.tex
[ASE] Added references / Changed red parts to black

@@
 Most parser generators target context-free languages with specific parsing
-algorithms for Context-Free Grammar (CFG): JavaCC with LL(k)~\inred{\cite{llk}},
-Bison with GLR~\inred{\cite{glr}}, and ANTLR with
-ALL(*)~\inred{\cite{all-star}}.  However, they are not directly applicable for the
-ECMAScript syntax because ECMAScript lexical and syntactic grammars require
-context-sensitive lexers and parsers:
+algorithms for Context-Free Grammar (CFG): JavaCC with LL(k)~\cite{llk}, Bison
+with GLR~\cite{glr}, and ANTLR with ALL(*)~\cite{all-star}.  However, they are
+not directly applicable for the ECMAScript syntax because ECMAScript lexical and
+syntactic grammars require context-sensitive lexers and parsers:
 \begin{itemize}%[leftmargin=0.5cm]
@@
 to linear time, we applied the memoization technique introduced in
-Packrat parsing~\cite{packrat}.  \inred{Moreover, we also
-implemented the \textit{growing the seed} technique presented
-by~\citet{packrat-lr} to support direct and even indirect left recursive
-productions.  It enables the synthesis of parsers without changing the structure of
-each production in \( \bnfes \).}
+Packrat parsing~\cite{packrat}.  Moreover, we also implemented the
+\textit{growing the seed} technique presented by~\citet{packrat-lr} to support
+direct and even indirect left recursive productions.  It enables the synthesis
+of parsers without changing the structure of each production in \( \bnfes \).
 

### 2020-04-12 ase20/compiler.tex
[ASE] Updated Section 4.

--- 2019-08-24 icse20/compiler.tex
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/algo_compiler.png}
-  \caption{Overall structure of {\sf Algorithm Compiler}}
+  \includegraphics[width=0.48\textwidth]{img/algo-compiler.pdf}
+  \caption{overall structure of {\sf algorithm compiler}}
   \label{fig:algo-compiler}
@@
 \subsection{Tokenizer}
-Before compiling abstract algorithms, {\sf Tokenizer} first tokenizes
-each abstract algorithm into a list of tagged tokens.  An algorithm
-consists of ordered steps, and a step may contain sub-steps as well.
-For example, the \textbf{\small ToPrimitive} algorithm in
-Figure~\ref{fig:to-primitive}(a) has three steps and the second step
-has seven sub-steps.  Moreover, the tokens of each step have their own
-HTML tags and each tag has a meaning.  For instance, \code{<var>}
-denotes variables, \code{<emu-grammar>} denotes productions, and
-\code{<code>} denotes ECMAScript code.
-% \[
-%   \begin{array}{c|l}
-%     \text{HTML tags} & \text{meanings}\\\hline\hline
-%     \code{<var>} & \text{variables}\\\hline
-%     \code{<emu-grammar>} & \text{productions}\\\hline
-%     \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
-%     \code{<code>} & \text{ECMAScript codes}\\\hline
-%     \code{<emu-const>} & \text{constant values}\\\hline
-%     \code{<emu-val>} & \text{values}\\\hline
-%     \code{<ol>} & \text{ordered sub-steps}\\\hline
-%     \code{<ul>} & \text{unordered sub-steps}\\\hline
-%     \code{<sup>} & \text{superscripts}\\\hline
-%     \text{otherwise} & \text{simple texts}\\\hline
-%   \end{array}
-% \]
-We keep such HTML tag information for each token to generate more precise
-{\sf Compile Rules}.  For example, because if and only if a token has
-a tag \( \code{<var>} \), it is a parameter or a local variable, we can
-construct {\sf Compile Rules} that precisely distinguish identifiers
-from other components.
-
-The {\sf Tokenizer} module recognizes the structure of each step,
-and divides the step into a sequence of tagged tokens.
-If an HTML element has an explicit tag, it is converted to a single token
-with the tag.  Otherwise, it is divided into multiple tokens and each token
-becomes a sequence of alphanumeric characters or a single non-alphanumeric
-character.  For example, in the \textbf{\small ToPrimitive} algorithm,
-\( \textbf{\code{"default"}} \) is a single token with the HTML tag \( \code{<code>} \)
-and \( \code{@@toPrimitive} \) is divided into three text tokens
-\( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).
+Before compiling abstract algorithms, {\sf Tokenizer} first tokenizes each
+abstract algorithm into a list of tagged tokens.  An algorithm consists of
+ordered steps, and a step may contain sub-steps as well.  For example, the
+\textbf{\small Evaluation} abstract algorithm in
+Figure~\ref{fig:array-literal-eval}(a) has seven steps.  Moreover, the tokens of
+each step have their own HTML tags and each tag has a meaning.  We keep such
+HTML tag information for each token to construct more precise {\sf Compile
+Rules}. If an HTML element is just a text without any explicit tags, it is
+divided into multiple tokens and each token becomes a sequence of alphanumeric
+characters or a single non-alphanumeric character.  For example, in the
+\textbf{\small Evaluation} algorithm, \( \textbf{\code{"length"}} \) is a single
+token with the HTML tag \( \code{<code>} \) and \( \code{Perform Set(} \) is
+divided into three text tokens \( \code{Perform} \), \( \code{Set} \), and \(
+\code{(} \).
 
@@
 \( \tout \) denote the start and the end of nested steps, respectively.
-For example, the \textbf{\small ToPrimitive} algorithm is tokenized as follows.
+For example, the following left abstract algorithm is tokenized to the right
+token list.
 \[
-  \begin{array}{l}
-    \code{Assert} \cdots \tend\\
-    \code{If} \cdots \tin \code{If} \cdots \tend
-    \cdots \code{Return} \cdots \tend \tout \tend\\
-    \code{Return} \cdots \tend\\
+  \begin{array}{lcl}
+    \code{1. A}\\
+    \code{2. B} &\Longrightarrow& \code{A} \tend \code{B} \tin \code{C} \tend \tout \tend\\
+    \code{\ \ a. C}\\
   \end{array}
@@
 \subsection{Token List Parser}
-Parsing rules determine the token list parser, and each parsing rule
-is written in extended Scala parser combinators.  We modified the
-meaning of the alternative composition operator ( \( ||| \) ) to collect
-all the longest matched results.  If a parser detects a step that
-cannot be parsed with given parsing rules, it reports the step into
-{\sf Fault Localizer}.  Even when a parser parses a step successfully,
-it also reports the step if it can parse the step in multiple ways.
-We use Packrat parsing~\cite{packrat} for parsing rules, which
-support left recursion.
+The token list parser is defined with \textit{parsing rules} written in extended
+Scala parser combinators. We modified the meaning of the alternative composition
+operator ( \( | \) ) to collect all the longest matched results. If a parser
+detects a step that cannot be parsed or parsed in multiple ways, it reports the
+step with the parsing results.  We use Packrat parsing~\cite{packrat} for
+parsing rules, which support left recursion.
 
-We provide two kinds of basic token parsers: tag-based parsers and
-content-based parsers.  A tag-based parser just checks whether the next
-token has a given tag.  For example, the tag-based parser \( \code{varT} \)
-checks whether the next token has the tag \( \code{<var>} \).  A
-content-based parser checks whether the next token is a text token and
-its content passes a given condition.  For example, the string literal
-\( \code{"Let"} \) denotes a content-based parser that checks whether
-the next token is a text token with the content \( \code{Let} \).
-We also provide two content-based parsers \( \code{word} \) and
-\( \code{number} \) that check whether the content of the next token
-consists of only alphabets or numbers, respectively.  In parsing
-rules, all the helper functions defined in Scala parser combinators
-are available.  For instance, the helper function \( \code{repsep(p, q)} \)
-generates a new parsing rule that denotes zero or more repetition of the
-parsing rule \( \code{p} \) using another parsing rule \( \code{q} \) as
-a separator.
+We provide two kinds of basic parsing rules: \textit{tag-based rules} and
+\textit{content-based rules}.  A tag-based rule just checks whether the next
+token has a given tag.  For example, the tag-based parser \( \code{varT} \) and
+\( \code{codeT} \) check whether the next token has the tag \( \code{<var>} \)
+and \( \code{<code>} \), respectively.  A content-based parser checks whether
+the next token is a text token and its content passes a given condition.  For
+example, the string literal \( \code{"Perform"} \) denotes a content-based
+parser that checks whether the next token is a text token with the content \(
+\code{Perform} \).  We also provide two content-based parsers \( \code{word} \)
+and \( \code{number} \) that check whether the content of the next token
+consists of only alphabets or numbers, respectively.  In parsing rules, all the
+helper functions defined in Scala parser combinators are available.  For
+instance, the helper function \( \code{repsep(p, q)} \) generates a new parsing
+rule that denotes zero or more repetition of the parsing rule \( \code{p} \)
+using another parsing rule \( \code{q} \) as a separator.
 
-Consider the following example parsing rule, which is a simplified
-version for the step 2-e-i of the \textbf{ToPrimitive} algorithm.
+Consider the following example parsing rule for the step 5 of the
+\textbf{Evaluation} algorithm in Figure~\ref{fig:array-literal-eval}(a).
 \begin{lstlisting}[style=myScalastyle]
 // statements
-val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
+val Stmt = "Perform" ~ Expr ~ "." ^^ ...
 // expressions
 val Expr =
-  // identifiers        // return if abrupt
-  varT      ^^ ... |||  "?" ~ Expr      ^^ ... |||
+  // codes        // false literal
+  codeT    ^^ ... |  "false"           ^^ ... |
+  // variables       // additions
+  varT     ^^ ... |  Expr ~ "+" ~ Expr ^^ ... |
   // function calls
-  word ~ "(" ~ repsep(Expr, ",") ~ ")"  ^^ ... |||
-  // lists
-  "<<" ~ repsep(varT, ",") ~ ">>"       ^^ ...
+  word ~ "(" ~ repsep(Expr, ",") ~ ")" ^^ ...
 \end{lstlisting}
-The \( \code{Stmt} \) compile rule describes how to compile statements
-with one parsing rule and its conversion rule is omitted for now for
-brevity.  The \( \code{Expr} \) compile rule describes how to compile
-expressions with four parsing rules.  A token parser with the above
-rules parses the step 2-e-i of \textbf{ToPrimitive} to the following
-token AST:
+We omit the conversion rule for each compile rule for the brevity.  The \(
+\code{Stmt} \) compile rule  describes how to compile statements with a single
+parsing rule, and the \( \code{Expr} \) compile rule describes how to compile
+expressions with five parsing rules.  A token parser with the above rules parses
+the step 5 of \textbf{Evaluation} to the following token AST:
 \begin{center}
-\includegraphics[width=0.5\textwidth]{img/token_ast.png}
+  \includegraphics[width=0.5\textwidth]{img/token-ast.pdf}
 \end{center}
@@
 \subsection{Token AST Converter}
-Conversion rules describe how to generate an \( \ires \) function for a
-given token AST.  Each conversion rule is defined with its
-corresponding parsing rule.  For basic token parsers, their conversion
-rules always return the string values of the contents in parsed tokens.
-For example, the following conversion rules are the omitted parts
-in the previous example for the step 2-e-i of \textbf{ToPrimitive}:
+\textit{Conversion rules} describe how to generate an \( \ires \) function for a
+given token AST.  Each conversion rule is defined with its corresponding parsing
+rule.  For basic parsing rules, their conversion rules always return the string
+values of the contents in parsed tokens.  For example, the following conversion
+rules are the omitted parts in the previous example for the step 5 of
+\textbf{Evaluation}:
 \begin{lstlisting}[style=myScalastyle]
 // statements
-val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
+val Stmt = ... ^^ { case _ ~ e ~ _ => IExpr(e) }
 // expressions
 val Expr =
-  // identifiers   // return if abrupt
-  ... ^^ EId |||   ... ^^ { _ ~ e => EAbrupt(e) } |||
+  // codes      // false literal
+  ... ^^ EStr | ... ^^ { _ => EBool(false) } |
+  // variables  // additions
+  ... ^^ EId  | ... ^^ { case x ~ _ ~ y => EAdd(x, y) } |
   // function calls
-  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }    |||
-  // lists
-  ... ^^ { case _ ~ x ~ _ => EList(e) }
+  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }
 )
 \end{lstlisting}
-The conversion rule of the compile rule \( \code{Stmt} \) uses only
-the second and fourth sub trees and converts them to \( \ires \)
-instructions.  The second sub-tree is converted to a string value
-because it was constructed via the basic token parser \( \code{varT} \).
-The fourth sub-tree is converted to an \( \ires \) expression
-because the conversion rules of the \( \code{Expr} \) compile rule
-construct \( \ires \) expressions.  Then, the conversion rule of
-\( \code{Stmt} \) constructs the lexical binding instruction \( \code{ILet} \)
-with the string value and the \( \ires \) expression.  In this way,
-the step 2-e-i of \textbf{ToPrimitive} is converted to the following
-\( \ires \) instruction:
+The conversion rule of the \code{Stmt} compile rule uses only the second sub
+tree and constructs an \code{IExpr} \( \ires \) instruction.  For the second
+sub-tree, the conversion rule of the fourth \code{Expr} compile rule is
+applied. It constructs \code{ECall} \( \ires \) expression with the string value
+of the first sub-tree and the sequence of the expressions of the third sub-tree.
+In this way, the step 5 of \textbf{Evaluation} is converted to the following \(
+\ires \) instruction:
 \begin{lstlisting}[style=ires]
-let result = ? (Call exoticToPrim input (new [hint]))
+(Set array "length" (ToUint32 (+ padding len)) false)
 \end{lstlisting}
@@
 functions with the following design choices:
-
 \begin{itemize}[leftmargin=0.5cm]
@@
 
-\item \textbf{Primitive values:} \( \ires \) supports ECMAScript
-primitive values except ``symbols'' because symbols can be represented
-as singleton objects.  Also, \( \ires \) provides the unique \(
-\code{absent} \) value to represent the absence of parameters.  For
-example, when the optional second parameter \( \code{PreferredType} \)
-of \textbf{ToPrimitive} in Figure~\ref{fig:to-primitive}(a) is absent,
-the parameter has the \( \code{absent} \) value.
+\item \textbf{Primitive values:} \( \ires \) supports ECMAScript primitive
+values except ``symbols'' because symbols can be represented as singleton
+objects.  Also, \( \ires \) provides the unique \( \code{absent} \) value to
+represent the absence of parameters.  For example, when the optional second
+parameter \textit{Elision} of \textbf{Evaluation} in
+Figure~\ref{fig:array-literal-eval}(a) is absent, the parameter has the \(
+\code{absent} \) value.
 
-\item \textbf{Abstract data types:} \( \ires \) supports only three
-abstract data types: \( \code{Record} \) for mappings from some values
-to other values, \( \code{List} \) for sequential data, and
-\( \code{Singleton} \) for singleton data.  For example, ECMAScript
-environment records are represented as \( \code{Record} \)
-from string values into addresses that represent other types of
-\( \code{Record} \) for bindings.  We also represent constants
-in the ECMAScript specification such as \( \code{empty} \)
-and \( \code{normal} \) as \( \code{Singleton} \) data types
-in \( \ires \).
+\item \textbf{Abstract data types:} \( \ires \) supports only three abstract
+data types: \( \code{Record} \) for mappings from some values to other values,
+\( \code{List} \) for sequential data, and \( \code{Symbol} \) for singleton
+data.  For example, ECMAScript environment records are represented as \(
+\code{Record} \) from string values into addresses that represent other types
+of \( \code{Record} \) for bindings.
 \end{itemize}
-
-\subsection{Fault Localizer}\label{sec:localizer}
-\begin{algorithm}[t]
-  \caption{Fault Localization}\label{alg:fault}
-  \begin{algorithmic}[1]
-    \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
-    \State $S = \varnothing$
-    \For{$i = 0$ to $n - 1$}
-    \For{$j = i$ to $n - 1$}
-    \State $T'$ = a copy of $T$
-    \State Substitute $T'[i..j]$ with $\tstar$
-    \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
-    \State Insert $(x, i, j)$ into $S$
-    \EndIf
-    \EndFor
-    \EndFor
-    \While{$s = (x, i, j) \in S$}
-    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
-    \State Remove $s$ from $S$
-    \EndIf
-    \EndWhile
-    \State \Return $S$
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
-which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
-The basic idea is to check whether we can parse the failed algorithm step
-with the assumption that a specific sub-sequence of the
-failed step is successfully parsed.  We define a \textit{rule suggestion}
-as such a sub-sequence of failed steps with the name of an existing compile rule.
-\textsf{Fault Localizer} refines candidates of rule suggestions into the
-most specific ones. It helped us when we update existing
-compile rules for new versions of the specification.
-
-The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
-For a given failed step $T$ and the size of a failed input $n$, it
-attempts to find a set of the most specific rule suggestions.  It
-substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
-special token \( \tstar \), which represents some sub-sequence of a
-failed step.  It collects a set of possible rule suggestions, and then
-removes more general ones than existing suggestions.  To support this
-process, we added a parsing rule  \( \code{starT} \) to each compile
-rule as follows:
-\begin{lstlisting}[style=myScalastyle]
-// statements
-val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
-// expressions
-val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
-\end{lstlisting}
-where \( \code{starT} \) is a special basic token parser that just
-checks whether a given token is the special token \( \tstar \). 
-Its corresponding conversion rule is a function that returns a dummy
-\( \ires \) component \( \code{Dummy} \) with a string value that
-represents the name of its compile rule.
-
-For example, let us assume that the \( \code{Expr} \) compile rule
-does not have the alternative for lists:
-\begin{lstlisting}[style=myScalastyle]
-  "<<" ~ repsep(varT, ",") ~ ">>" ^^
-       { case _ ~ x ~ _ => EList(e) } // lists
-\end{lstlisting}
-Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
-When we use the fault localization algorithm with the failed step and
-its size 15, it first finds one rule suggestion for statements and four
-rule suggestions for expressions as follows:
-\[
-\footnotesize
-\! \! \! \!
-  \begin{array}{c}
-    (\scode{"Stmt"}, 0, 14), \;
-    (\scode{"Expr"}, 3, 13), \;
-    (\scode{"Expr"}, 4, 13), \;
-    (\scode{"Expr"}, 6, 12), \;
-    (\scode{"Expr"}, 10, 12)
-  \end{array}
-\]
-In the \textbf{\small while} loop on lines 9--11, because the last one
-is the most specific sub-sequence, it removes the other four
-rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
-another expression compile rule for the token list \hint{}.
+We define syntax of \( \ires \) consisting 15 kinds of instructions and 26 kinds
+of expressions with the notation \( \irinst \) and \( \irexpr \), respectively.
+Moreover, we also formally define their operational semantics with the form \(
+\irstate \vdash \irinst \Rightarrow \irstate \) for instructions, and the form
+\( \irstate \vdash \irexpr \Rightarrow (\irvalue, \irstate) \) for expressions
+where \( \irvalue \) denotes a value and \( \irstate \) denotes a state.
+However, we omit this formalization in this paper for brevity, instead, we
+include it in the companion material\footnote{\inred{???}}.

### 2020-04-13 ase20/compiler.tex
[ASE] Merged Section 4 & 5

@@
 \subsection{Token List Parser}
-The token list parser is defined with \textit{parsing rules} written in extended
-Scala parser combinators. We modified the meaning of the alternative composition
-operator ( \( | \) ) to collect all the longest matched results. If a parser
-detects a step that cannot be parsed or parsed in multiple ways, it reports the
-step with the parsing results.  We use Packrat parsing~\cite{packrat} for
-parsing rules, which support left recursion.
+The token list parser is defined with \textit{parsing rules}. Each parsing rule
+is a basic parsing rule or a composition of other parsing rules. The composition
+\code{A | B} of two parsing rules \code{A} and \code{B} parses the input using
+both rules and collect the longest matched results.  If both rules are failed or
+matched the same length of the input, the composition is failed.
 
@@
 parser that checks whether the next token is a text token with the content \(
-\code{Perform} \).  We also provide two content-based parsers \( \code{word} \)
+\code{Perform} \).  We also define two content-based parsers \( \code{word} \)
 and \( \code{number} \) that check whether the content of the next token
-consists of only alphabets or numbers, respectively.  In parsing rules, all the
-helper functions defined in Scala parser combinators are available.  For
-instance, the helper function \( \code{repsep(p, q)} \) generates a new parsing
-rule that denotes zero or more repetition of the parsing rule \( \code{p} \)
-using another parsing rule \( \code{q} \) as a separator.
+consists of only alphabets or numbers, respectively.  In addition, we provide
+several helper functions in parsing rules such as optional rule \code{A?},
+positive(negative) predicate \code{+A}(\code{-A}).  For instance, the helper
+function \( \code{repsep(A, B)} \) generates a new parsing rule that denotes
+zero or more repetition of the parsing rule \( \code{A} \) using another parsing
+rule \( \code{B} \) as a separator.
 
@@
 \end{lstlisting}
-We omit the conversion rule for each compile rule for the brevity.  The \(
+We omit the conversion rule for each compile rule for brevity.  The \(
 \code{Stmt} \) compile rule  describes how to compile statements with a single
@@
 \end{itemize}
-We define syntax of \( \ires \) consisting 15 kinds of instructions and 26 kinds
+We define syntax of \( \ires \) including 15 kinds of instructions and 26 kinds
 of expressions with the notation \( \irinst \) and \( \irexpr \), respectively.
@@
 include it in the companion material\footnote{\inred{???}}.
+
+\subsection{Implementation}
+We implemented {\sf Algorithm Compiler} by extending Packrat
+parsing~\cite{packrat} library in Scala parser combinators. We modified the
+meaning of the composition operator ( \( | \) ) to collect all the
+longest matched results.  If a parser detects a step that cannot be parsed or
+parsed in multiple ways, it reports the step with the parsing results.
+
+\paragraph{Compile Rules}
+\textsf{Algorithm Compiler} requires compile rules to compile given abstract
+algorithms to \( \ires \) functions.  As already explained in
+Section~\ref{sec:overview}, we found general patterns in writing style of
+abstract algorithms.  We manually define the general compile rules to represent
+such writing style with six different kinds as summarized in
+Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
+generates \( \ires \) instructions.  The \( \code{Expr} \), \( \code{Cond} \),
+and \( \code{Value} \) compile rules generate \( \ires \) expressions, but they
+represents different contexts in ECMAScript; \( \code{Expr} \) represents a
+context where any expression can appear, \( \code{Cond} \) denotes a context
+where any boolean-valued expression can appear, and \( \code{Value} \)
+represents a context where a fully evaluated value can appear.  The \( \code{Ty}
+\) compile rule denotes type names and generates string primitives used in
+object constructions.  The \( \code{Ref} \) represents references such as
+identifier lookup and member accesses of objects, and it generates \( \ires \)
+references.
+
+\begin{table}[t]
+  \centering
+  \caption{General compile rules for ECMAScript}
+  \label{table:rules}
+\vspace*{-1em}
+  \[
+  \begin{array}{c?r|r|r|r|r|r}%|r}
+      \text{Name}
+      & \multicolumn{1}{c|}{\code{Stmt}}
+      & \multicolumn{1}{c|}{\code{Expr}}
+      & \multicolumn{1}{c|}{\code{Cond}}
+      & \multicolumn{1}{c|}{\code{Value}}
+      & \multicolumn{1}{c|}{\code{Ty}}
+      & \multicolumn{1}{c}{\code{Ref}}\\\hline
+      \text{\# Rules}
+      & \inred{17}
+      & \inred{16}
+      & \inred{8}
+      & \inred{11}
+      & \inred{33}
+      & \inred{7}
+    \end{array}
+  \]
+\vspace*{-2em}
+\end{table}
+
+\paragraph{Global Setting}
+To construct {\sf AST-\( \ires \) Translator}, global settings are also required
+and it consists of \textit{ECMAScript data types} and \textit{built-in objects}.
+Unlike compile rules, global settings are slightly different depending on
+ECMAScript versions. In this paper, we construct global settings only for the
+most recent ECMAScript version, ES10.
+
+ECMAScript describes data types with several fields and methods used in the
+specification.  Their methods are abstract algorithms but their semantics are
+slightly different with other. They implicitly get their receiver objects as
+arguments at callsites.  To mimic such implicit behavior, we added a special
+variable \( \code{this} \) as the first parameter of a method, and passed a
+receiver object at its callsite by modifying \textsf{Algorithm Compiler}.  For
+example, an Environment Record type has the \textsf{DeleteBinding (N)} method.
+Then, it gets two parameters, the special parameter \( \code{this} \) and normal
+one \( \code{N} \).  Thus, the method call
+\raisebox{-0.65ex}{\includegraphics[width=0.17\textwidth]{img/method-call.png}}
+is compiled into the \( \ires \) instruction: \code{(DclRec.DeleteBinding
+DclRec, N)}
+
+In ECMAScript, built-in objects are pre-defined functions with several
+built-in functions.  For example, \( \code{Array} \)
+is the constructor of array objects, and its prototype
+\( \code{Array.prototype} \) has built-in functions for array objects.
+For instance, \( \code{[1,2,3].flat()} \) calls the
+\( \code{Array.prototype.flat} \) built-in function with the array
+\( \code{[1,2,3]} \).  Because built-in functions are also abstract
+algorithms, each of them is automatically converted to an \( \ires \)
+function.  However, the structures of built-in objects should be
+manually implemented.  Thus, we implemented built-in objects in Scala
+and connected their properties with the extracted \( \ires \) functions.
+%
+Some built-in objects that are explicitly referenced in abstract
+algorithms are intrinsic objects, which have their own
+aliased names summarized in Table 7 of Section 6.1.7.4
+\textsf{Well-Known Intrinsic Objects}.  We extracted the alias
+into \textsf{Global Setting} to utilize it during evaluation.

### 2020-04-13 ase20/overview.tex
[ASE] Merged Section 4 & 5

@@
-\section{Overview}
+\section{Overview}\label{sec:overview}
 \begin{figure}
@@
 automatically generate parsers (Section~\ref{sec:parser}) and how to compile
-abstract algorithms (Section~\ref{sec:compiler}).  After describing implementation
-details (Section~\ref{sec:impl}), we evaluate \( \tool \)
-(Section~\ref{sec:eval}), discuss related work (Section~\ref{sec:related}), and
+abstract algorithms (Section~\ref{sec:compiler}).  After evaluating \( \tool \)
+(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}), and
 conclude (Section~\ref{sec:conclude}).

### 2020-04-13 ase20/compiler.tex
[ASE] Slightly revised Section 4

@@
 In this way, the step 5 of \textbf{Evaluation} is converted to the following \(
-\ires \) instruction:
+\ires \) instruction whose beautified form is the sixth line of the function
+body in Figure~\ref{fig:array-literal-eval}.
 \begin{lstlisting}[style=ires]
-(Set array "length" (ToUint32 (+ padding len)) false)
+IExpr(ECall(EId("Set"), List(
+  EId(array), EStr("length"), ECall(EId(ToUint32), List(
+    EAdd(EId("padding"), EId("len")))), EBool(false))))
 \end{lstlisting}
@@
 receiver object at its callsite by modifying \textsf{Algorithm Compiler}.  For
-example, an Environment Record type has the \textsf{DeleteBinding (N)} method.
-Then, it gets two parameters, the special parameter \( \code{this} \) and normal
-one \( \code{N} \).  Thus, the method call
+example, an Environment Record type has the \textbf{DeleteBinding (N)} method.
+Thus, the corresponding \( \ires \) function has two parameters, the special
+parameter \( \code{this} \) and normal one \( \code{N} \) and the method call
 \raisebox{-0.65ex}{\includegraphics[width=0.17\textwidth]{img/method-call.png}}
-is compiled into the \( \ires \) instruction: \code{(DclRec.DeleteBinding
-DclRec, N)}
+in an abstract algorithm is compiled to the \( \ires \) instruction:
+\code{(DclRec.DeleteBinding DclRec N)}
 

### 2020-04-13 ase20/compiler.tex
Revised Section 4

@@
   \includegraphics[width=0.48\textwidth]{img/algo-compiler.pdf}
-  \caption{overall structure of {\sf algorithm compiler}}
+  \caption{Overall structure of {\sf Algorithm Compiler}}
   \label{fig:algo-compiler}
@@
 \( \code{if}\!-\!\code{then}\!-\!\code{else} \) statement often consists of
-two steps: one for the \( \code{then} \)-branch and another
+two steps: one for the \( \code{then} \)-branch and the other
 for the \( \code{else} \)-branch.  To treat them as a linear structure,
@@
 \subsection{Token List Parser}
-The token list parser is defined with \textit{parsing rules}. Each parsing rule
-is a basic parsing rule or a composition of other parsing rules. The composition
-\code{A | B} of two parsing rules \code{A} and \code{B} parses the input using
-both rules and collect the longest matched results.  If both rules are failed or
-matched the same length of the input, the composition is failed.
+The token list parser is defined with \textit{parsing rules}. A parsing rule
+is a basic parsing rule or a composition of multiple parsing rules. The composition
+\code{A | B} of two parsing rules \code{A} and \code{B} parses an input using
+both rules and collects the longest matched results.  If both rules fail or
+match the same length of the input, the composition fails.
 
@@
 consists of only alphabets or numbers, respectively.  In addition, we provide
-several helper functions in parsing rules such as optional rule \code{A?},
-positive(negative) predicate \code{+A}(\code{-A}).  For instance, the helper
+several helper functions such as the optional rule \code{A?} and
+the positive(negative) predicate \code{+A}(\code{-A}).  For instance, the helper
 function \( \code{repsep(A, B)} \) generates a new parsing rule that denotes
@@
 tree and constructs an \code{IExpr} \( \ires \) instruction.  For the second
-sub-tree, the conversion rule of the fourth \code{Expr} compile rule is
+sub-tree, the conversion rule of the fifth \code{Expr} compile rule is
 applied. It constructs \code{ECall} \( \ires \) expression with the string value
@@
 In this way, the step 5 of \textbf{Evaluation} is converted to the following \(
-\ires \) instruction whose beautified form is the sixth line of the function
-body in Figure~\ref{fig:array-literal-eval}.
+\ires \) instruction whose beautified form is the seventh line
+in Figure~\ref{fig:array-literal-eval}(b).
 \begin{lstlisting}[style=ires]
@@
 \item \textbf{Abstract data types:} \( \ires \) supports only three abstract
-data types: \( \code{Record} \) for mappings from some values to other values,
+data types: \( \code{Record} \) for mappings from values to values,
 \( \code{List} \) for sequential data, and \( \code{Symbol} \) for singleton
 data.  For example, ECMAScript environment records are represented as \(
-\code{Record} \) from string values into addresses that represent other types
-of \( \code{Record} \) for bindings.
+\code{Record} \) from string values to addresses that represent the
+bindings of the string values.
 \end{itemize}
-We define syntax of \( \ires \) including 15 kinds of instructions and 26 kinds
+We define the syntax of \( \ires \) that has 15 kinds of instructions and 26 kinds
 of expressions with the notation \( \irinst \) and \( \irexpr \), respectively.
-Moreover, we also formally define their operational semantics with the form \(
-\irstate \vdash \irinst \Rightarrow \irstate \) for instructions, and the form
-\( \irstate \vdash \irexpr \Rightarrow (\irvalue, \irstate) \) for expressions
-where \( \irvalue \) denotes a value and \( \irstate \) denotes a state.
-However, we omit this formalization in this paper for brevity, instead, we
-include it in the companion material\footnote{\inred{???}}.
+We also formally define its operational semantics \(
+\irstate \vdash \irinst \Rightarrow \irstate \) for instructions and
+\( \irstate \vdash \irexpr \Rightarrow (\irvalue, \irstate) \) for expressions,
+where \( \irstate \) denotes a state and \( \irvalue \) denotes a value.
+For presentation brevity, we omit the formalization of \( \ires \) in this paper
+and include it in a companion report\inred{\cite{report}}.
 
 \subsection{Implementation}
-We implemented {\sf Algorithm Compiler} by extending Packrat
+We implemented {\sf Algorithm Compiler} by extending the Packrat
 parsing~\cite{packrat} library in Scala parser combinators. We modified the
@@
 longest matched results.  If a parser detects a step that cannot be parsed or
-parsed in multiple ways, it reports the step with the parsing results.
+is parsed in multiple ways, it reports the step with parsing results.
 
@@
 algorithms to \( \ires \) functions.  As already explained in
-Section~\ref{sec:overview}, we found general patterns in writing style of
-abstract algorithms.  We manually define the general compile rules to represent
-such writing style with six different kinds as summarized in
+Section~\ref{sec:overview}, we found common patterns in the writing style of
+abstract algorithms.  We manually defined general compile rules to represent
+such a writing style with six different kinds as summarized in
 Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
@@
 and \( \code{Value} \) compile rules generate \( \ires \) expressions, but they
-represents different contexts in ECMAScript; \( \code{Expr} \) represents a
+represent different contexts in ECMAScript; \( \code{Expr} \) represents a
 context where any expression can appear, \( \code{Cond} \) denotes a context
@@
 \) compile rule denotes type names and generates string primitives used in
-object constructions.  The \( \code{Ref} \) represents references such as
+object constructions.  The \( \code{Ref} \) compile rule represents references such as
 identifier lookup and member accesses of objects, and it generates \( \ires \)
@@
 \paragraph{Global Setting}
-To construct {\sf AST-\( \ires \) Translator}, global settings are also required
-and it consists of \textit{ECMAScript data types} and \textit{built-in objects}.
-Unlike compile rules, global settings are slightly different depending on
+{\sf AST-\( \ires \) Translator} uses global settings consisting
+of \textit{ECMAScript data types} and \textit{built-in objects}.
+Unlike compile rules, global settings depend on
 ECMAScript versions. In this paper, we construct global settings only for the
-most recent ECMAScript version, ES10.
+latest ECMAScript, ES10.
 
-ECMAScript describes data types with several fields and methods used in the
-specification.  Their methods are abstract algorithms but their semantics are
-slightly different with other. They implicitly get their receiver objects as
-arguments at callsites.  To mimic such implicit behavior, we added a special
-variable \( \code{this} \) as the first parameter of a method, and passed a
+ECMAScript describes data types with some fields and methods.
+While the methods are like abstract algorithms, their semantics are
+slightly different from abstract algorithms. They implicitly get their receiver objects as
+arguments at callsites.  To mimic such an implicit behavior, we added a special
+variable \( \code{this} \) as the first parameter of each method, and passed a
 receiver object at its callsite by modifying \textsf{Algorithm Compiler}.  For
 example, an Environment Record type has the \textbf{DeleteBinding (N)} method.
-Thus, the corresponding \( \ires \) function has two parameters, the special
-parameter \( \code{this} \) and normal one \( \code{N} \) and the method call
+Thus, its corresponding \( \ires \) function has two parameters, the special
+parameter \( \code{this} \) and a normal parameter \( \code{N} \), and the method call
 \raisebox{-0.65ex}{\includegraphics[width=0.17\textwidth]{img/method-call.png}}
 in an abstract algorithm is compiled to the \( \ires \) instruction:
-\code{(DclRec.DeleteBinding DclRec N)}
+\code{(DclRec.DeleteBinding DclRec N)}.
 
@@
 algorithms are intrinsic objects, which have their own
-aliased names summarized in Table 7 of Section 6.1.7.4
+aliased names summarized in Table~7 of Section~6.1.7.4
 \textsf{Well-Known Intrinsic Objects}.  We extracted the alias

### 2020-04-14 ase20/overview.tex
[ASE] Revised overview

@@
 
-In this section, we introduce the overall structure of \( \tool \)
-depicted in Figure~\ref{fig:overview}.
-Compared to the existing approaches shown in
-Figure~\ref{fig:existing}, \( \tool \) automatically synthesizes
-{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} directly from
-ECMAScript.
+In this section, we introduce the overall structure of \( \tool \) depicted in
+Figure~\ref{fig:overview}.  Compared to the existing approaches shown in
+Figure~\ref{fig:existing}, our tool automatically synthesizes {\sf JavaScript
+Parser} and {\sf AST-\( \ires \) Translator} directly from ECMAScript. The
+motivation of this work is twofold: 1) ECMAScript is written in a well-organized
+style, and 2) the writing style is converged since ES7 in 2016.
 
-The motivation of automatically extracting syntax and semantics of JavaScript
-from ECMAScript is twofold: 1) ECMAScript is written in a well-organized
-style, and 2) it is available as HTML files using various HTML tags.
-To easily manipulate ECMAScript written in HTML, we developed
-{\sf Spec Extractor} in JavaScript to extract the syntax and semantics in JSON format.
+We explain how \( \tool \) utilize such common patterns in the writing style to
+synthesize two modules with an example.  After {\sf Spec Extractor} extract
+syntax and semantics in JSON format, our tool consists consists of two parts for
+\textit{syntax} and \textit{semantics}.
 

### 2020-04-15 ase20/overview.tex
Revised Sec. 2

@@
 style, and 2) the writing style is converged since ES7 in 2016.
-
-We explain how \( \tool \) utilize such common patterns in the writing style to
-synthesize two modules with an example.  After {\sf Spec Extractor} extract
-syntax and semantics in JSON format, our tool consists consists of two parts for
-\textit{syntax} and \textit{semantics}.
+We explain how \( \tool \) utilizes such common patterns in the writing style to
+synthesize {\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator}
+using the syntax and semantics in JSON format
+extracted from ECMAScript by {\sf Spec Extractor}.
 

### 2020-04-20 ase20/abstract.tex
[ASE] five -> four in abstract

@@
 into \( \ires \), an Intermediate Representation that we designed for
-ECMAScript.  For the five most recent ECMAScript versions, \( \tool \) automatically
+ECMAScript.  For the four most recent ECMAScript versions, \( \tool \) automatically
 synthesized parsers for all versions, and compiled \inred{XX.XX}\% of the

### 2020-04-20 ase20/intro.tex
[ASE] minor changed: ES 5.1 -> ES5.1
[ASE] Revised intro for the new flow

@@
 Moreover, JavaScript syntax and semantics are annually updated.  Until
-ES 5.1, JavaScript was a stable language because the specification was
+ES5.1, JavaScript was a stable language because the specification was
 rarely updated.  However, the Ecma Technical Committee 39 (TC39)~\cite{tc39}
@@
 \begin{itemize}[leftmargin=0.5cm]
-  \item \textbf{\( \tool \) is the \textit{first tool that can automatically synthesize}
-    parsers and AST-IR translators directly from a language specification,
-    ECMAScript.}  For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
+  \item \textbf{\( \tool \) is the \textit{first tool that automatically
+    extract} IR-based semantics from a language specification, ECMAScript.}
+    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
     and propose a parser generation technique with
@@
     insertion. For semantics, we propose semi-automatic synthesis of AST-IR
-    translators assisted by compile rules due to the
-    difficulty in handling the semantics written in a natural language.  Compile rules describe
+    translators assisted by compile rules.  Compile rules describe
     how to convert each step of abstract algorithms into our intermediate
     representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
-    with the five most recent ECMAScript versions (ES6 to ES10).   \( \tool \) automatically generated
-    parsers for all versions, and automatically compiled
+    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
+    automatically generated parsers for all versions, and automatically compiled
     \inred{XX.X}\% of the steps in abstract algorithms on average.
-  \item \textbf{ Using \( \tool \), we could define the \textit{first IR-based
-    formal semantics of modern JavaScript}.}  The semantics targets the
-    core of ES10, and \( \tool \) successfully synthesizes its
-    parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
-    algorithm steps.  We manually completed the missing parts of the AST-IR
-    translator (\inred{XXX} steps) in \inred{XX} days.  We evaluated the correctness
-    of the formal semantics using Test262~\cite{test262}, the official
-    conformance test suite, and the semantics passed all \inred{XX,XXX}
-    applicable tests.  Moreover, we found \inred{X} specification errors in ES10
-    thanks to the formal semantics.  They were all confirmed by TC39 and will be
-    fixed in the next release.
-  \item \textbf{\( \tool \) is also \textit{forward compatible} with new language features
-    proposed for future ECMAScript specifications.}  
-     We evaluated the forward compatibility of \( \tool \) by applying it
-     to all \inred{XX} proposals that are ready for inclusion in the next ECMAScript  (ES11, 2020).
-    It automatically synthesized parsers and
-    compiled \inred{XX} out of \inred{XX} algorithm steps for all the proposals.
-    After completion of the missing parts, the extracted semantics passed all \inred{XX} tests.
+  \item \textbf{\( \tool \) bridges the gap between tests and the specification
+    written in a natural language.}
+    The formal semantics automatically extracted by \( \tool \) is executable
+    and its components have one-to-one correspondences with the components of
+    the ECMAScript.  It gives opportunity to directly verify the specification
+    through the official test conformance suite, Test262~\cite{test262}.  We
+    manually completed the missing parts for the latest ECMAScript (ES10, 2019),
+    and it is the \textit{first IR-based formal semantics of modern JavaScript}.
+    By executing tests, we found \inred{X} specification errors in ES10 and
+    \inred{XX} wrong tests in Test262. They were all confirmed by TC39 and will
+    be fixed in the next release.  After fixing them, our formal semantics
+    passed all \inred{XX,XXX} applicable tests.
+  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
+    language features proposed for future ECMAScript specifications.}
+    We evaluated the forward compatibility of \( \tool \) by applying it to all
+    \inred{X} proposals that are ready for inclusion in the next ECMAScript
+    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
+    out of \inred{XXX} algorithm steps for all the proposals.  After completion
+    of the missing parts, we found \inred{X} specifications errors by executing
+    the corresponding tests in Test262.  After fixing them, the extracted
+    semantics passed all \inred{XXX} tests.
 \end{itemize}

### 2020-04-21 ase20/intro.tex
[ASE] slightly revised intro.tex

@@
     and its components have one-to-one correspondences with the components of
-    the ECMAScript.  It gives opportunity to directly verify the specification
+    the ECMAScript.  It gives opportunity to directly check the specification
     through the official test conformance suite, Test262~\cite{test262}.  We
-    manually completed the missing parts for the latest ECMAScript (ES10, 2019),
-    and it is the \textit{first IR-based formal semantics of modern JavaScript}.
-    By executing tests, we found \inred{X} specification errors in ES10 and
-    \inred{XX} wrong tests in Test262. They were all confirmed by TC39 and will
-    be fixed in the next release.  After fixing them, our formal semantics
-    passed all \inred{XX,XXX} applicable tests.
+    manually completed the missing parts of the AST-IR translator for the latest
+    ECMAScript (ES10, 2019), and it is the \textit{first IR-based formal
+    semantics of modern JavaScript}.  By executing tests, we found \inred{X}
+    specification errors in ES10 and \inred{XX} wrong tests in Test262. They
+    were all confirmed by TC39 and will be fixed in the next release.  After
+    fixing them, our formal semantics passed all \inred{XX,XXX} applicable
+    tests.
   \item \textbf{\( \tool \) is also \textit{forward compatible} with new

### 2020-04-22 ase20/compiler.tex
[ASE] Updated Evaluation section

@@
 
-\subsection{Implementation}
+\subsection{Implementation}\label{sec:compiler-impl}
 We implemented {\sf Algorithm Compiler} by extending the Packrat

### 2020-04-22 ase20/eval.tex
[ASE] Merged Section 4 & 5
[ASE] Updated Evaluation section

@@
 
-We evaluate \( \tool \) based on the following four research questions:
+We developed \( \tool \) as an open source tool\footnote{The URL of the tool is
+anonymized due to a double-blind review process.}, and evaluated the tool
+based on the following three research questions:
 \begin{itemize}[leftmargin=0.5cm]
-\item RQ1. \textbf{Effectiveness:} Does \( \tool \) effectively reduce
-manual efforts in extracting the syntax and semantics from existing
-ECMAScript specifications? 
-\item RQ2. \textbf{Correctness:} Do the extracted syntax and semantics
-from ES10 behave correctly?
-\item RQ3. \textbf{Adaptability:} Is \( \tool \) applicable to
-incomplete feature proposals?
-\item RQ4. \textbf{Usefulness:} Does \( \tool \) detect any
-specification errors?
+\item RQ1. \textbf{Coverage:} How much parts \( \tool \) automatically extract
+the syntax and semantics from ES7 to ES10?
+\item RQ2. \textbf{Check with Tests:} The syntax and semantics of the latest
+version on ECMAScript (ES10) is compatible with official tests?
+\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
+features ready for inclusion in the next ECMAScript (ES11)?
 \end{itemize}
 
-\subsection{Effectiveness}
+\subsection{Coverage}
 
@@
   \[
-    \begin{array}{c?r|r|r|r|r?r}
+    \begin{array}{c?r|r|r|r?r}
       \textbf{Version}
-      & \multicolumn{1}{c|}{\textbf{2016}}
-      & \multicolumn{1}{c|}{\textbf{2017}}
-      & \multicolumn{1}{c|}{\textbf{2018}}
-      & \multicolumn{1}{c|}{\textbf{2019}}
-      & \multicolumn{1}{c?}{\textbf{2020}}
+      & \multicolumn{1}{c|}{\textbf{ES7}}
+      & \multicolumn{1}{c|}{\textbf{ES8}}
+      & \multicolumn{1}{c|}{\textbf{ES9}}
+      & \multicolumn{1}{c?}{\textbf{ES10}}
       & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
       \text{\# Lexical prod.}
-      & \text{78}
-      & \text{78}
-      & \text{78}
-      & \text{81}
-      & \text{81}
-      & \text{79.2}\\\hline
+      & \inred{\text{78}}
+      & \inred{\text{78}}
+      & \inred{\text{78}}
+      & \inred{\text{81}}
+      & \inred{\text{78.75}}\\\hline
       \text{\# Syntactic prod.}
-      & \text{157}
-      & \text{167}
-      & \text{167}
-      & \text{174}
-      & \text{175}
-      & \text{168}\\
+      & \inred{\text{157}}
+      & \inred{\text{167}}
+      & \inred{\text{167}}
+      & \inred{\text{174}}
+      & \inred{\text{166.25}}\\
     \end{array}
@@
   \[
-    \begin{array}{c|r|r|r|r?r}
+    \begin{array}{c?r|r|r?r}
       \textbf{Old version}
-      & \multicolumn{1}{c|}{\textbf{2016}}
-      & \multicolumn{1}{c|}{\textbf{2017}}
-      & \multicolumn{1}{c|}{\textbf{2018}}
-      & \multicolumn{1}{c?}{\textbf{2019}}
-      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
+      & \multicolumn{1}{c|}{\textbf{ES7}}
+      & \multicolumn{1}{c|}{\textbf{ES8}}
+      & \multicolumn{1}{c?}{\textbf{ES9}}
+      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-4}
       \textbf{New version}
-      & \multicolumn{1}{c|}{\textbf{2017}}
-      & \multicolumn{1}{c|}{\textbf{2018}}
-      & \multicolumn{1}{c|}{\textbf{2019}}
-      & \multicolumn{1}{c?}{\textbf{2020}}
+      & \multicolumn{1}{c|}{\textbf{ES8}}
+      & \multicolumn{1}{c|}{\textbf{ES9}}
+      & \multicolumn{1}{c?}{\textbf{ES10}}
       & \\\toprule
       \Delta \; \text{\# Lexical prod.}
-      & \text{3}
-      & \text{5}
-      & \text{6}
-      & \text{0}
-      & \text{4.7}\\\hline
+      & \inred{\text{3}}
+      & \inred{\text{5}}
+      & \inred{\text{6}}
+      & \inred{\text{4.67}}\\\hline
       \Delta \; \text{\# Syntactic prod.}
-      & \text{140}
-      & \text{15}
-      & \text{8}
-      & \text{2}
-      & \text{55}\\
+      & \inred{\text{140}}
+      & \inred{\text{15}}
+      & \inred{\text{8}}
+      & \inred{\text{54.33}}\\
     \end{array}
@@
 
+\( \tool \) targets ECMAScript specifications released after ES7 in 2016 because
+our tool utilizes common patterns in the converged writing style since ES7 as
+already explained in Section~\ref{sec:overview}.  Thus, we evaluate the coverage
+of \( \tool \) by applying it to the most recent four versions of ECMAScript,
+ES7 to ES10.  We measured for how many grammar productions and steps in abstract
+algorithms \( \tool \) automatically generates parsers and AST-IR translators,
+respectively, in two respects: 1) in each version and 2) in each difference
+between adjacent versions.
+
+For syntax, \( \tool \) automatically generated parsers for \textit{all} the
+lexical and syntactic productions.  As Table~\ref{fig:syntax-all-version} shows,
+the average numbers of lexical and syntactic productions are \inred{78.75} and
+\inred{166.25}, respectively.  Also, the average numbers of annually updated
+lexical and syntactic productions between adjacent versions are \inred{4.67} and
+\inred{54.33}, respectively.
+
 \begin{figure}[t]
   \centering
-  \begin{subfigure}{0.46\textwidth}
-    \includegraphics[width=\textwidth]{img/sem-all.png}
+  \begin{subfigure}{0.48\textwidth}
+    \includegraphics[width=\textwidth]{img/sem-all.pdf}
     \caption{Results for existing versions}
@@
   \begin{subfigure}{0.48\textwidth}
-    \includegraphics[width=\textwidth]{img/sem-delta.png}
+    \includegraphics[width=\textwidth]{img/sem-diff.pdf}
     \caption{Results for differences between adjacent versions}
-    \label{fig:semantics-all-version-delta}
+    \label{fig:semantics-all-version-diff}
   \end{subfigure}
@@
 
-We evaluate the effectiveness of \( \tool \) by applying it to the
-most recent five versions of ECMAScript, ES6 to ES10.
-We measured for how many grammar productions and
-steps in abstract algorithms \( \tool \) automatically generates parsers and
-semantics, respectively, in two respects: 1) in each version and 2) in
-each difference between adjacent versions.
-
-%For syntax, we measured the number of grammar productions for which
-%\textsf{Parser Generator} automatically generated parsers.  
-%Table~\ref{fig:syntax-all-version} shows the number of grammar productions
-
-For syntax, \( \tool \) automatically generated parsers for
-\textit{all} the productions.  As Table~\ref{fig:syntax-all-version} shows,
-the average numbers of lexical and syntactic productions are 79.2 and 168, respectively.
-Also, the average numbers of annually updated lexical and
-syntactic productions between adjacent versions are 4.7 and 55, respectively.
-
-For semantics, Figure~\ref{fig:all-version} shows that \( \tool \)
-automatically extracted semantics with the 91.60\% success rate on
-average for existing specifications, and 90.43\% for updates.
-We found that algorithm steps in
-built-in libraries have lower success rates (86.98\% for specifications
-and 86.09\% for updates) than core language semantics (95.35\%  for specifications
-and 95.25\% for updates) because of diverse writing styles in
-describing their own specific functionalities.
+For semantics, Figure~\ref{fig:all-version} shows that \( \tool \) automatically
+compile algorithm steps to the corresponding \( \ires \) instructions with
+\inred{91.60\%} success rate on average for existing specifications, and
+\inred{90.43\%} for updates.  ECMAScript abstract algorithms describe not only
+core language semantics but also other helper functions of built-in libraries.
+Built-in libraries written in more diverse styles in describing their own
+specific functionalities.  Thus, built-in libraries have lower success rates
+(\inred{86.98\%} for specifications and \inred{86.09\%} for updates) than core
+language semantics (\inred{95.35\%} for specifications and \inred{95.25\%} for
+updates).
 
@@
 
-\subsection{Correctness}
+\subsection{Check with Tests}\label{sec:check-with-tests}
+
+To define the \textit{first IR-based formal semantics of modern JavaScript}, we
+completed missing parts of the AST-IR translator for ES10.  Among \inred{9,674}
+steps in ES10, \inred{8,901} steps are automatically compiled via
+\textsf{Algorithm Compiler}.  Among the remaining \inred{773} steps, we manually
+implemented all remaining language semantics (\inred{221} steps) and essential
+parts of built-in libraries (\inred{XX} steps out of \inred{552}) in \inred{XX}
+days.  Moreover, we manually implemented the \textsf{Global Setting} as described
+in Section~\ref{sec:compiler-impl} for the core language features.  However, we
+do not support several minor language features that do not affect the overall
+JavaScript semantics critically: non-strict mode codes, modules, early errors
+before actual executions, and inessential built-in objects.
+
+Thanks to the executability of our extracted formal semantics, we checked the
+semantics with Test262, the official conformance test suite provided by TC39.
+We fixed version of Test262 as of February 28, 2019 because the ES10 was
+branched out with the branch name es2019 in that day.  While it consists of
+\inred{XX,XXX} tests, we filtered out \inred{XX,XXX} tests not applicable for
+our formal semantics as shown in Table~\ref{table:test262}.  Test262 targets not
+only the current official version of ECMAScript but several extensions and
+in-progress features. We excluded \inred{X,XXX} tests for such cases to focus on
+the semantics of ES10.  Among \inred{XX,XXX} ES10 tests, we also filtered out
+\inred{X,XXX} tests using language features not supported by our semantics.
+
+\begin{table*}[t]
+  \centering
+  \caption{Specification errors and wrong tests in Test262.}
+  \label{table:spec-tests-errors}
+  \vspace*{-0.5em}
+  \small
+  \begin{tabular}{|c|c|l|c|c|c|c|c|}
+    \hline
+    \multicolumn{1}{|c|}{\bf Name} &
+    \multicolumn{1}{c|}{\bf Feature} &
+    \multicolumn{1}{c|}{\bf Description} &
+    \multicolumn{1}{c|}{\bf Known} &
+    \multicolumn{1}{c|}{\bf Created} &
+    \multicolumn{1}{c|}{\bf Resolved} &
+    \multicolumn{1}{c|}{\bf Existed} &
+    \multicolumn{1}{c|}{\bf \# Failed Tests} \\\hline
+
+    es10-1 &
+    Await &
+    \makecell[l]{Passing wrong type of \\ the second argument for {\bf PromiseResolve}.} &
+    \textsf{O} &
+    2019-02-27 &
+    2019-04-13 &
+    45 days &
+    \inred{XX} \\\hline
+
+    es10-2 &
+    IterationKind &
+    \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
+    ForIn/OfHeadEvaluation}.} &
+    \textsf{X} &
+    2018-02-16 &
+    2020-03-25 &
+    768 days &
+    \inred{XX} \\\hline
+
+    es10-3 &
+    Completion &
+    \makecell[l]{Not handling abrupt completion \\ in {\bf Evaluation} of {\it
+    EqualityExpression}.} &
+    \textsf{O} &
+    2016-06-01 &
+    2019-05-02 &
+    1065 days &
+    \inred{XX} \\\hline
+
+    es10-4 &
+    Function &
+    \makecell[l]{No semantics of {\bf IsFunctionDefinition} \\ for
+    \code{function(...)\{...\}}.} &
+    \textsf{O} &
+    2015-10-30 &
+    2020-01-18 &
+    1541 days &
+    \inred{XX} \\\hline
+
+    es10-5 &
+    ForOf &
+    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
+    await(var x of e)\{...\}}.} &
+    \textsf{O} &
+    2018-02-16 &
+    2019-10-11 &
+    602 days &
+    \inred{XX} \\\hline
+
+    es10-6 &
+    Argument &
+    \makecell[l]{No semantics of {\bf ExpectedArgumentCount} \\ for the base case
+    of {\it FormalParameters}.} &
+    \textsf{O} &
+    2016-11-02 &
+    2020-02-20 &
+    1205 days &
+    \inred{XX} \\\hline
+
+    es10-7 &
+    String &
+    \makecell[l]{Wrong use of \code{=} operator in {\bf
+    StringGetOwnProperty}.} &
+    \textsf{X} &
+    2015-06-01 &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    \inred{XX} \\\hline
+
+    test-1 &
+    Global &
+    \makecell[l]{Testing implementation-dependent [[Prototype]] \\ of the global
+    object.} &
+    \textsf{X} &
+    \inred{2019-00-00} &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    10 \\\hline
+
+    bigint-1 &
+    UpdateExpression &
+    \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
+    \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.} &
+    \textsf{X} &
+    2019-11-27 &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    \inred{XX} \\\hline
+
+    bigint-2 &
+    NumberOp &
+    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
+    Number::unsignedRightShift}.} &
+    \textsf{X} &
+    2019-11-27 &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    \inred{XX} \\\hline
+
+    bigint-3 &
+    NumberOp &
+    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
+    NumberBitwiseOp}.} &
+    \textsf{X} &
+    2019-11-27 &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    \inred{XX} \\\hline
+
+    bigint-4 &
+    Number &
+    \makecell[l]{Not handling BigInt values in {\bf Number} constructor.} &
+    \textsf{O} &
+    2019-11-27 &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    \inred{XX} \\\hline
+
+  \end{tabular}
+\end{table*}
+
 \begin{table}[t]
   \centering
-  \caption{Testing results of Test262 for ES10}
+  \caption{Excluded tests in Test262}
   \label{table:test262}
-\vspace*{-.5em}
-\footnotesize
+  \vspace*{-0.5em}
+  \small
   \begin{tabular}{lr}\toprule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
+    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \inred{\textbf{XX,XXX}}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Annexes/Internationalization & 1,774\\\hdashline
-    In-progress features & 5,895\\\midrule
+    Annexes & \inred{XXX}\\\hdashline
+    Internationalization & \inred{XXX}\\\hdashline
+    In-progress features & \inred{X,XXX}\\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{ES10 Tests} & \textbf{29,125}\\
+    \rowcolor{gainsboro} \textbf{ES10 Tests} & \inred{\textbf{XX,XXX}}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict mode tests & 1,136\\\hdashline
-    Module tests& 918 \\\hdashline
-    Early error tests & 1,316\\\hdashline
-    Inessential built-in object tests & 6,473\\\midrule
+    Non-strict modes & \inred{X,XXX}\\\hdashline
+    Modules & \inred{X,XXX} \\\hdashline
+    Early errors & \inred{X,XXX} \\\hdashline
+    Inessential built-in objects & \inred{X,XXX} \\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
+    \rowcolor{gainsboro} \textbf{Applicable Tests} & \inred{\textbf{XX,XXX}}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Passed tests & 19,220 \\\hdashline
-    Failed tests & 62 \\\bottomrule
+    Passed tests & \inred{XX,XXX} \\\hdashline
+    Failed tests & \inred{XXX} \\\bottomrule
   \end{tabular}
-\vspace*{-1em}
+  \vspace*{-2em}
 \end{table}
 
-To evaluate the correctness of \( \tool \), we developed a JavaScript
-interpreter based on the extracted syntax and semantics from ES10.
-Among 9,657 steps in ES10,
-8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
-Among the remaining 731 steps, we selected 381 steps
-that are essential to the core semantics and manually
-implemented their corresponding \( \ires \) functions
-via the \textsf{Fault Localizer} introduced in Section~\ref{sec:localizer}.
-Moreover, we implement the \textsf{Global Setting} except
-the excluded language features discussed in Section~\ref{sec:exclusion}.
+For \inred{XX,XXX} applicable tests, the synthesized JavaScript parser
+successfully parses all tests but \inred{XXX} tests are failed to be executed
+because of the different semantics between ECMAScript and official tests.  Based
+on the failed tests, we found 7 specification errors in ES10 and 10 wrong tests
+in Test262 as described in Table~\ref{table:spec-tests-errors}.  For example,
+the specification error es10-1 is related to the JavaScript Await.  The {\bf
+PromiseResolve (C, x)} algorithm creates a new Promise object using a given
+constructor {\bf C} and resolved with a given value {\bf x}.  However, a
+specification update added three invocations of {\bf PromiseResolve} with a list
+of values for {\bf x} in February 27, 2019.  This error exists in 45 days until
+April 13, 2019 and fails \inred{XX} tests for ES10 in Test262.  For other cases,
+es10-2 arises because of the wrong assertion. es10-3 and es10-7 arise because
+contributors misunderstood the meaning of abrupt completion and \code{=}
+operator for numbers, respectively.  es10-4, es10-5, and es10-6 are
+specification errors that miss or define twice specific corner cases of
+semantic.  For example, es10-4 is an error that does not define the {\bf
+IsFunctionDefinition} algorithm for unnamed functions such as
+\code{function(){}}.  For these seven specification errors, they existed in ES10
+in \inred{XXX} days on average.  Besides, two errors es10-2 and es10-7 are even
+not known before we reported to TC39.
 
-We tested the interpreter using Test262, the official conformance test
-suite provided by TC39, as of August 6, 2019.  Because Test262
-contains tests for extensions and in-progress features, we excluded
-them to focus on the semantics of ES10.  As Table~\ref{table:test262} shows,
-Test262 consists of 36,794 tests and we excluded 7,669 tests for
-extensions and in-progress features.  We also filtered out
-tests for excluded features described in Section~\ref{sec:impl}.
-Finally, we tested 19,282 applicable tests and only 62 tests failed.
-Among them, 54 tests utilize implementation-dependent features,
-three are timeout with 20 minutes due to enormous computation,
-and five are wrong tests.  Thus, we believe that all the
-semantics extracted from \( \tool \) are correct.
+For tests in Test262, we found 10 wrong tests categorized in test-1 and they are
+related to the JavaScript global object. The [[Prototype]] internal property of
+the global object is fully implementation dependent thus the official tests
+should not check its attributes.  However, 10 tests assumes that [[Prototype]]
+of the global object is a prototype chain starts with \code{Object.prototype}.
+They violate the implementation dependent semantics of ES10.  Moreover, they
+existed in Test262 in \inred{XXX} days.
 
-% TODO if some tests failed, categorize them and explain why they failed.
+After resolving above specification errors in ES10, we extracted formal
+semantics from the revised specification again. The revised formal semantics of
+ES10 passed all \inred{XX,XXX} applicable tests in Test262.  We believe that our
+tool can assist to check and find bugs in ECMAScript by generating executable
+formal semantics and executing it with tests in Test262.
 
-\subsection{Adaptability}
-We show the adaptability of \( \tool \) with one case study: applying
-it to an incomplete feature proposal.  Because ECMAScript is an open
-standard language, various proposals are available with their own
-specification changes and tests.  A
-separate repository~\cite{proposals} maintains such proposals with six
-different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
-proposal starts with Stage 0, and the TC39 committee regularly
-examines Stage 3 proposals to decide their next stages.  If a proposal
-is confirmed, the committee changes its stage to Finished and
-integrates it into the next version of ECMAScript.
-Otherwise, the committee changes its stage to Inactive.  Thus, we
-applied \( \tool \) to one Stage 3 proposal.
-%https://github.com/tc39/proposal-optional-chaining
+\subsection{Forward Compatibility}
 
-The optional chaining operator (\( \code{?.} \)) is one of Stage 3
-proposals that removes specific boilerplate code.  It detects a code
-pattern like \( \code{x \&\& x.p} \), which first checks that the
-value of \( \code{x} \) is not \( \code{undefined} \) and then
-accesses its property \( \code{p} \).  With the optional chaining
-operator, we can reduce code size by implementing it as \( \code{x?.p} \).
-We extended ES10 with this proposal and applied \( \tool \)
-to the extended specification.  We found that \textsf{Parser Generator}
-successfully handled three updated lexical productions and three
-updated syntactic productions.  For semantics, the proposal had 22
-updated abstract algorithms.  At the first attempt,
-\textsf{Algorithm Compiler} succeeded compiling only 10 algorithms.
-However, we noticed that several algorithm steps have different styles
-from existing ECMAScript.  Thus, we revised them to the
-original style, sent three pull requests to the GitHub repository
-of the proposal, and the authors of the proposal accepted our pull
-requests\footnote{The URL of three pull requests are anonymized 
-due to a double-blind review process.}.  After revision, 21 of 22
-algorithms are successfully compiled and we manually compiled only one
-algorithm.  Test262 has 33 tests for the optional chaining operator
-and six of them are semantics tests.  The semantics extracted with the
-optional chaining operator proposal successfully passed all the six
-semantics tests.  This case study shows that \( \tool \) is applicable
-to future language features and it could be useful as a specification
-writing guide.
+We show the forward compatibility of \( \tool \) by applying it to the proposals
+that are ready for inclusion in the next ECMAScript (ES11, 2020). Because
+ECMAScript administered as an open-source project, various proposals for new
+language features are available with their own specification changes and tests.
+A separate repository~\cite{proposals} maintains such proposals with six
+different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each proposal
+starts with Stage 0, and the TC39 committee regularly examines Stage 3 proposals
+to decide their next stages.  If a proposal is confirmed, the committee changes
+its stage to Finished and integrates it into the next version of ECMAScript.
+Otherwise, the committee changes its stage to Inactive.  Among them, we applied
+\( \tool \) to all Finished proposals decided to be included in ES11.
 
-\subsection{Usefulness}
-We show the usefulness of \( \tool \) with one case study:
-specification error detection.  While applying \( \tool \) to
-ES10, we found three specification errors.  We fixed them
-and sent pull requests to the official GitHub repository of
-ECMAScript~\cite{es2020}.  They were all confirmed by TC39
-and will be fixed in the next release \footnote{The URL of three pull
-requests are anonymized due to a double-blind review process.}.
+\begin{table}[t]
+  \centering
+  \caption{Evaluation result of \( \tool \) for Finished stage proposals that
+  will be included in ES11.}
+  \label{table:spec-prop-result}
+  \vspace*{-0.5em}
+  \small
+  \begin{tabular}{c?r|r?r?r}
+    \hline
+    \multicolumn{1}{c?}{\multirow{2}{*}{\bf Name}} &
+    \multicolumn{2}{c?}{\bf \( \Delta \) \# Prod.} &
+    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Steps}} &
+    \multicolumn{1}{c}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}
 
-% https://github.com/tc39/ecma262/pull/1661
-% https://github.com/tc39/ecma262/pull/1662
-% https://github.com/tc39/ecma262/pull/1663
-The first error we found is an ambiguous production for
-\textit{IterationStatement}.  For some
-specific cases, the syntax-directed algorithm for
-\textbf{VarScopedDeclarations} is ambiguous.
-Our \( \tool \) detected the duplicated semantics while automatically
-extracting the abstract algorithms in JSON files.
+    &
+    \multicolumn{1}{c|}{\bf Lex.} &
+    \multicolumn{1}{c?}{\bf Syn.} &
+    &\\\hline\hline
 
-The second error is that the \textbf{ExpectedArgumentCount} algorithm
-has missing cases.  While this algorithm counts
-the number of expected arguments of given formal parameters, it does
-not cover the case with only one formal parameter in the sense that it
-does not provide any semantics for the case.  We found this error
-during evaluation of the Test262 tests under the extracted semantics
-via \( \tool \).  The interpreter threw an error because for specific
-tests no \textbf{ExpectedArgumentCount} algorithm was available.
+    \code{matchAll} of \code{String} &
+    \inred{X} &
+    \inred{X} &
+    9/9 &
+    5/5\\\hline
 
-The third error is in \textsf{Ecmarkup}~\cite{ecmarkup}, a
-toolchain that specifies ECMAScript and beautifies an HTML file with
-raw specification to a more readable one.  At first, we though we
-found a missing case for the \textbf{IsFunctionDefinition} algorithm
-of unnamed function expressions.  However, the HTML file with raw
-specification contained the corresponding case.  We investigated the
-issue and realized that \textsf{Ecmarkup} itself had a bug that
-silently removed the {\small opt} subscript in the \( \code{collapsed} \)
-syntax mode.  It was already reported in another pull request but
-\( \tool \) detected it in a mechanical way.
+    \code{import()} &
+    \inred{X} &
+    \inred{X} &
+    \inred{X/X} &
+    \inred{X/X}\\\hline
+
+    \code{BigInt} &
+    \inred{X} &
+    \inred{X} &
+    258/323 &
+    \inred{207}/207\\\hline
+
+    \code{Promise.allSettled} &
+    \inred{X} &
+    \inred{X} &
+    79/85 &
+    50/50\\\hline
+
+    \code{globalThis} &
+    \inred{X} &
+    \inred{X} &
+    1/1 &
+    1/1\\\hline
+
+    \code{for-in} mechanics &
+    \inred{X} &
+    \inred{X} &
+    \inred{X/X} &
+    \inred{X/X}\\\hline
+
+    Optional Chaining &
+    \inred{X} &
+    \inred{X} &
+    72/74 &
+    19/19\\\hline
+
+    Nullish Coalescing Op. &
+    \inred{X} &
+    \inred{X} &
+    10/10 &
+    21/21\\\hline
+
+    \code{import.meta} &
+    \inred{X} &
+    \inred{X} &
+    \inred{X/X} &
+    \inred{X/X}\\\hline
+
+    {\bf Total} &
+    \inred{X} &
+    \inred{X} &
+    \inred{X/X} &
+    \inred{X/X}\\\hline
+  \end{tabular}
+\end{table}
+
+Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to 9
+Finished proposals for ES11.  For all proposals, \inred{XX} lexical and
+\inred{XX} syntactic productions are modified and \( \tool \) successfully
+updated the changes to the synthesized JavaScript parser.  The updated parser
+parses all applicable tests for all proposals.  For abstract algorithms,
+\inred{XXX} steps out of \inred{XXX} steps are automatically converted to the
+corresponding \( \ires \) instructions by the algorithm compiler without
+changing of the compile rules.  Thus, our tool has \inred{XX.XX\%} success rate
+on average for future proposals.  Similar with
+Section~\ref{sec:check-with-tests}, we manually implemented missing part of the
+AST-IR translator for each Finished proposal and checked each extracted
+semantics with official tests.  Each of them passed all applicable tests except
+the semantics for \code{BigInt} proposal.  It fails \inred{XX} tests out of 207
+applicable tests.
+
+Based on the failed tests, we found three undiscovered specification errors
+(bigint-1, bigint-2, and bigint-3), and one reported error (bigint-4) in the
+BigInt proposal as described in Table~\ref{table:spec-tests-errors}.  All of
+them were confirmed by TC39 and will be fixed in the next release.  The BigInt
+proposal added a new type of primitives BigInt and unified the type with
+original Number type to Numeric types.  Thus, it not only added new
+algorithms for BigInt but also modified all existing algorithms related to
+number values.  The error bigint-1 is just a simple misuse of the variable
+\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}. bigint-2 and
+bigint-3 break the backward compatibility because of the incorrectly mixed uses
+of {\bf ToInt32} and {\bf ToUint32} algorithms in unsigned right shift operators
+and bitwise operators, respectively. The last one bigint-4 arises because the
+Number constructor does not consider BigInt primitives.  On average, ECMAScript
+included these four specification errors in \inred{XXX} days.
+
+After fixing all specification errors, we extracted the semantics for the BigInt
+proposal again.  The updated semantics passed all 207 applicable tests.  Thus,
+\( \tool \) also correctly extract IR-based semantics from future proposals.

### 2020-04-23 prop-result/grammar-diff.sh
Added grammar-diff.sh and results

@@ -1,0 +1,18 @@
+#!/bin/bash
+
+# prop_list="prop_matchAll prop_globalThis prop_nulllish_coalescing prop_Promise_allSettled prop_optional_chaining prop_BigInt"
+prop_list="prop_BigInt"
+
+for prop in $prop_list
+do
+  git checkout origin/$prop
+  git submodule update --recursive > /dev/null
+  echo "clean & compile..."
+  sbt clean compile 2>&1 >> /dev/null
+  echo "completed!"
+  echo "run grammar-diff..."
+  sbt "run grammar-diff"
+done
+
+git checkout master
+git submodule update --recursive

### 2020-04-23 prop-result/grammar-diff.sh
Finished filling Table 5

@@ -9,6 +9,7 @@ prop_list="\
   prop_BigInt \
   prop_dynamic_import \
   prop_import_meta \
+  prop_for_in_order \
 "
 
 for prop in $prop_list

### 2020-04-23 ase20/intro.tex
Revised Sec. 1

--- 2020-04-20 ase20/intro.tex
@@
     \inred{XX.X}\% of the steps in abstract algorithms on average.
-  \item \textbf{\( \tool \) bridges the gap between tests and the specification
+  \item \textbf{\( \tool \) bridges gaps between tests and the specification
     written in a natural language.}
-    The formal semantics automatically extracted by \( \tool \) is executable
+    Because the formal semantics automatically extracted by \( \tool \) is executable
     and its components have one-to-one correspondences with the components of
-    the ECMAScript.  It gives opportunity to directly verify the specification
-    through the official test conformance suite, Test262~\cite{test262}.  We
-    manually completed the missing parts for the latest ECMAScript (ES10, 2019),
-    and it is the \textit{first IR-based formal semantics of modern JavaScript}.
-    By executing tests, we found \inred{X} specification errors in ES10 and
-    \inred{XX} wrong tests in Test262. They were all confirmed by TC39 and will
-    be fixed in the next release.  After fixing them, our formal semantics
-    passed all \inred{XX,XXX} applicable tests.
+    ECMAScript, we can check the specification
+    using the official test conformance suite, Test262~\cite{test262}.  After
+    manually completing missing parts of the AST-IR translator for the latest
+    ECMAScript (ES10, 2019), which is the \textit{first IR-based formal
+    semantics of modern JavaScript}, we found \inred{X}
+    specification errors in ES10 and \inred{XX} wrong tests in Test262. They
+    were all confirmed by TC39 and will be fixed in the next release.  After
+    fixing them, the formal semantics passed all \inred{XX,XXX} applicable
+    tests.
   \item \textbf{\( \tool \) is also \textit{forward compatible} with new

### 2020-04-27 ase20/eval.tex
[ASE] Updated Table 3
Updated Table 5
Finished filling Table 5
Slightly revised eval.tex

@@
 anonymized due to a double-blind review process.}, and evaluated the tool
-based on the following three research questions:
+based on the following research questions:
 \begin{itemize}[leftmargin=0.5cm]
@@
 the syntax and semantics from ES7 to ES10?
-\item RQ2. \textbf{Check with Tests:} The syntax and semantics of the latest
-version on ECMAScript (ES10) is compatible with official tests?
+\item RQ2. \textbf{Correctness:} Does \( \tool \) correctly extract IR-based formal
+semantics from ECMAScript?
 \item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
@@
       & \multicolumn{1}{c?}{\textbf{ES10}}
-      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
-      \text{\# Lexical prod.}
+      & \multicolumn{1}{c}{\textbf{Average}}\\\toprule
+      \text{\# Lexical productions}
       & \inred{\text{78}}
@@
       & \inred{\text{78.75}}\\\hline
-      \text{\# Syntactic prod.}
+      \text{\# Syntactic productions}
       & \inred{\text{157}}
@@
       & \multicolumn{1}{c?}{\textbf{ES9}}
-      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-4}
+      & \multirow{2}{*}{\textbf{Average}}\\\cline{1-4}
       \textbf{New version}
@@
       & \\\toprule
-      \Delta \; \text{\# Lexical prod.}
+      \Delta \; \text{\# Lexical productions}
       & \inred{\text{3}}
@@
       & \inred{\text{4.67}}\\\hline
-      \Delta \; \text{\# Syntactic prod.}
+      \Delta \; \text{\# Syntactic productions}
       & \inred{\text{140}}
@@
     45 days &
-    \inred{XX} \\\hline
+    1100 \\\hline
 
@@
     768 days &
-    \inred{XX} \\\hline
+    1120 \\\hline
 
@@
     1065 days &
-    \inred{XX} \\\hline
+    1 \\\hline
 
@@
     602 days &
-    \inred{XX} \\\hline
+    0 \\\hline
 
@@
     \textsf{X} &
-    2019-11-27 &
-    \inred{2019-00-00} &
-    \inred{XX} days &
+    2019-09-27 &
+    2020-04-23 &
+    209 days &
     \inred{XX} \\\hline
@@
     \textsf{O} &
-    2019-11-27 &
-    \inred{2019-00-00} &
-    \inred{XX} days &
+    2019-09-27 &
+    2019-11-19 &
+    53 days &
     \inred{XX} \\\hline
@@
     \code{matchAll} of \code{String} &
-    \inred{X} &
-    \inred{X} &
+    0 &
+    0 &
     9/9 &
@@
     \code{import()} &
-    \inred{X} &
-    \inred{X} &
-    \inred{X/X} &
-    \inred{X/X}\\\hline
+    0 &
+    2 &
+    22/23 &
+    0/0\\\hline
 
     \code{BigInt} &
-    \inred{X} &
-    \inred{X} &
+    4 &
+    0 &
     258/323 &
@@
     \code{Promise.allSettled} &
-    \inred{X} &
-    \inred{X} &
+    0 &
+    0 &
     79/85 &
@@
     \code{globalThis} &
-    \inred{X} &
-    \inred{X} &
+    0 &
+    0 &
     1/1 &
@@
     \code{for-in} mechanics &
-    \inred{X} &
-    \inred{X} &
-    \inred{X/X} &
-    \inred{X/X}\\\hline
+    0 &
+    0 &
+    36/37 &
+    0/0\\\hline
 
     Optional Chaining &
-    \inred{X} &
-    \inred{X} &
+    3 &
+    3 &
     72/74 &
@@
     Nullish Coalescing Op. &
-    \inred{X} &
-    \inred{X} &
+    1 &
+    4 &
     10/10 &
@@
     \code{import.meta} &
-    \inred{X} &
-    \inred{X} &
-    \inred{X/X} &
-    \inred{X/X}\\\hline
+    0 &
+    2 &
+    15/15 &
+    0/0\\\hline
 
     {\bf Total} &
-    \inred{X} &
-    \inred{X} &
-    \inred{X/X} &
-    \inred{X/X}\\\hline
+    8 &
+    11 &
+    502/577 &
+    \inred{303}/303\\\hline
   \end{tabular}

### 2020-04-27 ase20/eval.tex
[ASE] Revised Evaluation section

@@
 algorithms \( \tool \) automatically generates parsers and AST-IR translators,
-respectively, in two respects: 1) in each version and 2) in each difference
-between adjacent versions.
+respectively, in two respects: 1) in each version and 2) in each update between
+adjacent versions.
 
@@
   \begin{subfigure}{0.48\textwidth}
-    \includegraphics[width=\textwidth]{img/sem-diff.pdf}
-    \caption{Results for differences between adjacent versions}
-    \label{fig:semantics-all-version-diff}
+    \includegraphics[width=\textwidth]{img/sem-update.pdf}
+    \caption{Results for annual updates}
+    \label{fig:semantics-all-version-update}
   \end{subfigure}
@@
 compile algorithm steps to the corresponding \( \ires \) instructions with
-\inred{91.60\%} success rate on average for existing specifications, and
-\inred{90.43\%} for updates.  ECMAScript abstract algorithms describe not only
+\inred{91.38\%} success rate on average for existing specifications, and
+\inred{92.08\%} for updates.  ECMAScript abstract algorithms describe not only
 core language semantics but also other helper functions of built-in libraries.
@@
 specific functionalities.  Thus, built-in libraries have lower success rates
-(\inred{86.98\%} for specifications and \inred{86.09\%} for updates) than core
-language semantics (\inred{95.35\%} for specifications and \inred{95.25\%} for
+(\inred{86.74\%} for specifications and \inred{88.24\%} for updates) than core
+language semantics (\inred{95.14\%} for specifications and \inred{96.41\%} for
 updates).
@@
 
-To define the \textit{first IR-based formal semantics of modern JavaScript}, we
-completed missing parts of the AST-IR translator for ES10.  Among \inred{9,674}
-steps in ES10, \inred{8,901} steps are automatically compiled via
-\textsf{Algorithm Compiler}.  Among the remaining \inred{773} steps, we manually
-implemented all remaining language semantics (\inred{221} steps) and essential
-parts of built-in libraries (\inred{XX} steps out of \inred{552}) in \inred{XX}
-days.  Moreover, we manually implemented the \textsf{Global Setting} as described
-in Section~\ref{sec:compiler-impl} for the core language features.  However, we
-do not support several minor language features that do not affect the overall
-JavaScript semantics critically: non-strict mode codes, modules, early errors
-before actual executions, and inessential built-in objects.
+To evaluate the correctness of \( \tool \), we utilizes Test262, the official
+conformance test suite provided by TC39.  First, we complete missing parts of
+the AST-IR translator for the latest version of ECMAScript (ES10). Then, we
+test the extracted semantics of ES10 with Test262 and reason about the failed
+tests.
 
-Thanks to the executability of our extracted formal semantics, we checked the
-semantics with Test262, the official conformance test suite provided by TC39.
-We fixed version of Test262 as of February 28, 2019 because the ES10 was
-branched out with the branch name es2019 in that day.  While it consists of
-\inred{XX,XXX} tests, we filtered out \inred{XX,XXX} tests not applicable for
-our formal semantics as shown in Table~\ref{table:test262}.  Test262 targets not
-only the current official version of ECMAScript but several extensions and
-in-progress features. We excluded \inred{X,XXX} tests for such cases to focus on
-the semantics of ES10.  Among \inred{XX,XXX} ES10 tests, we also filtered out
-\inred{X,XXX} tests using language features not supported by our semantics.
+To focus on core language semantics of JavaScript, we completed only necessary
+parts in missing parts of AST-IR translator for ES10.  For abstract algorithms
+in ES10, \inred{8,901} steps out of \inred{9,674} steps are automatically
+compiled via \textsf{Algorithm Compiler} as described in
+Figure~\ref{fig:all-version}(a).  Among the remaining \inred{773} steps, we
+manually implemented all missing steps for core language semantics (\inred{221}
+steps) and essential parts of built-in libraries (\inred{XX} steps out of
+\inred{552}).  Moreover, we manually implemented the \textsf{Global Setting} as
+described in Section~\ref{sec:compiler-impl} for the core language features.
+However, we do not support several minor language features that do not affect
+the overall JavaScript semantics critically: non-strict mode codes, modules,
+early errors before actual executions, and inessential built-in objects.
 
@@
   \centering
-  \caption{Specification errors and wrong tests in Test262.}
-  \label{table:spec-tests-errors}
+  \caption{Specification errors in ES10 and in proposals that are ready for
+  inclusion in ES11.}
+  \label{table:spec-errors}
   \vspace*{-0.5em}
@@
     es10-1 &
+    Condition &
+    \makecell[l]{Ambiguous production rule for \\
+    dangling \code{else} problem in {\it IfStatement}.} &
+    \textsf{X} &
+    2015-06-01 &
+    \inred{2020-00-10} &
+    \inred{XXX} days &
+    1 \\\hline
+
+    es10-2 &
     Await &
@@
 
-    es10-2 &
-    IterationKind &
+    es10-3 &
+    Iteration &
     \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
@@
 
-    es10-3 &
+    es10-4 &
     Completion &
@@
     \textsf{O} &
-    2016-06-01 &
+    2015-06-01 &
     2019-05-02 &
@@
 
-    es10-4 &
+    es10-5 &
+    String &
+    \makecell[l]{Wrong use of \code{=} operator in {\bf
+    StringGetOwnProperty}.} &
+    \textsf{X} &
+    2015-06-01 &
+    \inred{2019-00-00} &
+    \inred{XX} days &
+    \inred{XX} \\\hline
+
+    es10-6 &
     Function &
@@
 
-    es10-5 &
-    ForOf &
-    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
-    await(var x of e)\{...\}}.} &
-    \textsf{O} &
-    2018-02-16 &
-    2019-10-11 &
-    602 days &
-    0 \\\hline
-
-    es10-6 &
-    Argument &
+    es10-7 &
+    Function &
     \makecell[l]{No semantics of {\bf ExpectedArgumentCount} \\ for the base case
@@
 
-    es10-7 &
-    String &
-    \makecell[l]{Wrong use of \code{=} operator in {\bf
-    StringGetOwnProperty}.} &
-    \textsf{X} &
-    2015-06-01 &
-    \inred{2019-00-00} &
-    \inred{XX} days &
+    es10-8 &
+    Iteration &
+    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
+    await(var x of e)\{...\}}.} &
+    \textsf{O} &
+    2018-02-16 &
+    2019-10-11 &
+    602 days &
     \inred{XX} \\\hline
 
-    test-1 &
-    Global &
-    \makecell[l]{Testing implementation-dependent [[Prototype]] \\ of the global
-    object.} &
-    \textsf{X} &
-    \inred{2019-00-00} &
-    \inred{2019-00-00} &
-    \inred{XX} days &
-    10 \\\hline
-
     bigint-1 &
-    UpdateExpression &
+    Expression &
     \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
@@
     bigint-2 &
-    NumberOp &
+    Number &
     \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
@@
     bigint-3 &
-    NumberOp &
+    Number &
     \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
@@
 
+To check the correctness of the extracted IR-based semantics using Test262, we
+fixed version of Test262 as of February 28, 2019 because the ES10 was branched
+out with the branch name es2019 in that day.  While it consists of
+\inred{XX,XXX} tests, we filtered out \inred{XX,XXX} tests not applicable for
+our formal semantics as shown in Table~\ref{table:test262}.  Test262 targets not
+only the current official version of ECMAScript but several extensions and
+in-progress features. We excluded \inred{X,XXX} tests for such cases to focus on
+the semantics of ES10.  Among \inred{XX,XXX} ES10 tests, we also filtered out
+\inred{X,XXX} tests using language features not supported by our semantics.
+
 \begin{table}[t]
   \centering
-  \caption{Excluded tests in Test262}
+  \caption{Test results for Test262}
   \label{table:test262}
@@
 
-For \inred{XX,XXX} applicable tests, the synthesized JavaScript parser
-successfully parses all tests but \inred{XXX} tests are failed to be executed
-because of the different semantics between ECMAScript and official tests.  Based
-on the failed tests, we found 7 specification errors in ES10 and 10 wrong tests
-in Test262 as described in Table~\ref{table:spec-tests-errors}.  For example,
-the specification error es10-1 is related to the JavaScript Await.  The {\bf
-PromiseResolve (C, x)} algorithm creates a new Promise object using a given
-constructor {\bf C} and resolved with a given value {\bf x}.  However, a
-specification update added three invocations of {\bf PromiseResolve} with a list
-of values for {\bf x} in February 27, 2019.  This error exists in 45 days until
-April 13, 2019 and fails \inred{XX} tests for ES10 in Test262.  For other cases,
-es10-2 arises because of the wrong assertion. es10-3 and es10-7 arise because
-contributors misunderstood the meaning of abrupt completion and \code{=}
-operator for numbers, respectively.  es10-4, es10-5, and es10-6 are
-specification errors that miss or define twice specific corner cases of
-semantic.  For example, es10-4 is an error that does not define the {\bf
-IsFunctionDefinition} algorithm for unnamed functions such as
-\code{function(){}}.  For these seven specification errors, they existed in ES10
-in \inred{XXX} days on average.  Besides, two errors es10-2 and es10-7 are even
-not known before we reported to TC39.
+For \inred{XX,XXX} applicable tests, the extracted semantics fails \inred{XXX}
+tests.  We reason about the failed tests, and we discover that they failed
+because ES10 actually has specification errors. We found eight specification
+errors in ES10 (es10-1 to es10-9 in Table~\ref{table:spec-errors}).  Among them,
+five errors are already fixed in the draft version of ECMAScript but three errors
+are newly revealed.  We reported four new errors, and TC39 confirmed and
+merged them into the current draft.
 
-For tests in Test262, we found 10 wrong tests categorized in test-1 and they are
-related to the JavaScript global object. The [[Prototype]] internal property of
-the global object is fully implementation dependent thus the official tests
-should not check its attributes.  However, 10 tests assumes that [[Prototype]]
-of the global object is a prototype chain starts with \code{Object.prototype}.
-They violate the implementation dependent semantics of ES10.  Moreover, they
-existed in Test262 in \inred{XXX} days.
+es10-1 is related to the dangling \code{else} problem introduced in ALGOL
+60~\cite{dangling-else}. While ES10 describes the rule that the \code{else}
+should be associated with the nearest \code{if}, the rule is not explicitly
+represented in the ES10 grammar rule.  It causes one test failed and it is a not
+yet discovered error.  Thus, we revised the grammar rule to satisfy this rule
+and TC39 accepted it in \inred{May X, 2020}.
+
+es10-2 is related to the JavaScript Await.  The {\bf PromiseResolve (C, x)}
+algorithm creates a new Promise object using a given constructor {\bf C} and
+resolved with a given value {\bf x}.  However, a specification update added
+three invocations of {\bf PromiseResolve} with a list of values for {\bf x} in
+February 27, 2019.  This error exists in 45 days until April 13, 2019 and causes
+\inred{XX} tests failed.
+
+es10-3 arises because of the wrong assertion. ES9 introduced \code{for await}
+iteration statements thus it also introduced a new {\it iterationKind} tag,
+\code{async-iterate}. However, \code{ForIn/OfHeadEvaluation} algorithm misses
+the case of \code{async-iterate} in the assertion. It causes 1120 tests failed
+and it is an unknown error. Thus, we revised the assertion to cover the
+\code{async-iterate} case and TC39 accepted it in March 25, 2020.
+
+es10-4 and es10-5 arise because contributors misunderstood the meaning of
+operations used in abstract algorithms. Especially, es10-5 is related to
+\code{=} operator for numbers and not yet discovered. In abstract algorithms,
+``{\it x} = {\it y}'' denotes equality expression for double-precision 64-bit
+binary format IEEE 754-2008 values thus ``+0 = -0'' is true. However, the {\bf
+StringGetOwnProperty} algorithms uses ``{\it index} = -0'' to check whether
+index is exactly same with -0 but it is true even if {\it index} is +0.
+
+es10-6, es10-7, and es10-8 are errors that miss or define twice some parts of
+cases in semantics. For example, es10-8 is an error that define the {\bf
+VarScopedDeclarations} for \code{for await} iterations. If the choice is wrong,
+\inred{XX} tests will be failed.
 
@@
 semantics from the revised specification again. The revised formal semantics of
-ES10 passed all \inred{XX,XXX} applicable tests in Test262.  We believe that our
-tool can assist to check and find bugs in ECMAScript by generating executable
-formal semantics and executing it with tests in Test262.
+ES10 passed all \inred{XX,XXX} applicable tests in Test262.  \( \tool \) is
+helpful to correctly extract semantics from ECMAScript but also to detect bugs
+by directly check ECMAScript with Test262. Without our tool, above eight errors
+existed in ECMAScript in \inred{XXX} days on average. Besides, three errors
+es10-1, es10-3, and es10-5 are even not known before we reported to TC39. We
+believe that \( \tool \) bridges gaps between ECMAScript and Test262.
 
@@
   \small
-  \begin{tabular}{c?r|r?r?r}
+  \begin{tabular}{c?r|r?r?r?r}
     \hline
@@
     \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Steps}} &
+    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Tests}} &
     \multicolumn{1}{c}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}
@@
     9/9 &
-    5/5\\\hline
+    5/5 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     22/23 &
-    0/0\\\hline
+    0/0 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     258/323 &
-    \inred{207}/207\\\hline
+    \inred{207}/207 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     79/85 &
-    50/50\\\hline
+    50/50 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     1/1 &
-    1/1\\\hline
+    1/1 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     36/37 &
-    0/0\\\hline
+    0/0 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     72/74 &
-    19/19\\\hline
+    19/19 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     10/10 &
-    21/21\\\hline
+    21/21 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     15/15 &
-    0/0\\\hline
+    0/0 &
+    \inred{XXXXX}/\inred{XXXXX}\\\hline
 
@@
     11 &
-    502/577 &
-    \inred{303}/303\\\hline
+    502/577\\\cline{1-4}
   \end{tabular}
@@
 the semantics for \code{BigInt} proposal.  It fails \inred{XX} tests out of 207
-applicable tests.
+applicable tests for the proposal and \inred{XXXX} tests out of \inred{XXXXX}
+applicable tests for ES10.
 
@@
 (bigint-1, bigint-2, and bigint-3), and one reported error (bigint-4) in the
-BigInt proposal as described in Table~\ref{table:spec-tests-errors}.  All of
+BigInt proposal as described in Table~\ref{table:spec-errors}.  All of
 them were confirmed by TC39 and will be fixed in the next release.  The BigInt
@@
 After fixing all specification errors, we extracted the semantics for the BigInt
-proposal again.  The updated semantics passed all 207 applicable tests.  Thus,
-\( \tool \) also correctly extract IR-based semantics from future proposals.
+proposal again.  The updated semantics passed all 207 applicable tests for the
+proposal and \inred{XXXXX} applicable tests for ES10.  Thus, \( \tool \) also
+correctly extract IR-based semantics from future proposals.

### 2020-04-27 ase20/intro.tex
[ASE] Revised Evaluation section

@@
     \inred{XX.X}\% of the steps in abstract algorithms on average.
-  \item \textbf{\( \tool \) bridges gaps between tests and the specification
-    written in a natural language.}
-    Because the formal semantics automatically extracted by \( \tool \) is executable
-    and its components have one-to-one correspondences with the components of
-    ECMAScript, we can check the specification
-    using the official test conformance suite, Test262~\cite{test262}.  After
-    manually completing missing parts of the AST-IR translator for the latest
-    ECMAScript (ES10, 2019), which is the \textit{first IR-based formal
-    semantics of modern JavaScript}, we found \inred{X}
-    specification errors in ES10 and \inred{XX} wrong tests in Test262. They
-    were all confirmed by TC39 and will be fixed in the next release.  After
-    fixing them, the formal semantics passed all \inred{XX,XXX} applicable
-    tests.
+  \item \textbf{\( \tool \) bridges gaps between the specification written in a
+    natural language and tests.}
+    To evaluate the correctness of \( \tool \), we checked the extracted
+    semantics with the official test conformance suite, Test262~\cite{test262}.
+    By manually completing missing parts of the AST-IR translator for the latest
+    ECMAScript (ES10, 2019), we define the \textit{first IR-based formal
+    semantics of modern JavaScript}. It fails \inred{XXXX} tests because of the
+    specification errors in ES10. We found eight specification errors and
+    three of them are even not yet reported errors. They were all confirmed by
+    TC39 and will be fixed in the next release.  After fixing them, the formal
+    semantics passed all \inred{XX,XXX} applicable tests.
   \item \textbf{\( \tool \) is also \textit{forward compatible} with new

### 2020-04-27 ase20/conclusion.tex
[ASE] Revised Realted Work and Conclusion

@@
 \section{Conclusion}\label{sec:conclude}
-The annual updates of the ECMAScript makes it difficult to
-build program analysis or formal verification of JavaScript due to the
-required human efforts in modeling a moving target.  In this paper,
-we proposed a tool \( \tool \), which \textit{automatically} extracts the
-syntax and semantics specified in ECMAScript.  The tool
-generates a parser from a language grammar written in \( \bnfes \), and
-compiles abstract algorithms written in English to \( \ires \) functions.
-The only parts that require manual efforts are compile rules and
-language-specific global setting, which we provide for ECMAScript
-as an example case study.  We also support \textsf{Fault Localizer} to
-adapt updates of ECMAScript by suggesting new rules.
-We evaluated \( \tool \) by applying it to ES10 with Test262.
-The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.
-The tool also detected three confirmed errors from the specification.
-Moreover, we showed that the tool is also applicable to an incomplete
-language proposal. The implementation of the tool is publicly available
-as an open-source project.
+
+The annual updates of the ECMAScript makes it difficult to build program
+analysis or formal verification of JavaScript due to the required human efforts
+in modeling a moving target.  In this paper, we proposed a tool \( \tool \),
+which \textit{automatically} extracts the syntax and semantics specified in
+ECMAScript.  The tool generates a parser from a language grammar written in \(
+\bnfes \), and an AST-IR translator from abstract algorithms written in
+English.  The tool automatically extract all syntax and \inred{XX.XX\%} of
+semantics for the most recent four versions of ECMAScript (ES7 to ES10).  We
+evaluated the correctness of the tool by testing the extracted semantics from
+ES10 with Test262, the official conformance suite.  Based on \inred{X,XXX}
+failed tests, we found eight specification errors in ES10. After resolving
+them, the extracted semantics passed all \inred{XX,XXX} applicable tests.
+Moreover, we showed that \( \tool \) is also forward compatible for the future
+language features by applying it to nine proposals, and we found four
+specification errors in the proposal for BigInt.  We believe that it could
+dramatically reduce the human efforts to define formal semantics of ECMAScript
+and also bridge gaps between ECMAScript and Test262.

### 2020-04-27 ase20/related.tex
[ASE] Revised Realted Work and Conclusion

@@
 has the fundamental problem of ordered choices: \( ab \) is silently
-unmatched with \( a \mid ab \).  While Generalized LL (GLL) parsing~\cite{gll}
+unmatched with \( a ~/~ ab \).  While Generalized LL (GLL) parsing~\cite{gll}
 is basically recursive-descent with backtracking that can support general
 context-free grammars (CFGs) even in the presence of ambiguous grammars,
-its worst-time complexity is \( O(n^3) \) for the input size \( n \).
-Unlike GLL parsing, our lookahead parsing is not applicable to general CFGs,
-but we experimentally showed that it can generate JavaScript parsers.
-The complexity of lookahead parsing is \( O(k \cdot n) \) for the input size
-\( n \) and the constant number of tokens \( k \).
+its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
+does not support context-sensitive features.  Unlike GLL parsing, our lookahead
+parsing is applicable for JavaScript parsers having context sensitive features
+such as positive/negative lookaheads. Moreover, The complexity of lookahead
+parsing is \( O(k \cdot n) \) for the input size \( n \) and the constant
+number of tokens \( k \). We experimentally showed that it can generate parsers
+for the most recent four versions of ECMAScript.
 
@@
 of the API functions to find correct modeling.  Unlike their approach, we
-introduce a fault localization algorithm to support future language
-updates and to provide correct meaning of specification. Our tool is also
-applicable for testing even when the actual implementation is not available.
-
-% TODO pseudo code의 형태와 natural language의 결합이다.
-% TODO moudular test로 guide를 받을 수 없어서 user defined rule을 사용. 대신, statistical analysis를 기반으로 guide해줌
-
-% \begin{itemize}
-%   \item Automatic Model Generation from Documentation for Java API Functions (ICSE'16)~\cite{javadoc}
-% \end{itemize}
-
-% Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
-% web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
-% using it to formal verification or program analysis.
+introduce semi-automatic synthesis based on general compile rules that
+represent the common writing patterns to support future language updates and to
+provide correct meaning of specification.  The extracted semantics via our tool
+is also executable that helps to bridge gaps between the specification written
+in a natural language and tests.
 
@@
 specification to their own IR called JSIL to make further analysis.
-Our approach provides a mechanized framework to synthesize syntactic parsers and
-to automatically extract semantics
-using a rule-based compilation technique, which significantly reduces human
-efforts.
-
-% \begin{itemize}
-%   \item JaVerT: JavaScript verification toolchain (POPL'18)~\cite{javert}
-%   \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
-%   \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
-%   \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
-% \end{itemize}
+However, all of them targets only ES5.1 or former versions of ECMAScript and
+they do not provide solution for annual updates of ECMAScript. Our approach
+provides a mechanized framework to synthesize JavaScript parsers and to
+automatically extract semantics using a rule-based compilation technique, which
+significantly reduces human efforts.

### 2020-04-30 ase20/eval.tex
Minor edit in Intro and Till Sec. 5.1

@@
 
-We developed \( \tool \) as an open source tool\footnote{The URL of the tool is
+We developed \( \tool \) as an open-source tool\footnote{The URL of the tool is
 anonymized due to a double-blind review process.}, and evaluated the tool
@@
 \begin{itemize}[leftmargin=0.5cm]
-\item RQ1. \textbf{Coverage:} How much parts \( \tool \) automatically extract
-the syntax and semantics from ES7 to ES10?
-\item RQ2. \textbf{Correctness:} Does \( \tool \) correctly extract IR-based formal
-semantics from ECMAScript?
+\item RQ1. \textbf{Coverage:} How much percentage of 
+the syntax and semantics does \( \tool \) automatically extract from ES7 to ES10?
+\item RQ2. \textbf{Correctness:} Does \( \tool \) extract an IR-based formal
+semantics from ECMAScript correctly?
 \item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
@@
 \begin{table}[t]
-  \caption{Number of productions in specifications,
+  \caption{Syntax coverage: Number of productions in each specification
+and in each update between adjacent versions,
 from \textit{all} of which \( \tool \) automatically generated parsers}
@@
 
-\( \tool \) targets ECMAScript specifications released after ES7 in 2016 because
-our tool utilizes common patterns in the converged writing style since ES7 as
-already explained in Section~\ref{sec:overview}.  Thus, we evaluate the coverage
-of \( \tool \) by applying it to the most recent four versions of ECMAScript,
-ES7 to ES10.  We measured for how many grammar productions and steps in abstract
-algorithms \( \tool \) automatically generates parsers and AST-IR translators,
-respectively, in two respects: 1) in each version and 2) in each update between
+We evaluated the coverage of \( \tool \) in two respects: syntax
+and semantics.  For syntax, we measured how many grammar
+productions in specifications \( \tool \) automatically generated
+parsers from, and for semantics, we measured how many abstract
+algorithm steps in specifications it automatically generated the
+JavaScript semantics from.  Because \( \tool \) utilizes common
+patterns in the converged writing style since ES7 as we discussed in
+Section~\ref{sec:overview}, we evaluated its coverage using the most
+recent four versions of ECMAScript, ES7 to ES10.  We measured the
+numbers for each ECMAScript version and for each update between
 adjacent versions.
@@
     \includegraphics[width=\textwidth]{img/sem-all.pdf}
-    \caption{Results for existing versions}
+    \caption{For each ECMAScript version from ES7 to ES10}
+\vspace*{.5em}
     \label{fig:semantics-all-version}
@@
     \includegraphics[width=\textwidth]{img/sem-update.pdf}
-    \caption{Results for annual updates}
+    \caption{For each update between adjacent versions}
     \label{fig:semantics-all-version-update}
   \end{subfigure}
-  \caption{Number of abstract algorithm steps in specifications, from which
-\( \tool \) generated the JavaScript semantics}
+\vspace*{-.5em}
+\caption{Semantics coverage: Number of algorithm steps in specifications,
+from which \( \tool \) generated the semantics}
   \label{fig:all-version}
@@
 For semantics, Figure~\ref{fig:all-version} shows that \( \tool \) automatically
-compile algorithm steps to the corresponding \( \ires \) instructions with
-\inred{91.38\%} success rate on average for existing specifications, and
-\inred{92.08\%} for updates.  ECMAScript abstract algorithms describe not only
-core language semantics but also other helper functions of built-in libraries.
-Built-in libraries written in more diverse styles in describing their own
-specific functionalities.  Thus, built-in libraries have lower success rates
+compiled algorithm steps to corresponding \( \ires \) instructions with
+the success rate of \inred{91.38\%} on average for each ECMAScript version
+from ES7 to ES10, and \inred{92.08\%} for each update between adjacent
+versions.  ECMAScript abstract algorithms describe not only
+core language semantics but also built-in libraries with various helper functions.
+Note that built-in libraries are written in more diverse styles than
+core language semantics due to their own specific functionalities.
+Therefore, built-in libraries have lower success rates
 (\inred{86.74\%} for specifications and \inred{88.24\%} for updates) than core
@@
 
-This results show that \( \tool \) effectively reduces the efforts to
-extract the syntax and semantics of JavaScript not only for developing
-them from scratch, but also for updating existing ones.
+Because \( \tool \) automatically extracts the syntax
+and semantics from specifications and updates with high coverage rates,
+it reduces efforts not only in developing JavaScript tools from scratch
+from specifications but also in evolving existing tools for updates.
 

### 2020-04-30 ase20/intro.tex
Minor edit in Intro and Till Sec. 5.1

@@
     By manually completing missing parts of the AST-IR translator for the latest
-    ECMAScript (ES10, 2019), we define the \textit{first IR-based formal
-    semantics of modern JavaScript}. It fails \inred{XXXX} tests because of the
-    specification errors in ES10. We found eight specification errors and
-    three of them are even not yet reported errors. They were all confirmed by
+    ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
+    semantics of modern JavaScript}. It failed for \inred{XXXX} tests because of
+    specification errors in ES10. Using the tests, we found eight specification errors,
+    three of which had not been reported before. They were all confirmed by
     TC39 and will be fixed in the next release.  After fixing them, the formal

### 2020-04-30 ase20/eval.tex
Till Sec. 5.2

@@
 
-\subsection{Check with Tests}\label{sec:check-with-tests}
-
-To evaluate the correctness of \( \tool \), we utilizes Test262, the official
-conformance test suite provided by TC39.  First, we complete missing parts of
-the AST-IR translator for the latest version of ECMAScript (ES10). Then, we
-test the extracted semantics of ES10 with Test262 and reason about the failed
-tests.
-
-To focus on core language semantics of JavaScript, we completed only necessary
-parts in missing parts of AST-IR translator for ES10.  For abstract algorithms
-in ES10, \inred{8,901} steps out of \inred{9,674} steps are automatically
-compiled via \textsf{Algorithm Compiler} as described in
-Figure~\ref{fig:all-version}(a).  Among the remaining \inred{773} steps, we
-manually implemented all missing steps for core language semantics (\inred{221}
-steps) and essential parts of built-in libraries (\inred{XX} steps out of
-\inred{552}).  Moreover, we manually implemented the \textsf{Global Setting} as
-described in Section~\ref{sec:compiler-impl} for the core language features.
-However, we do not support several minor language features that do not affect
-the overall JavaScript semantics critically: non-strict mode codes, modules,
-early errors before actual executions, and inessential built-in objects.
-
+\subsection{Correctness}\label{sec:check-with-tests}
 \begin{table*}[t]
   \centering
-  \caption{Specification errors in ES10 and in proposals that are ready for
-  inclusion in ES11.}
+  \caption{Specification errors in ES10 and the BigInt proposal ready for
+  inclusion in ES11}
   \label{table:spec-errors}
-  \vspace*{-0.5em}
+  \vspace*{-.5em}
   \small
-  \begin{tabular}{|c|c|l|c|c|c|c|c|}
-    \hline
-    \multicolumn{1}{|c|}{\bf Name} &
-    \multicolumn{1}{c|}{\bf Feature} &
-    \multicolumn{1}{c|}{\bf Description} &
-    \multicolumn{1}{c|}{\bf Known} &
-    \multicolumn{1}{c|}{\bf Created} &
-    \multicolumn{1}{c|}{\bf Resolved} &
-    \multicolumn{1}{c|}{\bf Existed} &
-    \multicolumn{1}{c|}{\bf \# Failed Tests} \\\hline
+  \begin{tabular}{@{}c?c|l|@{}c@{}|c|c|r|@{}r@{}}
+\multicolumn{1}{@{}c?}{\bf Name} &
+\multicolumn{1}{c}{\bf Feature} &
+\multicolumn{1}{c}{\bf Description} &
+\multicolumn{1}{@{}c@{}}{\bf Known} &
+\multicolumn{1}{c}{\bf Created} &
+\multicolumn{1}{c}{\bf Resolved} &
+\multicolumn{1}{c}{\bf Existed} &
+\multicolumn{1}{@{}c@{}}{\bf \# Fails} \\\toprule
+&&&&&&&\\[-1.5em]
+    ES10-1 &
+    Iteration &
+    \makecell[l]{Missing the \code{async-iterate} case in the assertion of\\
+ {\bf ForIn/OfHeadEvaluation}} &
+    \textsf{X} &
+    2018-02-16 &
+    2020-03-25 &
+    768 days &
+    1,120 \\\hline
 
-    es10-1 &
+    ES10-2 &
     Condition &
-    \makecell[l]{Ambiguous production rule for \\
-    dangling \code{else} problem in {\it IfStatement}.} &
+    \makecell[l]{Ambiguous grammar production for the dangling \code{else} problem in\\
+    {\it IfStatement}} &
     \textsf{X} &
     2015-06-01 &
-    \inred{2020-00-10} &
-    \inred{XXX} days &
+    TBD &
+    \multicolumn{1}{c|}{TBD} &
     1 \\\hline
 
-    es10-2 &
+    ES10-3 &
+    String &
+    \makecell[l]{Wrong use of the \code{=} operator in {\bf
+    StringGetOwnProperty}} &
+    \textsf{X} &
+    2015-06-01 &
+    TBD &
+    \multicolumn{1}{c|}{TBD} &
+    \inred{XX} \\\hline
+
+ ES10-4 &
+ Completion &
+ Unhandling abrupt completion in {\bf Abstract Equality Comparison} &
+ \textsf{X} &
+\inred{0000-00-00}&
+ 2020-04-28 &
+ \inred{XX} days &
+ \inred{XX}
+ \\\hline
+
+    ES10-5 &
+    Completion &
+    \makecell[l]{Unhandling abrupt completion in {\bf Evaluation} of {\it
+    EqualityExpression}} &
+    \textsf{O} &
+    2015-06-01 &
+    2019-05-02 &
+    1,065 days &
+    1 \\\hline
+
+    ES10-6 &
     Await &
-    \makecell[l]{Passing wrong type of \\ the second argument for {\bf PromiseResolve}.} &
+    \makecell[l]{Passing a value of wrong type to the second parameter of\\ {\bf PromiseResolve}} &
     \textsf{O} &
@@
     45 days &
-    1100 \\\hline
+    1,100 \\\hline
 
-    es10-3 &
-    Iteration &
-    \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
-    ForIn/OfHeadEvaluation}.} &
-    \textsf{X} &
-    2018-02-16 &
-    2020-03-25 &
-    768 days &
-    1120 \\\hline
-
-    es10-4 &
-    Completion &
-    \makecell[l]{Not handling abrupt completion \\ in {\bf Evaluation} of {\it
-    EqualityExpression}.} &
-    \textsf{O} &
-    2015-06-01 &
-    2019-05-02 &
-    1065 days &
-    1 \\\hline
-
-    es10-5 &
-    String &
-    \makecell[l]{Wrong use of \code{=} operator in {\bf
-    StringGetOwnProperty}.} &
-    \textsf{X} &
-    2015-06-01 &
-    \inred{2019-00-00} &
-    \inred{XX} days &
-    \inred{XX} \\\hline
-
-    es10-6 &
+    ES10-7 &
     Function &
-    \makecell[l]{No semantics of {\bf IsFunctionDefinition} \\ for
-    \code{function(...)\{...\}}.} &
+    \makecell[l]{No semantics of {\bf IsFunctionDefinition} for
+    \code{function(...)\{...\}}} &
     \textsf{O} &
@@
     2020-01-18 &
-    1541 days &
+    1,541 days &
     \inred{XX} \\\hline
 
-    es10-7 &
+    ES10-8 &
     Function &
-    \makecell[l]{No semantics of {\bf ExpectedArgumentCount} \\ for the base case
-    of {\it FormalParameters}.} &
+    \makecell[l]{No semantics of {\bf ExpectedArgumentCount} for the base case
+    of\\ {\it FormalParameters}} &
     \textsf{O} &
@@
     2020-02-20 &
-    1205 days &
+    1,205 days &
     \inred{XX} \\\hline
 
-    es10-8 &
+    ES10-9 &
     Iteration &
-    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
-    await(var x of e)\{...\}}.} &
+    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} for\\ \code{for
+    await(var x of e)\{...\}}} &
     \textsf{O} &
@@
     602 days &
-    \inred{XX} \\\hline
+    \inred{XX} \\\hline\hline
 
-    bigint-1 &
+    BigInt-1 &
     Expression &
@@
 
-    bigint-2 &
+    BigInt-2 &
     Number &
@@
 
-    bigint-3 &
+    BigInt-3 &
     Number &
-    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
+    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} in {\bf
     NumberBitwiseOp}.} &
@@
 
-    bigint-4 &
+    BigInt-4 &
     Number &
@@
     53 days &
-    \inred{XX} \\\hline
-
+    \inred{XX}
   \end{tabular}
 \end{table*}
-
-To check the correctness of the extracted IR-based semantics using Test262, we
-fixed version of Test262 as of February 28, 2019 because the ES10 was branched
-out with the branch name es2019 in that day.  While it consists of
-\inred{XX,XXX} tests, we filtered out \inred{XX,XXX} tests not applicable for
-our formal semantics as shown in Table~\ref{table:test262}.  Test262 targets not
-only the current official version of ECMAScript but several extensions and
-in-progress features. We excluded \inred{X,XXX} tests for such cases to focus on
-the semantics of ES10.  Among \inred{XX,XXX} ES10 tests, we also filtered out
-\inred{X,XXX} tests using language features not supported by our semantics.
 
@@
   \label{table:test262}
-  \vspace*{-0.5em}
+  \vspace*{-.5em}
   \small
@@
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict modes & \inred{X,XXX}\\\hdashline
+    Non-strict mode & \inred{X,XXX}\\\hdashline
     Modules & \inred{X,XXX} \\\hdashline
-    Early errors & \inred{X,XXX} \\\hdashline
+    Early errors before actual execution & \inred{X,XXX} \\\hdashline
     Inessential built-in objects & \inred{X,XXX} \\\midrule
@@
   \end{tabular}
-  \vspace*{-2em}
+  \vspace*{-1em}
 \end{table}
 
-For \inred{XX,XXX} applicable tests, the extracted semantics fails \inred{XXX}
-tests.  We reason about the failed tests, and we discover that they failed
-because ES10 actually has specification errors. We found eight specification
-errors in ES10 (es10-1 to es10-9 in Table~\ref{table:spec-errors}).  Among them,
-five errors are already fixed in the draft version of ECMAScript but three errors
-are newly revealed.  We reported four new errors, and TC39 confirmed and
-merged them into the current draft.
+To evaluate the correctness of \( \tool \), we checked whether the
+extracted semantics from the latest ECMAScript (ES10) passes Test262
+as of February 28, 2019, when ES10 was branched out.
+To focus on the core language semantics of JavaScript, we completed
+only necessary parts missing from the extracted AST-IR translator.
+As Figure~\ref{fig:all-version}(a) shows, for the abstract algorithms
+in ES10, \inred{8,901} steps out of \inred{9,674} steps are
+automatically compiled by \textsf{Algorithm Compiler}.
+Among the remaining \inred{773} steps, we manually implemented all
+missing steps for the core language semantics (\inred{221} steps) and
+the essential parts of the built-in libraries (\inred{XX} steps out of
+\inred{552}).  We also manually implemented \textsf{Global Setting}
+as described in Section~\ref{sec:compiler-impl} for the core language features.
+Note that we do not support minor language features such as the
+non-strict mode, modules, early errors before actual execution, and
+inessential built-in objects.
+Among \inred{XX,XXX} tests in Test262, we filtered out \inred{XX,XXX}
+tests as summarized in Table~\ref{table:test262}.  To focus on ES10,
+we excluded \inred{X,XXX} tests for annexes, internationalization, and
+in-progress features.  We also filted out \inred{X,XXX} tests that use
+minor language features.
+Finally, for \inred{XX,XXX} applicable tests, the extracted semantics
+failed for \inred{XXX} tests.
 
-es10-1 is related to the dangling \code{else} problem introduced in ALGOL
-60~\cite{dangling-else}. While ES10 describes the rule that the \code{else}
-should be associated with the nearest \code{if}, the rule is not explicitly
-represented in the ES10 grammar rule.  It causes one test failed and it is a not
-yet discovered error.  Thus, we revised the grammar rule to satisfy this rule
-and TC39 accepted it in \inred{May X, 2020}.
+We investigated the failed tests and found out that they failed due to
+specification errors in ES10.  Using the failed tests, we
+discovered nine errors: ES10-1 to ES10-9 in
+Table~\ref{table:spec-errors}.  Among them, five errors (ES10-5 to
+ES10-9) were previously reported and fixed in the current draft of the
+next ECMAScript, and the remaining four errors (ES10-1 to ES10-4) were
+never reported before.  All four errors were confirmed by TC39, and
+will be fixed in the next ECMAScript, ES11.
 
-es10-2 is related to the JavaScript Await.  The {\bf PromiseResolve (C, x)}
-algorithm creates a new Promise object using a given constructor {\bf C} and
-resolved with a given value {\bf x}.  However, a specification update added
-three invocations of {\bf PromiseResolve} with a list of values for {\bf x} in
-February 27, 2019.  This error exists in 45 days until April 13, 2019 and causes
-\inred{XX} tests failed.
+The specification error ES10-1 is due to a wrong assertion.
+While ES9 introduced the \code{for await} iteration statement with a
+new {\it iterationKind} tag, \code{async-iterate}, the
+\code{ForIn/OfHeadEvaluation} algorithm missed the
+\code{async-iterate} case in an assertion, which caused 1,120
+tests failed.  We reported the error and proposed a specification fix
+to include  the \code{async-iterate} case, and TC39 accepted it on
+March 25, 2020.  Because the error was created on February 16, 2018,
+it existed for 768 days.
 
-es10-3 arises because of the wrong assertion. ES9 introduced \code{for await}
-iteration statements thus it also introduced a new {\it iterationKind} tag,
-\code{async-iterate}. However, \code{ForIn/OfHeadEvaluation} algorithm misses
-the case of \code{async-iterate} in the assertion. It causes 1120 tests failed
-and it is an unknown error. Thus, we revised the assertion to cover the
-\code{async-iterate} case and TC39 accepted it in March 25, 2020.
+ES10-2 comes from the well-known dangling \code{else} problem
+introduced in ALGOL 60~\cite{dangling-else}.  ES10 describes how to
+parse it in prose: the \code{else} statement should be associated with
+the nearest \code{if} statement.  Because it is written in prose
+rather than in the ES10 grammar productions, it caused one test
+failed.  We proposed a fix to revise the ambiguous grammar production,
+and TC39 confirmed it on April 23, 2020.
 
-es10-4 and es10-5 arise because contributors misunderstood the meaning of
-operations used in abstract algorithms. Especially, es10-5 is related to
-\code{=} operator for numbers and not yet discovered. In abstract algorithms,
-``{\it x} = {\it y}'' denotes equality expression for double-precision 64-bit
-binary format IEEE 754-2008 values thus ``+0 = -0'' is true. However, the {\bf
-StringGetOwnProperty} algorithms uses ``{\it index} = -0'' to check whether
-index is exactly same with -0 but it is true even if {\it index} is +0.
+ES10-3 is due to a misuse of the \code{=} operator for numbers.
+In abstract algorithms, ``{\it x} = {\it y}'' denotes equality testing
+for double-precision 64-bit binary format IEEE 754-2008 values;
+thus, \mbox{``+0 = -0''} evaluates to true.  However, to check whether
+{\it index} is exactly the same with -0,
+{\bf StringGetOwnProperty} used \mbox{``{\it index} = -0''},
+which is true even when {\it index} is +0.
+It caused \inred{XX} tests failed.  We proposed a fix, which is
+confirmed on April 22, 2020.
 
-es10-6, es10-7, and es10-8 are errors that miss or define twice some parts of
-cases in semantics. For example, es10-8 is an error that define the {\bf
-VarScopedDeclarations} for \code{for await} iterations. If the choice is wrong,
-\inred{XX} tests will be failed.
+ES10-4 and ES10-5 happened because ES10 did not handle
+abrupt completion from function calls.  Our proposed fix to ES10-4 was
+accepted on April 28, 2020, and ES10-5 was resolved on May 2, 2019
+after existing for 1,065 days.
 
-After resolving above specification errors in ES10, we extracted formal
-semantics from the revised specification again. The revised formal semantics of
-ES10 passed all \inred{XX,XXX} applicable tests in Test262.  \( \tool \) is
-helpful to correctly extract semantics from ECMAScript but also to detect bugs
-by directly check ECMAScript with Test262. Without our tool, above eight errors
-existed in ECMAScript in \inred{XXX} days on average. Besides, three errors
-es10-1, es10-3, and es10-5 are even not known before we reported to TC39. We
-believe that \( \tool \) bridges gaps between ECMAScript and Test262.
+ES10-6 is due to incorrect uses of an abstract algorithm.
+While {\bf PromiseResolve(C, x)} expects a JavaScript object for its
+second argument, ES10 passed a list of values rather than an object in
+three invocations of {\bf PromiseResolve}.  The wrong invocations were
+introduced on February 27, 2019 and caused \inred{XX} tests failed.
+They were fixed on April 13, 2019 after existing 45 days.
+
+ES10-7 and ES10-8 happened because ES10 missed semantics for some
+cases.  They both existed for more than 1,200 days.
+
+ES10-9 is due to multiple semantics.  Because only one semantics is
+intended, \inred{XX} tests fail when a wrong semantics is chosen.
+
+After resolving the nine specification errors in ES10, we extracted a
+semantics from the revised specification.  The extracted semantics
+from the revised ES10 passed all \inred{XX,XXX} applicable tests in Test262,
+which shows that \( \tool \) extracts an IR-based formal semantics
+from ECMAScript correctly.  In addition, the evaluation witnesses that
+\( \tool \) can detect specification errors effectively.
+We could detect not only five previously-known errors
+but also four new errors.  We believe that \( \tool \) bridges gaps
+between ECMAScript written in a natural language and executable tests
+in Test262.
 
@@
 Based on the failed tests, we found three undiscovered specification errors
-(bigint-1, bigint-2, and bigint-3), and one reported error (bigint-4) in the
+(BigInt-1, BigInt-2, and BigInt-3), and one reported error (BigInt-4) in the
 BigInt proposal as described in Table~\ref{table:spec-errors}.  All of
@@
 algorithms for BigInt but also modified all existing algorithms related to
-number values.  The error bigint-1 is just a simple misuse of the variable
-\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}. bigint-2 and
-bigint-3 break the backward compatibility because of the incorrectly mixed uses
+number values.  The error BigInt-1 is just a simple misuse of the variable
+\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}. BigInt-2 and
+BigInt-3 break the backward compatibility because of the incorrectly mixed uses
 of {\bf ToInt32} and {\bf ToUint32} algorithms in unsigned right shift operators
-and bitwise operators, respectively. The last one bigint-4 arises because the
+and bitwise operators, respectively. The last one BigInt-4 arises because the
 Number constructor does not consider BigInt primitives.  On average, ECMAScript

### 2020-04-30 ase20/eval.tex
Till Sec. 5.3

@@
     Expression &
-    \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
-    \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.} &
+    \makecell[l]{Using the wrong variable \code{oldvalue} instead of
+    \code{oldValue} in \\ {\bf Evaluation} of {\it UpdateExpression}} &
     \textsf{X} &
@@
     Number &
-    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
-    Number::unsignedRightShift}.} &
+    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} in \\ {\bf
+    Number::unsignedRightShift}} &
     \textsf{X} &
@@
     \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} in {\bf
-    NumberBitwiseOp}.} &
+    NumberBitwiseOp}} &
     \textsf{X} &
@@
     Number &
-    \makecell[l]{Not handling BigInt values in {\bf Number} constructor.} &
+    \makecell[l]{Unhandling BigInt values in the {\bf Number} constructor} &
     \textsf{O} &
@@
 
-\subsection{Forward Compatibility}
-
-We show the forward compatibility of \( \tool \) by applying it to the proposals
-that are ready for inclusion in the next ECMAScript (ES11, 2020). Because
-ECMAScript administered as an open-source project, various proposals for new
-language features are available with their own specification changes and tests.
-A separate repository~\cite{proposals} maintains such proposals with six
-different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each proposal
-starts with Stage 0, and the TC39 committee regularly examines Stage 3 proposals
-to decide their next stages.  If a proposal is confirmed, the committee changes
-its stage to Finished and integrates it into the next version of ECMAScript.
-Otherwise, the committee changes its stage to Inactive.  Among them, we applied
-\( \tool \) to all Finished proposals decided to be included in ES11.
-
 \begin{table}[t]
   \centering
-  \caption{Evaluation result of \( \tool \) for Finished stage proposals that
-  will be included in ES11.}
+  \caption{Proposals that will be included in ES11}
   \label{table:spec-prop-result}
@@
   \small
-  \begin{tabular}{c?r|r?r?r?r}
-    \hline
-    \multicolumn{1}{c?}{\multirow{2}{*}{\bf Name}} &
-    \multicolumn{2}{c?}{\bf \( \Delta \) \# Prod.} &
-    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Steps}} &
-    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Tests}} &
-    \multicolumn{1}{c}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}
+  \begin{tabular}{@{}c@{}?r|@{~}r@{~}|@{}c@{}|@{}c@{}|c@{}}
+    \multicolumn{1}{@{}c@{}?}{\multirow{2}{*}{\bf Proposal}} &
+    \multicolumn{2}{@{~}c@{~}|}{\bf \( \Delta \) \# Prod.} &
+    \multicolumn{1}{@{~}c@{~}|}{\multirow{2}{*}{\bf \( \Delta \)\! \#\! Steps}} &
+    \multicolumn{1}{@{~}c@{~}|}{\multirow{2}{*}{\bf \( \Delta \)\! \#\! Tests}} &
+    \multicolumn{1}{c@{}}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}
 
     &
-    \multicolumn{1}{c|}{\bf Lex.} &
-    \multicolumn{1}{c?}{\bf Syn.} &
-    &\\\hline\hline
+    \multicolumn{1}{@{~}c@{~}|}{\bf Lex.} &
+    \multicolumn{1}{@{~}c@{~}|}{\bf Syn.} &
+    &\\\toprule
 
-    \code{matchAll} of \code{String} &
+\footnotesize
+    \scode{matchAll} of \scode{String} &
     0 &
@@
 
-    \code{import()} &
+    \scode{import()} &
     0 &
@@
 
-    \code{BigInt} &
+    \scode{BigInt} &
     4 &
@@
 
-    \code{Promise.allSettled} &
+    \scode{Promise.allSettled } &
     0 &
@@
 
-    \code{globalThis} &
+    \scode{globalThis} &
     0 &
@@
 
-    \code{for-in} mechanics &
+\footnotesize
+    \scode{for-in}  mechanics &
     0 &
@@
 
-    Optional Chaining &
+\footnotesize    Optional Chaining &
     3 &
@@
 
-    Nullish Coalescing Op. &
+\footnotesize   Nullish Coalescing Op. &
     1 &
@@
 
-    \code{import.meta} &
+    \scode{import.meta} &
     0 &
@@
     11 &
-    502/577\\\cline{1-4}
+    502/577 &
   \end{tabular}
@@
 
-Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to 9
-Finished proposals for ES11.  For all proposals, \inred{XX} lexical and
-\inred{XX} syntactic productions are modified and \( \tool \) successfully
-updated the changes to the synthesized JavaScript parser.  The updated parser
-parses all applicable tests for all proposals.  For abstract algorithms,
-\inred{XXX} steps out of \inred{XXX} steps are automatically converted to the
-corresponding \( \ires \) instructions by the algorithm compiler without
-changing of the compile rules.  Thus, our tool has \inred{XX.XX\%} success rate
-on average for future proposals.  Similar with
-Section~\ref{sec:check-with-tests}, we manually implemented missing part of the
-AST-IR translator for each Finished proposal and checked each extracted
-semantics with official tests.  Each of them passed all applicable tests except
-the semantics for \code{BigInt} proposal.  It fails \inred{XX} tests out of 207
-applicable tests for the proposal and \inred{XXXX} tests out of \inred{XXXXX}
-applicable tests for ES10.
+\subsection{Forward Compatibility}
+We evaluated whether \( \tool \) is forward compatible by applying it
+to the proposals that are ready for inclusion in ES11.  Because
+ECMAScript is an open-source project, various proposals for new
+language features are available with their own specification changes and tests.
+A separate repository~\cite{proposals} maintains such proposals with six
+stages: Stage 0 to Stage 3, Finished, and Inactive.  A proposal
+starts with Stage 0, and the TC39 committee examines proposals in Stage 3.
+If a proposal is confirmed, the committee changes
+its stage to Finished and integrates it into the next ECMAScript.
+Otherwise, the committee changes its stage to Inactive.
+Thus, we applied \( \tool \) to all nine proposals in the Finished stage.
 
-Based on the failed tests, we found three undiscovered specification errors
-(BigInt-1, BigInt-2, and BigInt-3), and one reported error (BigInt-4) in the
-BigInt proposal as described in Table~\ref{table:spec-errors}.  All of
-them were confirmed by TC39 and will be fixed in the next release.  The BigInt
-proposal added a new type of primitives BigInt and unified the type with
-original Number type to Numeric types.  Thus, it not only added new
-algorithms for BigInt but also modified all existing algorithms related to
-number values.  The error BigInt-1 is just a simple misuse of the variable
-\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}. BigInt-2 and
-BigInt-3 break the backward compatibility because of the incorrectly mixed uses
-of {\bf ToInt32} and {\bf ToUint32} algorithms in unsigned right shift operators
-and bitwise operators, respectively. The last one BigInt-4 arises because the
-Number constructor does not consider BigInt primitives.  On average, ECMAScript
-included these four specification errors in \inred{XXX} days.
+Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to the
+Finished proposals.  Collectively, the proposals modified \inred{XX} lexical and
+\inred{XX} syntactic productions, and \( \tool \) successfully
+synthesized parsers for them.  The newly synthesized parsers parse all
+applicable tests for all proposals.  For abstract algorithms,
+\inred{XXX} steps out of \inred{XXX} are automatically converted to
+corresponding \( \ires \) instructions by \textsf{Algorithm Compiler}
+without changing {\sf Compile Rules}.  Thus, \( \tool \) has the
+success rate of \inred{XX.XX\%} on average for forthcoming proposals.
 
-After fixing all specification errors, we extracted the semantics for the BigInt
-proposal again.  The updated semantics passed all 207 applicable tests for the
-proposal and \inred{XXXXX} applicable tests for ES10.  Thus, \( \tool \) also
-correctly extract IR-based semantics from future proposals.
+We checked the extracted semantics from the proposals
+by implemented missing parts of the AST-IR translator for
+each proposal and checking the semantics with Test262.  All of them
+passed all applicable tests except the semantics from the
+\code{BigInt} proposal.  It failed for \inred{XX} tests out of 207
+applicable tests for the proposal and \inred{XXXX} tests out of
+\inred{XXXXX} applicable tests for ES10.
+
+Using the failed tests, we discovered four specification errors in the
+BigInt proposal: three new errors (BigInt-1 to BigInt-3) and one known
+error (BigInt-4) as summarized in Table~\ref{table:spec-errors}.
+All of them were confirmed by TC39 and will be fixed in the next ECMAScript.
+The proposal added two new types: BigInt as a new type of primitives
+and Numeric as a unified type of the original Number type and the new BigInt type.
+Therefore, it not only added new algorithms for BigInt but also modified
+all existing algorithms for number values.
+The error BigInt-1 is due to a simple misuse of the variable 
+\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
+BigInt-2 and BigInt-3 break the backward compatibility because of
+the incorrectly mixed uses of {\bf ToInt32} and {\bf ToUint32}
+in unsigned right shift operators and bitwise operators, respectively.
+Finally, BigInt-4 happened because the proposal did not consider
+BigInt primitives in the Number constructor.  On average, four
+specification errors existed for \inred{XXX} days in the proposal.
+
+After fixing the errors in the proposal, we extracted a semantics from
+the revised specification.  The extracted semantics passed all 207
+applicable tests for the proposal and \inred{XXXXX} applicable tests
+for ES10.  Thus, \( \tool \) also correctly extracts an IR-based
+semantics from future proposals, which implies that it is forward compatible.

### 2020-04-30 ase20/eval.tex
Revised 5.3

@@
   \label{table:spec-prop-result}
-  \vspace*{-0.5em}
+  \vspace*{-1em}
   \small
@@
 We evaluated whether \( \tool \) is forward compatible by applying it
-to the proposals that are ready for inclusion in ES11.  Because
+to the proposals ready for inclusion in ES11.  Because
 ECMAScript is an open-source project, various proposals for new
-language features are available with their own specification changes and tests.
-A separate repository~\cite{proposals} maintains such proposals with six
+features are available with their own specification changes and tests.
+A separate repository~\cite{proposals} maintains them in six
 stages: Stage 0 to Stage 3, Finished, and Inactive.  A proposal
@@
 its stage to Finished and integrates it into the next ECMAScript.
-Otherwise, the committee changes its stage to Inactive.
-Thus, we applied \( \tool \) to all nine proposals in the Finished stage.
+Otherwise, its stage becomes Inactive.
 
-Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to the
-Finished proposals.  Collectively, the proposals modified \inred{XX} lexical and
+We applied \( \tool \) to all nine Finished proposals as shown in
+Table~\ref{table:spec-prop-result}.
+Collectively, the proposals modified \inred{XX} lexical and
 \inred{XX} syntactic productions, and \( \tool \) successfully
-synthesized parsers for them.  The newly synthesized parsers parse all
+synthesized parsers for them.  The synthesized parsers parse all
 applicable tests for all proposals.  For abstract algorithms,
@@
 
-Using the failed tests, we discovered four specification errors in the
+Using the failed tests, we discovered four errors in the
 BigInt proposal: three new errors (BigInt-1 to BigInt-3) and one known
 error (BigInt-4) as summarized in Table~\ref{table:spec-errors}.
-All of them were confirmed by TC39 and will be fixed in the next ECMAScript.
+All of them were confirmed by TC39 and will be fixed in ES11.
 The proposal added two new types: BigInt as a new type of primitives
@@
 all existing algorithms for number values.
-The error BigInt-1 is due to a simple misuse of the variable 
+The error BigInt-1 is due to a misuse of the variable 
 \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
 BigInt-2 and BigInt-3 break the backward compatibility because of
-the incorrectly mixed uses of {\bf ToInt32} and {\bf ToUint32}
+misusing {\bf ToInt32} and {\bf ToUint32}
 in unsigned right shift operators and bitwise operators, respectively.
-Finally, BigInt-4 happened because the proposal did not consider
-BigInt primitives in the Number constructor.  On average, four
-specification errors existed for \inred{XXX} days in the proposal.
+BigInt-4 is due to missing BigInt primitives in the Number constructor.
+On average, four errors existed for \inred{XXX} days in the proposal.
 

### 2020-04-30 ase20/conclusion.tex
Till Sec. 7

@@
 \section{Conclusion}\label{sec:conclude}
-
-The annual updates of the ECMAScript makes it difficult to build program
+Annual updates of ECMAScript make it difficult to build program
 analysis or formal verification of JavaScript due to the required human efforts
-in modeling a moving target.  In this paper, we proposed a tool \( \tool \),
-which \textit{automatically} extracts the syntax and semantics specified in
-ECMAScript.  The tool generates a parser from a language grammar written in \(
-\bnfes \), and an AST-IR translator from abstract algorithms written in
-English.  The tool automatically extract all syntax and \inred{XX.XX\%} of
-semantics for the most recent four versions of ECMAScript (ES7 to ES10).  We
-evaluated the correctness of the tool by testing the extracted semantics from
-ES10 with Test262, the official conformance suite.  Based on \inred{X,XXX}
-failed tests, we found eight specification errors in ES10. After resolving
-them, the extracted semantics passed all \inred{XX,XXX} applicable tests.
-Moreover, we showed that \( \tool \) is also forward compatible for the future
-language features by applying it to nine proposals, and we found four
-specification errors in the proposal for BigInt.  We believe that it could
-dramatically reduce the human efforts to define formal semantics of ECMAScript
-and also bridge gaps between ECMAScript and Test262.
+in modeling a moving target.  In this paper, we proposed \( \tool \), a tool
+that \textit{automatically} extracts the syntax and semantics as a parser and
+an AST-IR translator from ECMAScript written in English.
+The tool automatically extracts all the syntax and \inred{XX.XX\%} of the
+semantics for the most recent four versions of ECMAScript (ES7 to ES10).
+We evaluated the correctness of the tool by testing the extracted
+semantics from ES10 with Test262, the official conformance suite.
+Using \inred{X,XXX} failed tests, we found nine specification errors,
+four of which are newly discovered, confirmed by TC39, and planned to
+be integrated in ES11.  After fixing the errors, the extracted
+semantics passed all \inred{XX,XXX} applicable tests in Test262.
+We also showed that \( \tool \) is forward compatible by applying it to nine
+proposals to be included in ES11, which let us find four errors in the
+BigInt proposal.  We believe that \( \tool \) can dramatically reduce
+human efforts in building various JavaScript tools correctly.

### 2020-04-30 ase20/related.tex
Till Sec. 7

@@
 is basically recursive-descent with backtracking that can support general
-context-free grammars (CFGs) even in the presence of ambiguous grammars,
+context-free grammars even in the presence of ambiguous grammars,
 its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
 does not support context-sensitive features.  Unlike GLL parsing, our lookahead
-parsing is applicable for JavaScript parsers having context sensitive features
-such as positive/negative lookaheads. Moreover, The complexity of lookahead
-parsing is \( O(k \cdot n) \) for the input size \( n \) and the constant
+parsing is applicable for JavaScript parsers with context sensitive features
+such as positive/negative lookaheads. Moreover, the complexity of lookahead
+parsing is \( O(k \cdot n) \) for the constant
 number of tokens \( k \). We experimentally showed that it can generate parsers
@@
 
-In the field of automatic model generation, the closest related work to
-ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
-for API functions.  Using NLP techniques and various heuristic methods,
-it produces several candidate code tests them with actual implementation
-of the API functions to find correct modeling.  Unlike their approach, we
-introduce semi-automatic synthesis based on general compile rules that
-represent the common writing patterns to support future language updates and to
-provide correct meaning of specification.  The extracted semantics via our tool
-is also executable that helps to bridge gaps between the specification written
-in a natural language and tests.
+The closest work to ours in automatic model generation
+is \citet{javadoc}'s, which generates Java code from Javadoc comments
+for API functions.  Using NLP techniques and heuristic methods,
+it produces candidate code and removes wrong ones
+by testing them with actual implementation. Unlike their approach, we
+introduce a semi-automatic synthesis using general compile rules that
+represent common writing patterns of specifications.  The extracted
+semantics by \(\tool\) is also executable, which allows to bridge gaps
+between the specification written in a natural language and executable
+tests.
 
-Several approaches have defined the formal semantics of JavaScript.
-\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
-rest as desugaring.  While it presents the core JavaScript semantics in
-an extension of the $\lambda$ calculus, it does not show the semantics
-correspondence defined in ECMAScript.  KJS~\cite{kjs} and
-JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
-ECMAScript to their own formal languages.  KJS mapped
-ES5.1 in the K framework~\cite{kframework}, which can be used
-for program verification and analysis.  Similarly, JaVerT converts the
-specification to their own IR called JSIL to make further analysis.
-However, all of them targets only ES5.1 or former versions of ECMAScript and
-they do not provide solution for annual updates of ECMAScript. Our approach
+Several approaches defined the formal semantics of JavaScript.
+\citet{lambdajs} defined a core calculus of JavaScript expressing non-core
+features using desugaring, but its correspondence with ECMAScript is
+not obvious.
+KJS~\cite{kjs} and JaVerT~\cite{javert} defined the JavaScript semantics
+by manually converting ECMAScript to their own formal languages.  KJS mapped
+ES5.1 in the K framework~\cite{kframework} and JaVerT converts the
+specification to their own IR.  However, they all target only ES5.1 or former and
+they do not provide any solution for annual updates of ECMAScript. Our approach
 provides a mechanized framework to synthesize JavaScript parsers and to

### 2020-05-01 ase20/eval.tex
[ASE] revised typo for Number values
[ASE] Updated numbers in 5.1

@@
       \text{\# Lexical productions}
-      & \inred{\text{78}}
-      & \inred{\text{78}}
-      & \inred{\text{78}}
-      & \inred{\text{81}}
-      & \inred{\text{78.75}}\\\hline
+      & \text{78}
+      & \text{78}
+      & \text{78}
+      & \text{81}
+      & \text{78.75}\\\hline
       \text{\# Syntactic productions}
-      & \inred{\text{157}}
-      & \inred{\text{167}}
-      & \inred{\text{167}}
-      & \inred{\text{174}}
-      & \inred{\text{166.25}}\\
+      & \text{157}
+      & \text{167}
+      & \text{167}
+      & \text{174}
+      & \text{166.25}\\
     \end{array}
@@
       \Delta \; \text{\# Lexical productions}
-      & \inred{\text{3}}
-      & \inred{\text{5}}
-      & \inred{\text{6}}
-      & \inred{\text{4.67}}\\\hline
+      & \text{3}
+      & \text{5}
+      & \text{6}
+      & \text{4.67}\\\hline
       \Delta \; \text{\# Syntactic productions}
-      & \inred{\text{140}}
-      & \inred{\text{15}}
-      & \inred{\text{8}}
-      & \inred{\text{54.33}}\\
+      & \text{140}
+      & \text{15}
+      & \text{8}
+      & \text{54.33}\\
     \end{array}
@@
 lexical and syntactic productions.  As Table~\ref{fig:syntax-all-version} shows,
-the average numbers of lexical and syntactic productions are \inred{78.75} and
-\inred{166.25}, respectively.  Also, the average numbers of annually updated
-lexical and syntactic productions between adjacent versions are \inred{4.67} and
-\inred{54.33}, respectively.
+the average numbers of lexical and syntactic productions are 78.75 and
+166.25, respectively.  Also, the average numbers of annually updated
+lexical and syntactic productions between adjacent versions are 4.67 and
+54.33, respectively.
 
@@
 compiled algorithm steps to corresponding \( \ires \) instructions with
-the success rate of \inred{91.38\%} on average for each ECMAScript version
-from ES7 to ES10, and \inred{92.08\%} for each update between adjacent
+the success rate of 95.03\% on average for each ECMAScript version
+from ES7 to ES10, and 94.31\% for each update between adjacent
 versions.  ECMAScript abstract algorithms describe not only
@@
 Therefore, built-in libraries have lower success rates
-(\inred{86.74\%} for specifications and \inred{88.24\%} for updates) than core
-language semantics (\inred{95.14\%} for specifications and \inred{96.41\%} for
+(92.55\% for specifications and 91.50\% for updates) than core
+language semantics (97.06\% for specifications and 97.14\% for
 updates).
@@
 Therefore, it not only added new algorithms for BigInt but also modified
-all existing algorithms for number values.
+all existing algorithms for Number values.
 The error BigInt-1 is due to a misuse of the variable 

### 2020-05-01 ase20/eval.tex
[ASE] Updated Table 4 except passed / failed tests

@@
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \inred{\textbf{XX,XXX}}\\
+    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{35,990}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Annexes & \inred{XXX}\\\hdashline
-    Internationalization & \inred{XXX}\\\hdashline
-    In-progress features & \inred{X,XXX}\\\midrule
+    Annexes & 1,060\\\hdashline
+    Internationalization & 640\\\hdashline
+    In-progress features & 5,338\\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{ES10 Tests} & \inred{\textbf{XX,XXX}}\\
+    \rowcolor{gainsboro} \textbf{ES10 Tests} & \textbf{28,952}\\
     \aboverulesepcolor{gainsboro}\midrule
-    Non-strict mode & \inred{X,XXX}\\\hdashline
-    Modules & \inred{X,XXX} \\\hdashline
-    Early errors before actual execution & \inred{X,XXX} \\\hdashline
-    Inessential built-in objects & \inred{X,XXX} \\\midrule
+    Non-strict mode & 1,150\\\hdashline
+    Modules & 918 \\\hdashline
+    Early errors before actual execution & 2,288 \\\hdashline
+    Inessential built-in objects & 6,532 \\\midrule
     \belowrulesepcolor{gainsboro}
-    \rowcolor{gainsboro} \textbf{Applicable Tests} & \inred{\textbf{XX,XXX}}\\
+    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{18,064}\\
     \aboverulesepcolor{gainsboro}\midrule

### 2020-05-01 ase20/abstract.tex
Revised abstract

--- 2020-04-01 ase20/abstract.tex
@@
 into \( \ires \), an Intermediate Representation that we designed for
-ECMAScript.  For the five most recent ECMAScript versions, \( \tool \) automatically
-synthesized parsers for all versions, and compiled \inred{XX.XX}\% of the
+ECMAScript.  For the four most recent ECMAScript versions, \( \tool \) automatically
+synthesized parsers for all versions, and compiled 95.03\% of the
 algorithm steps on average.  After we complete the missing parts manually,
-the extracted core semantics of the latest ECMAScript version (ES10, 2019)
-passed all \inred{XX,XXX} applicable tests.
-Using this \textit{first formal semantics of modern JavaScript}, we found
-\inred{X} specification errors in ES10, which were all confirmed by
-the Ecma Technical Committee 39.  Furthermore, we also successfully
-applied \( \tool \) to the current draft of the next ECMAScript (ES11, 2020),
-which shows the forward compatibility of \( \tool \).
+the extracted core semantics of the latest ECMAScript (ES10, 2019) passed all
+18,064 applicable tests.  Using this \textit{first formal semantics of modern
+JavaScript}, we found nine specification errors in ES10, which were all
+confirmed by the Ecma Technical Committee 39.  Furthermore, we showed that \(
+\tool \) is \textit{forward compatible} by applying it to nine feature
+proposals ready for inclusion in the next ECMAScript, which let us find four
+errors in the BigInt proposal.
 \end{abstract}

### 2020-05-01 ase20/intro.tex
Updated numbers in Intro

@@
     automatically generated parsers for all versions, and automatically compiled
-    \inred{XX.X}\% of the steps in abstract algorithms on average.
+    95.03\% of the steps in abstract algorithms on average.
   \item \textbf{\( \tool \) bridges gaps between the specification written in a
@@
     TC39 and will be fixed in the next release.  After fixing them, the formal
-    semantics passed all \inred{XX,XXX} applicable tests.
+    semantics passed all 18,064 applicable tests.
   \item \textbf{\( \tool \) is also \textit{forward compatible} with new
@@
     We evaluated the forward compatibility of \( \tool \) by applying it to all
-    \inred{X} proposals that are ready for inclusion in the next ECMAScript
+    nine proposals that are ready for inclusion in the next ECMAScript
     (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
     out of \inred{XXX} algorithm steps for all the proposals.  After completion
-    of the missing parts, we found \inred{X} specifications errors by executing
-    the corresponding tests in Test262.  After fixing them, the extracted
-    semantics passed all \inred{XXX} tests.
+    of the missing parts, we found four specifications errors in BigInt
+    proposal by executing the corresponding tests in Test262.  After fixing
+    them, the extracted semantics passed all \inred{XXX} tests.
 \end{itemize}

### 2020-05-01 ase20/eval.tex
Updated numbers in 5.2 / Table 5

@@
 As Figure~\ref{fig:all-version}(a) shows, for the abstract algorithms
-in ES10, \inred{8,901} steps out of \inred{9,674} steps are
+in ES10, 9,627 steps out of 10,101 steps are
 automatically compiled by \textsf{Algorithm Compiler}.
-Among the remaining \inred{773} steps, we manually implemented all
-missing steps for the core language semantics (\inred{221} steps) and
+Among the remaining 474 steps, we manually implemented all
+missing steps for the core language semantics (137 steps) and
 the essential parts of the built-in libraries (\inred{XX} steps out of
-\inred{552}).  We also manually implemented \textsf{Global Setting}
+337).  We also manually implemented \textsf{Global Setting}
 as described in Section~\ref{sec:compiler-impl} for the core language features.
@@
 inessential built-in objects.
-Among \inred{XX,XXX} tests in Test262, we filtered out \inred{XX,XXX}
+Among 35,990 tests in Test262, we filtered out 17,926
 tests as summarized in Table~\ref{table:test262}.  To focus on ES10,
-we excluded \inred{X,XXX} tests for annexes, internationalization, and
-in-progress features.  We also filted out \inred{X,XXX} tests that use
+we excluded 7,038 tests for annexes, internationalization, and
+in-progress features.  We also filted out 10,888 tests that use
 minor language features.
-Finally, for \inred{XX,XXX} applicable tests, the extracted semantics
+Finally, for 18,064 applicable tests, the extracted semantics
 failed for \inred{XXX} tests.
@@
 semantics from the revised specification.  The extracted semantics
-from the revised ES10 passed all \inred{XX,XXX} applicable tests in Test262,
+from the revised ES10 passed all 18,064 applicable tests in Test262,
 which shows that \( \tool \) extracts an IR-based formal semantics
@@
     5/5 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 
@@
     0/0 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 
@@
     \inred{207}/207 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 
@@
     50/50 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 
@@
     1/1 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 
@@
     19/19 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 
@@
     21/21 &
-    \inred{XXXXX}/\inred{XXXXX}\\\hline
+    \inred{XXXXX}/18,064\\\hline
 

### 2020-05-01 lib/spec_extractor/es2019.js
Handling es10-6 to es10-9 in JISET

@@ -141,10 +141,6 @@ SpecExtractor.loadSpec(() => {
         data.steps[8] = {
             tokens: ['ReturnCont', {'id': 'genContext'}, '.', '[', '[', 'ReturnCont', ']', ']', 'to', '!', 'AsyncGeneratorResolve', '(', {'id': 'generator'}, ',', {'id': 'value'}, ',', {'value': 'false'}, ')', '.']
         };
-      } else if (name == 'AsyncGeneratorResumeNext') {
-        data.steps[9].tokens[8].steps[1].tokens[6].steps[0].tokens[12].steps[1] = { //specError#1
-            tokens: ['Let', {id: 'promise'}, 'be', '?', 'PromiseResolve', '(', '%', 'Promise', '%', ',', {id: 'completion'}, '.', '[', '[', 'Value', ']', ']', ')', '.']
-        };
       } else if (name == 'GeneratorStart') {
         data.steps[3].tokens[24].steps[7].tokens[2].steps[1].tokens[0] = 'ReturnCont';
         data.steps[3].tokens[24].steps[8].tokens[0] = 'ReturnCont';
@@ -153,19 +149,10 @@ SpecExtractor.loadSpec(() => {
         data.steps[4].tokens[24].steps[6].tokens[0] = 'ReturnCont';
       } else if (name == 'AsyncFunctionStart') {
         data.steps[2].tokens[24].steps[6].tokens[0] = 'ReturnCont';
-      } else if (name == 'AsyncFromSyncIteratorContinuation') {
-          data.steps[4] = { // specError#1
-              tokens: ['Let', {id: 'valueWrapper'}, 'be', '?', 'PromiseResolve', '(', '%', 'Promise', '%', ',', {id: 'value'}, ')', '.']
-          };
       } else if (name == 'MemberExpression1Evaluation0') {
         addMethod('CallExpression3Evaluation0', length, data);
       } else if (name == 'MemberExpression2Evaluation0') {
         addMethod('CallExpression4Evaluation0', length, data);
-      } else if (name == 'FunctionExpression0IsFunctionDefinition1') {
-        let params = data.params;
-        data.params = ['this', 'FormalParameters', 'FunctionBody'];
-        addMethod('FunctionExpression0IsFunctionDefinition0', length, data)
-        data.params = params;
       } else if (name == 'ClassTail0ClassDefinitionEvaluation3') {
         let newSteps = data.steps.slice(0, 12);
         newSteps.push({
[…]

### 2020-05-01 src/main/scala/kr/ac/kaist/jiset/BugPatch.scala

@@ -87,6 +87,38 @@ object BugPatch extends RegexParsers {
       getTokens("ReturnIfAbrupt( id:r ) .")
   }
 
+  // es10-6
+  val wrongArgsInPromiseResolve = true
+  def patchWrongArgsInPromiseResolve(name: String, algo: Algorithm): Unit = name match {
+    case "AsyncGeneratorResumeNext" =>
+      algo.steps(9).tokens(8).asInstanceOf[StepList]
+        .steps(1).tokens(6).asInstanceOf[StepList]
+        .steps(0).tokens(12).asInstanceOf[StepList]
+        .steps(1).tokens = getTokens("Let id:promise be ?PromiseResolve(%Promise%, id:completion .[[Value]]).")
+    case "AsyncFromSyncIteratorContinuation" =>
+      algo.steps(4).tokens =
+        getTokens("Let id:valueWrapper be ?PromiseResolve(%Promise%, id:value ).")
+    case "Await" =>
+      algo.steps(1).tokens =
+        getTokens("Let id:promise be ?PromiseResolve(%Promise%, id:value ).")
+  }
+
+  // es10-7
+  val noIsFunctionDefinition = true
+
+  // es10-8
+  val noExpectedArgumentCount = true
+
+  // es10-9
+  val duplicatedVarScopedDecl = true
+  def patchDuplicatedVarScopedDecl(algo: Algorithm): Unit = {
+    algo.steps = List(
+      Step(getTokens("Let id:declarations be a List containing nt:ForBinding .")),
+      Step(getTokens("Append to id:declarations the elements of the VarScopedDeclarations of nt:Statement .")),
+      Step(getTokens("Return id:declarations ."))
+    )
+  }
+
   private lazy val word = "[a-zA-Z0-9]+".r
   private lazy val symobol = ".".r
   private lazy val any = "\\S+".r
@@ -94,7 +126,8 @@ object BugPatch extends RegexParsers {
   private lazy val id = "id:" ~> any ^^ { Id(_) }
   private lazy val value = "value:" ~> any ^^ { Value(_) }
   private lazy val const = "const:" ~> any ^^ { Const(_) }
-  private lazy val token = text ||| id ||| value ||| const
+  private lazy val nt = "nt:" ~> any ^^ { Nt(_) }
+  private lazy val token = text ||| id ||| value ||| const ||| nt
   private lazy val tokens = rep1(token)
   def getTokens(str: String): List[Token] = parseAll(tokens, str).get
 }

### 2020-05-01 src/main/scala/kr/ac/kaist/jiset/generator/ASTGenerator.scala

@@ -2,6 +2,7 @@ package kr.ac.kaist.jiset.generator
 
 import java.io.PrintWriter
 import kr.ac.kaist.jiset._
+import kr.ac.kaist.jiset.BugPatch._
 import kr.ac.kaist.jiset.spec._
 import kr.ac.kaist.jiset.util.Useful._
 
@@ -78,25 +79,34 @@ object ASTGenerator {
           for (file <- walkTree(s"$RESOURCE_DIR/$VERSION/manual/algorithm")) {
             if (scalaFilter(file.getName)) {
               val methodName = removedExt(file.getName)
-              val pre = s"$name$i"
-              val len = pre.length
-              if (methodName.startsWith(pre) && !methodName.charAt(len).isDigit) {
-                val semName = methodName.substring(len)
-                sems ::= s"""    "$semName" -> $methodName.func"""
+              if (noExpectedArgumentCount || (
+                methodName != "FormalParameterList0ExpectedArgumentCount0" &&
+                methodName != "FormalParameters1ExpectedArgumentCount0"
+              )) {
+                val pre = s"$name$i"
+                val len = pre.length
+                if (methodName.startsWith(pre) && !methodName.charAt(len).isDigit) {
+                  val semName = methodName.substring(len)
+                  sems ::= s"""    "$semName" -> $methodName.func"""
+                }
               }
             }
           }
           for (file <- walkTree(s"$RESOURCE_DIR/$VERSION/auto/algorithm")) {
             if (jsonFilter(file.getName)) {
               val methodName = removedExt(file.getName)
-              val pre = s"$name$i"
-              val len = pre.length
-              if (methodName.startsWith(pre) && !methodName.charAt(len).isDigit) {
-                val semName = methodName.substring(len)
-                sems ::= s"""    "$semName" -> $methodName.func"""
+              if (noIsFunctionDefinition || methodName != "FunctionExpression0IsFunctionDefinition0") {
+                val pre = s"$name$i"
+                val len = pre.length
+                if (methodName.startsWith(pre) && !methodName.charAt(len).isDigit) {
+                  val semName = methodName.substring(len)
+                  sems ::= s"""    "$semName" -> $methodName.func"""
+                }
               }
             }
           }
+          if (noIsFunctionDefinition && s"$name$i" == "FunctionExpression0")
[…]

### 2020-05-01 src/main/scala/kr/ac/kaist/jiset/generator/MethodGenerator.scala

@@ -16,22 +16,27 @@ object MethodGenerator {
       case "StringGetOwnProperty" if numberEqual => patchNumberEqual(algo)
       case "AbstractEqualityComparison" if completionInAbstractEquality => patchCompletionInAbstractEquality(algo)
       case "EqualityExpression2Evaluation0" if completionInEqualityExpr => patchCompletionInEqualityExpr(algo)
+      case "AsyncGeneratorResumeNext" | "AsyncFromSyncIteratorContinuation" | "Await" if wrongArgsInPromiseResolve => patchWrongArgsInPromiseResolve(name, algo)
+      case "IterationStatement12VarScopedDeclarations0" if duplicatedVarScopedDecl => patchDuplicatedVarScopedDecl(algo)
       case _ =>
     }
-    val len = algo.length
-    val (func, _) = AlgoCompiler(name, algo).result
+    generate(name, scalaName, algo)
+    def generate(name: String, scalaName: String, algo: Algorithm): Unit = {
+      val len = algo.length
+      val (func, _) = AlgoCompiler(name, algo).result
 
-    val nf = getPrintWriter(s"$modelDir/algorithm/$scalaName.scala")
-    val TRIPLE = "\"\"\""
-    nf.println(s"""package $packageName.model""")
-    nf.println(s"""""")
-    nf.println(s"""import $packageName.ir._""")
-    nf.println(s"""import $packageName.ir.Parser._""")
-    nf.println(s"""""")
-    nf.println(s"""object $scalaName {""")
-    nf.println(s"""  val length: Int = $len""")
-    nf.println(s"""  val func: Func = parseFunc($TRIPLE${beautify(func, "  ")}$TRIPLE)""")
-    nf.println(s"""}""")
-    nf.close()
+      val nf = getPrintWriter(s"$modelDir/algorithm/$scalaName.scala")
+      val TRIPLE = "\"\"\""
+      nf.println(s"""package $packageName.model""")
+      nf.println(s"""""")
+      nf.println(s"""import $packageName.ir._""")
+      nf.println(s"""import $packageName.ir.Parser._""")
+      nf.println(s"""""")
+      nf.println(s"""object $scalaName {""")
+      nf.println(s"""  val length: Int = $len""")
+      nf.println(s"""  val func: Func = parseFunc($TRIPLE${beautify(func, "  ")}$TRIPLE)""")
+      nf.println(s"""}""")
+      nf.close()
+    }
   }
 }

### 2020-05-01 src/main/scala/kr/ac/kaist/jiset/generator/ModelGenerator.scala

@@ -1,6 +1,7 @@
 package kr.ac.kaist.jiset.generator
 
 import kr.ac.kaist.jiset._
+import kr.ac.kaist.jiset.BugPatch._
 import kr.ac.kaist.jiset.util.Useful._
 import kr.ac.kaist.jiset.spec._
 import java.io.File
@@ -60,7 +61,7 @@ object ModelGenerator {
         nf.println
         nf.print(readFile(name))
         nf.close()
-      }
+      } else deleteFile(s"$modelDir/algorithm/$filename")
     }
 
     val nf = getPrintWriter(s"$modelDir/Model.scala")
@@ -84,8 +85,12 @@ object ModelGenerator {
       case (k, v) =>
         nf.println(s"""    Id("${getScalaName(k)}") -> NamedAddr("$v"),""")
     }
-    nf.println(methods.map(getScalaName _).map(x =>
-      s"""    Id("$x") -> $x.func""").mkString("," + LINE_SEP))
+    nf.println(methods.map(getScalaName _).map {
+      case x @ "FunctionExpression0IsFunctionDefinition1" if noIsFunctionDefinition =>
+        """    Id("FunctionExpression0IsFunctionDefinition0") -> FunctionExpression0IsFunctionDefinition0.func""" + "," + LINE_SEP +
+          s"""    Id("$x") -> $x.func"""
+      case x => s"""    Id("$x") -> $x.func"""
+    }.mkString("," + LINE_SEP))
     nf.println(s"""  ) ++ Map(""")
     nf.println(consts.map(i =>
       s"""      Id("CONST_$i") -> NamedAddr("CONST_$i")""").mkString("," + LINE_SEP))

### 2020-05-02 ase20/eval.tex
[ASE] Updated Table 3
[ASE] Revised Evaluation for es10-9

@@
     \caption{For each ECMAScript version from ES7 to ES10}
-\vspace*{.5em}
     \label{fig:semantics-all-version}
@@
   \label{fig:all-version}
-\vspace*{-1em}
+\vspace*{-1.5em}
 \end{figure}
@@
     768 days &
-    1,120 \\\hline
+    1,116 \\\hline
 
@@
     \multicolumn{1}{c|}{TBD} &
-    \inred{XX} \\\hline
+    7 \\\hline
 
@@
     \textsf{X} &
-\inred{0000-00-00}&
+    2015-06-01&
     2020-04-28 &
- \inred{XX} days &
- \inred{XX}
- \\\hline
+    1,793 days &
+    9 \\\hline
 
@@
     2019-05-02 &
-    1,065 days &
-    1 \\\hline
+    1,431 days &
+    2 \\\hline
 
@@
     45 days &
-    1,100 \\\hline
+    1,294 \\\hline
 
@@
     1,205 days &
-    \inred{XX} \\\hline
+    81 \\\hline
 
@@
     602 days &
-    \inred{XX} \\\hline\hline
+    0 \\\hline\hline
 
@@
 which is true even when {\it index} is +0.
-It caused \inred{XX} tests failed.  We proposed a fix, which is
+It caused seven tests failed.  We proposed a fix, which is
 confirmed on April 22, 2020.
@@
 accepted on April 28, 2020, and ES10-5 was resolved on May 2, 2019
-after existing for 1,065 days.
+after existing for 1,431 days.
 
@@
 three invocations of {\bf PromiseResolve}.  The wrong invocations were
-introduced on February 27, 2019 and caused \inred{XX} tests failed.
+introduced on February 27, 2019 and caused 1,294 tests failed.
 They were fixed on April 13, 2019 after existing 45 days.
@@
 
-ES10-9 is due to multiple semantics.  Because only one semantics is
-intended, \inred{XX} tests fail when a wrong semantics is chosen.
+ES10-9 is due to multiple semantics.  While any tests in Test262 do not fail
+with two different semantics, we could detect this error via {\sf Spec
+Extractor} even before executing semantics. It is a supplementary merit of
+the mechanization of IR-based semantics extraction.
 

### 2020-05-02 ase20/eval.tex
[ASE] Footnotesize in Table 5
Minor edit

@@
 
-ES10-9 is due to multiple semantics.  While any tests in Test262 do not fail
-with two different semantics, we could detect this error via {\sf Spec
-Extractor} even before executing semantics. It is a supplementary merit of
+ES10-9 is due to multiple semantics.  While no tests in Test262 fail
+with any of the semantics, we could detect this error via {\sf Spec
+Extractor} even before executing the semantics. It is supplementary merit of
 the mechanization of IR-based semantics extraction.
@@
 
-\footnotesize
-    \scode{matchAll} of \scode{String} &
+    \code{matchAll} of \code{String} &
     0 &
@@
     5/5 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-    \scode{import()} &
+    \code{import()} &
     0 &
@@
     0/0 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-    \scode{BigInt} &
+    \code{BigInt} &
     4 &
@@
     \inred{207}/207 &
-    \inred{XXXXX}/18,064\\\hline
+    \inred{18,064}/18,064\\\hline
 
-    \scode{Promise.allSettled } &
+    \code{Promise.allSettled } &
     0 &
@@
     50/50 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-    \scode{globalThis} &
+    \code{globalThis} &
     0 &
@@
     1/1 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-\footnotesize
-    \scode{for-in}  mechanics &
+    \code{for-in}  mechanics &
     0 &
@@
     0/0 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-\footnotesize    Optional Chaining &
+    Optional Chaining &
     3 &
@@
     19/19 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-\footnotesize   Nullish Coalescing Op. &
+    Nullish Coalescing Op. &
     1 &
@@
     21/21 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 
-    \scode{import.meta} &
+    \code{import.meta} &
     0 &
@@
     0/0 &
-    \inred{XXXXX}/18,064\\\hline
+    18,064/18,064\\\hline
 

### 2020-05-02 ase20/eval.tex
[ASE] Updated numbers in Evaluation section

@@
     1,541 days &
-    \inred{XX} \\\hline
+    306 \\\hline
 
@@
     \aboverulesepcolor{gainsboro}\midrule
-    Passed tests & \inred{XX,XXX} \\\hdashline
-    Failed tests & \inred{XXX} \\\bottomrule
+    Passed tests & 16,355 \\\hdashline
+    Failed tests & 1,709 \\\bottomrule
   \end{tabular}
@@
 missing steps for the core language semantics (137 steps) and
-the essential parts of the built-in libraries (\inred{XX} steps out of
+the essential parts of the built-in libraries (140 steps out of
 337).  We also manually implemented \textsf{Global Setting}
@@
 Finally, for 18,064 applicable tests, the extracted semantics
-failed for \inred{XXX} tests.
+failed for 1,709 tests.
 
@@
 Table~\ref{table:spec-prop-result}.
-Collectively, the proposals modified \inred{XX} lexical and
-\inred{XX} syntactic productions, and \( \tool \) successfully
+Collectively, the proposals modified eight lexical and
+11 syntactic productions, and \( \tool \) successfully
 synthesized parsers for them.  The synthesized parsers parse all
@@
 BigInt-4 is due to missing BigInt primitives in the Number constructor.
-On average, four errors existed for \inred{XXX} days in the proposal.
+On average, four errors existed for 170 days in the proposal.
 
@@
 the revised specification.  The extracted semantics passed all 207
-applicable tests for the proposal and \inred{XXXXX} applicable tests
+applicable tests for the proposal and 18,064 applicable tests
 for ES10.  Thus, \( \tool \) also correctly extracts an IR-based

### 2020-05-02 ase20/conclusion.tex
[ASE] Removed bigint-3 / Updated Table 5

@@
 We also showed that \( \tool \) is forward compatible by applying it to nine
-proposals to be included in ES11, which let us find four errors in the
+proposals to be included in ES11, which let us find three errors in the
 BigInt proposal.  We believe that \( \tool \) can dramatically reduce

### 2020-05-02 ase20/eval.tex
[ASE] Removed bigint-3 / Updated Table 5

@@
     \caption{For each ECMAScript version from ES7 to ES10}
+    \vspace*{1.5em}
     \label{fig:semantics-all-version}
@@
   \label{fig:all-version}
-\vspace*{-1.5em}
+\vspace*{-0.5em}
 \end{figure}
@@
     BigInt-3 &
-    Number &
-    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} in {\bf
-    NumberBitwiseOp}} &
-    \textsf{X} &
-    2019-09-27 &
-    2020-04-23 &
-    209 days &
-    \inred{XX} \\\hline
-
-    BigInt-4 &
     Number &
@@
     2 &
-    22/23 &
+    38/38 &
     0/0 &
@@
     0 &
-    258/323 &
+    298/326 &
     \inred{207}/207 &
@@
     3 &
-    72/74 &
+    74/74 &
     19/19 &
@@
     11 &
-    502/577 &
+    560/595 &
   \end{tabular}
@@
 applicable tests for all proposals.  For abstract algorithms,
-\inred{XXX} steps out of \inred{XXX} are automatically converted to
+560 steps out of 595 are automatically converted to
 corresponding \( \ires \) instructions by \textsf{Algorithm Compiler}
 without changing {\sf Compile Rules}.  Thus, \( \tool \) has the
-success rate of \inred{XX.XX\%} on average for forthcoming proposals.
+success rate of 94.12\% on average for forthcoming proposals.
 
@@
 
-Using the failed tests, we discovered four errors in the
-BigInt proposal: three new errors (BigInt-1 to BigInt-3) and one known
-error (BigInt-4) as summarized in Table~\ref{table:spec-errors}.
+Using the failed tests, we discovered three errors in the
+BigInt proposal: two new errors (BigInt-1 and BigInt-2) and one known
+error (BigInt-3) as summarized in Table~\ref{table:spec-errors}.
 All of them were confirmed by TC39 and will be fixed in ES11.
@@
 \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
-BigInt-2 and BigInt-3 break the backward compatibility because of
-misusing {\bf ToInt32} and {\bf ToUint32}
-in unsigned right shift operators and bitwise operators, respectively.
-BigInt-4 is due to missing BigInt primitives in the Number constructor.
-On average, four errors existed for 170 days in the proposal.
+BigInt-2 breaks the backward compatibility because of
+misusing {\bf ToInt32} instead of {\bf ToUint32}
+in unsigned right shift operators.
+BigInt-3 is due to missing BigInt primitives in the Number constructor.
+On average, three errors existed for 157 days in the proposal.
 

### 2020-05-03 ase20/conclusion.tex
[ASE] Fill all numbers

@@
 an AST-IR translator from ECMAScript written in English.
-The tool automatically extracts all the syntax and \inred{XX.XX\%} of the
+The tool automatically extracts all the syntax and 95.03\% of the
 semantics for the most recent four versions of ECMAScript (ES7 to ES10).
@@
 semantics from ES10 with Test262, the official conformance suite.
-Using \inred{X,XXX} failed tests, we found nine specification errors,
+Using 1,709 failed tests, we found nine specification errors,
 four of which are newly discovered, confirmed by TC39, and planned to
 be integrated in ES11.  After fixing the errors, the extracted
-semantics passed all \inred{XX,XXX} applicable tests in Test262.
+semantics passed all 18,064 applicable tests in Test262.
 We also showed that \( \tool \) is forward compatible by applying it to nine

### 2020-05-03 ase20/intro.tex
[ASE] Removed bigint-3 / Updated Table 5
[ASE] Fill all numbers

@@
     ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
-    semantics of modern JavaScript}. It failed for \inred{XXXX} tests because of
+    semantics of modern JavaScript}. It failed for 1,709 tests because of
     specification errors in ES10. Using the tests, we found eight specification errors,
@@
     nine proposals that are ready for inclusion in the next ECMAScript
-    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
-    out of \inred{XXX} algorithm steps for all the proposals.  After completion
-    of the missing parts, we found four specifications errors in BigInt
+    (ES11, 2020).  It automatically synthesized parsers and compiled 560
+    out of 595 algorithm steps for all the proposals.  After completion
+    of the missing parts, we found three specifications errors in BigInt
     proposal by executing the corresponding tests in Test262.  After fixing
-    them, the extracted semantics passed all \inred{XXX} tests.
+    them, the extracted semantics passed all applicable ES10 tests and 303 new
+    applicable tests.
 \end{itemize}

### 2020-05-08 ase20/eval.tex
[ASE] Fill all numbers
[ASE] Updated eval for ES10-3

@@
     2015-06-01 &
-    TBD &
-    \multicolumn{1}{c|}{TBD} &
+    2020-05-07 &
+    1,802 days &
     7 \\\hline
@@
     209 days &
-    \inred{XX} \\\hline
+    533 \\\hline
 
@@
     209 days &
-    \inred{XX} \\\hline
+    2 \\\hline
 
@@
     53 days &
-    \inred{XX}
+    1
   \end{tabular}
@@
 which is true even when {\it index} is +0.
-It caused seven tests failed.  We proposed a fix, which is
-confirmed on April 22, 2020.
+It caused seven tests failed. We proposed a fix accepted on May 8, 2020.
+Thus, ES10-3 existed for 1,802 days.
 
@@
     298/326 &
-    \inred{207}/207 &
-    \inred{18,064}/18,064\\\hline
+    196/207 &
+    17,539/18,064\\\hline
 
@@
 passed all applicable tests except the semantics from the
-\code{BigInt} proposal.  It failed for \inred{XX} tests out of 207
-applicable tests for the proposal and \inred{XXXX} tests out of
-\inred{XXXXX} applicable tests for ES10.
+\code{BigInt} proposal.  It failed for 11 tests out of 207
+applicable tests for the proposal and 525 tests out of
+18,064 applicable tests for ES10.
 

### 2020-08-09 src/main/scala/kr/ac/kaist/jiset/phase/AlgoStepDiff.scala
Show algorithm coverage in algo-step-diff

@@ -4,6 +4,7 @@ import java.io.File
 import kr.ac.kaist.ires.ir._
 import kr.ac.kaist.jiset.{ DIFFLIST, RESOURCE_DIR }
 import kr.ac.kaist.jiset.algorithm._
+import kr.ac.kaist.jiset.model.AlgoCompiler
 import kr.ac.kaist.jiset.util.Useful._
 import kr.ac.kaist.jiset.{ LINE_SEP, JISETConfig }
 import scala.Console.{ RESET, GREEN }
@@ -19,16 +20,24 @@ case object AlgoStepDiff extends PhaseObj[Unit, AlgoStepDiffConfig, Unit] {
     unit: Unit,
     jisetConfig: JISETConfig,
     config: AlgoStepDiffConfig
+  ): Unit = {
+    apply("general", GeneralAlgoCompiler("", _))
+    apply("manual", AlgoCompiler("", _))
+  }
+
+  def apply(
+    genName: String,
+    algoGen: Algorithm => GeneralAlgoCompilerHelper
   ): Unit = DIFFLIST match {
     case base :: rest =>
       println("calculating algorithm steps...")
-      val initSt = getState(base)
+      val initSt = getState(base, algoGen)
       val initRes = getRes(initSt)
       val (_, res) = rest.foldLeft((initSt, initRes)) {
         case ((prevSt, prevRes), _version) =>
           val State(prevVersion, prevAlgoMap, _, _) = prevSt
           val AllResult(each, diff) = prevRes
-          val st = getState(_version)
+          val st = getState(_version, algoGen)
           val version = _version.dropRight(5)
           val tlb = getTLB(st)
           val diffLang = MMap[String, Boolean]()
@@ -55,9 +64,8 @@ case object AlgoStepDiff extends PhaseObj[Unit, AlgoStepDiffConfig, Unit] {
           (st, AllResult(each + (version -> tlb), diff + (diffVersion -> diffTLB)))
       }
       val (each, diff) = getAverage(res)
-      println("finished")
       println("========================================")
-      println("ECMAScript each version")
+      println(s"ECMAScript each version ($genName)")
       println("========================================")
       for ((version, TLB(all, lang, builtin)) <- res.each) {
         println(f"${"   "}%-8s Total   : ${getCountString(all)}")
@@ -71,7 +79,7 @@ case object AlgoStepDiff extends PhaseObj[Unit, AlgoStepDiffConfig, Unit] {
[…]

### 2020-08-09 ase20/compiler.tex
[ASE] Updated Table 1
Updated report
[ASE20] Updated paper

@@
 For presentation brevity, we omit the formalization of \( \ires \) in this paper
-and include it in a companion report\inred{\cite{report}}.
+and include it in a companion report~\cite{report}.
 
@@
       \text{\# Rules}
-      & \inred{17}
-      & \inred{16}
-      & \inred{8}
-      & \inred{11}
-      & \inred{33}
-      & \inred{7}
+      & 21
+      & 27
+      & 16
+      & 11
+      & 34
+      & 9
     \end{array}
@@
 algorithms are intrinsic objects, which have their own
-aliased names summarized in Table~7 of Section~6.1.7.4
-\textsf{Well-Known Intrinsic Objects}.  We extracted the alias
+aliased names summarized in
+Table~7\footnote{https://www.ecma-international.org/ecma-262/10.0/\#sec-well-known-intrinsic-objects} of Section~6.1.7.4
+\textsf{Well-Known Intrinsic Objects} in ES10.  We extracted the alias
 into \textsf{Global Setting} to utilize it during evaluation.

### 2020-08-09 ase20/eval.tex
[ASE] Fixed a small typo in eval
[ASE20] Updated paper

@@
 
-We developed \( \tool \) as an open-source tool\footnote{The URL of the tool is
-anonymized due to a double-blind review process.}, and evaluated the tool
-based on the following research questions:
+We developed \( \tool \) as an open-source
+tool\footnote{https://github.com/kaist-plrg/jiset}, and evaluated the tool based
+on the following research questions:
 \begin{itemize}[leftmargin=0.5cm]
@@
 \end{itemize}
+We performed our experiments on a machine equipped with 4.2GHz Quad-Core Intel
+Core i7 and 64GB of RAM.  On the machine, \( \tool \) took less than one minute
+to extract IR-based semantics from a given ECMAScript.
 
@@
 
-To evaluate the correctness of \( \tool \), we checked whether the
-extracted semantics from the latest ECMAScript (ES10) passes Test262
-as of February 28, 2019, when ES10 was branched out.
+To evaluate the correctness of \( \tool \), we tested the extracted semantics
+from the latest ECMAScript (ES10) by executing Test262 as of February 28, 2019,
+when ES10 was branched out.
 To focus on the core language semantics of JavaScript, we completed
@@
 automatically compiled by \textsf{Algorithm Compiler}.
+It fully covers 1,783 algorithms out of 2,026 abstract algorithms
+and 243 algorithms are partially covered.
 Among the remaining 474 steps, we manually implemented all
 missing steps for the core language semantics (137 steps) and
-the essential parts of the built-in libraries (140 steps out of
-337).  We also manually implemented \textsf{Global Setting}
+the essential parts of the built-in libraries (140 steps out of 337).
+Based on this manual implementation, 146 more abstract algorithms are fully covered.
+We also manually implemented \textsf{Global Setting}
 as described in Section~\ref{sec:compiler-impl} for the core language features.
@@
 minor language features.
-Finally, for 18,064 applicable tests, the extracted semantics
-failed for 1,709 tests.
+Finally, the extracted semantics took about three hours to evaluate 18,064
+applicable tests and failed for 1,709 tests.
 
@@
 the nearest \code{if} statement.  Because it is written in prose
-rather than in the ES10 grammar productions, it caused one test
-failed.  We proposed a fix to revise the ambiguous grammar production,
+rather than in the ES10 grammar productions, it caused one failed
+test.  We proposed a fix to revise the ambiguous grammar production,
 and TC39 confirmed it on April 23, 2020.
@@
 which is true even when {\it index} is +0.
-It caused seven tests failed. We proposed a fix accepted on May 8, 2020.
+It caused seven failed tests. We proposed a fix accepted on May 7, 2020.
 Thus, ES10-3 existed for 1,802 days.

### 2020-08-25 ase20/main.tex
[ASE] Merged Section 4 & 5
Added authors / Removed review style
Added copyright / Shorten author info / Relocated figures/tables
Added Acknowledgements for NRF / Updated report

@@
-\documentclass[sigconf,review,anonymous]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 \usepackage{booktabs}
+\usepackage{makecell}
 
@@
 
+% copyright
+\copyrightyear{2020}
+\acmYear{2020}
+\setcopyright{acmcopyright}\acmConference[ASE '20]{35th IEEE/ACM International Conference on Automated Software Engineering}{September 21--25, 2020}{Virtual Event, Australia}
+% \acmBooktitle{35th IEEE/ACM International Conference on Automated Software Engineering (ASE '20), September 21--25, 2020, Virtual Event, Australia}
+\acmPrice{15.00}
+\acmDOI{10.1145/3324884.3416632}
+\acmISBN{978-1-4503-6768-4/20/09}
+
 \begin{document}
@@
 \affiliation{%
-  \institution{KAIST}
-  \department{School of Computing}
-  \city{Daejeon}
-  \country{South Korea}
+  \institution{KAIST, South Korea}
 }
@@
 
+\author{Seungmin An}
+\affiliation{%
+  \institution{KAIST, South Korea}
+}
+\email{h2oche@kaist.ac.kr}
+
 \author{Sukyoung Ryu}
 \affiliation{%
-  \institution{KAIST}
-  \department{School of Computing}
-  \city{Daejeon}
-  \country{South Korea}
+  \institution{KAIST, South Korea}
 }
@@
 \input{compiler}
-\input{impl}
 \input{eval}
@@
 \input{conclusion}
+
+\section*{Acknowledgements}
+This work was supported by National Research Foundation of
+Korea (NRF) (Grants NRF-2017R1A2B3012020 and 2017M3C4A7068177).
 

### 2020-08-26 ase20-final/abstract.tex
[ASE20] Final Version approved by IEEE PDF eXpress

--- 2020-05-01 ase20/abstract.tex
@@
 \tool \) is \textit{forward compatible} by applying it to nine feature
-proposals ready for inclusion in the next ECMAScript, which let us find four
+proposals ready for inclusion in the next ECMAScript, which let us find three
 errors in the BigInt proposal.

### 2020-08-26 ase20-final/related.tex
[ASE20] Final Version approved by IEEE PDF eXpress

--- 2020-04-30 ase20/related.tex
@@
 Our technique is closely related to three fields: parser generation,
-automatic model generation, and formal semantics of JavaScript.
+automatic semantics extraction, and formal semantics of JavaScript.
 
-From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
+\textbf{Parser Generation:} From Packrat parsing~\cite{packrat} with
+PEG~\cite{peg}, recursive-descent
 parsers with backtracking support linear-time parsing.  However, it
@@
 
-The closest work to ours in automatic model generation
-is \citet{javadoc}'s, which generates Java code from Javadoc comments
-for API functions.  Using NLP techniques and heuristic methods,
-it produces candidate code and removes wrong ones
+\textbf{Automatic Semantics Extraction:} The closest work to ours is the formal
+semantics extraction for x86~\cite{extract-x86} and ARM~\cite{extract-arm}.
+They utilized complex Natural Language Processing (NLP) and Machine Learning
+(ML) to extract formal semantics of small-sized low-level assembly languages.
+Another related work is \citet{javadoc}'s automatic model generation, which
+generates Java code from Javadoc comments for API functions.  Using NLP techniques
+and heuristic methods, it produces candidate code and removes wrong ones
 by testing them with actual implementation. Unlike their approach, we

### 2021-03-29 paper/ase21/related.tex
[ASE21] Format

\section{Related Work}\label{sec:related}

\begin{itemize}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
\end{itemize}

### 2021-03-29 paper/ase21/abstract.tex
[ASE21] Abstract

\begin{abstract}
  JavaScript is one of mainstream programming languages not only in client-side
  programming but also in serever-side programming and even embedded systems.
  Thus, various JavaScript engines are developed and maintained in various
  fields and they must conform to the syntax and semantics described in
  ECMAScript, the standard specification of JavaScript.  Since an incorrect
  description in ECMAScript can lead to the wrong implementation of JavaScript
  engines, it is important to check the correctness of ECMAScript.  However, all
  the specification updates are currently manually checked by the Ecma Technical
  Committee 39 (TC39) without any automated tools.  Moreover, in late 2014, the
  committee announced yearly release cadence and open development process of
  ECMAScript to quickly adapt to an evolving development environment.  Thus, the
  manual checking becoems more labor-intensive and error-prone.

  To alleviate this problem, we propose $\tool$, an ECMAScript Static Checker
  based on Refinement Types.  Our tool performs the following three steps for a
  given specification: 1) to convert abstract algorithms in the specification to
  untyped intermediate representation, 2) to extract type information of data
  structures used in the specification,  and 2) to perform type analysis with
  the extracted type information to detect specification errors.  Moreover, we
  use \textit{refinement types} over the extracted type information to reduce
  false alarms.  \inred{TODO: explanation of refinement types.} We evaluated
  $\tool$ with \inred{XXX different versions of ECMAScript in the official GitHub
  repository between 2018 June and 2021 March.} Among \inred{XXX} known
  specification errors, our tool detected \inred{XXX} errors with \inred{XXX}
  false alarms.  Moreover, $\tool$ detected \inred{X} new specification errors
  in the draft of next release of ECMAScript (ES12, 2021).
\end{abstract}

### 2021-03-29 src/main/scala/kr/ac/kaist/jiset/analyzer/AbsState.scala
More modeling

@@ -104,6 +104,7 @@ case class AbsState(
     base.escaped.foreach(_ match {
       case MapT(elem) => t ⊔= elem
       case ListT(elem) if prop ⊑ NumT.abs => t ⊔= elem
+      case StrT if prop ⊑ NumT.abs => t ⊔= StrT
       case _ =>
     })
     t

### 2021-03-29 paper/ase21/abstract.tex
[ASE21] Bullet list for Introduction

@@
   untyped intermediate representation, 2) to extract type information of data
-  structures used in the specification,  and 2) to perform type analysis with
-  the extracted type information to detect specification errors.  Moreover, we
-  use \textit{refinement types} over the extracted type information to reduce
-  false alarms.  \inred{TODO: explanation of refinement types.} We evaluated
-  $\tool$ with \inred{XXX different versions of ECMAScript in the official GitHub
+  structures used in the specification, and 3) to perform type analysis with the
+  extracted type information to detect specification errors.  Moreover, we use
+  \textit{refinement types} over the extracted type information to reduce false
+  alarms.  \inred{TODO: explanation of refinement types.} We evaluated $\tool$
+  with \inred{XXX different versions of ECMAScript in the official GitHub
   repository between 2018 June and 2021 March.} Among \inred{XXX} known

### 2021-03-29 paper/ase21/intro.tex
[ASE21] Bullet list for Introduction

\section{Introduction}\label{sec:intro}

\begin{itemize}
  \item JavaScript is one of mainstream programming languages not only in
    client-side programming but also in serever-side programming and even
    embedded systems.

  \item Various JavaScript engines are developed and maintained in various
    fields and they must conform to the syntax and semantics described in
    ECMAScript, the standard specification of JavaScript.

  \item Since an incorrect description in ECMAScript can lead to the wrong
    implementation of JavaScript engines, it is important to check the
    correctness of ECMAScript.

  \item However, all the specification updates are currently manually checked by
    the Ecma Technical Committee 39 (TC39) without any automated tools.

  \item Moreover, in late 2014, the committee announced yearly release cadence
    and open development process of ECMAScript to quickly adapt to an evolving
    development environment.

  \item Thus, the manual checking becoems more labor-intensive and error-prone.

  \item To alleviate this problem, we propose $\tool$, an ECMAScript Static
    Checker based on Refinement Types.  Our tool performs the following three
    steps for a given specification: 1) to convert abstract algorithms in the
    specification to untyped intermediate representation, 2) to extract type
    information of data structures used in the specification, and 3) to perform
    type analysis with the extracted type information to detect specification
    errors.  Moreover, we use \textit{refinement types} over the extracted type
    information to reduce false alarms.  \inred{TODO: explanation of refinement
    types.}
\end{itemize}

Our main contributions are as follows:
\begin{itemize}
  \item We implemented $\tool$, which is the first tool that statically checks the
    correctness of JavaScript language specifications using type analysis.  It
    can detect variuos kinds of specification errors including \inred{reference
    errors, $\cdots$}.
  \item We present \inred{...} to increase the precision of type analysis.
    \inred{$\cdots$}.
  \item We evaluate $\tool$ with \inred{XXX different versions of ECMAScript in
    the official repository between 2018 June and 2021 March.} Among \inred{XXX}
    known specification errors, our tool detected \inred{XXX} errors with
    \inred{XXX} false alarms.  Moreover, $\tool$ detected \inred{X} new
    specification errors in the draft of next release of ECMAScript (ES12,
    2021).
\end{itemize}

### 2021-04-02 src/main/scala/kr/ac/kaist/jiset/analyzer/AnalyzeREPL.scala
Refactored AnalyzeREPL

@@ -49,72 +49,51 @@ object AnalyzeREPL {
     .build()
   private val prompt: String = LINE_SEP + s"${MAGENTA}analyzer>${RESET} "
 
-  // helper for break
-  private def isBreak(cp: ControlPoint): Boolean = cp match {
-    case NodePoint(node: Entry, _) => breakpoints.exists {
-      case (CmdBreak.func, name) => name == cfg.funcOf(node).name
-      case (CmdBreak.block, uid) => uid.toInt == node.uid
-      case _ => ???
-    }
-    case NodePoint(node, _) => breakpoints.exists {
-      case (CmdBreak.block, uid) => uid.toInt == node.uid
-      case _ => false
-    }
-    case _ => false
-  }
-  private def addBreak(opt: String, bp: List[String]): Unit = bp match {
-    case Nil => println("need arguments")
-    case str :: _ => breakpoints += (opt -> str)
-  }
-
-  // stop
-  private def stop(): Unit = { breakpoints.clear(); continue = true }
-
   // help
   private lazy val help = { Command.help; println }
 
-  // info
-  private def printInfo(opt: String, args: List[String]): Unit = args match {
-    case Nil => println("need arguments")
-    case str :: _ =>
-      val info = opt match {
-        case CmdInfo.ret => sem.getReturnPointByName(str)
-        case CmdInfo.block => sem.getNodePointsById(str.toInt)
-      }
-      info.foreach(cp => {
-        println(sem.getString(cp, CYAN, true))
-        println
-      })
+  // break
+  private def break(args: List[String]) = {
+    import CmdBreak._
+    args match {
+      case opt :: bp :: _ if options contains opt.substring(1) =>
+        breakpoints += (opt.substring(1) -> bp)
+      case _ => println("Inappropriate argument")
+    }
   }
 
-  // entry
-  var visited: Set[ReturnPoint] = Set()
-
-  private def getEntryFunc(cp: ControlPoint): Set[String] = {
-    val rp = getRpOf(cp)
-    if (visited contains rp) Set()
-    else {
-      visited += rp
-      rp.func.algo.head match {
-        case head @ SyntaxDirectedHead(_, _, _, _, _, withParam) if withParam.isEmpty =>
-          Set(rp.func.name)
-        case _ => getCallNodes(rp).flatMap(getEntryFunc(_))
+  // rm-break
+  private def rmBreak(args: List[String]) = {
+    import CmdRmBreak._;
+    args match {
+      case Nil => println("need arguments")
[…]

### 2021-04-02 paper/ase21/checker.tex
[ASE21] More brainstroming

\section{Static Checker}\label{sec:checker}

\subsection{Reference Checker}
\begin{itemize}
  \item unknown variables
  \item already defined variables
  \item already defined variables
\end{itemize}

\subsection{Parameter Arity Checker}
\begin{itemize}
  \item remaining normal parameters
    (parameter types: normal / optional / variadic)
  \item remaining arguments
\end{itemize}

\subsection{Type Checker}
\begin{itemize}
  \item unchecked abrupt completions
  \item typed operators
\end{itemize}

\subsection{Assertion Checker}
\begin{itemize}
  \item `typeof` assertions
  \item `instance-of` assertions
  \item reachability assertions
\end{itemize}

### 2021-04-02 paper/ase21/eval.tex
[ASE21] More brainstroming

\section{Evaluation}\label{sec:eval}

\begin{itemize}
  \item RQ1: Quality of $\tool$: Performance / Precision
  \item RQ2: Survey of true bugs: TTL / creater or solver / \# by kinds
  \item RQ3: How many $\tool$ detect new bugs in the recent version? - detailed
    explanation
\end{itemize}

### 2021-04-02 paper/ase21/overview.tex
[ASE21] More brainstroming

\section{Overview}\label{sec:overview}

\subsection{Background}
\subsection{Motivation}
\subsection{Overall Structure}

### 2021-04-05 paper/ase21/abstract.tex
[ASE21] New title / Abstract

@@
   JavaScript is one of mainstream programming languages not only in client-side
-  programming but also in serever-side programming and even embedded systems.
+  programming but also in server-side programming and even embedded systems.
   Thus, various JavaScript engines are developed and maintained in various
@@
   ECMAScript to quickly adapt to an evolving development environment.  Thus, the
-  manual checking becoems more labor-intensive and error-prone.
+  manual checking becomes more labor-intensive and error-prone.
 
-  To alleviate this problem, we propose $\tool$, an ECMAScript Static Checker
-  based on Refinement Types.  Our tool performs the following three steps for a
-  given specification: 1) to convert abstract algorithms in the specification to
-  untyped intermediate representation, 2) to extract type information of data
-  structures used in the specification, and 3) to perform type analysis with the
-  extracted type information to detect specification errors.  Moreover, we use
-  \textit{refinement types} over the extracted type information to reduce false
-  alarms.  \inred{TODO: explanation of refinement types.} We evaluated $\tool$
-  with \inred{XXX different versions of ECMAScript in the official GitHub
-  repository between 2018 June and 2021 March.} Among \inred{XXX} known
-  specification errors, our tool detected \inred{XXX} errors with \inred{XXX}
-  false alarms.  Moreover, $\tool$ detected \inred{X} new specification errors
-  in the draft of next release of ECMAScript (ES12, 2021).
+  To alleviate this problem, we propose $\tool$, a JavaScript Specification Type
+  Analyzer using Refinement.  It is the first tool that performs \textit{type
+  analysis} on JavaScript specifications and detects specification bugs using
+  \textit{bug checkers}.  For a given specification, our tool first compiles
+  each abstract algorithm written in a structured natural language to the
+  corresponding function of $\ires$, which is an untyped intermediate
+  representation for ECMAScript.  Then, it performs type analysis for compiled
+  functions with specification types defined in the given ECMAScript.  Based on
+  the result of type analysis, $\tool$ detects specification bugs using four
+  different bug checkers.  Moreover, to increase precision of type analysis, we
+  also present \textit{refinement} for type analysis, which prunes out
+  infeasible abstract states by using conditions in assertions and branches.
+  We evaluated $\tool$ with all 787 different versions of ECMAScript existed in
+  the official repository for the recent three years (from 20 March 2018 to 9
+  March 2021).  Our tool detected \inred{XXX} specification bugs including only
+  \inred{XXX} false alarms caused by the imprecision of type analysis.  Among
+  \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
+  \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
+  version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX} newly
+  found bugs and they are confirmed by the committee.
 \end{abstract}

### 2021-04-05 paper/ase21/abstract.tex
Updated abstract

@@
   representation for ECMAScript.  Then, it performs type analysis for compiled
-  functions with specification types defined in the given ECMAScript.  Based on
-  the result of type analysis, $\tool$ detects specification bugs using four
-  different bug checkers.  Moreover, to increase precision of type analysis, we
-  also present \textit{refinement} for type analysis, which prunes out
-  infeasible abstract states by using conditions in assertions and branches.
-  We evaluated $\tool$ with all 787 different versions of ECMAScript existed in
-  the official repository for the recent three years (from 20 March 2018 to 9
-  March 2021).  Our tool detected \inred{XXX} specification bugs including only
+  functions with specification types defined in ECMAScript.  Based on the result
+  of type analysis, $\tool$ detects specification bugs using four different bug
+  checkers.  Moreover, to increase precision of type analysis, we also present
+  \textit{refinement for type analysis}, which prunes out infeasible abstract
+  states by using conditions of assertions and branches.  We evaluated $\tool$
+  with all \inred{787} different versions of ECMAScript existed in the official
+  repository for the recent three years (\inred{from 20 March 2018 to 9 March
+  2021}).  Our tool detected \inred{XXX} specification bugs including only
   \inred{XXX} false alarms caused by the imprecision of type analysis.  Among

### 2021-04-06 paper/ase21/abstract.tex
[ASE21] Intro

@@
   analysis} on JavaScript specifications and detects specification bugs using
-  \textit{bug checkers}.  For a given specification, our tool first compiles
+  \textit{bug detector}.  For a given specification, our tool first compiles
   each abstract algorithm written in a structured natural language to the
@@
   functions with specification types defined in ECMAScript.  Based on the result
-  of type analysis, $\tool$ detects specification bugs using four different bug
-  checkers.  Moreover, to increase precision of type analysis, we also present
-  \textit{refinement for type analysis}, which prunes out infeasible abstract
-  states by using conditions of assertions and branches.  We evaluated $\tool$
-  with all \inred{787} different versions of ECMAScript existed in the official
-  repository for the recent three years (\inred{from 20 March 2018 to 9 March
-  2021}).  Our tool detected \inred{XXX} specification bugs including only
-  \inred{XXX} false alarms caused by the imprecision of type analysis.  Among
+  of type analysis, $\tool$ detects specification bugs using the bug detector
+  consisting of four different checkers.  Moreover, to increase precision of
+  type analysis, we also present \textit{condition-based refinement} for type
+  analysis, which prunes out infeasible abstract states by using conditions of
+  assertions and branches.  We evaluated $\tool$ with all \inred{XXX} different
+  versions existed in the official ECMAScript repository for the recent
+  \inred{three years from 2018 to 2021}.  Our tool detected \inred{XXX}
+  specification bugs including only \inred{XXX} false alarms caused by the
+  imprecision of type analysis in \inred{XX} minutes on average.  Among
   \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for

### 2021-04-06 paper/ase21/intro.tex
[ASE21] Intro

@@
 
+JavaScript is one of the most popular programming languages.  According to the
+2020 State of the Octoverse\footnote{https://octoverse.github.com/}, which is
+the annual report of GitHub, the most dominated programming language in GitHub
+repositories was JavaScript since 2014 to 2020.  While JavaScript was initially
+designed for client-side programming in web browsers, now it is widely used in
+server-side programming~\cite{nodejs} and even in embedded
+systems~\cite{espruino, tessel2, moddable}.  Thus, its engines are also
+developed and maintained in diverse fields conforming to ECMAScript, the
+JavaScript standard specification that describes the syntax and semantics of
+JavaScript.
+
+The correctness of ECMAScript becomes more important because an incorrect
+description of syntax or semantics in the specification can lead to the wrong
+implementation of existing JavaScript engines used in various fields.  However,
+all the specification updates are currently manually checked by the Ecma
+Technical Committee 39 (TC39) without any automated tools.  This manual checking
+process is obviously labor-intensive and also error-prone thus the current
+JavaScript specification is vulnerable to specification bugs.  Besides, in late
+2014, the committee announced yearly release cadence and open development
+process of ECMAScript to quickly adapt to an evolving development environment.
+According to \citet{jiset}, the average number of updated steps of abstract
+algorithms between consecutive releases from ES7 (2016) to ES10 (ES2019) is
+9645.5.  In the official repository of ECMAScript, \inred{X,XXX} pull requests
+and \inred{X,XXX} commits exist in the master branch.  Therefore, it makes more
+difficult to manually check all the specification updates using limited human
+resources.
+
+Unfortunately, there is no existing tool to automatically detect bugs in the
+rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
+have tried to resolve this problem using additional annotations in abstract
+algorithms.  Additional annotations make the specification more readable and
+also they are useful for the specification-based tools such as JavaScript
+engines~\cite{v8, graaljs, qjs, moddable}, static analyzers~\cite{safe, tajs,
+jsai, wala}, and verification tools~\cite{javert}.  Thus, they decided to
+manually insert two different annotations: 1) \textit{assertions} to denotes the
+assumptions in a certain point of abstract algorithms, and 2) two different
+\textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
+records might be abrupt or not.  For example, $\code{"Assert: Type(O) is
+Object"}$ denotes that the variable $\code{O}$ always has $\code{Object}$ values
+at this point and $\code{"? GetV(V, P)"}$ denotes that return values of
+$\code{GetV(V, P)}$ might be abrupt completions.  Moreover, they recently
+started the internal discussion of manual type annotations for variables,
+parameters, and return values for each abstract algorithm.  However, to manually
+annotate types for all of them without any automated tool is also
+labor-intensive and error-prone.  Furthermore, even though the such manual type
+annotations can give more information for manual checking of specification
+updates, it still does not provide any automatic approach to detect
+specification bugs.
+
+To alleviate this problem, we propose a tool $\tool$, a \textbf{J}avaScript
+\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
+\textbf{R}efinement.  The main idea of our tool is to perform \textit{type
+analysis} for JavaScript specifications to statically detect type-related
+specification bugs in an automatic way.  However, it is difficult to directly
+perform type analysis to ECMAScript because its abstract algorithms are written
+in a natural language.  For a decade, researchers~\cite{lambdajs, jscert, kjs}
+have tried to formally define various mechanized JavaScript specification for a
+specific version of ECMAScript by hand.  However, the manual formalization is
+not suitable for the automatic detection of bugs in the rapidly evolved
+JavaScript specifications.  On the other hand, several approaches to utilize
+information directly extracted from specifications written in a structured
+natural language are recently presented in diverse fields such as system
+architectures~\cite{x86, arm}, network protocols~\cite{basespec}, and language
+specifications~\cite{spectest}.  For JavaScript, \citet{jiset} presents $\jiset$
+that automatically compiles each abstract algorithm written in a structured
+natural language to the corresponding function of $\ires$, an untyped
+intermediate representation for ECMAScript.  Therefore, we leverage this tool to
+automatically get mechanized specifications for JavaScript.
+
+For the compiled mechanized specifications, $\tool$ performs type analysis for
+compiled functions with specification types defined in ECMAScript.  ECMAScript
+contains not only JavaScript language types but also specification types such as
+abstract syntax trees (ASTs), internal records (i.e. environments, completions,
+or property descriptors), and internal lists.  Our tool extract syntax and
+table-based type information from ECMAScript and constructs type hierarchy and
+fields for ASTs and records.  Based on the extracted types, $\tool$ performs
+type analysis and detects specification bugs using a \textit{bug detector}
+consisting of four different checkers: 1) reference checker, 2) arity checker,
+3) operator type checker, and 4) assertion checker.  Moreover, to increase
+precision of type analysis, we also present \textit{condition-based refinement}
+for type analysis on ECMAScript. Its main concept is to prunes out infeasible
+abstract states by using conditions of assertions and branches.  The refinement
+technique can reduce false alarms caused by spurious types inferred by imprecise
+analysis.  We evaluate our tool with all \inred{XXX} different versions existed
+in the official ECMAScript repository for the recent \inred{three years from
+2018 to 2021}.
+
+In summary, our main contributions are as follows:
 \begin{itemize}
-  \item JavaScript is one of mainstream programming languages not only in
-    client-side programming but also in serever-side programming and even
-    embedded systems.
-
-  \item Various JavaScript engines are developed and maintained in various
-    fields and they must conform to the syntax and semantics described in
-    ECMAScript, the standard specification of JavaScript.
-
-  \item Since an incorrect description in ECMAScript can lead to the wrong
-    implementation of JavaScript engines, it is important to check the
-    correctness of ECMAScript.
-
-  \item However, all the specification updates are currently manually checked by
-    the Ecma Technical Committee 39 (TC39) without any automated tools.
-
-  \item Moreover, in late 2014, the committee announced yearly release cadence
-    and open development process of ECMAScript to quickly adapt to an evolving
-    development environment.
-
-  \item Thus, the manual checking becoems more labor-intensive and error-prone.
-
-  \item To alleviate this problem, we propose $\tool$, an ECMAScript Static
-    Checker based on Refinement Types.  Our tool performs the following three
-    steps for a given specification: 1) to convert abstract algorithms in the
-    specification to untyped intermediate representation, 2) to extract type
-    information of data structures used in the specification, and 3) to perform
-    type analysis with the extracted type information to detect specification
-    errors.  Moreover, we use \textit{refinement types} over the extracted type
-    information to reduce false alarms.  \inred{TODO: explanation of refinement
-    types.}
+  \item We present $\tool$, which is the first tool that performs \textit{type
+    analysis} on ECMAScript to check the the correctness of JavaScript language
+    specifications.  $\tool$ automatically detects specification bugs via the
+    \textit{bug detector} consisting of four different checkers: 1) reference
+    checker, 2) arity checker, 3) operator type checker, and 4) assertion
+    checker.
+  \item We present \textit{condition-based refinement} for type analysis of
+    ECMAScript to reduce false alarms by increasing the analysis precision.  Its
+    main idea is to prune out infeasible abstract states by using conditions of
+    assertions and branches.
+  \item We demonstrate the practicality of $\tool$. For recent \inred{XXX}
+    different versions of ECMAScript, our tool detected \inred{XXX}
+    specification bugs including only \inred{XXX} false alarms caused by the
+    imprecision of type analysis in \inred{XX} minutes on average.  Among
+    \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
+    \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
+    version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX}
+    newly found bugs and they are confirmed by the committee.
 \end{itemize}
-
-Our main contributions are as follows:
-\begin{itemize}
-  \item We implemented $\tool$, which is the first tool that statically checks the
-    correctness of JavaScript language specifications using type analysis.  It
-    can detect variuos kinds of specification errors including \inred{reference
-    errors, $\cdots$}.
-  \item We present \inred{...} to increase the precision of type analysis.
-    \inred{$\cdots$}.
-  \item We evaluate $\tool$ with \inred{XXX different versions of ECMAScript in
-    the official repository between 2018 June and 2021 March.} Among \inred{XXX}
-    known specification errors, our tool detected \inred{XXX} errors with
-    \inred{XXX} false alarms.  Moreover, $\tool$ detected \inred{X} new
-    specification errors in the draft of next release of ECMAScript (ES12,
-    2021).
-\end{itemize}

### 2021-04-06 paper/ase21/related.tex
[ASE21] Intro

@@
 \begin{itemize}
+  \item Abstract Interpretation~\cite{ai1977, ai1992}
   \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
+  \item JavaScript Manual Mechanized Specification:
+    \begin{itemize}
+      \item The Essence of Javascript~\cite{lambdajs}
+      \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
+      \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
+      \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
+      \item JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
+      \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
+        and Specification~\cite{jest}
     \end{itemize}
+  \item Automatic Mechanized Specification for others:
+    \begin{itemize}
+      \item Automatic extraction of x86 formal semantics from its natural
+        language description~\cite{x86}
+      \item Formal semantics extraction from natural language specifications for
+        ARM~\cite{arm}
+      \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
+      \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
+        Specifications for L3 Protocols~\cite{basespec}
+    \end{itemize}
+\end{itemize}

### 2021-04-06 src/main/scala/kr/ac/kaist/jiset/cfg/DotPrinter.scala
Fixed bug in DotPrinter and added rule

@@ -198,6 +198,7 @@ class DotPrinter {
   // normalize beautified view
   private val normPattern = """[\[\](),\s~?"]""".r
   private def norm(view: View): String = normPattern.replaceAllIn(view.tys.map {
+    case NormalT(RecordT(props)) => NormalT(NameT("Record"))
     case RecordT(props) => NameT("Record")
     case t => t
   }.toString, "")

### 2021-04-07 paper/ase21/overview.tex
[ASE21] temporal dump
[ASE21] Overall structure
[ASE21] Figure 2. example

@@
 
-\subsection{Background}
-\subsection{Motivation}
-\subsection{Overall Structure}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.48\textwidth]{img/overall}
+  \vspace*{-1.5em}
+  \caption{Overall structure of $\tool$: a type analyzer and a bug detector for
+  mechanized specifications extracted from ECMAScript by $\jiset$.}
+  \label{fig:overall}
+\end{figure}
+
+In this section, we demonstrate overall structure of $\tool$ depicted in
+Figure~\ref{fig:overall} with a simple motivating example.
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.85\textwidth]{img/example}
+  \vspace*{-1em}
+  \caption{A motivating example: a simple avaScript code with corresponding
+  previous specification bugs and their bugfixs.}
+  \label{fig:example}
+\end{figure*}

### 2021-04-08 paper/ase21/intro.tex
[ASE21] Overview

@@
 JavaScript specifications.  On the other hand, several approaches to utilize
-information directly extracted from specifications written in a structured
-natural language are recently presented in diverse fields such as system
-architectures~\cite{x86, arm}, network protocols~\cite{basespec}, and language
+information directly extracted from specifications written in a natural language
+are recently presented in diverse fields such as system architectures~\cite{x86,
+arm}, network protocols~\cite{basespec}, and language
 specifications~\cite{spectest}.  For JavaScript, \citet{jiset} presents $\jiset$
@@
 natural language to the corresponding function of $\ires$, an untyped
-intermediate representation for ECMAScript.  Therefore, we leverage this tool to
+intermediate representation for ECMAScript.  Therefore, we utilize this tool to
 automatically get mechanized specifications for JavaScript.
@@
 consisting of four different checkers: 1) reference checker, 2) arity checker,
-3) operator type checker, and 4) assertion checker.  Moreover, to increase
+and 3) assertion checker, 4) operand type checker.  Moreover, to increase
 precision of type analysis, we also present \textit{condition-based refinement}
@@
     \textit{bug detector} consisting of four different checkers: 1) reference
-    checker, 2) arity checker, 3) operator type checker, and 4) assertion
+    checker, 2) arity checker, and 3) assertion checker, 4) operand type
     checker.

### 2021-04-08 paper/ase21/overview.tex
[ASE21] Overview

@@
   \label{fig:overall}
+  \vspace*{-1.5em}
 \end{figure}
-
-In this section, we demonstrate overall structure of $\tool$ depicted in
-Figure~\ref{fig:overall} with a simple motivating example.
 
@@
   \centering
-  \includegraphics[width=0.85\textwidth]{img/example}
+  \includegraphics[width=0.9\textwidth]{img/example}
   \vspace*{-1em}
-  \caption{A motivating example: a simple avaScript code with corresponding
-  previous specification bugs and their bugfixs.}
+  \caption{An example JavaScript program with related previous specification
+  bugs and their bugfixes.}
   \label{fig:example}
 \end{figure*}
+% XXX
+% \begin{lstlisting}[style=FigureJS]
+% let f;    f ??= (x) => Math.round(x);    f(true);
+% \end{lstlisting}
+
+In this section, we demonstrate overall structure of $\tool$ depicted in
+Figure~\ref{fig:overall}.  Our tool consists of three different steps:
+1) specification extraction, 2) type analysis, and 3) bug detection.
+
+\subsection{Specification Extraction}\label{sec:overview-spec-extract}
+
+ECMAScript describes JavaScript syntax and semantics written in a structured
+natural language.  We utilize $\jiset$ to extract mechanized specification from
+a given ECMAScript.
+
+\paragraph{Syntax and Semantics} ECMAScript uses a variant of extended BNF
+notations to describe JavaScript syntax.  $\jiset$ synthesizes AST structures
+and JavaScript parsers from its lexical and syntactic productions.  Our tool
+utilizes only AST structures to define AST types and to access corresponding
+syntax-directed algorithms.  For JavaScript semantics, ECMAScript contains
+abstract algorithms written in a structured natural language.  $\jiset$ compiles
+them to functions of $\ires$, an untyped intermediate representation for
+ECMAScript.  For brevity, we will formally define syntax and semantics of
+a simplified $\ires$ in Section~\ref{sec:ires}.
+
+\paragraph{Types} In ECMAScript, types denote not only JavaScript types but also
+specification types for ASTs, internal records, and internal lists.  For ASTs,
+we use non-terminal names as thier type names and AST types $A$ and $B$ have a
+subtype relation $A \subtype B$ when $A$ is an alternative of $B$.  If record
+types have names, we treat them as normal types and manually define their fields
+according to the latest version of ECMAScript.  For example, fields of the
+\code{Realm} record types are defined in ``Table 23: Realm Record Fields'' in
+ECMAScript.  Ohterwise, we define structural types for unnamed record types.
+For lists, we define \code{Nil} types for empty lists and parametric list types
+\code{List[T]} for lists whose elements have \code{T} type.
+
+\subsection{Type Analysis}\label{sec:overview-type-analysis}
+
+The type analyzer performs flow-sensitive type analysis with type-sensitivity
+for parameters to precisely detect specification bugs.  It consists of two
+sub-modules: an \textit{analysis initializer} and an \textit{abstract transfer}.
+We use a stack-based worklist algorithm to calculate fixpoint of abstract
+transfer and assign the initial set of worklist using analysis initializer.
+
+\paragraph{Analysis Initializer} In ECMAScript, there are three different kinds
+of abstract algorithms \textit{normal}, \textit{syntax-directed} and
+\textit{built-in}.  Since all the parameter types are known for built-in
+algorithms and syntax-directed algorithms having no additional parameters, we
+utilize them as entry points of type analysis.  For each entry point, the
+initializer defines its abstract environment with parameter types and push the
+pair of entry point and its abstract environment to the worklist.
+
+\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
+pair of a control point and its abstract environment from the worklist, produces
+other pairs based on abstract semantics, and pushes them to the worklist.  The
+iteration will be finished when the worklist becomes empty.
+
+\subsection{Bug Detection}\label{sec:overview-bug-detect}
+
+To detect specification bugs based on the result of type analysis, we develop
+four different checkers in the bug detector.  We explain targets of checkers
+using an example JavaScript program with related previous specification bugs and
+their bugfixes descirbed in Figure~\ref{fig:example}.
+
+\paragraph{Reference Checker} The example JavaScript program first defines a
+variable \jscode{f} without initialization thus it stores \jscode{undefined}.
+Then, it assigns an arrow function to \jscode{f} using the operator
+\jscode{??=}.  While the corresponding \textbf{Evaluation} algorithm originally
+used \textbf{GetReferencedName} algorithm to get reference name at line 4.a, a
+contributor removed the \textbf{GetReferencedName} algorithm and replaced its
+all invocations to accesses of the field [[ReferencedName]] on October 28, 2020.
+However, there were several missing cases including the semantics of
+\jscode{??=} until another contributor fixed this bug on November 3, 2020.
+Thus, an unknown variable bug of \textbf{GetReferencedName} lated for 6 days.
+The reference checker detects reference bugs including unknown variable bugs.
+
+\paragraph{Arity Checker} After the program assigns an arrow function to
+\jscode{f}, it calls the function with an argument \jscode{true}.  During the
+initialization of a function call, the \textbf{IteratorBindingInitialization}
+algorithm is evaluated with additional parameters \textit{iteratorRecord} and
+\textit{environment} to assigns arguments to proper parameters.  However, a
+contributor missed the additional parameters at line 2 in the
+\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September
+6, 2018.  It caused an arity mismatch bug and lasted for 532 days until another
+contributor fixed this bug on February 20, 2020.  The arity checker checks such
+arity mismatches.
+
+\paragraph{Assertion Checker} During the initialization of the function call,
+another specification bug existed in \textbf{IteratorBindingInitialization} of
+\textit{FormalParameter}.  The additional \textit{environment} parameter might
+contains \jscode{undefined} or an environment record exactly same with
+\textit{originalEnv} as described in the assertion at line 5.  However, a
+contributor initially added the assertion without considering of
+\jscode{undefined} on \inred{XXXXXX XX, XXXX}.  Thus, the assertion failure bug
+lasted for \inred{XXXX} days until April 10, 2019.  The assertion checker checks
+whether such assertions are failed or not.
+
+\paragraph{Operand Type Checker} The last checker checks whether operand types
+are correct for typed operators.  After the function call initialization, the
+parameter \jscode{x} points to \jscode{true} thus \jscode{Math.round} is invoked
+with the argument \jscode{true}.  The \jscode{Math.round} built-in library
+first converts the given parameter \textit{x} to the corresponding number value
+\textit{n} using \textbf{ToNumber} algorithm, and then performs remaining steps
+using the number value \textit{n}.  However, a contributor made a mistake of
+using \textit{x} instead of \textit{n} at line 3 and 4 on September 11 2020.
+According to this specification, the specification tries to compare a boolean
+value \jscode{true} with a numeric value 0.5 or 0 in the example JavaScript
+program.  Fortunately, another contributor fixed this bug after two days.  In
+the bug detector, the operand type checker detects whether the operand types are
+compatible with the typed operators.
+
+In the remainder of this paper, we explain the details of how to perform type
+analysis for $\ires$ functions (Section~\ref{sec:analysis}) and how to detect
+type-related specification bugs using four different checkers
+(Section~\ref{sec:checker}).  After we evaluate $\tool$
+(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
+and conclude (Section~\ref{sec:conclusion}).

### 2021-04-08 paper/ase21/overview.tex
[ASE21] Updated overview

@@
 other pairs based on abstract semantics, and pushes them to the worklist.  The
-iteration will be finished when the worklist becomes empty.
+iteration will be finished when the worklist becomes empty.  Moreover, to reduce
+false alarms by increasing the analysis precision, we perform refinement for
+abstract environment when the current control point is a branch or an assertion.
+The refinement will be described in detail in Section~\ref{sec:refine}.
 
@@
 In the remainder of this paper, we explain the details of how to perform type
-analysis for $\ires$ functions (Section~\ref{sec:analysis}) and how to detect
-type-related specification bugs using four different checkers
-(Section~\ref{sec:checker}).  After we evaluate $\tool$
-(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
-and conclude (Section~\ref{sec:conclusion}).
+analysis for $\ires$ functions and how to increase analysis precision using
+refinement (Section~\ref{sec:analysis}) and how to detect type-related
+specification bugs using four different checkers (Section~\ref{sec:checker}).
+After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
+(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).

### 2021-04-09 paper/ase21/analyzer.tex
[ASE21] Till 3.1 without Figure 3 and subtype example

\section{Type Analyzer}\label{sec:analyzer}

In this section, we explain the detail of the type analyzer of $\tool$. We first
formally define a modified $\ires$ and explain how to perform type analysis
for the modified $\ires$.  Besides, we explain a refinement of type analysis
based on conditions of assertions and branches to increase analysis precision.

\subsection{Intermediate Representation}\label{sec:ires}

$\ires$ is an untyped intermediate representation introduced by \citet{jiset}.
For brevity, we formally define a modified $\ires$ as follows:
\[
  \begin{array}{lr@{~}r@{~}l}
    \text{Instructions}
    & \inst &::=&
    \kwlet \; \x = \expr \mid
    \kwlet \; \x = \kwrl \expr \; \expr^* \kwrr \mid
    \kwassert \; \expr \\

    &&\mid&
    \kwif \; \expr \; \lab \; \lab \mid
    \kwreturn \; \expr \mid
    \refer = \expr \\

    \text{References}
    & \refer &::=&
    \x \mid
    \refer \kwsl \expr \kwsr \\

    \text{Expressions}
    & \expr &::=&
    \tname \kwcl [\x \kwarrow \expr]^* \kwcr \mid
    \expr: \ty \mid
    \refer \kwexists \mid
    \expr \bop \expr \mid
    \uop \expr \mid
    \refer \mid
    \const \mid
    \prim \\

    \text{Primitives}
    & \prim &::=&
    \undefval \mid \nullval \mid \bool \mid
    \num \mid \bigint \mid \str \mid \symb \\

    \text{Types}
    & \ty &::=& \tname \mid \tjs \mid \tprim \mid
    \undefval \mid \nullval \mid \tbool\\

    &&\mid&
    \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
  \end{array}
\]
A modified $\ires$ program $\prog = (\getlab, \nextlab)$ is a pair of two finite
mappings. The getter mapping $\getlab: \labset \finmap \instset$ represents
instructions attached to labels, and the next mapping $\nextlab: \labset \finmap
\labset$ denotes next labels. A label $\lab \in \labset$ denotes a program
point.  An instruction $\inst$ is a variable declaration, a function call, an
assertion, a branch, a return, or an reference update.  Each invocation of an
abstract algorithm in ECMAScript is compiled to a function call instruction with
a newly introduced temporal variable.  We represent loops using branch
instructions with cyclic pointing of labels in the next mapping $\nextlab$.  A
reference $\refer$ is a variable $\x$ or a field access $\refer \kwsl \expr
\kwsr$.  An expression $\expr$ is a record, a type check, an existence check, a
binary operation, a unary operation, a reference, a constant, or a primitive,
which is either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a
BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{img/overall}
  \vspace*{-1.5em}
  \caption{The subtype relation $\subtype$ between types.}
  \label{fig:subtype}
  \vspace*{-1.5em}
\end{figure}

A type $\ty \in \tyset$ is a norminal type $\tname$ or a pre-defined type;
$\tjs$ denotes JavaScript values, $\tprim$ primitives, $\tnumeric$ either Number
or BigInt values, and $\tnum$, $\tbigint$, $\tstr$, and $\tsymb$ denote Number,
BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is a
production name for ASTs or a record type name used in abstract algorithms.  The
subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  For
example, \inred{name and subtype example using 14.1.19 in Figure 2}.  Based on
this subtype relation, a type check expression $\expr: \ty$ checks whether the
evaluation result of $\expr$ has a type $\ty' \subtype \ty$.

\subsection{Type Analysis}\label{sec:analysis}

\subsection{Refinement}\label{sec:refine}

### 2021-04-09 paper/ase21/overview.tex
[ASE21] Till 3.1 without Figure 3 and subtype example

@@
 ECMAScript.  For brevity, we will formally define syntax and semantics of
-a simplified $\ires$ in Section~\ref{sec:ires}.
+a modified $\ires$ in Section~\ref{sec:ires}.
 
@@
 analysis for $\ires$ functions and how to increase analysis precision using
-refinement (Section~\ref{sec:analysis}) and how to detect type-related
+refinement (Section~\ref{sec:analyzer}) and how to detect type-related
 specification bugs using four different checkers (Section~\ref{sec:checker}).

### 2021-04-09 paper/ase21/intro.tex
[ASE21] Added subtype figure

@@
 \textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
-records might be abrupt or not.  For example, $\code{"Assert: Type(O) is
-Object"}$ denotes that the variable $\code{O}$ always has $\code{Object}$ values
-at this point and $\code{"? GetV(V, P)"}$ denotes that return values of
-$\code{GetV(V, P)}$ might be abrupt completions.  Moreover, they recently
-started the internal discussion of manual type annotations for variables,
-parameters, and return values for each abstract algorithm.  However, to manually
-annotate types for all of them without any automated tool is also
-labor-intensive and error-prone.  Furthermore, even though the such manual type
-annotations can give more information for manual checking of specification
-updates, it still does not provide any automatic approach to detect
-specification bugs.
+records might be abrupt or not.  For example, ``Assert: Type(\textit{O}) is
+Object'' denotes that the variable $\textit{O}$ always has an Object value at
+this point and ``? \textbf{GetV}(\textit{V}, \textit{P})'' denotes that return
+values of \textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions.
+Moreover, they recently started the internal discussion of manual type
+annotations for variables, parameters, and return values for each abstract
+algorithm.  However, to manually annotate types for all of them without any
+automated tool is also labor-intensive and error-prone.  Furthermore, even
+though the such manual type annotations can give more information for manual
+checking of specification updates, it still does not provide any automatic
+approach to detect specification bugs.
 

### 2021-04-11 paper/ase21/analyzer.tex
[ASE21] Added subtype figure
[ASE21] A small change in 3.1

@@
 $\ires$ is an untyped intermediate representation introduced by \citet{jiset}.
-For brevity, we formally define a modified $\ires$ as follows:
+To make it more suitable for type analysis, we modify it as a label-based
+language as follows:
 \[
-  \begin{array}{lr@{~}r@{~}l}
+  \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
+    \text{Functions}
+    &\funcset&\ni&\func&::=&\kwdef \; \x (\x^*, \x^*). \; \lab\\
+
     \text{Instructions}
-    & \inst &::=&
+    &\instset&\ni&\inst&::=&
     \kwlet \; \x = \expr \mid
@@
 
-    &&\mid&
+    &&&&\mid&
     \kwif \; \expr \; \lab \; \lab \mid
@@
     \text{References}
-    & \refer &::=&
+    &&&\refer&::=&
     \x \mid
@@
     \text{Expressions}
-    & \expr &::=&
-    \tname \kwcl [\x \kwarrow \expr]^* \kwcr \mid
+    &&&\expr&::=&
+    \tname^? \; \kwcl [\x: \expr]^* \kwcr \mid
+    \kwsl \expr^* \kwsr \mid
     \expr: \ty \mid
-    \refer \kwexists \mid
+    \refer \kwexists \\
+
+    &&&&\mid&
     \expr \bop \expr \mid
-    \uop \expr \mid
+    \uop \; \expr \mid
     \refer \mid
@@
     \text{Primitives}
-    & \prim &::=&
+    &\primset&\ni&\prim&::=&
     \undefval \mid \nullval \mid \bool \mid
@@
     \text{Types}
-    & \ty &::=& \tname \mid \tjs \mid \tprim \mid
+    &\tyset&\ni&\ty&::=&\tname \mid \tjs \mid \tprim \mid
     \undefval \mid \nullval \mid \tbool\\
 
-    &&\mid&
+    &&&&\mid&
     \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
@@
 \]
-A modified $\ires$ program $\prog = (\getlab, \nextlab)$ is a pair of two finite
-mappings. The getter mapping $\getlab: \labset \finmap \instset$ represents
-instructions attached to labels, and the next mapping $\nextlab: \labset \finmap
-\labset$ denotes next labels. A label $\lab \in \labset$ denotes a program
-point.  An instruction $\inst$ is a variable declaration, a function call, an
-assertion, a branch, a return, or an reference update.  Each invocation of an
-abstract algorithm in ECMAScript is compiled to a function call instruction with
-a newly introduced temporal variable.  We represent loops using branch
-instructions with cyclic pointing of labels in the next mapping $\nextlab$.  A
-reference $\refer$ is a variable $\x$ or a field access $\refer \kwsl \expr
-\kwsr$.  An expression $\expr$ is a record, a type check, an existence check, a
-binary operation, a unary operation, a reference, a constant, or a primitive,
-which is either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a
-BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.
+A modified $\ires$ program $\prog = (\funcs, \getlab, \nextlab)$ is a triple of
+a set of functions $\funcs \subseteq \and \funcset$ and two finite mappings
+$\getlab$ and $nextlab$.  The getter mapping $\getlab: \labset \finmap \instset$
+represents instructions attached to labels, and the next mapping $\nextlab:
+\labset \finmap \labset$ denotes next labels.  A function $\kwdef \; \f (\x^*,
+\y^*). \; \lab \in \funcset$ consists of a name $\f$, normal parameters $\x^*$,
+optional parameters $\y^*$, and a body label $\lab$.  A label $\lab \in \labset$
+denotes a program point.  An instruction $\inst$ is a variable declaration, a
+function call, an assertion, a branch, a return, or an reference update.  Each
+invocation of an abstract algorithm in ECMAScript is compiled to a function call
+instruction with a newly introduced temporal variable.  We represent loops using
+branch instructions with cyclic pointing of labels in the next mapping
+$\nextlab$.  A reference $\refer$ is a variable $\x$ or a field access $\refer
+\kwsl \expr \kwsr$.  An expression $\expr$ is a record, a list, a type check, an
+existence check, a binary operation, a unary operation, a reference, a constant,
+or a primitive, which is either $\undefval$, $\nullval$, a Boolean $\bool$, a
+Number $\num$, a BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.
 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/overall}
+  \includegraphics[width=0.48\textwidth]{img/subtype}
   \vspace*{-1.5em}
-  \caption{The subtype relation $\subtype$ between types.}
+  \caption{A graphical representation of subtype relation $\subtype$.}
   \label{fig:subtype}
@@
 described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
-denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  For
-example, \inred{name and subtype example using 14.1.19 in Figure 2}.  Based on
-this subtype relation, a type check expression $\expr: \ty$ checks whether the
-evaluation result of $\expr$ has a type $\ty' \subtype \ty$.
+denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
+subtype relation is dependent on the syntax and defined record types in
+ECMAScript.  We manually model subtypes between record types but automatically
+extract subtypes for AST types.  For example, consider the syntax-directed
+abstract algorithm at the right bottom in Figure~\ref{fig:example}.  The
+non-terminal \textit{BindingElement} is the unique token in a alternative of
+\textit{FormalParameter} thus we automatically extract the subtype relation:
+\textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on this
+subtype relation, a type check expression $\expr: \ty$ checks whether the
+evaluation result of $\expr$ has a type $\ty'$ satisfying $\ty' \subtype \ty$.
+We represent semantics of the modified $\ires$ as a state transition system
+$(\stset, \trans, \istset)$ with the transition relation $\trans \subseteq
+\stset \times \stset$.  For presentation brevity, we omit its detail in this
+paper and include it in a companion report~\inred{\cite{report}}.
+% \[
+%   \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
+%     \text{States}
+%     &\st&\in&\stset&::=&\ctxtset^* \times \labset \times \envset\\
+% 
+%     \text{Contexts}
+%     &\ctxt$\in$\ctxtset&::=&\labset \times \varset \times \envset\\
+% 
+%     \text{Environments}
+%     &\env$\in$\envset&::=&\varset \finmap \valset\\
+% 
+%     \text{Values}
+%     &\val$\in$\valset&::=& \addrset \uplus \addr \uplus \primset\\\
+%   \end{array}
+% \]
 
@@
 
+Abstract Interpretation~\cite{ai1977, ai1992}
+
+\begin{figure*}[t]
+  \centering
+  \[
+    \todo
+  \]
+  \vspace*{-1em}
+  \caption{Abstract .}
+  \label{fig:example}
+\end{figure*}
+
 \subsection{Refinement}\label{sec:refine}

### 2021-04-11 paper/ase21/intro.tex
[ASE21] A small change in 3.1

@@
 abstract syntax trees (ASTs), internal records (i.e. environments, completions,
-or property descriptors), and internal lists.  Our tool extract syntax and
-table-based type information from ECMAScript and constructs type hierarchy and
-fields for ASTs and records.  Based on the extracted types, $\tool$ performs
-type analysis and detects specification bugs using a \textit{bug detector}
-consisting of four different checkers: 1) reference checker, 2) arity checker,
-and 3) assertion checker, 4) operand type checker.  Moreover, to increase
-precision of type analysis, we also present \textit{condition-based refinement}
-for type analysis on ECMAScript. Its main concept is to prunes out infeasible
-abstract states by using conditions of assertions and branches.  The refinement
-technique can reduce false alarms caused by spurious types inferred by imprecise
-analysis.  We evaluate our tool with all \inred{XXX} different versions existed
-in the official ECMAScript repository for the recent \inred{three years from
-2018 to 2021}.
+or property descriptors), and internal list-like structures.  Our tool extract
+syntax and table-based type information from ECMAScript and constructs type
+hierarchy and fields for ASTs and records.  Based on the extracted types,
+$\tool$ performs type analysis and detects specification bugs using a
+\textit{bug detector} consisting of four different checkers: 1) reference
+checker, 2) arity checker, and 3) assertion checker, 4) operand type checker.
+Moreover, to increase precision of type analysis, we also present
+\textit{condition-based refinement} for type analysis on ECMAScript. Its main
+concept is to prunes out infeasible abstract states by using conditions of
+assertions and branches.  The refinement technique can reduce false alarms
+caused by spurious types inferred by imprecise analysis.  We evaluate our tool
+with all \inred{XXX} different versions existed in the official ECMAScript
+repository for the recent \inred{three years from 2018 to 2021}.
 

### 2021-04-12 paper/ase21/analyzer.tex
[ASE21] temporal dump

@@
 In this section, we explain the detail of the type analyzer of $\tool$. We first
-formally define a modified $\ires$ and explain how to perform type analysis
-for the modified $\ires$.  Besides, we explain a refinement of type analysis
+formally define a modified $\ires$ and explain how to perform type analysis for
+the modified $\ires$.  Moreover, we also explain a refinement of type analysis
 based on conditions of assertions and branches to increase analysis precision.
@@
 language as follows:
+\small
 \[
@@
     &&&\expr&::=&
-    \tname^? \; \kwcl [\x: \expr]^* \kwcr \mid
-    \kwsl \expr^* \kwsr \mid
+    \tname \; \kwcl [\x: \expr]^* \kwcr \mid
+    \clist{\expr^*} \mid
     \expr: \ty \mid
@@
     \text{Types}
-    &\tyset&\ni&\ty&::=&\tname \mid \tjs \mid \tprim \mid
-    \undefval \mid \nullval \mid \tbool\\
+    &\tyset&\ni&\ty&::=&\tname \mid \clist{} \mid \clist{\ty} \mid \tjs \mid
+    \tprim \mid \undefval \mid \nullval\\
 
     &&&&\mid&
-    \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
+    \tbool \mid \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
   \end{array}
@@
 or BigInt values, and $\tnum$, $\tbigint$, $\tstr$, and $\tsymb$ denote Number,
-BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is a
-production name for ASTs or a record type name used in abstract algorithms.  The
-subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
+BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is
+either 1) a \textit{production type} for ASTs or 2) a \textit{record type} name
+used in abstract algorithms, and ECMAScript describes its fields with
+pre-defined or possible values.  A production type has corresponding
+syntax-directed algorithms as its fields and a record type has specific fields
+with possible values described in the corresponding table in ECMAScript.  For
+example, the ``Table 10: References Record Fields'' in 
+``Reference'' record has
+
+Each norminal type has own fields 
+ECMAScript describes fields of each norminal type with their possible values in
+table structures ad
+scattered tables or syntax-directed algorithms
+tables or 
+It has pre-defined fields
+It has fields
+
+The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
 described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
@@
 We represent semantics of the modified $\ires$ as a state transition system
-$(\stset, \trans, \istset)$ with the transition relation $\trans \subseteq
-\stset \times \stset$.  For presentation brevity, we omit its detail in this
+$(\dom, \trans, \ielemset)$ with the transition relation $\trans \subseteq
+\dom \times \dom$.  For presentation brevity, we omit its detail in this
 paper and include it in a companion report~\inred{\cite{report}}.
@@
 %     \text{States}
-%     &\st&\in&\stset&::=&\ctxtset^* \times \labset \times \envset\\
+%     &\elem&\in&\dom&::=&\ctxtset^* \times \labset \times \envset\\
 % 
@@
 
-Abstract Interpretation~\cite{ai1977, ai1992}
+We design a type analysis for the modified $\ires$ based on abstract
+interpretation framework~\cite{ai1977, ai1992} with analysis
+sensitivity~\cite{sens-toplas}.  We first extend types $\tyset$ to $\etyset$ as
+follows:
+\[
+  \etyset \ni \ety ::=
+  \ty \mid
+  \func \mid
+  \const \mid
+  \tnormal(\ety) \mid
+  \tabrupt \mid
+  \bool \mid
+  \str \mid
+  \tabsent
+\]
+There are three different extensions; we add 1) functions and constants
+because the original types $\tyset$ do not cover them, 2) normal completions
+$\tnormal(\ety)$, abrupt completions $\tabrupt$, Boolean values $\bool$, and
+String values $\str$ to increase the precision of type analysis. and 3) the
+absent type $\tabsent$ to represent the existence of variables.  Using such
+extended types, we define abstract states with flow-sensitivity and
+type-sensitivity for parameters as follows:
+\[
+  \begin{array}{lr@{~}c@{~}c@{~}r@{~}l}
+    \text{Abstract States}
+    &\aelem&\in&\adom&=&
+    \viewset \rightarrow (\aenvset \times \partsof{\viewset})\\
+
+    \text{Views}
+    &\view&\in&\viewset&=&
+    (\labset \times \etyset^*) \uplus
+    (\funcset \times \etyset^*)\\
+
+    \text{Abstract Environments}
+    &\aenv&\in&\aenvset&=&\varset \rightarrow \atyset\\
+
+    \text{Abstract Types}
+    &\aty&\in&\atyset&=&\partsof{\etyset}\\
+  \end{array}
+\]
+An abstract state $\aelem \in \adom$ is a mapping from views to pairs of
+abstract environments and next views.  A view $\view$ is a pair of a label for
+the flow-sensitivity and a
+sequence of extended types for the type-sensitivity for parameters.  An abstract
+environment $\aenv \in \aenvset$ is a mapping from variables to abstract types
+and an abstract type is a set of extended types.
 
@@
   \centering
+  \begin{subfigure}[b]{0.48\textwidth}
     \[
-    \todo
+      \begin{array}{r@{~}c@{~}l}
+        \asem{\kwlet \; \x = \expr}
+        ((\lab, \overline{\ety}), \aenv)(\aelem)
+        &=& \todo \\
+
+        \asem{\kwlet \; \x = \kwrl \expr_0 \; \expr_1 \cdots \expr_n \kwrr}
+        ((\lab, \overline{\ety}), \aenv)(\aelem)
+        &=& \todo \\
+
+        \asem{\kwassert \; \expr}
+        ((\lab, \overline{\ety}), \aenv)(\aelem)
+        &=& \todo \\
+
+        \asem{\kwif \; \expr \; \lab_0 \; \lab_1}
+        ((\lab, \overline{\ety}), \aenv)(\aelem)
+        &=& \todo \\
+
+        \asem{\kwreturn \; \expr}
+        ((\lab, \overline{\ety}), \aenv)(\aelem)
+        &=& \todo \\
+
+        \asem{\refer = \expr}
+        ((\lab, \overline{\ety}), \aenv)(\aelem)
+        &=& \todo \\
+      \end{array}
     \]
-  \vspace*{-1em}
-  \caption{Abstract .}
+    \caption{Instructions with $\asem{\inst}: (\viewset \times
+    \aenvset) \rightarrow \adom \rightarrow \adom$}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.48\textwidth}
+    \[
+      \begin{array}{r@{~}c@{~}l}
+        \tname^? \; \kwcl [\x: \expr]^* \kwcr
+        \clist{\expr^*}
+        \expr: \ty
+        \refer \kwexists
+        \expr \bop \expr
+        \uop \; \expr
+        \refer
+        \const
+        \prim
+      \end{array}
+    \]
+    \caption{Expressions with $\asem{\expr}: (\viewset \times \aenvset)
+    \rightarrow \atyset$}
+  \end{subfigure}
+  \caption{Abstract semantics of $\ires$ components.}
   \label{fig:example}

### 2021-04-12 paper/ase21/overview.tex
[ASE21] A small change in 3.1
[ASE21] temporal dump

@@
 them to functions of $\ires$, an untyped intermediate representation for
-ECMAScript.  For brevity, we will formally define syntax and semantics of
-a modified $\ires$ in Section~\ref{sec:ires}.
+ECMAScript.  We modify $\ires$ to make it more suitable for type analysis, and
+formally define its syntax and semantics in Section~\ref{sec:ires}.
 
 \paragraph{Types} In ECMAScript, types denote not only JavaScript types but also
-specification types for ASTs, internal records, and internal lists.  For ASTs,
-we use non-terminal names as thier type names and AST types $A$ and $B$ have a
-subtype relation $A \subtype B$ when $A$ is an alternative of $B$.  If record
-types have names, we treat them as normal types and manually define their fields
-according to the latest version of ECMAScript.  For example, fields of the
-\code{Realm} record types are defined in ``Table 23: Realm Record Fields'' in
-ECMAScript.  Ohterwise, we define structural types for unnamed record types.
-For lists, we define \code{Nil} types for empty lists and parametric list types
-\code{List[T]} for lists whose elements have \code{T} type.
+specification types for ASTs, records, and lists.  In abstract algorithms, ASTs
+are also values thus they can be stored in the variables or passed as arguments.
+For such ASTs, we use their production names as their types and automatically
+link corresponding syntax-directed algorithms to them as their fields.
+ECMAScript also supports various record types and their fields and possible
+values are defined in the corresponding tables.  For example, fields of the
+``Realm'' record type are defined in ``Table 23: Realm Record Fields'' in
+ECMAScript.  The latests version of ECMAScriptThe contains tens of tables for
+record types and they are backward compatible in general.  Thus, we manually
+model them to use them in type analysis.  For lists, we define the empty list
+type $\clist{}$ and parametric list types $\clist{\tau}$.
 
@@
 
-The type analyzer performs flow-sensitive type analysis with type-sensitivity
-for parameters to precisely detect specification bugs.  It consists of two
-sub-modules: an \textit{analysis initializer} and an \textit{abstract transfer}.
-We use a stack-based worklist algorithm to calculate fixpoint of abstract
-transfer and assign the initial set of worklist using analysis initializer.
+The type analyzer performs type analysis with flow-sensitivity and
+type-sensitivity for parameters to precisely detect specification bugs.  It
+consists of two sub-modules: an \textit{analysis initializer} and an
+\textit{abstract transfer}.  We use a stack-based worklist algorithm to
+calculate fixpoint of abstract transfer and assign the initial set of worklist
+using analysis initializer.
 

### 2021-04-12 paper/ase21/analyzer.tex
[ASE21] Figure 5 - abstract semantics

--- 2021-04-11 paper/ase21/analyzer.tex
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.48\textwidth]{img/record-fields-table}
+  \vspace*{-1.5em}
+  \caption{Fields of completion records in ES11.}
+  \label{fig:record-fields-table}
+  \vspace*{-1.5em}
+\end{figure}
+
 $\ires$ is an untyped intermediate representation introduced by \citet{jiset}.
@@
     \kwlet \; \x = \expr \mid
-    \kwlet \; \x = \kwrl \expr \; \expr^* \kwrr \mid
+    \x = \kwrl \expr \; \expr^* \kwrr \mid
     \kwassert \; \expr \\
@@
     \text{Types}
-    &\tyset&\ni&\ty&::=&\tname \mid \tjs \mid \tprim \mid
-    \undefval \mid \nullval \mid \tbool\\
+    &\tyset&\ni&\ty&::=&\tname \mid \clist{} \mid \clist{\ty} \mid \tjs \mid
+    \tprim \mid \undefval \mid \nullval\\
 
     &&&&\mid&
-    \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
+    \tbool \mid \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
   \end{array}
 \]
-A modified $\ires$ program $\prog = (\funcs, \getlab, \nextlab)$ is a triple of
-a set of functions $\funcs \subseteq \and \funcset$ and two finite mappings
-$\getlab$ and $nextlab$.  The getter mapping $\getlab: \labset \finmap \instset$
-represents instructions attached to labels, and the next mapping $\nextlab:
-\labset \finmap \labset$ denotes next labels.  A function $\kwdef \; \f (\x^*,
-\y^*). \; \lab \in \funcset$ consists of a name $\f$, normal parameters $\x^*$,
-optional parameters $\y^*$, and a body label $\lab$.  A label $\lab \in \labset$
-denotes a program point.  An instruction $\inst$ is a variable declaration, a
-function call, an assertion, a branch, a return, or an reference update.  Each
-invocation of an abstract algorithm in ECMAScript is compiled to a function call
-instruction with a newly introduced temporal variable.  We represent loops using
-branch instructions with cyclic pointing of labels in the next mapping
-$\nextlab$.  A reference $\refer$ is a variable $\x$ or a field access $\refer
-\kwsl \expr \kwsr$.  An expression $\expr$ is a record, a list, a type check, an
-existence check, a binary operation, a unary operation, a reference, a constant,
-or a primitive, which is either $\undefval$, $\nullval$, a Boolean $\bool$, a
-Number $\num$, a BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.
+
+A modified $\ires$ program $\prog = (\getfunc, \getlab, \getnext)$ is consists
+of three mappings from labels;  $\getfunc: \labset \rightarrow \funcset$
+represents that labels are in which functions, $\getlab: \labset \rightarrow
+\instset$ represents instructions attached to labels, and $\getnext: \labset
+\rightarrow \labset$ denotes next labels where a label $\lab \in \labset$
+denotes a program point.  function $\kwdef \; \f (\x^*, \y^*). \; \lab \in
+\funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
+parameters $\y^*$, and a body label $\lab$.  Although global variables exist in
+ECMAScript, we assume that only local variables exist in this paper for brevity
+An instruction $\inst$ is a variable declaration, a function call, an assertion,
+a branch, a return, or an reference update.  Each invocation of an abstract
+algorithm in ECMAScript is compiled to a function call instruction with a newly
+introduced temporal variable.  We represent loops using branch instructions with
+cyclic pointing of labels in the next mapping $\getnext$.  A reference $\refer$
+is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  An expression
+$\expr$ is a record, a list, a type check, an existence check, a binary
+operation, a unary operation, a reference, a constant, or a primitive, which is
+either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a BigInt
+$\bigint$, a String $\str$, or a Symbol $\symb$.
 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/subtype}
+  \includegraphics[width=0.4\textwidth]{img/subtype}
   \vspace*{-1.5em}
@@
 or BigInt values, and $\tnum$, $\tbigint$, $\tstr$, and $\tsymb$ denote Number,
-BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is a
-production name for ASTs or a record type name used in abstract algorithms.  The
-subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
+BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is
+either 1) a \textit{production type} for ASTs or 2) a \textit{record type} used
+in abstract algorithms, and ECMAScript describes its fields with pre-defined or
+possible values.  A production type has corresponding syntax-directed algorithms
+as its fields and a record type has specific fields with possible values
+described in the corresponding table and additional description in ECMAScript.
+The production type is automatically extracted but we manually model fields of
+record types.  For example, Figure~\label{fig:record-fields-table} is an excerpt
+from ES11 that describes fields of completion
+records~\footnote{https://262.ecma-international.org/11.0/\#table-8}; it
+contains three fields ``Type'' with a constant such as \code{normal}, ``Value''
+with JavaScript values or an constant \code{empty}, and ``Target'' with String
+values or \code{empty}.  We model them as follows:
+\small
+\[
+  \begin{array}{l}
+    \text{Completion} = \kwcl\\
+    \quad \text{Type}: \kwcl \nconst{normal}, \nconst{break}, \nconst{continue},
+    \nconst{return}, \nconst{throw} \kwcr\\
+    \quad \text{Value}: \kwcl \tjs, \nconst{empty} \kwcr\\
+    \quad \text{Target}: \kwcl \tstr, \nconst{empty} \kwcr\\
+    \kwcr\\
+  \end{array}
+\]
+
+The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
 described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
@@
 subtype relation is dependent on the syntax and defined record types in
-ECMAScript.  We manually model subtypes between record types but automatically
-extract subtypes for AST types.  For example, consider the syntax-directed
+ECMAScript.  We extract subtypes for production types and manually model
+subtypes between record types.  For example, consider the syntax-directed
 abstract algorithm at the right bottom in Figure~\ref{fig:example}.  The
 non-terminal \textit{BindingElement} is the unique token in a alternative of
-\textit{FormalParameter} thus we automatically extract the subtype relation:
-\textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on this
-subtype relation, a type check expression $\expr: \ty$ checks whether the
+\textit{FormalParameter} production thus we automatically extract the subtype
+relation: \textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on
+this subtype relation, a type check expression $\expr: \ty$ checks whether the
 evaluation result of $\expr$ has a type $\ty'$ satisfying $\ty' \subtype \ty$.
-We represent semantics of the modified $\ires$ as a state transition system
-$(\stset, \trans, \istset)$ with the transition relation $\trans \subseteq
-\stset \times \stset$.  For presentation brevity, we omit its detail in this
-paper and include it in a companion report~\inred{\cite{report}}.
+
+We define a denotational semantics of the modified $\ires$ for instructions
+$\sem{\inst}: \dom \rightarrow \dom$ and expressions $\sem{\expr}: \dom
+\rightarrow \valset$.  For presentation brevity, we omit it in this paper and
+include it in a companion report~\inred{\cite{report}}.
 % \[
@@
 
-Abstract Interpretation~\cite{ai1977, ai1992}
-
 \begin{figure*}[t]
   \centering
+  \begin{subfigure}[b]{\textwidth}
     \[
-    \todo
+      \begin{array}{r@{~}c@{~}ll}
+        \asemi{\kwlet \; \x = \expr}
+        (\lab, \tys, \aenv, \_) &=&
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv_\x \}, \emp) &
+        \text{where} \;
+        \aenv_\x = \aenv[\x \mapsto \aty] \wedge
+        \aty = \aseme{\expr}(\aenv)\\
+
+        \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_n \kwrr}
+        (\lab, \tys, \aenv, \_) &=&
+        \left(
+          \begin{array}{@{}l@{}}
+            \{ (\lab_\func, \tys_a) \mapsto \aenv_{\func, \tys_a} \mid \func \in
+              F \wedge \tys_a \in T_a
+            \},\\
+            \{ (\func, \tys_a) \mapsto \{ (\getnext(\lab), \tys, \x) \} \mid
+              \func \in F \wedge \tys_a \in T_a
+            \}\\
+          \end{array}
+        \right) &
+        \text{where} \;
+        \left\{
+          \begin{array}{@{}l@{}}
+            \aty_i = \aseme{\expr_i}(\aenv) \wedge T_a = \{ \upcasts([ \ty_1,
+            \cdots, \ty_n ] \mid \ty_i \in \aty_i \} \wedge\\
+            F = \{ \func \in \aty_0 \mid \func = \kwdef \; \_ (\p_1, \cdots,
+            \p_m). \; \lab_\func \} \wedge\\
+            \aenv_{\func, \tys_a} = \aenv[\p_1 \mapsto \{ \tys_a[1] \}, \cdots,
+            \p_m \mapsto \{ \tys_a[m] \}]\\
+          \end{array}
+        \right.\\
+
+        \asemi{\kwassert \; \expr}
+        (\lab, \tys, \aenv, \_) &=&
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv_\mt \}, \emp) &
+        \text{where} \; \aenv_\mt = \refine(\aenv, \expr, \true)\\
+
+        \asemi{\kwif \; \expr \; \lab_\mt \; \lab_\mf}
+        (\lab, \tys, \aenv, \_) &=&
+        (\{ (\lab_\mt, \tys) \mapsto \aenv_\mt, (\lab_\mf, \tys) \mapsto
+        \aenv_\mf \}, \emp) &
+        \text{where} \;
+        \aenv_\mt = \refine(\aenv, \expr, \true) \wedge
+        \aenv_\mf = \refine(\aenv, \expr, \false)\\
+
+        \asemi{\kwreturn \; \expr}
+        (\lab, \tys, \aenv, \aelem) &=&
+        (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid (\lab_r, \tys_r, \x) \in
+        \retp(\getfunc(\lab), \tys)\}, \emp) &
+        \text{where} \;
+        \aelem = (\rmap, \retp) \wedge
+        \aenv_r = \rmap(\lab_r, \tys_r)[\x \mapsto \aty] \wedge
+        \aty = \aseme{\expr}(\aenv)\\
+
+        \asemi{\x = \expr}
+        (\lab, \tys, \aenv, \_) &=&
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv_\x \}, \emp) &
+        \text{where} \;
+        \aenv_\x = \aenv[\x \mapsto \aty] \wedge
+        \aty = \aseme{\expr}(\aenv)\\
+
+        \asemi{\refer \kwsl \expr_0 \kwsr = \expr_1}
+        (\lab, \tys, \aenv, \_) &=&
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv \}, \emp)
+      \end{array}
     \]
-  \vspace*{-1em}
-  \caption{Abstract .}
-  \label{fig:example}
+    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^* \times
+    \aenvset \times \adom) \rightarrow \adom$}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.48\textwidth}
+    \[
+      \asemr{\x}(\aenv) = \aenv(\x)
+      \qquad
+      \asemr{\refer \kwsl \expr \kwsr}(\aenv) = \{ \ty[\str] \mid \ty \in
+      \asemr{\refer}(\aenv) \wedge \str \in \aseme{\expr}(\aenv) \}
+    \]
+    \caption{References with $\asemr{\refer}: \aenvset \rightarrow \atyset$}
+  \end{subfigure}
+  \begin{subfigure}[b]{\textwidth}
+    \[
+      \begin{array}{r@{~}c@{~}lr@{~}c@{~}lr@{~}c@{~}l}
+        \aseme{\tname \; \kwcl \fields \kwcr}(\aenv)
+        &=& \multicolumn{7}{@{}l}{
+          \left\{
+            \begin{array}{ll}
+              \{ \tnormal(\ty) \mid \ty \in \aseme{\fields(\code{Value})}(\aenv)
+              \} & \text{if} \; \tname = \text{Completion} \wedge
+              \fields(\code{Type}) = \nconst{normal}\\
+
+              \{ \tabrupt \} & \text{if} \; \tname = \text{Completion} \wedge
+              \fields(\code{Type}) \neq \nconst{normal}\\
+
+              \{ \tname \} & \text{otherwise}\\
+            \end{array}
+          \right.
+          \quad \aseme{\prim}(\aenv) =
+          \left\{
+            \begin{array}{ll}
+              \{ \tnum \} & \text{if} \; \prim = \num\\
+              \{ \tbigint \} & \text{if} \; \prim = \bigint\\
+              \{ \tsymb \} & \text{if} \; \prim = \symb\\
+              \{ \prim \} & \text{otherwise}\\
+            \end{array}
+          \right.
+        }
+
+        \\
+
+        \aseme{\const}(\aenv) &=& \const &
+
+        \aseme{\clist{}}(\aenv) &=& \clist{} &
+
+        \aseme{\clist{\expr_0, \cdots, \expr_n}}(\aenv)
+        &=& \{ \clist{\ty} \mid \ty \in \bigjoin_{0 \leq i
+        \leq n} \aseme{\expr_i}(\aenv) \}
+
+        \\
+
+        \aseme{\expr: \ty}(\aenv)
+        &=& \{ \ty' \subtype \ty \mid \ty' \in
+        \aseme{\expr}(\aenv) \} &
+
+        \aseme{\refer \kwexists}(\aenv)
+        &=& \{ \ty \neq \tabsent \mid \ty \in
+        \aseme{\expr}(\aenv) \} &
+
+        \aseme{\refer}(\aenv)
+        &=& \asemr{\refer}(\aenv) \setminus \{ \tabsent \}
+
+        \\
+
+        \aseme{\uop \; \expr}(\aenv)
+        &=& \{ \abs{\uop} \ty \mid \ty \in
+        \aseme{\expr}(\aenv) \} &
+
+        \aseme{\expr_0 \bop \expr_1}(\aenv)
+        &=& \multicolumn{4}{@{}l}{\{ \ty_0 \abs{\bop} \ty_1 \mid \ty_0 \in
+        \aseme{\expr_0}(\aenv) \wedge \ty_1 \in \aseme{\expr_1}(\aenv) \}}
+
+        \\
+      \end{array}
+    \]
+    \caption{Expressions with $\aseme{\expr}: \aenvset \rightarrow \atyset$}
+  \end{subfigure}
+  \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
+  (\getfunc, \getlab, \getnext)$.}
+  \vspace*{-1.5em}
+  \label{fig:abs-sem}
 \end{figure*}
 
+We design a type analysis for the modified $\ires$ based on abstract
+interpretation framework~\cite{ai1977, ai1992} with analysis
+sensitivity~\cite{sens-toplas}.  We first extend types $\tyset$ as follows:
+\[
+  \tyset \ni \ty ::=
+  \cdots \mid
+  \func \mid
+  \const \mid
+  \tnormal(\ty) \mid
+  \tabrupt \mid
+  \bool \mid
+  \str \mid
+  \tabsent
+\]
+There are three different reasons why we extend types.  First, the original
+types $\tyset$ do not cover all types of values thus we add functions and
+constants.  Second, we add more specific types to increase the precision of type
+analysis.  A completion record is a \textit{normal completion} when its Type
+field is a constant $\nconst{normal}$ or an \textit{abrupt completion}
+otherwise.  We add $\tnormal(\ty)$ and $\tabrupt$ for normal and abrupt
+completions.  Moreover, we also add Boolean values $\bool$, and String values
+$\str$ to precisely handle the control flows of branches and field accesses,
+respectively.  Third, we add the absent type $\tabsent$ to represent the
+existence of variables.  Using such extended types, we define abstract states
+with flow-sensitivity and type-sensitivity for parameters as follows:
+\[
+  \begin{array}{lr@{~}c@{~}c@{~}r@{~}l}
+    \text{Abstract States}
+    &\aelem&\in&\adom&=& \rmapset \times \retpset\\
+
+    \text{Result Maps}
+    &\rmap&\in&\rmapset&=& \labset \times \tyset^* \rightarrow \aenvset\\
+
+    \text{Return Points}
+    &\retp&\in&\retpset&=& \funcset \times \tyset^*
+    \rightarrow \partsof{\labset \times \tyset^* \times \varset} \\
+
+    \text{Abstract Environments}
+    &\aenv&\in&\aenvset&=&\varset \rightarrow \atyset\\
+
+    \text{Abstract Types}
+    &\aty&\in&\atyset&=&\partsof{\tyset}\\
+  \end{array}
+\]
+An abstract state $\aelem \in \adom$ is pair of a return map and a return point
+mapping.  A result map $\rmap \in \rmapset$ represents an abstract environment
+for each flow-sensitive and type-sensitive view, and a return point mapping
+$\retp \in \retpset$ represents possible return points of each function with
+a type-sensitive context.  An abstract environment $\aenv \in \aenvset$
+represents possible types of each variable, and $\aenv(\x) = \{ \tabsent \}$
+when $\x$ is not defined in $\aenv$.  An abstract type $\aty \in \atyset$ is a
+set of extended types.
+
+We define the abstract semantics of the modified $\ires$ as described in
+Figure~\ref{fig:abs-sem} for a program $\prog = (\getfunc, \getlab,
+\getnext)$.
+
 \subsection{Refinement}\label{sec:refine}

### 2021-04-12 paper/ase21/overview.tex
[ASE21] Figure 5 - abstract semantics

@@
 and JavaScript parsers from its lexical and syntactic productions.  Our tool
-utilizes only AST structures to define AST types and to access corresponding
+utilizes only AST structures to define their types and to access corresponding
 syntax-directed algorithms.  For JavaScript semantics, ECMAScript contains
@@
 ECMAScript also supports various record types and their fields and possible
-values are defined in the corresponding tables.  For example, fields of the
-``Realm'' record type are defined in ``Table 23: Realm Record Fields'' in
-ECMAScript.  The latests version of ECMAScriptThe contains tens of tables for
-record types and they are backward compatible in general.  Thus, we manually
-model them to use them in type analysis.  For lists, we define the empty list
-type $\clist{}$ and parametric list types $\clist{\tau}$.
+values are defined in the corresponding tables.  For example, ``Table 9:
+Completion Record Fields'' in the latest ECMAScript describes fields of the
+completion records.  The latest version contains tens of tables for record types
+but they are backward compatible in general.  Thus, we manually model fields of
+record types based on the latest version to use them in type analysis.  For
+lists, we define the empty list type $\clist{}$ and parametric list types
+$\clist{\tau}$.
 

### 2021-04-12 paper/ase21/analyzer.tex
[ASE21] Till 3.2

@@
 
-A modified $\ires$ program $\prog = (\getfunc, \getlab, \getnext)$ is consists
+A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ is consists
 of three mappings from labels;  $\getfunc: \labset \rightarrow \funcset$
-represents that labels are in which functions, $\getlab: \labset \rightarrow
+represents that labels are in which functions, $\getinst: \labset \rightarrow
 \instset$ represents instructions attached to labels, and $\getnext: \labset
@@
 subtypes between record types.  For example, consider the syntax-directed
-abstract algorithm at the right bottom in Figure~\ref{fig:example}.  The
+abstract algorithm at the lower-right in Figure~\ref{fig:example}.  The
 non-terminal \textit{BindingElement} is the unique token in a alternative of
@@
         \asemi{\kwlet \; \x = \expr}
-        (\lab, \tys, \aenv, \_) &=&
+        (\lab, \tys)(\aelem) &=&
         (\{ (\getnext(\lab), \tys) \mapsto \aenv_\x \}, \emp) &
@@
         \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_n \kwrr}
-        (\lab, \tys, \aenv, \_) &=&
+        (\lab, \tys)(\aelem) &=&
         \left(
@@
         \asemi{\kwassert \; \expr}
-        (\lab, \tys, \aenv, \_) &=&
+        (\lab, \tys)(\aelem) &=&
         (\{ (\getnext(\lab), \tys) \mapsto \aenv_\mt \}, \emp) &
@@
         \asemi{\kwif \; \expr \; \lab_\mt \; \lab_\mf}
-        (\lab, \tys, \aenv, \_) &=&
+        (\lab, \tys)(\aelem) &=&
         (\{ (\lab_\mt, \tys) \mapsto \aenv_\mt, (\lab_\mf, \tys) \mapsto
@@
         \asemi{\kwreturn \; \expr}
-        (\lab, \tys, \aenv, \aelem) &=&
+        (\lab, \tys)(\aelem) &=&
         (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid (\lab_r, \tys_r, \x) \in
@@
         \asemi{\x = \expr}
-        (\lab, \tys, \aenv, \_) &=&
+        (\lab, \tys)(\aelem) &=&
         (\{ (\getnext(\lab), \tys) \mapsto \aenv_\x \}, \emp) &
@@
         \asemi{\refer \kwsl \expr_0 \kwsr = \expr_1}
-        (\lab, \tys, \aenv, \_) &=&
+        (\lab, \tys)(\aelem) &=&
         (\{ (\getnext(\lab), \tys) \mapsto \aenv \}, \emp)
@@
     \]
-    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^* \times
-    \aenvset \times \adom) \rightarrow \adom$}
+    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
+    \rightarrow \adom \rightarrow \adom$ where $\aenv = \aelem(\lab, \tys)$.}
   \end{subfigure}
@@
     \]
-    \caption{References with $\asemr{\refer}: \aenvset \rightarrow \atyset$}
+    \caption{References with $\asemr{\refer}: \aenvset \rightarrow \atyset$.}
   \end{subfigure}
@@
     \]
-    \caption{Expressions with $\aseme{\expr}: \aenvset \rightarrow \atyset$}
+    \caption{Expressions with $\aseme{\expr}: \aenvset \rightarrow \atyset$.}
   \end{subfigure}
   \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
-  (\getfunc, \getlab, \getnext)$.}
+  (\getfunc, \getinst, \getnext)$.}
   \vspace*{-1.5em}
@@
 when $\x$ is not defined in $\aenv$.  An abstract type $\aty \in \atyset$ is a
-set of extended types.
+set of types.  While the join operator $\join$ and the partial order $\order$
+for abstract states are defined in a point-wise manner, the operators for types
+are defined with a normalization function $\norm$ because of their subtype
+relations as follows:
+\[
+  \begin{array}{l}
+    \aty_0 \join \aty_1 = \norm(\aty_0 \cup \aty_1)\\
+    \aty_0 \order \aty_1 \Leftrightarrow \forall \ty_0 \in \aty_0. \; \exists
+    \ty_1 \in \norm(\aty_1). \; \text{s.t.} \; \ty_0 \subtype \ty_1\\
+  \end{array}
+\]
+where $\norm(\aty) = \{ \ty \mid \ty \in \aty_e \wedge \not\exists \ty' \in
+\aty_e. \; \text{s.t.} \; \ty \neq \ty' \wedge \ty \subtype \ty' \}$.
 
-We define the abstract semantics of the modified $\ires$ as described in
-Figure~\ref{fig:abs-sem} for a program $\prog = (\getfunc, \getlab,
-\getnext)$.
+Based on abstract states, we define the abstract semantics of instructions,
+references, and expressions in the modified $\ires$ described in
+Figure~\ref{fig:abs-sem}.  To prevent the explosion of the number of type-sensitive
+views, we upcast the type of each argument before function calls with the
+following function:
+\[
+  \upcast(\ty) = \left\{
+    \begin{array}{ll}
+      \tnormal(\upcast(\ty')) & \text{if} \; \ty = \tnormal(\ty')\\
+      \clist{\upcast(\ty')} & \text{if} \; \ty = \clist{\ty'}\\
+      \tstr & \text{if} \; \ty = \str\\
+      \tbool & \text{if} \; \ty = \bool\\
+      \ty & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
+For conditions, we apply the $\refine$ function that prunes out infeasible parts
+in abstract states based on given conditions to increase analysis precision.  We
+explain its detail in Section~\ref{sec:refine}.  Then, we define the abstract
+semantics $\asem{\prog}$ of a program $\prog = (\getfunc, \getinst, \getnext)$
+as the least fixpoint of abstract transfer $\atransfer: \adom \rightarrow \adom$
+as follows:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \asem{\prog} &=& \lim_{n \rightarrow \infty}(\atransfer)^n(\iaelem)\\
+    \atransfer(\aelem) &=& \aelem \join \left(
+      \underset{(\lab, \tys) \in \domain{\rmap}}{\bigjoin}
+      \asemi{\getinst(\lab)}(\lab, \tys)(\aelem)
+    \right)\\
+  \end{array}
+\]
+where $\aelem = (\rmap, \_)$ and $\iaelem$ denotes the initial abstract state.
+As described in the Section~\ref{sec:overview}, $\iaelem$ contains all
+syntax-directed algorithms having no additional parameters and built-in
+algorithms with appropriate abstract environments.  For syntax-directed
+algorithms, we construct its abstract environment containing the variable
+$\this$ with a production type and other variables for non-terminals.  For
+example, the upper-left syntax-directed algorithm in Figure~\ref{fig:example} is
+initialized with the following abstract environment:
+\[
+  \left\{
+    \begin{array}{r@{~}c@{~}l}
+      \this &\mapsto& \{ \text{AssignmentExpression} \},\\
+      \mcode{LeftHandSideExpression} &\mapsto& \{ \text{LeftHandSideExpression} \},\\
+      \mcode{AssignmentExpression} &\mapsto& \{ \text{AssignmentExpression} \}
+    \end{array}
+  \right.
+\]
+For built-in algorithms, we assign pre-defined variables $\this$, $\args$, and
+$\NewTarget$ with corresponding types and parameters with $\tjs$ types.  For
+example, the following abstract environment is for the built-in
+algorithm $\jscode{Math.round}$ at the upper-right in Figure~\ref{fig:example}:
+\[
+  \left\{
+    \begin{array}{r@{~}c@{~}l}
+      \this &\mapsto& \{ \tjs \},
+      \args \mapsto \{ \clist{\tjs} \},
+      \x \mapsto \tjs\\
+      \NewTarget &\mapsto& \{ \text{Object}, \undefval \},\\
+    \end{array}
+  \right.
+\]
 
 \subsection{Refinement}\label{sec:refine}
+
+\todo

### 2021-04-12 paper/ase21/analyzer.tex
[ASE21] Till 3.3

@@
 cyclic pointing of labels in the next mapping $\getnext$.  A reference $\refer$
-is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  An expression
-$\expr$ is a record, a list, a type check, an existence check, a binary
-operation, a unary operation, a reference, a constant, or a primitive, which is
-either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a BigInt
-$\bigint$, a String $\str$, or a Symbol $\symb$.
+is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We use the
+notation $\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An
+expression $\expr$ is a record, a list, a type check, an existence check, a
+binary operation, a unary operation, a reference, a constant, or a primitive,
+which is either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a
+BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.
 
@@
 with JavaScript values or an constant \code{empty}, and ``Target'' with String
-values or \code{empty}.  We model them as follows:
+values or \code{empty}.  We manually model them as follows:
 \small
@@
     \text{Completion} = \kwcl\\
-    \quad \text{Type}: \kwcl \nconst{normal}, \nconst{break}, \nconst{continue},
+    \quad \Type: \kwcl \nconst{normal}, \nconst{break}, \nconst{continue},
     \nconst{return}, \nconst{throw} \kwcr\\
-    \quad \text{Value}: \kwcl \tjs, \nconst{empty} \kwcr\\
-    \quad \text{Target}: \kwcl \tstr, \nconst{empty} \kwcr\\
+    \quad \Value: \kwcl \tjs, \nconst{empty} \kwcr\\
+    \quad \Target: \kwcl \tstr, \nconst{empty} \kwcr\\
     \kwcr\\
@@
 existence of variables.  Using such extended types, we define abstract states
-with flow-sensitivity and type-sensitivity for parameters as follows:
+with flow-sensitivity and type-sensitivity for parameters:
 \[
@@
 when $\x$ is not defined in $\aenv$.  An abstract type $\aty \in \atyset$ is a
-set of types.  While the join operator $\join$ and the partial order $\order$
-for abstract states are defined in a point-wise manner, the operators for types
-are defined with a normalization function $\norm$ because of their subtype
-relations as follows:
+set of types.  While we define the join operator $\join$, the meet operator
+$\meet$, and the partial order $\order$ for most of abstract domains in a
+point-wise manner, we define the operators for types with a normalization
+function $\norm$ because of their subtype relations:
 \[
@@
     \aty_0 \join \aty_1 = \norm(\aty_0 \cup \aty_1)\\
+    \aty_0 \meet \aty_1 = \norm(
+      \{\ty_0 \in \aty_0 \mid \{ \ty_0 \} \order \aty_1 \} \cup
+      \{\ty_1 \in \aty_1 \mid \{ \ty_1 \} \order \aty_0 \}
+    )\\
     \aty_0 \order \aty_1 \Leftrightarrow \forall \ty_0 \in \aty_0. \; \exists
@@
 and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
-For conditions, we apply the $\refine$ function that prunes out infeasible parts
-in abstract states based on given conditions to increase analysis precision.  We
-explain its detail in Section~\ref{sec:refine}.  Then, we define the abstract
-semantics $\asem{\prog}$ of a program $\prog = (\getfunc, \getinst, \getnext)$
-as the least fixpoint of abstract transfer $\atransfer: \adom \rightarrow \adom$
-as follows:
+For branches and assertions, we apply the $\refine$ function that prunes out
+infeasible parts in abstract environments based on their conditions to increase
+analysis precision.  We explain its detail in Section~\ref{sec:refine}.  Then,
+we define the abstract semantics $\asem{\prog}$ of a program $\prog = (\getfunc,
+\getinst, \getnext)$ as the least fixpoint of abstract transfer $\atransfer:
+\adom \rightarrow \adom$:
 \[
@@
 
-\todo
+The $\refine$ function that prunes out infeasible parts in abstract environments
+based on conditions of branches of assertions.  A simple definition is to
+prevent infeasible control flows by producing an empty abstract environment as
+follows:
+\[
+  \refine_0(\aenv, \expr, \bool) = \left\{
+    \begin{array}{ll}
+      \aenv & \text{if} \; \{ \bool \} \order \aseme{\expr}(\aenv)\\
+      \emp & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+Beyond control flows, we extend it to refine the shape of a given abstract
+environment based on the conditions for variables:
+\[
+  \refine_1(\aenv, \expr, \bool) = \aenv_0[\aenv_\x]\\
+\]
+where $\aenv_0 = \refine_0(\aenv, \expr, \bool)$ and $\aenv_\x =
+\refineVar(\aenv_0, \expr, \bool)$.  The notation $\aenv_0[\aenv_1]$ denotes
+$\{ \x \mapsto \aty \mid \text{if} (\x \in \aenv_1) \aty = \aenv_1(\x) \;
+\text{else} \; \aty = \aenv_0(\x) \}$.  The variable refinement function
+$\refineVar$ is defined as follows:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \refineVar(\emp, \_, \_) &=&
+    \emp\\
+
+    \refineVar(\aenv, \code{!} \expr, \bool) &=&
+    \refineVar(\aenv, \expr, \neg \bool)\\
+
+    \refineVar(\aenv, \expr_0 \; \code{||} \; \expr_1, \bool) &=&
+    \refineVar(\aenv, \expr_0, \bool) \; \join\\ &&
+    \refineVar(\aenv, \expr_1, \bool)\\
+
+    \refineVar(\aenv, \expr_0 \; \code{\&\&} \; \expr_1, \bool) &=&
+    \refineVar(\aenv, \expr_0, \bool) \; \meet\\ &&
+    \refineVar(\aenv, \expr_1, \bool)\\
+
+    \refineVar(\aenv, \x.\Type \code{=} \nconst{normal}, \true) &=&
+    \{ \x \mapsto \aseme{\x}(\aenv) \cap \tnormal(\tyset) \}\\
+    \refineVar(\aenv, \x.\Type \code{=} \nconst{normal}, \false) &=&
+    \{ \x \mapsto \aseme{\x}(\aenv) \cap \{ \tabrupt \} \}\\
+
+    \refineVar(\aenv, \x \code{=} \expr, \true) &=&
+    \{ \x \mapsto \aseme{\x}(\aenv) \meet \aseme{\expr}(\aenv) \}\\
+    \refineVar(\aenv, \x \code{=} \expr, \false) &=&
+    \{ \x \mapsto \aseme{\x}(\aenv) \setminus \lfloor\aseme{\expr}(\aenv)\rfloor \}\\
+
+    \refineVar(\aenv, \x : \ty, \true) &=&
+    \{ \x \mapsto \aseme{\x}(\aenv) \meet \{ \ty \} \}\\
+    \refineVar(\aenv, \x : \ty, \false) &=&
+    \{ \x \mapsto \aseme{\x}(\aenv) - \ty \}\\
+  \end{array}
+\]
+and it returns $\emp$ for other cases.  The notation $\lfloor \aty \rfloor$
+denotes to get a singleton type:
+\[
+  \lfloor \aty \rfloor = \left\{
+    \begin{array}{ll}
+      \{ \ty \} &
+      \text{if} \; \aty = \{ \ty \} \wedge \ty = \const \mid \func \mid \clist{}
+      \mid \tabsent \mid\\ & \phantom{\text{if}\; \aty = \{ \ty \} \wedge \ty=}
+      \undefval \mid \nullval \mid \bool \mid \str\\
+      \emp & \text{otherwise}
+    \end{array}
+  \right.
+\]
+
+\todo: more explanation
+
+\todo: $\refine_2$

### 2021-04-13 paper/ase21/analyzer.tex
[ASE21] Till 4.2

--- 2021-04-12 paper/ase21/analyzer.tex
@@
 formally define a modified $\ires$ and explain how to perform type analysis for
-the modified $\ires$.  Moreover, we also explain a refinement of type analysis
-based on conditions of assertions and branches to increase analysis precision.
+the modified $\ires$.  Moreover, we also explain a condition-based refinement of
+type analysis based on conditions of assertions and branches to increase
+analysis precision.
 
@@
     \text{Functions}
-    &\funcset&\ni&\func&::=&\kwdef \; \x (\x^*, \x^*). \; \lab\\
+    &\funcset&\ni&\func&::=&\kwdef \; \x (\x^*, \kwsl \x^* \kwsr). \; \lab\\
 
@@
 \rightarrow \labset$ denotes next labels where a label $\lab \in \labset$
-denotes a program point.  function $\kwdef \; \f (\x^*, \y^*). \; \lab \in
-\funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
+denotes a program point.  function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
+\lab \in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
 parameters $\y^*$, and a body label $\lab$.  Although global variables exist in
@@
 The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
-described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
+depicted in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
 denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
@@
 We define a denotational semantics of the modified $\ires$ for instructions
-$\sem{\inst}: \dom \rightarrow \dom$ and expressions $\sem{\expr}: \dom
-\rightarrow \valset$.  For presentation brevity, we omit it in this paper and
-include it in a companion report~\inred{\cite{report}}.
-% \[
-%   \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
-%     \text{States}
-%     &\elem&\in&\dom&::=&\ctxtset^* \times \labset \times \envset\\
-% 
-%     \text{Contexts}
-%     &\ctxt$\in$\ctxtset&::=&\labset \times \varset \times \envset\\
-% 
-%     \text{Environments}
-%     &\env$\in$\envset&::=&\varset \finmap \valset\\
-% 
-%     \text{Values}
-%     &\val$\in$\valset&::=& \addrset \uplus \addr \uplus \primset\\\
-%   \end{array}
-% \]
+$\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
+\rightarrow \valset$, and expressions $\sem{\expr}: \dom \rightarrow \valset$.
+For presentation brevity, we omit it in this paper and include it in a companion
+report~\inred{\cite{report}}.
 
@@
             F = \{ \func \in \aty_0 \mid \func = \kwdef \; \_ (\p_1, \cdots,
-            \p_m). \; \lab_\func \} \wedge\\
+            \kwsl \cdots, \p_m \kwsr). \; \lab_\func \} \wedge\\
             \aenv_{\func, \tys_a} = \aenv[\p_1 \mapsto \{ \tys_a[1] \}, \cdots,
@@
         (\{ (\getnext(\lab), \tys) \mapsto \aenv_\mt \}, \emp) &
-        \text{where} \; \aenv_\mt = \refine(\aenv, \expr, \true)\\
+        \text{where} \; \aenv_\mt = \refine(\expr, \true)(\aenv)\\
 
@@
         \text{where} \;
-        \aenv_\mt = \refine(\aenv, \expr, \true) \wedge
-        \aenv_\mf = \refine(\aenv, \expr, \false)\\
+        \aenv_\mt = \refine(\expr, \true)(\aenv) \wedge
+        \aenv_\mf = \refine(\expr, \false)(\aenv)\\
 
@@
 
-\subsection{Refinement}\label{sec:refine}
+\subsection{Condition-based Refinement}\label{sec:refine}
 
-\todo
+We present a \textit{condition-based refinement} of type analysis for the
+modified $\ires$ to increase analysis precision.  It prunes out infeasible parts
+in abstract environments based on conditions of branches of assertions, and we
+formally define the $\refine$ function as a composition of two functions
+$\refineFlow$ and $\refineVar$:
+\[
+  \refine(\expr, \bool) =
+  \refineVar(\expr, \bool) \circ \refineFlow(\expr, \bool)
+\]
+The $\refineFlow$ prevents infeasible \textit{control flows} by producing an
+empty abstract environment as follows:
+\[
+  \refineFlow(\expr, \bool)(\aenv) = \left\{
+    \begin{array}{ll}
+      \aenv & \text{if} \; \{ \bool \} \order \aseme{\expr}(\aenv)\\
+      \emp & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+Beyond control flows, $\refineVar$ refines the shape of a given abstract
+environment based on the conditions for variables:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \refineVar(\code{!} \expr, \bool)(\aenv) &=&
+    \refineVar(\expr, \neg \bool)(\aenv)\\
+
+    \refineVar(\expr_0 \bop \expr_1, \bool)(\aenv) &=&
+    \left\{
+      \begin{array}{ll}
+        \aenv_0 \join \aenv_1 & \text{if} \; \bool \wedge \bop = \code{||}\\
+        \aenv_0 \meet \aenv_1 & \text{if} \; \neg\bool \wedge \bop = \code{||}\\
+        \aenv_0 \meet \aenv_1 & \text{if} \; \bool \wedge \bop = \code{\&\&}\\
+        \aenv_0 \join \aenv_1 & \text{if} \; \neg\bool \wedge \bop = \code{\&\&}\\
+        \aenv & \text{otherwise}\\
+      \end{array}
+    \right.\\
+    \multicolumn{3}{r}{
+      \text{where} \;
+      \aenv_0 = \refineVar(\expr_0, \bool)(\aenv) \wedge
+      \aenv_1 = \refineVar(\expr_1, \bool)(\aenv)
+    }\\
+
+    \refineVar(\x.\Type \code{=} \nconst{normal}, \true)(\aenv) &=&
+    \aenv[ \x \mapsto \aseme{\x}(\aenv) \cap \tnormal(\tyset) ]\\
+    \refineVar(\x.\Type \code{=} \nconst{normal}, \false)(\aenv) &=&
+    \aenv[ \x \mapsto \aseme{\x}(\aenv) \cap \{ \tabrupt \} ]\\
+
+    \refineVar(\x \code{=} \expr, \true)(\aenv) &=&
+    \aenv[ \x \mapsto \aseme{\x}(\aenv) \meet \aseme{\expr}(\aenv) ]\\
+    \refineVar(\x \code{=} \expr, \false)(\aenv) &=&
+    \aenv[ \x \mapsto \aseme{\x}(\aenv) \setminus
+    \lfloor\aseme{\expr}(\aenv)\rfloor ]\\
+
+    \refineVar(\x : \ty, \true)(\aenv) &=&
+    \aenv[ \x \mapsto \aseme{\x}(\aenv) \meet \{ \ty \} ]\\
+    \refineVar(\x : \ty, \false)(\aenv) &=&
+    \aenv[ \x \mapsto \aseme{\x}(\aenv) \setminus \{ \ty' \mid \ty' \subtype \ty
+    \}]\\
+  \end{array}
+\]
+and it returns $\aenvset$ for other cases.  The notation $\getSingle{\aty}$ denotes
+to checks whether it is a singleton; $\getSingle{\aty} = \aty$ if $\aty = \{ \ty
+\}$ and $\ty$ is a singleton type such as a constant $\const$, an empty list
+$\clist{}$, an absent value $\tabsent$, a primitive value, etc., and
+$\getSingle{\aty} = \emp$ otherwise.
+
+\todo: $\refinePred$?

### 2021-04-13 paper/ase21/checker.tex
[ASE21] Overview
[ASE21] Till 4.2

@@
-\section{Static Checker}\label{sec:checker}
+\section{Bug Detector}\label{sec:checker}
+
+\begin{table}
+  \centering
+  \caption{Type-related specification bugs fixed by pull requests for the recent
+  three years from 2018 to 2021.}
+  \label{table:pr-bugs}
+  \vspace*{-1.5em}
+  \[
+    \begin{array}{c|l|r}
+      \multicolumn{1}{c}{\textbf{Category}} &
+      \multicolumn{1}{|c}{\textbf{Bug Kind}} &
+      \multicolumn{1}{|c}{\textbf{\# Bugs}}\\
+      \hline
+
+      \multirow{2}{*}{\text{Reference}}
+      & \text{Unknown Variables} & \inred{XXX}\\\cline{2-3}
+      & \text{Already Defined Variables} & \inred{XXX}\\\hline
+
+      \multirow{1}{*}{\text{Parameter}}
+      & \text{Arity Mismatches} & \inred{XXX}\\\hline
+
+      \multirow{1}{*}{\text{Assertion}}
+      & \text{Assertion Failures} & \inred{XXX}\\\hline
+
+      \multirow{2}{*}{\text{Type}}
+      & \text{Non-Numeric Operands} & \inred{XXX}\\\cline{2-3}
+      & \text{Unchecked Abrupt Completions} & \inred{XXX}\\\hline
+
+      \multicolumn{2}{c|}{\textbf{Total}} & \inred{XXX}\\
+
+    \end{array}
+  \]
+  \vspace*{-1.5em}
+\end{table}
+
+We develop a \textit{bug detector} to statically detect type-related
+specification bugs in ECMAScript using an augmented abstract transfer
+$\detector$ with additional checkers.  The abstract semantics $\asem{\prog}$ of
+a program $\prog = (\getfunc, \getinst, \getnext)$ is the least fixpoint of the
+original abstract transfer $\atransfer$.  Thus, $\detector(\asem{\prog})$ also
+produces $\asem{\prog}$ and detects type-related specification bugs.  Before
+implementing checkers, we manually investigate pull requests for the recent
+\inred{three years from 2018 to 2021}.  As described in
+Table~\ref{table:pr-bugs}, pull requests include \inred{XXX} type-related
+specification bugs classified in six different kinds and four categories.  We
+implement four checkers for each category bugs: \textit{reference checker},
+\textit{arity checker}, \textit{assertion checker}, and \textit{operand type
+checker}.  Now, we explain how each checker detects corresponding bugs in the
+augmented abstract transfer $\detector$.
 
 \subsection{Reference Checker}
-\begin{itemize}
-  \item unknown variables
-  \item already defined variables
-  \item already defined variables
-\end{itemize}
 
-\subsection{Parameter Arity Checker}
-\begin{itemize}
-  \item remaining normal parameters
-    (parameter types: normal / optional / variadic)
-  \item remaining arguments
-\end{itemize}
+In ECMAScript abstract algorithms, variables are dynamically introduced in any
+contexts.  The reference bugs are caused when trying to access not yet defined
+variables or to redefine already defined variables.  Such reference bugs are the
+most prevalent type-related specification bugs according to the our manual
+investigation of previous pull requests.  Thus, we implement the reference
+checker by adding additional checks to abstract semantics of variable lookups
+$\aseme{\x}$ and variable declarations $\asemi{\kwlet \; \x = \expr}$ to detect
+unknown variables and already defined variables, respectively:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \aseme{\x}(\aenv) &=& \left\{
+      \begin{array}{ll}
+        \text{unknown variable} \; $\x$
+        & \text{if} \; \asemr{\x}(\aenv) = \{ \tabsent \}\\
+        \cdots
+        & \text{otherwise}\\
+      \end{array}
+    \right.\\
 
-\subsection{Type Checker}
-\begin{itemize}
-  \item unchecked abrupt completions
-  \item typed operators
-\end{itemize}
+    \asemi{\kwlet \; \x = \expr}(\lab, \tys)(\aelem) &=& \left\{
+      \begin{array}{ll}
+        \text{already defined variable} \; $\x$
+        & \text{if} \; \aty = \{ \true \}\\
+        \cdots
+        & \text{otherwise}\\
+      \end{array}
+    \right.\\ &&
+    \text{where} \; \aty = \aseme{\x \kwexists}(\aelem(\lab, \tys))\\
+  \end{array}
+\]
+If the abstract semantics of a variable lookup for $\x$ is a singleton $\{
+\tabsent \}$, it means the variable $\x$ is always an unknown variable.  In this
+case, the reference checker reports a unknown variable bug for $\x$.  For
+example, revisit the syntax-directed algorithm at the upper-left in
+Figure~\ref{fig:example}.  Since the \textbf{GetReferencedName} algorithm is
+removed, the variable \code{GetReferencedName} does not exist in abstract
+environments and its lookup always return $\{ \tabsent \}$ thus the reference
+checker can detect this unknown variable bug.  For already defined variables,
+the reference checker examines whether the variable of each variable declaration
+is always defined using the abstract semantics of existence checks $\aseme{\x
+\kwexists}$.
+
+\subsection{Arity Checker}
+Arity $\size{\func}$ of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n,
+\kwsl \cdots, p_m \kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$
+and $m-n$ denote numbers of normal and optional parameters, respectively.  The
+arity checker detects mismatches of such arities with the number of arguments by
+adding an additional checks in the function call instructions $\asemi{\x = \kwrl
+\expr_0 \; \expr_1 \cdots \expr_k \kwrr}$:
+\[
+  \begin{array}{l}
+    \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k \kwrr}(\lab,
+    \tys)(\aelem) =\\
+    \qquad \left\{
+      \begin{array}{ll}
+        \text{missing parameters} \; \p_{k+1}, \cdots, \p_{n_\func} &
+        \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k < n_\func\\
+
+        \text{reamining arguments} \; \expr_{m_\func+1}, \cdots, \expr_k &
+        \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k > m_\func\\
+
+        \cdots &
+        \text{otherwise}\\
+      \end{array}
+    \right.\\
+  \end{array}
+\]
+where $\func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func}, \kwsl \cdots,
+p_{m_\func} \kwsr). \; \lab \wedge \aty_0 = \aseme{\expr_0}(\aelem(\lab,
+\tys))$.  For each function $\func$ in the abstract semantics of the function
+expression $\expr_0$, the arity checker compares the number of arguments with
+its arity $\size{\func}$ and reports a corresponding arity bug.  For example,
+consider the lower-left syntax directed algorithm in Figure~\ref{fig:example}.
+The algorithm invocation in line 2 is compiled to a function call instruction:
+\[
+  \x = \kwrl \code{formal}.\code{IteratorBindingInitialization} \; \code{formal}
+  \kwrr
+\]
+with a temporal variable $\x$ thus the number of arguments is 1.  However, arity
+of the function stored in $\code{formal}.\code{IteratorBindingInitialization}$
+is $[3, 3]$ thus the arity checker reports missing parameter bugs for two
+additional parameters $\code{iteratorRecord}$ and $\code{environment}$.
 
 \subsection{Assertion Checker}
-\begin{itemize}
-  \item `typeof` assertions
-  \item `instance-of` assertions
-  \item reachability assertions
-\end{itemize}
+\todo
+
+\subsection{Operand Type Checker}
+\todo

### 2021-04-13 src/main/scala/kr/ac/kaist/jiset/analyzer/PruneHelper.scala
Fix bug in pruneInstance

@@ -112,12 +112,13 @@ trait PruneHelper { this: AbsTransfer.Helper =>
   def pruneInstance(l: AbsType, name: String, pass: Boolean): AbsType = {
     val nameT = NameT(name)
     val astT = AstT(name)
-    val isAST = cfg.spec.grammar.nameMap.keySet contains name
-    (pass, isAST) match {
+    val isAst = cfg.spec.grammar.recSubs.keySet contains name
+    val prevAstT = AbsType(cfg.spec.grammar.recSubs(name).map(AstT(_): Type))
+    (pass, isAst) match {
       case (false, false) => l - nameT
-      case (false, true) => l - astT
+      case (false, true) => (l - astT) ⊔ (prevAstT - astT)
       case (true, false) => l ⊓ nameT.abs
-      case (true, true) => l ⊓ astT.abs
+      case (true, true) => prevAstT ⊓ astT.abs
     }
   }
 }

### 2021-04-13 paper/ase21/checker.tex
[ASE21] Added todos
[ASE21] Till Section 4

@@
   \[
-    \begin{array}{c|l|r}
+    \begin{array}{c|l|r|r}
       \multicolumn{1}{c}{\textbf{Category}} &
       \multicolumn{1}{|c}{\textbf{Bug Kind}} &
+      \multicolumn{1}{|c}{\textbf{\# PR}} &
       \multicolumn{1}{|c}{\textbf{\# Bugs}}\\
@@
       \multirow{2}{*}{\text{Reference}}
-      & \text{Unknown Variables} & \inred{XXX}\\\cline{2-3}
-      & \text{Already Defined Variables} & \inred{XXX}\\\hline
+      & \text{Unknown Variables} & \inred{XXX} & \inred{XXX}\\\cline{2-4}
+      & \text{Already Defined Variables} & \inred{XXX} & \inred{XXX}\\\hline
 
       \multirow{1}{*}{\text{Parameter}}
-      & \text{Arity Mismatches} & \inred{XXX}\\\hline
+      & \text{Arity Mismatches} & \inred{XXX} & \inred{XXX}\\\hline
 
       \multirow{1}{*}{\text{Assertion}}
-      & \text{Assertion Failures} & \inred{XXX}\\\hline
+      & \text{Assertion Failures} & \inred{XXX} & \inred{XXX}\\\hline
 
       \multirow{2}{*}{\text{Type}}
-      & \text{Non-Numeric Operands} & \inred{XXX}\\\cline{2-3}
-      & \text{Unchecked Abrupt Completions} & \inred{XXX}\\\hline
+      & \text{Non-Numeric Operands} & \inred{XXX} & \inred{XXX}\\\cline{2-4}
+      & \text{Unchecked Abrupt Completions} & \inred{XXX} & \inred{XXX}\\\hline
 
-      \multicolumn{2}{c|}{\textbf{Total}} & \inred{XXX}\\
+      \multicolumn{2}{c|}{\textbf{Total}} & \inred{XXX} & \inred{XXX}\\
 
@@
 \inred{three years from 2018 to 2021}.  As described in
-Table~\ref{table:pr-bugs}, pull requests include \inred{XXX} type-related
-specification bugs classified in six different kinds and four categories.  We
-implement four checkers for each category bugs: \textit{reference checker},
-\textit{arity checker}, \textit{assertion checker}, and \textit{operand type
-checker}.  Now, we explain how each checker detects corresponding bugs in the
-augmented abstract transfer $\detector$.
+Table~\ref{table:pr-bugs}, \inred{XXX} pull requests existed having bugfixes of
+\inred{XXX} type-related specification bugs classified in six different kinds
+and four categories.  To detect such specification bugs, we implement four
+checkers for each category of bugs: \textit{reference checker}, \textit{arity
+checker}, \textit{assertion checker}, and \textit{operand type checker}.  Now,
+we explain how each checker detects corresponding bugs in the augmented abstract
+transfer $\detector$.
 
@@
 In ECMAScript abstract algorithms, variables are dynamically introduced in any
-contexts.  The reference bugs are caused when trying to access not yet defined
-variables or to redefine already defined variables.  Such reference bugs are the
-most prevalent type-related specification bugs according to the our manual
-investigation of previous pull requests.  Thus, we implement the reference
-checker by adding additional checks to abstract semantics of variable lookups
-$\aseme{\x}$ and variable declarations $\asemi{\kwlet \; \x = \expr}$ to detect
-unknown variables and already defined variables, respectively:
+contexts.  A \textit{reference bug} occurs when trying to access a not yet
+defined variable or to redefine an already defined variable.  According to our
+manual investigation of pull requests, the reference bug is the most prevalent
+type-related specification bugs; \inred{XXX} pull requests fixed \inred{XXX}
+unknown variable bugs and \inred{XXX} pull requests fixed \inred{XXX} already
+defined variable bugs.  We implement the reference checker by adding additional
+checks to abstract semantics of variable lookups $\aseme{\x}$ and variable
+declarations $\asemi{\kwlet \; \x = \expr}$ to detect unknown variables and
+already defined variables, respectively:
 \[
@@
 \tabsent \}$, it means the variable $\x$ is always an unknown variable.  In this
-case, the reference checker reports a unknown variable bug for $\x$.  For
-example, revisit the syntax-directed algorithm at the upper-left in
+case, the reference checker reports an unknown variable bug for $\x$.  For
+example, consider the syntax-directed algorithm at the upper-left in
 Figure~\ref{fig:example}.  Since the \textbf{GetReferencedName} algorithm is
 removed, the variable \code{GetReferencedName} does not exist in abstract
-environments and its lookup always return $\{ \tabsent \}$ thus the reference
-checker can detect this unknown variable bug.  For already defined variables,
-the reference checker examines whether the variable of each variable declaration
-is always defined using the abstract semantics of existence checks $\aseme{\x
-\kwexists}$.
+environments and its lookup returns $\{ \tabsent \}$ thus the reference checker
+reports the unknown variable bug for \code{GetReferencedName}.  For already
+defined variables, the reference checker utilizes the abstract semantics of
+existence check $\aseme{\x \kwexists}$ to check whether the variable $\x$ in
+each variable declaration is already defined.
 
 \subsection{Arity Checker}
+
 Arity $\size{\func}$ of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n,
 \kwsl \cdots, p_m \kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$
-and $m-n$ denote numbers of normal and optional parameters, respectively.  The
-arity checker detects mismatches of such arities with the number of arguments by
-adding an additional checks in the function call instructions $\asemi{\x = \kwrl
-\expr_0 \; \expr_1 \cdots \expr_k \kwrr}$:
+and $m-n$ denote numbers of normal and optional parameters, respectively.  In
+function invocations, an \textit{arity mismatch} occurs when the number of
+arguments is not matched with the arity of a function, and \inred{XXX} pull
+requests fixed \inred{XXX} arity mismatches.  The arity checker detects such
+arity mismatches by using additional checks in the abstract semantics of
+function call instructions $\asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k
+\kwrr}$:
 \[
@@
 
-        \text{reamining arguments} \; \expr_{m_\func+1}, \cdots, \expr_k &
+        \text{remaining arguments} \; \expr_{m_\func+1}, \cdots, \expr_k &
         \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k > m_\func\\
@@
 expression $\expr_0$, the arity checker compares the number of arguments with
-its arity $\size{\func}$ and reports a corresponding arity bug.  For example,
-consider the lower-left syntax directed algorithm in Figure~\ref{fig:example}.
-The algorithm invocation in line 2 is compiled to a function call instruction:
+the arity $\size{\func}$ to detect arity mismatches.  For example, consider the
+lower-left syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm
+invocation in line 2 is compiled to a function call instruction:
 \[
@@
 \]
-with a temporal variable $\x$ thus the number of arguments is 1.  However, arity
-of the function stored in $\code{formal}.\code{IteratorBindingInitialization}$
-is $[3, 3]$ thus the arity checker reports missing parameter bugs for two
-additional parameters $\code{iteratorRecord}$ and $\code{environment}$.
+with a temporal variable $\x$.  While it passes only a single argument
+$\code{formal}$, the arity of the function
+$\code{formal}.\code{IteratorBindingInitialization}$ is $[3, 3]$ thus the arity
+checker reports missing parameter bugs for two additional parameters
+$\code{iteratorRecord}$ and $\code{environment}$.
 
 \subsection{Assertion Checker}
-\todo
+An \textit{assertion failure} is a specification bug that occurs when the
+condition of an assertion instruction is not true.  There were \inred{XXX} pull
+requests that fixed \inred{XXX} assertion failures.  The assertion checker
+detects such bugs using additional checks in the abstract semantics of assertion
+instructions $\asemi{\kwassert \; \expr}$:
+\[
+  \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = \left\{
+    \begin{array}{ll}
+      \text{assertion failure} \; \expr &
+      \text{if} \; \{ \true \} \norder \aty\\
+
+      \cdots &
+      \text{otherwise}\\
+    \end{array}
+  \right.\\
+\]
+where $\aty = \aseme{\expr}(\aelem(\lab, \tys))$.  It checks whether $\{ \true
+\}$ does not have partial order with the abstract semantics of the condition
+expression $\expr$.  For example, consider the lower-right syntax directed
+algorithm in Figure~\ref{fig:example}.  The parameter $\code{environment}$ of
+this algorithm has an environment record or $\undefval$.  Since type sensitivity
+divides the abstract types of arguments to upcasted single types, there are two
+different abstract environments whose variable $\code{environment}$ points to
+$\{ \text{Environment} \}$ or $\{ \undefval \}$.  When $\code{environment}$ is
+$\{ \text{Environment} \}$, the abstract semantics of assertion condition
+$\code{environment = originalEnv}$ is $\{ \tbool \}$.  Even though we know that
+the type of $\code{originalEnv}$ is also $\{ \text{Environment} \}$,
+\text{Environment} is not a singleton type thus we cannot convince that they are
+the exactly same environment.  Thus, we cannot say that the assertion must be
+failed in this case.  However, if $\code{environment}$ is $\{ \undefval \}$, the
+abstract semantics of the condition $\code{environment = originalEnv}$ is $\{
+\false \}$ because an environment is never equal to $\undefval$.  Thus, the
+assertion checker reports an assertion failure for the condition
+$\code{environment = originalEnv}$.
 
 \subsection{Operand Type Checker}
-\todo
+
+Several operators are typed and a \textit{wrong typed operand bug} occurs when
+the type of an operand is not conform to the expected type.  For example, the
+comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.  If
+an expression tries to compare between non-numeric values such as $\true <
+\code{"abc"}$, then it is a non-numeric operand bug.  Besides, ECMAScript has a
+special implicit conversion for normal completions when their actual values
+stored in the $\code{Value}$ field are required including conditions, values of
+field updates, operands of operators, etc.  For example, if the variable $\x$
+has a normal completion with 42 as its actual value, $\x + 1$ should 43 because
+the normal completion implicitly converted into its actual value 42.  To
+explicitly represent this conversion, let's define a unary operator $\escaped$:
+\[
+  \escaped \val = \left\{
+    \begin{array}{ll}
+      \val.\code{Value} &
+      \text{if} \; \val \; \text{is a normal completion}\\
+
+      \text{unchecked abrupt completion} \; \val &
+      \text{if} \; \val \; \text{is an abrupt completion}\\
+
+      \val &
+      \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+and assume that the operator $\escaped$ is used when the actual value is
+required.  Then, an unchecked abrupt completion bug occurs when the actual value
+is required but it is an abrupt completion.  According to our manual
+investigation, \inred{XXX} pull requests are related to \inred{XXX} non-numeric
+operand bugs and \inred{XXX} pull requests are related to \inred{XXX} unchecked
+abrupt completion bugs.
+
+The operand checker detects such wrong typed operand bugs by using additional
+checks in the abstract semantics of binary operations $\aseme{\expr \bop \expr}$
+or unary operations $\aseme{\uop \; \expr}$:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \left\{
+      \begin{array}{ll}
+        \text{wrong typed operand} \; \expr_0
+        & \text{if} \; \asemr{\expr_0}(\aenv) \norder \aty_0\\
+        \text{wrong typed operand} \; \expr_1
+        & \text{if} \; \asemr{\expr_1}(\aenv) \norder \aty_1\\
+        \cdots
+        & \text{otherwise}\\
+      \end{array}
+    \right.\\
+
+    \aseme{\uop \; \expr}(\aenv) &=& \left\{
+      \begin{array}{ll}
+        \text{wrong typed operand} \; $\expr$
+        & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
+        \cdots
+        & \text{otherwise}\\
+      \end{array}
+    \right.\\
+  \end{array}
+\]
+where $\aty$, $\aty$, and $\aty$ are expected abstract types of $\expr_0$,
+$\expr_1$, and $\expr$, respectively.  The additional check reports when the
+given operand does not conform to the expected types.  For example, consider the
+upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
+The parameter $\x$ has $\{ \tjs \}$ and $\n$ has $\{ \tnum \}$ because the
+\textbf{ToNumber} algorithm always return number values or abrupt completions
+but later cases are removed by the \textbf{ReturnIfAbrupt} prefix ?.  While the
+built-in algorithm correctly uses $\n$ in line 2, it misuses $\x$ in line 3 and
+4 and $\{ \tjs \}$ does not have a partial order with the expected abstract type
+$\{ \tnum, \tbigint \}$.  Thus, the operand type checker reports non-numeric
+operand bugs.

### 2021-04-13 paper/ase21/abstract.tex
[ASE21] Updated abstract

@@
 \begin{abstract}
-  JavaScript is one of mainstream programming languages not only in client-side
-  programming but also in server-side programming and even embedded systems.
-  Thus, various JavaScript engines are developed and maintained in various
-  fields and they must conform to the syntax and semantics described in
-  ECMAScript, the standard specification of JavaScript.  Since an incorrect
-  description in ECMAScript can lead to the wrong implementation of JavaScript
-  engines, it is important to check the correctness of ECMAScript.  However, all
-  the specification updates are currently manually checked by the Ecma Technical
-  Committee 39 (TC39) without any automated tools.  Moreover, in late 2014, the
-  committee announced yearly release cadence and open development process of
-  ECMAScript to quickly adapt to an evolving development environment.  Thus, the
-  manual checking becomes more labor-intensive and error-prone.
+  JavaScript is one of mainstream programming languages for client-side
+  programming, server-side programming, and even embedded systems.  Thus,
+  various JavaScript engines are developed and maintained in diverse fields, and
+  they must conform to the syntax and semantics described in ECMAScript, the
+  standard specification of JavaScript.  Since an incorrect description in
+  ECMAScript can lead to the wrong JavaScript engine implementations, checking
+  the correctness of ECMAScript is essential.  However, all the specification
+  updates are currently manually reviewed by the Ecma Technical Committee 39
+  (TC39) without any automated tools.  Moreover, in late 2014, the committee
+  announced yearly release cadence and open development process of ECMAScript to
+  adapt to eolving development environments quickly.  Because of such frequent
+  updates, checking the correctness of ECMAScript becomes more labor-intensive
+  and error-prone.
 
-  To alleviate this problem, we propose $\tool$, a JavaScript Specification Type
+  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
   Analyzer using Refinement.  It is the first tool that performs \textit{type
-  analysis} on JavaScript specifications and detects specification bugs using
-  \textit{bug detector}.  For a given specification, our tool first compiles
-  each abstract algorithm written in a structured natural language to the
-  corresponding function of $\ires$, which is an untyped intermediate
-  representation for ECMAScript.  Then, it performs type analysis for compiled
-  functions with specification types defined in ECMAScript.  Based on the result
-  of type analysis, $\tool$ detects specification bugs using the bug detector
-  consisting of four different checkers.  Moreover, to increase precision of
-  type analysis, we also present \textit{condition-based refinement} for type
-  analysis, which prunes out infeasible abstract states by using conditions of
-  assertions and branches.  We evaluated $\tool$ with all \inred{XXX} different
-  versions existed in the official ECMAScript repository for the recent
-  \inred{three years from 2018 to 2021}.  Our tool detected \inred{XXX}
-  specification bugs including only \inred{XXX} false alarms caused by the
-  imprecision of type analysis in \inred{XX} minutes on average.  Among
-  \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
-  \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
-  version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX} newly
-  found bugs and they are confirmed by the committee.
+  analysis} on JavaScript specifications and detects specification bugs using a
+  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
+  abstract algorithm written in a structured natural language to a corresponding
+  function in $\ires$, an untyped intermediate representation for ECMAScript.
+  Then, it performs type analysis for compiled functions with specification
+  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
+  detects specification bugs using a bug detector consisting of four checkers.
+  Moreover, to increase precision of type analysis, we present
+  \textit{condition-based refinement} for type analysis, which prunes out
+  infeasible abstract states using conditions of assertions and branches.  We
+  evaluated $\tool$ with all \inred{XXX} versions in the official ECMAScript
+  repository for the recent \inred{three years from 2018 to 2021}.  Our tool
+  detected \inred{XXX} specification bugs including only \inred{XXX} false
+  alarms caused by the imprecision of type analysis in \inred{XX} minutes on
+  average.  Among \inred{XXX} true alarms, \inred{XXX} bugs are resolved after
+  existing for \inred{XXX} days on average and \inred{XX} bugs still exist in
+  the latest version of ECMAScript for \inred{XXX} days.  We reported all
+  \inred{XX} newly found bugs and they are confirmed by the committee.
 \end{abstract}

### 2021-04-13 paper/ase21/intro.tex
[ASE21] Till 4.2
[ASE21] Added todos
[ASE21] link of ECMA262 discussion in intro

@@
 
+% TODO: links in footnote
 Unfortunately, there is no existing tool to automatically detect bugs in the
@@
 annotations for variables, parameters, and return values for each abstract
-algorithm.  However, to manually annotate types for all of them without any
-automated tool is also labor-intensive and error-prone.  Furthermore, even
-though the such manual type annotations can give more information for manual
-checking of specification updates, it still does not provide any automatic
-approach to detect specification bugs.
+algorithm~\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
+However, to manually annotate types for all of them without any automated tool
+is also labor-intensive and error-prone.  Furthermore, even though the such
+manual type annotations can give more information for manual checking of
+specification updates, it still does not provide any automatic approach to
+detect specification bugs.
 

### 2021-04-14 paper/ase21/eval.tex
[ASE21] temporal dump

@@
 
+We implemented $\tool$ in Scala by extending $\jiset$, a JavaScript IR-based
+semantics extraction toolchain, with a worklist-based fixpoint algorithm for
+type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
+having uncommon writing styles to $\ires$ instructions, our tool reports
+type-related specification bugs detected in fully compiled abstract algorithms.
+For built-in libraries, we only targeted essential algorithms for
+\jscode{Array}, \jscode{Object}, \jscode{Function}, \jscode{Math},
+\jscode{Proxy}, and primitive types.  To evaluate $\tool$, we answer the
+following research questions:
 \begin{itemize}
-  \item RQ1: Quality of $\tool$: Performance / Precision
-  \item RQ2: Survey of true bugs: TTL / creater or solver / \# by kinds
-  \item RQ3: How many $\tool$ detect new bugs in the recent version? - detailed
-    explanation
+  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
+    analysis for JavaScript specifications?
+  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
+    detcted by $\tool$ are true bugs?
+  \item RQ3. \textbf{(Effect of Refinement)} What is the effect of
+    condition-based refinement for type analysis?
+  \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
+    bugs detected by $\tool$ have?
 \end{itemize}
+The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
+2021.  Thus, we targeted all different \inred{XXX} versions existed in the
+official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
+the recent three years from January 1, 2018 to March 9, 2021.  We performed our
+experiments on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7
+and 32GB of RAM.
+
+\subsection{Performance}
+
+\todo: extract / type analysis / refinement
+
+\subsection{Precision}
+
+\todo: precision / refinement
+
+\subsection{Survey of Detected Bugs}
+
+\todo: TTL / creater or solver / \# by kinds / new bugs

### 2021-04-14 paper/ase21/intro.tex
[ASE21] temporal dump

@@
 also they are useful for the specification-based tools such as JavaScript
-engines~\cite{v8, graaljs, qjs, moddable}, static analyzers~\cite{safe, tajs,
-jsai, wala}, and verification tools~\cite{javert}.  Thus, they decided to
-manually insert two different annotations: 1) \textit{assertions} to denotes the
-assumptions in a certain point of abstract algorithms, and 2) two different
-\textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
-records might be abrupt or not.  For example, ``Assert: Type(\textit{O}) is
-Object'' denotes that the variable $\textit{O}$ always has an Object value at
-this point and ``? \textbf{GetV}(\textit{V}, \textit{P})'' denotes that return
-values of \textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions.
-Moreover, they recently started the internal discussion of manual type
-annotations for variables, parameters, and return values for each abstract
+engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
+analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert}.
+Thus, they decided to manually insert two different annotations: 1)
+\textit{assertions} to denotes the assumptions in a certain point of abstract
+algorithms, and 2) two different \textit{prefixes} $\code{?}$ and $\code{!}$ to
+represent whether completion records might be abrupt or not.  For example,
+``Assert: Type(\textit{O}) is Object'' denotes that the variable $\textit{O}$
+always has an Object value at this point and ``? \textbf{GetV}(\textit{V},
+\textit{P})'' denotes that return values of \textbf{GetV}(\textit{V},
+\textit{P}) might be abrupt completions.  Moreover, they recently started the
+internal discussion of manual type annotations for variables, parameters, and
+return values for each abstract
 algorithm~\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.

### 2021-04-14 paper/ase21/related.tex
[ASE21] temporal dump

@@
 
+\paragraph{ECMAScript-based Applications}
 \begin{itemize}
-  \item Abstract Interpretation~\cite{ai1977, ai1992}
-  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
-  \item JavaScript Manual Mechanized Specification:
+  \item Engines~\cite{v8, graaljs, qjs, moddable}
+  \item Static Analyzer~\cite{safe, tajs, jsai, wala}
+  \item Debuggers: JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
+  \item Verification Tool: JaVerT: JavaScript Verification
+    Toolchain~\cite{javert}
+\end{itemize}
+
+\paragraph{Mechanized Specifications}
 \begin{itemize}
+  % manual
   \item The Essence of Javascript~\cite{lambdajs}
   \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
-      \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
   \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
-      \item JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
-      \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
-        and Specification~\cite{jest}
-    \end{itemize}
-  \item Automatic Mechanized Specification for others:
-    \begin{itemize}
+
+  % automatic
+  \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
+    Specifications for L3 Protocols~\cite{basespec}
   \item Automatic extraction of x86 formal semantics from its natural
@@
   \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
-      \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
-        Specifications for L3 Protocols~\cite{basespec}
+  \item Automatic Model Generation from Documentation for Java API Functions
+  \item COMFORT: JS Fuzzer using ECMAScript
+  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
 \end{itemize}
+
+\paragraph{Correctness of ECMAScript}
+\begin{itemize}
+  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
+  \item JEST: N+1-version Differential Testing of Both JavaScript Engines
+    and Specification~\cite{jest}
 \end{itemize}
+
+% \begin{itemize}
+%   \item Abstract Interpretation~\cite{ai1977, ai1992}
+%   \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
+%   \item JavaScript Manual Mechanized Specification:
+%     \begin{itemize}
+%       \item The Essence of Javascript~\cite{lambdajs}
+%       \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
+%       \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
+%       \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
+%       \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
+%         and Specification~\cite{jest}
+%     \end{itemize}
+%   \item Automatic Mechanized Specification for others:
+%     \begin{itemize}
+%       \item Automatic extraction of x86 formal semantics from its natural
+%         language description~\cite{x86}
+%       \item Formal semantics extraction from natural language specifications for
+%         ARM~\cite{arm}
+%       \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
+%       \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
+%         Specifications for L3 Protocols~\cite{basespec}
+%     \end{itemize}
+% \end{itemize}

### 2021-04-14 eval/eval.py
Change start version in eval.py

@@ -37,7 +37,8 @@ EVAL_LOG = join(RESULT_DIR, "log")
 
 # Global
 FIRST_VERSION = "fc85c50181b2b8d7d75f034800528d87fda6b654"
-ES2018_VERSION = "59d73dc08ea371866c1d9d45843e6752f26a48e4"
+# ES2018_VERSION = "59d73dc08ea371866c1d9d45843e6752f26a48e4"
+ES2018_VERSION = "8fadde42cf6a9879b4ab0cb6142b31c4ee501667"
 COMMIT_REGEX = re.compile("^[a-z0-9]{40}$")
 
 # Shell util

### 2021-04-14 paper/ase21/eval.tex
[ASE21] temporal dump

@@
 type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
-having uncommon writing styles to $\ires$ instructions, our tool reports
+having uncommon writing styles to $\ires$ instructions, our tool only reports
 type-related specification bugs detected in fully compiled abstract algorithms.
@@
     bugs detected by $\tool$ have?
+  \item RQ5: \textbf{(Impact)} How much of an impact does $\tool$ potentially
+    have by detecting type-related specification bugs?
 \end{itemize}
@@
 
-\todo: extract / type analysis / refinement
+\todo: extract / type analysis / refinement?
 
@@
 
-\todo: precision / refinement
+\todo: precision / refinement?
+
+\subsection{Effect of Refinement}
+
+\todo: refinement -> performance / precision
 
@@
 \todo: TTL / creater or solver / \# by kinds / new bugs
+
+\subsection{Impact}
+
+\todo: TTL / creater or solver / \# by kinds / new bugs

### 2021-04-16 paper/ase21/eval.tex
[ASE21] Added images.xlsx

@@
 type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
-having uncommon writing styles to $\ires$ instructions, our tool only reports
-type-related specification bugs detected in fully compiled abstract algorithms.
-For built-in libraries, we only targeted essential algorithms for
-\jscode{Array}, \jscode{Object}, \jscode{Function}, \jscode{Math},
-\jscode{Proxy}, and primitive types.  To evaluate $\tool$, we answer the
-following research questions:
+written in an uncommon writing style to $\ires$ instructions, our tool only
+reports type-related specification bugs detected in fully compiled abstract
+algorithms.  For built-in libraries, we only targeted abstract algorithms of
+essential built-in objects: \jscode{Array}, \jscode{Object}, \jscode{Function},
+\jscode{Math}, \jscode{Proxy}, and objects for primitive types.  To evaluate
+$\tool$, we answer the following research questions:
 \begin{itemize}
@@
   \item RQ3. \textbf{(Effect of Refinement)} What is the effect of
-    condition-based refinement for type analysis?
-  \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
-    bugs detected by $\tool$ have?
-  \item RQ5: \textbf{(Impact)} How much of an impact does $\tool$ potentially
+  %   condition-based refinement for type analysis?
+  % \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
+  %   bugs detected by $\tool$ have?
+  \item RQ4: \textbf{(Impact)} How much of an impact does $\tool$ potentially
     have by detecting type-related specification bugs?
@@
 
-\subsection{Survey of Detected Bugs}
-
-\todo: TTL / creater or solver / \# by kinds / new bugs
-
 \subsection{Impact}

### 2021-04-16 paper/ase21/abstract.tex
[ASE21] Using IEEEtrans format

@@
   announced yearly release cadence and open development process of ECMAScript to
-  adapt to eolving development environments quickly.  Because of such frequent
+  adapt to evolving development environments quickly.  Because of such frequent
   updates, checking the correctness of ECMAScript becomes more labor-intensive

### 2021-04-16 paper/ase21/analyzer.tex
[ASE21] Till Section 4
[ASE21] temporal dump
[ASE21] Using IEEEtrans format

@@
   \includegraphics[width=0.48\textwidth]{img/record-fields-table}
-  \vspace*{-1.5em}
   \caption{Fields of completion records in ES11.}
@@
 language as follows:
+\[
   \small
-\[
   \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
@@
 
-    \text{Types}
-    &\tyset&\ni&\ty&::=&\tname \mid \clist{} \mid \clist{\ty} \mid \tjs \mid
-    \tprim \mid \undefval \mid \nullval\\
+    \text{Types} &\tyset&\ni&\ty&::=&\tname \mid \clist{} \mid \clist{\ty} \mid
+    \tjs \mid \tprim\\
 
     &&&&\mid&
-    \tbool \mid \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
+    \undefval \mid \nullval \mid \tbool \mid \tnumeric\\
+
+    &&&&\mid&
+    \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
   \end{array}
@@
   \includegraphics[width=0.4\textwidth]{img/subtype}
-  \vspace*{-1.5em}
   \caption{A graphical representation of subtype relation $\subtype$.}
@@
 from ES11 that describes fields of completion
-records~\footnote{https://262.ecma-international.org/11.0/\#table-8}; it
-contains three fields ``Type'' with a constant such as \code{normal}, ``Value''
-with JavaScript values or an constant \code{empty}, and ``Target'' with String
-values or \code{empty}.  We manually model them as follows:
+records\footnote{https://262.ecma-international.org/11.0/\#table-8}; it contains
+three fields \code{Type} with a constant such as \code{normal}, \code{Value}
+with JavaScript values or an constant \code{empty}, and \code{Target} with
+String values or \code{empty}.  We manually model them as follows:
+
+\[
   \small
-\[
   \begin{array}{l}
@@
 $\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
-\rightarrow \valset$, and expressions $\sem{\expr}: \dom \rightarrow \valset$.
+\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$.
 For presentation brevity, we omit it in this paper and include it in a companion
@@
     \[
+      \footnotesize
       \begin{array}{r@{~}c@{~}ll}
@@
     \[
+      \footnotesize
       \asemr{\x}(\aenv) = \aenv(\x)
@@
     \[
+      \footnotesize
       \begin{array}{r@{~}c@{~}lr@{~}c@{~}lr@{~}c@{~}l}
@@
 \[
+  \small
   \tyset \ni \ty ::=
@@
 \[
+  \small
   \begin{array}{lr@{~}c@{~}c@{~}r@{~}l}
@@
 \[
+  \small
   \begin{array}{l}
@@
 \]
-where $\norm(\aty) = \{ \ty \mid \ty \in \aty_e \wedge \not\exists \ty' \in
-\aty_e. \; \text{s.t.} \; \ty \neq \ty' \wedge \ty \subtype \ty' \}$.
+where $\small{\norm(\aty) = \{ \ty \mid \ty \in \aty \wedge \nexists \ty' \in
+\aty. \setminus \{ \ty \}\; \text{s.t.} \; \ty \subtype \ty' \}}$.
 
@@
 \[
+  \small
   \upcast(\ty) = \left\{
@@
 \[
+  \small
   \begin{array}{r@{~}c@{~}l}
@@
 \[
+  \small
   \left\{
@@
       \this &\mapsto& \{ \text{AssignmentExpression} \},\\
-      \mcode{LeftHandSideExpression} &\mapsto& \{ \text{LeftHandSideExpression} \},\\
-      \mcode{AssignmentExpression} &\mapsto& \{ \text{AssignmentExpression} \}
+      \code{LeftHandSideExpression} &\mapsto& \{ \text{LeftHandSideExpression} \},\\
+      \code{AssignmentExpression} &\mapsto& \{ \text{AssignmentExpression} \}
     \end{array}
@@
 \[
+  \small
   \refine(\expr, \bool) =
@@
 \[
+  \small
   \refineFlow(\expr, \bool)(\aenv) = \left\{
@@
 \[
+  \tiny
   \begin{array}{r@{~}c@{~}l}
@@
 $\getSingle{\aty} = \emp$ otherwise.
-
-\todo: $\refinePred$?

### 2021-04-16 paper/ase21/eval.tex
[ASE21] Writing Evaluation

@@
 
-We implemented $\tool$ in Scala by extending $\jiset$, a JavaScript IR-based
-semantics extraction toolchain, with a worklist-based fixpoint algorithm for
-type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
-written in an uncommon writing style to $\ires$ instructions, our tool only
-reports type-related specification bugs detected in fully compiled abstract
-algorithms.  For built-in libraries, we only targeted abstract algorithms of
-essential built-in objects: \jscode{Array}, \jscode{Object}, \jscode{Function},
-\jscode{Math}, \jscode{Proxy}, and objects for primitive types.  To evaluate
-$\tool$, we answer the following research questions:
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/func}
+    \caption{The number of functions.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/view}
+    \caption{The number of views.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/iter}
+    \caption{The number of iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/time}
+    \caption{The analysis time.}
+  \end{subfigure}
+  \caption{The statistics of $\tool$ for each version of ECMAScript.}
+  \label{fig:stat}
+\end{figure*}
+
+We implemented $\tool$ as an open-source tool~\footnote{The link is anonymized
+because of a double-blind review process} in Scala by extending $\jiset$, a
+JavaScript IR-based semantics extraction toolchain, with a worklist-based
+fixpoint algorithm for type analysis.  Since $\jiset$ cannot automatically
+compiles algorithm steps written in an uncommon writing style to $\ires$
+instructions, our tool only reports type-related specification bugs detected in
+fully compiled abstract algorithms.  For built-in libraries, we only targeted
+abstract algorithms of essential built-in objects: \jscode{Array},
+\jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
+for primitive types.
+
+To evaluate $\tool$, we answer the following research questions:
 \begin{itemize}
@@
     detcted by $\tool$ are true bugs?
-  \item RQ3. \textbf{(Effect of Refinement)} What is the effect of
-  %   condition-based refinement for type analysis?
-  % \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
-  %   bugs detected by $\tool$ have?
-  \item RQ4: \textbf{(Impact)} How much of an impact does $\tool$ potentially
-    have by detecting type-related specification bugs?
+  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
+    improve the analysis precision with endurable performance degradation?
+  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
+    specification bugs in the latest version of ECMAScript?
 \end{itemize}
 The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
-2021.  Thus, we targeted all different \inred{XXX} versions existed in the
+2021.  Thus, we targeted all different \inred{864} versions existed in the
 official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
@@
 
-\todo: extract / type analysis / refinement?
+To evaluate the performance of $\tool$, we measured the analysis time for
+\inred{864} versions of ECMAScript.  For each version, we assigned an unsigned
+integer as its unique identifier in chronological order starting from 1; the
+identifier of the oldest version is 1 and that of the latest version is
+\inred{864}.  Figure~\ref{fig:time} depicts the analysis time of $\tool$ for
+each version in chronological order.  The dark gray, blue, and red bars
+represent times of specification extraction (\code{extract}), type analysis
+(\code{analyze}), and bug detection (\code{detect}), respectively.  $\tool$ took
+\inred{XXX.XX} seconds to analyze each version of ECMAScript on average; the
+specification extraction took \inred{XX.XX} seconds (\inred{XX.XX}\%), the type
+analysis took \inred{XX.XX} seconds (\inred{XX.XX}\%), and the bug detection
+took \inred{XX.XX} seconds (\inred{XX.XX}\%) on average.
 
@@
 
-\todo: precision / refinement?
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-time}
+    \caption{The analysis time.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-time}
+    \caption{The ratio of analysis time.}
+  \end{subfigure}
+  \caption{The comparison between analysis time without and without condition-based
+  refinement.}
+  \label{fig:refine}
+\end{figure}
 
-\subsection{Effect of Refinement}
+\begin{table*}
+  \centering
+  \[
+    \footnotesize
+    \begin{array}{c|c?c|c?c|c?c|c}
+      \multirow{2}{*}{\textbf{Checker}} &
+      \multirow{2}{*}{\textbf{Bug Kind}} &
+      \multicolumn{6}{c}{
+        \textbf{Precision = (\# True Bugs) / (\# Total Bugs)}
+      }\\\cline{3-8} &&
+      \multicolumn{2}{c?}{\text{no-refine}} &
+      \multicolumn{2}{c?}{\text{refine}} &
+      \multicolumn{2}{c}{\Delta}\\\hline\hline
 
-\todo: refinement -> performance / precision
+      \myrowc{2}
+      {Reference}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
+      {UnknownVar}    {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
+      \myrowh
+      {DuplicatedVar} {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
+
+      \hline
+
+      \myrowc{2}
+      {Arity}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
+      {MissParam}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
+      \myrowh
+      {RemainArg}     {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
+
+      \hline
+
+      \myrowc{1}
+      {Assertion}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
+      {Assertion}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
+
+      \hline
+
+      \myrowc{2}
+      {Operand Type}  {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
+      {NoNumber}      {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
+      \myrowh
+      {Abrupt}        {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
+
+      \hline\hline
+
+      \mysrowh
+      {Total}         {43/44 (97.7\%)}  {43/44 (97.7\%)}  {\md{12}{3}{51.7}}
+
+    \end{array}
+  \]
+  \caption{The analysis precision of $\tool$ without and with condition-based
+  refinement.}
+  \label{fig:refine}
+\end{table*}
+
+  Moreover, Figure~\ref{fig:function}
+represents the number of functions analyzed by $\tool$ for each version of
+ECMAScript; the gray and dark gray bars denote numbers of partially and fully
+compiled functions, respectively.  On average, \inred{XXXX} functions are
+analyzed by $\tool$ thus
+
+Figure~\ref{fig:function}
+Figure~\ref{fig:time}
+
+$\tool$ consists of three steps:
+specification extraction, type analysis, and bug detection, and we measured the
+duration time
+
+For different \inred{864} versions of ECMAScript,
+
+We evaluated performance
+
+\subsection{Effectiveness of Refinement}
+
+\todo: refinement: performance / precision
 

### 2021-04-17 paper/ase21/checker.tex
[ASE21] temporal dump
[ASE21] Using IEEEtrans format
[ASE21] Writing Evaluation
[ASE21] More eval.tex

@@
   \[
+    \small
     \begin{array}{c|l|r|r}
-      \multicolumn{1}{c}{\textbf{Category}} &
-      \multicolumn{1}{|c}{\textbf{Bug Kind}} &
-      \multicolumn{1}{|c}{\textbf{\# PR}} &
-      \multicolumn{1}{|c}{\textbf{\# Bugs}}\\
+      \multicolumn{1}{c|}{\textbf{Category}} &
+      \multicolumn{1}{c|}{\textbf{Bug Kind}} &
+      \multicolumn{1}{c|}{\textbf{\# PR}} &
+      \multicolumn{1}{c}{\textbf{\# Bugs}}\\
       \hline
@@
 \end{table}
+
+% TODO: more detail of investigation
 
@@
 \[
+  \small
   \x = \kwrl \code{formal}.\code{IteratorBindingInitialization} \; \code{formal}
@@
 \[
+  \small
   \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = \left\{
@@
 
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/func}
+    \caption{The number of functions.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/view}
+    \caption{The number of views.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/iter}
+    \caption{The number of iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/time}
+    \caption{The analysis time.}
+  \end{subfigure}
+  \caption{The statistics of type analysis using $\tool$ for 864 versions of
+  ECMAScript.}
+  \vspace*{-1.5em}
+  \label{fig:stat}
+\end{figure*}
+
 Several operators are typed and a \textit{wrong typed operand bug} occurs when
@@
 \[
+  \small
   \escaped \val = \left\{
@@
 \]
-where $\aty$, $\aty$, and $\aty$ are expected abstract types of $\expr_0$,
+where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
 $\expr_1$, and $\expr$, respectively.  The additional check reports when the

### 2021-04-17 paper/ase21/eval.tex
[ASE21] Minor change in evaluation
[ASE21] More eval.tex

@@
 \section{Evaluation}\label{sec:eval}
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/func}
-    \caption{The number of functions.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/view}
-    \caption{The number of views.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/iter}
-    \caption{The number of iterations.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/time}
-    \caption{The analysis time.}
-  \end{subfigure}
-  \caption{The statistics of $\tool$ for each version of ECMAScript.}
-  \label{fig:stat}
-\end{figure*}
-
-We implemented $\tool$ as an open-source tool~\footnote{The link is anonymized
-because of a double-blind review process} in Scala by extending $\jiset$, a
-JavaScript IR-based semantics extraction toolchain, with a worklist-based
-fixpoint algorithm for type analysis.  Since $\jiset$ cannot automatically
-compiles algorithm steps written in an uncommon writing style to $\ires$
-instructions, our tool only reports type-related specification bugs detected in
-fully compiled abstract algorithms.  For built-in libraries, we only targeted
-abstract algorithms of essential built-in objects: \jscode{Array},
-\jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
-for primitive types.
-
-To evaluate $\tool$, we answer the following research questions:
-\begin{itemize}
-  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
-    analysis for JavaScript specifications?
-  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
-    detcted by $\tool$ are true bugs?
-  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
-    improve the analysis precision with endurable performance degradation?
-  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
-    specification bugs in the latest version of ECMAScript?
-\end{itemize}
-The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
-2021.  Thus, we targeted all different \inred{864} versions existed in the
-official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
-the recent three years from January 1, 2018 to March 9, 2021.  We performed our
-experiments on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7
-and 32GB of RAM.
-
-\subsection{Performance}
-
-To evaluate the performance of $\tool$, we measured the analysis time for
-\inred{864} versions of ECMAScript.  For each version, we assigned an unsigned
-integer as its unique identifier in chronological order starting from 1; the
-identifier of the oldest version is 1 and that of the latest version is
-\inred{864}.  Figure~\ref{fig:time} depicts the analysis time of $\tool$ for
-each version in chronological order.  The dark gray, blue, and red bars
-represent times of specification extraction (\code{extract}), type analysis
-(\code{analyze}), and bug detection (\code{detect}), respectively.  $\tool$ took
-\inred{XXX.XX} seconds to analyze each version of ECMAScript on average; the
-specification extraction took \inred{XX.XX} seconds (\inred{XX.XX}\%), the type
-analysis took \inred{XX.XX} seconds (\inred{XX.XX}\%), and the bug detection
-took \inred{XX.XX} seconds (\inred{XX.XX}\%) on average.
-
-\subsection{Precision}
-
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/compare-time}
-    \caption{The analysis time.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ratio-time}
-    \caption{The ratio of analysis time.}
-  \end{subfigure}
-  \caption{The comparison between analysis time without and without condition-based
-  refinement.}
-  \label{fig:refine}
-\end{figure}
 
@@
   \centering
-  \[
-    \footnotesize
-    \begin{array}{c|c?c|c?c|c?c|c}
+  \caption{The analysis precision of $\tool$ without and with condition-based
+  refinement.}
+  \label{fig:refine}
+  \resizebox{\textwidth}{!}{%
+  \begin{tabular}{c|c?c|c?c|c?c|c}
     \multirow{2}{*}{\textbf{Checker}} &
@@
     }\\\cline{3-8} &&
-      \multicolumn{2}{c?}{\text{no-refine}} &
-      \multicolumn{2}{c?}{\text{refine}} &
-      \multicolumn{2}{c}{\Delta}\\\hline\hline
+    \multicolumn{2}{c?}{no-refine} &
+    \multicolumn{2}{c?}{refine} &
+    \multicolumn{2}{c}{$\Delta$}\\
+
+    \specialrule{.1em}{.0em}{.0em}
 
@@
 
-      \hline\hline
+    \specialrule{.1em}{.0em}{.0em}
 
     \mysrowh
-      {Total}         {43/44 (97.7\%)}  {43/44 (97.7\%)}  {\md{12}{3}{51.7}}
+    {\textbf{Total}}{43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
 
-    \end{array}
-  \]
-  \caption{The analysis precision of $\tool$ without and with condition-based
-  refinement.}
-  \label{fig:refine}
+  \end{tabular}
+  }
 \end{table*}
 
-  Moreover, Figure~\ref{fig:function}
-represents the number of functions analyzed by $\tool$ for each version of
-ECMAScript; the gray and dark gray bars denote numbers of partially and fully
-compiled functions, respectively.  On average, \inred{XXXX} functions are
-analyzed by $\tool$ thus
+We implemented $\tool$ as an open-source tool~\footnote{The link is anonymized
+because of a double-blind review process} in Scala by extending $\jiset$, a
+JavaScript IR-based semantics extraction toolchain, with a worklist-based
+fixpoint algorithm for type analysis.  Since $\jiset$ cannot automatically
+compiles algorithm steps written in an uncommon writing style to $\ires$
+instructions, our tool only reports type-related specification bugs detected in
+fully compiled abstract algorithms.  For built-in libraries, we only targeted
+abstract algorithms of essential built-in objects: \jscode{Array},
+\jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
+for primitive types.
 
-Figure~\ref{fig:function}
-Figure~\ref{fig:time}
+To evaluate $\tool$, we answer the following research questions:
+\begin{itemize}
+  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
+    analysis for JavaScript specifications?
+  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
+    detcted by $\tool$ are true bugs?
+  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
+    improve the analysis precision with endurable performance degradation?
+  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
+    specification bugs in the latest version of ECMAScript?
+\end{itemize}
+The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
+2021.  Thus, we targeted all different 864 versions existed in the official
+ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the recent
+three years from January 1, 2018 to March 9, 2021.  We performed our experiments
+on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of
+RAM.
 
-$\tool$ consists of three steps:
-specification extraction, type analysis, and bug detection, and we measured the
-duration time
+\subsection{Performance}
 
-For different \inred{864} versions of ECMAScript,
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ttl-chro}
+    \caption{TTL sorted by creation time.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ttl-count}
+    \caption{True bugs classfied by TTL.}
+  \end{subfigure}
+  \caption{Time to Live (TTL) of true bugs.}
+  \vspace*{-1.5em}
+  \label{fig:ttl}
+\end{figure}
 
-We evaluated performance
+Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
+864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
+of flow- and type-sensitive views, (c) the number of worklist iteration, and (d)
+the analysis time.  For each version of ECMAScript, \inred{1,999.9} functions
+(\textsf{func}) are analyzed and \inred{1,999.9} functions among them are fully
+compiled (\textsf{full-func}) on average.  Since the compile rules in $\jiset$
+is more suitable for recent versions, the number of fully compiled functions in
+older versions are less than in more recent versions.  $\tool$ keeps different
+abstract environments for each functions divided by flow- and type-sensitive
+views.  In the analysis result, \inred{1.3}M views existed for each version and
+\inred{1.3}K views existed for each function on average.
+
+We measured performance of $\tool$ based on the number of iteration for worklist
+algorithm and the analysis time.  For each version of ECMAScript, $\tool$ took
+\inred{300.0} seconds with \inred{19,999.9} iterations of worklist algorithm on
+average.  The analysis time consists of \inred{10.0} seconds for the
+specification extraction (\textsf{extract}), \inred{340.0} seconds for the type
+analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
+(\textsf{detect}).
+
+\subsection{Precision}
+
+\begin{table}
+  \centering
+  \caption{The creaters and resolvers of true bugs.}
+  \label{fig:author}
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{c|c|c?c|c|c}
+    \multicolumn{3}{c?}{\textbf{Creater}} &
+    \multicolumn{3}{c}{\textbf{Resolver}}\\\hline
+
+    \textbf{Committee} &
+    \textbf{Outsider} &
+    \textbf{Inherited} &
+    \textbf{Committee} &
+    \textbf{Outsider} &
+    \textbf{NotYet}\\\hline
+
+    \inred{60} &
+    \inred{12} &
+    \inred{20} &
+    \inred{60} &
+    \inred{23} &
+    \inred{10}\\
+  \end{tabular}
+  }
+\end{table}
 
@@
 
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-iter}
+    \caption{The number of iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-iter}
+    \caption{The ratio of iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-time}
+    \caption{The analysis time.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-time}
+    \caption{The ratio of analysis time.}
+  \end{subfigure}
+  \caption{The comparison of iterations and analysis time without and with
+  condition-based refinement.}
+  \label{fig:refine}
+\end{figure}
+
 \todo: refinement: performance / precision
 
-\subsection{Impact}
+\subsection{Detection of New Bugs}
+
+\begin{table*}
+  \centering
+  \caption{Type-related specification bugs newly detected by $\tool$ in the
+  official draft of ECMAScript 2021 (ES12).}
+  \label{fig:new-bug}
+  \resizebox{\textwidth}{!}{%
+  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}c@{~}|@{~}r@{}}
+    \multicolumn{1}{@{}c?}{\textbf{Name}} &
+    \multicolumn{1}{c}{\textbf{Feature}} &
+    \multicolumn{1}{@{}c@{~}}{\textbf{\#}} &
+    \multicolumn{1}{c}{\textbf{Description}} &
+    \multicolumn{1}{@{~}c@{~}}{\textbf{Checker}} &
+    \multicolumn{1}{@{}c}{\textbf{Created}} &
+    \multicolumn{1}{@{}c}{\textbf{Resolved}} &
+    \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}
+
+    ES12-1 &
+    Switch &
+    3 &
+    \makecell[l]{
+        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already
+        defined \\ in algorithms for \jscode{case} blocks of \jscode{switch}
+        statements.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-2 &
+    Try &
+    3 &
+    \makecell[l]{
+        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already
+        defined \\ in algorithms for \jscode{try} statements.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-3 &
+    Arguments &
+    1 &
+    \makecell[l]{
+        A variable \code{index} is already defined in
+        \textbf{CreateMappedArgumentsObject}.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-4 &
+    Array &
+    2 &
+    \makecell[l]{
+        A variable \code{succeeded} is already defined in algorithms for
+        \jscode{Array} objects.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-5 &
+    Class &
+    1 &
+    \makecell[l]{
+        A variable \code{ClassHeritage} is not defined in \textbf{Contains}
+        \\ for tails of \jscode{class} declarations.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-6 &
+    Branch &
+    1 &
+    \makecell[l]{
+        A variable \code{Statement} is not defined in \textbf{EarlyErrors} for
+        \jscode{if} statement.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-7 &
+    Async &
+    1 &
+    \makecell[l]{
+        A variable \code{value} is already defined in \textbf{Evaluation} for
+        \jscode{yield} expressions.
+    } &
+    Reference &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-8 &
+    Arguments &
+    2 &
+    \makecell[l]{
+        The result of the \textbf{Get} algorithm is used without checking of
+        abrupt completions \\ in \textbf{DefineOwnProperty} and
+        \textbf{GetOwnProperty} for \jscode{arguments} objects.
+    } &
+    \makecell[c]{
+      Operand \\ Type
+    }&
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\
+  \end{tabular}
+  }
+\end{table*}
 

### 2021-04-17 paper/ase21/eval.tex
[ASE21] More eval.tex

@@
 864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
-of flow- and type-sensitive views, (c) the number of worklist iteration, and (d)
-the analysis time.  For each version of ECMAScript, \inred{1,999.9} functions
-(\textsf{func}) are analyzed and \inred{1,999.9} functions among them are fully
-compiled (\textsf{full-func}) on average.  Since the compile rules in $\jiset$
-is more suitable for recent versions, the number of fully compiled functions in
-older versions are less than in more recent versions.  $\tool$ keeps different
-abstract environments for each functions divided by flow- and type-sensitive
-views.  In the analysis result, \inred{1.3}M views existed for each version and
-\inred{1.3}K views existed for each function on average.
+of flow- and type-sensitive views, (c) the number of worklist iterations, and
+(d) the analysis time.  For each version of ECMAScript, \inred{1,999.9}
+functions (\textsf{func}) are analyzed and \inred{1,999.9} functions among them
+are fully compiled (\textsf{full-func}) on average.  Since the compile rules in
+$\jiset$ is more suitable for recent versions, the number of fully compiled
+functions in older versions are less than in more recent versions.  $\tool$
+keeps different abstract environments for each functions divided by flow- and
+type-sensitive views.  In the analysis result, \inred{1.3}M views existed for
+each version and \inred{1.3}K views existed for each function on average.
 
-We measured performance of $\tool$ based on the number of iteration for worklist
-algorithm and the analysis time.  For each version of ECMAScript, $\tool$ took
-\inred{300.0} seconds with \inred{19,999.9} iterations of worklist algorithm on
-average.  The analysis time consists of \inred{10.0} seconds for the
-specification extraction (\textsf{extract}), \inred{340.0} seconds for the type
-analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
+We measured performance of $\tool$ based on the number of iterations for
+worklist algorithm and the analysis time.  For each version of ECMAScript,
+$\tool$ took \inred{300.0} seconds with \inred{19,999.9} iterations of worklist
+algorithm on average.  The analysis time consists of \inred{10.0} seconds for
+the specification extraction (\textsf{extract}), \inred{340.0} seconds for the
+type analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
 (\textsf{detect}).

### 2021-04-17 paper/ase21/checker.tex
[ASE21] More eval.tex
[ASE21] Till V.B Precision

@@
 
-      \multirow{2}{*}{\text{Reference}}
+      \multirow{2}{*}{\stextsf{Reference}}
       & \text{Unknown Variables} & \inred{XXX} & \inred{XXX}\\\cline{2-4}
@@
 
-      \multirow{1}{*}{\text{Parameter}}
+      \multirow{1}{*}{\stextsf{Arity}}
       & \text{Arity Mismatches} & \inred{XXX} & \inred{XXX}\\\hline
 
-      \multirow{1}{*}{\text{Assertion}}
+      \multirow{1}{*}{\stextsf{Assertion}}
       & \text{Assertion Failures} & \inred{XXX} & \inred{XXX}\\\hline
 
-      \multirow{2}{*}{\text{Type}}
+      \multirow{2}{*}{\stextsf{Type}}
       & \text{Non-Numeric Operands} & \inred{XXX} & \inred{XXX}\\\cline{2-4}
@@
 checkers for each category of bugs: \textit{reference checker}, \textit{arity
-checker}, \textit{assertion checker}, and \textit{operand type checker}.  Now,
-we explain how each checker detects corresponding bugs in the augmented abstract
+checker}, \textit{assertion checker}, and \textit{operand checker}.  Now, we
+explain how each checker detects corresponding bugs in the augmented abstract
 transfer $\detector$.
@@
 
-\subsection{Operand Type Checker}
+\subsection{Operand Checker}
 

### 2021-04-17 paper/ase21/eval.tex
[ASE21] Till V.B Precision

@@
   \centering
-  \caption{The analysis precision of $\tool$ without and with condition-based
-  refinement.}
-  \label{fig:refine}
+  \caption{The analysis precision of $\tool$ without refinement
+  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
+  difference ($\Delta$)}
+  \label{table:precision}
   \resizebox{\textwidth}{!}{%
@@
     \multicolumn{6}{c}{
-      \textbf{Precision = (\# True Bugs) / (\# Total Bugs)}
+      \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
     }\\\cline{3-8} &&
@@
 
-    \myrowc{2}
+    \myrowc{1}
     {Arity}         {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
     {MissParam}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
-    \myrowh
-    {RemainArg}     {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
 
@@
     \myrowc{2}
-    {Operand Type}  {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
+    {Operand}       {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
     {NoNumber}      {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
@@
   }
+  \vspace*{-1.5em}
 \end{table*}
@@
 
-\subsection{Performance}
-
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ttl-chro}
-    \caption{TTL sorted by creation time.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ttl-count}
-    \caption{True bugs classfied by TTL.}
-  \end{subfigure}
-  \caption{Time to Live (TTL) of true bugs.}
-  \vspace*{-1.5em}
-  \label{fig:ttl}
-\end{figure}
+\subsection{Performance}\label{sec:performance}
 
@@
 (d) the analysis time.  For each version of ECMAScript, \inred{1,999.9}
-functions (\textsf{func}) are analyzed and \inred{1,999.9} functions among them
-are fully compiled (\textsf{full-func}) on average.  Since the compile rules in
+functions (\stextsf{func}) are analyzed and \inred{1,999.9} functions among them
+are fully compiled (\stextsf{full-func}) on average.  Since the compile rules in
 $\jiset$ is more suitable for recent versions, the number of fully compiled
@@
 algorithm on average.  The analysis time consists of \inred{10.0} seconds for
-the specification extraction (\textsf{extract}), \inred{340.0} seconds for the
-type analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
-(\textsf{detect}).
+the specification extraction (\stextsf{extract} with gray bars), \inred{340.0}
+seconds for the type analysis (\stextsf{analyze} with blue bars), \inred{10.0}
+seconds for the bug detection (\stextsf{detect} with red bars).
 
-\subsection{Precision}
+\subsection{Precision}\label{sec:precision}
 
@@
   \centering
-  \caption{The creaters and resolvers of true bugs.}
-  \label{fig:author}
+  \caption{The creators and resolvers of true bugs.}
+  \label{table:author}
   \resizebox{\columnwidth}{!}{%
   \begin{tabular}{c|c|c?c|c|c}
-    \multicolumn{3}{c?}{\textbf{Creater}} &
+    \multicolumn{3}{c?}{\textbf{Creator}} &
     \multicolumn{3}{c}{\textbf{Resolver}}\\\hline
@@
   }
+  \vspace*{-1.5em}
 \end{table}
 
-\subsection{Effectiveness of Refinement}
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ttl-chro}
+    \caption{Existence period sorted by creation time.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ttl-count}
+    \caption{The histogram by TTL.}
+  \end{subfigure}
+  \caption{Time to Live (TTL) of true bugs.}
+  \vspace*{-1.5em}
+  \label{fig:ttl}
+\end{figure}
+
+We measured the analysis precision based on the number of true bugs in
+type-related specification bugs detected by $\tool$.  As described in the
+\stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
+is \inred{51.7}\% because it detected \inred{190} type-related bugs and
+\inred{89} bugs are true bugs among them.  The reference checker detected the
+largest number of bugs with \inred{51.7}\% precision; it found \inred{12} true
+reference bugs for \inred{32} unknown variables (\stextsf{UnknownVar}) and
+\inred{32} already defined variables (\stextsf{DuplicatedVar}). The arity
+checker and the assertion checker found \inred{12} missing parameters
+(\stextsf{MissParam}) with \inred{90.2}\% precision and \inred{12} assertion
+failures (\stextsf{Assertion}) with \inred{90.2}\% precision, respectively.
+Finally, the operand checker detected two different kinds of wrong typed operand
+bugs: \inred{12} non-numeric operand bugs (\stextsf{NoNumber}) for numeric
+operators with \inred{12.3}\% precision and \inred{12} unchecked abrupt
+completion bugs (\stextsf{Abrupt}) with \inred{12.3}\% precision.
+
+Moreover, we extended $\tool$ to automatically extract more statistics of
+detected true bugs.  \inred{First, we checked that true bugs are created or
+resolved by whom as described in Table~\ref{table:author}.  Among \inred{89}
+true bugs, we cannot automatically know who created \inred{20} inherited bugs
+created before 2018.  For remaining \inred{20} bugs, only \inred{20} bugs are
+created by members of the Ecma Technical Committee 39 (TC39) but others
+(\inred{20} bugs) are created by outside contributors not committee members.
+On the other hand, most of them (\inred{20} bugs) are resolved by the committee
+members but only \inred{20} bugs are resolved by non-committee contributors.
+Other \inred{14} bugs are newly found and we will explain their details in
+Section~\ref{sec:new-bug}.}  Another statistic of true bugs is Time to Live
+(TTL) that denotes how many days specification bugs existed.
+Figure~\ref{fig:ttl} describes TTL of true bugs; the left chart depicts the
+period of existing bugs sorted by their creation time, and the right chart
+depicts the histogram of TTL in a logarithmic scale.  The average TTL of true
+bugs is \inred{300.0} days although we assume that \inred{20} inherited bugs are
+created in January 1, 2018.  The maximum length of TTL is \inred{1,000} and this
+bug is created before 2018 but not yet resolved in the latest version.  We
+manually investigated the creation time of this bug, and we discovered that it
+was created at the initial commit of the open development process in September
+22, 2015.  It means that the bug actually existed for \inred{3,000} days.
+
+\subsection{Effectiveness of Refinement}\label{sec:effect-refine}
+
+We showed that the condition-based refinement for type analysis of ECMAScript
+effectively increased analysis precision without significant performance
+degradation. \todo
 
@@
   \end{subfigure}
-  \caption{The comparison of iterations and analysis time without and with
-  condition-based refinement.}
-  \label{fig:refine}
+  \caption{The comparison of iterations and analysis time without refinement
+  (\stextsf{no-refine}) and those with refinement (\stextsf{refine}).}
+  \label{fig:performance-comp}
+  \vspace*{-1.5em}
 \end{figure}
 
-\todo: refinement: performance / precision
-
-\subsection{Detection of New Bugs}
+\subsection{Detection of New Bugs}\label{sec:new-bug}
 
@@
   official draft of ECMAScript 2021 (ES12).}
-  \label{fig:new-bug}
+  \label{table:new-bug}
   \resizebox{\textwidth}{!}{%
@@
     \makecell[l]{
-        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already
-        defined \\ in algorithms for \jscode{case} blocks of \jscode{switch}
+        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already \\
+        defined in algorithms for \jscode{case} blocks of \jscode{switch}
         statements.
     } &
-    Reference &
+    \stextsf{Reference} &
     \inred{2015-01-01} &
@@
     \makecell[l]{
-        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already
-        defined \\ in algorithms for \jscode{try} statements.
+        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already \\
+        defined in algorithms for \jscode{try} statements.
     } &
-    Reference &
+    \stextsf{Reference} &
     \inred{2015-01-01} &
@@
     } &
-    Reference &
+    \stextsf{Reference} &
     \inred{2015-01-01} &
@@
     \makecell[l]{
-        The result of the \textbf{Get} algorithm is used without checking of
-        abrupt completions \\ in \textbf{DefineOwnProperty} and
-        \textbf{GetOwnProperty} for \jscode{arguments} objects.
+        Abrupt completions are used in \textbf{DefineOwnProperty} and
+        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
+        checks.
     } &
-    \makecell[c]{
-      Operand \\ Type
-    }&
+    \stextsf{Operand} &
     \inred{2015-01-01} &
@@
   }
+  \vspace*{-1.5em}
 \end{table*}
-
-\todo: TTL / creater or solver / \# by kinds / new bugs

### 2021-04-17 paper/ase21/overview.tex
[ASE21] Till 4.2
[ASE21] Using IEEEtrans format
[ASE21] Till V.B Precision

@@
   \centering
-  \includegraphics[width=0.48\textwidth]{img/overall}
-  \vspace*{-1.5em}
+  \includegraphics[width=\columnwidth]{img/overall}
   \caption{Overall structure of $\tool$: a type analyzer and a bug detector for
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{img/example}
-  \vspace*{-1em}
+  \includegraphics[width=\textwidth]{img/example}
+  \vspace*{-1.5em}
   \caption{An example JavaScript program with related previous specification
@@
   \label{fig:example}
+  \vspace*{-1.5em}
 \end{figure*}
@@
 
-\paragraph{Operand Type Checker} The last checker checks whether operand types
-are correct for typed operators.  After the function call initialization, the
+\paragraph{Operand Checker} The last checker checks whether operand types are
+correct for typed operators.  After the function call initialization, the
 parameter \jscode{x} points to \jscode{true} thus \jscode{Math.round} is invoked
@@
 program.  Fortunately, another contributor fixed this bug after two days.  In
-the bug detector, the operand type checker detects whether the operand types are
+the bug detector, the operand checker detects whether the operand types are
 compatible with the typed operators.

### 2021-04-18 paper/ase21/eval.tex
[ASE21] Till Evaluation

@@
     \includegraphics[width=\textwidth]{img/ttl-chro}
-    \caption{Existence period sorted by creation time.}
+    \caption{TTLs sorted by creation time.}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{img/ttl-count}
-    \caption{The histogram by TTL.}
+    \caption{The histogram of TTLs.}
   \end{subfigure}
-  \caption{Time to Live (TTL) of true bugs.}
+  \caption{Time to Lives (TTLs) of true bugs.}
   \vspace*{-1.5em}
@@
 resolved by whom as described in Table~\ref{table:author}.  Among \inred{89}
-true bugs, we cannot automatically know who created \inred{20} inherited bugs
-created before 2018.  For remaining \inred{20} bugs, only \inred{20} bugs are
-created by members of the Ecma Technical Committee 39 (TC39) but others
-(\inred{20} bugs) are created by outside contributors not committee members.
-On the other hand, most of them (\inred{20} bugs) are resolved by the committee
-members but only \inred{20} bugs are resolved by non-committee contributors.
-Other \inred{14} bugs are newly found and we will explain their details in
-Section~\ref{sec:new-bug}.}  Another statistic of true bugs is Time to Live
-(TTL) that denotes how many days specification bugs existed.
-Figure~\ref{fig:ttl} describes TTL of true bugs; the left chart depicts the
-period of existing bugs sorted by their creation time, and the right chart
-depicts the histogram of TTL in a logarithmic scale.  The average TTL of true
-bugs is \inred{300.0} days although we assume that \inred{20} inherited bugs are
-created in January 1, 2018.  The maximum length of TTL is \inred{1,000} and this
-bug is created before 2018 but not yet resolved in the latest version.  We
-manually investigated the creation time of this bug, and we discovered that it
-was created at the initial commit of the open development process in September
-22, 2015.  It means that the bug actually existed for \inred{3,000} days.
+true bugs, we cannot automatically know who created \inred{20}
+\textit{inherited} bugs, which are created before 2018.  For remaining
+\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
+Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
+outside contributors not committee members.  On the other hand, most of them
+(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
+are resolved by non-committee contributors.  Other \inred{14} bugs are newly
+found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
+statistic of true bugs is Time to Live (TTL) that denotes how many days
+specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
+the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
+creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
+histogram of TTLs in a logarithmic scale.  The average days of TTL is
+\inred{300.0} even though we assume that \inred{20} inherited bugs are created
+in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
+corresponding bug is inherited and not yet resolved in the latest version.  We
+manually investigated its creation time in the history of the official
+repository, and we discovered that it was created at the initial commit of the
+open development process in September 22, 2015.  It means that the bug actually
+existed for \inred{3,000} days.
 
 \subsection{Effectiveness of Refinement}\label{sec:effect-refine}
-
-We showed that the condition-based refinement for type analysis of ECMAScript
-effectively increased analysis precision without significant performance
-degradation. \todo
-
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/compare-iter}
-    \caption{The number of iterations.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ratio-iter}
-    \caption{The ratio of iterations.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/compare-time}
-    \caption{The analysis time.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ratio-time}
-    \caption{The ratio of analysis time.}
-  \end{subfigure}
-  \caption{The comparison of iterations and analysis time without refinement
-  (\stextsf{no-refine}) and those with refinement (\stextsf{refine}).}
-  \label{fig:performance-comp}
-  \vspace*{-1.5em}
-\end{figure}
-
-\subsection{Detection of New Bugs}\label{sec:new-bug}
 
@@
     ES12-5 &
+    Async &
+    1 &
+    \makecell[l]{
+        A variable \code{value} is already defined in \textbf{Evaluation} for
+        \jscode{yield} expressions.
+    } &
+    \stextsf{Reference} &
+    \inred{2015-01-01} &
+    \inred{2015-01-01} &
+    \inred{1,999} days\\\hline
+
+    ES12-6 &
     Class &
@@
 
-    ES12-6 &
+    ES12-7 &
     Branch &
@@
         \jscode{if} statement.
-    } &
-    \stextsf{Reference} &
-    \inred{2015-01-01} &
-    \inred{2015-01-01} &
-    \inred{1,999} days\\\hline
-
-    ES12-7 &
-    Async &
-    1 &
-    \makecell[l]{
-        A variable \code{value} is already defined in \textbf{Evaluation} for
-        \jscode{yield} expressions.
     } &
@@
 \end{table*}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-iter}
+    \caption{The histogram of iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-iter}
+    \caption{The ratio of iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-time}
+    \caption{The histogram of analysis time.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-time}
+    \caption{The ratio of analysis time.}
+  \end{subfigure}
+  \caption{The comparison of iterations and analysis time without refinement
+  (\stextsf{no-refine}) and with refinement (\stextsf{refine}).}
+  \label{fig:performance-compare}
+  \vspace*{-1.5em}
+\end{figure}
+
+We evaluated the effectiveness of condition-based refinement based on how much
+it improved analysis precision without significant performance degradation.  To
+compare performance and precision of analysis without refinement
+(\stextsf{no-refine}) and with refinement (\stextsf{refine}), we also performed
+$\tool$ without refinement for 864 versions of ECMAScript.
+
+For performance, Figure~\ref{fig:performance-compare} describes the comparison
+of iterations and analysis time without refinement and with refinement; the left
+charts (Figure~\ref{fig:performance-compare}(a) and
+\ref{fig:performance-compare}(c)) are histograms of iterations and analysis
+time, and the right charts (Figure~\ref{fig:performance-compare}(b) and
+\ref{fig:performance-compare}(d)) are scatter charts for their ratio.  Without
+refinement, type analysis took \inred{234.3} seconds with \inred{232}K
+iterations on average.  With refinement, it took \inred{234.3} seconds with
+\inred{232}K iterations on average.  For each version, analysis time is
+increased at least \inred{2.3}x, at most \inred{2.3}x, and \inred{2.3}x on
+average, and the number of iterations is increased at least \inred{2.3}x, at
+most \inred{2.3}x, and \inred{2.3}x on average.
+
+Table~\ref{table:precision} shows the analysis precision without refinement,
+with refinement, and their difference.  The refinement improved the analysis
+precision from \inred{23.2}\% to \inred{23.3}\% by removing \inred{10} false
+bugs and to detect \inred{10} more true bugs.  (\todo: investigate the result for
+each checker.)
+
+\subsection{Detection of New Bugs}\label{sec:new-bug}
+
+Among \inred{91} true bugs detected by $\tool$, \inred{14} bugs are newly
+detected and still exist in the latestest version of ECMAScript.
+Table~\ref{table:new-bug} summarizes the bugs categorized by their kinds and
+related JavaScript language features. It includes their TTLs, and we manually
+investigated their extact creation time if they are created before 2018.  We
+reported the newly detected bugs to TC39; all of them are confirmed by the
+committee and will be fixed in ECMAScript 2022 (ES13).
+
+ES12-1 contains three bugs that are due to the duplicated definition of
+variables in three different algorithms for \jscode{case} blocks of
+\jscode{switch} statements: \code{hasDuplicates} in
+\textbf{ContainsDuplicateLabels}, and \code{hasUndefinedLabels} in
+\textbf{ContainsUndefinedBreakTarget} and
+\textbf{ContainsUndefinedContinueTarget}.  Each \jscode{case} block optionally
+contains \jscode{case} clauses, and three algorithms perform additional stpes
+including to define \code{hasDuplicates} (or \code{hasUndefinedLabels}) when the
+clauses exist at the beginning.  However, the exactly same variable is defined
+again after the coditionally additional steps.  It means that the semantics of
+\jscode{case} blocks having \jscode{case} clauses always have reference for
+already defined variable \code{hasDuplicates} (or \code{hasUndefinedLabels}).
+ES12-2 also contains three bugs caused by the exactly same reasons in same
+abstract algorithms for \jscode{try} statements.
+
+The bug in ES12-3 is a reference bug for already defined variable \code{index}
+in the abstract algorithm \textbf{CreateMappedArgumentsObject}.  For each
+function call in JavaScript programs, an \jscode{arguments} object is created by
+\textbf{CreateMappedArgumentsObject}.  In the algorithm, the variable
+\code{index} is defined to handle the index of a given list of arguments.
+However, the variable is defined twice in step 14 and 17 of the algorithm.
+
+ES12-4 contains two reference bugs for already defined variable \code{succeeded}
+in \textbf{DefineOwnProperty} of \jscode{Array} objects and
+\textbf{ArraySetLength}.  The \jscode{Array} objects are exotic, which means
+that they are not ordinay objects and have special algorithms for specific
+behaviors.  The two algorithms are wrapper algorithms of
+\textbf{OrdinaryDefineOwnProperty} which updates object properties.  They define
+the variable \code{succeeded} to represent the result of
+\textbf{OrdinaryDefineOwnProperty}.  However, the variable is defined twice in a
+specific condition.
+
+The bug in ES12-5 is a reference bug for already defined variable \code{value}
+in \textbf{Evaluation} of defined \jscode{yield} expressions.  In the evaluation
+of \jscode{yield * e}, the variable \code{value} is defined twice to
+represent 1) the evaluation result of the given expression \jscode{e} in step
+3, and 2) to the iterator value in step 7.c.viii.1.
+
+The bug in ES12-6 is a reference bug for unknown variable \code{ClassHeritage}
+in \textbf{Contains} for tails of \jscode{class} declarations.  A tail of
+\jscode{class} declaration consists of an optional class heritage with
+\jscode{extneds} keyword and a class body enclosed by curly braces.  When the
+optional class heritage does not exist, the variable \code{ClassHeritage} is not
+defined but the \textbf{Contains} algorithm tries to access it without any check
+of its existence.
+
+The bug in ES12-7 is a reference bug for unknown variable \code{Statement} in
+\textbf{EarlyErrors} for \jscode{if} statements.  In syntax-directed algorithms,
+the ordinal numbers are used as prefixes of variables when multiple sub-ASTs are
+produced by same productions.  A \jscode{if} statement contains two sub-ASTs
+produced by the \textit{Statement} production thus the ordinal number prefixes
+are required for the variable \code{Statement}.  However, the
+\textbf{EarlyErrors} algorithm for \jscode{if} statements uses it without any
+ordinal number prefixes.
+
+ES12-8 contains two operand type bugs related to abrupt completions in
+\textbf{DefineOwnProperty} and \textbf{GetOwnProperty} for \jscode{arguments}
+objects.  The two algorithms define or get own properties of \jscode{arguments}
+exotic objects.  They utilize the \textbf{Get} algorithm that returns JavaScript
+values stored in object properties or abrupt completions.  Thus, they should
+check whether results of \textbf{Get} are abstract completions or not before
+using them.  However, they use the results without any abrupt completion checks.

### 2021-04-18 paper/ase21/abstract.tex
[ASE21] Till Conclusion

@@
   infeasible abstract states using conditions of assertions and branches.  We
-  evaluated $\tool$ with all \inred{XXX} versions in the official ECMAScript
-  repository for the recent \inred{three years from 2018 to 2021}.  Our tool
-  detected \inred{XXX} specification bugs including only \inred{XXX} false
-  alarms caused by the imprecision of type analysis in \inred{XX} minutes on
-  average.  Among \inred{XXX} true alarms, \inred{XXX} bugs are resolved after
-  existing for \inred{XXX} days on average and \inred{XX} bugs still exist in
-  the latest version of ECMAScript for \inred{XXX} days.  We reported all
-  \inred{XX} newly found bugs and they are confirmed by the committee.
+  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
+  for the recent three years from 2018 to 2021.  Our tool took \inred{230}
+  seconds on average to perform type analysis for each version, and detected
+  \inred{200} type-related specification bugs with \inred{50.3}\% precision;
+  \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14} bugs
+  are newly detected by $\tool$ and the committee confirmed all of them.
 \end{abstract}

### 2021-04-18 paper/ase21/conclusion.tex
[ASE21] Till Conclusion

\section{Conclusion}\label{sec:conclusion}
Since an incorrect description in ECMAScript can lead to the wrong JavaScript
engine implementations, checking the correctness of ECMAScript is essential.
Since ECMAScript is annually released and developed in open process, it becomes
more labor-intensive and error-prone.  To alleviate the problem, we propose
$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  Moreover, to increase
precision of type analysis, we present \textit{condition-based refinement} for
type analysis, which prunes out infeasible abstract states using conditions of
assertions and branches.  We evaluated $\tool$ with all 864 versions in the
official ECMAScript repository for the recent three years from 2018 to 2021.
Our tool took \inred{230} seconds on average to perform type analysis for each
version, and detected \inred{200} type-related specification bugs with
\inred{50.3}\% precision; \inred{91} out of \inred{200} bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$ and the committee
confirmed all of them.

### 2021-04-18 paper/ase21/intro.tex
[ASE21] Till V.B Precision
[ASE21] Till Conclusion

@@
 algorithms between consecutive releases from ES7 (2016) to ES10 (ES2019) is
-9645.5.  In the official repository of ECMAScript, \inred{X,XXX} pull requests
-and \inred{X,XXX} commits exist in the master branch.  Therefore, it makes more
+9645.5.  In the official repository of ECMAScript, \inred{1,200} pull requests
+and \inred{3,000} commits exist in the master branch.  Therefore, it makes more
 difficult to manually check all the specification updates using limited human
@@
 \textit{bug detector} consisting of four different checkers: 1) reference
-checker, 2) arity checker, and 3) assertion checker, 4) operand type checker.
+checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
 Moreover, to increase precision of type analysis, we also present
@@
 caused by spurious types inferred by imprecise analysis.  We evaluate our tool
-with all \inred{XXX} different versions existed in the official ECMAScript
+with all \inred{864} different versions existed in the official ECMAScript
 repository for the recent \inred{three years from 2018 to 2021}.
@@
     \textit{bug detector} consisting of four different checkers: 1) reference
-    checker, 2) arity checker, and 3) assertion checker, 4) operand type
-    checker.
+    checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
   \item We present \textit{condition-based refinement} for type analysis of
@@
     assertions and branches.
-  \item We demonstrate the practicality of $\tool$. For recent \inred{XXX}
-    different versions of ECMAScript, our tool detected \inred{XXX}
-    specification bugs including only \inred{XXX} false alarms caused by the
-    imprecision of type analysis in \inred{XX} minutes on average.  Among
-    \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
-    \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
-    version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX}
-    newly found bugs and they are confirmed by the committee.
+  \item We demonstrate the practicality of $\tool$. Our tool took \inred{230}
+    seconds on average to perform type analysis for each version, and detected
+    \inred{200} type-related specification bugs with \inred{50.3}\% precision;
+    \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14}
+    bugs are newly detected by $\tool$ and the committee confirmed all of them.
 \end{itemize}

### 2021-04-18 paper/ase21/related.tex
[ASE21] Till Conclusion

--- 2021-03-29 paper/ase21/related.tex
@@
 
-\begin{itemize}
-  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
-\end{itemize}
+JavaScript specification type analysis is related to two research fields:
+JavaScript tools, mechanized specification extraction, specification-based
+testing.
+
+\paragraph{JavaScript Tools}
+ECMAScript is the standard language specification for JavaScript maintained by
+the Ecma Technical Committee 39 (TC39).  In late 2014, the committee announced
+yearly release cadence and open development process of ECMAScript to quickly
+adapt to an evolving development environment.  Existing JavaScript engines, such
+as Google V8~\cite{v8}, GraalJS~\cite{graaljs}, QuickJS~\cite{qjs}, and Moddable
+XS~\cite{moddable}, must conform to the syntax and semantics described in
+annually updated ECMAScript.  Beyond JavaScript engines, there are diverse
+research directions to utilize JavaScript specifications.  Several researchers
+developed static analyzers, such as TAJS~\cite{tajs}, SAFE~\cite{safe},
+JSAI~\cite{jsai}, and WALA~\cite{wala}, based on abstract interpretation
+framework~\cite{ai1977, ai1992} with various analysis techniques.  They defined
+abstract semantics of JavaScript semantics described in ECMAScript to statically
+analyze given JavaScript programs in a finite time.  \citet{jsexplain} presented
+JSExplain, a debugger for JavaScript, by implementing a reference interpreter in
+OCaml directly conforms to algorithm steps in ECMAScript.  For a given
+JavaScript program, the debugger produces execution traces interactively
+invesitgated in a browser, with an interface that displays not only the code and
+the state of the interpreter.  \citet{javert} introduced JaVerT, a JavaScript
+verification toolchain, based on separation logic with their own intermediate
+goto language JSIL.  Moreover, JaVerT 2.0~\cite{javert2} extends it to support
+compositional symbolic execution for JavaScript based on bi-abduction.  However,
+all of them manually handles ECMAScript with their own intermediate
+representations thus many of them still targets ES5.1, the most famous old
+version of ECMAScript released in 2011, not the latest one.
+
+\paragraph{Mechanized Specification Extraction}
+Several researchers extracted mechanized specifications from specifications
+written in a natural language to mechanically handle materials in
+specifications.  For system architectures, researchers utilized complex Natural
+Language Processing (NLP) and Machine Learning (ML) to extract formal semantics
+of small-sized low-level assembly languages for x86~\cite{x86} and
+ARM~\cite{arm}.  For Java API functions, \citet{javadoc} presented a technique
+to automatically extract models from their documentation using NLP techniques.
+Instead of specific API functions, \citet{jiset} presented $\jiset$, a tool that
+extracts mechanized language specification from ECMAScript.  While previous
+JavaScript formal semantics~\cite{lambdajs, jscert, kjs} were manually defined,
+$\jiset$ automatically extracts formal semantics directly from ECMAScript.  We
+utilized $\jiset$ to perform type analysis for diverse versions of ECMAScript in
+$\tool$.
+
+\paragraph{Specification-based Testing}
+Several researchers utilized specifications to test their implementations.  For
+network protocols, \citet{basespec} proposed a novel approach named
+\textsc{BaseSpec}, which extracts message structures from tables in cellular
+specifications for L3 protocols to perform comparative analysis with baseband
+software.  \citet{spectest} presented SpecTest that utilized an executable
+language semantics to perform fuzzing for Java and Solidity compilers.  For
+JavaScript, \citet{comfort} presented \textsc{Comfort}, a compiler fuzzing
+framework to detect JavaScript engine bugs using ECMAScript with deep
+learning-based language models.  \citet{jest} extended $\jiset$ to $\jest$ that
+performs $N$+1-version differential testing with a reference interpreter
+extracted from ECMAScript and $N$ different JavaScript engines.  $\jest$ detects
+not only engine bugs but also specification bugs in ECMAScript based on the
+cross-referencing oracle.  However, it requires multiple JavaScript engines and
+takes dozens of hours to cover semantics for each version of ECMAScript.
+Instead, $\tool$ can detect specification bugs without JavaScript engines less
+than 5 minutes.  Moreover, $\tool$ utilizes abstract semantics instead of
+concrete semantics used in $\jest$ thus it can quickly cover more semantics.

### 2021-04-19 paper/ase21/abstract.tex
[ASE21] Updated abstract

@@
   evaluated $\tool$ with all 864 versions in the official ECMAScript repository
-  for the recent three years from 2018 to 2021.  Our tool took \inred{230}
+  for the recent three years from 2018 to 2021.  Our tool took \inred{136.1}
   seconds on average to perform type analysis for each version, and detected
-  \inred{200} type-related specification bugs with \inred{50.3}\% precision;
-  \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14} bugs
-  are newly detected by $\tool$ and the committee confirmed all of them.
+  \inred{177} type-related specification bugs with \inred{52.0}\% precision;
+  \inred{92} bugs out of \inred{177} bugs are true bugs.  Among them, \inred{14}
+  bugs are newly detected by $\tool$ and the committee confirmed all of them.
 \end{abstract}

### 2021-04-19 paper/ase21/intro.tex
[ASE21] Updated intro

@@
 According to \citet{jiset}, the average number of updated steps of abstract
-algorithms between consecutive releases from ES7 (2016) to ES10 (ES2019) is
-9645.5.  In the official repository of ECMAScript, \inred{1,200} pull requests
-and \inred{3,000} commits exist in the master branch.  Therefore, it makes more
-difficult to manually check all the specification updates using limited human
-resources.
+algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019
+(ES10) is 9645.5.  In the official repository of ECMAScript, \inred{1,355} pull
+requests and \inred{2,005} commits exist in the master branch.  Therefore, it
+makes more difficult to manually check all the specification updates using
+limited human resources.
 
-% TODO: links in footnote
 Unfortunately, there is no existing tool to automatically detect bugs in the
@@
 engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
-analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert}.
-Thus, they decided to manually insert two different annotations: 1)
-\textit{assertions} to denotes the assumptions in a certain point of abstract
-algorithms, and 2) two different \textit{prefixes} $\code{?}$ and $\code{!}$ to
+analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert,
+javert2}.  Thus, they decided to manually insert two different annotations: 1)
+\textit{assertions} to denote the assumptions in a certain point of abstract
+algorithms, and 2) two different \textit{prefixes} \textbf{?} and \textbf{!} to
 represent whether completion records might be abrupt or not.  For example,
 ``Assert: Type(\textit{O}) is Object'' denotes that the variable $\textit{O}$
-always has an Object value at this point and ``? \textbf{GetV}(\textit{V},
-\textit{P})'' denotes that return values of \textbf{GetV}(\textit{V},
-\textit{P}) might be abrupt completions.  Moreover, they recently started the
-internal discussion of manual type annotations for variables, parameters, and
-return values for each abstract
-algorithm~\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
+always has an \jscode{Object} value at this point and ``\textbf{?}
+\textbf{GetV}(\textit{V}, \textit{P})'' denotes that return values of
+\textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions and directly
+return them if they are.  Moreover, they recently started the internal
+discussion of manual type annotations for variables, parameters, and return
+values for each abstract algorithm
+\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
 However, to manually annotate types for all of them without any automated tool
-is also labor-intensive and error-prone.  Furthermore, even though the such
-manual type annotations can give more information for manual checking of
-specification updates, it still does not provide any automatic approach to
-detect specification bugs.
+is also labor-intensive and error-prone.  Furthermore, even though such manual
+type annotations can give more information for manual checking of specification
+updates, it still does not provide any automatic mechanism to detect
+specification bugs.
 
@@
 in a natural language.  For a decade, researchers~\cite{lambdajs, jscert, kjs}
-have tried to formally define various mechanized JavaScript specification for a
-specific version of ECMAScript by hand.  However, the manual formalization is
-not suitable for the automatic detection of bugs in the rapidly evolved
-JavaScript specifications.  On the other hand, several approaches to utilize
+have tried to formally define various JavaScript semantics for a specific
+version of ECMAScript by hand.  However, the manual formalization is not
+suitable for the automatic detection of bugs in the rapidly evolved JavaScript
+specifications.  To lessen such burden, several approaches to utilize
 information directly extracted from specifications written in a natural language
-are recently presented in diverse fields such as system architectures~\cite{x86,
-arm}, network protocols~\cite{basespec}, and language
-specifications~\cite{spectest}.  For JavaScript, \citet{jiset} presents $\jiset$
-that automatically compiles each abstract algorithm written in a structured
-natural language to the corresponding function of $\ires$, an untyped
+are recently presented in diverse fields including system
+architectures~\cite{x86, arm}, network protocols~\cite{basespec}, and language
+specifications~\cite{spectest, javadoc}.  For JavaScript, \citet{jiset} presents
+$\jiset$ that automatically compiles each abstract algorithm written in a
+structured natural language to the corresponding function of $\ires$, an untyped
 intermediate representation for ECMAScript.  Therefore, we utilize this tool to
-automatically get mechanized specifications for JavaScript.
+mechanically handle JavaScript specifications.
 
@@
 contains not only JavaScript language types but also specification types such as
-abstract syntax trees (ASTs), internal records (i.e. environments, completions,
-or property descriptors), and internal list-like structures.  Our tool extract
-syntax and table-based type information from ECMAScript and constructs type
-hierarchy and fields for ASTs and records.  Based on the extracted types,
-$\tool$ performs type analysis and detects specification bugs using a
-\textit{bug detector} consisting of four different checkers: 1) reference
+abstract syntax trees (ASTs), internal records (e.g. environments, completions,
+or property descriptors), and internal list-like structures.  We define their
+type hierarchy and fields based on type-related tables in ECMAScript and
+automatically extracted syntax-directed algorithms.  Based on such type
+information, $\tool$ performs type analysis and detects specification bugs using
+a \textit{bug detector} consisting of four different checkers: 1) reference
 checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
-Moreover, to increase precision of type analysis, we also present
+Moreover, to increase precision of type analysis, we also present a
 \textit{condition-based refinement} for type analysis on ECMAScript. Its main
-concept is to prunes out infeasible abstract states by using conditions of
-assertions and branches.  The refinement technique can reduce false alarms
-caused by spurious types inferred by imprecise analysis.  We evaluate our tool
-with all \inred{864} different versions existed in the official ECMAScript
-repository for the recent \inred{three years from 2018 to 2021}.
+concept is to prune out infeasible parts in abstract states by using conditions
+of assertions and branches.  The refinement technique can reduce the number of
+false bugs caused by spurious types inferred by imprecise analysis.  We evaluate
+our tool with all \inred{864} different versions existed in the official
+ECMAScript repository for the recent three years from 2018 to 2021.
 
@@
   \item We present $\tool$, which is the first tool that performs \textit{type
-    analysis} on ECMAScript to check the the correctness of JavaScript language
-    specifications.  $\tool$ automatically detects specification bugs via the
-    \textit{bug detector} consisting of four different checkers: 1) reference
-    checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
-  \item We present \textit{condition-based refinement} for type analysis of
-    ECMAScript to reduce false alarms by increasing the analysis precision.  Its
-    main idea is to prune out infeasible abstract states by using conditions of
-    assertions and branches.
-  \item We demonstrate the practicality of $\tool$. Our tool took \inred{230}
+    analysis} on ECMAScript to check the correctness of JavaScript language
+    specifications.  $\tool$ automatically detects type-related specification
+    bugs via the \textit{bug detector} consisting of four different checkers: 1)
+    reference checker, 2) arity checker, 3) assertion checker, and 4) operand
+    checker.
+  \item We present a \textit{condition-based refinement} for type analysis of
+    ECMAScript to reduce the number of false bugs by increasing the analysis
+    precision.  We show that the refinement technique increase the analysis
+    precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
+    false bugs and detecting \inred{one} more true bug.
+  \item We demonstrate the practicality of $\tool$. It takes \inred{136.1}
     seconds on average to perform type analysis for each version, and detected
-    \inred{200} type-related specification bugs with \inred{50.3}\% precision;
-    \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14}
+    \inred{177} type-related specification bugs with \inred{52.0}\% precision;
+    \inred{92} out of \inred{177} bugs are true bugs.  Among them, \inred{14}
     bugs are newly detected by $\tool$ and the committee confirmed all of them.

### 2021-04-19 paper/ase21/overview.tex
[ASE21] Till Conclusion
[ASE21] Updated overview

@@
 ECMAScript.  We modify $\ires$ to make it more suitable for type analysis, and
-formally define its syntax and semantics in Section~\ref{sec:ires}.
+formally define it in Section~\ref{sec:ires}.
 
 \paragraph{Types} In ECMAScript, types denote not only JavaScript types but also
-specification types for ASTs, records, and lists.  In abstract algorithms, ASTs
-are also values thus they can be stored in the variables or passed as arguments.
-For such ASTs, we use their production names as their types and automatically
-link corresponding syntax-directed algorithms to them as their fields.
-ECMAScript also supports various record types and their fields and possible
-values are defined in the corresponding tables.  For example, ``Table 9:
-Completion Record Fields'' in the latest ECMAScript describes fields of the
-completion records.  The latest version contains tens of tables for record types
-but they are backward compatible in general.  Thus, we manually model fields of
-record types based on the latest version to use them in type analysis.  For
-lists, we define the empty list type $\clist{}$ and parametric list types
-$\clist{\tau}$.
+specification types for ASTs, records, and list-like structures.  In abstract
+algorithms, ASTs are also values thus they can be stored in the variables or
+passed as arguments.  For such ASTs, we use their production names as their
+types and automatically link corresponding syntax-directed algorithms to them as
+their fields.  ECMAScript also supports various record types and their fields
+and possible values are defined in the corresponding tables.  For example,
+``Table 9: Completion Record Fields'' in the latest ECMAScript describes fields
+of the completion records.  The latest version contains tens of tables for
+record types but they are backward compatible in general.  Thus, we manually
+model fields of record types based on tables in the latest version and use use
+them in type analysis.  For list-like structures, we define the empty list type
+$\clist{}$ and parametric list types $\clist{\tau}$.
 
@@
 The type analyzer performs type analysis with flow-sensitivity and
-type-sensitivity for parameters to precisely detect specification bugs.  It
+type-sensitivity for arguments to precisely detect specification bugs.  Each
+function is divided into multiple flow- and type-sensitive views, and an
+abstract state stores mapping from views to corresponding abstract environments.
+To separately handle views, we use a worklist algorithm.  The type analyzer
 consists of two sub-modules: an \textit{analysis initializer} and an
-\textit{abstract transfer}.  We use a stack-based worklist algorithm to
-calculate fixpoint of abstract transfer and assign the initial set of worklist
-using analysis initializer.
+\textit{abstract transfer}.
 
-\paragraph{Analysis Initializer} In ECMAScript, there are three different kinds
-of abstract algorithms \textit{normal}, \textit{syntax-directed} and
+\paragraph{Analysis Initializer} It defines the initial abstract state and the
+initial set of views in worklist.  In ECMAScript, there are three different
+kinds of abstract algorithms \textit{normal}, \textit{syntax-directed} and
 \textit{built-in}.  Since all the parameter types are known for built-in
@@
 utilize them as entry points of type analysis.  For each entry point, the
-initializer defines its abstract environment with parameter types and push the
-pair of entry point and its abstract environment to the worklist.
+initializer defines its abstract environment with parameter types and pushes the
+flow- and type-sensitive views of entry points to the worklist.
 
 \paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
-pair of a control point and its abstract environment from the worklist, produces
-other pairs based on abstract semantics, and pushes them to the worklist.  The
-iteration will be finished when the worklist becomes empty.  Moreover, to reduce
-false alarms by increasing the analysis precision, we perform refinement for
-abstract environment when the current control point is a branch or an assertion.
-The refinement will be described in detail in Section~\ref{sec:refine}.
+specific view from the worklist and udpates the abstract environment of next
+views based on an abstract semantics.  It pushes next views to the worklist if
+it changes their abstract environments, and the iteration will be finished when
+the worklist becomes empty.  Moreover, to increase the analysis precision, we
+perform condition-based refinement for abstract environment when the current
+control point is a branch or an assertion.  The detail of refinement will be
+described in Section~\ref{sec:refine}.
 
@@
 \jscode{??=}.  While the corresponding \textbf{Evaluation} algorithm originally
-used \textbf{GetReferencedName} algorithm to get reference name at line 4.a, a
+used \textbf{GetReferencedName} algorithm to get reference name in line 4.a, a
 contributor removed the \textbf{GetReferencedName} algorithm and replaced its
@@
 \jscode{??=} until another contributor fixed this bug on November 3, 2020.
-Thus, an unknown variable bug of \textbf{GetReferencedName} lated for 6 days.
-The reference checker detects reference bugs including unknown variable bugs.
+Thus, an unknown variable bug for \textbf{GetReferencedName} existed for 7 days.
+The reference checker detects reference bugs including such unknown variable
+bugs.
 
@@
 algorithm is evaluated with additional parameters \textit{iteratorRecord} and
-\textit{environment} to assigns arguments to proper parameters.  However, a
-contributor missed the additional parameters at line 2 in the
+\textit{environment} to assign arguments to proper parameters.  However, a
+contributor missed to pass additional arguments for them in line 2 in the
 \textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September
-6, 2018.  It caused an arity mismatch bug and lasted for 532 days until another
+6, 2018.  It caused an arity mismatch bug and existed for 533 days until another
 contributor fixed this bug on February 20, 2020.  The arity checker checks such
@@
 contains \jscode{undefined} or an environment record exactly same with
-\textit{originalEnv} as described in the assertion at line 5.  However, a
-contributor initially added the assertion without considering of
-\jscode{undefined} on \inred{XXXXXX XX, XXXX}.  Thus, the assertion failure bug
-lasted for \inred{XXXX} days until April 10, 2019.  The assertion checker checks
-whether such assertions are failed or not.
+\textit{originalEnv} as described in the assertion at line 5.  However, the
+assertion did not consider \jscode{undefined} introduced by the initial commit
+of the open development process on September 22, 2015.  Thus, the assertion
+failure bug existed for 1,297 days until April 10, 2019.  The assertion checker
+checks whether such assertions are failed or not.
 
-\paragraph{Operand Checker} The last checker checks whether operand types are
-correct for typed operators.  After the function call initialization, the
+\paragraph{Operand Checker} After the function call initialization, the
 parameter \jscode{x} points to \jscode{true} thus \jscode{Math.round} is invoked
-with the argument \jscode{true}.  The \jscode{Math.round} built-in library
-first converts the given parameter \textit{x} to the corresponding number value
-\textit{n} using \textbf{ToNumber} algorithm, and then performs remaining steps
-using the number value \textit{n}.  However, a contributor made a mistake of
-using \textit{x} instead of \textit{n} at line 3 and 4 on September 11 2020.
-According to this specification, the specification tries to compare a boolean
-value \jscode{true} with a numeric value 0.5 or 0 in the example JavaScript
-program.  Fortunately, another contributor fixed this bug after two days.  In
-the bug detector, the operand checker detects whether the operand types are
-compatible with the typed operators.
+with the argument \jscode{true}.  The \jscode{Math.round} built-in library first
+converts the given parameter \textit{x} to the corresponding number value
+\textit{n} using \textbf{ToNumber} algorithm, and then should perform remaining
+steps using the number value \textit{n}.  However, a contributor made a mistake
+of using \textit{x} instead of \textit{n} in line 3 and 4 on September 11, 2020.
+It makes the specification tries to compare a boolean value \jscode{true} with a
+numeric value 0.5 or 0 in the example JavaScript program.  Fortunately, another
+contributor fixed this bug after two days.  The operand checker detects such
+bugs by checking whether the operand types are compatible with the typed
+operators.
 
@@
 analysis for $\ires$ functions and how to increase analysis precision using
-refinement (Section~\ref{sec:analyzer}) and how to detect type-related
-specification bugs using four different checkers (Section~\ref{sec:checker}).
-After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
-(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).
+condition-based refinement (Section~\ref{sec:analyzer}) and how to detect
+type-related specification bugs using four different checkers
+(Section~\ref{sec:checker}).  After we evaluate $\tool$
+(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
+and conclude (Section~\ref{sec:conclusion}).

### 2021-04-19 paper/ase21/abstract.tex
Revised Abstract

@@
 \begin{abstract}
-  JavaScript is one of mainstream programming languages for client-side
-  programming, server-side programming, and even embedded systems.  Thus,
-  various JavaScript engines are developed and maintained in diverse fields, and
-  they must conform to the syntax and semantics described in ECMAScript, the
+  JavaScript is one of the mainstream programming languages for client-side
+  programming, server-side programming, and even embedded systems.
+  Various JavaScript engines developed and maintained in diverse fields
+  must conform to the syntax and semantics described in ECMAScript, the
   standard specification of JavaScript.  Since an incorrect description in
-  ECMAScript can lead to the wrong JavaScript engine implementations, checking
-  the correctness of ECMAScript is essential.  However, all the specification
+  ECMAScript can lead to wrong JavaScript engine implementations, checking
+  the correctness of ECMAScript is critical and essential.  However, all the specification
   updates are currently manually reviewed by the Ecma Technical Committee 39
   (TC39) without any automated tools.  Moreover, in late 2014, the committee
-  announced yearly release cadence and open development process of ECMAScript to
-  adapt to evolving development environments quickly.  Because of such frequent
+  announced the yearly release cadence and open development process of ECMAScript to
+  quickly adapt to evolving development environments.  Because of such frequent
   updates, checking the correctness of ECMAScript becomes more labor-intensive
@@
   detects specification bugs using a bug detector consisting of four checkers.
-  Moreover, to increase precision of type analysis, we present
+  To increase the precision of the type analysis, we present
   \textit{condition-based refinement} for type analysis, which prunes out
@@
   evaluated $\tool$ with all 864 versions in the official ECMAScript repository
-  for the recent three years from 2018 to 2021.  Our tool took \inred{136.1}
+  for the recent three years from 2018 to 2021.  $\tool$ took \inred{136.1}
   seconds on average to perform type analysis for each version, and detected
   \inred{177} type-related specification bugs with \inred{52.0}\% precision;
-  \inred{92} bugs out of \inred{177} bugs are true bugs.  Among them, \inred{14}
-  bugs are newly detected by $\tool$ and the committee confirmed all of them.
+  \inred{92} out of \inred{177} bugs are true bugs.  Among them, \inred{14}
+  bugs are newly detected by $\tool$, and the committee confirmed them all.
 \end{abstract}

### 2021-04-19 paper/ase21/analyzer.tex
[ASE21] Updated analyzer except Figure 5

@@
 
-In this section, we explain the detail of the type analyzer of $\tool$. We first
+In this section, we explain the detail of the type analyzer in $\tool$. We first
 formally define a modified $\ires$ and explain how to perform type analysis for
-the modified $\ires$.  Moreover, we also explain a condition-based refinement of
+the its functions.  Moreover, we also explain a condition-based refinement of
 type analysis based on conditions of assertions and branches to increase
@@
 language as follows:
-\[
-  \small
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{\columnwidth}{!}{$
     \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
@@
     \end{array}
-\]
-
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
 A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ is consists
@@
 parameters $\y^*$, and a body label $\lab$.  Although global variables exist in
-ECMAScript, we assume that only local variables exist in this paper for brevity
+ECMAScript, we assume that only local variables exist in this paper for brevity.
 An instruction $\inst$ is a variable declaration, a function call, an assertion,
-a branch, a return, or an reference update.  Each invocation of an abstract
+a branch, a return, or a reference update.  Each invocation of an abstract
 algorithm in ECMAScript is compiled to a function call instruction with a newly
@@
 binary operation, a unary operation, a reference, a constant, or a primitive,
-which is either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a
-BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.
+which is either $\undefval$, $\nullval$, a \jscode{Boolean} $\bool$, a
+\jscode{Number} $\num$, a \jscode{BigInt} $\bigint$, a \jscode{String} $\str$,
+or a \jscode{Symbol} $\symb$.
 
@@
 \end{figure}
-
-A type $\ty \in \tyset$ is a norminal type $\tname$ or a pre-defined type;
-$\tjs$ denotes JavaScript values, $\tprim$ primitives, $\tnumeric$ either Number
-or BigInt values, and $\tnum$, $\tbigint$, $\tstr$, and $\tsymb$ denote Number,
-BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is
-either 1) a \textit{production type} for ASTs or 2) a \textit{record type} used
-in abstract algorithms, and ECMAScript describes its fields with pre-defined or
-possible values.  A production type has corresponding syntax-directed algorithms
-as its fields and a record type has specific fields with possible values
-described in the corresponding table and additional description in ECMAScript.
-The production type is automatically extracted but we manually model fields of
-record types.  For example, Figure~\label{fig:record-fields-table} is an excerpt
-from ES11 that describes fields of completion
-records\footnote{https://262.ecma-international.org/11.0/\#table-8}; it contains
-three fields \code{Type} with a constant such as \code{normal}, \code{Value}
-with JavaScript values or an constant \code{empty}, and \code{Target} with
-String values or \code{empty}.  We manually model them as follows:
-
-\[
-  \small
-  \begin{array}{l}
-    \text{Completion} = \kwcl\\
-    \quad \Type: \kwcl \nconst{normal}, \nconst{break}, \nconst{continue},
-    \nconst{return}, \nconst{throw} \kwcr\\
-    \quad \Value: \kwcl \tjs, \nconst{empty} \kwcr\\
-    \quad \Target: \kwcl \tstr, \nconst{empty} \kwcr\\
-    \kwcr\\
-  \end{array}
-\]
-
-The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
-depicted in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
-denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
-subtype relation is dependent on the syntax and defined record types in
-ECMAScript.  We extract subtypes for production types and manually model
-subtypes between record types.  For example, consider the syntax-directed
-abstract algorithm at the lower-right in Figure~\ref{fig:example}.  The
-non-terminal \textit{BindingElement} is the unique token in a alternative of
-\textit{FormalParameter} production thus we automatically extract the subtype
-relation: \textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on
-this subtype relation, a type check expression $\expr: \ty$ checks whether the
-evaluation result of $\expr$ has a type $\ty'$ satisfying $\ty' \subtype \ty$.
-
-We define a denotational semantics of the modified $\ires$ for instructions
-$\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
-\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$.
-For presentation brevity, we omit it in this paper and include it in a companion
-report~\inred{\cite{report}}.
-
-\subsection{Type Analysis}\label{sec:analysis}
 
@@
         \text{where} \;
-        \aelem = (\rmap, \retp) \wedge
         \aenv_r = \rmap(\lab_r, \tys_r)[\x \mapsto \aty] \wedge
@@
     \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
-    \rightarrow \adom \rightarrow \adom$ where $\aenv = \aelem(\lab, \tys)$.}
+    \rightarrow \adom \rightarrow \adom$ where $\aelem = (\rmap, \retp) \wedge
+    \aenv = \aelem(\lab, \tys)$.}
   \end{subfigure}
@@
 
+A type $\ty \in \tyset$ is either a norminal type $\tname$, an empty list type
+$\clist{}$, a parametric list type $\clist{\ty}$, or a pre-defined type; $\tjs$
+denotes JavaScript values, $\tprim$ primitives, $\tnumeric$ either
+\jscode{Number} or \jscode{BigInt} values, and $\tnum$, $\tbigint$, $\tstr$, and
+$\tsymb$ denote \jscode{Number}, \jscode{BigInt}, \jscode{String}, and
+\jscode{Symbol} values, respectively.  A norminal type $\tname$ is either 1) an
+\textit{AST type} having corresponding syntax-directed algorithms as its fields,
+or 2) a \textit{record type} having specific fields with possible values
+described in the corresponding table and additional description in ECMAScript.
+AST types are automatically extracted but we manually model fields of record
+types.  For example, Figure~\ref{fig:record-fields-table} is an excerpt from
+ES11 that describes fields of completion records%
+\footnote{https://262.ecma-international.org/11.0/\#table-8} and we manually
+model them as follows:
+
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{\columnwidth}{!}{$
+    \begin{array}{l}
+      \code{Completion} \code{=} \; \kwcl\\
+        \quad \Type: \{ \nconst{normal}, \nconst{break}, \nconst{continue},
+        \nconst{return}, \nconst{throw} \},\\
+        \quad \Value: \{ \tjs, \nconst{empty} \},
+        \quad \Target: \{ \tstr, \nconst{empty} \}\\
+      \kwcr\\
+    \end{array}
+  $}
+  \vspace{-0.5em}
+\end{figure}
+
+The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
+depicted in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
+denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
+subtype relation is dependent on the norminal types defined in ECMAScript.  We
+extract subtypes for AST types from the JavaScript syntax and manually model
+subtypes for record types.  For example, consider the syntax-directed abstract
+algorithm at the lower-right in Figure~\ref{fig:example}.  The non-terminal
+\textit{BindingElement} is the unique token in an alternative of
+\textit{FormalParameter} production thus we automatically extract the subtype
+relation: \textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on
+this subtype relation, a type check expression $\expr: \ty$ checks whether the
+evaluation result of $\expr$ has a type $\ty'$ satisfying $\ty' \subtype \ty$.
+
+We define a denotational semantics of the modified $\ires$ for instructions
+$\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
+\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$.
+For presentation brevity, we omit it in this paper and include it in a companion
+report~\inred{\cite{report}}.
+
+\subsection{Type Analysis}\label{sec:analysis}
+
 We design a type analysis for the modified $\ires$ based on abstract
@@
 sensitivity~\cite{sens-toplas}.  We first extend types $\tyset$ as follows:
-\[
-  \small
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{0.8\columnwidth}{!}{$
     \tyset \ni \ty ::=
@@
     \tabsent
-\]
-There are three different reasons why we extend types.  First, the original
-types $\tyset$ do not cover all types of values thus we add functions and
-constants.  Second, we add more specific types to increase the precision of type
-analysis.  A completion record is a \textit{normal completion} when its Type
-field is a constant $\nconst{normal}$ or an \textit{abrupt completion}
-otherwise.  We add $\tnormal(\ty)$ and $\tabrupt$ for normal and abrupt
-completions.  Moreover, we also add Boolean values $\bool$, and String values
-$\str$ to precisely handle the control flows of branches and field accesses,
-respectively.  Third, we add the absent type $\tabsent$ to represent the
-existence of variables.  Using such extended types, we define abstract states
-with flow-sensitivity and type-sensitivity for parameters:
-\[
-  \small
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
+There are three reasons why we extend types.  First, the original types $\tyset$
+do not cover all types of values thus we add functions and constants.  Second,
+we add more specific types to increase the precision of type analysis.  A
+completion record is a \textit{normal completion} when its \code{Type} field is
+$\nconst{normal}$ or an \textit{abrupt completion} otherwise.  We add
+$\tnormal(\ty)$ for normal completions whose \code{Value} field is a value of
+the type $\ty$, and $\tabrupt$ for abrupt completions.  Moreover, we also add
+\jscode{Boolean} values $\bool$, and \jscode{String} values $\str$ to precisely
+handle the control flows of branches and field accesses, respectively.  Third,
+we add the absent type $\tabsent$ to represent the existence of variables.
+Using such extended types, we define abstract states with flow-sensitivity and
+type-sensitivity for arguments:
+
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{\columnwidth}{!}{$
     \begin{array}{lr@{~}c@{~}c@{~}r@{~}l}
@@
     \end{array}
-\]
-An abstract state $\aelem \in \adom$ is pair of a return map and a return point
-mapping.  A result map $\rmap \in \rmapset$ represents an abstract environment
-for each flow-sensitive and type-sensitive view, and a return point mapping
-$\retp \in \retpset$ represents possible return points of each function with
-a type-sensitive context.  An abstract environment $\aenv \in \aenvset$
-represents possible types of each variable, and $\aenv(\x) = \{ \tabsent \}$
-when $\x$ is not defined in $\aenv$.  An abstract type $\aty \in \atyset$ is a
-set of types.  While we define the join operator $\join$, the meet operator
-$\meet$, and the partial order $\order$ for most of abstract domains in a
-point-wise manner, we define the operators for types with a normalization
-function $\norm$ because of their subtype relations:
-\[
-  \small
+  $}
+  \vspace{-0.5em}
+\end{figure}
+
+An abstract state $\aelem \in \adom$ is a pair of a result map and a return
+point mapping.  A result map $\rmap \in \rmapset$ represents an abstract
+environment for each flow- and type-sensitive view, and a return point mapping
+$\retp \in \retpset$ represents possible return points of each function
+with a type-sensitive context; each return point consists of a view for the
+caller function and a variable that represents the return value.  An abstract
+environment $\aenv \in \aenvset$ represents possible types for variables, and
+$\aenv(\x) = \{ \tabsent \}$ when $\x$ is not defined in $\aenv$.  An abstract
+type $\aty \in \atyset$ is a set of types.  While we define the join operator
+$\join$, the meet operator $\meet$, and the partial order $\order$ for most of
+abstract domains in a point-wise manner, we define the operators for types with
+a normalization function $\norm$ because of their subtype relations:
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{\columnwidth}{!}{$
     \begin{array}{l}
@@
     \end{array}
-\]
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
 where $\small{\norm(\aty) = \{ \ty \mid \ty \in \aty \wedge \nexists \ty' \in
@@
 following function:
-\[
-  \small
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{0.8\columnwidth}{!}{$
     \upcast(\ty) = \left\{
@@
     \right.
-\]
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
 and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
@@
 infeasible parts in abstract environments based on their conditions to increase
-analysis precision.  We explain its detail in Section~\ref{sec:refine}.  Then,
-we define the abstract semantics $\asem{\prog}$ of a program $\prog = (\getfunc,
-\getinst, \getnext)$ as the least fixpoint of abstract transfer $\atransfer:
-\adom \rightarrow \adom$:
-\[
-  \small
+analysis precision.  We will explain its detail in Section~\ref{sec:refine}.
+Then, we define the abstract semantics $\asem{\prog}$ of a program $\prog =
+(\getfunc, \getinst, \getnext)$ as the least fixpoint of abstract transfer
+$\atransfer: \adom \rightarrow \adom$:
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{0.9\columnwidth}{!}{$
     \begin{array}{r@{~}c@{~}l}
@@
       \atransfer(\aelem) &=& \aelem \join \left(
-      \underset{(\lab, \tys) \in \domain{\rmap}}{\bigjoin}
+        \bigjoin_{(\lab, \tys) \in \domain{\rmap}}
         \asemi{\getinst(\lab)}(\lab, \tys)(\aelem)
@@
     \end{array}
-\]
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
 where $\aelem = (\rmap, \_)$ and $\iaelem$ denotes the initial abstract state.
-As described in the Section~\ref{sec:overview}, $\iaelem$ contains all
-syntax-directed algorithms having no additional parameters and built-in
+As described in Section~\ref{sec:overview}, $\iaelem$ contains entry points of
+all syntax-directed algorithms having no additional parameters and built-in
 algorithms with appropriate abstract environments.  For syntax-directed
@@
 initialized with the following abstract environment:
-\[
-  \small
-  \left\{
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{\columnwidth}{!}{$
     \begin{array}{r@{~}c@{~}l}
-      \this &\mapsto& \{ \text{AssignmentExpression} \},\\
-      \code{LeftHandSideExpression} &\mapsto& \{ \text{LeftHandSideExpression} \},\\
-      \code{AssignmentExpression} &\mapsto& \{ \text{AssignmentExpression} \}
+      \this &\mapsto& \{ \code{AssignmentExpression} \},\\
+      \code{LeftHandSideExpression} &\mapsto& \{ \code{LeftHandSideExpression} \},\\
+      \code{AssignmentExpression} &\mapsto& \{ \code{AssignmentExpression} \}
     \end{array}
-  \right.
-\]
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
 For built-in algorithms, we assign pre-defined variables $\this$, $\args$, and
@@
 algorithm $\jscode{Math.round}$ at the upper-right in Figure~\ref{fig:example}:
-\[
-  \small
-  \left\{
-    \begin{array}{r@{~}c@{~}l}
-      \this &\mapsto& \{ \tjs \},
-      \args \mapsto \{ \clist{\tjs} \},
-      \x \mapsto \tjs\\
-      \NewTarget &\mapsto& \{ \text{Object}, \undefval \},\\
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{0.9\columnwidth}{!}{$
+    \begin{array}{r@{~}c@{~}lr@{~}c@{~}l}
+      \this &\mapsto& \{ \tjs \}, &
+      \args &\mapsto& \{ \clist{\tjs} \},\\
+      \NewTarget &\mapsto& \{ \code{Object}, \undefval \}, &
+      \x &\mapsto& \tjs\\
     \end{array}
-  \right.
-\]
+  $}
+  \vspace{-0.5em}
+\end{figure}
 
@@
 in abstract environments based on conditions of branches of assertions, and we
-formally define the $\refine$ function as a composition of two functions
-$\refineFlow$ and $\refineVar$:
-\[
-  \small
-  \refine(\expr, \bool) =
-  \refineVar(\expr, \bool) \circ \refineFlow(\expr, \bool)
-\]
-The $\refineFlow$ prevents infeasible \textit{control flows} by producing an
-empty abstract environment as follows:
-\[
-  \small
-  \refineFlow(\expr, \bool)(\aenv) = \left\{
-    \begin{array}{ll}
-      \aenv & \text{if} \; \{ \bool \} \order \aseme{\expr}(\aenv)\\
-      \emp & \text{otherwise}\\
-    \end{array}
-  \right.
-\]
-Beyond control flows, $\refineVar$ refines the shape of a given abstract
-environment based on the conditions for variables:
-\[
-  \tiny
-  \begin{array}{r@{~}c@{~}l}
-    \refineVar(\code{!} \expr, \bool)(\aenv) &=&
-    \refineVar(\expr, \neg \bool)(\aenv)\\
+formally define the $\refine$ function as follows:
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{\columnwidth}{!}{$
+    \begin{array}{@{}r@{~}c@{~}l@{}}
+      \refine(\code{!} \expr, \bool)(\aenv) &=&
+      \refine(\expr, \neg \bool)(\aenv)\\
 
-    \refineVar(\expr_0 \bop \expr_1, \bool)(\aenv) &=&
+      \refine(\expr_0 \; \code{||} \; \expr_1, \bool)(\aenv) &=&
       \left\{
         \begin{array}{ll}
-        \aenv_0 \join \aenv_1 & \text{if} \; \bool \wedge \bop = \code{||}\\
-        \aenv_0 \meet \aenv_1 & \text{if} \; \neg\bool \wedge \bop = \code{||}\\
-        \aenv_0 \meet \aenv_1 & \text{if} \; \bool \wedge \bop = \code{\&\&}\\
-        \aenv_0 \join \aenv_1 & \text{if} \; \neg\bool \wedge \bop = \code{\&\&}\\
-        \aenv & \text{otherwise}\\
+          \aenv_0 \join \aenv_1 & \text{if} \; \bool\\
+          \aenv_0 \meet \aenv_1 & \text{if} \; \neg\bool\\
         \end{array}
       \right.\\
-    \multicolumn{3}{r}{
-      \text{where} \;
-      \aenv_0 = \refineVar(\expr_0, \bool)(\aenv) \wedge
-      \aenv_1 = \refineVar(\expr_1, \bool)(\aenv)
-    }\\
+      \refine(\expr_0 \; \code{\&\&} \; \expr_1, \bool)(\aenv) &=&
+      \left\{
+        \begin{array}{ll}
+          \aenv_0 \meet \aenv_1 & \text{if} \; \bool\\
+          \aenv_0 \join \aenv_1 & \text{if} \; \neg\bool\\
+        \end{array}
+      \right.\\
 
-    \refineVar(\x.\Type \code{=} \nconst{normal}, \true)(\aenv) &=&
-    \aenv[ \x \mapsto \aseme{\x}(\aenv) \cap \tnormal(\tyset) ]\\
-    \refineVar(\x.\Type \code{=} \nconst{normal}, \false)(\aenv) &=&
-    \aenv[ \x \mapsto \aseme{\x}(\aenv) \cap \{ \tabrupt \} ]\\
+      \refine(\x.\Type \; \code{==} \; \nconst{normal}, \true)(\aenv) &=&
+      \aenv[ \x \mapsto \aty_\x \cap \tnormal(\tyset) ]\\
+      \refine(\x.\Type \; \code{==} \; \nconst{normal}, \false)(\aenv) &=&
+      \aenv[ \x \mapsto \aty_\x \cap \{ \tabrupt \} ]\\
 
-    \refineVar(\x \code{=} \expr, \true)(\aenv) &=&
-    \aenv[ \x \mapsto \aseme{\x}(\aenv) \meet \aseme{\expr}(\aenv) ]\\
-    \refineVar(\x \code{=} \expr, \false)(\aenv) &=&
-    \aenv[ \x \mapsto \aseme{\x}(\aenv) \setminus
-    \lfloor\aseme{\expr}(\aenv)\rfloor ]\\
+      \refine(\x \; \code{==} \; \expr, \true)(\aenv) &=&
+      \aenv[ \x \mapsto \aty_\x \meet \aty_\expr ]\\
+      \refine(\x \; \code{==} \; \expr, \false)(\aenv) &=&
+      \aenv[ \x \mapsto \aty_\x \setminus
+      \lfloor\aty_\expr\rfloor ]\\
 
-    \refineVar(\x : \ty, \true)(\aenv) &=&
-    \aenv[ \x \mapsto \aseme{\x}(\aenv) \meet \{ \ty \} ]\\
-    \refineVar(\x : \ty, \false)(\aenv) &=&
-    \aenv[ \x \mapsto \aseme{\x}(\aenv) \setminus \{ \ty' \mid \ty' \subtype \ty
+      \refine(\x : \ty, \true)(\aenv) &=&
+      \aenv[ \x \mapsto \aty_\x \meet \{ \ty \} ]\\
+      \refine(\x : \ty, \false)(\aenv) &=&
+      \aenv[ \x \mapsto \aty_\x \setminus \{ \ty' \mid \ty' \subtype \ty
       \}]\\
+      \refine(\expr, \true)(\aenv) &=& \aenv\\
     \end{array}
-\]
-and it returns $\aenvset$ for other cases.  The notation $\getSingle{\aty}$ denotes
-to checks whether it is a singleton; $\getSingle{\aty} = \aty$ if $\aty = \{ \ty
-\}$ and $\ty$ is a singleton type such as a constant $\const$, an empty list
-$\clist{}$, an absent value $\tabsent$, a primitive value, etc., and
-$\getSingle{\aty} = \emp$ otherwise.
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
+where $\aenv_i = \refine(\expr_i, \bool)(\aenv)$ and $\aty_\expr =
+\aseme{\expr}(\aenv)$.  The notation $\getSingle{\aty}$ denotes to check whether
+$\aty$ is a singleton; $\getSingle{\aty} = \aty$ if $\aty = \{ \ty \}$ and $\ty$
+is a singleton type such as a constant $\const$, an empty list $\clist{}$, an
+absent value $\tabsent$, a primitive value, etc., or $\getSingle{\aty} = \emp$
+otherwise.

### 2021-04-19 paper/ase21/analyzer.tex
[ASE21] Updated analyzer

@@
   \centering
-  \begin{subfigure}[b]{\textwidth}
-    \[
-      \footnotesize
-      \begin{array}{r@{~}c@{~}ll}
+  \begin{subfigure}[b]{0.52\textwidth}
+    \resizebox{\textwidth}{!}{$
+      \begin{array}{@{}l@{~}c@{~}l}
         \asemi{\kwlet \; \x = \expr}
         (\lab, \tys)(\aelem) &=&
-        (\{ (\getnext(\lab), \tys) \mapsto \aenv_\x \}, \emp) &
-        \text{where} \;
-        \aenv_\x = \aenv[\x \mapsto \aty] \wedge
-        \aty = \aseme{\expr}(\aenv)\\
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv[\x \mapsto
+        \aseme{\expr}(\aenv)] \}, \emp)\\
 
-        \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_n \kwrr}
-        (\lab, \tys)(\aelem) &=&
-        \left(
-          \begin{array}{@{}l@{}}
-            \{ (\lab_\func, \tys_a) \mapsto \aenv_{\func, \tys_a} \mid \func \in
-              F \wedge \tys_a \in T_a
-            \},\\
-            \{ (\func, \tys_a) \mapsto \{ (\getnext(\lab), \tys, \x) \} \mid
-              \func \in F \wedge \tys_a \in T_a
-            \}\\
-          \end{array}
-        \right) &
+        \asemi{\x = \kwrl \expr \; \expr_1 \cdots \expr_n \kwrr}
+        (\lab, \tys)(\aelem) &=& (\rmap', \retp')\\
+        \multicolumn{3}{@{}l}{
           \text{where} \;
           \left\{
-          \begin{array}{@{}l@{}}
-            \aty_i = \aseme{\expr_i}(\aenv) \wedge T_a = \{ \upcasts([ \ty_1,
-            \cdots, \ty_n ] \mid \ty_i \in \aty_i \} \wedge\\
-            F = \{ \func \in \aty_0 \mid \func = \kwdef \; \_ (\p_1, \cdots,
-            \kwsl \cdots, \p_m \kwsr). \; \lab_\func \} \wedge\\
-            \aenv_{\func, \tys_a} = \aenv[\p_1 \mapsto \{ \tys_a[1] \}, \cdots,
-            \p_m \mapsto \{ \tys_a[m] \}]\\
+            \begin{array}{l@{}}
+              \aty = \aseme{\expr}(\aenv) \;\wedge\;
+              \aty_1 = \aseme{\expr_1}(\aenv) \;\wedge\;
+              \cdots \;\wedge\;
+              \aty_n = \aseme{\expr_n}(\aenv) \;\wedge\;\\
+
+              T' = \{ \upcasts([ \ty_1, \cdots, \ty_n ]) \mid \ty_1 \in \aty_1
+              \;\wedge\; \cdots \;\wedge\; \ty_n \in \aty_n \} \;\wedge\;\\
+
+              \func = \kwdef \; \f (\p_1, \cdots, \kwsl \cdots, \p_{m_\func}
+              \kwsr). \; \lab_\func \;\wedge\;\\
+
+              \aenv_{\func, \tys'} = [\p_1 \mapsto \{ \tys'[1] \}, \cdots,
+              \p_{m_\func} \mapsto \{ \tys'[m] \}] \;\wedge\;\\
+
+              \rmap' = \{ (\lab_\func, \tys') \mapsto \aenv_{\func, \tys'}
+              \mid \func \in \aty \;\wedge\; \tys' \in T' \} \;\wedge\;\\
+
+              \retp' = \{ (\func, \tys') \mapsto \{ (\getnext(\lab), \tys, \x)
+              \} \mid \func \in \aty \;\wedge\; \tys' \in T' \}\\
             \end{array}
-        \right.\\
+          \right.
+        }\\
+
+        \asemi{\kwreturn \; \expr}
+        (\lab, \tys)(\aelem) &=&
+        (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid
+        (\lab_r, \tys_r, \x) \in R\}, \emp)\\
+        \multicolumn{3}{@{}l}{
+          \text{where} \; R = \retp(\getfunc(\lab), \tys) \;\wedge\; \aenv_r =
+          \rmap(\lab_r, \tys_r)[\x \mapsto \aseme{\expr}(\aenv)]
+        }\\
 
@@
         (\lab, \tys)(\aelem) &=&
-        (\{ (\getnext(\lab), \tys) \mapsto \aenv_\mt \}, \emp) &
-        \text{where} \; \aenv_\mt = \refine(\expr, \true)(\aenv)\\
+        (\{ (\getnext(\lab), \tys) \mapsto \pass(\expr, \true)(\aenv) \}, \emp)\\
 
@@
         (\lab, \tys)(\aelem) &=&
-        (\{ (\lab_\mt, \tys) \mapsto \aenv_\mt, (\lab_\mf, \tys) \mapsto
-        \aenv_\mf \}, \emp) &
-        \text{where} \;
-        \aenv_\mt = \refine(\expr, \true)(\aenv) \wedge
-        \aenv_\mf = \refine(\expr, \false)(\aenv)\\
-
-        \asemi{\kwreturn \; \expr}
-        (\lab, \tys)(\aelem) &=&
-        (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid (\lab_r, \tys_r, \x) \in
-        \retp(\getfunc(\lab), \tys)\}, \emp) &
-        \text{where} \;
-        \aenv_r = \rmap(\lab_r, \tys_r)[\x \mapsto \aty] \wedge
-        \aty = \aseme{\expr}(\aenv)\\
+        (\{ (\lab_\mt, \tys) \mapsto \pass(\expr, \true)(\aenv),\\ &&
+        \phantom{(\{} (\lab_\mf, \tys) \mapsto \pass(\expr, \false)(\aenv) \}, \emp)\\
 
@@
         (\lab, \tys)(\aelem) &=&
-        (\{ (\getnext(\lab), \tys) \mapsto \aenv_\x \}, \emp) &
-        \text{where} \;
-        \aenv_\x = \aenv[\x \mapsto \aty] \wedge
-        \aty = \aseme{\expr}(\aenv)\\
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv[\x \mapsto
+        \aseme{\expr}(\aenv)] \}, \emp)\\
 
@@
         (\lab, \tys)(\aelem) &=&
-        (\{ (\getnext(\lab), \tys) \mapsto \aenv \}, \emp)
+        (\{ (\getnext(\lab), \tys) \mapsto \aenv \}, \emp)\\
+
+        \multicolumn{3}{@{}l}{\text{where} \; \aelem = (\rmap, \retp) \;\wedge\;
+        \aenv = \rmap(\lab, \tys)}
       \end{array}
-    \]
+    $}
     \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
-    \rightarrow \adom \rightarrow \adom$ where $\aelem = (\rmap, \retp) \wedge
-    \aenv = \aelem(\lab, \tys)$.}
+    \rightarrow \adom \rightarrow \adom$.}
   \end{subfigure}
-  \begin{subfigure}[b]{0.48\textwidth}
-    \[
-      \footnotesize
-      \asemr{\x}(\aenv) = \aenv(\x)
-      \qquad
-      \asemr{\refer \kwsl \expr \kwsr}(\aenv) = \{ \ty[\str] \mid \ty \in
-      \asemr{\refer}(\aenv) \wedge \str \in \aseme{\expr}(\aenv) \}
-    \]
+  \begin{minipage}[b][0.3\textheight][s]{0.46\textwidth}
+    \begin{subfigure}[b]{\textwidth}
+      \centering
+      \vspace*{0.1em}
+      \resizebox{0.8\textwidth}{!}{$
+        \begin{array}{l@{~}c@{~}l}
+          \asemr{\x}(\aenv) &=& \aenv(\x)\\
+          \asemr{\refer \kwsl \expr \kwsr}(\aenv) &=& \{ \ty[\str] \mid \ty \in
+          \asemr{\refer}(\aenv) \wedge \str \in \aseme{\expr}(\aenv) \}\\
+        \end{array}
+      $}
       \caption{References with $\asemr{\refer}: \aenvset \rightarrow \atyset$.}
+      \vspace*{0.5em}
     \end{subfigure}
     \begin{subfigure}[b]{\textwidth}
-    \[
-      \footnotesize
-      \begin{array}{r@{~}c@{~}lr@{~}c@{~}lr@{~}c@{~}l}
-        \aseme{\tname \; \kwcl \fields \kwcr}(\aenv)
-        &=& \multicolumn{7}{@{}l}{
-          \left\{
+      \centering
+      \resizebox{\textwidth}{!}{$
+        \begin{array}{l@{~}c@{~}l@{}}
+          \multicolumn{3}{l}{
+            \aseme{\num}(\aenv) = \tnum \qquad
+            \aseme{\bigint}(\aenv) = \tbigint \qquad
+            \aseme{\symb}(\aenv) = \tsymb
+          }\\
+
+          \multicolumn{3}{l}{
+            \aseme{\prim}(\aenv) = \prim \qquad
+            \aseme{\const}(\aenv) = \const \qquad
+            \aseme{\clist{}}(\aenv) = \clist{}
+          }\\
+
+          \multicolumn{3}{l}{
+            \aseme{\clist{\expr_0, \cdots, \expr_n}}(\aenv) = \{ \clist{\ty} \mid
+            \ty \in \bigjoin_{0 \leq i \leq n} \aseme{\expr_i}(\aenv) \}
+          }\\
+
+          \multicolumn{3}{l}{
+            \aseme{\code{Completion} \; \kwcl \cdots, \code{Type}:
+            \expr_0, \code{Value}: \expr_1, \cdots \kwcr}(\aenv) =
+          }\\
+          \multicolumn{3}{l}{
+            \qquad \left\{
               \begin{array}{ll}
-              \{ \tnormal(\ty) \mid \ty \in \aseme{\fields(\code{Value})}(\aenv)
-              \} & \text{if} \; \tname = \text{Completion} \wedge
-              \fields(\code{Type}) = \nconst{normal}\\
+                \{ \tnormal(\ty) \mid \ty \in \aseme{\expr_1}(\aenv) \} &
+                \text{if} \; \aseme{\expr_0} = \nconst{normal}\\
 
-              \{ \tabrupt \} & \text{if} \; \tname = \text{Completion} \wedge
-              \fields(\code{Type}) \neq \nconst{normal}\\
-
-              \{ \tname \} & \text{otherwise}\\
+                \{ \tabrupt \} &
+                \text{otherwise}\\
               \end{array}
             \right.
-          \quad \aseme{\prim}(\aenv) =
-          \left\{
-            \begin{array}{ll}
-              \{ \tnum \} & \text{if} \; \prim = \num\\
-              \{ \tbigint \} & \text{if} \; \prim = \bigint\\
-              \{ \tsymb \} & \text{if} \; \prim = \symb\\
-              \{ \prim \} & \text{otherwise}\\
+          }\\
+
+          \aseme{\tname \; \kwcl \cdots \kwcr}(\aenv) &=& \{ \tname \}\\
+
+          \aseme{\expr: \ty}(\aenv) &=& \{ \ty' \subtype \ty \mid \ty' \in
+          \aseme{\expr}(\aenv) \}\\
+
+          \aseme{\refer \kwexists}(\aenv) &=& \{ \ty \neq \tabsent \mid \ty \in
+          \aseme{\expr}(\aenv) \}\\
+
+          \aseme{\refer}(\aenv) &=& \asemr{\refer}(\aenv) \setminus \{ \tabsent \}\\
+
+          \aseme{\uop \; \expr}(\aenv) &=& \{ \abs{\uop} \ty \mid \ty \in
+          \aseme{\expr}(\aenv) \}\\
+
+          \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \{ \ty_0 \abs{\bop} \ty_1 \mid
+          \ty_0 \in \aseme{\expr_0}(\aenv) \wedge \ty_1 \in
+          \aseme{\expr_1}(\aenv) \}\\
         \end{array}
-          \right.
-        }
-
-        \\
-
-        \aseme{\const}(\aenv) &=& \const &
-
-        \aseme{\clist{}}(\aenv) &=& \clist{} &
-
-        \aseme{\clist{\expr_0, \cdots, \expr_n}}(\aenv)
-        &=& \{ \clist{\ty} \mid \ty \in \bigjoin_{0 \leq i
-        \leq n} \aseme{\expr_i}(\aenv) \}
-
-        \\
-
-        \aseme{\expr: \ty}(\aenv)
-        &=& \{ \ty' \subtype \ty \mid \ty' \in
-        \aseme{\expr}(\aenv) \} &
-
-        \aseme{\refer \kwexists}(\aenv)
-        &=& \{ \ty \neq \tabsent \mid \ty \in
-        \aseme{\expr}(\aenv) \} &
-
-        \aseme{\refer}(\aenv)
-        &=& \asemr{\refer}(\aenv) \setminus \{ \tabsent \}
-
-        \\
-
-        \aseme{\uop \; \expr}(\aenv)
-        &=& \{ \abs{\uop} \ty \mid \ty \in
-        \aseme{\expr}(\aenv) \} &
-
-        \aseme{\expr_0 \bop \expr_1}(\aenv)
-        &=& \multicolumn{4}{@{}l}{\{ \ty_0 \abs{\bop} \ty_1 \mid \ty_0 \in
-        \aseme{\expr_0}(\aenv) \wedge \ty_1 \in \aseme{\expr_1}(\aenv) \}}
-
-        \\
-      \end{array}
-    \]
+      $}
       \caption{Expressions with $\aseme{\expr}: \aenvset \rightarrow \atyset$.}
     \end{subfigure}
+  \end{minipage}
   \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
@@
 and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
-For branches and assertions, we apply the $\refine$ function that prunes out
-infeasible parts in abstract environments based on their conditions to increase
-analysis precision.  We will explain its detail in Section~\ref{sec:refine}.
-Then, we define the abstract semantics $\asem{\prog}$ of a program $\prog =
-(\getfunc, \getinst, \getnext)$ as the least fixpoint of abstract transfer
-$\atransfer: \adom \rightarrow \adom$:
+For branches and assertions, we apply the $\pass$ function to prevent the
+infeasible control flows defined as follows:
+
+\begin{figure}[H]
+  \centering
+  \vspace{-0.5em}
+  \resizebox{0.9\columnwidth}{!}{$
+    \pass(\expr, \bool)(\aenv) = \left\{
+      \begin{array}{ll}
+        \refine(\expr, \bool)(\aenv)
+        & \text{if} \; \{ \true \} \order \aseme{\expr}(\aenv)\\
+
+        \emp
+        & \text{otherwise}\\
+      \end{array}
+    \right.
+  $}
+  \vspace{-0.5em}
+\end{figure} \noindent
+where $\refine$ is a function that prunes out infeasible parts in abstract
+environments based on their conditions to increase analysis precision.  We will
+explain its detail in Section~\ref{sec:refine}.  Then, we define the abstract
+semantics $\asem{\prog}$ of a program $\prog = (\getfunc, \getinst, \getnext)$
+as the least fixpoint of abstract transfer $\atransfer: \adom \rightarrow
+\adom$:
 \begin{figure}[H]

### 2021-04-19 paper/ase21/intro.tex
Revised Sec. 1

@@
 JavaScript is one of the most popular programming languages.  According to the
-2020 State of the Octoverse\footnote{https://octoverse.github.com/}, which is
-the annual report of GitHub, the most dominated programming language in GitHub
+2020 State of the Octoverse\footnote{https://octoverse.github.com/},
+the annual report of GitHub, the most dominating programming language in GitHub
 repositories was JavaScript since 2014 to 2020.  While JavaScript was initially
-designed for client-side programming in web browsers, now it is widely used in
+designed for client-side programming in web browsers, it is now widely used in
 server-side programming~\cite{nodejs} and even in embedded
-systems~\cite{espruino, tessel2, moddable}.  Thus, its engines are also
-developed and maintained in diverse fields conforming to ECMAScript, the
-JavaScript standard specification that describes the syntax and semantics of
-JavaScript.
+systems~\cite{espruino, tessel2, moddable}.  Developers in diverse fields
+build and maintain JavaScript engines conforming to ECMAScript, the
+JavaScript standard specification, which describes the syntax and semantics of
+JavaScript in a natural language.
 
-The correctness of ECMAScript becomes more important because an incorrect
-description of syntax or semantics in the specification can lead to the wrong
-implementation of existing JavaScript engines used in various fields.  However,
-all the specification updates are currently manually checked by the Ecma
-Technical Committee 39 (TC39) without any automated tools.  This manual checking
-process is obviously labor-intensive and also error-prone thus the current
-JavaScript specification is vulnerable to specification bugs.  Besides, in late
-2014, the committee announced yearly release cadence and open development
-process of ECMAScript to quickly adapt to an evolving development environment.
+The correctness of ECMAScript is critical because an incorrect
+description in the specification can lead to wrong
+implementations of JavaScript engines in various fields.  However,
+all the specification updates are currently manually reviewed by the Ecma
+Technical Committee 39 (TC39) without any automated tools.
+Such a manual review process is inherently labor-intensive and error-prone,
+making ECMAScript vulnerable to specification bugs.
+Besides, in late 2014, the committee announced the yearly release cadence and open development
+process of ECMAScript to quickly adapt to evolving development environments.
 According to \citet{jiset}, the average number of updated steps of abstract
-algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019
-(ES10) is 9645.5.  In the official repository of ECMAScript, \inred{1,355} pull
-requests and \inred{2,005} commits exist in the master branch.  Therefore, it
-makes more difficult to manually check all the specification updates using
-limited human resources.
+algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.
+In the official ECMAScript repository, \inred{1,355} pull
+requests and \inred{2,005} commits exist in the master branch.
+Therefore, manually checking all the frequent specification updates is
+a challenging task.
 
-Unfortunately, there is no existing tool to automatically detect bugs in the
-rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
-have tried to resolve this problem using additional annotations in abstract
-algorithms.  Additional annotations make the specification more readable and
-also they are useful for the specification-based tools such as JavaScript
+Unfortunately, no existing tools can automatically detect bugs in
+rapidly evolving JavaScript specifications written in English. Thus,
+the ECMAScript committee has pursued various manual annotations in
+abstract algorithms to reduce specification bugs.
+First, the committee has introduced two kinds of annotations: 1)
+\textit{assertions} to denote assumptions at specific points of abstract
+algorithms and 2) two \textit{prefixes} \textbf{?} and \textbf{!} to
+represent whether the execution of an abstract algorithm completes
+abruptly or not. For example, ``Assert: Type(\textit{O}) is Object'' denotes that
+the variable $\textit{O}$ always has an \jscode{Object} value at the
+point of the assertion, and ``\textbf{?} \textbf{GetV}(\textit{V}, \textit{P})'' denotes that
+the execution of \textbf{GetV}(\textit{V}, \textit{P}) may complete abruptly.
+Such annotations help readers understand specifications clearly, and
+they are also helpful for specification-based tools such as JavaScript
 engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
 analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert,
-javert2}.  Thus, they decided to manually insert two different annotations: 1)
-\textit{assertions} to denote the assumptions in a certain point of abstract
-algorithms, and 2) two different \textit{prefixes} \textbf{?} and \textbf{!} to
-represent whether completion records might be abrupt or not.  For example,
-``Assert: Type(\textit{O}) is Object'' denotes that the variable $\textit{O}$
-always has an \jscode{Object} value at this point and ``\textbf{?}
-\textbf{GetV}(\textit{V}, \textit{P})'' denotes that return values of
-\textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions and directly
-return them if they are.  Moreover, they recently started the internal
-discussion of manual type annotations for variables, parameters, and return
-values for each abstract algorithm
-\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
-However, to manually annotate types for all of them without any automated tool
-is also labor-intensive and error-prone.  Furthermore, even though such manual
-type annotations can give more information for manual checking of specification
-updates, it still does not provide any automatic mechanism to detect
+javert2}\footnote{https://github.com/tc39/ecmarkup/issues/173}.
+Second, the committee has started internal discussions on type
+annotations for variables, parameters, and return values of abstract
+algorithms\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
+However, any kinds of manual annotations are labor-intensive and
+error-prone, and they do not provide any automatic mechanism to detect
 specification bugs.
@@
 \textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
-\textbf{R}efinement.  The main idea of our tool is to perform \textit{type
-analysis} for JavaScript specifications to statically detect type-related
-specification bugs in an automatic way.  However, it is difficult to directly
-perform type analysis to ECMAScript because its abstract algorithms are written
-in a natural language.  For a decade, researchers~\cite{lambdajs, jscert, kjs}
-have tried to formally define various JavaScript semantics for a specific
-version of ECMAScript by hand.  However, the manual formalization is not
-suitable for the automatic detection of bugs in the rapidly evolved JavaScript
-specifications.  To lessen such burden, several approaches to utilize
-information directly extracted from specifications written in a natural language
-are recently presented in diverse fields including system
-architectures~\cite{x86, arm}, network protocols~\cite{basespec}, and language
-specifications~\cite{spectest, javadoc}.  For JavaScript, \citet{jiset} presents
-$\jiset$ that automatically compiles each abstract algorithm written in a
-structured natural language to the corresponding function of $\ires$, an untyped
-intermediate representation for ECMAScript.  Therefore, we utilize this tool to
-mechanically handle JavaScript specifications.
+\textbf{R}efinement. In order to perform a \textit{type analysis} on ECMAScript
+to statically detect type-related specification bugs automatically,
+the main challenge is that ECMAScript describes abstract algorithms in
+a natural language, English. While researchers~\cite{lambdajs, jscert, kjs}
+have formally defined various JavaScript semantics for different
+versions of ECMAScript by hand, manual formalization is not suitable for
+automatically detecting bugs in rapidly evolving JavaScript specifications. 
+Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
+network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
+have utilized information directly extracted from specifications written in a natural language
+to lessen such burdens.
+Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
+a structured natural language to functions in $\ires$, an untyped
+intermediate representation for ECMAScript.
+Therefore, $\tool$ can handle JavaScript specifications mechanically using $\jiset$.
 
-For the compiled mechanized specifications, $\tool$ performs type analysis for
-compiled functions with specification types defined in ECMAScript.  ECMAScript
-contains not only JavaScript language types but also specification types such as
-abstract syntax trees (ASTs), internal records (e.g. environments, completions,
-or property descriptors), and internal list-like structures.  We define their
-type hierarchy and fields based on type-related tables in ECMAScript and
-automatically extracted syntax-directed algorithms.  Based on such type
-information, $\tool$ performs type analysis and detects specification bugs using
-a \textit{bug detector} consisting of four different checkers: 1) reference
-checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
-Moreover, to increase precision of type analysis, we also present a
-\textit{condition-based refinement} for type analysis on ECMAScript. Its main
-concept is to prune out infeasible parts in abstract states by using conditions
-of assertions and branches.  The refinement technique can reduce the number of
-false bugs caused by spurious types inferred by imprecise analysis.  We evaluate
-our tool with all \inred{864} different versions existed in the official
+For mechanized JavaScript specifications by $\jiset$, $\tool$ performs
+a type analysis of compiled functions using \textit{specification types}
+defined in ECMAScript. ECMAScript contains not only JavaScript
+language types but also specification types such as abstract syntax
+trees (ASTs), internal list-like structures, and internal records
+including environments, completions, and property descriptors. We
+define their type hierarchies and fields based on the type-related
+tables in ECMAScript and automatically extracted syntax-directed algorithms.
+Using such type information, $\tool$ performs a type analysis and detects specification bugs using
+a \textit{bug detector} consisting of four checkers: 1) a reference
+checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
+$\tool$ also uses a \textit{condition-based refinement} for type
+analysis, which prunes out infeasible parts in abstract states by using conditions
+of assertions and branches to improve the precision of type analysis.
+We evaluated $\tool$ with all \inred{864} versions in the official
 ECMAScript repository for the recent three years from 2018 to 2021.
+The experiments showed that the refinement technique could reduce the number of
+false-positive bugs caused by spurious types inferred by imprecise type analysis.
 
-In summary, our main contributions are as follows:
+The main contributions of this paper are as follows:
 \begin{itemize}
-  \item We present $\tool$, which is the first tool that performs \textit{type
-    analysis} on ECMAScript to check the correctness of JavaScript language
+  \item We present $\tool$, the first tool that performs a \textit{type
+    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
     specifications.  $\tool$ automatically detects type-related specification
-    bugs via the \textit{bug detector} consisting of four different checkers: 1)
-    reference checker, 2) arity checker, 3) assertion checker, and 4) operand
-    checker.
+    bugs such as unknown variables, duplicated variables, missing
+    parameters, assertion failures, ill-typed operands, and unchecked
+    abrupt completion bugs.
   \item We present a \textit{condition-based refinement} for type analysis of
-    ECMAScript to reduce the number of false bugs by increasing the analysis
-    precision.  We show that the refinement technique increase the analysis
+    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
+    precision.  We show that the refinement technique increases the analysis
     precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
@@
   \item We demonstrate the practicality of $\tool$. It takes \inred{136.1}
-    seconds on average to perform type analysis for each version, and detected
+    seconds on average to perform a type analysis for each version of ECMAScript and detected
     \inred{177} type-related specification bugs with \inred{52.0}\% precision;
-    \inred{92} out of \inred{177} bugs are true bugs.  Among them, \inred{14}
-    bugs are newly detected by $\tool$ and the committee confirmed all of them.
+    \inred{92} out of \inred{177} bugs are true bugs.  Among them, $\tool$ 
+    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
 \end{itemize}

### 2021-04-19 paper/ase21/checker.tex
[ASE21] Updated checker

@@
   \[
-    \small
     \begin{array}{c|l|r|r}
@@
       \multirow{2}{*}{\stextsf{Reference}}
-      & \text{Unknown Variables} & \inred{XXX} & \inred{XXX}\\\cline{2-4}
-      & \text{Already Defined Variables} & \inred{XXX} & \inred{XXX}\\\hline
+      & \stextsf{UnknownVar} & 5 & 12\\\cline{2-4}
+      & \stextsf{DuplicatedVar} & 2 & 12\\\hline
 
       \multirow{1}{*}{\stextsf{Arity}}
-      & \text{Arity Mismatches} & \inred{XXX} & \inred{XXX}\\\hline
+      & \stextsf{MissParam} & 2 & 4\\\hline
 
       \multirow{1}{*}{\stextsf{Assertion}}
-      & \text{Assertion Failures} & \inred{XXX} & \inred{XXX}\\\hline
+      & \stextsf{Assertion} & 4 & 5\\\hline
 
-      \multirow{2}{*}{\stextsf{Type}}
-      & \text{Non-Numeric Operands} & \inred{XXX} & \inred{XXX}\\\cline{2-4}
-      & \text{Unchecked Abrupt Completions} & \inred{XXX} & \inred{XXX}\\\hline
+      \multirow{2}{*}{\stextsf{Operand}}
+      & \stextsf{NoNumber} & 1 & 2\\\cline{2-4}
+      & \stextsf{Abrupt} & 5 & 6\\\hline
 
-      \multicolumn{2}{c|}{\textbf{Total}} & \inred{XXX} & \inred{XXX}\\
+      \multicolumn{2}{c|}{\textbf{Total}} & 19 & 41\\
 
@@
 
-% TODO: more detail of investigation
-
 We develop a \textit{bug detector} to statically detect type-related
 specification bugs in ECMAScript using an augmented abstract transfer
-$\detector$ with additional checkers.  The abstract semantics $\asem{\prog}$ of
-a program $\prog = (\getfunc, \getinst, \getnext)$ is the least fixpoint of the
-original abstract transfer $\atransfer$.  Thus, $\detector(\asem{\prog})$ also
-produces $\asem{\prog}$ and detects type-related specification bugs.  Before
-implementing checkers, we manually investigate pull requests for the recent
-\inred{three years from 2018 to 2021}.  As described in
-Table~\ref{table:pr-bugs}, \inred{XXX} pull requests existed having bugfixes of
-\inred{XXX} type-related specification bugs classified in six different kinds
-and four categories.  To detect such specification bugs, we implement four
-checkers for each category of bugs: \textit{reference checker}, \textit{arity
-checker}, \textit{assertion checker}, and \textit{operand checker}.  Now, we
-explain how each checker detects corresponding bugs in the augmented abstract
-transfer $\detector$.
+$\detector$ with additional checkers.  Before implementing checkers, we manually
+investigated pull requests for the recent three years from 2018 to 2021 to get
+insight of checkers.  As described in Table~\ref{table:pr-bugs}, there existed
+19 pull requests that fixed 41 type-related specification bugs classified in
+four categories and six kinds.  To detect such specification bugs, we implement
+four checkers for four bug categories: a \textit{reference checker}, an
+\textit{arity checker}, an \textit{assertion checker}, and an \textit{operand
+checker}.  Now, we explain how each checker detects corresponding category of
+bugs in the augmented abstract transfer $\detector$.
 
@@
 In ECMAScript abstract algorithms, variables are dynamically introduced in any
-contexts.  A \textit{reference bug} occurs when trying to access a not yet
-defined variable or to redefine an already defined variable.  According to our
-manual investigation of pull requests, the reference bug is the most prevalent
-type-related specification bugs; \inred{XXX} pull requests fixed \inred{XXX}
-unknown variable bugs and \inred{XXX} pull requests fixed \inred{XXX} already
-defined variable bugs.  We implement the reference checker by adding additional
-checks to abstract semantics of variable lookups $\aseme{\x}$ and variable
-declarations $\asemi{\kwlet \; \x = \expr}$ to detect unknown variables and
-already defined variables, respectively:
-\[
-  \small
-  \begin{array}{r@{~}c@{~}l}
+contexts.  A \textit{reference bug} occurs when trying to access not yet defined
+variables (\stextsf{UnknownVar}) or to redefine already defined variables
+(\stextsf{DuplicatedVar}).  According to our manual investigation of pull
+requests, the reference bug is the most prevalent type-related specification
+bugs; 5 pull requests fixed 12 unknown variable bugs and 2 pull requests fixed
+12 already defined variable bugs.  We implement the reference checker by adding
+additional checks to abstract semantics of variable lookups and variable
+declarations:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \resizebox{\columnwidth}{!}{$
+    \begin{array}{@{}l@{~}c@{~}l@{}}
       \aseme{\x}(\aenv) &=& \left\{
@@
     \end{array}
-\]
+  $}
+  \vspace*{-0.5em}
+\end{figure} \noindent
 If the abstract semantics of a variable lookup for $\x$ is a singleton $\{
-\tabsent \}$, it means the variable $\x$ is always an unknown variable.  In this
-case, the reference checker reports an unknown variable bug for $\x$.  For
-example, consider the syntax-directed algorithm at the upper-left in
-Figure~\ref{fig:example}.  Since the \textbf{GetReferencedName} algorithm is
-removed, the variable \code{GetReferencedName} does not exist in abstract
-environments and its lookup returns $\{ \tabsent \}$ thus the reference checker
-reports the unknown variable bug for \code{GetReferencedName}.  For already
-defined variables, the reference checker utilizes the abstract semantics of
-existence check $\aseme{\x \kwexists}$ to check whether the variable $\x$ in
-each variable declaration is already defined.
+\tabsent \}$, $\x$ is always an unknown variable.  For example, consider the
+syntax-directed algorithm at the upper-left in Figure~\ref{fig:example}.  Since
+the \textbf{GetReferencedName} algorithm is removed, the variable
+\code{GetReferencedName} does not exist in abstract environments and its lookup
+returns $\{ \tabsent \}$ thus the reference checker reports the unknown variable
+bug for \code{GetReferencedName}.  For already defined variables, the reference
+checker utilizes the abstract semantics of existence check $\aseme{\x
+\kwexists}$ to check whether the variable $\x$ of each variable declaration is
+already defined.
 
@@
 
-Arity $\size{\func}$ of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n,
-\kwsl \cdots, p_m \kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$
-and $m-n$ denote numbers of normal and optional parameters, respectively.  In
-function invocations, an \textit{arity mismatch} occurs when the number of
-arguments is not matched with the arity of a function, and \inred{XXX} pull
-requests fixed \inred{XXX} arity mismatches.  The arity checker detects such
-arity mismatches by using additional checks in the abstract semantics of
-function call instructions $\asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k
-\kwrr}$:
-\[
-  \small
-  \begin{array}{l}
-    \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k \kwrr}(\lab,
+Arity of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n, \kwsl \cdots, p_m
+\kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$ and $m-n$ denote
+numbers of normal and optional parameters, respectively.  In function
+invocations, \textit{missing parameters} (\stextsf{MissParam}) bugs occurs when
+the number of arguments is not matched with the function arity.  In three years,
+2 pull requests fixed 4 missing parameter bugs.  The arity checker detects such
+missing parameters by using additional checks in the abstract semantics of
+function call instructions:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \resizebox{\columnwidth}{!}{$
+    \begin{array}{@{}l@{}}
+      \asemi{\x = \kwrl \expr \; \expr_1 \cdots \expr_k \kwrr}(\lab,
       \tys)(\aelem) =\\
@@
           \text{missing parameters} \; \p_{k+1}, \cdots, \p_{n_\func} &
-        \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k < n_\func\\
-
-        \text{remaining arguments} \; \expr_{m_\func+1}, \cdots, \expr_k &
-        \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k > m_\func\\
+          \text{if} \; \exists \func \in \aty. \;\text{s.t.}\; k < n_\func\\
 
@@
       \right.\\
+      \qquad \text{where} \; \func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func},
+      \kwsl \cdots, p_{m_\func} \kwsr). \; \lab \;\wedge\;\\
+      \qquad \phantom{\text{where}} \; \aty = \aseme{\expr}(\aelem(\lab,
+      \tys)).\\
     \end{array}
-\]
-where $\func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func}, \kwsl \cdots,
-p_{m_\func} \kwsr). \; \lab \wedge \aty_0 = \aseme{\expr_0}(\aelem(\lab,
-\tys))$.  For each function $\func$ in the abstract semantics of the function
-expression $\expr_0$, the arity checker compares the number of arguments with
-the arity $\size{\func}$ to detect arity mismatches.  For example, consider the
-lower-left syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm
-invocation in line 2 is compiled to a function call instruction:
+  $}
+  \vspace*{-0.5em}
+\end{figure} \noindent
+For each function $\func$ in the abstract semantics of the function expression
+$\expr$, the arity checker compares the number of arguments with the arity of
+$\func$ to detect missing parameters.  For example, consider the lower-left
+syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm invocation
+in line 2 is compiled to a function call instruction:
 \[
-  \small
-  \x = \kwrl \code{formal}.\code{IteratorBindingInitialization} \; \code{formal}
-  \kwrr
+  \fcode{x = (formal.IteratorBindingInitialization formal)}
 \]
 with a temporal variable $\x$.  While it passes only a single argument
-$\code{formal}$, the arity of the function
-$\code{formal}.\code{IteratorBindingInitialization}$ is $[3, 3]$ thus the arity
-checker reports missing parameter bugs for two additional parameters
-$\code{iteratorRecord}$ and $\code{environment}$.
+$\code{formal}$, the function arity is $[3, 3]$ thus the arity checker reports
+missing parameter bugs for two additional parameters $\code{iteratorRecord}$ and
+$\code{environment}$.
 
 \subsection{Assertion Checker}
-An \textit{assertion failure} is a specification bug that occurs when the
-condition of an assertion instruction is not true.  There were \inred{XXX} pull
-requests that fixed \inred{XXX} assertion failures.  The assertion checker
+An \textit{assertion failure} (\stextsf{Assertion}) is a specification bug that
+occurs when the condition of an assertion instruction is not true.  There
+existed 4 pull requests that fixed 5 assertion failures.  The assertion checker
 detects such bugs using additional checks in the abstract semantics of assertion
-instructions $\asemi{\kwassert \; \expr}$:
-\[
-  \small
-  \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = \left\{
+instructions:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \resizebox{0.95\columnwidth}{!}{$
+    \begin{array}{@{}l@{~}l@{}}
+      \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = & \left\{
         \begin{array}{ll}
@@
         \end{array}
-  \right.\\
-\]
-where $\aty = \aseme{\expr}(\aelem(\lab, \tys))$.  It checks whether $\{ \true
-\}$ does not have partial order with the abstract semantics of the condition
-expression $\expr$.  For example, consider the lower-right syntax directed
-algorithm in Figure~\ref{fig:example}.  The parameter $\code{environment}$ of
-this algorithm has an environment record or $\undefval$.  Since type sensitivity
-divides the abstract types of arguments to upcasted single types, there are two
-different abstract environments whose variable $\code{environment}$ points to
-$\{ \text{Environment} \}$ or $\{ \undefval \}$.  When $\code{environment}$ is
-$\{ \text{Environment} \}$, the abstract semantics of assertion condition
-$\code{environment = originalEnv}$ is $\{ \tbool \}$.  Even though we know that
-the type of $\code{originalEnv}$ is also $\{ \text{Environment} \}$,
-\text{Environment} is not a singleton type thus we cannot convince that they are
-the exactly same environment.  Thus, we cannot say that the assertion must be
-failed in this case.  However, if $\code{environment}$ is $\{ \undefval \}$, the
-abstract semantics of the condition $\code{environment = originalEnv}$ is $\{
-\false \}$ because an environment is never equal to $\undefval$.  Thus, the
-assertion checker reports an assertion failure for the condition
-$\code{environment = originalEnv}$.
+      \right.\\ &
+      \text{where} \; \aty = \aseme{\expr}(\aelem(\lab, \tys))\\
+    \end{array}
+  $}
+  \vspace*{-0.5em}
+\end{figure} \noindent
+It checks whether $\{ \true \}$ does not have partial order with the abstract
+semantics of the condition expression $\expr$.  For example, consider the
+lower-right syntax directed algorithm in Figure~\ref{fig:example}.  The
+parameter $\code{environment}$ of this algorithm has an environment record or
+$\undefval$.  Since type sensitivity divides the abstract types of arguments to
+upcasted single types, there are two different abstract environments whose
+variable $\code{environment}$ points to $\{ \code{Environment} \}$ or $\{
+\undefval \}$.  When $\code{environment}$ is $\{ \code{Environment} \}$, the
+abstract semantics of assertion condition $\code{environment = originalEnv}$ is
+$\{ \tbool \}$.  Even though we know that the type of $\code{originalEnv}$ is
+also $\{ \code{Environment} \}$, \code{Environment} is not a singleton type thus
+we cannot convince that they are the exactly same environment.  Thus, we cannot
+say that the assertion must be failed in this case.  However, if
+$\code{environment}$ is $\{ \undefval \}$, the abstract semantics of the
+condition $\code{environment = originalEnv}$ is $\{ \false \}$ because an
+environment is never equal to $\undefval$.  Thus, the assertion checker reports
+an assertion failure for the condition $\code{environment = originalEnv}$.
 
@@
 
-Several operators are typed and a \textit{wrong typed operand bug} occurs when
+Several operators are typed and a \textit{ill-typed operand bug} occurs when
 the type of an operand is not conform to the expected type.  For example, the
-comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.  If
-an expression tries to compare between non-numeric values such as $\true <
-\code{"abc"}$, then it is a non-numeric operand bug.  Besides, ECMAScript has a
-special implicit conversion for normal completions when their actual values
-stored in the $\code{Value}$ field are required including conditions, values of
-field updates, operands of operators, etc.  For example, if the variable $\x$
-has a normal completion with 42 as its actual value, $\x + 1$ should 43 because
-the normal completion implicitly converted into its actual value 42.  To
-explicitly represent this conversion, let's define a unary operator $\escaped$:
-\[
-  \small
+comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.
+If an expression tries to compare between non-numeric values such as $\true <
+\code{"abc"}$, then it is a non-numeric operand bug (\stextsf{NoNumber}).
+Besides, ECMAScript has a special implicit conversion for normal completions
+when their actual values stored in the $\code{Value}$ field are required
+including conditions, values of field updates, operands of operators, etc.  For
+example, if the variable $\x$ has a normal completion with \code{42} as its
+actual value, $\code{x + 1}$ should \code{43} because the normal completion
+implicitly converted into its actual value \code{42}.  To explicitly represent
+this conversion, let's define a unary operator $\escaped$:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \resizebox{\columnwidth}{!}{$
     \escaped \val = \left\{
       \begin{array}{ll}
+        \val &
+        \text{if} \; \val \; \text{is not a completion}\\
+
         \val.\code{Value} &
-      \text{if} \; \val \; \text{is a normal completion}\\
+        \text{if} \; \val \; \text{is normal}\\
 
         \text{unchecked abrupt completion} \; \val &
-      \text{if} \; \val \; \text{is an abrupt completion}\\
-
-      \val &
         \text{otherwise}\\
@@
     \right.
-\]
+  $}
+  \vspace*{-0.5em}
+\end{figure} \noindent
 and assume that the operator $\escaped$ is used when the actual value is
-required.  Then, an unchecked abrupt completion bug occurs when the actual value
-is required but it is an abrupt completion.  According to our manual
-investigation, \inred{XXX} pull requests are related to \inred{XXX} non-numeric
-operand bugs and \inred{XXX} pull requests are related to \inred{XXX} unchecked
-abrupt completion bugs.
+required.  Then, an unchecked abrupt completion bug (\stextsf{Abrupt}) occurs
+when the actual value is required but it is an abrupt completion.  According to
+our manual investigation, 1 pull request is related to 2 non-numeric operand
+bugs and 5 pull requests are related to 6 unchecked abrupt completion bugs.
 
-The operand checker detects such wrong typed operand bugs by using additional
-checks in the abstract semantics of binary operations $\aseme{\expr \bop \expr}$
-or unary operations $\aseme{\uop \; \expr}$:
-\[
-  \small
-  \begin{array}{r@{~}c@{~}l}
+The operand checker detects such ill-typed operand bugs by using additional
+checks in the abstract semantics of binary operations and unary operations:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \resizebox{0.9\columnwidth}{!}{$
+    \begin{array}{@{}l@{~}c@{~}l@{}}
       \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \left\{
         \begin{array}{ll}
-        \text{wrong typed operand} \; \expr_0
+          \text{ill-typed operand} \; \expr_0
           & \text{if} \; \asemr{\expr_0}(\aenv) \norder \aty_0\\
-        \text{wrong typed operand} \; \expr_1
+          \text{ill-typed operand} \; \expr_1
           & \text{if} \; \asemr{\expr_1}(\aenv) \norder \aty_1\\
@@
         \begin{array}{ll}
-        \text{wrong typed operand} \; $\expr$
+          \text{ill-typed operand} \; $\expr$
           & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
@@
     \end{array}
-\]
+  $}
+  \vspace*{-0.5em}
+\end{figure} \noindent
 where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,

### 2021-04-20 paper/ase21/overview.tex
Revised Sec. 2

--- 2021-04-17 paper/ase21/overview.tex
@@
   \includegraphics[width=\columnwidth]{img/overall}
-  \caption{Overall structure of $\tool$: a type analyzer and a bug detector for
-  mechanized specifications extracted from ECMAScript by $\jiset$.}
+  \caption{$\tool$: a type analyzer and a bug detector for
+  mechanized specifications extracted from ECMAScript by $\jiset$}
   \label{fig:overall}
@@
   \centering
-  \includegraphics[width=\textwidth]{img/example}
-  \vspace*{-1.5em}
+  \includegraphics[width=.9\textwidth]{img/example}
+%  \vspace*{-1.5em}
   \caption{An example JavaScript program with related previous specification
-  bugs and their bugfixes.}
+  bugs and their bug fixes}
   \label{fig:example}
@@
 
-In this section, we demonstrate overall structure of $\tool$ depicted in
-Figure~\ref{fig:overall}.  Our tool consists of three different steps:
+In this section, we demonstrate the overall structure of $\tool$ depicted in
+Figure~\ref{fig:overall}.  It consists of three components:
 1) specification extraction, 2) type analysis, and 3) bug detection.
@@
 \subsection{Specification Extraction}\label{sec:overview-spec-extract}
+$\tool$ extracts the JavaScript syntax and semantics using $\jiset$,
+and it extracts specification types from ECMAScript.
 
-ECMAScript describes JavaScript syntax and semantics written in a structured
-natural language.  We utilize $\jiset$ to extract mechanized specification from
-a given ECMAScript.
+\paragraph{Syntax and Semantics}
+ECMAScript uses a variant of extended BNF notations to describe the JavaScript syntax.
+While $\jiset$ synthesizes AST structures and JavaScript parsers from
+the lexical and syntactic productions in ECMAScript, $\tool$ uses only
+AST structures to define their types and access corresponding syntax-directed algorithms.
+ECMAScript uses abstract algorithms written in a structured natural language to
+describe the JavaScript semantics. While $\jiset$ compiles abstract algorithms to functions in $\ires$,
+we modify $\ires$ to make it more suitable for type analysis as
+formally defined in Section~\ref{sec:ires}.
 
-\paragraph{Syntax and Semantics} ECMAScript uses a variant of extended BNF
-notations to describe JavaScript syntax.  $\jiset$ synthesizes AST structures
-and JavaScript parsers from its lexical and syntactic productions.  Our tool
-utilizes only AST structures to define their types and to access corresponding
-syntax-directed algorithms.  For JavaScript semantics, ECMAScript contains
-abstract algorithms written in a structured natural language.  $\jiset$ compiles
-them to functions of $\ires$, an untyped intermediate representation for
-ECMAScript.  We modify $\ires$ to make it more suitable for type analysis, and
-formally define its syntax and semantics in Section~\ref{sec:ires}.
-
-\paragraph{Types} In ECMAScript, types denote not only JavaScript types but also
-specification types for ASTs, records, and lists.  In abstract algorithms, ASTs
-are also values thus they can be stored in the variables or passed as arguments.
-For such ASTs, we use their production names as their types and automatically
-link corresponding syntax-directed algorithms to them as their fields.
-ECMAScript also supports various record types and their fields and possible
-values are defined in the corresponding tables.  For example, ``Table 9:
-Completion Record Fields'' in the latest ECMAScript describes fields of the
-completion records.  The latest version contains tens of tables for record types
-but they are backward compatible in general.  Thus, we manually model fields of
-record types based on the latest version to use them in type analysis.  For
-lists, we define the empty list type $\clist{}$ and parametric list types
-$\clist{\tau}$.
+\paragraph{Types}
+$\tool$ represents three kinds of specification types.
+First, because ASTs are values in abstract algorithms, 
+they can be stored in variables and passed as function arguments.
+For ASTs, we use their production names as their
+types and automatically link their corresponding syntax-directed algorithms as their fields.
+Second, ECMAScript supports various record types and fields
+whose possible values are defined in their corresponding tables.
+For example, ``Table 9: Completion Record Fields'' in the latest
+ECMAScript describes the fields of the completion records.
+% The newest version contains tens of tables for record types, and they are backward compatible in general.
+Thus, we manually model the fields of record types based on the tables
+in the latest version and use them in a type analysis.
+Third, for list-like structures, we define the empty list type
+$\clist{}$ and parametric list types $\clist{\tau}$.
 
@@
 
-The type analyzer performs type analysis with flow-sensitivity and
-type-sensitivity for parameters to precisely detect specification bugs.  It
-consists of two sub-modules: an \textit{analysis initializer} and an
-\textit{abstract transfer}.  We use a stack-based worklist algorithm to
-calculate fixpoint of abstract transfer and assign the initial set of worklist
-using analysis initializer.
+$\tool$ performs a type analysis with flow-sensitivity and
+type-sensitivity for arguments.
+Each function is split into multiple flow- and type-sensitive views, and an
+abstract state stores mapping from views to corresponding abstract environments.
+To andle views separately, we use a worklist algorithm.
+The type analyzer consists of two sub-modules: an \textit{analysis initializer} and an
+\textit{abstract transfer}.
 
-\paragraph{Analysis Initializer} In ECMAScript, there are three different kinds
-of abstract algorithms \textit{normal}, \textit{syntax-directed} and
-\textit{built-in}.  Since all the parameter types are known for built-in
-algorithms and syntax-directed algorithms having no additional parameters, we
-utilize them as entry points of type analysis.  For each entry point, the
-initializer defines its abstract environment with parameter types and push the
-pair of entry point and its abstract environment to the worklist.
+\paragraph{Analysis Initializer} It defines the initial abstract state and the
+initial set of views for a worklist. ECMAScript provides three
+kinds of abstract algorithms: \textit{normal}, \textit{syntax-directed}, and
+\textit{built-in}. Since syntax-directed algorithms and built-in algorithms have
+their parameter types, we use them as entry points of type analysis.  For each entry point, the
+initializer defines its abstract environment with parameter types and adds the
+flow- and type-sensitive views of the entry point to the worklist.
 
 \paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
-pair of a control point and its abstract environment from the worklist, produces
-other pairs based on abstract semantics, and pushes them to the worklist.  The
-iteration will be finished when the worklist becomes empty.  Moreover, to reduce
-false alarms by increasing the analysis precision, we perform refinement for
-abstract environment when the current control point is a branch or an assertion.
-The refinement will be described in detail in Section~\ref{sec:refine}.
+specific view from the worklist and udpates the abstract environments of the next
+views based on the abstract semantics.  It adds the next views to the worklist if
+it changes their abstract environments, and the iteration finishes when
+the worklist becomes empty.  To increase the analysis precision, we
+perform a condition-based refinement for an abstract environment when the current
+control point is a branch or an assertion as described in Section~\ref{sec:refine}.
 
@@
 
-To detect specification bugs based on the result of type analysis, we develop
-four different checkers in the bug detector.  We explain targets of checkers
-using an example JavaScript program with related previous specification bugs and
-their bugfixes descirbed in Figure~\ref{fig:example}.
+To detect specification bugs utilizing the type analysis, we develop
+four checkers in a bug detector.  We explain the targets of the checkers
+with an example JavaScript program that contains related previous specification bugs and
+their bug fixes, as shown in Figure~\ref{fig:example}.
 
 \paragraph{Reference Checker} The example JavaScript program first defines a
-variable \jscode{f} without initialization thus it stores \jscode{undefined}.
-Then, it assigns an arrow function to \jscode{f} using the operator
-\jscode{??=}.  While the corresponding \textbf{Evaluation} algorithm originally
-used \textbf{GetReferencedName} algorithm to get reference name at line 4.a, a
-contributor removed the \textbf{GetReferencedName} algorithm and replaced its
-all invocations to accesses of the field [[ReferencedName]] on October 28, 2020.
-However, there were several missing cases including the semantics of
-\jscode{??=} until another contributor fixed this bug on November 3, 2020.
-Thus, an unknown variable bug of \textbf{GetReferencedName} lated for 6 days.
-The reference checker detects reference bugs including unknown variable bugs.
+variable \jscode{f} without initialization, which has the value \jscode{undefined}.
+It then assigns an anonymous function to \jscode{f} using the operator \jscode{??=}.
+While the corresponding \textbf{Evaluation} algorithm originally
+used the \textbf{GetReferencedName} algorithm to get a reference name on line 4.a,
+a contributor removed the \textbf{GetReferencedName} algorithm and replaced all its
+invocations with accesses of the field [[ReferencedName]] on October 28, 2020.
+However, the contributor missed several cases including the semantics of
+\jscode{??=}, which was fixed by another contributor on November 3, 2020.
+Thus, the unknown variable bug for \textbf{GetReferencedName} existed for 7 days,
+which the reference checker can detect.
 
-\paragraph{Arity Checker} After the program assigns an arrow function to
-\jscode{f}, it calls the function with an argument \jscode{true}.  During the
-initialization of a function call, the \textbf{IteratorBindingInitialization}
-algorithm is evaluated with additional parameters \textit{iteratorRecord} and
-\textit{environment} to assigns arguments to proper parameters.  However, a
-contributor missed the additional parameters at line 2 in the
-\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September
-6, 2018.  It caused an arity mismatch bug and lasted for 532 days until another
-contributor fixed this bug on February 20, 2020.  The arity checker checks such
-arity mismatches.
+\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
+During the initialization of the function call, the \textbf{IteratorBindingInitialization}
+algorithm executes with additional parameters \textit{iteratorRecord} and
+\textit{environment} to assign argument values to parameters.
+However, a contributor missed passing additional arguments to them on line 2 in
+\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
+It caused an arity mismatch bug, which existed for 533 days until another
+contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.
 
@@
 another specification bug existed in \textbf{IteratorBindingInitialization} of
-\textit{FormalParameter}.  The additional \textit{environment} parameter might
-contains \jscode{undefined} or an environment record exactly same with
-\textit{originalEnv} as described in the assertion at line 5.  However, a
-contributor initially added the assertion without considering of
-\jscode{undefined} on \inred{XXXXXX XX, XXXX}.  Thus, the assertion failure bug
-lasted for \inred{XXXX} days until April 10, 2019.  The assertion checker checks
-whether such assertions are failed or not.
+\textit{FormalParameter}.  The additional \textit{environment} parameter may
+contain \jscode{undefined} or an environment record exactly the same as
+\textit{originalEnv} as described in the assertion on line 5.
+However, the assertion missed that the initial commit
+of the open development process on September 22, 2015 introduced
+\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.
+The assertion checker can detect such assertion failures.
 
-\paragraph{Operand Checker} The last checker checks whether operand types are
-correct for typed operators.  After the function call initialization, the
-parameter \jscode{x} points to \jscode{true} thus \jscode{Math.round} is invoked
-with the argument \jscode{true}.  The \jscode{Math.round} built-in library
-first converts the given parameter \textit{x} to the corresponding number value
-\textit{n} using \textbf{ToNumber} algorithm, and then performs remaining steps
-using the number value \textit{n}.  However, a contributor made a mistake of
-using \textit{x} instead of \textit{n} at line 3 and 4 on September 11 2020.
-According to this specification, the specification tries to compare a boolean
-value \jscode{true} with a numeric value 0.5 or 0 in the example JavaScript
-program.  Fortunately, another contributor fixed this bug after two days.  In
-the bug detector, the operand checker detects whether the operand types are
-compatible with the typed operators.
+\paragraph{Operand Checker} After the function call initialization, the
+parameter \jscode{x} has the value \jscode{true}, and \jscode{Math.round} is invoked
+with the argument \jscode{true}.  The \jscode{Math.round} built-in library first
+converts the given parameter \textit{x} to its corresponding number value
+\textit{n} using \textbf{ToNumber}, and then performs the remaining
+steps using \textit{n}.  However, a contributor mistakenly used
+\textit{x} instead of \textit{n} on lines 3 and 4 on September 11, 2020.
+This bug caused the algorithm to compare the boolean value \jscode{true} with the
+numeric value 0.5 or 0 in the example JavaScript program.
+This bug lived for two days until another contributor fixed it, and
+the operand checker can detect such bugs.
 
 In the remainder of this paper, we explain the details of how to perform type
-analysis for $\ires$ functions and how to increase analysis precision using
-refinement (Section~\ref{sec:analyzer}) and how to detect type-related
-specification bugs using four different checkers (Section~\ref{sec:checker}).
-After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
-(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).
+analysis for $\ires$ functions and how to increase the analysis precision using
+the condition-based refinement (Section~\ref{sec:analyzer}) and how to detect
+type-related specification bugs (Section~\ref{sec:checker}).  After we evaluate $\tool$
+(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
+and conclude (Section~\ref{sec:conclusion}).

### 2021-04-20 paper/ase21/overview.tex
[ASE21] Minor typos in overview

@@
 abstract state stores mapping from views to corresponding abstract environments.
-To andle views separately, we use a worklist algorithm.
+To handle views separately, we use a worklist algorithm.
 The type analyzer consists of two sub-modules: an \textit{analysis initializer} and an
@@
 \paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
-specific view from the worklist and udpates the abstract environments of the next
+specific view from the worklist and updates the abstract environments of the next
 views based on the abstract semantics.  It adds the next views to the worklist if

### 2021-04-20 paper/ase21/intro.tex
[ASE21] Moved footnote in intro

@@
 Such annotations help readers understand specifications clearly, and
-they are also helpful for specification-based tools such as JavaScript
+they are also helpful for specification-based
+tools\footnote{https://github.com/tc39/ecmarkup/issues/173} such as JavaScript
 engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
 analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert,
-javert2}\footnote{https://github.com/tc39/ecmarkup/issues/173}.
+javert2}.
 Second, the committee has started internal discussions on type

### 2021-04-20 paper/ase21/eval.tex
[ASE21] Till Conclusion
[ASE21] Updated Figure 6 and 8
[ASE21] Updated figures and tables in eval

@@
 \section{Evaluation}\label{sec:eval}
-
-\begin{table*}
-  \centering
-  \caption{The analysis precision of $\tool$ without refinement
-  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
-  difference ($\Delta$)}
-  \label{table:precision}
-  \resizebox{\textwidth}{!}{%
-  \begin{tabular}{c|c?c|c?c|c?c|c}
-    \multirow{2}{*}{\textbf{Checker}} &
-    \multirow{2}{*}{\textbf{Bug Kind}} &
-    \multicolumn{6}{c}{
-      \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
-    }\\\cline{3-8} &&
-    \multicolumn{2}{c?}{no-refine} &
-    \multicolumn{2}{c?}{refine} &
-    \multicolumn{2}{c}{$\Delta$}\\
-
-    \specialrule{.1em}{.0em}{.0em}
-
-    \myrowc{2}
-    {Reference}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
-    {UnknownVar}    {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
-    \myrowh
-    {DuplicatedVar} {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
-
-    \hline
-
-    \myrowc{1}
-    {Arity}         {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
-    {MissParam}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
-
-    \hline
-
-    \myrowc{1}
-    {Assertion}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
-    {Assertion}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
-
-    \hline
-
-    \myrowc{2}
-    {Operand}       {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
-    {NoNumber}      {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
-    \myrowh
-    {Abrupt}        {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
-
-    \specialrule{.1em}{.0em}{.0em}
-
-    \mysrowh
-    {\textbf{Total}}{43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}
-
-  \end{tabular}
-  }
-  \vspace*{-1.5em}
-\end{table*}
 
@@
 
-\begin{table}
+\begin{figure}
   \centering
+  \includegraphics[width=\columnwidth]{img/author}
   \caption{The creators and resolvers of true bugs.}
-  \label{table:author}
-  \resizebox{\columnwidth}{!}{%
-  \begin{tabular}{c|c|c?c|c|c}
-    \multicolumn{3}{c?}{\textbf{Creator}} &
-    \multicolumn{3}{c}{\textbf{Resolver}}\\\hline
-
-    \textbf{Committee} &
-    \textbf{Outsider} &
-    \textbf{Inherited} &
-    \textbf{Committee} &
-    \textbf{Outsider} &
-    \textbf{NotYet}\\\hline
-
-    \inred{60} &
-    \inred{12} &
-    \inred{20} &
-    \inred{60} &
-    \inred{23} &
-    \inred{10}\\
-  \end{tabular}
-  }
+  \label{fig:author}
   \vspace*{-1.5em}
-\end{table}
+\end{figure}
 
@@
 \end{figure}
+
+\begin{table*}
+  \centering
+  \caption{The analysis precision of $\tool$ without refinement
+  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
+  difference ($\Delta$)}
+  \label{table:precision}
+  \resizebox{\textwidth}{!}{%
+    \begin{tabular}{c|c?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l}
+      \multirow{2}{*}{\textbf{Checker}} &
+      \multirow{2}{*}{\textbf{Bug Kind}} &
+      \multicolumn{24}{c}{
+        \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
+      }\\\cline{3-26} &&
+      \multicolumn{8}{c?}{no-refine} &
+      \multicolumn{8}{c?}{refine} &
+      \multicolumn{8}{c}{$\Delta$}\\
+
+      \specialrule{.1em}{.0em}{.0em}
+
+      \myrowc
+      {\mr{2}{\stextsf{Reference}}}
+      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
+      {\mr{1}{\stextsf{UnknownVar}}}
+      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{-}{-28}{+11.1}}
+
+      \myrowh
+      {\mr{1}{\stextsf{DuplicatedVar}}}
+      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
+
+      \hline
+
+      \smyrowc
+      {\mr{1}{\stextsf{Arity}}}
+      {\mr{1}{\stextsf{MissParam}}}
+      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
+
+      \hline
+
+      \smyrowc
+      {\mr{1}{\stextsf{Assertion}}}
+      {\mr{1}{\stextsf{Assertion}}}
+      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{-}{-26}{+7.4}}
+
+      \hline
+
+      \myrowc
+      {\mr{2}{\stextsf{Operand}}}
+      {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{-}{-69}{+30.5}}
+      {\mr{1}{\stextsf{NoNumber}}}
+      {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{-}{-59}{+30.3}}
+
+      \myrowh
+      {\mr{1}{\stextsf{Abrupt}}}
+      {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{-}{-10}{+11.0}}
+
+      \specialrule{.1em}{.0em}{.0em}
+
+      \mysrowh
+      {\textbf{Total}}
+      {91 / 299 (30.4\%)}{92 / 177 (52.0\%)}{+1 / -122 (+21.5\%)}
+
+    \end{tabular}
+  }
+  \vspace*{-1.5em}
+\end{table*}
 
@@
 detected true bugs.  \inred{First, we checked that true bugs are created or
-resolved by whom as described in Table~\ref{table:author}.  Among \inred{89}
+resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{89}
 true bugs, we cannot automatically know who created \inred{20}
@@
     \includegraphics[width=\textwidth]{img/compare-time}
-    \caption{The histogram of analysis time.}
+    \caption{The histogram of time.}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{img/ratio-time}
-    \caption{The ratio of analysis time.}
+    \caption{The ratio of time.}
   \end{subfigure}
@@
 precision from \inred{23.2}\% to \inred{23.3}\% by removing \inred{10} false
-bugs and to detect \inred{10} more true bugs.  (\todo: investigate the result for
-each checker.)
+bugs and to detect \inred{10} more true bugs.  \inred{(\todo: investigate the result for
+each checker.)}
 

### 2021-04-20 paper/ase21/analyzer.tex
[ASE21] Minior update in analyzer
[ASE21] Updated checker
Revised Sec. 3

@@
 
-In this section, we explain the detail of the type analyzer in $\tool$. We first
-formally define a modified $\ires$ and explain how to perform type analysis for
-the its functions.  Moreover, we also explain a condition-based refinement of
-type analysis based on conditions of assertions and branches to increase
-analysis precision.
+This section formally defines a modified $\ires$ and its type analysis
+and presents a condition-based refinement of the type analysis to improve the analysis precision.
 
@@
   \includegraphics[width=0.48\textwidth]{img/record-fields-table}
-  \caption{Fields of completion records in ES11.}
+  \caption{Fields of completion records in ECMAScript 2020}
   \label{fig:record-fields-table}
@@
 
-$\ires$ is an untyped intermediate representation introduced by \citet{jiset}.
-To make it more suitable for type analysis, we modify it as a label-based
-language as follows:
+$\ires$ is an untyped intermediate representation for ECMAScript~\cite{jiset}.
+We modify it as a label-based language to make it suitable for type analysis as follows:
 \begin{figure}[H]
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{\columnwidth}{!}{$
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
-A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ is consists
-of three mappings from labels;  $\getfunc: \labset \rightarrow \funcset$
-represents that labels are in which functions, $\getinst: \labset \rightarrow
-\instset$ represents instructions attached to labels, and $\getnext: \labset
-\rightarrow \labset$ denotes next labels where a label $\lab \in \labset$
-denotes a program point.  function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
+A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ consists
+of three mappings;  $\getfunc: \labset \rightarrow \funcset$
+maps labels to their functions, $\getinst: \labset \rightarrow
+\instset$ maps labels to their instructions, and $\getnext: \labset
+\rightarrow \labset$ maps labels totheir next labels, where a label $\lab \in \labset$
+denotes a program point. A function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
 \lab \in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
-parameters $\y^*$, and a body label $\lab$.  Although global variables exist in
-ECMAScript, we assume that only local variables exist in this paper for brevity.
+parameters $\y^*$, and a body label $\lab$.  For presentation brevity,
+we assume that no global variables exist in this paper.
 An instruction $\inst$ is a variable declaration, a function call, an assertion,
-a branch, a return, or a reference update.  Each invocation of an abstract
-algorithm in ECMAScript is compiled to a function call instruction with a newly
-introduced temporal variable.  We represent loops using branch instructions with
-cyclic pointing of labels in the next mapping $\getnext$.  A reference $\refer$
-is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We use the
-notation $\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An
+a branch, a return, or a reference update.  An invocation of an abstract
+algorithm in ECMAScript is compiled to a function call instruction with a new
+temporary variable.  We represent loops using branch instructions with
+cyclic pointing of labels in $\getnext$.  A reference $\refer$
+is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We write
+$\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An
 expression $\expr$ is a record, a list, a type check, an existence check, a
@@
   \includegraphics[width=0.4\textwidth]{img/subtype}
-  \caption{A graphical representation of subtype relation $\subtype$.}
+  \caption{A graphical representation of the subtype relation $\subtype$}
   \label{fig:subtype}
@@
   \centering
-  \begin{subfigure}[b]{0.52\textwidth}
-    \resizebox{\textwidth}{!}{$
+  \resizebox{0.49\textwidth}{!}{$
     \begin{array}{@{}l@{~}c@{~}l}
@@
       }\\
-
+    \end{array}
+  $}
+  \resizebox{0.49\textwidth}{!}{$
+    \begin{array}{@{}l@{~}c@{~}l}
       \asemi{\kwreturn \; \expr}
@@
   $}
-    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
-    \rightarrow \adom \rightarrow \adom$.}
-  \end{subfigure}
-  \begin{minipage}[b][0.3\textheight][s]{0.46\textwidth}
-    \begin{subfigure}[b]{\textwidth}
-      \centering
-      \vspace*{0.1em}
-      \resizebox{0.8\textwidth}{!}{$
-        \begin{array}{l@{~}c@{~}l}
-          \asemr{\x}(\aenv) &=& \aenv(\x)\\
-          \asemr{\refer \kwsl \expr \kwsr}(\aenv) &=& \{ \ty[\str] \mid \ty \in
-          \asemr{\refer}(\aenv) \wedge \str \in \aseme{\expr}(\aenv) \}\\
-        \end{array}
-      $}
-      \caption{References with $\asemr{\refer}: \aenvset \rightarrow \atyset$.}
-      \vspace*{0.5em}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-      \centering
-      \resizebox{\textwidth}{!}{$
-        \begin{array}{l@{~}c@{~}l@{}}
-          \multicolumn{3}{l}{
-            \aseme{\num}(\aenv) = \tnum \qquad
-            \aseme{\bigint}(\aenv) = \tbigint \qquad
-            \aseme{\symb}(\aenv) = \tsymb
-          }\\
-
-          \multicolumn{3}{l}{
-            \aseme{\prim}(\aenv) = \prim \qquad
-            \aseme{\const}(\aenv) = \const \qquad
-            \aseme{\clist{}}(\aenv) = \clist{}
-          }\\
-
-          \multicolumn{3}{l}{
-            \aseme{\clist{\expr_0, \cdots, \expr_n}}(\aenv) = \{ \clist{\ty} \mid
-            \ty \in \bigjoin_{0 \leq i \leq n} \aseme{\expr_i}(\aenv) \}
-          }\\
-
-          \multicolumn{3}{l}{
-            \aseme{\code{Completion} \; \kwcl \cdots, \code{Type}:
-            \expr_0, \code{Value}: \expr_1, \cdots \kwcr}(\aenv) =
-          }\\
-          \multicolumn{3}{l}{
-            \qquad \left\{
-              \begin{array}{ll}
-                \{ \tnormal(\ty) \mid \ty \in \aseme{\expr_1}(\aenv) \} &
-                \text{if} \; \aseme{\expr_0} = \nconst{normal}\\
-
-                \{ \tabrupt \} &
-                \text{otherwise}\\
-              \end{array}
-            \right.
-          }\\
-
-          \aseme{\tname \; \kwcl \cdots \kwcr}(\aenv) &=& \{ \tname \}\\
-
-          \aseme{\expr: \ty}(\aenv) &=& \{ \ty' \subtype \ty \mid \ty' \in
-          \aseme{\expr}(\aenv) \}\\
-
-          \aseme{\refer \kwexists}(\aenv) &=& \{ \ty \neq \tabsent \mid \ty \in
-          \aseme{\expr}(\aenv) \}\\
-
-          \aseme{\refer}(\aenv) &=& \asemr{\refer}(\aenv) \setminus \{ \tabsent \}\\
-
-          \aseme{\uop \; \expr}(\aenv) &=& \{ \abs{\uop} \ty \mid \ty \in
-          \aseme{\expr}(\aenv) \}\\
-
-          \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \{ \ty_0 \abs{\bop} \ty_1 \mid
-          \ty_0 \in \aseme{\expr_0}(\aenv) \wedge \ty_1 \in
-          \aseme{\expr_1}(\aenv) \}\\
-        \end{array}
-      $}
-      \caption{Expressions with $\aseme{\expr}: \aenvset \rightarrow \atyset$.}
-    \end{subfigure}
-  \end{minipage}
-  \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
-  (\getfunc, \getinst, \getnext)$.}
-  \vspace*{-1.5em}
+\caption{Abstract semantics of instructions for a program $\prog = (\getfunc, \getinst, \getnext)$,
+$\asemi{\inst}: (\labset \times \tyset^*) \rightarrow \adom \rightarrow \adom$
+}
+  \vspace*{-1em}
   \label{fig:abs-sem}
@@
 
-A type $\ty \in \tyset$ is either a norminal type $\tname$, an empty list type
-$\clist{}$, a parametric list type $\clist{\ty}$, or a pre-defined type; $\tjs$
-denotes JavaScript values, $\tprim$ primitives, $\tnumeric$ either
-\jscode{Number} or \jscode{BigInt} values, and $\tnum$, $\tbigint$, $\tstr$, and
-$\tsymb$ denote \jscode{Number}, \jscode{BigInt}, \jscode{String}, and
-\jscode{Symbol} values, respectively.  A norminal type $\tname$ is either 1) an
-\textit{AST type} having corresponding syntax-directed algorithms as its fields,
-or 2) a \textit{record type} having specific fields with possible values
-described in the corresponding table and additional description in ECMAScript.
-AST types are automatically extracted but we manually model fields of record
-types.  For example, Figure~\ref{fig:record-fields-table} is an excerpt from
-ES11 that describes fields of completion records%
-\footnote{https://262.ecma-international.org/11.0/\#table-8} and we manually
-model them as follows:
+%    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
+%    \rightarrow \adom \rightarrow \adom$.}
+%  \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
+%  (\getfunc, \getinst, \getnext)$}
+
+A type $\ty \in \tyset$ is either a nominal type $\tname$, an empty list type
+$\clist{}$, a parametric list type $\clist{\ty}$,
+a JavaScript type $\tjs$,
+a primitive type $\tprim$,
+$\tnumeric$ that is either \jscode{Number} or \jscode{BigInt},
+$\tnum$, $\tbigint$, $\tstr$, or $\tsymb$.
+A nominal type $\tname$ is either 1) an
+\textit{AST type} with its corresponding syntax-directed algorithms as its fields,
+or 2) a \textit{record type} with specific fields as described in ECMAScript.
+For example, Figure~\ref{fig:record-fields-table} shows an excerpt from
+ECMAScript 2020 (ES11) that describes the fields of completion records%
+\footnote{https://262.ecma-international.org/11.0/\#table-8}, which we
+model as follows:
 
@@
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{\columnwidth}{!}{$
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure}
@@
 The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
-depicted in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
+depicted in Figure~\ref{fig:subtype}; a directed edge from $\ty'$ to $\ty$
 denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
-subtype relation is dependent on the norminal types defined in ECMAScript.  We
-extract subtypes for AST types from the JavaScript syntax and manually model
-subtypes for record types.  For example, consider the syntax-directed abstract
-algorithm at the lower-right in Figure~\ref{fig:example}.  The non-terminal
-\textit{BindingElement} is the unique token in an alternative of
-\textit{FormalParameter} production thus we automatically extract the subtype
-relation: \textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on
-this subtype relation, a type check expression $\expr: \ty$ checks whether the
-evaluation result of $\expr$ has a type $\ty'$ satisfying $\ty' \subtype \ty$.
+subtype relation is dependent on the nominal types defined in ECMAScript.  We
+extract the subtype relation for AST types from the JavaScript syntax.
+For example, consider the syntax-directed abstract
+algorithm at the lower-right part in Figure~\ref{fig:example}.
+Because the nonterminal \textit{BindingElement} is the unique alternative of the
+\textit{FormalParameter} production, we automatically extract the subtype
+relation: \textit{BindingElement} $\subtype$ \textit{FormalParameter}. Using
+the subtype relation, the expression $\expr: \ty$ checks whether the
+evaluation result of $\expr$ has type $\ty'$ satisfying $\ty' \subtype \ty$.
 
@@
 $\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
-\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$.
-For presentation brevity, we omit it in this paper and include it in a companion
-report~\inred{\cite{report}}.
+\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$
+where $\dom$ and $\valset$ denote states and values, respectively.
+For brevity, we omit it in this paper and refer the
+interested readers to a companion report~\inred{\cite{report}}.
 
@@
 
-We design a type analysis for the modified $\ires$ based on abstract
+We design a type analysis for the modified $\ires$ based on the abstract
 interpretation framework~\cite{ai1977, ai1992} with analysis
-sensitivity~\cite{sens-toplas}.  We first extend types $\tyset$ as follows:
+sensitivity~\cite{sens-toplas}.  We first extend types as follows:
 \begin{figure}[H]
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{0.8\columnwidth}{!}{$
@@
     \const \mid
-    \tnormal(\ty) \mid
-    \tabrupt \mid
     \bool \mid
     \str \mid
-    \tabsent
+    \tabsent \mid
+    \tnormal(\ty) \mid
+    \tabrupt
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
-There are three reasons why we extend types.  First, the original types $\tyset$
-do not cover all types of values thus we add functions and constants.  Second,
-we add more specific types to increase the precision of type analysis.  A
-completion record is a \textit{normal completion} when its \code{Type} field is
-$\nconst{normal}$ or an \textit{abrupt completion} otherwise.  We add
-$\tnormal(\ty)$ for normal completions whose \code{Value} field is a value of
-the type $\ty$, and $\tabrupt$ for abrupt completions.  Moreover, we also add
-\jscode{Boolean} values $\bool$, and \jscode{String} values $\str$ to precisely
-handle the control flows of branches and field accesses, respectively.  Third,
-we add the absent type $\tabsent$ to represent the existence of variables.
-Using such extended types, we define abstract states with flow-sensitivity and
+We add types for functions $\func$ and constants $\const$,
+\jscode{Boolean} values $\bool$ and \jscode{String} values $\str$ to precisely
+handle the control flows of branches and field accesses, respectively,
+the absent type $\tabsent$ to represent the absence of variables, and
+$\tnormal(\ty)$ for normal completions whose \code{Value} fields have
+type $\ty$ and $\tabrupt$ for abrupt completions to enhance the
+analysis precision.
+
+Using the extended types, we define abstract states with flow-sensitivity and
 type-sensitivity for arguments:
@@
 
-      \text{Return Points}
+      \text{Return Point Maps}
       &\retp&\in&\retpset&=& \funcset \times \tyset^*
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure}
-
+\noindent
 An abstract state $\aelem \in \adom$ is a pair of a result map and a return
-point mapping.  A result map $\rmap \in \rmapset$ represents an abstract
-environment for each flow- and type-sensitive view, and a return point mapping
+point map.  A result map $\rmap \in \rmapset$ represents an abstract
+environment for each flow- and type-sensitive view, and a return point map
 $\retp \in \retpset$ represents possible return points of each function
@@
 $\aenv(\x) = \{ \tabsent \}$ when $\x$ is not defined in $\aenv$.  An abstract
-type $\aty \in \atyset$ is a set of types.  While we define the join operator
+type $\aty \in \atyset$ is a set of types.  We define the join operator
 $\join$, the meet operator $\meet$, and the partial order $\order$ for most of
-abstract domains in a point-wise manner, we define the operators for types with
+abstract domains in a point-wise manner, and define the operators for types with
 a normalization function $\norm$ because of their subtype relations:
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
 where $\small{\norm(\aty) = \{ \ty \mid \ty \in \aty \wedge \nexists \ty' \in
-\aty. \setminus \{ \ty \}\; \text{s.t.} \; \ty \subtype \ty' \}}$.
+\aty\setminus \{ \ty \}. \; \text{s.t.} \; \ty \subtype \ty' \}}$.
 
-Based on abstract states, we define the abstract semantics of instructions,
-references, and expressions in the modified $\ires$ described in
-Figure~\ref{fig:abs-sem}.  To prevent the explosion of the number of type-sensitive
-views, we upcast the type of each argument before function calls with the
+We now define the abstract semantics of instructions $\asemi{\inst}$ in Figure~\ref{fig:abs-sem}
+and the abstract semantics of references $\asemr{\refer}$
+and expressions $\aseme{\expr}$ in a companion report~\inred{\cite{report}}.
+To avoid the explosion of type-sensitive
+views, we upcast the argument type before function calls with the
 following function:
@@
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{0.8\columnwidth}{!}{$
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
 and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
-For branches and assertions, we apply the $\pass$ function to prevent the
-infeasible control flows defined as follows:
+For branches and assertions, we use the following $\pass$ function to prevent
+infeasible control flows:
 
@@
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{0.9\columnwidth}{!}{$
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
-where $\refine$ is a function that prunes out infeasible parts in abstract
-environments based on their conditions to increase analysis precision.  We will
-explain its detail in Section~\ref{sec:refine}.  Then, we define the abstract
-semantics $\asem{\prog}$ of a program $\prog = (\getfunc, \getinst, \getnext)$
-as the least fixpoint of abstract transfer $\atransfer: \adom \rightarrow
+where $\refine$ prunes out infeasible parts in abstract
+environments using their conditions as we describe in Section~\ref{sec:refine}.
+Then, we define the abstract
+semantics $\asem{\prog}$ of a program $\prog$
+as the least fixpoint of the abstract transfer $\atransfer: \adom \rightarrow
 \adom$:
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
 where $\aelem = (\rmap, \_)$ and $\iaelem$ denotes the initial abstract state.
-As described in Section~\ref{sec:overview}, $\iaelem$ contains entry points of
-all syntax-directed algorithms having no additional parameters and built-in
-algorithms with appropriate abstract environments.  For syntax-directed
-algorithms, we construct its abstract environment containing the variable
-$\this$ with a production type and other variables for non-terminals.  For
-example, the upper-left syntax-directed algorithm in Figure~\ref{fig:example} is
+As described in Section~\ref{sec:overview}, $\iaelem$ contains the entry points of
+all syntax-directed algorithms without additional parameters and built-in
+algorithms with appropriate abstract environments.
+For a syntax-directed algorithm, we construct its abstract environment containing the variable
+$\this$ with its production type and other variables for nonterminals.
+For example, the upper-left syntax-directed algorithm in Figure~\ref{fig:example} is
 initialized with the following abstract environment:
@@
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
 For built-in algorithms, we assign pre-defined variables $\this$, $\args$, and
-$\NewTarget$ with corresponding types and parameters with $\tjs$ types.  For
+$\NewTarget$ with their corresponding types and parameters with $\tjs$ types.  For
 example, the following abstract environment is for the built-in
-algorithm $\jscode{Math.round}$ at the upper-right in Figure~\ref{fig:example}:
+algorithm $\jscode{Math.round}$ at the upper-right part in Figure~\ref{fig:example}:
 \begin{figure}[H]
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{0.9\columnwidth}{!}{$
@@
       \NewTarget &\mapsto& \{ \code{Object}, \undefval \}, &
-      \x &\mapsto& \tjs\\
+      \x &\mapsto& \{ \tjs \}\\
     \end{array}
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure}
@@
 
-We present a \textit{condition-based refinement} of type analysis for the
-modified $\ires$ to increase analysis precision.  It prunes out infeasible parts
-in abstract environments based on conditions of branches of assertions, and we
-formally define the $\refine$ function as follows:
+We present a \textit{condition-based refinement} of the type analysis for the
+modified $\ires$ to enhance the analysis precision.  It prunes out infeasible parts
+in abstract environments using the conditions of branches and assertions.
+We formally define the $\refine$ function as follows:
 \begin{figure}[H]
   \centering
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
   \resizebox{\columnwidth}{!}{$
@@
       \}]\\
-      \refine(\expr, \true)(\aenv) &=& \aenv\\
+      \refine(\expr, \bool)(\aenv) &=& \aenv\\
     \end{array}
   $}
-  \vspace{-0.5em}
+  \vspace*{-0.5em}
 \end{figure} \noindent
-where $\aenv_i = \refine(\expr_i, \bool)(\aenv)$ and $\aty_\expr =
-\aseme{\expr}(\aenv)$.  The notation $\getSingle{\aty}$ denotes to check whether
-$\aty$ is a singleton; $\getSingle{\aty} = \aty$ if $\aty = \{ \ty \}$ and $\ty$
-is a singleton type such as a constant $\const$, an empty list $\clist{}$, an
-absent value $\tabsent$, a primitive value, etc., or $\getSingle{\aty} = \emp$
-otherwise.
+where $\aenv_j = \refine(\expr_j, \bool)(\aenv)$ for $j = 0, 1$,
+$\aty_\expr = \aseme{\expr}(\aenv)$, and $\getSingle{\aty}$
+returns $\{ \ty \}$ if $\aty$ denotes a single type $\ty$, or
+returns $\emp$, otherwise.

### 2021-04-20 paper/ase21/analyzer.tex
[ASE21] Minor typo in analyzer

@@
 \instset$ maps labels to their instructions, and $\getnext: \labset
-\rightarrow \labset$ maps labels totheir next labels, where a label $\lab \in \labset$
+\rightarrow \labset$ maps labels to their next labels, where a label $\lab \in \labset$
 denotes a program point. A function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
@@
   \resizebox{0.49\textwidth}{!}{$
+\renewcommand{\arraystretch}{1.3}
     \begin{array}{@{}l@{~}c@{~}l}
@@
 }
-  \vspace*{-1em}
+  \vspace*{-.5em}
   \label{fig:abs-sem}
 \end{figure*}
-
-%    \caption{Instructions with $\asemi{\inst}: (\labset \times \tyset^*)
-%    \rightarrow \adom \rightarrow \adom$.}
-%  \caption{Abstract semantics of the modified $\ires$ for a program $\prog =
-%  (\getfunc, \getinst, \getnext)$}
 
@@
 a primitive type $\tprim$,
-$\tnumeric$ that is either \jscode{Number} or \jscode{BigInt},
+a numeric type $\tnumeric$,
 $\tnum$, $\tbigint$, $\tstr$, or $\tsymb$.
@@
 $\aty_\expr = \aseme{\expr}(\aenv)$, and $\getSingle{\aty}$
-returns $\{ \ty \}$ if $\aty$ denotes a single type $\ty$, or
+returns $\{ \ty \}$ if $\aty$ denotes a singleton type $\ty$, or
 returns $\emp$, otherwise.

### 2021-04-20 paper/ase21/eval.tex
[ASE21] Updated Table 3
[ASE21] Updating eval

@@
 \section{Evaluation}\label{sec:eval}
+
+\begin{table*}
+  \centering
+  \caption{The analysis precision of $\tool$ without refinement
+  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
+  difference ($\Delta$)}
+  \label{table:precision}
+  \resizebox{\textwidth}{!}{%
+    \begin{tabular}{c|c?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r}
+      \multirow{2}{*}{\textbf{Checker}} &
+      \multirow{2}{*}{\textbf{Bug Kind}} &
+      \multicolumn{30}{c}{
+        \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
+      }\\\cline{3-32} &&
+      \multicolumn{10}{c?}{no-refine} &
+      \multicolumn{10}{c?}{refine} &
+      \multicolumn{10}{c}{$\Delta$}\\
+
+      \specialrule{.1em}{.0em}{.0em}
+
+      \myrowc
+      {\mr{2}{\stextsf{Reference}}}
+      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
+      {\mr{1}{\stextsf{UnknownVar}}}
+      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{}{-28}{+11.1}}
+
+      \myrowh
+      {\mr{1}{\stextsf{DuplicatedVar}}}
+      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
+
+      \hline
+
+      \smyrowc
+      {\mr{1}{\stextsf{Arity}}}
+      {\mr{1}{\stextsf{MissParam}}}
+      {\me{1}{4}{4}{100.0}} {\me{1}{4}{4}{100.0}} {\me{1}{}{}{}}
+
+      \hline
+
+      \smyrowc
+      {\mr{1}{\stextsf{Assertion}}}
+      {\mr{1}{\stextsf{Assertion}}}
+      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{}{-26}{+7.4}}
+
+      \hline
+
+      \myrowc
+      {\mr{2}{\stextsf{Operand}}}
+      {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{}{-69}{+30.5}}
+      {\mr{1}{\stextsf{NoNumber}}}
+      {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{}{-59}{+30.3}}
+
+      \myrowh
+      {\mr{1}{\stextsf{Abrupt}}}
+      {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{}{-10}{+11.0}}
+
+      \specialrule{.1em}{.0em}{.0em}
+
+      \mysrowh
+      {\textbf{Total}}
+      {91 / 299 (30.4\%)}{92 / 177 (52.0\%)}{+1 / -122 (+21.5\%)}
+
+    \end{tabular}
+  }
+  \vspace*{-1.5em}
+\end{table*}
 
@@
 \jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
-for primitive types.
+for JavaScript primitive types.
 
@@
 of flow- and type-sensitive views, (c) the number of worklist iterations, and
-(d) the analysis time.  For each version of ECMAScript, \inred{1,999.9}
-functions (\stextsf{func}) are analyzed and \inred{1,999.9} functions among them
-are fully compiled (\stextsf{full-func}) on average.  Since the compile rules in
-$\jiset$ is more suitable for recent versions, the number of fully compiled
-functions in older versions are less than in more recent versions.  $\tool$
-keeps different abstract environments for each functions divided by flow- and
-type-sensitive views.  In the analysis result, \inred{1.3}M views existed for
-each version and \inred{1.3}K views existed for each function on average.
+(d) the analysis time.  For each version of ECMAScript, \inred{1,689.6}
+functions (\stextsf{analyzed}) are analyzed and \inred{1,570.0} functions among
+them are fully compiled (\stextsf{compiled}) on average.  Since ECMAScript has
+gradually evolved for three years, \inred{1,357} out of \inred{1,490} analyzed
+functions are fully compiled at the first version in 2018 but \inred{1741} out
+of \inred{1,863} analyzed functions are fully compiled in the latest version.
+$\tool$ divides functions to flow- and type-sensitive views.  On average,
+\inred{91.2}K views existed for each version and \inred{53.9} views existed for
+each function.
 
@@
 worklist algorithm and the analysis time.  For each version of ECMAScript,
-$\tool$ took \inred{300.0} seconds with \inred{19,999.9} iterations of worklist
-algorithm on average.  The analysis time consists of \inred{10.0} seconds for
-the specification extraction (\stextsf{extract} with gray bars), \inred{340.0}
-seconds for the type analysis (\stextsf{analyze} with blue bars), \inred{10.0}
-seconds for the bug detection (\stextsf{detect} with red bars).
+$\tool$ took \inred{136.0} seconds with \inred{298.8}K iterations of worklist
+algorithm on average.  The average analysis time consists of \inred{8.0} seconds
+for the specification extraction (\stextsf{extract} with gray bars),
+\inred{127.0} seconds for the type analysis (\stextsf{analyze} with blue bars),
+\inred{0.7} seconds for the bug detection (\stextsf{detect} with red bars).
 
@@
 
-\begin{table*}
-  \centering
-  \caption{The analysis precision of $\tool$ without refinement
-  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
-  difference ($\Delta$)}
-  \label{table:precision}
-  \resizebox{\textwidth}{!}{%
-    \begin{tabular}{c|c?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l}
-      \multirow{2}{*}{\textbf{Checker}} &
-      \multirow{2}{*}{\textbf{Bug Kind}} &
-      \multicolumn{24}{c}{
-        \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
-      }\\\cline{3-26} &&
-      \multicolumn{8}{c?}{no-refine} &
-      \multicolumn{8}{c?}{refine} &
-      \multicolumn{8}{c}{$\Delta$}\\
-
-      \specialrule{.1em}{.0em}{.0em}
-
-      \myrowc
-      {\mr{2}{\stextsf{Reference}}}
-      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
-      {\mr{1}{\stextsf{UnknownVar}}}
-      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{-}{-28}{+11.1}}
-
-      \myrowh
-      {\mr{1}{\stextsf{DuplicatedVar}}}
-      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
-
-      \hline
-
-      \smyrowc
-      {\mr{1}{\stextsf{Arity}}}
-      {\mr{1}{\stextsf{MissParam}}}
-      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
-
-      \hline
-
-      \smyrowc
-      {\mr{1}{\stextsf{Assertion}}}
-      {\mr{1}{\stextsf{Assertion}}}
-      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{-}{-26}{+7.4}}
-
-      \hline
-
-      \myrowc
-      {\mr{2}{\stextsf{Operand}}}
-      {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{-}{-69}{+30.5}}
-      {\mr{1}{\stextsf{NoNumber}}}
-      {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{-}{-59}{+30.3}}
-
-      \myrowh
-      {\mr{1}{\stextsf{Abrupt}}}
-      {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{-}{-10}{+11.0}}
-
-      \specialrule{.1em}{.0em}{.0em}
-
-      \mysrowh
-      {\textbf{Total}}
-      {91 / 299 (30.4\%)}{92 / 177 (52.0\%)}{+1 / -122 (+21.5\%)}
-
-    \end{tabular}
-  }
-  \vspace*{-1.5em}
-\end{table*}
-
 We measured the analysis precision based on the number of true bugs in
@@
 \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
-is \inred{51.7}\% because it detected \inred{190} type-related bugs and
-\inred{89} bugs are true bugs among them.  The reference checker detected the
-largest number of bugs with \inred{51.7}\% precision; it found \inred{12} true
-reference bugs for \inred{32} unknown variables (\stextsf{UnknownVar}) and
-\inred{32} already defined variables (\stextsf{DuplicatedVar}). The arity
-checker and the assertion checker found \inred{12} missing parameters
-(\stextsf{MissParam}) with \inred{90.2}\% precision and \inred{12} assertion
-failures (\stextsf{Assertion}) with \inred{90.2}\% precision, respectively.
+is \inred{52.0}\% because it detected \inred{177} type-related bugs and
+\inred{92} bugs are true bugs among them.  The reference checker detected the
+largest number of bugs with \inred{62.2}\% precision; it found \inred{61} true
+reference bugs for \inred{17} unknown variables (\stextsf{UnknownVar}) and
+\inred{44} already defined variables (\stextsf{DuplicatedVar}). The arity
+checker and the assertion checker found \inred{4} missing parameters
+(\stextsf{MissParam}) with \inred{100.0}\% precision and \inred{5} assertion
+failures (\stextsf{Assertion}) with \inred{16.1}\% precision, respectively.
 Finally, the operand checker detected two different kinds of wrong typed operand
-bugs: \inred{12} non-numeric operand bugs (\stextsf{NoNumber}) for numeric
-operators with \inred{12.3}\% precision and \inred{12} unchecked abrupt
-completion bugs (\stextsf{Abrupt}) with \inred{12.3}\% precision.
+bugs: \inred{2} non-numeric operand bugs (\stextsf{NoNumber}) for numeric
+operators with \inred{33.3}\% precision and \inred{20} unchecked abrupt
+completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.
 
@@
 detected true bugs.  \inred{First, we checked that true bugs are created or
-resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{89}
-true bugs, we cannot automatically know who created \inred{20}
-\textit{inherited} bugs, which are created before 2018.  For remaining
+resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{92}
+true bugs, \inred{47} bugs are \textit{inherited}, which means that they are
+created before 2018, and \inred{14} bugs are newly found
+
 \inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
@@
   \resizebox{\textwidth}{!}{%
-  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}c@{~}|@{~}r@{}}
+  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}r@{}}
     \multicolumn{1}{@{}c?}{\textbf{Name}} &
@@
     \multicolumn{1}{@{}c}{\textbf{Created}} &
-    \multicolumn{1}{@{}c}{\textbf{Resolved}} &
     \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}
@@
     \stextsf{Reference} &
-    \inred{2015-01-01} &
-    \inred{2015-01-01} &
-    \inred{1,999} days\\\hline
+    2015-09-22 &
+    1,996 days\\\hline
 
@@
     \stextsf{Operand} &
-    \inred{2015-01-01} &
-    \inred{2015-01-01} &
-    \inred{1,999} days\\
+    \inred{2015-09-22} &
+    \inred{1,996 days}\\
   \end{tabular}

### 2021-04-20 src/main/scala/kr/ac/kaist/jiset/analyzer/AbsState.scala
Implement pop in AbsState

@@ -194,7 +194,14 @@ case class AbsState(
   def append(t: AbsType, list: AbsType): AbsState = notyet("append")
   def prepend(t: AbsType, list: AbsType): AbsState = notyet("prepend")
   def delete(ref: AbsRef): AbsState = notyet("delete")
-  def pop(list: AbsType, k: AbsType): (AbsType, AbsState) = notyet(Absent, "pop")
+  def pop(list: AbsType, k: AbsType): (AbsType, AbsState) = {
+    if (k !⊑ NumericT) warning(s"invalid pop index: ${k}")
+    val ty = list.set.foldLeft(AbsType.Bot) {
+      case (ty, ListT(elem)) => ty ⊔ elem
+      case (ty, _) => warning(s"invalid pop expression: ${list}"); ty
+    }
+    (ty, this)
+  }
 
   // typeof operation
   def typeof(t: AbsType): AbsType = norm(AbsType(for {

### 2021-04-20 paper/ase21/conclusion.tex
[ASE21] Till conclusion

@@
 official ECMAScript repository for the recent three years from 2018 to 2021.
-Our tool took \inred{230} seconds on average to perform type analysis for each
-version, and detected \inred{200} type-related specification bugs with
-\inred{50.3}\% precision; \inred{91} out of \inred{200} bugs are true bugs.
-Among them, \inred{14} bugs are newly detected by $\tool$ and the committee
+Our tool took \inred{136.0} seconds on average to perform type analysis for each
+version, and detected \inred{177} type-related specification bugs with
+\inred{52.0}\% precision; \inred{92} out of \inred{177} bugs are true bugs.
+Among them, \inred{14} bugs are newly detected by $\tool$, and the committee
 confirmed all of them.

### 2021-04-20 paper/ase21/eval.tex
[ASE21] Till conclusion

@@
   \item RQ2. \textbf{(Precision)} How many type-related specification bugs
-    detcted by $\tool$ are true bugs?
+    detected by $\tool$ are true bugs?
   \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{img/author}
-  \caption{The creators and resolvers of true bugs.}
-  \label{fig:author}
-  \vspace*{-1.5em}
-\end{figure}
+% \begin{table}
+%   \centering
+%   % \includegraphics[width=\columnwidth]{img/author}
+%   \caption{The creators and resolvers of true bugs.}
+%   \label{fig:author}
+%   \resizebox{\columnwidth}{!}{$
+%     \inred{
+%     \begin{array}{c?r|r|r|r|r|r?c?c}
+%       \textbf{Rank} >
+%       & 0 & 10 & 20 & 30 & 40 & 50
+%       & \multicolumn{1}{c?}{\multirow{2}{*}{\textbf{Total}}}
+%       & \multicolumn{1}{c}{\multirow{2}{*}{\textbf{Unknown}}}\\\cline{1-7}
+%       \textbf{Rank} \leq
+%       & 10 & 20 & 30 & 40 & 50 & 60
+%       & & \\
+% 
+%       \specialrule{.1em}{.0em}{.0em}
+% 
+%       \textbf{\# Created}
+%       & 23 & 4 & 1 & 14 & 2 & 1
+%       & 45 & 46\\\hline
+%       \textbf{\# Resolved}
+%       & 57 & 6 & 12 & 2 & 0 & 0
+%       & 77 & 14\\
+% 
+%     \end{array}
+%     }
+%   $}
+%   \vspace*{-1em}
+% \end{table}
 
@@
 
-Moreover, we extended $\tool$ to automatically extract more statistics of
-detected true bugs.  \inred{First, we checked that true bugs are created or
-resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{92}
-true bugs, \inred{47} bugs are \textit{inherited}, which means that they are
-created before 2018, and \inred{14} bugs are newly found
+To understand the severity of detected true bugs, we extended $\tool$ to
+automatically extract when they are created and resolved in the ECMAScript
+official repository.  We defined that a bug is \textit{created} when it exists
+in a certain version but does not exist in the right before version, it is
+\textit{resolved} vice versa, and the \textit{Time to Live (TTL)} of a bug is
+how many days they last.  Figure~\ref{fig:ttl} describes TTLs of true bugs; the
+left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
+creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
+histogram of TTLs in a logarithmic scale.  Among \inred{92} true bugs,
+\inred{47} bugs are \textit{inherited}, which means that they are created before
+2018, and \inred{14} bugs still existed in the latest ECMAScript thus they are
+newly detected bugs by $\tool$.  We will discuss details of \inred{14} newly
+found bugs in Section~\ref{sec:new-bug}.  Even though we assume that \inred{47}
+inherited bugs are created in January 1, 2018, the average TTL is \inred{409.5}
+and the maximum TTL is \inred{1,164}.  All bugs having the maximum TTL are
+inherited and newly detected bugs.
 
-\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
-Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
-outside contributors not committee members.  On the other hand, most of them
-(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
-are resolved by non-committee contributors.  Other \inred{14} bugs are newly
-found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
-statistic of true bugs is Time to Live (TTL) that denotes how many days
-specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
-the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
-creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
-histogram of TTLs in a logarithmic scale.  The average days of TTL is
-\inred{300.0} even though we assume that \inred{20} inherited bugs are created
-in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
-corresponding bug is inherited and not yet resolved in the latest version.  We
-manually investigated its creation time in the history of the official
-repository, and we discovered that it was created at the initial commit of the
-open development process in September 22, 2015.  It means that the bug actually
-existed for \inred{3,000} days.
+We investigated \inred{85} false-positive bugs to reason about why they are
+detected by $\tool$.  Among them, \inred{30} bugs are caused by the failed
+extraction of mechanized specification because of wrong writing styles.  For
+example, ECMAScript is written in HTML and $\jiset$ extracts abstract algorithms
+based on \code{emu-alg} HTML tags.  However, several abstract algorithms are
+defined with the opening tag \code{<emu-alg>} but without the closing tag
+\code{</emu-alg>}.  Thus, $\jiset$ fails to extract them and it causes
+false-positive bugs.  The remaining \inred{55} bugs are caused by imprecise type
+analysis results.  Among them, \inred{20} bugs are caused by imprecise analysis
+for conditions of assertions and branches strongly related with specific
+function calls.  For example, consider the following algorithm step in the
+algorithm \textbf{GetValue}:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \includegraphics[width=0.7\columnwidth]{img/adv-refine-example}
+  \vspace*{-0.5em}
+\end{figure} \noindent
+Since the algorithm \textbf{IsUnresolvableReference} always returns
+$\code{false}$ when the $\code{Base}$ field of a given reference record is
+$\nconst{unresolvable}$, the field access \code{V.Base} never be
+$\nconst{unresolvable}$ on line 4.a.  However, the abstract environment in type
+analysis only stores that the variable $\code{V}$ has the $\code{Reference}$
+type thus $\nconst{unresolvable}$ is also passed as the argument of
+\textbf{ToObject}.  We believe that more advanced refinement technique can
+resolve this problem by pruning out infeasible field types depending on specific
+contexts.
 
@@
 We evaluated the effectiveness of condition-based refinement based on how much
-it improved analysis precision without significant performance degradation.  To
-compare performance and precision of analysis without refinement
-(\stextsf{no-refine}) and with refinement (\stextsf{refine}), we also performed
-$\tool$ without refinement for 864 versions of ECMAScript.
+it improved analysis precision without significant performance degradation.  We
+performed $\tool$ without refinement (\stextsf{no-refine}) for 864 versions of
+ECMAScript, and compared their analysis results with the analysis with
+refinement (\stextsf{refine}).
 
@@
 \ref{fig:performance-compare}(d)) are scatter charts for their ratio.  Without
-refinement, type analysis took \inred{234.3} seconds with \inred{232}K
-iterations on average.  With refinement, it took \inred{234.3} seconds with
-\inred{232}K iterations on average.  For each version, analysis time is
-increased at least \inred{2.3}x, at most \inred{2.3}x, and \inred{2.3}x on
-average, and the number of iterations is increased at least \inred{2.3}x, at
-most \inred{2.3}x, and \inred{2.3}x on average.
+refinement, type analysis took \inred{90.9} seconds with \inred{259.1}K
+iterations on average.  For each version, the number of iterations is increased
+at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
+the analysis time is increased at least \inred{1.05}x, at most \inred{1.41}x,
+and \inred{1.98}x on average.
 
@@
 with refinement, and their difference.  The refinement improved the analysis
-precision from \inred{23.2}\% to \inred{23.3}\% by removing \inred{10} false
-bugs and to detect \inred{10} more true bugs.  \inred{(\todo: investigate the result for
-each checker.)}
+precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
+false-positive bugs and to detect \inred{one} more true bug.  Among six
+difference bug kinds, the most significant improvement is about non-numeric
+operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
+by removing \inred{59} false-positive bugs.  The refinement technique
+successfully prunes out non-numeric values in conditions for numeric types.
+The refinement also significantly increased the analysis precision for unknown
+variable bugs (\stextsf{UnknownVar}) and assertion failures
+(\stextsf{Assertion}) by removing \inred{28} and \inred{26} false-positive bugs,
+respectively.  However, there is no effect of refinement to detect missing
+parameter bugs (\stextsf{MissParam}) because it is possible to precisely analyze
+possible callee functions for each function invocation without condition-based
+refinement.
 
@@
 
-Among \inred{91} true bugs detected by $\tool$, \inred{14} bugs are newly
-detected and still exist in the latestest version of ECMAScript.
+Among \inred{92} true bugs detected by $\tool$, \inred{14} bugs are newly
+detected and still exist in the latest version of ECMAScript.
 Table~\ref{table:new-bug} summarizes the bugs categorized by their kinds and
-related JavaScript language features. It includes their TTLs, and we manually
-investigated their extact creation time if they are created before 2018.  We
-reported the newly detected bugs to TC39; all of them are confirmed by the
-committee and will be fixed in ECMAScript 2022 (ES13).
+related JavaScript language features and it also contains their TTLs. We
+manually investigated their exact creation time if they are created before
+2018.  Except two bugs in ES12-8, all bugs were introduced in the initial
+commit of the open development on September 22, 2015.  Thus, 12 newly detected
+bugs last for 1,966 days until March 9, 2021.  The other two bugs in ES12-8 were
+created when a contributor introduced the prefixes \textbf{?} and \textbf{!}
+on December 16, 2015 thus it last for 1,910 days.  We reported the newly
+detected bugs to TC39; all of them are confirmed by the committee and will be
+fixed in ECMAScript 2022 (ES13).
 
 ES12-1 contains three bugs that are due to the duplicated definition of
-variables in three different algorithms for \jscode{case} blocks of
-\jscode{switch} statements: \code{hasDuplicates} in
+variables in three different syntax-directed algorithms for \jscode{case} blocks
+of \jscode{switch} statements: \code{hasDuplicates} in
 \textbf{ContainsDuplicateLabels}, and \code{hasUndefinedLabels} in
 \textbf{ContainsUndefinedBreakTarget} and
-\textbf{ContainsUndefinedContinueTarget}.  Each \jscode{case} block optionally
-contains \jscode{case} clauses, and three algorithms perform additional stpes
-including to define \code{hasDuplicates} (or \code{hasUndefinedLabels}) when the
-clauses exist at the beginning.  However, the exactly same variable is defined
-again after the coditionally additional steps.  It means that the semantics of
-\jscode{case} blocks having \jscode{case} clauses always have reference for
-already defined variable \code{hasDuplicates} (or \code{hasUndefinedLabels}).
-ES12-2 also contains three bugs caused by the exactly same reasons in same
-abstract algorithms for \jscode{try} statements.
+\textbf{ContainsUndefinedContinueTarget}.  A \jscode{case} block optionally
+contains \jscode{case} clauses.  In the beginning of three algorithms,
+\code{hasDuplicates} (or \code{hasUndefinedLabels}) is defined if the clauses
+exist.  However, the exactly same variable is defined again after this
+conditional steps.  It means that three algorithms for \jscode{case} blocks
+having \jscode{case} clauses always have already defined variable bugs for
+\code{hasDuplicates} (or \code{hasUndefinedLabels}).  Similarly, ES12-2 also
+contains three bugs caused by the exactly same reason in same abstract
+algorithms for \jscode{try} statements.
 
-The bug in ES12-3 is a reference bug for already defined variable \code{index}
-in the abstract algorithm \textbf{CreateMappedArgumentsObject}.  For each
-function call in JavaScript programs, an \jscode{arguments} object is created by
-\textbf{CreateMappedArgumentsObject}.  In the algorithm, the variable
+The bug in ES12-3 is a reference bug for an already defined variable
+\code{index} in the abstract algorithm \textbf{CreateMappedArgumentsObject}.
+For each function call in JavaScript programs, an \jscode{arguments} object is
+created by \textbf{CreateMappedArgumentsObject}.  In the algorithm, the variable
 \code{index} is defined to handle the index of a given list of arguments.
@@
 \textbf{ArraySetLength}.  The \jscode{Array} objects are exotic, which means
-that they are not ordinay objects and have special algorithms for specific
+that they are not ordinary objects and have special algorithms for specific
 behaviors.  The two algorithms are wrapper algorithms of
@@
 \jscode{class} declaration consists of an optional class heritage with
-\jscode{extneds} keyword and a class body enclosed by curly braces.  When the
+\jscode{extends} keyword and a class body enclosed by curly braces.  When the
 optional class heritage does not exist, the variable \code{ClassHeritage} is not

### 2021-04-21 paper/ase21/checker.tex
Revised Sec. 3
Revised Sec. 4

@@
   \caption{Type-related specification bugs fixed by pull requests for the recent
-  three years from 2018 to 2021.}
+  three years from 2018 to 2021}
   \label{table:pr-bugs}
-  \vspace*{-1.5em}
+  \vspace*{-1em}
   \[
+\renewcommand{\arraystretch}{1.2}
     \begin{array}{c|l|r|r}
@@
       \multicolumn{1}{c|}{\textbf{Bug Kind}} &
-      \multicolumn{1}{c|}{\textbf{\# PR}} &
-      \multicolumn{1}{c}{\textbf{\# Bugs}}\\
-      \hline
+      \multicolumn{1}{c|}{\textbf{\# Pull Requests}} &
+      \multicolumn{1}{c}{\textbf{\# Bug Fixes}}\\
+      \hline \hline
 
-      \multirow{2}{*}{\stextsf{Reference}}
-      & \stextsf{UnknownVar} & 5 & 12\\\cline{2-4}
-      & \stextsf{DuplicatedVar} & 2 & 12\\\hline
+      \multirow{2}{*}{\stextsf{\footnotesize Reference}}
+      & \stextsf{\footnotesize UnknownVar} & 5 & 12\\\cline{2-4}
+      & \stextsf{\footnotesize DuplicatedVar} & 2 & 12\\\hline
 
-      \multirow{1}{*}{\stextsf{Arity}}
-      & \stextsf{MissParam} & 2 & 4\\\hline
+      \multirow{1}{*}{\stextsf{\footnotesize Arity}}
+      & \stextsf{\footnotesize MissingParam} & 2 & 4\\\hline
 
-      \multirow{1}{*}{\stextsf{Assertion}}
-      & \stextsf{Assertion} & 4 & 5\\\hline
+      \multirow{1}{*}{\stextsf{\footnotesize Assertion}}
+      & \stextsf{\footnotesize Assertion} & 4 & 5\\\hline
 
-      \multirow{2}{*}{\stextsf{Operand}}
-      & \stextsf{NoNumber} & 1 & 2\\\cline{2-4}
-      & \stextsf{Abrupt} & 5 & 6\\\hline
+      \multirow{2}{*}{\stextsf{\footnotesize Operand}}
+      & \stextsf{\footnotesize NoNumber} & 1 & 2\\\cline{2-4}
+      & \stextsf{\footnotesize Abrupt} & 5 & 6\\\hline \hline
 
@@
 $\detector$ with additional checkers.  Before implementing checkers, we manually
-investigated pull requests for the recent three years from 2018 to 2021 to get
-insight of checkers.  As described in Table~\ref{table:pr-bugs}, there existed
-19 pull requests that fixed 41 type-related specification bugs classified in
-four categories and six kinds.  To detect such specification bugs, we implement
-four checkers for four bug categories: a \textit{reference checker}, an
-\textit{arity checker}, an \textit{assertion checker}, and an \textit{operand
-checker}.  Now, we explain how each checker detects corresponding category of
-bugs in the augmented abstract transfer $\detector$.
+investigated pull requests for the recent three years from 2018 to 2021 to identify
+important bugs to detect.  As summarized in Table~\ref{table:pr-bugs},
+we found 19 pull requests that fixed 41 type-related specification bugs,
+and classified the bugs into four categories with six kinds.
+To detect them automatically, we implement four checkers:
+a \textit{reference checker}, an \textit{arity checker},
+an \textit{assertion checker}, and an \textit{operand checker}.
 
@@
 
-In ECMAScript abstract algorithms, variables are dynamically introduced in any
-contexts.  A \textit{reference bug} occurs when trying to access not yet defined
-variables (\stextsf{UnknownVar}) or to redefine already defined variables
-(\stextsf{DuplicatedVar}).  According to our manual investigation of pull
-requests, the reference bug is the most prevalent type-related specification
-bugs; 5 pull requests fixed 12 unknown variable bugs and 2 pull requests fixed
-12 already defined variable bugs.  We implement the reference checker by adding
-additional checks to abstract semantics of variable lookups and variable
-declarations:
+ECMAScript abstract algorithms dynamically introduce variables in any contexts.
+A \textit{reference bug} occurs when trying to access variables not yet defined (\stextsf{UnknownVar})
+or to redefine variables already defined (\stextsf{DuplicatedVar}).
+According to our manual investigation of the pull requests,
+the reference bug is the most prevalent type-related specification bugs;
+five pull requests fixed 12 unknown variable bugs and two pull requests fixed
+12 duplicated variable declaration bugs.  We implement a reference checker by adding
+additional checks to the abstract semantics of variable lookups and variable
+declarations as follows:
 \begin{figure}[H]
@@
 \end{figure} \noindent
-If the abstract semantics of a variable lookup for $\x$ is a singleton $\{
-\tabsent \}$, $\x$ is always an unknown variable.  For example, consider the
-syntax-directed algorithm at the upper-left in Figure~\ref{fig:example}.  Since
-the \textbf{GetReferencedName} algorithm is removed, the variable
+If the abstract semantics of a variable lookup for $\x$ is a singleton $\{ \tabsent \}$,
+$\x$ is always an unknown variable.  For example, consider the syntax-directed algorithm
+at the upper-left part in Figure~\ref{fig:example}.
+Since the \textbf{GetReferencedName} algorithm is removed, the variable
 \code{GetReferencedName} does not exist in abstract environments and its lookup
-returns $\{ \tabsent \}$ thus the reference checker reports the unknown variable
-bug for \code{GetReferencedName}.  For already defined variables, the reference
-checker utilizes the abstract semantics of existence check $\aseme{\x
-\kwexists}$ to check whether the variable $\x$ of each variable declaration is
+returns $\{ \tabsent \}$. Thus, the reference checker reports the unknown variable
+bug for \code{GetReferencedName}.  For duplicated variable declarations,
+the reference checker utilizes the abstract semantics of the existence check
+$\aseme{\x \kwexists}$ to see whether the variable $\x$ of each variable declaration is
 already defined.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/func}
+    \caption{The number of functions}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/view}
+    \caption{The number of views}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/iter}
+    \caption{The number of iterations}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/time}
+    \caption{The analysis time}
+  \end{subfigure}
+  \caption{The statistics of type analysis using $\tool$ for 864 versions of
+  ECMAScript}
+  \vspace*{-1em}
+  \label{fig:stat}
+\end{figure*}
 
@@
 
-Arity of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n, \kwsl \cdots, p_m
-\kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$ and $m-n$ denote
-numbers of normal and optional parameters, respectively.  In function
-invocations, \textit{missing parameters} (\stextsf{MissParam}) bugs occurs when
-the number of arguments is not matched with the function arity.  In three years,
-2 pull requests fixed 4 missing parameter bugs.  The arity checker detects such
-missing parameters by using additional checks in the abstract semantics of
-function call instructions:
+The arity of a function \mbox{\small
+$\func=\kwdef\ \f (\p_1, \cdots, \p_n, \kwsl \cdots, p_m \kwsr).\lab$}
+is an interval $[n, m]$ where $n$ and $m-n$ denote the
+numbers of normal and optional parameters, respectively.
+In function invocations, an \textit{arity bug} occurs when
+the number of arguments does not match with the function arity (\stextsf{MissingParam}).
+In the last three years, two pull requests fixed four missing parameter bugs.
+The arity checker detects them by adding an additional check to the abstract semantics of
+the function call instruction:
 \begin{figure}[H]
@@
 $\func$ to detect missing parameters.  For example, consider the lower-left
-syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm invocation
-in line 2 is compiled to a function call instruction:
+syntax-directed algorithm in Figure~\ref{fig:example}.  The algorithm invocation
+on line 2 is compiled to the following function call instruction:
 \[
@@
 \]
-with a temporal variable $\x$.  While it passes only a single argument
-$\code{formal}$, the function arity is $[3, 3]$ thus the arity checker reports
+using a temporary variable $\x$.  Because it passes only a single argument
+$\code{formal}$ even though the function arity is $[3, 3]$, the arity checker reports
 missing parameter bugs for two additional parameters $\code{iteratorRecord}$ and
@@
 An \textit{assertion failure} (\stextsf{Assertion}) is a specification bug that
-occurs when the condition of an assertion instruction is not true.  There
-existed 4 pull requests that fixed 5 assertion failures.  The assertion checker
-detects such bugs using additional checks in the abstract semantics of assertion
-instructions:
+occurs when the condition of an assertion instruction is not true.
+We found four pull requests that fixed five assertion failures.
+The assertion checker detects them using an additional check in the
+abstract semantics of the assertion instruction:
 \begin{figure}[H]
@@
 \end{figure} \noindent
-It checks whether $\{ \true \}$ does not have partial order with the abstract
-semantics of the condition expression $\expr$.  For example, consider the
-lower-right syntax directed algorithm in Figure~\ref{fig:example}.  The
-parameter $\code{environment}$ of this algorithm has an environment record or
-$\undefval$.  Since type sensitivity divides the abstract types of arguments to
+It checks whether the abstract semantics of the condition expression $\expr$ 
+subsumes $\{ \true \}$.  For example, consider the lower-right syntax-directed
+algorithm in Figure~\ref{fig:example}.  The parameter $\code{environment}$ of
+this algorithm has an environment record or $\undefval$.
+Since type sensitivity divides the abstract types of arguments to
 upcasted single types, there are two different abstract environments whose
-variable $\code{environment}$ points to $\{ \code{Environment} \}$ or $\{
-\undefval \}$.  When $\code{environment}$ is $\{ \code{Environment} \}$, the
-abstract semantics of assertion condition $\code{environment = originalEnv}$ is
-$\{ \tbool \}$.  Even though we know that the type of $\code{originalEnv}$ is
-also $\{ \code{Environment} \}$, \code{Environment} is not a singleton type thus
-we cannot convince that they are the exactly same environment.  Thus, we cannot
-say that the assertion must be failed in this case.  However, if
-$\code{environment}$ is $\{ \undefval \}$, the abstract semantics of the
+variable $\code{environment}$ points to $\{ \code{Environment} \}$ or $\{ \undefval \}$.
+When $\code{environment}$ is $\{ \code{Environment} \}$, the
+abstract semantics of the assertion condition $\code{environment = originalEnv}$ is $\{ \tbool \}$.
+Even though we know that the type of $\code{originalEnv}$ is
+also $\{ \code{Environment} \}$, because \code{Environment} is not a singleton type,
+we cannot conclude that they are the exactly same environment.
+Thus, the assertion checker does not report any bug for this case.
+However, if $\code{environment}$ is $\{ \undefval \}$, the abstract semantics of the
 condition $\code{environment = originalEnv}$ is $\{ \false \}$ because an
-environment is never equal to $\undefval$.  Thus, the assertion checker reports
-an assertion failure for the condition $\code{environment = originalEnv}$.
+environment is never equal to $\undefval$.
+Therefore, the assertion checker reports an assertion failure for
+the condition $\code{environment = originalEnv}$.
 
@@
 
-\begin{figure*}
-  \centering
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/func}
-    \caption{The number of functions.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/view}
-    \caption{The number of views.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/iter}
-    \caption{The number of iterations.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/time}
-    \caption{The analysis time.}
-  \end{subfigure}
-  \caption{The statistics of type analysis using $\tool$ for 864 versions of
-  ECMAScript.}
-  \vspace*{-1.5em}
-  \label{fig:stat}
-\end{figure*}
-
-Several operators are typed and a \textit{ill-typed operand bug} occurs when
-the type of an operand is not conform to the expected type.  For example, the
-comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.
-If an expression tries to compare between non-numeric values such as $\true <
+An \textit{ill-typed operand bug} occurs when
+the type of an operand does not conform to its corresponding parameter type.
+For example, the comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.
+If an expression tries to compare non-numeric values such as $\true <
 \code{"abc"}$, then it is a non-numeric operand bug (\stextsf{NoNumber}).
 Besides, ECMAScript has a special implicit conversion for normal completions
-when their actual values stored in the $\code{Value}$ field are required
-including conditions, values of field updates, operands of operators, etc.  For
-example, if the variable $\x$ has a normal completion with \code{42} as its
-actual value, $\code{x + 1}$ should \code{43} because the normal completion
-implicitly converted into its actual value \code{42}.  To explicitly represent
-this conversion, let's define a unary operator $\escaped$:
+when their actual values stored in the $\code{Value}$ field are necessary
+such as conditions, values of field updates, and operands of operators.
+For example, if the variable $\x$ has a normal completion with \code{42} as its
+actual value, $\code{x + 1}$ should be \code{43} because the normal completion
+gets implicitly converted into its actual value \code{42}.
+To explicitly represent this conversion, we define a unary operator
+$\escaped$ as follows:
 \begin{figure}[H]
@@
 \end{figure} \noindent
-and assume that the operator $\escaped$ is used when the actual value is
-required.  Then, an unchecked abrupt completion bug (\stextsf{Abrupt}) occurs
-when the actual value is required but it is an abrupt completion.  According to
-our manual investigation, 1 pull request is related to 2 non-numeric operand
-bugs and 5 pull requests are related to 6 unchecked abrupt completion bugs.
+and assume that the operator $\escaped$ is used when the actual value is necessary.
+Then, an unchecked abrupt completion bug (\stextsf{Abrupt}) occurs
+when the actual value is necessary but it is an abrupt completion.
+According to our manual investigation, one pull request fixed two non-numeric operand
+bugs and five pull requests fixed six unchecked abrupt completion bugs.
 
-The operand checker detects such ill-typed operand bugs by using additional
-checks in the abstract semantics of binary operations and unary operations:
+The operand checker detects such ill-typed operand bugs by additional
+checks in the abstract semantics of operations:
 \begin{figure}[H]
@@
         \begin{array}{ll}
-          \text{ill-typed operand} \; $\expr$
+          \text{ill-typed operand} \; \expr\ \ \,
           & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
@@
 where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
-$\expr_1$, and $\expr$, respectively.  The additional check reports when the
-given operand does not conform to the expected types.  For example, consider the
+$\expr_1$, and $\expr$, respectively.  The additional checks report
+when a given operand does not conform to its expected type.  For example, consider the
 upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
-The parameter $\x$ has $\{ \tjs \}$ and $\n$ has $\{ \tnum \}$ because the
-\textbf{ToNumber} algorithm always return number values or abrupt completions
-but later cases are removed by the \textbf{ReturnIfAbrupt} prefix ?.  While the
-built-in algorithm correctly uses $\n$ in line 2, it misuses $\x$ in line 3 and
-4 and $\{ \tjs \}$ does not have a partial order with the expected abstract type
-$\{ \tnum, \tbigint \}$.  Thus, the operand type checker reports non-numeric
-operand bugs.
+The types of $\x$ and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the
+\textbf{ToNumber} algorithm always returns number values or abrupt completions,
+and the prefix ? of \textbf{ReturnIfAbrupt} removes the latter case.
+The built-in algorithm misuses $\x$ rather than $\n$ on lines 3 and 4,
+and because the expected abstract type $\{ \tnum, \tbigint \}$ does not subsume $\{ \tjs \}$,
+the operand checker reports non-numeric operand bugs.

### 2021-04-21 paper/ase21/checker.tex
[ASE21] Minor typo in checker

@@
 \[
-  \fcode{x = (formal.IteratorBindingInitialization formal)}
+  \fcode{x = (formals.IteratorBindingInitialization formals)}
 \]
 using a temporary variable $\x$.  Because it passes only a single argument
-$\code{formal}$ even though the function arity is $[3, 3]$, the arity checker reports
+$\code{formals}$ even though the function arity is $[3, 3]$, the arity checker reports
 missing parameter bugs for two additional parameters $\code{iteratorRecord}$ and

### 2021-04-21 paper/ase21/abstract.tex
[ASE21] Updating eval
[ASE21] Updated numbers except eval.tex

@@
   evaluated $\tool$ with all 864 versions in the official ECMAScript repository
-  for the recent three years from 2018 to 2021.  $\tool$ took \inred{136.1}
+  for the recent three years from 2018 to 2021.  $\tool$ took \inred{137.3}
   seconds on average to perform type analysis for each version, and detected
-  \inred{177} type-related specification bugs with \inred{52.0}\% precision;
-  \inred{92} out of \inred{177} bugs are true bugs.  Among them, \inred{14}
+  \inred{161} type-related specification bugs with \inred{56.5}\% precision;
+  \inred{91} out of \inred{161} bugs are true bugs.  Among them, \inred{14}
   bugs are newly detected by $\tool$, and the committee confirmed them all.

### 2021-04-21 paper/ase21/conclusion.tex
[ASE21] Updated numbers except eval.tex

@@
 official ECMAScript repository for the recent three years from 2018 to 2021.
-Our tool took \inred{136.0} seconds on average to perform type analysis for each
-version, and detected \inred{177} type-related specification bugs with
-\inred{52.0}\% precision; \inred{92} out of \inred{177} bugs are true bugs.
+Our tool took \inred{137.3} seconds on average to perform type analysis for each
+version, and detected \inred{161} type-related specification bugs with
+\inred{56.5}\% precision; \inred{91} out of \inred{161} bugs are true bugs.
 Among them, \inred{14} bugs are newly detected by $\tool$, and the committee

### 2021-04-21 paper/ase21/intro.tex
[ASE21] Updating eval
[ASE21] Updated numbers except eval.tex

@@
     precision.  We show that the refinement technique increases the analysis
-    precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
+    precision from \inred{31.8}\% to \inred{56.5}\% by removing \inred{122}
     false bugs and detecting \inred{one} more true bug.
-  \item We demonstrate the practicality of $\tool$. It takes \inred{136.1}
+  \item We demonstrate the practicality of $\tool$. It takes \inred{137.3}
     seconds on average to perform a type analysis for each version of ECMAScript and detected
-    \inred{177} type-related specification bugs with \inred{52.0}\% precision;
-    \inred{92} out of \inred{177} bugs are true bugs.  Among them, $\tool$ 
+    \inred{161} type-related specification bugs with \inred{56.5}\% precision;
+    \inred{91} out of \inred{161} bugs are true bugs.  Among them, $\tool$
     newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.

### 2021-04-21 paper/ase21/intro.tex
[ASE21] Removed natbib package

@@
 process of ECMAScript to quickly adapt to evolving development environments.
-According to \citet{jiset}, the average number of updated steps of abstract
+According to Park et al.~\cite{jiset}, the average number of updated steps of abstract
 algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.

### 2021-04-21 paper/ase21/related.tex
[ASE21] Removed natbib package

@@
 abstract semantics of JavaScript semantics described in ECMAScript to statically
-analyze given JavaScript programs in a finite time.  \citet{jsexplain} presented
-JSExplain, a debugger for JavaScript, by implementing a reference interpreter in
-OCaml directly conforms to algorithm steps in ECMAScript.  For a given
-JavaScript program, the debugger produces execution traces interactively
-invesitgated in a browser, with an interface that displays not only the code and
-the state of the interpreter.  \citet{javert} introduced JaVerT, a JavaScript
-verification toolchain, based on separation logic with their own intermediate
-goto language JSIL.  Moreover, JaVerT 2.0~\cite{javert2} extends it to support
-compositional symbolic execution for JavaScript based on bi-abduction.  However,
-all of them manually handles ECMAScript with their own intermediate
-representations thus many of them still targets ES5.1, the most famous old
-version of ECMAScript released in 2011, not the latest one.
+analyze given JavaScript programs in a finite time.  Chargu{\'e}raud et
+al.~\cite{jsexplain} presented JSExplain, a debugger for JavaScript, by
+implementing a reference interpreter in OCaml directly conforms to algorithm
+steps in ECMAScript.  For a given JavaScript program, the debugger produces
+execution traces interactively invesitgated in a browser, with an interface that
+displays not only the code and the state of the interpreter.  Fragoso Santos et
+al.~\cite{javert} introduced JaVerT, a JavaScript verification toolchain, based
+on separation logic with their own intermediate goto language JSIL.  Moreover,
+JaVerT 2.0~\cite{javert2} extends it to support compositional symbolic execution
+for JavaScript based on bi-abduction.  However, all of them manually handles
+ECMAScript with their own intermediate representations thus many of them still
+targets ES5.1, the most famous old version of ECMAScript released in 2011, not
+the latest one.
 
@@
 of small-sized low-level assembly languages for x86~\cite{x86} and
-ARM~\cite{arm}.  For Java API functions, \citet{javadoc} presented a technique
-to automatically extract models from their documentation using NLP techniques.
-Instead of specific API functions, \citet{jiset} presented $\jiset$, a tool that
-extracts mechanized language specification from ECMAScript.  While previous
-JavaScript formal semantics~\cite{lambdajs, jscert, kjs} were manually defined,
-$\jiset$ automatically extracts formal semantics directly from ECMAScript.  We
-utilized $\jiset$ to perform type analysis for diverse versions of ECMAScript in
-$\tool$.
+ARM~\cite{arm}.  For Java API functions, Zhai et al.~\cite{javadoc} presented a
+technique to automatically extract models from their documentation using NLP
+techniques.  Instead of specific API functions, Park et al.~\cite{jiset}
+presented $\jiset$, a tool that extracts mechanized language specification from
+ECMAScript.  While previous JavaScript formal semantics~\cite{lambdajs, jscert,
+kjs} were manually defined, $\jiset$ automatically extracts formal semantics
+directly from ECMAScript.  We utilized $\jiset$ to perform type analysis for
+diverse versions of ECMAScript in $\tool$.
 
@@
 Several researchers utilized specifications to test their implementations.  For
-network protocols, \citet{basespec} proposed a novel approach named
+network protocols, Kim et al.~\cite{basespec} proposed a novel approach named
 \textsc{BaseSpec}, which extracts message structures from tables in cellular
 specifications for L3 protocols to perform comparative analysis with baseband
-software.  \citet{spectest} presented SpecTest that utilized an executable
-language semantics to perform fuzzing for Java and Solidity compilers.  For
-JavaScript, \citet{comfort} presented \textsc{Comfort}, a compiler fuzzing
-framework to detect JavaScript engine bugs using ECMAScript with deep
-learning-based language models.  \citet{jest} extended $\jiset$ to $\jest$ that
-performs $N$+1-version differential testing with a reference interpreter
-extracted from ECMAScript and $N$ different JavaScript engines.  $\jest$ detects
-not only engine bugs but also specification bugs in ECMAScript based on the
-cross-referencing oracle.  However, it requires multiple JavaScript engines and
-takes dozens of hours to cover semantics for each version of ECMAScript.
-Instead, $\tool$ can detect specification bugs without JavaScript engines less
-than 5 minutes.  Moreover, $\tool$ utilizes abstract semantics instead of
-concrete semantics used in $\jest$ thus it can quickly cover more semantics.
+software.  Schumi and Sun~\cite{spectest} presented SpecTest that utilized an
+executable language semantics to perform fuzzing for Java and Solidity
+compilers.  For JavaScript, Ye et al.~\cite{comfort} presented \textsc{Comfort}, a
+compiler fuzzing framework to detect JavaScript engine bugs using ECMAScript
+with deep learning-based language models.  Park et al.~\cite{jest} extended
+$\jiset$ to $\jest$ that performs $N$+1-version differential testing with a
+reference interpreter extracted from ECMAScript and $N$ different JavaScript
+engines.  $\jest$ detects not only engine bugs but also specification bugs in
+ECMAScript based on the cross-referencing oracle.  However, it requires multiple
+JavaScript engines and takes dozens of hours to cover semantics for each version
+of ECMAScript.  Instead, $\tool$ can detect specification bugs without
+JavaScript engines less than 5 minutes.  Moreover, $\tool$ utilizes abstract
+semantics instead of concrete semantics used in $\jest$ thus it can quickly
+cover more semantics.

### 2021-04-21 paper/ase21/report/abstract.tex
[ASE21] Init report

\begin{abstract}
  In this report, we formally define a modified $\ires$ with its syntax and
  semantics.  Moreover, we define type analysis for the modified $\ires$.
\end{abstract}

### 2021-04-21 paper/ase21/report/syntax.tex
[ASE21] Init report

--- 2021-04-20 paper/ase21/analyzer.tex
@@
-\section{Type Analyzer}\label{sec:analyzer}
-
-This section formally defines a modified $\ires$ and its type analysis
-and presents a condition-based refinement of the type analysis to improve the analysis precision.
-
-\subsection{Intermediate Representation}\label{sec:ires}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.48\textwidth]{img/record-fields-table}
-  \caption{Fields of completion records in ECMAScript 2020}
-  \label{fig:record-fields-table}
-  \vspace*{-1.5em}
-\end{figure}
-
-$\ires$ is an untyped intermediate representation for ECMAScript~\cite{jiset}.
-We modify it as a label-based language to make it suitable for type analysis as follows:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
+\section{Syntax}\label{sec:syntax}
+We first define syntax of the modified $\ires$ as follows:
+\[
+  \vspace*{-1em}
   \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
@@
     \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
+    \vspace*{1em}
   \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ consists
-of three mappings;  $\getfunc: \labset \rightarrow \funcset$
-maps labels to their functions, $\getinst: \labset \rightarrow
-\instset$ maps labels to their instructions, and $\getnext: \labset
-\rightarrow \labset$ maps labels to their next labels, where a label $\lab \in \labset$
-denotes a program point. A function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
-\lab \in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
-parameters $\y^*$, and a body label $\lab$.  For presentation brevity,
-we assume that no global variables exist in this paper.
-An instruction $\inst$ is a variable declaration, a function call, an assertion,
-a branch, a return, or a reference update.  An invocation of an abstract
-algorithm in ECMAScript is compiled to a function call instruction with a new
-temporary variable.  We represent loops using branch instructions with
-cyclic pointing of labels in $\getnext$.  A reference $\refer$
-is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We write
-$\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An
-expression $\expr$ is a record, a list, a type check, an existence check, a
-binary operation, a unary operation, a reference, a constant, or a primitive,
-which is either $\undefval$, $\nullval$, a \jscode{Boolean} $\bool$, a
-\jscode{Number} $\num$, a \jscode{BigInt} $\bigint$, a \jscode{String} $\str$,
-or a \jscode{Symbol} $\symb$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.4\textwidth]{img/subtype}
-  \caption{A graphical representation of the subtype relation $\subtype$}
-  \label{fig:subtype}
-  \vspace*{-1.5em}
-\end{figure}
-
-\begin{figure*}[t]
-  \centering
-  \resizebox{0.49\textwidth}{!}{$
-\renewcommand{\arraystretch}{1.3}
-    \begin{array}{@{}l@{~}c@{~}l}
-      \asemi{\kwlet \; \x = \expr}
-      (\lab, \tys)(\aelem) &=&
-      (\{ (\getnext(\lab), \tys) \mapsto \aenv[\x \mapsto
-      \aseme{\expr}(\aenv)] \}, \emp)\\
-
-      \asemi{\x = \kwrl \expr \; \expr_1 \cdots \expr_n \kwrr}
-      (\lab, \tys)(\aelem) &=& (\rmap', \retp')\\
-      \multicolumn{3}{@{}l}{
-        \text{where} \;
-        \left\{
-          \begin{array}{l@{}}
-            \aty = \aseme{\expr}(\aenv) \;\wedge\;
-            \aty_1 = \aseme{\expr_1}(\aenv) \;\wedge\;
-            \cdots \;\wedge\;
-            \aty_n = \aseme{\expr_n}(\aenv) \;\wedge\;\\
-
-            T' = \{ \upcasts([ \ty_1, \cdots, \ty_n ]) \mid \ty_1 \in \aty_1
-            \;\wedge\; \cdots \;\wedge\; \ty_n \in \aty_n \} \;\wedge\;\\
-
-            \func = \kwdef \; \f (\p_1, \cdots, \kwsl \cdots, \p_{m_\func}
-            \kwsr). \; \lab_\func \;\wedge\;\\
-
-            \aenv_{\func, \tys'} = [\p_1 \mapsto \{ \tys'[1] \}, \cdots,
-            \p_{m_\func} \mapsto \{ \tys'[m] \}] \;\wedge\;\\
-
-            \rmap' = \{ (\lab_\func, \tys') \mapsto \aenv_{\func, \tys'}
-            \mid \func \in \aty \;\wedge\; \tys' \in T' \} \;\wedge\;\\
-
-            \retp' = \{ (\func, \tys') \mapsto \{ (\getnext(\lab), \tys, \x)
-            \} \mid \func \in \aty \;\wedge\; \tys' \in T' \}\\
-          \end{array}
-        \right.
-      }\\
-    \end{array}
-  $}
-  \resizebox{0.49\textwidth}{!}{$
-\renewcommand{\arraystretch}{1.3}
-    \begin{array}{@{}l@{~}c@{~}l}
-      \asemi{\kwreturn \; \expr}
-      (\lab, \tys)(\aelem) &=&
-      (\{ (\lab_r, \tys_r) \mapsto \aenv_r \mid
-      (\lab_r, \tys_r, \x) \in R\}, \emp)\\
-      \multicolumn{3}{@{}l}{
-        \text{where} \; R = \retp(\getfunc(\lab), \tys) \;\wedge\; \aenv_r =
-        \rmap(\lab_r, \tys_r)[\x \mapsto \aseme{\expr}(\aenv)]
-      }\\
-
-      \asemi{\kwassert \; \expr}
-      (\lab, \tys)(\aelem) &=&
-      (\{ (\getnext(\lab), \tys) \mapsto \pass(\expr, \true)(\aenv) \}, \emp)\\
-
-      \asemi{\kwif \; \expr \; \lab_\mt \; \lab_\mf}
-      (\lab, \tys)(\aelem) &=&
-      (\{ (\lab_\mt, \tys) \mapsto \pass(\expr, \true)(\aenv),\\ &&
-      \phantom{(\{} (\lab_\mf, \tys) \mapsto \pass(\expr, \false)(\aenv) \}, \emp)\\
-
-      \asemi{\x = \expr}
-      (\lab, \tys)(\aelem) &=&
-      (\{ (\getnext(\lab), \tys) \mapsto \aenv[\x \mapsto
-      \aseme{\expr}(\aenv)] \}, \emp)\\
-
-      \asemi{\refer \kwsl \expr_0 \kwsr = \expr_1}
-      (\lab, \tys)(\aelem) &=&
-      (\{ (\getnext(\lab), \tys) \mapsto \aenv \}, \emp)\\
-
-      \multicolumn{3}{@{}l}{\text{where} \; \aelem = (\rmap, \retp) \;\wedge\;
-      \aenv = \rmap(\lab, \tys)}
-    \end{array}
-  $}
-\caption{Abstract semantics of instructions for a program $\prog = (\getfunc, \getinst, \getnext)$,
-$\asemi{\inst}: (\labset \times \tyset^*) \rightarrow \adom \rightarrow \adom$
-}
-  \vspace*{-.5em}
-  \label{fig:abs-sem}
-\end{figure*}
-
-A type $\ty \in \tyset$ is either a nominal type $\tname$, an empty list type
-$\clist{}$, a parametric list type $\clist{\ty}$,
-a JavaScript type $\tjs$,
-a primitive type $\tprim$,
-a numeric type $\tnumeric$,
-$\tnum$, $\tbigint$, $\tstr$, or $\tsymb$.
-A nominal type $\tname$ is either 1) an
-\textit{AST type} with its corresponding syntax-directed algorithms as its fields,
-or 2) a \textit{record type} with specific fields as described in ECMAScript.
-For example, Figure~\ref{fig:record-fields-table} shows an excerpt from
-ECMAScript 2020 (ES11) that describes the fields of completion records%
-\footnote{https://262.ecma-international.org/11.0/\#table-8}, which we
-model as follows:
-
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
-    \begin{array}{l}
-      \code{Completion} \code{=} \; \kwcl\\
-        \quad \Type: \{ \nconst{normal}, \nconst{break}, \nconst{continue},
-        \nconst{return}, \nconst{throw} \},\\
-        \quad \Value: \{ \tjs, \nconst{empty} \},
-        \quad \Target: \{ \tstr, \nconst{empty} \}\\
-      \kwcr\\
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure}
-
-The subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
-depicted in Figure~\ref{fig:subtype}; a directed edge from $\ty'$ to $\ty$
-denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
-subtype relation is dependent on the nominal types defined in ECMAScript.  We
-extract the subtype relation for AST types from the JavaScript syntax.
-For example, consider the syntax-directed abstract
-algorithm at the lower-right part in Figure~\ref{fig:example}.
-Because the nonterminal \textit{BindingElement} is the unique alternative of the
-\textit{FormalParameter} production, we automatically extract the subtype
-relation: \textit{BindingElement} $\subtype$ \textit{FormalParameter}. Using
-the subtype relation, the expression $\expr: \ty$ checks whether the
-evaluation result of $\expr$ has type $\ty'$ satisfying $\ty' \subtype \ty$.
-
-We define a denotational semantics of the modified $\ires$ for instructions
-$\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
-\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$
-where $\dom$ and $\valset$ denote states and values, respectively.
-For brevity, we omit it in this paper and refer the
-interested readers to a companion report~\inred{\cite{report}}.
-
-\subsection{Type Analysis}\label{sec:analysis}
-
-We design a type analysis for the modified $\ires$ based on the abstract
-interpretation framework~\cite{ai1977, ai1992} with analysis
-sensitivity~\cite{sens-toplas}.  We first extend types as follows:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{0.8\columnwidth}{!}{$
-    \tyset \ni \ty ::=
-    \cdots \mid
-    \func \mid
-    \const \mid
-    \bool \mid
-    \str \mid
-    \tabsent \mid
-    \tnormal(\ty) \mid
-    \tabrupt
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-We add types for functions $\func$ and constants $\const$,
-\jscode{Boolean} values $\bool$ and \jscode{String} values $\str$ to precisely
-handle the control flows of branches and field accesses, respectively,
-the absent type $\tabsent$ to represent the absence of variables, and
-$\tnormal(\ty)$ for normal completions whose \code{Value} fields have
-type $\ty$ and $\tabrupt$ for abrupt completions to enhance the
-analysis precision.
-
-Using the extended types, we define abstract states with flow-sensitivity and
-type-sensitivity for arguments:
-
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
-    \begin{array}{lr@{~}c@{~}c@{~}r@{~}l}
-      \text{Abstract States}
-      &\aelem&\in&\adom&=& \rmapset \times \retpset\\
-
-      \text{Result Maps}
-      &\rmap&\in&\rmapset&=& \labset \times \tyset^* \rightarrow \aenvset\\
-
-      \text{Return Point Maps}
-      &\retp&\in&\retpset&=& \funcset \times \tyset^*
-      \rightarrow \partsof{\labset \times \tyset^* \times \varset} \\
-
-      \text{Abstract Environments}
-      &\aenv&\in&\aenvset&=&\varset \rightarrow \atyset\\
-
-      \text{Abstract Types}
-      &\aty&\in&\atyset&=&\partsof{\tyset}\\
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure}
-\noindent
-An abstract state $\aelem \in \adom$ is a pair of a result map and a return
-point map.  A result map $\rmap \in \rmapset$ represents an abstract
-environment for each flow- and type-sensitive view, and a return point map
-$\retp \in \retpset$ represents possible return points of each function
-with a type-sensitive context; each return point consists of a view for the
-caller function and a variable that represents the return value.  An abstract
-environment $\aenv \in \aenvset$ represents possible types for variables, and
-$\aenv(\x) = \{ \tabsent \}$ when $\x$ is not defined in $\aenv$.  An abstract
-type $\aty \in \atyset$ is a set of types.  We define the join operator
-$\join$, the meet operator $\meet$, and the partial order $\order$ for most of
-abstract domains in a point-wise manner, and define the operators for types with
-a normalization function $\norm$ because of their subtype relations:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
-    \begin{array}{l}
-      \aty_0 \join \aty_1 = \norm(\aty_0 \cup \aty_1)\\
-      \aty_0 \meet \aty_1 = \norm(
-      \{\ty_0 \in \aty_0 \mid \{ \ty_0 \} \order \aty_1 \} \cup
-      \{\ty_1 \in \aty_1 \mid \{ \ty_1 \} \order \aty_0 \}
-      )\\
-      \aty_0 \order \aty_1 \Leftrightarrow \forall \ty_0 \in \aty_0. \; \exists
-      \ty_1 \in \norm(\aty_1). \; \text{s.t.} \; \ty_0 \subtype \ty_1\\
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-where $\small{\norm(\aty) = \{ \ty \mid \ty \in \aty \wedge \nexists \ty' \in
-\aty\setminus \{ \ty \}. \; \text{s.t.} \; \ty \subtype \ty' \}}$.
-
-We now define the abstract semantics of instructions $\asemi{\inst}$ in Figure~\ref{fig:abs-sem}
-and the abstract semantics of references $\asemr{\refer}$
-and expressions $\aseme{\expr}$ in a companion report~\inred{\cite{report}}.
-To avoid the explosion of type-sensitive
-views, we upcast the argument type before function calls with the
-following function:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{0.8\columnwidth}{!}{$
-    \upcast(\ty) = \left\{
-      \begin{array}{ll}
-        \tnormal(\upcast(\ty')) & \text{if} \; \ty = \tnormal(\ty')\\
-        \clist{\upcast(\ty')} & \text{if} \; \ty = \clist{\ty'}\\
-        \tstr & \text{if} \; \ty = \str\\
-        \tbool & \text{if} \; \ty = \bool\\
-        \ty & \text{otherwise}\\
-      \end{array}
-    \right.
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
-For branches and assertions, we use the following $\pass$ function to prevent
-infeasible control flows:
-
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{0.9\columnwidth}{!}{$
-    \pass(\expr, \bool)(\aenv) = \left\{
-      \begin{array}{ll}
-        \refine(\expr, \bool)(\aenv)
-        & \text{if} \; \{ \true \} \order \aseme{\expr}(\aenv)\\
-
-        \emp
-        & \text{otherwise}\\
-      \end{array}
-    \right.
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-where $\refine$ prunes out infeasible parts in abstract
-environments using their conditions as we describe in Section~\ref{sec:refine}.
-Then, we define the abstract
-semantics $\asem{\prog}$ of a program $\prog$
-as the least fixpoint of the abstract transfer $\atransfer: \adom \rightarrow
-\adom$:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{0.9\columnwidth}{!}{$
-    \begin{array}{r@{~}c@{~}l}
-      \asem{\prog} &=& \lim_{n \rightarrow \infty}(\atransfer)^n(\iaelem)\\
-      \atransfer(\aelem) &=& \aelem \join \left(
-        \bigjoin_{(\lab, \tys) \in \domain{\rmap}}
-        \asemi{\getinst(\lab)}(\lab, \tys)(\aelem)
-      \right)\\
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-where $\aelem = (\rmap, \_)$ and $\iaelem$ denotes the initial abstract state.
-As described in Section~\ref{sec:overview}, $\iaelem$ contains the entry points of
-all syntax-directed algorithms without additional parameters and built-in
-algorithms with appropriate abstract environments.
-For a syntax-directed algorithm, we construct its abstract environment containing the variable
-$\this$ with its production type and other variables for nonterminals.
-For example, the upper-left syntax-directed algorithm in Figure~\ref{fig:example} is
-initialized with the following abstract environment:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
-    \begin{array}{r@{~}c@{~}l}
-      \this &\mapsto& \{ \code{AssignmentExpression} \},\\
-      \code{LeftHandSideExpression} &\mapsto& \{ \code{LeftHandSideExpression} \},\\
-      \code{AssignmentExpression} &\mapsto& \{ \code{AssignmentExpression} \}
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-For built-in algorithms, we assign pre-defined variables $\this$, $\args$, and
-$\NewTarget$ with their corresponding types and parameters with $\tjs$ types.  For
-example, the following abstract environment is for the built-in
-algorithm $\jscode{Math.round}$ at the upper-right part in Figure~\ref{fig:example}:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{0.9\columnwidth}{!}{$
-    \begin{array}{r@{~}c@{~}lr@{~}c@{~}l}
-      \this &\mapsto& \{ \tjs \}, &
-      \args &\mapsto& \{ \clist{\tjs} \},\\
-      \NewTarget &\mapsto& \{ \code{Object}, \undefval \}, &
-      \x &\mapsto& \{ \tjs \}\\
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure}
-
-\subsection{Condition-based Refinement}\label{sec:refine}
-
-We present a \textit{condition-based refinement} of the type analysis for the
-modified $\ires$ to enhance the analysis precision.  It prunes out infeasible parts
-in abstract environments using the conditions of branches and assertions.
-We formally define the $\refine$ function as follows:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
-    \begin{array}{@{}r@{~}c@{~}l@{}}
-      \refine(\code{!} \expr, \bool)(\aenv) &=&
-      \refine(\expr, \neg \bool)(\aenv)\\
-
-      \refine(\expr_0 \; \code{||} \; \expr_1, \bool)(\aenv) &=&
-      \left\{
-        \begin{array}{ll}
-          \aenv_0 \join \aenv_1 & \text{if} \; \bool\\
-          \aenv_0 \meet \aenv_1 & \text{if} \; \neg\bool\\
-        \end{array}
-      \right.\\
-      \refine(\expr_0 \; \code{\&\&} \; \expr_1, \bool)(\aenv) &=&
-      \left\{
-        \begin{array}{ll}
-          \aenv_0 \meet \aenv_1 & \text{if} \; \bool\\
-          \aenv_0 \join \aenv_1 & \text{if} \; \neg\bool\\
-        \end{array}
-      \right.\\
-
-      \refine(\x.\Type \; \code{==} \; \nconst{normal}, \true)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \cap \tnormal(\tyset) ]\\
-      \refine(\x.\Type \; \code{==} \; \nconst{normal}, \false)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \cap \{ \tabrupt \} ]\\
-
-      \refine(\x \; \code{==} \; \expr, \true)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \meet \aty_\expr ]\\
-      \refine(\x \; \code{==} \; \expr, \false)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \setminus
-      \lfloor\aty_\expr\rfloor ]\\
-
-      \refine(\x : \ty, \true)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \meet \{ \ty \} ]\\
-      \refine(\x : \ty, \false)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \setminus \{ \ty' \mid \ty' \subtype \ty
-      \}]\\
-      \refine(\expr, \bool)(\aenv) &=& \aenv\\
-    \end{array}
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-where $\aenv_j = \refine(\expr_j, \bool)(\aenv)$ for $j = 0, 1$,
-$\aty_\expr = \aseme{\expr}(\aenv)$, and $\getSingle{\aty}$
-returns $\{ \ty \}$ if $\aty$ denotes a singleton type $\ty$, or
-returns $\emp$, otherwise.
+\]

### 2021-04-21 paper/ase21/analyzer.tex
Revised Sec. 3
[ASE21] Updated citation for report

@@
 For brevity, we omit it in this paper and refer the
-interested readers to a companion report~\inred{\cite{report}}.
+interested readers to a companion report~\cite{report}.
 
@@
 and the abstract semantics of references $\asemr{\refer}$
-and expressions $\aseme{\expr}$ in a companion report~\inred{\cite{report}}.
+and expressions $\aseme{\expr}$ in a companion report~\cite{report}.
 To avoid the explosion of type-sensitive

### 2021-04-21 paper/ase21/eval.tex
Revised Sec. 5

@@
   \resizebox{\textwidth}{!}{%
-    \begin{tabular}{c|c?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r}
+    \begin{tabular}{c|l?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r}
       \multirow{2}{*}{\textbf{Checker}} &
@@
       }\\\cline{3-32} &&
-      \multicolumn{10}{c?}{no-refine} &
-      \multicolumn{10}{c?}{refine} &
+      \multicolumn{10}{c?}{\stextsf{\footnotesize no-refine}} &
+      \multicolumn{10}{c?}{\stextsf{\footnotesize refine}} &
       \multicolumn{10}{c}{$\Delta$}\\
@@
       \myrowc
-      {\mr{2}{\stextsf{Reference}}}
+      {\mr{2}{\stextsf{\scriptsize Reference}}}
       {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
-      {\mr{1}{\stextsf{UnknownVar}}}
+      {\mr{1}{\stextsf{\scriptsize UnknownVar}}}
       {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{}{-28}{+11.1}}
@@
       \myrowh
-      {\mr{1}{\stextsf{DuplicatedVar}}}
+      {\mr{1}{\stextsf{\scriptsize DuplicatedVar}}}
       {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
@@
       \smyrowc
-      {\mr{1}{\stextsf{Arity}}}
-      {\mr{1}{\stextsf{MissParam}}}
+      {\mr{1}{\stextsf{\scriptsize Arity}}}
+      {\mr{1}{\stextsf{\scriptsize MissingParam}}}
       {\me{1}{4}{4}{100.0}} {\me{1}{4}{4}{100.0}} {\me{1}{}{}{}}
@@
       \smyrowc
-      {\mr{1}{\stextsf{Assertion}}}
-      {\mr{1}{\stextsf{Assertion}}}
+      {\mr{1}{\stextsf{\scriptsize Assertion}}}
+      {\mr{1}{\stextsf{\scriptsize Assertion}}}
       {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{}{-26}{+7.4}}
@@
       \myrowc
-      {\mr{2}{\stextsf{Operand}}}
+      {\mr{2}{\stextsf{\scriptsize Operand}}}
       {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{}{-69}{+30.5}}
-      {\mr{1}{\stextsf{NoNumber}}}
+      {\mr{1}{\stextsf{\scriptsize NoNumber}}}
       {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{}{-59}{+30.3}}
@@
       \myrowh
-      {\mr{1}{\stextsf{Abrupt}}}
+      {\mr{1}{\stextsf{\scriptsize Abrupt}}}
       {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{}{-10}{+11.0}}
@@
 
-We implemented $\tool$ as an open-source tool~\footnote{The link is anonymized
-because of a double-blind review process} in Scala by extending $\jiset$, a
-JavaScript IR-based semantics extraction toolchain, with a worklist-based
-fixpoint algorithm for type analysis.  Since $\jiset$ cannot automatically
-compiles algorithm steps written in an uncommon writing style to $\ires$
-instructions, our tool only reports type-related specification bugs detected in
-fully compiled abstract algorithms.  For built-in libraries, we only targeted
-abstract algorithms of essential built-in objects: \jscode{Array},
+We implemented $\tool$ as an open-source tool\footnote{The link is anonymized
+because of a double-blind review process.} in Scala by extending $\jiset$, a
+JavaScript IR-based semantics extraction toolchain~\cite{jiset}, with a worklist-based
+fixpoint algorithm for type analysis. Thus, $\tool$ reports type-related specification bugs
+detected in fully compiled abstract algorithms by $\jiset$.  For built-in libraries,
+$\tool$ analyzes the abstract algorithms of the essential built-in objects: \jscode{Array},
 \jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
@@
 
-To evaluate $\tool$, we answer the following research questions:
+We evaluate $\tool$ using the following research questions:
 \begin{itemize}
@@
     detected by $\tool$ are true bugs?
-  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
-    improve the analysis precision with endurable performance degradation?
+  \item RQ3. \textbf{(Effectiveness of Refinement)} Does the condition-based refinement
+    improve the analysis precision with modest performance overhead?
   \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
@@
 \end{itemize}
-The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
-2021.  Thus, we targeted all different 864 versions existed in the official
-ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the recent
+Because the draft of the next ECMAScript (ES12, 2021) is fixed on March 9,
+2021, we analyzed all 864 versions in the official
+ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the last
 three years from January 1, 2018 to March 9, 2021.  We performed our experiments
@@
 
-Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
+Figure~\ref{fig:stat} shows the statistics of the type analysis using $\tool$ for
 864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
 of flow- and type-sensitive views, (c) the number of worklist iterations, and
-(d) the analysis time.  For each version of ECMAScript, \inred{1,689.6}
-functions (\stextsf{analyzed}) are analyzed and \inred{1,570.0} functions among
-them are fully compiled (\stextsf{compiled}) on average.  Since ECMAScript has
-gradually evolved for three years, \inred{1,357} out of \inred{1,490} analyzed
-functions are fully compiled at the first version in 2018 but \inred{1741} out
-of \inred{1,863} analyzed functions are fully compiled in the latest version.
-$\tool$ divides functions to flow- and type-sensitive views.  On average,
-\inred{91.2}K views existed for each version and \inred{53.9} views existed for
-each function.
+(d) the analysis time.  For each version, $\tool$ analyzed
+\inred{1,689.6} functions on average.  Since ECMAScript has gradually evolved,
+it analyzed \inred{1,490} functions for the first version in 2018
+but analyzed \inred{1,863} functions in the latest.
+$\tool$ analyzes functions with flow- and type-sensitive views.
+On average, each version has \inred{91.2}K views and each function has
+\inred{53.9}~views.
 
-We measured performance of $\tool$ based on the number of iterations for
-worklist algorithm and the analysis time.  For each version of ECMAScript,
-$\tool$ took \inred{136.0} seconds with \inred{298.8}K iterations of worklist
-algorithm on average.  The average analysis time consists of \inred{8.0} seconds
-for the specification extraction (\stextsf{extract} with gray bars),
-\inred{127.0} seconds for the type analysis (\stextsf{analyze} with blue bars),
-\inred{0.7} seconds for the bug detection (\stextsf{detect} with red bars).
+We measured the performance of $\tool$ with the worklist iteration number
+and the analysis time.  For each version of ECMAScript,
+$\tool$ took \inred{136.0} seconds with \inred{298.8}K iterations of
+the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
+for the specification extraction (\stextsf{extract}),
+\inred{127.0} seconds for the type analysis (\stextsf{analyze}), and
+\inred{0.7} seconds for the bug detection (\stextsf{detect}).
 
@@
     \includegraphics[width=\textwidth]{img/ttl-chro}
-    \caption{TTLs sorted by creation time.}
+    \caption{TTLs sorted by creation time}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{img/ttl-count}
-    \caption{The histogram of TTLs.}
+    \caption{The histogram of TTLs}
   \end{subfigure}
-  \caption{Time to Lives (TTLs) of true bugs.}
+  \caption{Time to Lives (TTLs) of true bugs}
   \vspace*{-1.5em}
@@
 
-We measured the analysis precision based on the number of true bugs in
-type-related specification bugs detected by $\tool$.  As described in the
-\stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
-is \inred{52.0}\% because it detected \inred{177} type-related bugs and
-\inred{92} bugs are true bugs among them.  The reference checker detected the
-largest number of bugs with \inred{62.2}\% precision; it found \inred{61} true
-reference bugs for \inred{17} unknown variables (\stextsf{UnknownVar}) and
-\inred{44} already defined variables (\stextsf{DuplicatedVar}). The arity
-checker and the assertion checker found \inred{4} missing parameters
-(\stextsf{MissParam}) with \inred{100.0}\% precision and \inred{5} assertion
-failures (\stextsf{Assertion}) with \inred{16.1}\% precision, respectively.
-Finally, the operand checker detected two different kinds of wrong typed operand
-bugs: \inred{2} non-numeric operand bugs (\stextsf{NoNumber}) for numeric
-operators with \inred{33.3}\% precision and \inred{20} unchecked abrupt
-completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.
+We measured the analysis precision with the number of true bugs in
+the type-related specification bugs detected by $\tool$.
+As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
+is \inred{52.0}\%; \inred{92} out of \inred{177} detected bugs are true bugs.
+The reference checker detected the most bugs with \inred{62.2}\% precision;
+\inred{17} unknown variables (\stextsf{UnknownVar}) and
+\inred{44} deplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
+We found \inred{4} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
+\inred{5} assertion failures (\stextsf{Assertion}) with \inred{16.1}\% precision.
+Finally, the operand checker detected
+\inred{2} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
+\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.
 
-To understand the severity of detected true bugs, we extended $\tool$ to
+To understand the severity of the detected true bugs, we extended $\tool$ to
 automatically extract when they are created and resolved in the ECMAScript
-official repository.  We defined that a bug is \textit{created} when it exists
-in a certain version but does not exist in the right before version, it is
-\textit{resolved} vice versa, and the \textit{Time to Live (TTL)} of a bug is
-how many days they last.  Figure~\ref{fig:ttl} describes TTLs of true bugs; the
-left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
-creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
-histogram of TTLs in a logarithmic scale.  Among \inred{92} true bugs,
-\inred{47} bugs are \textit{inherited}, which means that they are created before
-2018, and \inred{14} bugs still existed in the latest ECMAScript thus they are
-newly detected bugs by $\tool$.  We will discuss details of \inred{14} newly
-found bugs in Section~\ref{sec:new-bug}.  Even though we assume that \inred{47}
-inherited bugs are created in January 1, 2018, the average TTL is \inred{409.5}
-and the maximum TTL is \inred{1,164}.  All bugs having the maximum TTL are
-inherited and newly detected bugs.
+official repository.  A bug is \textit{created} when it exists
+in a specific version but does not exist in its previous version, and
+a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
+how many days the bug lasts.  Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
+Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
+Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
+Among \inred{92} true bugs, \inred{47} bugs are \textit{inherited},
+which means that they are created before 2018,
+and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
+We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
+Even though we assume that \inred{47} inherited bugs are created on January 1, 2018,
+the average TTL is \inred{409.5} and the maximum TTL is \inred{1,164}.
+All the bugs with the maximum TTL are inherited ones and they are all newly detected.
 
-We investigated \inred{85} false-positive bugs to reason about why they are
-detected by $\tool$.  Among them, \inred{30} bugs are caused by the failed
-extraction of mechanized specification because of wrong writing styles.  For
-example, ECMAScript is written in HTML and $\jiset$ extracts abstract algorithms
-based on \code{emu-alg} HTML tags.  However, several abstract algorithms are
-defined with the opening tag \code{<emu-alg>} but without the closing tag
-\code{</emu-alg>}.  Thus, $\jiset$ fails to extract them and it causes
-false-positive bugs.  The remaining \inred{55} bugs are caused by imprecise type
-analysis results.  Among them, \inred{20} bugs are caused by imprecise analysis
-for conditions of assertions and branches strongly related with specific
-function calls.  For example, consider the following algorithm step in the
-algorithm \textbf{GetValue}:
+We manually investigated \inred{85} false-positive bugs to understand why
+$\tool$ detected them.  Among them, \inred{30} bugs are due to extraction failure
+of mechanized specifications caused by wrong writing styles.
+Because ECMAScript is written in HTML, $\jiset$ extracts abstract algorithms
+using the \code{emu-alg} HTML tag.  Unfortunately, several abstract algorithms are
+defined with the opening tag \code{<emu-alg>} but without the closing tag \code{</emu-alg>},
+which causes extraction failure of mechanized specifications leading
+to false-positive bugs.  The remaining \inred{55} bugs are due to imprecise analysis.
+We found that \inred{20} bugs are due to imprecise analysis of the
+conditions of assertions and branches for specific function calls.
+For example, consider the following algorithm step for \textbf{GetValue}:
 \begin{figure}[H]
@@
 \end{figure} \noindent
-Since the algorithm \textbf{IsUnresolvableReference} always returns
+Since \textbf{IsPropertyReference} always returns
 $\code{false}$ when the $\code{Base}$ field of a given reference record is
-$\nconst{unresolvable}$, the field access \code{V.Base} never be
-$\nconst{unresolvable}$ on line 4.a.  However, the abstract environment in type
-analysis only stores that the variable $\code{V}$ has the $\code{Reference}$
-type thus $\nconst{unresolvable}$ is also passed as the argument of
-\textbf{ToObject}.  We believe that more advanced refinement technique can
-resolve this problem by pruning out infeasible field types depending on specific
-contexts.
+$\nconst{unresolvable}$, the field access $V$.[[Base]] cannot be
+$\nconst{unresolvable}$ on line 4.a.  However, because the type analysis
+does not compute such information,
+$\nconst{unresolvable}$ is also passed as the argument of \textbf{ToObject}.
+We believe that an advanced refinement technique can
+resolve this problem by pruning out infeasible field types depending on specific contexts.
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-iter}
+    \caption{The histogram of iterations}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-iter}
+    \caption{The ratio of iterations}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/compare-time}
+    \caption{The histogram of time}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.24\textwidth}
+    \includegraphics[width=\textwidth]{img/ratio-time}
+    \caption{The ratio of time}
+  \end{subfigure}
+  \caption{Comparison of iterations and analysis time without refinement
+  (\stextsf{no-refine}) and with refinement (\stextsf{refine})}
+  \label{fig:performance-compare}
+  \vspace*{-1.5em}
+\end{figure}
 
@@
   \caption{Type-related specification bugs newly detected by $\tool$ in the
-  official draft of ECMAScript 2021 (ES12).}
+  official draft of ECMAScript 2021 (ES12)}
   \label{table:new-bug}
@@
     } &
-    \stextsf{Reference} &
+    \stextsf{\footnotesize Reference} &
     2015-09-22 &
@@
     } &
-    \stextsf{Operand} &
+    \stextsf{\footnotesize Operand} &
     \inred{2015-09-22} &
@@
 
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/compare-iter}
-    \caption{The histogram of iterations.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ratio-iter}
-    \caption{The ratio of iterations.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/compare-time}
-    \caption{The histogram of time.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ratio-time}
-    \caption{The ratio of time.}
-  \end{subfigure}
-  \caption{The comparison of iterations and analysis time without refinement
-  (\stextsf{no-refine}) and with refinement (\stextsf{refine}).}
-  \label{fig:performance-compare}
-  \vspace*{-1.5em}
-\end{figure}
+We measured the effectiveness of the condition-based refinement by comparing
+the performance and the analysis precision of $\tool$
+without (\stextsf{no-refine}) and with refinement (\stextsf{refine}).
 
-We evaluated the effectiveness of condition-based refinement based on how much
-it improved analysis precision without significant performance degradation.  We
-performed $\tool$ without refinement (\stextsf{no-refine}) for 864 versions of
-ECMAScript, and compared their analysis results with the analysis with
-refinement (\stextsf{refine}).
-
-For performance, Figure~\ref{fig:performance-compare} describes the comparison
-of iterations and analysis time without refinement and with refinement; the left
-charts (Figure~\ref{fig:performance-compare}(a) and
-\ref{fig:performance-compare}(c)) are histograms of iterations and analysis
-time, and the right charts (Figure~\ref{fig:performance-compare}(b) and
-\ref{fig:performance-compare}(d)) are scatter charts for their ratio.  Without
-refinement, type analysis took \inred{90.9} seconds with \inred{259.1}K
+For performance comparison, Figure~\ref{fig:performance-compare} presents the
+iterations and analysis time without and with refinement.
+Figures~\ref{fig:performance-compare}(a) and
+\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
+time, respectively, and Figures~\ref{fig:performance-compare}(b) and
+\ref{fig:performance-compare}(d) are scatter charts for their ratios.
+Without refinement, the type analysis took \inred{90.9} seconds with \inred{259.1}K
 iterations on average.  For each version, the number of iterations is increased
 at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
-the analysis time is increased at least \inred{1.05}x, at most \inred{1.41}x,
-and \inred{1.98}x on average.
+the analysis time is increased at least \inred{1.05}x, at most \inred{1.98}x,
+and \inred{1.41}x on average.
 
@@
 precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
-false-positive bugs and to detect \inred{one} more true bug.  Among six
-difference bug kinds, the most significant improvement is about non-numeric
+false-positive bugs and detecting \inred{one} more true bug.  Among six
+bug kinds, the most significant improvement is for non-numeric
 operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
 by removing \inred{59} false-positive bugs.  The refinement technique
-successfully prunes out non-numeric values in conditions for numeric types.
+successfully prunes out non-numeric values for numeric types.
 The refinement also significantly increased the analysis precision for unknown
 variable bugs (\stextsf{UnknownVar}) and assertion failures
-(\stextsf{Assertion}) by removing \inred{28} and \inred{26} false-positive bugs,
-respectively.  However, there is no effect of refinement to detect missing
-parameter bugs (\stextsf{MissParam}) because it is possible to precisely analyze
-possible callee functions for each function invocation without condition-based
-refinement.
+(\stextsf{Assertion}) by removing \inred{28} and \inred{26} false-positive bugs, respectively.
+Because $\tool$ can precisely analyze callees of function invocations
+without refinement, we found no improvement for missing
+parameter bugs (\stextsf{MissingParam}).
 
@@
 
-Among \inred{92} true bugs detected by $\tool$, \inred{14} bugs are newly
+Among \inred{92} true bugs detected by $\tool$, \inred{14} are newly
 detected and still exist in the latest version of ECMAScript.
-Table~\ref{table:new-bug} summarizes the bugs categorized by their kinds and
-related JavaScript language features and it also contains their TTLs. We
-manually investigated their exact creation time if they are created before
-2018.  Except two bugs in ES12-8, all bugs were introduced in the initial
-commit of the open development on September 22, 2015.  Thus, 12 newly detected
-bugs last for 1,966 days until March 9, 2021.  The other two bugs in ES12-8 were
-created when a contributor introduced the prefixes \textbf{?} and \textbf{!}
-on December 16, 2015 thus it last for 1,910 days.  We reported the newly
-detected bugs to TC39; all of them are confirmed by the committee and will be
-fixed in ECMAScript 2022 (ES13).
+Table~\ref{table:new-bug} summarizes the bugs, their
+related JavaScript language features, and their TTLs.
+Except for two bugs in ES12-8, all bugs were introduced in the initial
+commit of the open development on September 22, 2015.
+Thus, 12 newly detected bugs last for 1,966 days until March 9, 2021.
+The two bugs in ES12-8 were created when a contributor introduced
+the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
+We reported the newly detected bugs to TC39, and all of them were
+confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).
 
-ES12-1 contains three bugs that are due to the duplicated definition of
-variables in three different syntax-directed algorithms for \jscode{case} blocks
-of \jscode{switch} statements: \code{hasDuplicates} in
-\textbf{ContainsDuplicateLabels}, and \code{hasUndefinedLabels} in
-\textbf{ContainsUndefinedBreakTarget} and
-\textbf{ContainsUndefinedContinueTarget}.  A \jscode{case} block optionally
-contains \jscode{case} clauses.  In the beginning of three algorithms,
-\code{hasDuplicates} (or \code{hasUndefinedLabels}) is defined if the clauses
-exist.  However, the exactly same variable is defined again after this
-conditional steps.  It means that three algorithms for \jscode{case} blocks
-having \jscode{case} clauses always have already defined variable bugs for
-\code{hasDuplicates} (or \code{hasUndefinedLabels}).  Similarly, ES12-2 also
-contains three bugs caused by the exactly same reason in same abstract
-algorithms for \jscode{try} statements.
+ES12-1 contains three bugs due to duplicated variable declarations
+in three syntax-directed algorithms for the \jscode{case} block
+of the \jscode{switch} statement:
+\code{hasDuplicates} in \textbf{ContainsDuplicateLabels} and
+\code{hasUndefinedLabels} in \textbf{ContainsUndefinedBreakTarget} and
+\textbf{ContainsUndefinedContinueTarget}.
+A \jscode{case} block optionally contains \jscode{case} clauses.
+In the beginning of three algorithms,
+\code{hasDuplicates} or \code{hasUndefinedLabels} is defined if the clauses exist.
+However, because the same variable is defined again after the conditional steps,
+three algorithms for \jscode{case} blocks
+with \jscode{case} clauses always have the duplicated variable declaration bugs for
+\code{hasDuplicates} (or \code{hasUndefinedLabels}).
+Similarly, ES12-2 contains three bugs caused by the same reason in the
+same abstract algorithms for the \jscode{try} statement.
 
-The bug in ES12-3 is a reference bug for an already defined variable
+The bug in ES12-3 is a reference bug for a duplicated declaration of the variable
 \code{index} in the abstract algorithm \textbf{CreateMappedArgumentsObject}.
@@
 
-ES12-4 contains two reference bugs for already defined variable \code{succeeded}
+ES12-4 contains two reference bugs for the already defined variable \code{succeeded}
 in \textbf{DefineOwnProperty} of \jscode{Array} objects and
-\textbf{ArraySetLength}.  The \jscode{Array} objects are exotic, which means
-that they are not ordinary objects and have special algorithms for specific
-behaviors.  The two algorithms are wrapper algorithms of
-\textbf{OrdinaryDefineOwnProperty} which updates object properties.  They define
-the variable \code{succeeded} to represent the result of
-\textbf{OrdinaryDefineOwnProperty}.  However, the variable is defined twice in a
-specific condition.
+\textbf{ArraySetLength}.  The \jscode{Array} objects are
+not ordinary objects and have special algorithms for specific behaviors.
+Two such algorithms are wrapper algorithms of
+\textbf{OrdinaryDefineOwnProperty}, which updates object properties.
+While they define the variable \code{succeeded} to represent the result of
+\textbf{OrdinaryDefineOwnProperty}, the variable is defined twice in a specific condition.
 
-The bug in ES12-5 is a reference bug for already defined variable \code{value}
-in \textbf{Evaluation} of defined \jscode{yield} expressions.  In the evaluation
-of \jscode{yield * e}, the variable \code{value} is defined twice to
+The bug in ES12-5 is a reference bug for the already defined variable \code{value}
+in \textbf{Evaluation} of the \jscode{yield *} expression.
+  In the evaluation of \jscode{yield * e}, the variable \code{value} is defined twice to
 represent 1) the evaluation result of the given expression \jscode{e} in step
-3, and 2) to the iterator value in step 7.c.viii.1.
+3, and 2) the iterator value in step 7.c.viii.1.
 
-The bug in ES12-6 is a reference bug for unknown variable \code{ClassHeritage}
-in \textbf{Contains} for tails of \jscode{class} declarations.  A tail of
-\jscode{class} declaration consists of an optional class heritage with
-\jscode{extends} keyword and a class body enclosed by curly braces.  When the
-optional class heritage does not exist, the variable \code{ClassHeritage} is not
+The bug in ES12-6 is a reference bug for the unknown variable \code{ClassHeritage}
+in \textbf{Contains} for the tails of \jscode{class} declarations.  A tail of a
+\jscode{class} declaration consists of an optional class extension with the
+\jscode{extends} keyword and a class body.  When the
+optional class extension does not exist, the variable \code{ClassHeritage} is not
 defined but the \textbf{Contains} algorithm tries to access it without any check
@@
 
-The bug in ES12-7 is a reference bug for unknown variable \code{Statement} in
-\textbf{EarlyErrors} for \jscode{if} statements.  In syntax-directed algorithms,
-the ordinal numbers are used as prefixes of variables when multiple sub-ASTs are
-produced by same productions.  A \jscode{if} statement contains two sub-ASTs
-produced by the \textit{Statement} production thus the ordinal number prefixes
-are required for the variable \code{Statement}.  However, the
-\textbf{EarlyErrors} algorithm for \jscode{if} statements uses it without any
+The bug in ES12-7 is a reference bug for the unknown variable \code{Statement} in
+\textbf{EarlyErrors} for the \jscode{if} statement.  In syntax-directed algorithms,
+when a production produces multiple sub-ASTs, it uses ordinal numbers as prefixes of variables.
+Because the \jscode{if} statement contains two sub-ASTs
+produced by the \textit{Statement} production, the ordinal number prefixes
+are necessary for the variable \code{Statement}.  However, the
+\textbf{EarlyErrors} algorithm for the \jscode{if} statement uses the variable without any
 ordinal number prefixes.
@@
 ES12-8 contains two operand type bugs related to abrupt completions in
-\textbf{DefineOwnProperty} and \textbf{GetOwnProperty} for \jscode{arguments}
-objects.  The two algorithms define or get own properties of \jscode{arguments}
-exotic objects.  They utilize the \textbf{Get} algorithm that returns JavaScript
-values stored in object properties or abrupt completions.  Thus, they should
-check whether results of \textbf{Get} are abstract completions or not before
-using them.  However, they use the results without any abrupt completion checks.
+\textbf{DefineOwnProperty} and \textbf{GetOwnProperty} for \jscode{arguments} objects.
+The two algorithms define or get own properties of \jscode{arguments} objects.
+They use the \textbf{Get} algorithm, which returns JavaScript
+values stored in object properties or abrupt completions.
+Thus, they should check whether the results of \textbf{Get} are abstract completions or not
+before using them but they use the results without any checking of abrupt completion.

### 2021-04-21 paper/ase21/eval.tex
[ASE21] Minor typo in eval

@@
 2021, we analyzed all 864 versions in the official
-ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the last
+ECMAScript repository\footnote{https://github.com/tc39/ecma262} for the last
 three years from January 1, 2018 to March 9, 2021.  We performed our experiments
@@
 \inred{17} unknown variables (\stextsf{UnknownVar}) and
-\inred{44} deplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
+\inred{44} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
 We found \inred{4} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and

### 2021-04-21 paper/ase21/report/syntax.tex
[ASE21] Report: concrete semantics

@@
 \]
+A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ consists of
+three mappings;  $\getfunc: \labset \rightarrow \funcset$ maps labels to their
+functions, $\getinst: \labset \rightarrow \instset$ maps labels to their
+instructions, and $\getnext: \labset \rightarrow \labset$ maps labels to their
+next labels, where a label $\lab \in \labset$ denotes a program point. A
+function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \; \lab \in \funcset$ consists
+of its name $\f$, normal parameters $\x^*$, optional parameters $\y^*$, and a
+body label $\lab$.  For presentation brevity, we assume that no global variables
+exist in this paper.  An instruction $\inst$ is a variable declaration, a
+function call, an assertion, a branch, a return, or a reference update.  An
+invocation of an abstract algorithm in ECMAScript is compiled to a function call
+instruction with a new temporary variable.  We represent loops using branch
+instructions with cyclic pointing of labels in $\getnext$.  A reference $\refer$
+is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We write
+$\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An expression
+$\expr$ is a record, a list, a type check, an existence check, a binary
+operation, a unary operation, a reference, a constant, or a primitive, which is
+either $\undefval$, $\nullval$, a \jscode{Boolean} $\bool$, a \jscode{Number}
+$\num$, a \jscode{BigInt} $\bigint$, a \jscode{String} $\str$, or a
+\jscode{Symbol} $\symb$.
+
+A type $\ty \in \tyset$ is either a nominal type $\tname$, an empty list type
+$\clist{}$, a parametric list type $\clist{\ty}$, a JavaScript type $\tjs$, a
+primitive type $\tprim$, a numeric type $\tnumeric$, $\tnum$, $\tbigint$,
+$\tstr$, or $\tsymb$.  The subtype relation $\subtype \subseteq \tyset \times
+\tyset$ between types is reflexive and transitive.

### 2021-04-21 paper/ase21/conclusion.tex
Revised Sec. 6 & 7

--- 2021-04-18 paper/ase21/conclusion.tex
@@
 \section{Conclusion}\label{sec:conclusion}
-Since an incorrect description in ECMAScript can lead to the wrong JavaScript
-engine implementations, checking the correctness of ECMAScript is essential.
-Since ECMAScript is annually released and developed in open process, it becomes
-more labor-intensive and error-prone.  To alleviate the problem, we propose
-$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
-first tool that performs \textit{type analysis} on JavaScript specifications and
-detects specification bugs using a \textit{bug detector}.  Moreover, to increase
-precision of type analysis, we present \textit{condition-based refinement} for
-type analysis, which prunes out infeasible abstract states using conditions of
-assertions and branches.  We evaluated $\tool$ with all 864 versions in the
-official ECMAScript repository for the recent three years from 2018 to 2021.
-Our tool took \inred{230} seconds on average to perform type analysis for each
-version, and detected \inred{200} type-related specification bugs with
-\inred{50.3}\% precision; \inred{91} out of \inred{200} bugs are true bugs.
-Among them, \inred{14} bugs are newly detected by $\tool$ and the committee
-confirmed all of them.
+Checking the correctness of ECMAScript is essential because an incorrect description
+in ECMAScript can lead to wrong implementations of JavaScript engines. However,
+since ECMAScript is annually released and developed in an open process, checking
+its correctness becomes more labor-intensive and error-prone.  To alleviate the problem,
+we propose $\tool$, a JavaScript Specification Type Analyzer using Refinement.
+It is the first tool that performs \textit{type analysis} on JavaScript specifications and
+detects specification bugs using a \textit{bug detector}.  We also present
+\textit{condition-based refinement} for type analysis, which prunes out infeasible abstract states
+using conditions of assertions and branches to improve the analysis precision.
+We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
+for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
+to perform type analysis for each version, and detected \inred{161} type-related specification bugs with
+\inred{56.5}\% precision; \inred{91} out of \inred{161} reported bugs are true bugs.
+Among them, \inred{14} bugs are newly detected by $\tool$, and the
+committee confirmed them all.

### 2021-04-21 paper/ase21/related.tex
Revised Sec. 6 & 7

--- 2021-04-14 paper/ase21/related.tex
@@
 
-\paragraph{ECMAScript-based Applications}
-\begin{itemize}
-  \item Engines~\cite{v8, graaljs, qjs, moddable}
-  \item Static Analyzer~\cite{safe, tajs, jsai, wala}
-  \item Debuggers: JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
-  \item Verification Tool: JaVerT: JavaScript Verification
-    Toolchain~\cite{javert}
-\end{itemize}
+Type analysis of JavaScript specifications has three related topics:
+JavaScript tools, mechanized specification extraction, and specification-based testing.
 
-\paragraph{Mechanized Specifications}
-\begin{itemize}
-  % manual
-  \item The Essence of Javascript~\cite{lambdajs}
-  \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
-  \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
+\paragraph{JavaScript Tools}
+ECMAScript is the standard language specification for JavaScript maintained by
+the Ecma Technical Committee 39 (TC39).  In late 2014, the committee announced
+its plan to release ECMAScript annually and adopt the open development process
+to quickly adapt to evolving development environments.  Various JavaScript engines such
+as Google V8~\cite{v8}, GraalJS~\cite{graaljs}, QuickJS~\cite{qjs}, and Moddable
+XS~\cite{moddable} should conform to the syntax and semantics described in
+annually updated ECMAScript.  Beyond JavaScript engines, diverse
+research projects use JavaScript specifications.  The main research direction
+has been static analyzers such as JSAI~\cite{jsai}, SAFE~\cite{safe},
+TAJS~\cite{tajs}, and WALA~\cite{wala} based on the abstract interpretation
+framework~\cite{ai1977, ai1992} with their own analysis techniques.
+They defined abstract semantics of the JavaScript semantics described in ECMAScript to statically
+analyze JavaScript programs in a finite time.
+Chargu{\'e}raud et al.~\cite{jsexplain} presented JSExplain, a debugger for JavaScript, by
+implementing a reference interpreter in OCaml following the algorithm steps in ECMAScript closely.
+For a given JavaScript program, the debugger interactively produces execution traces
+investigated in a browser, with an interface that displays the
+JavaScript code and the interpreter's state.
+Fragoso Santos et al.~\cite{javert} introduced JaVerT, a JavaScript verification toolchain, based
+on the separation logic with an intermediate goto language JSIL.
+JaVerT 2.0~\cite{javert2} extends it to support compositional symbolic execution
+for JavaScript based on bi-abduction.  However, because all of them manually handle
+ECMAScript with their own intermediate representations, most of them still 
+target ES5.1 released in 2011 instead of the latest one.
 
-  % automatic
-  \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
-    Specifications for L3 Protocols~\cite{basespec}
-  \item Automatic extraction of x86 formal semantics from its natural
-    language description~\cite{x86}
-  \item Formal semantics extraction from natural language specifications for
-    ARM~\cite{arm}
-  \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
-  \item Automatic Model Generation from Documentation for Java API Functions
-  \item COMFORT: JS Fuzzer using ECMAScript
-  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
-\end{itemize}
+\paragraph{Mechanized Specification Extraction}
+Researchers in various application domains have extracted mechanized specifications from
+specifications written in natural languages to handle the contents in the specifications automatically.
+For system architectures, researchers utilized Natural
+Language Processing (NLP) and Machine Learning (ML) techniques to extract formal semantics
+of small-sized low-level assembly languages for x86~\cite{x86} and ARM~\cite{arm}.
+For Java API functions, Zhai et al.~\cite{javadoc} presented a
+technique to automatically extract models from their documentation using NLP techniques.
+For the JavaScript programming language, Park et al.~\cite{jiset}
+presented $\jiset$, a tool that extracts a mechanized specification from ECMAScript.
+While all the previous JavaScript formal semantics~\cite{lambdajs, jscert,
+kjs} were manually defined, $\jiset$ automatically extracts formal semantics directly from ECMAScript.
+We utilized $\jiset$ to analyze 864 ECMAScript versions via $\tool$.
 
-\paragraph{Correctness of ECMAScript}
-\begin{itemize}
-  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
-  \item JEST: N+1-version Differential Testing of Both JavaScript Engines
-    and Specification~\cite{jest}
-\end{itemize}
-
-% \begin{itemize}
-%   \item Abstract Interpretation~\cite{ai1977, ai1992}
-%   \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
-%   \item JavaScript Manual Mechanized Specification:
-%     \begin{itemize}
-%       \item The Essence of Javascript~\cite{lambdajs}
-%       \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
-%       \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
-%       \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
-%       \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
-%         and Specification~\cite{jest}
-%     \end{itemize}
-%   \item Automatic Mechanized Specification for others:
-%     \begin{itemize}
-%       \item Automatic extraction of x86 formal semantics from its natural
-%         language description~\cite{x86}
-%       \item Formal semantics extraction from natural language specifications for
-%         ARM~\cite{arm}
-%       \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
-%       \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
-%         Specifications for L3 Protocols~\cite{basespec}
-%     \end{itemize}
-% \end{itemize}
+\paragraph{Specification-based Testing}
+Recently, researchers have utilized specifications to test their implementations.
+For network protocols, Kim et al.~\cite{basespec} proposed a novel approach named
+\textsc{BaseSpec}, which extracts message structures from tables in cellular
+specifications for L3 protocols to perform comparative analysis of baseband software.
+Schumi and Sun~\cite{spectest} presented SpecTest, which utilized an
+executable language semantics to perform fuzzing for Java and Solidity compilers.
+For JavaScript, Ye et al.~\cite{comfort} presented \textsc{Comfort}, a
+compiler fuzzing framework to detect JavaScript engine bugs using ECMAScript
+with deep learning-based language models.
+Park et al.~\cite{jest} extended $\jiset$ to $\jest$, which performs $N$+1-version differential testing
+with $N$ different JavaScript engines and a reference interpreter extracted from ECMAScript.
+$\jest$ detects not only engine bugs but also specification bugs in
+ECMAScript using the cross-referencing oracle.  However, it requires multiple JavaScript engines and
+takes dozens of hours to test a version of ECMAScript.
+Instead, $\tool$ can detect specification bugs without JavaScript engines in less than five minutes.
+Because $\tool$ uses abstract semantics while $\jest$ uses concrete semantics,
+$\tool$ can quickly analyze more semantics than $\jest$.

### 2021-04-22 paper/ase21/report/abstract.tex
[ASE21] Draft of report

@@
 \begin{abstract}
-  In this report, we formally define a modified $\ires$ with its syntax and
-  semantics.  Moreover, we define type analysis for the modified $\ires$.
+  This technical report is a companion report of the research paper for $\tool$,
+  a JavaScript Specification Type Analyzer using Refinement.  In this report, we
+  formally define the syntax and semantics of a modified $\ires$, an untyped
+  intermediate representation for ECMAScript.  Moreover, we formally define type
+  analysis for the modified $\ires$ based on the abstract interpretation
+  framework with flow- and type-sensitivity for arguments.  To increase the
+  precision of the type analysis, we also present \textit{condition-based
+  refinement} for type analysis, which prunes out infeasible abstract states
+  using conditions of assertions and branches.
 \end{abstract}

### 2021-04-22 paper/ase21/conclusion.tex
[ASE21] Updated numbers

@@
 for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
-to perform type analysis for each version, and detected \inred{161} type-related specification bugs with
-\inred{56.5}\% precision; \inred{91} out of \inred{161} reported bugs are true bugs.
+to perform type analysis for each version, and detected \inred{157} type-related specification bugs with
+\inred{59.2}\% precision; \inred{93} out of \inred{157} reported bugs are true bugs.
 Among them, \inred{14} bugs are newly detected by $\tool$, and the

### 2021-04-22 paper/ase21/eval.tex
Removed unnecessary parentheses
[ASE21] Updated numbers

@@
 (d) the analysis time.  For each version, $\tool$ analyzed
-\inred{1,689.6} functions on average.  Since ECMAScript has gradually evolved,
-it analyzed \inred{1,490} functions for the first version in 2018
-but analyzed \inred{1,863} functions in the latest.
+\inred{1,696.6} functions on average.  Since ECMAScript has gradually evolved,
+it analyzed \inred{1,491} functions for the first version in 2018
+but analyzed \inred{1,864} functions in the latest.
 $\tool$ analyzes functions with flow- and type-sensitive views.
-On average, each version has \inred{91.2}K views and each function has
-\inred{53.9}~views.
+On average, each version has \inred{92.0}K views and each function has
+\inred{54.1}~views.
 
@@
 and the analysis time.  For each version of ECMAScript,
-$\tool$ took \inred{136.0} seconds with \inred{298.8}K iterations of
+$\tool$ took \inred{137.3} seconds with \inred{301.6}K iterations of
 the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
 for the specification extraction (\stextsf{extract}),
-\inred{127.0} seconds for the type analysis (\stextsf{analyze}), and
-\inred{0.7} seconds for the bug detection (\stextsf{detect}).
+\inred{128.5} seconds for the type analysis (\stextsf{analyze}), and
+\inred{0.8} seconds for the bug detection (\stextsf{detect}).
 
@@
 As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
-is \inred{52.0}\%; \inred{92} out of \inred{177} detected bugs are true bugs.
-The reference checker detected the most bugs with \inred{62.2}\% precision;
+is \inred{59.2}\%; \inred{93} out of \inred{157} detected bugs are true bugs.
+The reference checker detected the most bugs with \inred{80.8}\% precision;
 \inred{17} unknown variables (\stextsf{UnknownVar}) and
-\inred{44} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
-We found \inred{4} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
-\inred{5} assertion failures (\stextsf{Assertion}) with \inred{16.1}\% precision.
+\inred{46} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
+We found \inred{four} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
+\inred{four} assertion failures (\stextsf{Assertion}) with \inred{12.9}\% precision.
 Finally, the operand checker detected
-\inred{2} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
+\inred{two} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
 \inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.
@@
 Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
-Among \inred{92} true bugs, \inred{47} bugs are \textit{inherited},
+Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
 which means that they are created before 2018,
@@
 We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
-Even though we assume that \inred{47} inherited bugs are created on January 1, 2018,
-the average TTL is \inred{409.5} and the maximum TTL is \inred{1,164}.
+Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
+the average TTL is \inred{414.5} and the maximum TTL is \inred{1,164}.
 All the bugs with the maximum TTL are inherited ones and they are all newly detected.
 
-We manually investigated \inred{85} false-positive bugs to understand why
-$\tool$ detected them.  Among them, \inred{30} bugs are due to extraction failure
+We manually investigated \inred{64} false-positive bugs to understand why
+$\tool$ detected them.  Among them, \inred{17} bugs are due to extraction failure
 of mechanized specifications caused by wrong writing styles.
@@
 which causes extraction failure of mechanized specifications leading
-to false-positive bugs.  The remaining \inred{55} bugs are due to imprecise analysis.
-We found that \inred{20} bugs are due to imprecise analysis of the
+to false-positive bugs.  The remaining \inred{47} bugs are due to imprecise analysis.
+We found that \inred{28} bugs are due to imprecise analysis of the
 conditions of assertions and branches for specific function calls.
@@
     \stextsf{\footnotesize Operand} &
-    \inred{2015-09-22} &
-    \inred{1,996 days}\\
+    \inred{2015-12-16} &
+    \inred{1,910 days}\\
   \end{tabular}
@@
 \ref{fig:performance-compare}(d) are scatter charts for their ratios.
-Without refinement, the type analysis took \inred{90.9} seconds with \inred{259.1}K
+Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
 iterations on average.  For each version, the number of iterations is increased
 at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
-the analysis time is increased at least \inred{1.05}x, at most \inred{1.98}x,
+the analysis time is increased at least \inred{1.05}x, at most \inred{1.99}x,
 and \inred{1.41}x on average.
@@
 with refinement, and their difference.  The refinement improved the analysis
-precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
+precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
 false-positive bugs and detecting \inred{one} more true bug.  Among six
@@
 variable bugs (\stextsf{UnknownVar}) and assertion failures
-(\stextsf{Assertion}) by removing \inred{28} and \inred{26} false-positive bugs, respectively.
+(\stextsf{Assertion}) by removing \inred{29} and \inred{25} false-positive bugs, respectively.
 Because $\tool$ can precisely analyze callees of function invocations
@@
 
-Among \inred{92} true bugs detected by $\tool$, \inred{14} are newly
+Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
 detected and still exist in the latest version of ECMAScript.
@@
 with \jscode{case} clauses always have the duplicated variable declaration bugs for
-\code{hasDuplicates} (or \code{hasUndefinedLabels}).
+\code{hasDuplicates} or \code{hasUndefinedLabels}.
 Similarly, ES12-2 contains three bugs caused by the same reason in the

### 2021-04-22 paper/ase21/intro.tex
[ASE21] Updated numbers

@@
     precision.  We show that the refinement technique increases the analysis
-    precision from \inred{31.8}\% to \inred{56.5}\% by removing \inred{122}
+    precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
     false bugs and detecting \inred{one} more true bug.
@@
     seconds on average to perform a type analysis for each version of ECMAScript and detected
-    \inred{161} type-related specification bugs with \inred{56.5}\% precision;
-    \inred{91} out of \inred{161} bugs are true bugs.  Among them, $\tool$
+    \inred{157} type-related specification bugs with \inred{59.2}\% precision;
+    \inred{93} out of \inred{157} bugs are true bugs.  Among them, $\tool$
     newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.

### 2021-04-22 paper/ase21/analyzer.tex
[ASE21] Changed format of concrete semantics
[ASE21] Hotfix errors in formalization
[ASE21] Applied comments

@@
       \text{Functions}
-      &\funcset&\ni&\func&::=&\kwdef \; \x (\x^*, \kwsl \x^* \kwsr). \; \lab\\
+      &\funcset&\ni&\func&::=& \kwfunc{\x}{\x^*, \kwsl \x^* \kwsr}{\lab}\\
 
@@
 \rightarrow \labset$ maps labels to their next labels, where a label $\lab \in \labset$
-denotes a program point. A function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \;
-\lab \in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
+denotes a program point. A function $\kwfunc{\f}{\x^*, \kwsl \y^* \kwsr}{\lab}
+\in \funcset$ consists of its name $\f$, normal parameters $\x^*$, optional
 parameters $\y^*$, and a body label $\lab$.  For presentation brevity,
@@
 
-            \func = \kwdef \; \f (\p_1, \cdots, \kwsl \cdots, \p_{m_\func}
-            \kwsr). \; \lab_\func \;\wedge\;\\
+            \func = \kwfunc{\f}{p_1, \cdots, \kwsl \cdots, \p_{k_\func}
+            \kwsr}{\lab_\func} \;\wedge\;\\
 
             \aenv_{\func, \tys'} = [\p_1 \mapsto \{ \tys'[1] \}, \cdots,
-            \p_{m_\func} \mapsto \{ \tys'[m] \}] \;\wedge\;\\
+            \p_{k_\func} \mapsto \{ \tys'[k_\func] \}] \;\wedge\;\\
 
@@
 depicted in Figure~\ref{fig:subtype}; a directed edge from $\ty'$ to $\ty$
-denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
-subtype relation is dependent on the nominal types defined in ECMAScript.  We
+denotes $\ty' \subtype \ty$, and the relation is reflexive and transitive.  The
+subtype relation depends on the nominal types defined in ECMAScript.  We
 extract the subtype relation for AST types from the JavaScript syntax.
@@
 $\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
-\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$
-where $\dom$ and $\valset$ denote states and values, respectively.
-For brevity, we omit it in this paper and refer the
+\rightarrow \dom \times \valset$, and expressions $\seme{\expr}: \dom
+\rightarrow \dom \times \valset$ where $\dom$ and $\valset$ denote states and
+values, respectively.  For brevity, we omit it in this paper and refer the
 interested readers to a companion report~\cite{report}.
@@
 \end{figure} \noindent
-where $\small{\norm(\aty) = \{ \ty \mid \ty \in \aty \wedge \nexists \ty' \in
+where $\small{\norm(\aty) = \{ \ty \in \aty \mid \nexists \ty' \in
 \aty\setminus \{ \ty \}. \; \text{s.t.} \; \ty \subtype \ty' \}}$.
 
-We now define the abstract semantics of instructions $\asemi{\inst}$ in Figure~\ref{fig:abs-sem}
-and the abstract semantics of references $\asemr{\refer}$
-and expressions $\aseme{\expr}$ in a companion report~\cite{report}.
+We now define the abstract semantics of instructions $\asemi{\inst}: (\labset
+\times \tyset^*) \rightarrow \adom \rightarrow \adom$ in Figure~\ref{fig:abs-sem}
+and the abstract semantics of references $\asemr{\refer}: \aenvset \rightarrow \atyset$
+and expressions $\aseme{\expr}: \aenvset \rightarrow \atyset$ in a companion report~\cite{report}.
 To avoid the explosion of type-sensitive
@@
         \refine(\expr, \bool)(\aenv)
-        & \text{if} \; \{ \true \} \order \aseme{\expr}(\aenv)\\
+        & \text{if} \; \bool \order \aseme{\expr}(\aenv)\\
 
@@
 semantics $\asem{\prog}$ of a program $\prog$
-as the least fixpoint of the abstract transfer $\atransfer: \adom \rightarrow
+as the least fixpoint of the abstract transfer function $\atransfer: \adom \rightarrow
 \adom$:
@@
       \refine(\x.\Type \; \code{==} \; \nconst{normal}, \true)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \cap \tnormal(\tyset) ]\\
+      \aenv[ \x \mapsto \aty_\x \meet \tnormal(\tyset) ]\\
       \refine(\x.\Type \; \code{==} \; \nconst{normal}, \false)(\aenv) &=&
-      \aenv[ \x \mapsto \aty_\x \cap \{ \tabrupt \} ]\\
+      \aenv[ \x \mapsto \aty_\x \meet \{ \tabrupt \} ]\\
 

### 2021-04-22 paper/ase21/checker.tex
Revised Sec. 5
[ASE21] Applied comments

@@
 We develop a \textit{bug detector} to statically detect type-related
-specification bugs in ECMAScript using an augmented abstract transfer
+specification bugs in ECMAScript using an augmented abstract transfer function
 $\detector$ with additional checkers.  Before implementing checkers, we manually
@@
   \end{subfigure}
-  \caption{The statistics of type analysis using $\tool$ for 864 versions of
+  \caption{The statistics of the type analysis using $\tool$ for 864 versions of
   ECMAScript}
@@
 The arity of a function \mbox{\small
-$\func=\kwdef\ \f (\p_1, \cdots, \p_n, \kwsl \cdots, p_m \kwsr).\lab$}
+$\func = \kwfunc{\f}{\p_1, \cdots, \p_n, \kwsl \cdots, p_m \kwsr}{\lab}$}
 is an interval $[n, m]$ where $n$ and $m-n$ denote the
@@
       \right.\\
-      \qquad \text{where} \; \func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func},
-      \kwsl \cdots, p_{m_\func} \kwsr). \; \lab \;\wedge\;\\
+      \qquad \text{where} \; \func = \kwfunc{\f}{\p_1, \cdots, \p_{n_\func},
+      \kwsl \cdots, p_{m_\func} \kwsr}{\lab} \;\wedge\;\\
       \qquad \phantom{\text{where}} \; \aty = \aseme{\expr}(\aelem(\lab,
@@
 the type of an operand does not conform to its corresponding parameter type.
-For example, the comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.
-If an expression tries to compare non-numeric values such as $\true <
-\code{"abc"}$, then it is a non-numeric operand bug (\stextsf{NoNumber}).
-Besides, ECMAScript has a special implicit conversion for normal completions
-when their actual values stored in the $\code{Value}$ field are necessary
-such as conditions, values of field updates, and operands of operators.
-For example, if the variable $\x$ has a normal completion with \code{42} as its
-actual value, $\code{x + 1}$ should be \code{43} because the normal completion
-gets implicitly converted into its actual value \code{42}.
-To explicitly represent this conversion, we define a unary operator
-$\escaped$ as follows:
-\begin{figure}[H]
-  \centering
-  \vspace*{-0.5em}
-  \resizebox{\columnwidth}{!}{$
-    \escaped \val = \left\{
-      \begin{array}{ll}
-        \val &
-        \text{if} \; \val \; \text{is not a completion}\\
-
-        \val.\code{Value} &
-        \text{if} \; \val \; \text{is normal}\\
-
-        \text{unchecked abrupt completion} \; \val &
-        \text{otherwise}\\
-      \end{array}
-    \right.
-  $}
-  \vspace*{-0.5em}
-\end{figure} \noindent
-and assume that the operator $\escaped$ is used when the actual value is necessary.
-Then, an unchecked abrupt completion bug (\stextsf{Abrupt}) occurs
-when the actual value is necessary but it is an abrupt completion.
-According to our manual investigation, one pull request fixed two non-numeric operand
-bugs and five pull requests fixed six unchecked abrupt completion bugs.
-
 The operand checker detects such ill-typed operand bugs by additional
@@
 $\expr_1$, and $\expr$, respectively.  The additional checks report
-when a given operand does not conform to its expected type.  For example, consider the
-upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
-The types of $\x$ and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the
+when a given operand does not conform to its expected type.  According to our
+manual investigation, there existed two different kinds of ill-typed operand
+bugs: two non-numeric operand bugs (\stextsf{NoNumber}) in one pull request, and
+six unchecked abrupt completion bugs (\stextsf{Abrupt}) in five pull requests.
+
+For an example of non-numeric operand bugs, consider the upper-right built-in
+algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.  The types of $\x$
+and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the
 \textbf{ToNumber} algorithm always returns number values or abrupt completions,
-and the prefix ? of \textbf{ReturnIfAbrupt} removes the latter case.
-The built-in algorithm misuses $\x$ rather than $\n$ on lines 3 and 4,
-and because the expected abstract type $\{ \tnum, \tbigint \}$ does not subsume $\{ \tjs \}$,
-the operand checker reports non-numeric operand bugs.
+and the prefix \textbf{?} removes the latter case.  The built-in algorithm
+misuses $\x$ rather than $\n$ on lines 3 and 4, and because the expected
+abstract type $\{ \tnum, \tbigint \}$ does not subsume $\{ \tjs \}$, the operand
+checker reports non-numeric operand bugs.
+
+An unchecked abrupt completion bug occurs when the actual value is necessary but
+it is an abrupt completion.  ECMAScript has a special implicit conversion for
+normal completions when their actual values stored in the $\code{Value}$ field
+are necessary, such as conditions, values of field updates, and operands of
+operators.  For example, if the variable $\x$ has a normal completion with
+\code{42} as its actual value, $\code{x + 1}$ should be \code{43} because the
+normal completion gets implicitly converted into its actual value \code{42}.  To
+explicitly represent this conversion, we define a unary operator $\escaped$ as
+follows:
+\begin{figure}[H]
+  \centering
+  \vspace*{-0.5em}
+  \resizebox{\columnwidth}{!}{$
+    \escaped \val = \left\{
+      \begin{array}{ll}
+        \val &
+        \text{if} \; \val \; \text{is not a completion}\\
+
+        \val.\code{Value} &
+        \text{if} \; \val \; \text{is normal}\\
+
+        \text{unchecked abrupt completion} \; \val &
+        \text{otherwise}\\
+      \end{array}
+    \right.
+  $}
+  \vspace*{-0.5em}
+\end{figure} \noindent
+and assume that the operator $\escaped$ is used when the actual value is necessary.

### 2021-04-22 paper/ase21/eval.tex
[ASE21] Applied comments

@@
 \inred{0.8} seconds for the bug detection (\stextsf{detect}).
+Therefore, We believe that $\tool$ is enough to be as part of continuous
+integration pipeline in open development process of ECMAScript.
 
@@
 
-To understand the severity of the detected true bugs, we extended $\tool$ to
+To understand the impact of the detected true bugs, we extended $\tool$ to
 automatically extract when they are created and resolved in the ECMAScript
@@
 a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
-how many days the bug lasts.  Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
+the number of days between the created date and the resolved date.
+Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
 Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
@@
 Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
-iterations on average.  For each version, the number of iterations is increased
+iterations on average.  After applying refinement, the number of iterations is increased
 at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
@@
 successfully prunes out non-numeric values for numeric types.
-The refinement also significantly increased the analysis precision for unknown
+The refinement significantly increased the analysis precision also for unknown
 variable bugs (\stextsf{UnknownVar}) and assertion failures
@@
 commit of the open development on September 22, 2015.
-Thus, 12 newly detected bugs last for 1,966 days until March 9, 2021.
+Thus, 12 newly detected bugs last for 1,996 days until March 9, 2021.
 The two bugs in ES12-8 were created when a contributor introduced

### 2021-04-22 paper/ase21/intro.tex
[ASE21] Applied comments

@@
 
-To alleviate this problem, we propose a tool $\tool$, a \textbf{J}avaScript
+To alleviate this problem, we propose a novel tool $\tool$, a \textbf{J}avaScript
 \textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
@@
 intermediate representation for ECMAScript.
-Therefore, $\tool$ can handle JavaScript specifications mechanically using $\jiset$.
+Therefore, $\tool$ leverages $\jiset$ to mechanically handle JavaScript specifications.
 
@@
 including environments, completions, and property descriptors. We
-define their type hierarchies and fields based on the type-related
-tables in ECMAScript and automatically extracted syntax-directed algorithms.
+define their type hierarchies based on subtype relations and fields for record and AST types.
 Using such type information, $\tool$ performs a type analysis and detects specification bugs using

### 2021-04-22 paper/ase21/overview.tex
[ASE21] Applied comments

@@
 \paragraph{Types}
+In addition to JavaScript types,
 $\tool$ represents three kinds of specification types.
@@
 The type analyzer consists of two sub-modules: an \textit{analysis initializer} and an
-\textit{abstract transfer}.
+\textit{abstract transfer function}.
 
@@
 
-\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
+\paragraph{Abstract Transfer Function} For each iteration, the abstract transfer function gets a
 specific view from the worklist and updates the abstract environments of the next
@@
 During the initialization of the function call, the \textbf{IteratorBindingInitialization}
-algorithm executes with additional parameters \textit{iteratorRecord} and
+algorithm is executed with additional parameters \textit{iteratorRecord} and
 \textit{environment} to assign argument values to parameters.
@@
 type-related specification bugs (Section~\ref{sec:checker}).  After we evaluate $\tool$
-(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
+(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related})
 and conclude (Section~\ref{sec:conclusion}).

### 2021-04-22 paper/ase21/related.tex
[ASE21] Applied comments

@@
 ECMAScript is the standard language specification for JavaScript maintained by
-the Ecma Technical Committee 39 (TC39).  In late 2014, the committee announced
+TC39.  In late 2014, the committee announced
 its plan to release ECMAScript annually and adopt the open development process
@@
 For system architectures, researchers utilized Natural
-Language Processing (NLP) and Machine Learning (ML) techniques to extract formal semantics
+Language Processing (NLP) and Machine Learning techniques to extract formal semantics
 of small-sized low-level assembly languages for x86~\cite{x86} and ARM~\cite{arm}.
@@
 takes dozens of hours to test a version of ECMAScript.
-Instead, $\tool$ can detect specification bugs without JavaScript engines in less than five minutes.
+Instead, $\tool$ can detect specification bugs without JavaScript engines in two minutes.
 Because $\tool$ uses abstract semantics while $\jest$ uses concrete semantics,
-$\tool$ can quickly analyze more semantics than $\jest$.
+$\tool$ can quickly analyze more scope of semantics than $\jest$.

### 2021-04-22 paper/ase21/analyzer.tex
[ASE21] Updated Figure 2 and related parts

@@
 extract the subtype relation for AST types from the JavaScript syntax.
-For example, consider the syntax-directed abstract
-algorithm at the lower-right part in Figure~\ref{fig:example}.
+For example, consider the syntax-directed abstract algorithm in Figure~\ref{fig:example}(c).
 Because the nonterminal \textit{BindingElement} is the unique alternative of the
@@
 $\this$ with its production type and other variables for nonterminals.
-For example, the upper-left syntax-directed algorithm in Figure~\ref{fig:example} is
+For example, the syntax-directed algorithm in Figure~\ref{fig:example}(a) is
 initialized with the following abstract environment:
@@
 example, the following abstract environment is for the built-in
-algorithm $\jscode{Math.round}$ at the upper-right part in Figure~\ref{fig:example}:
+algorithm $\jscode{Math.round}$ in Figure~\ref{fig:example}(d):
 \begin{figure}[H]

### 2021-04-22 paper/ase21/checker.tex
[ASE21] Updated Figure 2 and related parts

@@
 $\x$ is always an unknown variable.  For example, consider the syntax-directed algorithm
-at the upper-left part in Figure~\ref{fig:example}.
+in Figure~\ref{fig:example}(a).
 Since the \textbf{GetReferencedName} algorithm is removed, the variable
@@
 $\expr$, the arity checker compares the number of arguments with the arity of
-$\func$ to detect missing parameters.  For example, consider the lower-left
-syntax-directed algorithm in Figure~\ref{fig:example}.  The algorithm invocation
+$\func$ to detect missing parameters.  For example, consider the
+syntax-directed algorithm in Figure~\ref{fig:example}(b).  The algorithm invocation
 on line 2 is compiled to the following function call instruction:
@@
 It checks whether the abstract semantics of the condition expression $\expr$ 
-subsumes $\{ \true \}$.  For example, consider the lower-right syntax-directed
-algorithm in Figure~\ref{fig:example}.  The parameter $\code{environment}$ of
+subsumes $\{ \true \}$.  For example, consider the syntax-directed
+algorithm in Figure~\ref{fig:example}(c).  The parameter $\code{environment}$ of
 this algorithm has an environment record or $\undefval$.
@@
 
-For an example of non-numeric operand bugs, consider the upper-right built-in
-algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.  The types of $\x$
+For an example of non-numeric operand bugs, consider the built-in
+algorithm $\code{Math.round}$ in Figure~\ref{fig:example}(d).  The types of $\x$
 and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the

### 2021-04-22 paper/ase21/overview.tex
[ASE21] Updated Figure 2 and related parts

@@
 It then assigns an anonymous function to \jscode{f} using the operator \jscode{??=}.
-While the corresponding \textbf{Evaluation} algorithm originally
+While the corresponding \textbf{Evaluation} algorithm in Figure~\ref{fig:example}(a) originally
 used the \textbf{GetReferencedName} algorithm to get a reference name on line 4.a,
@@
 During the initialization of the function call, the \textbf{IteratorBindingInitialization}
-algorithm is executed with additional parameters \textit{iteratorRecord} and
+algorithm in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
 \textit{environment} to assign argument values to parameters.
@@
 another specification bug existed in \textbf{IteratorBindingInitialization} of
-\textit{FormalParameter}.  The additional \textit{environment} parameter may
+\textit{FormalParameter} in Figure~\ref{fig:example}(c).  The additional \textit{environment} parameter may
 contain \jscode{undefined} or an environment record exactly the same as
@@
 \paragraph{Operand Checker} After the function call initialization, the
-parameter \jscode{x} has the value \jscode{true}, and \jscode{Math.round} is invoked
+parameter \jscode{x} has the value \jscode{true}, and \jscode{Math.round} in Figure~\ref{fig:example}(d) is invoked
 with the argument \jscode{true}.  The \jscode{Math.round} built-in library first

### 2021-04-22 paper/ase21/overview.tex
[ASE21] Added compilation example in overview

@@
 ECMAScript uses abstract algorithms written in a structured natural language to
-describe the JavaScript semantics. While $\jiset$ compiles abstract algorithms to functions in $\ires$,
-we modify $\ires$ to make it more suitable for type analysis as
-formally defined in Section~\ref{sec:ires}.
+describe the JavaScript semantics.  $\jiset$ compiles such abstract algorithms to
+$\ires$ functions with parameters and local variables.  For example, the
+algorithm step
+``\raisebox{-0.55ex}{\includegraphics[width=0.55\columnwidth]{img/compile-example}}''
+is compiled to an $\ires$ instruction $\kwlet \; \code{baseObj} \code{=}
+\escaped\!  \code{ToObject(V.Base)}$.  To make it more suitable for type
+analysis, we modify $\ires$ as formally defined in Section~\ref{sec:ires}.
 

### 2021-04-22 paper/ase21/eval.tex
[ASE21] Applied more comments / Updated all numbers

@@
       {\mr{2}{\stextsf{\scriptsize Reference}}}
-      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
+      {\me{2}{62}{106}{58.5}} {\me{2}{63}{78}{80.8}} {\me{2}{+1}{-28}{+22.3}}
       {\mr{1}{\stextsf{\scriptsize UnknownVar}}}
-      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{}{-28}{+11.1}}
+      {\me{1}{17}{60}{28.3}} {\me{1}{17}{31}{54.8}} {\me{1}{}{-29}{+26.5}}
 
@@
       {\mr{1}{\stextsf{\scriptsize DuplicatedVar}}}
-      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}
+      {\me{1}{45}{46}{97.8}} {\me{1}{46}{47}{97.9}} {\me{1}{+1}{+1}{+0.1}}
 
@@
       {\mr{1}{\stextsf{\scriptsize Assertion}}}
-      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{}{-26}{+7.4}}
+      {\me{1}{4}{56}{7.1}} {\me{1}{4}{31}{12.9}} {\me{1}{}{-25}{+5.8}}
 
@@
       {\textbf{Total}}
-      {91 / 299 (30.4\%)}{92 / 177 (52.0\%)}{+1 / -122 (+21.5\%)}
+      {92 / 279 (33.0\%)}{93 / 157 (59.2\%)}{+1 / -122 (+26.3\%)}
 
@@
   \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ttl-chro}
-    \caption{TTLs sorted by creation time}
+    \includegraphics[width=\textwidth]{img/life-sort}
+    \caption{Life spans sorted by creation}
   \end{subfigure}
   \begin{subfigure}[b]{0.24\textwidth}
-    \includegraphics[width=\textwidth]{img/ttl-count}
-    \caption{The histogram of TTLs}
+    \includegraphics[width=\textwidth]{img/life-hist}
+    \caption{The histogram of life spans}
   \end{subfigure}
-  \caption{Time to Lives (TTLs) of true bugs}
+  \caption{Life spans of true bugs}
   \vspace*{-1.5em}
-  \label{fig:ttl}
+  \label{fig:life}
 \end{figure}
@@
 in a specific version but does not exist in its previous version, and
-a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
+a bug is \textit{resolved} vice versa. The \textit{life span} of a bug denotes
 the number of days between the created date and the resolved date.
-Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
-Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
-Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
+Figure~\ref{fig:life} illustrates the life spans of true bugs;
+Figure~\ref{fig:life}(a) depicts the life spans sorted by creation and
+Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
 Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
@@
 Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
-the average TTL is \inred{414.5} and the maximum TTL is \inred{1,164}.
-All the bugs with the maximum TTL are inherited ones and they are all newly detected.
+the average life spans is \inred{414.5} and the maximum life span is \inred{1,164}.
+All the bugs with the maximum life span are inherited ones and they are all newly detected.
 
@@
     \multicolumn{1}{@{}c}{\textbf{Created}} &
-    \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}
+    \multicolumn{1}{@{}c@{~}}{\textbf{Life Span}}\\\specialrule{.1em}{.0em}{.0em}
 
@@
 Table~\ref{table:new-bug} summarizes the bugs, their
-related JavaScript language features, and their TTLs.
+related JavaScript language features, and their life spans.
 Except for two bugs in ES12-8, all bugs were introduced in the initial

### 2021-04-22 paper/ase21/abstract.tex
[ASE21] Updated numbers
Reflected comments

@@
   evaluated $\tool$ with all 864 versions in the official ECMAScript repository
-  for the recent three years from 2018 to 2021.  $\tool$ took \inred{137.3}
+  for the recent three years from 2018 to 2021.  $\tool$ took 137.3
   seconds on average to perform type analysis for each version, and detected
-  \inred{161} type-related specification bugs with \inred{56.5}\% precision;
-  \inred{91} out of \inred{161} bugs are true bugs.  Among them, \inred{14}
+  157 type-related specification bugs with 59.2\% precision;
+  93 out of 157 bugs are true bugs.  Among them, 14
   bugs are newly detected by $\tool$, and the committee confirmed them all.

### 2021-04-22 paper/ase21/analyzer.tex
Reflected comments

@@
 interpretation framework~\cite{ai1977, ai1992} with analysis
-sensitivity~\cite{sens-toplas}.  We first extend types as follows:
+sensitivity~\cite{sens-toplas}.  We extend types as follows:
 \begin{figure}[H]
@@
     \const \mid
+    \tabsent \mid
     \bool \mid
     \str \mid
-    \tabsent \mid
     \tnormal(\ty) \mid
@@
 \end{figure} \noindent
-We add types for functions $\func$ and constants $\const$,
-\jscode{Boolean} values $\bool$ and \jscode{String} values $\str$ to precisely
-handle the control flows of branches and field accesses, respectively,
-the absent type $\tabsent$ to represent the absence of variables, and
-$\tnormal(\ty)$ for normal completions whose \code{Value} fields have
-type $\ty$ and $\tabrupt$ for abrupt completions to enhance the
-analysis precision.
+with function types $\func$, constant types $\const$, and
+the absent type $\tabsent$ representing the absence of variables.
+\jscode{Boolean} values $\bool$, \jscode{String} values $\str$,
+$\tnormal(\ty)$ denoting normal completions with \code{Value} fields of type $\ty$,
+and $\tabrupt$ denoting abrupt completions serve to improve the analysis precision.
 

### 2021-04-22 paper/ase21/checker.tex
Reflected comments

@@
 $\expr_1$, and $\expr$, respectively.  The additional checks report
-when a given operand does not conform to its expected type.  According to our
-manual investigation, there existed two different kinds of ill-typed operand
-bugs: two non-numeric operand bugs (\stextsf{NoNumber}) in one pull request, and
-six unchecked abrupt completion bugs (\stextsf{Abrupt}) in five pull requests.
+when a given operand does not conform to its expected type.
+Our manual investigation found two non-numeric operand bugs (\stextsf{NoNumber})
+in one pull request and six unchecked abrupt completion bugs (\stextsf{Abrupt})
+in five pull requests.
 
-For an example of non-numeric operand bugs, consider the built-in
+For an example non-numeric operand bug, consider the built-in
 algorithm $\code{Math.round}$ in Figure~\ref{fig:example}(d).  The types of $\x$
-and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the
-\textbf{ToNumber} algorithm always returns number values or abrupt completions,
+and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because
+\textbf{ToNumber} always returns number values or abrupt completions,
 and the prefix \textbf{?} removes the latter case.  The built-in algorithm
@@
 
-An unchecked abrupt completion bug occurs when the actual value is necessary but
-it is an abrupt completion.  ECMAScript has a special implicit conversion for
-normal completions when their actual values stored in the $\code{Value}$ field
-are necessary, such as conditions, values of field updates, and operands of
-operators.  For example, if the variable $\x$ has a normal completion with
+An unchecked abrupt completion bug occurs when an actual value is necessary but
+it is an abrupt completion.  ECMAScript has a special implicit conversion for normal completions
+when their actual values stored in the $\code{Value}$ field are necessary.
+An actual value is necessary in various contexts such as
+conditions, values of field updates, and operands of operators.
+For example, if the variable $\x$ has a normal completion with
 \code{42} as its actual value, $\code{x + 1}$ should be \code{43} because the
-normal completion gets implicitly converted into its actual value \code{42}.  To
-explicitly represent this conversion, we define a unary operator $\escaped$ as
-follows:
+normal completion gets implicitly converted into its actual value \code{42}.
+We define a unary operator $\escaped$ to explicitly represent this conversion:
 \begin{figure}[H]
@@
 \end{figure} \noindent
-and assume that the operator $\escaped$ is used when the actual value is necessary.
+The operand checker detects unchecked abrupt completion bugs by assuming
+that the operator $\escaped$ is used when the actual value is necessary.

### 2021-04-22 paper/ase21/conclusion.tex
Reflected comments

@@
 We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
-for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
-to perform type analysis for each version, and detected \inred{157} type-related specification bugs with
-\inred{59.2}\% precision; \inred{93} out of \inred{157} reported bugs are true bugs.
-Among them, \inred{14} bugs are newly detected by $\tool$, and the
+for the last three years from 2018 to 2021.  It took 137.3 seconds on average
+to perform type analysis for each version, and detected 157 type-related specification bugs with
+59.2\% precision; 93 out of 157 reported bugs are true bugs.
+Among them, 14 bugs are newly detected by $\tool$, and the
 committee confirmed them all.

### 2021-04-22 paper/ase21/eval.tex
Reflected comments

@@
 (d) the analysis time.  For each version, $\tool$ analyzed
-\inred{1,696.6} functions on average.  Since ECMAScript has gradually evolved,
-it analyzed \inred{1,491} functions for the first version in 2018
-but analyzed \inred{1,864} functions in the latest.
+1,696.6 functions on average.  Since ECMAScript has gradually evolved,
+it analyzed 1,491 functions for the first version in 2018
+but analyzed 1,864 functions in the latest.
 $\tool$ analyzes functions with flow- and type-sensitive views.
-On average, each version has \inred{92.0}K views and each function has
-\inred{54.1}~views.
+On average, each version has 92.0K views and each function has
+54.1~views.
 
@@
 and the analysis time.  For each version of ECMAScript,
-$\tool$ took \inred{137.3} seconds with \inred{301.6}K iterations of
-the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
-for the specification extraction (\stextsf{extract}),
-\inred{128.5} seconds for the type analysis (\stextsf{analyze}), and
-\inred{0.8} seconds for the bug detection (\stextsf{detect}).
-Therefore, We believe that $\tool$ is enough to be as part of continuous
-integration pipeline in open development process of ECMAScript.
+$\tool$ took 137.3 seconds with 301.6K worklist iterations
+on average.  The average analysis time is 8.0 seconds
+for specification extraction (\stextsf{extract}),
+128.5 seconds for type analysis (\stextsf{analyze}), and
+0.8 seconds for bug detection (\stextsf{detect}).
+The performance overhead is modest enough for $\tool$ to be integrated
+in the open development process of ECMAScript.
 
@@
 
-We measured the analysis precision with the number of true bugs in
-the type-related specification bugs detected by $\tool$.
+We measured the analysis precision with the ratio of true bugs in the reported bugs by $\tool$.
 As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
-is \inred{59.2}\%; \inred{93} out of \inred{157} detected bugs are true bugs.
-The reference checker detected the most bugs with \inred{80.8}\% precision;
-\inred{17} unknown variables (\stextsf{UnknownVar}) and
-\inred{46} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
-We found \inred{four} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
-\inred{four} assertion failures (\stextsf{Assertion}) with \inred{12.9}\% precision.
+is 59.2\%; 93 out of 157 detected bugs are true bugs.
+The reference checker detected the most bugs with 80.8\% precision;
+17 unknown variables (\stextsf{UnknownVar}) and
+46 duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
+We found four missing parameters (\stextsf{MissingParam}) with 100.0\% precision and
+four assertion failures (\stextsf{Assertion}) with 12.9\% precision.
 Finally, the operand checker detected
-\inred{two} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
-\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.
+two non-numeric operand bugs (\stextsf{NoNumber}) with 33.3\% precision and
+20 unchecked abrupt completion bugs (\stextsf{Abrupt}) with 52.6\% precision.
 
@@
 Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
-Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
+Among 93 true bugs, 48 bugs are \textit{inherited},
 which means that they are created before 2018,
-and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
-We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
-Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
-the average life spans is \inred{414.5} and the maximum life span is \inred{1,164}.
+and 14 bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
+We discuss the details of 14 newly found bugs in Section~\ref{sec:new-bug}.
+Even though we assume that 48 inherited bugs are created on January 1, 2018,
+the average life span is 414.5 and the maximum life span is 1,164.
 All the bugs with the maximum life span are inherited ones and they are all newly detected.
 
-We manually investigated \inred{64} false-positive bugs to understand why
-$\tool$ detected them.  Among them, \inred{17} bugs are due to extraction failure
+We manually investigated 64 false-positive bugs to understand why
+$\tool$ detected them.  Among them, 17 bugs are due to extraction failure
 of mechanized specifications caused by wrong writing styles.
@@
 which causes extraction failure of mechanized specifications leading
-to false-positive bugs.  The remaining \inred{47} bugs are due to imprecise analysis.
-We found that \inred{28} bugs are due to imprecise analysis of the
+to false-positive bugs.  The remaining 47 bugs are due to imprecise analysis.
+We found that 28 bugs are due to imprecise analysis of the
 conditions of assertions and branches for specific function calls.
@@
     \stextsf{\footnotesize Operand} &
-    \inred{2015-12-16} &
-    \inred{1,910 days}\\
+    2015-12-16 &
+    1,910 days\\
   \end{tabular}
@@
 \ref{fig:performance-compare}(d) are scatter charts for their ratios.
-Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
+Without refinement, the type analysis took 91.9 seconds with 261.5K
 iterations on average.  After applying refinement, the number of iterations is increased
-at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
-the analysis time is increased at least \inred{1.05}x, at most \inred{1.99}x,
-and \inred{1.41}x on average.
+at least 0.99x, at most 1.36x, and 1.16x on average, and
+the analysis time is increased at least 1.05x, at most 1.99x,
+and 1.41x on average.
 
@@
 with refinement, and their difference.  The refinement improved the analysis
-precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
-false-positive bugs and detecting \inred{one} more true bug.  Among six
+precision from 33.0\% to 59.2\% by removing 122
+false-positive bugs and detecting one more true bug.  Among six
 bug kinds, the most significant improvement is for non-numeric
-operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
-by removing \inred{59} false-positive bugs.  The refinement technique
+operand bugs (\stextsf{NoNumber}) from 3.1\% to 33.3\%
+by removing 59 false-positive bugs.  The refinement technique
 successfully prunes out non-numeric values for numeric types.
@@
 variable bugs (\stextsf{UnknownVar}) and assertion failures
-(\stextsf{Assertion}) by removing \inred{29} and \inred{25} false-positive bugs, respectively.
+(\stextsf{Assertion}) by removing 29 and 25 false-positive bugs, respectively.
 Because $\tool$ can precisely analyze callees of function invocations
@@
 
-Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
+Among 93 true bugs detected by $\tool$, 14 are newly
 detected and still exist in the latest version of ECMAScript.

### 2021-04-22 paper/ase21/intro.tex
Reflected comments

@@
 algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.
-In the official ECMAScript repository, \inred{1,355} pull
-requests and \inred{2,005} commits exist in the master branch.
+In the official ECMAScript repository, 1,355 pull
+requests and 2,005 commits exist in the master branch.
 Therefore, manually checking all the frequent specification updates is
@@
 \textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
-\textbf{R}efinement. In order to perform a \textit{type analysis} on ECMAScript
-to statically detect type-related specification bugs automatically,
-the main challenge is that ECMAScript describes abstract algorithms in
-a natural language, English. While researchers~\cite{lambdajs, jscert, kjs}
+\textbf{R}efinement. The main challenge of ECMAScript type analysis to
+statically detect type-related specification bugs automatically is
+that ECMAScript describes abstract algorithms in a natural language,
+English.  While researchers~\cite{lambdajs, jscert, kjs}
 have formally defined various JavaScript semantics for different
@@
 
-For mechanized JavaScript specifications by $\jiset$, $\tool$ performs
+$\tool$ takes mechanized JavaScript specifications from $\jiset$ and performs
 a type analysis of compiled functions using \textit{specification types}
@@
 trees (ASTs), internal list-like structures, and internal records
-including environments, completions, and property descriptors. We
-define their type hierarchies based on subtype relations and fields for record and AST types.
+including environments, completions, and property descriptors.
+\inred{We define their type hierarchies based on subtype relations and fields for record and AST types.}
 Using such type information, $\tool$ performs a type analysis and detects specification bugs using
@@
 of assertions and branches to improve the precision of type analysis.
-We evaluated $\tool$ with all \inred{864} versions in the official
+We evaluated $\tool$ with all 864 versions in the official
 ECMAScript repository for the recent three years from 2018 to 2021.
@@
     precision.  We show that the refinement technique increases the analysis
-    precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
-    false bugs and detecting \inred{one} more true bug.
-  \item We demonstrate the practicality of $\tool$. It takes \inred{137.3}
+    precision from 33.0\% to 59.2\% by removing 122
+    false bugs and detecting one more true bug.
+  \item We demonstrate the practicality of $\tool$. It takes 137.3
     seconds on average to perform a type analysis for each version of ECMAScript and detected
-    \inred{157} type-related specification bugs with \inred{59.2}\% precision;
-    \inred{93} out of \inred{157} bugs are true bugs.  Among them, $\tool$
-    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
+    157 type-related specification bugs with 59.2\% precision;
+    93 out of 157 bugs are true bugs.  Among them, $\tool$
+    newly detected 14 bugs, and the ECMAScript committee confirmed them all.
 \end{itemize}

### 2021-04-22 paper/ase21/overview.tex
Reflected comments

--- 2021-04-22 paper/ase21/overview.tex
@@
 \subsection{Specification Extraction}\label{sec:overview-spec-extract}
-$\tool$ extracts the JavaScript syntax and semantics using $\jiset$,
-and it extracts specification types from ECMAScript.
+$\tool$ extracts the JavaScript syntax and semantics using $\jiset$
+and extracts specification types from ECMAScript.
 
 \paragraph{Syntax and Semantics}
-ECMAScript uses a variant of extended BNF notations to describe the JavaScript syntax.
-While $\jiset$ synthesizes AST structures and JavaScript parsers from
-the lexical and syntactic productions in ECMAScript, $\tool$ uses only
-AST structures to define their types and access corresponding syntax-directed algorithms.
-ECMAScript uses abstract algorithms written in a structured natural language to
-describe the JavaScript semantics. While $\jiset$ compiles abstract algorithms to functions in $\ires$,
-we modify $\ires$ to make it more suitable for type analysis as
-formally defined in Section~\ref{sec:ires}.
+ECMAScript describes the JavaScript syntax in an EBNF notation
+and the semantics using abstract algorithms written in a structured natural language.
+From ECMAScript, $\jiset$ synthesizes AST structures for syntax and 
+compiles the abstract algorithms to $\ires$ functions with parameters
+and local variables for semantics.  For example, the algorithm step
+``\raisebox{-0.55ex}{\includegraphics[width=0.55\columnwidth]{img/compile-example}}''
+is compiled to an $\ires$ instruction $\kwlet \; \code{baseObj}\; \code{=}
+\escaped\!  \code{ToObject(V.Base)}$.  To make it suitable for type analysis,
+we modify $\ires$ as formally defined in Section~\ref{sec:ires}.
 
@@
 For ASTs, we use their production names as their
-types and automatically link their corresponding syntax-directed algorithms as their fields.
+types and automatically link their corresponding syntax-directed algorithms to their fields.
 Second, ECMAScript supports various record types and fields
@@
 initial set of views for a worklist. ECMAScript provides three
-kinds of abstract algorithms: \textit{normal}, \textit{syntax-directed}, and
-\textit{built-in}. Since syntax-directed algorithms and built-in algorithms have
-their parameter types, we use them as entry points of type analysis.  For each entry point, the
+kinds of abstract algorithms: \textit{normal}, \textit{syntax-directed}, and \textit{built-in}. 
+As for entry points of type analysis, we use syntax-directed algorithms and built-in algorithms
+because they have their parameter types.  For each entry point, the
 initializer defines its abstract environment with parameter types and adds the
@@
 \paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
-During the initialization of the function call, the \textbf{IteratorBindingInitialization}
-algorithm in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
+During the initialization of the function call, \textbf{IteratorBindingInitialization}
+in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
 \textit{environment} to assign argument values to parameters.
@@
 \paragraph{Assertion Checker} During the initialization of the function call,
-another specification bug existed in \textbf{IteratorBindingInitialization} of
-\textit{FormalParameter} in Figure~\ref{fig:example}(c).  The additional \textit{environment} parameter may
+another bug existed in \textbf{IteratorBindingInitialization} of
+\textit{FormalParameter} in Figure~\ref{fig:example}(c).
+The additional \textit{environment} parameter may
 contain \jscode{undefined} or an environment record exactly the same as
 \textit{originalEnv} as described in the assertion on line 5.
-However, the assertion missed that the initial commit
+\inred{However, the assertion missed that the initial commit
 of the open development process on September 22, 2015 introduced
-\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.
+\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.}
 The assertion checker can detect such assertion failures.
@@
 converts the given parameter \textit{x} to its corresponding number value
-\textit{n} using \textbf{ToNumber}, and then performs the remaining
+\textit{n} using \textbf{ToNumber}, and performs the remaining
 steps using \textit{n}.  However, a contributor mistakenly used
@@
 This bug caused the algorithm to compare the boolean value \jscode{true} with the
-numeric value 0.5 or 0 in the example JavaScript program.
+numeric value 0.5 or 0 in the example code.
 This bug lived for two days until another contributor fixed it, and
-the operand checker can detect such bugs.
+the operand checker can detect them.
 

### 2021-04-23 paper/ase21/intro.tex
Revised two parts

@@
 including environments, completions, and property descriptors.
-\inred{We define their type hierarchies based on subtype relations and fields for record and AST types.}
+We define their type hierarchies based on subtype relations.
+For records and AST types, we also define their fields.
 Using such type information, $\tool$ performs a type analysis and detects specification bugs using

### 2021-04-23 paper/ase21/overview.tex
Revised two parts

@@
 \jscode{??=}, which was fixed by another contributor on November 3, 2020.
-Thus, the unknown variable bug for \textbf{GetReferencedName} existed for 7 days,
+Thus, the unknown variable bug for \textbf{GetReferencedName} lasted for 7 days,
 which the reference checker can detect.
@@
 \textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
-It caused an arity mismatch bug, which existed for 533 days until another
+It caused an arity mismatch bug, which lasted for 533 days until another
 contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.
@@
 \paragraph{Assertion Checker} During the initialization of the function call,
-another bug existed in \textbf{IteratorBindingInitialization} of
-\textit{FormalParameter} in Figure~\ref{fig:example}(c).
-The additional \textit{environment} parameter may
-contain \jscode{undefined} or an environment record exactly the same as
-\textit{originalEnv} as described in the assertion on line 5.
-\inred{However, the assertion missed that the initial commit
-of the open development process on September 22, 2015 introduced
-\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.}
+\textbf{IteratorBindingInitialization} of \textit{FormalParameter} in Figure~\ref{fig:example}(c)
+contains another bug.
+Even though the additional \textit{environment} parameter may contain \jscode{undefined},
+a contributor did not consider it on line 5 in the initial commit of the open development process
+on September 22, 2015.  It caused an assertion failure bug, which lasted for 1,297 days until another
+contributor fixed it on April 10, 2019.
 The assertion checker can detect such assertion failures.

### 2021-07-09 paper/ase21/eval.tex
Fixed minor number typo in eval.tex

@@
 Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
-Among 93 true bugs, 48 bugs are \textit{inherited},
-which means that they are created before 2018,
-and 14 bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
+Among 93 true bugs, 49 bugs are \textit{inherited},
+which means that they are created before 2018.
+Moreover, 14 bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
 We discuss the details of 14 newly found bugs in Section~\ref{sec:new-bug}.
-Even though we assume that 48 inherited bugs are created on January 1, 2018,
-the average life span is 414.5 and the maximum life span is 1,164.
+Even though we assume that 49 inherited bugs are created on January 1, 2018,
+the average life span is 422.8 and the maximum life span is 1,164.
 All the bugs with the maximum life span are inherited ones and they are all newly detected.

### 2021-07-10 paper/ase21/artifact/main.tex
Added artifiact pdf

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{url}
\usepackage{stmaryrd}
\usepackage{colortbl}
\usepackage{ctable}
\usepackage{makecell}
\usepackage{graphics}
\usepackage{float}

\lstset{basicstyle=\ttfamily}
\newcommand{\stextsf}[1]{\textsf{\small #1}}
\newcommand{\bigtool}{\textsf{JSTAR}}
\newcommand{\tool}{\stextsf{JSTAR}}
\newcommand{\jiset}{\stextsf{JISET}}

\lstdefinestyle{code}{
  numbers=none,
  extendedchars=true,
  basicstyle=\small\ttfamily,
  showstringspaces=false,
  showspaces=false,
  xleftmargin=\parindent,
  tabsize=2,
  breaklines=true,
  showtabs=false,
  captionpos=b
}

\newcommand{\code}[1]{\text{\lstinline[style=code]!#1!}}

\begin{document}

\title{$\bigtool$: JavaScript Specification Type Analyzer using Refinement}

\author{
  \IEEEauthorblockN{Jihyeok Park}
  \IEEEauthorblockA{\textit{School of Computing}\\
  \textit{KAIST}\\
  Daejeon, South Korea\\
  jhpark0223@kaist.ac.kr}

  \and

  \IEEEauthorblockN{Seungmin An}
  \IEEEauthorblockA{\textit{School of Computing}\\
  \textit{KAIST}\\
  Daejeon, South Korea\\
  h2oche@kaist.ac.kr}

  \and

  \IEEEauthorblockN{Wonho Shin}
  \IEEEauthorblockA{\textit{School of Computing}\\
  \textit{KAIST}\\
  Daejeon, South Korea\\
  new170527@kaist.ac.kr}

  \and

  \IEEEauthorblockN{Yusung Sim}
  \IEEEauthorblockA{\textit{School of Computing}\\
  \textit{KAIST}\\
  Daejeon, South Korea\\
  yusungsim@kaist.ac.kr}

  \and

  \IEEEauthorblockN{Sukyoung Ryu}
  \IEEEauthorblockA{\textit{School of Computing}\\
  \textit{KAIST}\\
  Daejeon, South Korea\\
  sryu.cs@kaist.ac.kr}
}

\maketitle

\begin{abstract}
  This document describes the artifact package accompanying the ASE 2021 paper
  ``$\tool$: JavaScript Specification Type Analyzer using Refinement.'' The
  artifact includes $\tool$ source code, the accepted paper, a companion report,
  ECMAScript (JavaScript specification) open-source repository as a git
  submodule, and scripts to replicate the data presented in the paper. $\tool$
  performs type analysis on any commit version of ECMAScript to detect
  type-related specification bugs. $\tool$ is an extended tool of $\jiset$, a
  JavaScript IR-based Semantics Extraction Toolchain. We hope that the artifact
  will be useful for contributors who update JavaScript specifications by
  automatically detecting type-related specification bugs before releasing them.
\end{abstract}

\begin{IEEEkeywords}
JavaScript, mechanized specification, type analysis, refinement, bug detection
\end{IEEEkeywords}

\section{Getting Started Guide}
The artifact is open-source can be obtained by cloning the following git
repository:
\begin{lstlisting}
$ git clone --recurse-submodules \
  https://github.com/kaist-plrg/jstar.git
\end{lstlisting}
Please see \code{INSTALL.md} for the detailed guide of installation, how to use
this artifact.

\section{Overall Structure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{../img/overall}
  \vspace*{-1.5em}
\end{figure}

$\tool$ consists of three phases: 1) specification extraction, 2) type analysis,
and 3) bug detection.  Details of the JSTAR framework are available in the paper
\code{ase21-park-jstar.pdf} and the companion report
\code{ase21-park-jstar-report.pdf}.

\subsection{Specification Extraction}
We utilizes another tool $\jiset$\footnote{https://github.com/kaist-plrg/jiset},
which is a \textbf{J}avaScript \textbf{I}R-based \textbf{S}emantics
\textbf{E}xtraction \textbf{T}oolchain, to extract a mechanized specification
from given ECMAScript.

\subsection{Type Analysis}
JSTAR performs a type analysis with flow-sensitivity and type-sensitivity for
arguments.  Each function is split into multiple flow- and type-sensitive views,
and an abstract state stores mapping from views to corresponding abstract
environments.  To handle views separately, we use a worklist algorithm.  The
type analyzer consists of two sub-modules: an \textbf{Analysis Initializer} and
an \textbf{Abstract Transfer Function}.
\begin{itemize}
  \item \textbf{Analysis Initializer} defines the initial abstract state and the initial
    set of views for a worklist.
  \item \textbf{Abstract Transfer Function} gets a specific view from the worklist and
    updates the abstract environments of the next views based on the abstract
    semantics for each iteration.
\end{itemize}

\subsection{Bug Detection}
To detect type-related specification bugs utilizing the type analysis, we
developed four checkers in a bug detector:

\begin{itemize}
  \item \textbf{Reference Checker} detects \textit{reference bugs} which occur
    when trying to access variables not yet defined (`UnknownVar`) or to
    redefine variables already defined (`DuplicatedVar`).
  \item \textbf{Arity Checker} detects \textit{arity bugs}. An arity bug occurs
    when the number of arguments does not match with the function arity
    (`MissingParam`).
  \item \textbf{Assertion Checker} detects \textit{assertion failures}. An
    assertion failure (`Assertion`) occurs when the condition of an assertion
    instruction is not true.
  \item \textbf{Operand Checker} detects \textit{ill-typed operand bugs}. An
    ill-typed operand bug occurs when the type of an operand does not conform to
    its corresponding parameter type.  It contains non-numeric operand bugs
    (`NoNumber`) and unchecked abrupt completion bugs (`Abrupt`).
\end{itemize}

\end{document}

### 2021-08-15 paper/ase21/artifact/main.tex
Updated artifact pdf

@@
 Please see \code{INSTALL.md} for the detailed guide of installation, how to use
-this artifact.
+this artifact.  We also provide this artifact in Zenodo with a
+DOI\footnote{https://doi.org/10.5281/zenodo.5084817}
+and docker image as follows:
+\begin{lstlisting}
+$ docker run -it --rm jhnaldo/jstar
+\end{lstlisting}
 
@@
 and an abstract state stores mapping from views to corresponding abstract
-environments.  To handle views separately, we use a worklist algorithm.  The
-type analyzer consists of two sub-modules: an \textbf{Analysis Initializer} and
-an \textbf{Abstract Transfer Function}.
+environments.  The type analyzer consists of two sub-modules: an
+\textbf{Analysis Initializer} and an \textbf{Abstract Transfer Function}.
 \begin{itemize}
@@
     ill-typed operand bug occurs when the type of an operand does not conform to
-    its corresponding parameter type.  It contains non-numeric operand bugs
-    (`NoNumber`) and unchecked abrupt completion bugs (`Abrupt`).
+    its corresponding parameter type.
 \end{itemize}

### 2021-08-15 src/main/scala/kr/ac/kaist/jiset/analyzer/AbsTransfer.scala
Pass jsAnalyzeTest

@@ -422,7 +422,19 @@ case class AbsTransfer(sem: AbsSemantics) {
           set
         }
       } yield resB).map(Bool(_))))
-      case EGetElems(base, name) => ???
+      case elems @ EGetElems(base, name) => {
+        val loc: AllocSite = AllocSite(elems.asite, cp.view)
+        for {
+          bv <- escape(transfer(base))
+          _ <- bv.getSingle match {
+            case FlatBot => put(AbsState.Bot)
+            case FlatElem(AAst(ast)) =>
+              val vs = ast.getElems(name).map(AbsValue(_))
+              modify(_.allocList(vs)(loc))
+            case _ => ???
+          }
+        } yield AbsValue(loc)
+      }
       case EGetSyntax(base) => for {
         v <- escape(transfer(base))
         s = AbsStr(v.ast.toList.map(x => Str(x.ast.toString)))

### 2021-08-15 src/main/scala/kr/ac/kaist/jiset/analyzer/domain/BasicState.scala

@@ -217,7 +217,7 @@ object BasicState extends Domain {
       val escaped = base.escaped
       // TODO check soundness
       // handle base: {~normal~ -> (#REALM, ~empty~)}, prop: "Type" case
-      val locValue = 
+      val locValue =
         if (compValue != AbsValue.Bot && prop ⊑ AV_COMP_PROPS) AbsValue.Bot
         else heap(escaped.loc, prop)
       val strValue = (escaped.str.getSingle, prop.getSingle) match {

### 2021-08-15 src/main/scala/kr/ac/kaist/jiset/ir/syntax/Expr.scala

@@ -30,7 +30,7 @@ case class EBOp(bop: BOp, left: Expr, right: Expr) extends Expr
 case class ETypeOf(expr: Expr) extends Expr
 case class EIsCompletion(expr: Expr) extends Expr
 case class EIsInstanceOf(base: Expr, name: String) extends Expr with AllocSite
-case class EGetElems(base: Expr, name: String) extends Expr
+case class EGetElems(base: Expr, name: String) extends Expr with AllocSite
 case class EGetSyntax(base: Expr) extends Expr
 case class EParseSyntax(code: Expr, rule: Expr, parserParams: List[Boolean]) extends Expr
 case class EConvert(source: Expr, target: COp, flags: List[Expr]) extends Expr

### 2021-08-15 paper/ase21/artifact/rebuttal.md
Added rebuttal.md

We sincerely thank the reviewers for their careful reviews and detailed
suggestions for improvement. We reflected the suggestions in the artifact and
we answered the questions from the reviewers as follows:

### Q1) Author Information
We missed to explicitly include author information in the artifact. We added
`AUTHORS.md` file in the updated version.

### Q2) DOI (Zenodo)
We already provided the following DOI created by Zenodo in the submission:
- [https://doi.org/10.5281/zenodo.5084817](https://doi.org/10.5281/zenodo.5084817)

However, since it points to a specific version of the artifact, we updated DOI
to point out all versions of the artifact as follows:
- [https://doi.org/10.5281/zenodo.5084816](https://doi.org/10.5281/zenodo.5084816)

### Q3) Docker image
In the submission, we omitted to create docker image because we believe that
our installation guide is enough to evaluate the artifact and reproduce the
evaluation results in the paper.  However, we totally agree that providing
docker image is much easier to do them.  Thus, we create the following docker
image:
```bash
$ docker run -it -m=16g --rm jhnaldo/jstar
# user: jstar / password: jstar
```

### Q4) `ValueError` during `jstar-exp` (for Reviewer A)
The `ValueError` might occur when the `$JSTAR_HOME/eval/result` contains illegal
data.  Please try again after cleaning the `result` directory as follows:
```bash
$ rm -rf $JSTAR_HOME/eval/result && mkdir $JSTAR_HOME/eval/result
```
Moreover, you don't have to perform type analysis for all versions.  We
recommend you check several random versions using the following commands:
```bash
$ jstar-exp -v <version> # add `-nr` for no refinement
```
and use given raw data in directories `raw-refine` and `raw-no-refine` in the
`eval` directory:
```bash
$ rm -rf result && mkdir result  # clean up result directory
$ cp -r raw-refine result/raw    # copy the given raw data
$ jstar-exp -s                   # create summary of raw data
```
and
```bash
$ rm -rf result && mkdir result  # clean up result directory
$ cp -r raw-no-refine result/raw # copy the given raw data
$ jstar-exp -s                   # create summary of raw data
```

### 2021-10-07 paper/pldi22/abstract.tex
Added paper

\begin{abstract}\label{sec:abstract}
  \todo
\end{abstract}

### 2021-10-07 paper/pldi22/intro.tex
Added paper

--- 2021-04-22 paper/ase21/intro.tex
@@
 
-JavaScript is one of the most popular programming languages.  According to the
-2020 State of the Octoverse\footnote{https://octoverse.github.com/},
-the annual report of GitHub, the most dominating programming language in GitHub
-repositories was JavaScript since 2014 to 2020.  While JavaScript was initially
-designed for client-side programming in web browsers, it is now widely used in
-server-side programming~\cite{nodejs} and even in embedded
-systems~\cite{espruino, tessel2, moddable}.  Developers in diverse fields
-build and maintain JavaScript engines conforming to ECMAScript, the
-JavaScript standard specification, which describes the syntax and semantics of
-JavaScript in a natural language.
-
-The correctness of ECMAScript is critical because an incorrect
-description in the specification can lead to wrong
-implementations of JavaScript engines in various fields.  However,
-all the specification updates are currently manually reviewed by the Ecma
-Technical Committee 39 (TC39) without any automated tools.
-Such a manual review process is inherently labor-intensive and error-prone,
-making ECMAScript vulnerable to specification bugs.
-Besides, in late 2014, the committee announced the yearly release cadence and open development
-process of ECMAScript to quickly adapt to evolving development environments.
-According to Park et al.~\cite{jiset}, the average number of updated steps of abstract
-algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.
-In the official ECMAScript repository, 1,355 pull
-requests and 2,005 commits exist in the master branch.
-Therefore, manually checking all the frequent specification updates is
-a challenging task.
-
-Unfortunately, no existing tools can automatically detect bugs in
-rapidly evolving JavaScript specifications written in English. Thus,
-the ECMAScript committee has pursued various manual annotations in
-abstract algorithms to reduce specification bugs.
-First, the committee has introduced two kinds of annotations: 1)
-\textit{assertions} to denote assumptions at specific points of abstract
-algorithms and 2) two \textit{prefixes} \textbf{?} and \textbf{!} to
-represent whether the execution of an abstract algorithm completes
-abruptly or not. For example, ``Assert: Type(\textit{O}) is Object'' denotes that
-the variable $\textit{O}$ always has an \jscode{Object} value at the
-point of the assertion, and ``\textbf{?} \textbf{GetV}(\textit{V}, \textit{P})'' denotes that
-the execution of \textbf{GetV}(\textit{V}, \textit{P}) may complete abruptly.
-Such annotations help readers understand specifications clearly, and
-they are also helpful for specification-based
-tools\footnote{https://github.com/tc39/ecmarkup/issues/173} such as JavaScript
-engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
-analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert,
-javert2}.
-Second, the committee has started internal discussions on type
-annotations for variables, parameters, and return values of abstract
-algorithms\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
-However, any kinds of manual annotations are labor-intensive and
-error-prone, and they do not provide any automatic mechanism to detect
-specification bugs.
-
-To alleviate this problem, we propose a novel tool $\tool$, a \textbf{J}avaScript
-\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
-\textbf{R}efinement. The main challenge of ECMAScript type analysis to
-statically detect type-related specification bugs automatically is
-that ECMAScript describes abstract algorithms in a natural language,
-English.  While researchers~\cite{lambdajs, jscert, kjs}
-have formally defined various JavaScript semantics for different
-versions of ECMAScript by hand, manual formalization is not suitable for
-automatically detecting bugs in rapidly evolving JavaScript specifications. 
-Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
-network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
-have utilized information directly extracted from specifications written in a natural language
-to lessen such burdens.
-Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
-a structured natural language to functions in $\ires$, an untyped
-intermediate representation for ECMAScript.
-Therefore, $\tool$ leverages $\jiset$ to mechanically handle JavaScript specifications.
-
-$\tool$ takes mechanized JavaScript specifications from $\jiset$ and performs
-a type analysis of compiled functions using \textit{specification types}
-defined in ECMAScript.  ECMAScript contains not only JavaScript
-language types but also specification types such as abstract syntax
-trees (ASTs), internal list-like structures, and internal records
-including environments, completions, and property descriptors.
-\inred{We define their type hierarchies based on subtype relations and fields for record and AST types.}
-Using such type information, $\tool$ performs a type analysis and detects specification bugs using
-a \textit{bug detector} consisting of four checkers: 1) a reference
-checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
-$\tool$ also uses a \textit{condition-based refinement} for type
-analysis, which prunes out infeasible parts in abstract states by using conditions
-of assertions and branches to improve the precision of type analysis.
-We evaluated $\tool$ with all 864 versions in the official
-ECMAScript repository for the recent three years from 2018 to 2021.
-The experiments showed that the refinement technique could reduce the number of
-false-positive bugs caused by spurious types inferred by imprecise type analysis.
-
-The main contributions of this paper are as follows:
 \begin{itemize}
-  \item We present $\tool$, the first tool that performs a \textit{type
-    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
-    specifications.  $\tool$ automatically detects type-related specification
-    bugs such as unknown variables, duplicated variables, missing
-    parameters, assertion failures, ill-typed operands, and unchecked
-    abrupt completion bugs.
-  \item We present a \textit{condition-based refinement} for type analysis of
-    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
-    precision.  We show that the refinement technique increases the analysis
-    precision from 33.0\% to 59.2\% by removing 122
-    false bugs and detecting one more true bug.
-  \item We demonstrate the practicality of $\tool$. It takes 137.3
-    seconds on average to perform a type analysis for each version of ECMAScript and detected
-    157 type-related specification bugs with 59.2\% precision;
-    93 out of 157 bugs are true bugs.  Among them, $\tool$
-    newly detected 14 bugs, and the ECMAScript committee confirmed them all.
+  \item \todo
 \end{itemize}

### 2021-10-07 paper/pldi22/related.tex
Added paper

\section{Related Work}\label{sec:related}

\begin{itemize}
  \item Semantics of programming languages: A tool-oriented approach~\cite{lda}
  \item LISA: An interactive environment for programming language
    development~\cite{lisa}
  \item When and how to develop domain-specific languages~\cite{dsl-survey}
  \item Incremental programming language development~\cite{ipld}
\end{itemize}

\todo

### 2021-10-07 paper/pldi22/related.tex
Added related work with references

@@
 \begin{itemize}
-  \item Semantics of programming languages: A tool-oriented approach~\cite{lda}
-  \item LISA: An interactive environment for programming language
-    development~\cite{lisa}
-  \item When and how to develop domain-specific languages~\cite{dsl-survey}
-  \item Incremental programming language development~\cite{ipld}
+  \item JavaScript specificaiton: ECMAScript (ES12, 2021)~\cite{es12}
+  \item JavaScript tests: Test262~\cite{test262}
+  \item JavaScript tools: engines~\cite{v8, jscore, chakra, spidermonkey},
+    static analyzers~\cite{safe, safe2, tajs, wala, jsai},
+    debugger~\cite{jsexplain}, verification tools~\cite{javert, javert2,
+    ad-safety, javanni}, symbolic execution~\cite{symbolic-js, sym-js, expo-se},
+    concolic testing~\cite{jalangi, type-conc-test}.
+  \item Language Design Assistant (LDA)~\cite{lda, lisa, ipld, asf-sdf,
+    meta-env}
+  \item Domain Specific Language (DSL)~\cite{dsl-survey, dsl-survey2}
+  \item Live Programming~\cite{omnicode, situ-vis, proj-box}
+  \item JISET family: JISET~\cite{jiset}, JEST~\cite{jest}, JSTAR~\cite{jstar}.
+  \item Partial Evaluation~\cite{peval, peval-survey}
 \end{itemize}

### 2021-10-08 paper/pldi22/abstract.tex
Abstract

@@
 \begin{abstract}\label{sec:abstract}
-  \todo
+  JavaScript is a widely-used programming language in various fields.  Recently,
+  it rapidly evolves with a yearly release cadence and open development process
+  to quickly adapt users' demands to the language.  In this fast-evolving nature
+  of JavaScript, the need of \textit{language design assistants} has grown to
+  correctly understand original or revised semantics in the revision process.
+  While several tools have been proposed as language design assistants for
+  JavaScript in academia and industry, they should be manually updated to
+  represent revised semantics and lack the information for better comprehension
+  of language semantics.  To alleviate this problem, we present $\tool$, the
+  first language design assistant for JavaScript that directly synchronizes with
+  language specification and even conformance tests. Moreover, our tool provides
+  a way to focus on specific semantics by automatically reducing semantics and
+  filtering out conformance tests with \textit{syntactic views}. In this paper,
+  we conduct several case studies for the JavaScript language design with
+  $\tool$. Moreover, we evaluate how effectively do syntactic views reduce the
+  semantics and filtering out conformance tests.
 \end{abstract}

### 2021-10-12 paper/pldi22/abstract.tex
Revised abstract

--- 2021-10-07 paper/pldi22/abstract.tex
@@
 \begin{abstract}\label{sec:abstract}
-  \todo
+  JavaScript is a widely-used programming language in various fields. Recently,
+  it rapidly evolved with a yearly release cadence and open development process
+  to quickly adapt users’ demands to the language. In this fast-evolving nature
+  of JavaScript, the need for \textit{language design assistants} has grown to
+  understand original or revised semantics in the revision process correctly.
+  Unfortunately, while several tools have been proposed as language design
+  assistants for JavaScript in academia and industry, they should be manually
+  updated to represent revised semantics every time. Besides, they lack the
+  additional information for better comprehension of language semantics,
+  including the relationship between specific semantics with conformance tests.
+
+  To alleviate this problem, we present $\tool$, a \textit{live} language design
+  assistant for JavaScript. It automatically synchronizes with a given language
+  specification and shows related conformance tests in the revision process.
+  Moreover, to better comprehend language semantics, we present a way to focus
+  on specific semantics by automatically reducing semantics and filtering out
+  conformance tests with user-defined \textit{syntactic views}. In this paper,
+  we conduct several case studies for JEDIT to demonstrate the effectiveness of
+  live language design with syntactic views. Moreover, we experimentally show
+  that syntactic views successfully reduce the \inred{XX.X}\% of semantics and
+  filter out \inred{XX.X}\% of conformance tests on average using historically
+  representative syntactic views.
 \end{abstract}

### 2021-10-12 src/main/scala/kr/ac/kaist/jiset/ir/Debugger.scala
Remove JS breakpoint, JS state viewer

@@ -99,7 +99,6 @@ trait Debugger {
 
   // breakpoints
   val breakpoints = ArrayBuffer[(InterpHook, Breakpoint)]()
-  // val breakpointsJS = ArrayBuffer[(InterpHook, Breakpoint)]()
 
   // check if current step is in break
   final def isBreak: Boolean = breakpoints.foldLeft(false) {
@@ -153,42 +152,6 @@ trait Debugger {
       bp.toggle()
   }
 
-  // // add break on JS
-  // final def addBreakJS(line: Int, enabled: Boolean = true) = {
-  //   val bp = JSBreakpoint(line)
-  //   val hook = interp.subscribe("", Interp.Event.Call, st => {
-  //     val (l0, l1, _, _) = st.getJSInfo()
-  //     if (l0 == l1) { bp.check(l0.toString) }
-  //   })
-  //   bp.enabled = enabled
-  //   breakpointsJS += ((hook, bp))
-  // }
-
-  // // remove break on JS
-  // final def rmBreakJS(opt: String) = opt match {
-  //   case "all" =>
-  //     breakpointsJS.foreach { case (hook, _) => interp.unsubscribe(hook) }
-  //     breakpointsJS.clear
-  //   case _ =>
-  //     val idx = getBreakIdx(breakpointsJS, opt)
-  //     val (hook, _) = breakpointsJS(idx)
-  //     breakpointsJS.remove(idx)
-  //     interp.unsubscribe(hook)
-  // }
-  // // toggle break on JS
-  // final def toggleBreakJS(opt: String) = opt match {
-  //   case "all" =>
-  //     breakpointsJS.foreach { case (_, bp) => bp.toggle() }
-  //   case _ =>
-  //     val idx = getBreakIdx(breakpointsJS, opt)
-  //     val (_, bp) = breakpointsJS(idx)
-  //     bp.toggle()
-  // }
-
-  // final def isBreakJS: Boolean = breakpointsJS.foldLeft(false) {
-  //   case (acc, (_, bp)) => bp.needTrigger || acc
-  // }
-
   // remove watch
   final def rmWatch(opt: String) = opt match {
     case "all" =>
@@ -227,74 +190,5 @@ trait Debugger {
       case (expr, i) =>
         val result = evalExpr(expr)
         println(f"$i: $expr%-20s $result")
-    }
-
-  private def findAddrInHeap(from: Addr, key: String): Long =
-    st.heap.apply(from, Str(key)) match {
[…]

### 2021-10-12 src/main/scala/kr/ac/kaist/jiset/js/Debugger.scala

@@ -10,6 +10,7 @@ import kr.ac.kaist.jiset.spec.JsonProtocol._
 import scala.collection.mutable.{ Map => MMap }
 
 // ECMAScript Debugger
+// TODO JS breakpoint, JS state
 class Debugger(override val st: State) extends IRDebugger {
   type StepResult = Debugger.StepResult
   detail = false
@@ -92,12 +93,6 @@ class Debugger(override val st: State) extends IRDebugger {
       case (addr, obj) => (addr.toString, obj.toString)
     }
   )
-
-  // TODO JS
-  // def addJSBreak(line: Int, enabled: Boolean = true) = addBreakJS(line, enabled)
-  // def rmJSBreak(opt: String) = rmBreakJS(opt)
-  // def toggleJSBreak(opt: String) = toggleBreakJS(opt)
-  // def getEnv(): String = getFullEnv().asJson.noSpaces
 
   // helpers
   def isValidLine(line: Int): Boolean = line != -1

### 2021-10-12 src/main/scala/kr/ac/kaist/jiset/web/WebServer.scala

@@ -28,7 +28,6 @@ object WebServer {
     val rootRoute = cors(settings) {
       concat(
         pathPrefix("spec")(SpecRoute()), // spec route
-        pathPrefix("state")(StateRoute()), // state route
         pathPrefix("exec")(ExecRoute()), // exec route
         pathPrefix("breakpoint")(BreakpointRoute()), // breakpoint route
       )

### 2021-10-12 src/main/scala/kr/ac/kaist/jiset/web/routes/BreakpointRoute.scala

@@ -11,7 +11,6 @@ import kr.ac.kaist.jiset.web
 
 // breakpoint router
 object BreakpointRoute extends FailFastCirceSupport {
-  // TODO JS
   // root router
   def apply(): Route = pathEnd {
     concat(

### 2021-10-12 src/main/scala/kr/ac/kaist/jiset/web/routes/ExecRoute.scala

@@ -30,7 +30,6 @@ object ExecRoute extends FailFastCirceSupport {
         path("run") {
           entity(as[RunParams]) {
             case RunParams(bps, compressed) => {
-              println(bps, compressed)
               web.setDebugger(bps, compressed)
               complete(HttpEntity(ContentTypes.`application/json`, "null"))
             }

### 2021-10-12 src/main/scala/kr/ac/kaist/jiset/web/routes/StateRoute.scala

@@ -1,24 +1,0 @@
-package kr.ac.kaist.jiset.web.routes
-
-import akka.http.scaladsl.model._
-import akka.http.scaladsl.server.Directives._
-import akka.http.scaladsl.server.Route
-
-// state router
-object StateRoute {
-  // // get state info
-  // getStackFrame (): string;
-  // getHeap (): string;
-  // getEnv (): string;
-  // getJsRange (): string;
-
-  // initialize state by input JS program
-  def init(): Route = ???
-
-  // root router
-  def apply(): Route = {
-    get {
-      complete(HttpEntity(ContentTypes.`text/html(UTF-8)`, "<h1>Say hello to akka-http</h1>"))
-    }
-  }
-}

### 2021-10-12 web/src/store/reducers/JS.ts

@@ -5,9 +5,6 @@ export enum JSActionType {
   EDIT = "JSAction/EDIT",
   CLEAR = "JSAction/CLEAR",
   UPDATE_RANGE = "JSAction/UPDATE_RANGE",
-  ADD_BREAK = "JSAction/ADD_BREAK",
-  RM_BREAK = "JSAction/RM_BREAK",
-  TOGGLE_BREAK = "JSAction/TOGGLE_BREAK",
 }
 export const edit = (code: string): JSAction => ({
   type: JSActionType.EDIT,
@@ -29,24 +26,6 @@ export const clearJS = (): JSAction => ({
   type: JSActionType.CLEAR,
 });
 
-export function addBreakJs(line: number): JSAction {
-  return {
-    type: JSActionType.ADD_BREAK,
-    line,
-  };
-}
-export function rmBreakJs(opt: string): JSAction {
-  return {
-    type: JSActionType.RM_BREAK,
-    opt,
-  };
-}
-export function toggleBreakJs(opt: string): JSAction {
-  return {
-    type: JSActionType.TOGGLE_BREAK,
-    opt,
-  };
-}
 export type JSAction =
   | {
       type: JSActionType.EDIT;
@@ -61,34 +40,18 @@ export type JSAction =
       lineTo: number;
       start: number;
       end: number;
-    }
-  | {
-      type: JSActionType.ADD_BREAK;
-      line: number;
-    }
-  | {
-      type: JSActionType.RM_BREAK;
-      opt: string;
-    }
-  | {
-      type: JSActionType.TOGGLE_BREAK;
-      opt: string;
     };
 
 // redux state
 type JSState = {
   code: string;
-  line: number;
   start: number;
   end: number;
-  breakpoints: { line: number; enable: boolean }[];
 };
 const initialState: JSState = {
   code: "var x = 1;\nvar y = 2;\nvar z = x + y;",
-  line: 0,
   start: -1,
   end: -1,
-  breakpoints: [],
 };
 
 // reducer
@@ -100,43 +63,13 @@ export default function reducer(state = initialState, action: JSAction) {
       });
     case JSActionType.CLEAR:
       return produce(state, (draft) => {
-        draft.line = 0;
         draft.start = -1;
         draft.end = -1;
       });
     case JSActionType.UPDATE_RANGE:
       return produce(state, (draft) => {
-        if (action.lineFrom === action.lineTo) {
-          draft.line = action.lineFrom;
-        }
[…]

### 2021-10-12 paper/pldi22/abstract.tex
Minor update in abstract

@@
   on specific semantics by automatically reducing semantics and filtering out
-  conformance tests with user-defined \textit{syntactic views}. In this paper,
-  we conduct several case studies for JEDIT to demonstrate the effectiveness of
-  live language design with syntactic views. Moreover, we experimentally show
-  that syntactic views successfully reduce the \inred{XX.X}\% of semantics and
-  filter out \inred{XX.X}\% of conformance tests on average using historically
-  representative syntactic views.
+  conformance tests using user-defined \textit{syntactic views}, abstract syntax
+  trees with abstracted nodes. In this paper, we conduct several case studies
+  for JEDIT to demonstrate the effectiveness of live language design with
+  syntactic views. Moreover, we experimentally show that syntactic views
+  successfully reduce the \inred{XX.X}\% of semantics and filter out
+  \inred{XX.X}\% of conformance tests on average using \inred{historically
+  representative syntactic views}.
 \end{abstract}

### 2021-10-12 paper/pldi22/abstract.tex
Writing intro

@@
   JavaScript is a widely-used programming language in various fields. Recently,
-  it rapidly evolved with a yearly release cadence and open development process
-  to quickly adapt users’ demands to the language. In this fast-evolving nature
-  of JavaScript, the need for \textit{language design assistants} has grown to
-  understand original or revised semantics in the revision process correctly.
-  Unfortunately, while several tools have been proposed as language design
-  assistants for JavaScript in academia and industry, they should be manually
-  updated to represent revised semantics every time. Besides, they lack the
-  additional information for better comprehension of language semantics,
-  including the relationship between specific semantics with conformance tests.
+  it has rapidly evolved with a yearly release cadence and open development
+  process to adapt users' demands to the language quickly. In this fast-evolving
+  nature of JavaScript, the need for \textit{language design assistants} has
+  grown to understand original or revised semantics correctly in the revision
+  process. Unfortunately, while several tools have been proposed as language
+  design assistants for JavaScript in academia and industry, they should be
+  manually updated to represent revised semantics every time. Besides, they lack
+  information about the relationship between specific semantics with conformance
+  tests.
 
   To alleviate this problem, we present $\tool$, a \textit{live} language design
-  assistant for JavaScript. It automatically synchronizes with a given language
-  specification and shows related conformance tests in the revision process.
-  Moreover, to better comprehend language semantics, we present a way to focus
-  on specific semantics by automatically reducing semantics and filtering out
-  conformance tests using user-defined \textit{syntactic views}, abstract syntax
-  trees with abstracted nodes. In this paper, we conduct several case studies
-  for JEDIT to demonstrate the effectiveness of live language design with
-  syntactic views. Moreover, we experimentally show that syntactic views
-  successfully reduce the \inred{XX.X}\% of semantics and filter out
-  \inred{XX.X}\% of conformance tests on average using \inred{historically
-  representative syntactic views}.
+  assistant for JavaScript, which automatically synchronizes with a given
+  language specification and shows related conformance tests in the revision
+  process. Moreover, to better comprehend language semantics, we present a way
+  to focus on specific semantics by automatically reducing semantics and
+  filtering out conformance tests using user-defined \textit{syntactic views},
+  abstract syntax trees with abstracted nodes. In this paper, we conduct several
+  case studies for $\tool$ with historical semantic updates to demonstrate the
+  effectiveness of live language design with syntactic views. Moreover, we
+  experimentally show that syntactic views successfully reduce the
+  \inred{XX.X}\% of semantics and filter out \inred{XX.X}\% of conformance tests
+  on average.
 \end{abstract}

### 2021-10-12 paper/pldi22/intro.tex
Writing intro

@@
 
-\begin{itemize}
-  \item \todo
-\end{itemize}
+In the beginning, JavaScript was a scripting language designed in a ten-day
+hack. However, it has become a de facto Web standard and eventually becomes one
+of the dominating programming languages in various fields. For example, Node.js
+introduced full-stack JavaScript by supporting server-side programming, and
+JavaScript has recently begun to be used even in embedded systems and
+microcontrollers for the Internet of Things (IoT). Furthermore, according to the
+annual report of GitHub\footnote{\url{https://octoverse.github.com/}},
+JavaScript has consistently been the most popular programming language based on
+the number of contributors to GitHub projects.
+
+Recently, JavaScript has rapidly evolved with a yearly release cadence and open
+development process. In 2015, The Ecma Technical Committee 39 (TC39) decided to
+annually release ECMAScript, the standard specification for JavaScript, with a
+massive update in ECMAScript 2015 (ES6, 2015)~\cite{es6}. Moreover, they
+published the specification as an open-source project in a GitHub repository to
+quickly adapt users' demands to the language.
+
+In this fast-evolving nature of JavaScript, the need for language design
+assistants (LDAs)~\cite{lda} has grown to understand original or revised
+semantics correctly in the revision process. Historically, researchers have
+proposed several language design assistants, such as LISA~\cite{lisa} and
+$\asfsdf$~\cite{asf-sdf, meta-env}, with semantics editors and the generators
+for language-based tools, such as parsers, compilers, interpreters, and so on.
+However, only small-size domain-specific languages are their targets due to
+their low expressive power. On the other hand, there are several attempts to
+develop language design assistants for JavaScript in the academy and industry.
+For example, in the academy, \citet{jsexplain} presented JSExplain, a JavaScript
+reference interpreter written in OCaml that closely follows ECMAScript and
+produces execution traces for debugging both ECMAScript and a given program. In
+the industry, Mozilla and several contributors introduced JavaScript
+interpreters written in pure JavaScript, such as Narcissus~\cite{narcissus} and
+engine262~\cite{engine262}, to aid the development of new features in
+JavaScript.
+
+However, existing language design assistants for JavaScript have two
+limitations: \textit{manual updates} and \textit{lack of connection with
+conformance tests}. First, all existing assistants are developed manually; thus,
+developers should manually update them for each frequent evolution of
+ECMAScript. This manual approach is a tedious, labor-intensive, and even
+error-prone process. Moreover, they lack information about the relationship
+between specific semantics with conformance tests. When a language designer
+desires to understand specific language semantics, one possible approach is to
+learn them from related conformance tests. Fortunately, TC39 provides Test262,
+an official conformance test suite for the latest version of ECMAScript.
+However, existing assistants do not utilize them to give a better comprehension
+of language semantics.
+
+In this paper, we present $\tool$, a \textit{live} language design assistant for
+JavaScript, which automatically synchronizes with a given language specification
+and shows related conformance tests in the revision process. To synchronize our
+tool with ECMAScript, we utilize another tool $\jiset$~\cite{jiset}, which
+automatically extracts a mechanized specification from a given version of
+ECMAScript. Note that a specification is mechanized if and only if it is both
+executable and formalized.
+\todo

### 2021-10-13 paper/pldi22/abstract.tex
Updated abstract

@@
   nature of JavaScript, the need for \textit{language design assistants} has
-  grown to understand original or revised semantics correctly in the revision
-  process. Unfortunately, while several tools have been proposed as language
-  design assistants for JavaScript in academia and industry, they should be
-  manually updated to represent revised semantics every time. Besides, they lack
-  information about the relationship between specific semantics with conformance
-  tests.
+  grown to understand target semantics and to synchronize three language
+  components: specifications, conformance tests, and language-based tools.
+  Unfortunately, while several language design assistants for JavaScript have
+  been proposed in academia and industry, they have two limitations: 1) no
+  functionalities to focus the target semantics and 2) manual or slow updates of
+  language components.
 
   To alleviate this problem, we present $\tool$, a \textit{live} language design
-  assistant for JavaScript, which automatically synchronizes with a given
-  language specification and shows related conformance tests in the revision
-  process. Moreover, to better comprehend language semantics, we present a way
-  to focus on specific semantics by automatically reducing semantics and
-  filtering out conformance tests using user-defined \textit{syntactic views},
-  abstract syntax trees with abstracted nodes. In this paper, we conduct several
-  case studies for $\tool$ with historical semantic updates to demonstrate the
-  effectiveness of live language design with syntactic views. Moreover, we
-  experimentally show that syntactic views successfully reduce the
-  \inred{XX.X}\% of semantics and filter out \inred{XX.X}\% of conformance tests
-  on average.
+  assistant for JavaScript with \textit{syntactic views}. First, our tool
+  provides a way to focus on target semantics using syntactic views, abstract
+  syntax trees with abstracted nodes. It automatically reduces semantics and
+  filters out conformance tests depending on user-defined syntactic views.
+  Second, $\tool$ automatically and quickly synchronizes language components in
+  the language design process. It detects which parts of semantics are revised
+  and partially updates specifications and conformance tests. For evaluation, we
+  demonstrate the effectiveness of $\tool$ with randomly selected syntactic
+  views and randomly modified semantics. With randomly selected syntactic views,
+  it reduces the \inred{XX.X}\% of semantics and filters out \inred{XX.X}\% of
+  conformance tests on average. With randomly modified semantics, it shortens
+  the time to synchronize three language components by \inred{XX.X}\%.
 \end{abstract}

### 2021-10-13 paper/pldi22/abstract.tex
Writing intro

@@
   nature of JavaScript, the need for \textit{language design assistants} has
-  grown to understand target semantics and to synchronize three language
+  grown to understand the current language semantics and to update it with new
+  language features in a tool-based approach. Unfortunately, existing tools have
+  two limitations related to the \textit{understanding} and \textit{update} of
+  language semantics. They 1) do not provide any automatic ways to focus on
+  target semantics and 2) manually or slowly synchronize three language
   components: specifications, conformance tests, and language-based tools.
-  Unfortunately, while several language design assistants for JavaScript have
-  been proposed in academia and industry, they have two limitations: 1) no
-  functionalities to focus the target semantics and 2) manual or slow updates of
-  language components.
 
@@
   assistant for JavaScript with \textit{syntactic views}. First, our tool
-  provides a way to focus on target semantics using syntactic views, abstract
-  syntax trees with abstracted nodes. It automatically reduces semantics and
-  filters out conformance tests depending on user-defined syntactic views.
-  Second, $\tool$ automatically and quickly synchronizes language components in
-  the language design process. It detects which parts of semantics are revised
-  and partially updates specifications and conformance tests. For evaluation, we
-  demonstrate the effectiveness of $\tool$ with randomly selected syntactic
-  views and randomly modified semantics. With randomly selected syntactic views,
-  it reduces the \inred{XX.X}\% of semantics and filters out \inred{XX.X}\% of
-  conformance tests on average. With randomly modified semantics, it shortens
-  the time to synchronize three language components by \inred{XX.X}\%.
+  provides a way to enhance the understanding of the target semantics using a
+  syntactic view, an abstract syntax tree containing abstracted nodes. It
+  automatically reduces semantics and filters out conformance tests depending on
+  user-defined syntactic views. Second, $\tool$ automatically and quickly
+  synchronizes language components in the language design process. It detects
+  which parts of semantics are revised and partially updates related parts in
+  specifications, conformance tests, and language-based tools. For evaluation,
+  we experimentally demonstrate the effectiveness of $\tool$. With randomly
+  selected syntactic views, our tool reduces the \inred{XX.X}\% of semantics and
+  filters out \inred{XX.X}\% of conformance tests on average. With randomly
+  modified semantics, it shortens the time to synchronize three language
+  components by \inred{XX.X}\% on average.
 \end{abstract}

### 2021-10-13 paper/pldi22/intro.tex
Writing intro

--- 2021-10-07 paper/pldi22/intro.tex
@@
 
+\todo Figure
+
+In the beginning, JavaScript was a scripting language designed in a ten-day
+hack. However, it has become a de facto Web standard and eventually becomes one
+of the dominating programming languages in various fields. For example,
+Node.js\footnote{https://nodejs.org/} introduced full-stack JavaScript by
+supporting server-side programming, and JavaScript has recently begun to be used
+even in embedded systems and microcontrollers for the Internet of
+Things\footnote{https://www.espruino.com/}. Furthermore, according to the annual
+report of GitHub\footnote{\url{https://octoverse.github.com/}}, JavaScript has
+consistently been the most popular programming language based on the number of
+contributors to GitHub projects.
+
+Recently, JavaScript has rapidly evolved with a yearly release cadence and open
+development process. In 2015, The Ecma Technical Committee 39 (TC39) decided to
+annually release ECMAScript, the standard specification for JavaScript, with a
+massive update in ECMAScript 6 (ES6, 2015)~\cite{es6}. Therefore, six more
+versions from ES7 to ES12 have already been released since 2015. Moreover, they
+published the specification as an open-source project in a GitHub repository to
+quickly adapt users' demands to the language.
+
+In this fast-evolving nature of JavaScript, the need for \textit{language design
+assistants}~\cite{lda} has grown to understand the current language semantics
+and to update it with new language features in a tool-based approach. In the
+early 2000s, \citet{lda} first presented the concept of language design
+assistants, and several researchers actualized it in tools such as
+LISA~\cite{lisa} and $\asfsdf$~\cite{asf-sdf, meta-env}. As described in
+Figure~\ref{fig:lda}, they bridge the gap between three language components:
+specifications, conformance tests, and language-based tools (e.g., parsers,
+interpreters, and compilers) by automatically generating them from the language
+semantics. However, only small-size domain-specific languages are their targets
+due to their low expressive power. On the other hand, several tools recently
+have been presented towards language design assistants for JavaScript in
+academia and industry. For example, JSExplain~\cite{jsexplain},
+Narcissus~\cite{narcissus}, and engine262~\cite{engine262} are reference
+interpreters that closely follow writing styles of ECMAScript, and they provide
+debugger-style support. $\jiset$~\cite{jiset} is a tool to compile ECMAScript to
+an executable specification. $\jest$~\cite{jest} is an extension of $\jiset$ to
+synthesize conformance tests, and $\jstar$~\cite{jstar} is another extension
+that performs type analysis for the specification.
+
+However, existing language design assistants for JavaScript have two limitations
+related to the \textit{understanding} and \textit{update} of language semantics.
+First, they do not provide any automatic ways to focus on target semantics for
+better comprehension. JavaScript language designers often want to understand
+specific language semantics in the revision process. However, existing tools do
+not provide mechanized methods; thus, finding related parts manually in the
+specification or conformance tests is tedious. For example, while reference
+interpreters and $\jstar$ visualize execution states and type information,
+respectively, in the specification, they cannot localize parts in the
+specification or conformance tests related to the target semantics. Second, they
+manually or slowly synchronize three language components. For example, there is
+no synchronization between reference interpreters with other language
+components: ECMAScript and conformance tests. While $\jiset$ and $\jest$
+automatically generate interpreters and conformance tests from ECMAScript, they
+are appropriate for live language design because of the long time to extract
+them from scratch for each semantics update.
+
+In this paper, we present $\tool$, a \textit{live} language design assistant for
+JavaScript with \textit{syntactic views}. Our tool extends $\jiset$ and $\jest$
+to automatically synchronize language components and visualize additional
+information for better understanding. To alleviate problems in existing tools,
+we present two different techniques for better understanding and fast update of
+language semantics, respectively. First, our tool provides a way to enhance the
+understanding of the target semantics using a syntactic view, an abstract syntax
+tree containing abstracted nodes. It automatically reduces semantics and filters
+out conformance tests depending on user-defined syntactic views. To reduce
+semantics in ECMAScript, we augment a partial evaluation~\cite{peval,
+peval-survey} with syntactic views. We utilize statistical information to find
+test programs related to a given syntactic view. Second, $\tool$ quickly
+synchronizes language components in the language design process. Unlike $\jiset$
+and $\jest$, our tool first detects which parts of semantics are revised and
+partially updates related parts in specifications, conformance tests, and
+language-based tools.
+
+Our contributions are as follows:
 \begin{itemize}
-  \item \todo
+  \item \todo language design assistant for JavaScript with automatic sync
+  \item \todo filtering with syntactic views
+  \item \todo fast update for live language design
 \end{itemize}

### 2021-10-14 paper/pldi22/abstract.tex
First draft of intro

@@
   grown to understand the current language semantics and to update it with new
-  language features in a tool-based approach. Unfortunately, existing tools have
+  language features in a tool-oriented approach. Unfortunately, existing tools have
   two limitations related to the \textit{understanding} and \textit{update} of

### 2021-10-14 paper/pldi22/intro.tex
First draft of intro

@@
 
-\todo Figure
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{img/lda.png}
+  \caption{A manual approach (left) and a tool-oriented approach with language
+    design assistants (right) with three language components: specifications,
+  conformance tests, and language-based tools.}
+  \label{fig:lda}
+  \vspace*{-.5em}
+\end{figure}
 
@@
 In this fast-evolving nature of JavaScript, the need for \textit{language design
-assistants}~\cite{lda} has grown to understand the current language semantics
-and to update it with new language features in a tool-based approach. In the
-early 2000s, \citet{lda} first presented the concept of language design
-assistants, and several researchers actualized it in tools such as
-LISA~\cite{lisa} and $\asfsdf$~\cite{asf-sdf, meta-env}. As described in
-Figure~\ref{fig:lda}, they bridge the gap between three language components:
-specifications, conformance tests, and language-based tools (e.g., parsers,
-interpreters, and compilers) by automatically generating them from the language
-semantics. However, only small-size domain-specific languages are their targets
-due to their low expressive power. On the other hand, several tools recently
-have been presented towards language design assistants for JavaScript in
-academia and industry. For example, JSExplain~\cite{jsexplain},
-Narcissus~\cite{narcissus}, and engine262~\cite{engine262} are reference
-interpreters that closely follow writing styles of ECMAScript, and they provide
-debugger-style support. $\jiset$~\cite{jiset} is a tool to compile ECMAScript to
-an executable specification. $\jest$~\cite{jest} is an extension of $\jiset$ to
-synthesize conformance tests, and $\jstar$~\cite{jstar} is another extension
-that performs type analysis for the specification.
+assistants} has grown to understand the current language semantics and to update
+it with new language features in a tool-based approach. In the early 2000s,
+\citet{lda} first presented the concept of language design assistants, and
+several researchers actualized it in tools such as LISA~\cite{lisa} and
+$\asfsdf$~\cite{asf-sdf, meta-env}. As described in Figure~\ref{fig:lda}, they
+bridge the gap between three language components: specifications, conformance
+tests, and language-based tools (e.g., parsers, interpreters, and compilers) by
+automatically generating them from the language semantics. Moreover, they
+provide query-based interactions to language designers for better understanding.
+However, only small-size domain-specific languages are their targets due to
+their low expressive power. On the other hand, several tools recently have been
+presented towards language design assistants for JavaScript in academia and
+industry. For example, JSExplain~\cite{jsexplain}, Narcissus~\cite{narcissus},
+and engine262~\cite{engine262} are reference interpreters that closely follow
+writing styles of ECMAScript, and they provide debugger-style support.
+$\jiset$~\cite{jiset} is a tool to compile ECMAScript to an executable
+specification. $\jest$~\cite{jest} is an extension of $\jiset$ to synthesize
+conformance tests, and $\jstar$~\cite{jstar} is another extension that performs
+type analysis for the specification.
 
-However, existing language design assistants for JavaScript have two limitations
-related to the \textit{understanding} and \textit{update} of language semantics.
-First, they do not provide any automatic ways to focus on target semantics for
-better comprehension. JavaScript language designers often want to understand
-specific language semantics in the revision process. However, existing tools do
-not provide mechanized methods; thus, finding related parts manually in the
-specification or conformance tests is tedious. For example, while reference
-interpreters and $\jstar$ visualize execution states and type information,
-respectively, in the specification, they cannot localize parts in the
-specification or conformance tests related to the target semantics. Second, they
-manually or slowly synchronize three language components. For example, there is
-no synchronization between reference interpreters with other language
+However, existing tools for JavaScript language design assistants have two
+limitations related to the \textit{understanding} and \textit{update} of
+language semantics. First, they do not provide any automatic ways to focus on
+target semantics for better comprehension. JavaScript language designers often
+want to understand specific language semantics in the revision process. However,
+existing tools do not provide mechanized methods; thus, finding related parts
+manually in the specification or conformance tests is tedious. For example,
+while reference interpreters and $\jstar$ visualize execution states and type
+information, respectively, in the specification, they cannot localize parts in
+the specification or conformance tests related to the target semantics. Second,
+they manually or slowly synchronize three language components. For example,
+there is no synchronization between reference interpreters with other language
 components: ECMAScript and conformance tests. While $\jiset$ and $\jest$
@@
 \begin{itemize}
-  \item \todo language design assistant for JavaScript with automatic sync
-  \item \todo filtering with syntactic views
-  \item \todo fast update for live language design
+  \item We present $\tool$, a live language design assistant for JavaScript with
+    syntactic views. It automatically synchronizes three language components:
+    specifications, conformance tests, and language-based tools.
+  \item We introduce a way to enhance the understanding of the target semantics
+    using user-defined \textit{syntactic views}, abstract syntax trees
+    containing abstract nodes. We experimentally demonstrate its effectiveness
+    with randomly selected syntactic views.
+  \item Towards \textit{live} language designs, we present an approach to detect
+    which parts of semantics are revised and partially update related parts in
+    language components. We also evaluate how it efficiently propagates
+    modification to language components with randomly modified semantics.
 \end{itemize}

### 2021-10-20 paper/pldi22/formal.tex
Added appendix for PE for IRES / More related work

\section{Partial Evaluation of $\ires$}\label{sec:formal}

\subsection{Abstract Syntax}

\[
  \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
    \text{Programs} & \progset &\ni& \prog &::=& \langle \func^*, \inst \rangle\\
    \text{Functions} & \funcset &\ni& \func &::=&
    \kwdef \; x \; \kwrl x^* \kwrr \; \kwcl [\lab: \inst]^* \kwcr\\
    \text{Variables} & \varset &\ni& x\\
    \text{Labels} & \labset &\ni& \lab\\
    \text{Instructions} & \instset &\ni& \inst &::=&
    x = \pval \mid
    x = \op \kwrl x^* \kwrr \mid
    x = x \kwrl x^* \kwrr\\
    &&&&\mid&
    x = \kwcl \kwcr \mid
    x = x \kwsl x \kwsr \mid
    x \kwsl x \kwsr = x\\
    &&&&\mid&
    \kwif \; x \; \lab \; \lab \mid
    \kwret \; x\\
  \end{array}
\]

A program $\prog \in \progset$ is a pair of functions and a top-level
instruction.  A function $\func \in \funcset$ is defined with its name,
parameters, and body instructions with labels $\labset$.  An instruction $\inst
\in \instset$ is
a primitive value assignment $x = \pval$,
an operation between values $x = \op \kwrl x^* \kwrr$,
a function call $x = x \kwrl x^* \kwrr$,
a record allocation $x = \kwcl \kwcr$,
a field access $x = x \kwsl x \kwsr$,
a field assignment $x \kwsl x \kwsr = x$,
a conditional branch $\kwif \; x \; \lab \; \lab$,
or a return instruction $\kwret \; x$.

\subsection{States}

\[
  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
    \text{States} & \st &\in& \stset &=&
    \heapset \times \ctxtset\\
    \text{Heaps} & \heap &\in& \heapset &=&
    \addrset \finmap \recset\\
    \text{Contexts} & \ctxt &\in& \ctxtset &=&
    \labset \times \envset \times \ctxtset^?\\
    \text{Environments} & \env &\in& \envset &=&
    \varset \finmap \valset\\
    \text{Values} & \val &\in& \valset &=&
    \pvalset \uplus \addrset \uplus \treeset \uplus \funcset\\
    \text{Primive Values} & \pval &\in& \pvalset &=&
    \strset \uplus \cdots\\
    \text{JavaScript ASTs} & \tree &\in& \treeset\\
    \text{Records} & \rec &\in& \recset &=&
    \strset \finmap \valset\\
  \end{array}
\]

States $\stset$ consists of heaps $\heapset$ and contexts $\ctxtset$.  A heap
$\heap \in \heapset$ is a finite mapping from addresses to records.  Each record
allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
\addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
a triple of 1) a program point, 2) an environment, and 3) an optional calling
context.  An environment $\env \in \envset$ is a finite mapping from variables
to values. A value $\val \in \valset$ is a primitive value $\pval \in \pvalset$
(e.g., a string value $\str \in \strset$), an address $\addr \in \addrset$, an
JavaScript AST $\tree \in \treeset$, or a function $f \in \funcset$.  A record
$\rec \in \recset$ is a finite mappings from strings to values.

### 2021-10-20 paper/pldi22/formal.tex
Outline for formalization of PE

@@
 
-\subsection{Abstract Syntax}
+We first define $\ires$ with its abstract syntax, states, and concrete
+semantics.  Then, we define syntactic views as JavaScript ASTs with abstract
+nodes. Finally, we define the partial evaluation as a transformation of $\ires$
+to specialize $\ires$ functions.  To prove the semantics preservation of the
+partial evaluation, we introduce an observational semantics of $\ires$ and prove
+that each specialized $\ires$ functions has equivalent observational semantics
+of the corresponding original one.
+
+\subsection{$\ires$: Intermediate Representations for ECMAScript}
+
+First, we define abstract syntax, states, and concrete semantics of $\ires$.
+
+\subsubsection{Abstract Syntax}
 
@@
   \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
-    \text{Programs} & \progset &\ni& \prog &::=& \langle \func^*, \inst \rangle\\
     \text{Functions} & \funcset &\ni& \func &::=&
@@
 
-A program $\prog \in \progset$ is a pair of functions and a top-level
-instruction.  A function $\func \in \funcset$ is defined with its name,
-parameters, and body instructions with labels $\labset$.  An instruction $\inst
-\in \instset$ is
+A function $\func \in \funcset$ is defined with its name, parameters, and body
+instructions with labels $\labset$.  An instruction $\inst \in \instset$ is
 a primitive value assignment $x = \pval$,
@@
 
-\subsection{States}
+\subsubsection{States}
 
@@
     \text{States} & \st &\in& \stset &=&
-    \heapset \times \ctxtset\\
+    \heapset \times \envset \times \ctxtset\\
     \text{Heaps} & \heap &\in& \heapset &=&
@@
 
-States $\stset$ consists of heaps $\heapset$ and contexts $\ctxtset$.  A heap
-$\heap \in \heapset$ is a finite mapping from addresses to records.  Each record
-allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
-\addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
-a triple of 1) a program point, 2) an environment, and 3) an optional calling
-context.  An environment $\env \in \envset$ is a finite mapping from variables
-to values. A value $\val \in \valset$ is a primitive value $\pval \in \pvalset$
-(e.g., a string value $\str \in \strset$), an address $\addr \in \addrset$, an
-JavaScript AST $\tree \in \treeset$, or a function $f \in \funcset$.  A record
-$\rec \in \recset$ is a finite mappings from strings to values.
+States $\stset$ consist of heaps $\heapset$, global environments $\envset$, and
+contexts $\ctxtset$.  A heap $\heap \in \heapset$ is a finite mapping from
+addresses to records.  Each record allocation instruction $x = \kwcl \kwcr$
+creates a unique address $\addr \in \addrset$ different from existing addresses.
+A context $\ctxt \in \ctxtset$ is a triple of a label, a local environment, and
+an optional calling context.  An environment $\env \in \envset$ is a finite
+mapping from variables to values. A value $\val \in \valset$ is a primitive
+value $\pval \in \pvalset$ (e.g., a string value $\str \in \strset$), an address
+$\addr \in \addrset$, a JavaScript AST $\tree \in \treeset$, or a function $f
+\in \funcset$.  A record $\rec \in \recset$ is a finite mappings from strings to
+values.
+
+\subsubsection{Concrete Semantics of Instructions}
+
+\[
+  \framebox{$\sem{\inst}: \stset \rightarrow \stset$}
+\]
+
+\todo
+
+\subsubsection{Concrete Semantics of Functions}
+
+\[
+  \framebox{$\sem{\func}: \stset \times \valset^* \rightarrow \stset$}
+\]
+
+\todo
+
+\subsection{Syntatic Views}
+
+\todo
+
+\subsection{Partial Evaluation}
+
+\todo
+
+\subsection{Observational Semantics}
+
+\todo
+
+\subsection{Proof of Semantics Preservation}
+
+\todo

### 2021-10-21 paper/pldi22/formal.tex
More formalization in appendix

@@
-\section{Partial Evaluation of $\ires$}\label{sec:formal}
+\section{$\ires$ Specialization}\label{sec:formal}
 
@@
 semantics.  Then, we define syntactic views as JavaScript ASTs with abstract
-nodes. Finally, we define the partial evaluation as a transformation of $\ires$
-to specialize $\ires$ functions.  To prove the semantics preservation of the
-partial evaluation, we introduce an observational semantics of $\ires$ and prove
+nodes. Finally, we define the specialization of $\ires$ as a transformation to
+specialize $\ires$ functions.  To prove the semantics preservation of the
+specialization, we introduce an observational semantics of $\ires$ and prove
 that each specialized $\ires$ functions has equivalent observational semantics
@@
     \kwdef \; x \; \kwrl x^* \kwrr \; \kwcl [\lab: \inst]^* \kwcr\\
+
     \text{Variables} & \varset &\ni& x\\
+
     \text{Labels} & \labset &\ni& \lab\\
+
     \text{Instructions} & \instset &\ni& \inst &::=&
-    x = \pval \mid
-    x = \op \kwrl x^* \kwrr \mid
-    x = x \kwrl x^* \kwrr\\
-    &&&&\mid&
-    x = \kwcl \kwcr \mid
-    x = x \kwsl x \kwsr \mid
-    x \kwsl x \kwsr = x\\
-    &&&&\mid&
-    \kwif \; x \; \lab \; \lab \mid
-    \kwret \; x\\
+    \refer = \expr \mid
+    x = \expr \kwrl \expr^* \kwrr \mid
+    \kwif \; \expr \; \lab \; \lab \mid
+    \kwret \; \expr\\
+
+    \text{Expressions} & \exprset &\ni& \expr &::=&
+    \pval \mid
+    \op \kwrl \expr^* \kwrr \mid
+    \kwcl \kwcr \mid
+    \refer\\
+
+    \text{References} & \referset &\ni& \refer &::=&
+    x \mid \refer \kwsl \expr \kwsr\\
   \end{array}
 \]
+
+\todo update explanation
 
@@
 a function call $x = x \kwrl x^* \kwrr$,
-a record allocation $x = \kwcl \kwcr$,
+a object allocation $x = \kwcl \kwcr$,
 a field access $x = x \kwsl x \kwsr$,
@@
     \text{States} & \st &\in& \stset &=&
-    \heapset \times \envset \times \ctxtset\\
+    \labset \times \ctxtset^* \times \heapset \times \envset\\
+
+    \text{Calling Contexts} & \ctxt &\in& \ctxtset &=&
+    \labset \times \envset \times \varset\\
+
     \text{Heaps} & \heap &\in& \heapset &=&
-    \addrset \finmap \recset\\
-    \text{Contexts} & \ctxt &\in& \ctxtset &=&
-    \labset \times \envset \times \ctxtset^?\\
+    \addrset \finmap \objset\\
+
     \text{Environments} & \env &\in& \envset &=&
     \varset \finmap \valset\\
+
     \text{Values} & \val &\in& \valset &=&
     \pvalset \uplus \addrset \uplus \treeset \uplus \funcset\\
+
     \text{Primive Values} & \pval &\in& \pvalset &=&
     \strset \uplus \cdots\\
+
     \text{JavaScript ASTs} & \tree &\in& \treeset\\
-    \text{Records} & \rec &\in& \recset &=&
+
+    \text{Objects} & \obj &\in& \objset &=&
     \strset \finmap \valset\\
@@
 
-States $\stset$ consist of heaps $\heapset$, global environments $\envset$, and
-contexts $\ctxtset$.  A heap $\heap \in \heapset$ is a finite mapping from
-addresses to records.  Each record allocation instruction $x = \kwcl \kwcr$
-creates a unique address $\addr \in \addrset$ different from existing addresses.
-A context $\ctxt \in \ctxtset$ is a triple of a label, a local environment, and
-an optional calling context.  An environment $\env \in \envset$ is a finite
-mapping from variables to values. A value $\val \in \valset$ is a primitive
-value $\pval \in \pvalset$ (e.g., a string value $\str \in \strset$), an address
-$\addr \in \addrset$, a JavaScript AST $\tree \in \treeset$, or a function $f
-\in \funcset$.  A record $\rec \in \recset$ is a finite mappings from strings to
-values.
+States $\stset$ consist of heaps $\heapset$ and contexts $\ctxtset$.  A heap
+$\heap \in \heapset$ is a finite mapping from addresses to objects.  Each object
+allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
+\addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
+a triple of a label, a environment, and an optional calling context $\ctxtopt
+\in \ctxtoptset = \ctxtset \uplus \{ \bot \}$.  An environment $\env \in
+\envset$ is a finite mapping from variables to values. A value $\val \in
+\valset$ is a primitive value $\pval \in \pvalset$ (e.g., a string value $\str
+\in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree \in
+\treeset$, or a function $f \in \funcset$.  A object $\obj \in \objset$ is a
+finite mappings from strings to values.
+
+\subsubsection{Concrete Semantics of Functions}
+
+\[
+  \framebox{$\sem{\func}: \stset \times \valset^* \rightarrow \stset \times
+  \valset$}
+\]
+
+\todo
 
@@
 \todo
+% \[
+%   \begin{array}{l}
+%     \sem{x = \pval}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad (\heap, (\lab, \env[x \mapsto \pval], \ctxtopt)) \\
+%     \\
+% 
+%     \sem{x = \op \kwrl x_1, \cdots, x_n \kwrr}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad (\heap, (\lab, \env[x \mapsto \sem{\op}(x_1, \cdots, x_n)], \ctxtopt)) \\
+%     \\
+% 
+%     \sem{x = x \kwrl x^* \kwrr}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad \todo \\
+%     \\
+% 
+%     \sem{x = \kwcl \kwcr}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad \todo \\
+%     \\
+% 
+%     \sem{x = x \kwsl x \kwsr}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad \todo \\
+%     \\
+% 
+%     \sem{x \kwsl x \kwsr = x}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad \todo \\
+%     \\
+% 
+%     \sem{\kwif \; x \; \lab \; \lab}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad \todo \\
+%     \\
+% 
+%     \sem{\kwret \; x}(\heap, (\lab, \env, \ctxtopt)) =\\
+%     \qquad \todo \\
+% 
+%   \end{array}
+% \]
 
-\subsubsection{Concrete Semantics of Functions}
+\subsubsection{Concrete Semantics of Expressions}
 
 \[
-  \framebox{$\sem{\func}: \stset \times \valset^* \rightarrow \stset$}
+  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
 \]
@@
 
-\subsection{Syntatic Views}
+\subsubsection{Concrete Semantics of References}
+
+\[
+  \framebox{$\sem{\refer}: \stset \rightarrow \stset \times \valset$}
+\]
 
@@
 
-\subsection{Partial Evaluation}
+\subsection{Specialization}
+
+\todo
+
+\subsubsection{Constant Propagation Transformation}
+
+\todo
+
+\subsubsection{Cleanup Transformation}
 
@@
 \todo
+
+\section{Syntatic Views}
+
+\todo

### 2021-10-21 paper/pldi22/formal.tex
More formalization in appendix

@@
-\section{$\ires$ Specialization}\label{sec:formal}
+\section{JavaScript Semantics Specialization with Syntactic Views}\label{sec:formal}
 
-We first define $\ires$ with its abstract syntax, states, and concrete
-semantics.  Then, we define syntactic views as JavaScript ASTs with abstract
-nodes. Finally, we define the specialization of $\ires$ as a transformation to
-specialize $\ires$ functions.  To prove the semantics preservation of the
-specialization, we introduce an observational semantics of $\ires$ and prove
-that each specialized $\ires$ functions has equivalent observational semantics
-of the corresponding original one.
+We first define $\ires$ as a specification language to describe JavaScript
+semantics.  Then, we define a function specialization in $\ires$ with two
+different source-to-source transformations: a constant propagation
+transformation and a redundancy elimination transformation.  We prove the
+semantics preservation of function specialization under an observational
+semantics.  Finally, we define the JavaScript semantics specialization with
+syntactic views using function specialization.
 
@@
 
-First, we define abstract syntax, states, and concrete semantics of $\ires$.
+We first introduce $\ires$, an \textbf{I}ntermediate \textbf{R}epresentations
+for \textbf{E}CMA\textbf{S}cript, as a specification language for JavaScript to
+describe JavaScript semantics. We define its abstract syntax, states, and
+concrete semantics in the remainder of this section.
 
@@
 
-States $\stset$ consist of heaps $\heapset$ and contexts $\ctxtset$.  A heap
-$\heap \in \heapset$ is a finite mapping from addresses to objects.  Each object
-allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
-\addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
-a triple of a label, a environment, and an optional calling context $\ctxtopt
-\in \ctxtoptset = \ctxtset \uplus \{ \bot \}$.  An environment $\env \in
-\envset$ is a finite mapping from variables to values. A value $\val \in
-\valset$ is a primitive value $\pval \in \pvalset$ (e.g., a string value $\str
-\in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree \in
-\treeset$, or a function $f \in \funcset$.  A object $\obj \in \objset$ is a
-finite mappings from strings to values.
+\todo
+% States $\stset$ consist of heaps $\heapset$ and contexts $\ctxtset$.  A heap
+% $\heap \in \heapset$ is a finite mapping from addresses to objects.  Each object
+% allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
+% \addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
+% a triple of a label, a environment, and an optional calling context $\ctxtopt
+% \in \ctxtoptset = \ctxtset \uplus \{ \bot \}$.  An environment $\env \in
+% \envset$ is a finite mapping from variables to values. A value $\val \in
+% \valset$ is a primitive value $\pval \in \pvalset$ (e.g., a string value $\str
+% \in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree \in
+% \treeset$, or a function $f \in \funcset$.  A object $\obj \in \objset$ is a
+% finite mappings from strings to values.
 
@@
 
-\subsection{Specialization}
+\subsection{Function Specialization}
+
+\todo
+
+A source-to-source transformation is defined with parameteric restrictions
+$\restrictset$ and its concretization $\gamma: \restrictset \rightarrow
+\powerset{\stset \times \valset^*}$.
+\[
+  \framebox{$\transf: \funcset \times \restrictset \rightarrow \funcset$}
+\]
 
@@
 \subsubsection{Constant Propagation Transformation}
+\[
+  \begin{array}{lr@{~}c@{~}l}
+    \text{Restrictions} & (\valoptset)^* &=& (\valset \uplus \{ \top \})^*\\
+    \text{Concretization} & \gamma(\valopt_1, \cdots, \valopt_n) &=& \\
+    \multicolumn{4}{l}{\qquad \{
+      (\st, (\val_1, \cdots, \val_n)) \mid
+      \val_i \in \left\{
+        \begin{array}{ll}
+          \valset & \text{if} \; \valopt_i = \top\\
+          \{ \valopt_i \} & \text{otherwise}\\
+        \end{array}
+      \right.
+    \}}\\
+  \end{array}
+\]
+
+In the constant propagation transformation, restrictions $(\valoptset)^*$ are
+sequences of static values $\valset$ or a dynamic value $\top$.
+
+\[
+  \framebox{$\transcpe: \exprset \times \envset \rightarrow \exprset$}
+\]
 
@@
 
-\subsubsection{Cleanup Transformation}
+\[
+  \framebox{$\transcpi: \instset \times \envset \rightarrow \instset \times
+  \envset$}
+\]
 
@@
 
-\subsection{Observational Semantics}
+\[
+  \framebox{$\transcpf: \funcset \times (\valoptset)^* \rightarrow \funcset$}
+\]
+
+\todo
+
+\subsubsection{Redundancy Elimination Transformation}
+
+\todo
+
+\[
+  \begin{array}{lr@{~}c@{~}l}
+    \text{Restrictions} &\{ \top \}\\
+    \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
+  \end{array}
+\]
+
+The redundancy elimination transformation is defined without any restriction,
+which means its restriction set consists of a single element $\top$
+representing all possible cases.  Therefore, we omit the restriction part in
+this transformation for the brevity.
+
+\[
+  \framebox{$\transref: \funcset \rightarrow \funcset$}
+\]
 
@@
 
-\section{Syntatic Views}
+\subsubsection{Observational Semantics}
 
 \todo
+
+\subsection{JavaScript Semantics Specialization}
+
+\todo
+
+\subsubsection{Syntatic Views}
+
+\todo
+
+\subsubsection{Specialization with Syntatic Views}
+
+\todo

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/cfg/Stringifier.scala
Refactor IRLogger & test262 test script

@@ -22,7 +22,6 @@ class Stringifier(
     case func: Function => FunctionApp(app, func)
     case origin: Origin => OriginApp(app, origin)
     case node: Node => NodeApp(app, node)
-    case comp: VisitRecorder => VisitRecorderApp(app, comp)
   }
 
   // CFGs
@@ -48,10 +47,5 @@ class Stringifier(
       case Exit(_) =>
     }
     app
-  }
-
-  // visit recorder
-  implicit lazy val VisitRecorderApp: App[VisitRecorder] = (app, vr) => {
-    app >> vr.fileMap
   }
 }

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/cfg/VisitRecorder.scala

@@ -1,75 +1,0 @@
-package kr.ac.kaist.jiset.cfg
-
-import kr.ac.kaist.jiset.{ LINE_SEP }
-import kr.ac.kaist.jiset.cfg._
-import kr.ac.kaist.jiset.js._
-import kr.ac.kaist.jiset.util.JvmUseful._
-import scala.collection.mutable.{ Map => MMap }
-
-// recorder for visited CFG nodes
-case class VisitRecorder(
-  fileMap: VisitRecorder.FileMap
-) extends CFGElem {
-  import VisitRecorder._
-
-  // Data for CSV
-  def funcData: List[String] = {
-    val fmap: MMap[Function, Set[String]] = MMap()
-    for {
-      (file, nodeMap) <- fileMap
-      (node, (func, _)) <- nodeMap
-    } {
-      val fileSet = fmap.getOrElseUpdate(func, Set())
-      fmap += func -> (fileSet + file)
-    }
-    (for {
-      (func, fileset) <- fmap
-    } yield List(func, fileset.size).mkString(",")).toList
-  }
-
-  def nodeData: List[String] = {
-    val nmap: MMap[Node, Set[String]] = MMap()
-    for {
-      (file, nodeMap) <- fileMap
-      (node, _) <- nodeMap
-    } {
-      val fileSet = nmap.getOrElseUpdate(node, Set())
-      nmap += node -> (fileSet + file)
-    }
-    (for {
-      (node, fileset) <- nmap
-    } yield List(node, fileset.size).mkString(",")).toList
-  }
-
-  def dumpCsv(dirname: String): Unit = {
-    dumpFile(
-      "Visited-nodes-func.csv",
-      (List("Func", "# File").mkString(",") :: funcData).mkString(LINE_SEP),
-      s"$dirname/visited-nodes-func.csv"
-    )
-    dumpFile(
-      "Visited-nodes-node.csv",
-      (List("Node", "# File").mkString(",") :: nodeData).mkString(LINE_SEP),
-      s"$dirname/visited-nodes-node.csv"
-    )
-  }
-}
-object VisitRecorder {
-  // internal types
-  type FileMap = Map[String, NodeMap]
-  type NodeMap = Map[Node, (Function, Int)]
-
-  // load VisitRecorder
-  def apply(dirname: String, passfile: String): VisitRecorder = {
-    import cfg.jsonProtocol._
-    val passTests = readFile(passfile).split(LINE_SEP).toSet
-    VisitRecorder(
[…]

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/editor/JSFilter.scala

@@ -1,10 +1,13 @@
 package kr.ac.kaist.jiset.editor
 
-import kr.ac.kaist.jiset.{ VISITED_LOG_DIR, BASE_DIR }
+import kr.ac.kaist.jiset.BASE_DIR
 import kr.ac.kaist.jiset.cfg._
+import kr.ac.kaist.jiset.ir.Logger
+import kr.ac.kaist.jiset.ir.JsonProtocol._
 import kr.ac.kaist.jiset.js._
 import kr.ac.kaist.jiset.js.ast._
 import kr.ac.kaist.jiset.util.JvmUseful._
+import kr.ac.kaist.jiset.util.{ UIdGen, UId }
 import scala.math.log10
 
 // filtering JavaScript programs using a given syntactic view
@@ -12,38 +15,45 @@ object JSFilter {
   def apply(ast: AST, view: SyntacticView): Boolean =
     ast.contains(view.ast)
 
-  // test with trace
-  case class Test(name: String, trace: Map[Node, Int]) {
+  // test id generator
+  val tidGen: UIdGen[Test] = new UIdGen
+
+  // test object
+  case class Test(
+    uidGen: UIdGen[Test],
+    result: Logger.Result
+  ) extends UId[Test] {
+    def name: String = result.name
+    def touched: Map[Node, Int] = result.touched
+
+    // stats
     def max: Int = ???
-    def sum: Int = trace.values.sum
+    def sum: Int = touched.values.sum
 
     // term frequency(tf)
-    def tf_binary(node: Node) = if (trace.contains(node)) 1 else 0
-    def tf_raw(node: Node) = trace.getOrElse(node, 0)
-    def tf_basic(node: Node) = tf_raw(node) / sum
-    def tf_log(node: Node) = log10(1 + tf_raw(node))
-    def tf_augmented(node: Node, k: Double = 0.5) = k + k * tf_raw(node) / max
+    def tf_binary(n: Node) = if (touched.contains(n)) 1 else 0
+    def tf_raw(n: Node) = touched.getOrElse(n, 0)
+    def tf_basic(n: Node) = tf_raw(n) / sum
+    def tf_log(n: Node) = log10(1 + tf_raw(n))
+    def tf_augmented(n: Node, k: Double = 0.5) = k + k * tf_raw(n) / max
   }
 
   object Test {
     // NOTE: spec should be loaded before
-    def apply(path: String): Test = {
-      import cfg.jsonProtocol._
[…]

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/ir/Debugger.scala

@@ -98,7 +98,7 @@ trait Debugger {
   final def continue: StepResult = stepUntil { true }
 
   // breakpoints
-  val breakpoints = ArrayBuffer[(InterpHook, Breakpoint)]()
+  val breakpoints = ArrayBuffer[(Interp.Hook, Breakpoint)]()
 
   // check if current step is in break
   final def isBreak: Boolean = breakpoints.foldLeft(false) {
@@ -107,7 +107,7 @@ trait Debugger {
 
   // get breakpoint by index
   private def getBreakIdx(
-    bpList: ArrayBuffer[(InterpHook, Breakpoint)],
+    bpList: ArrayBuffer[(Interp.Hook, Breakpoint)],
     idx: String
   ): Int =
     optional(idx.toInt) match {

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/ir/IRLogger.scala

@@ -1,81 +1,0 @@
-package kr.ac.kaist.jiset.ir
-
-import kr.ac.kaist.jiset._
-import kr.ac.kaist.jiset.cfg
-import kr.ac.kaist.jiset.cfg._
-import kr.ac.kaist.jiset.js._
-import kr.ac.kaist.jiset.util.JvmUseful._
-import kr.ac.kaist.jiset.util.Useful._
-import kr.ac.kaist.jiset.util.Appender._
-
-object IRLogger {
-  val cfgStringifer = CFGElem.getStringifier(true, false, false)
-
-  // iteration counter
-  private var _iterSum: Long = 0L
-  private var _iterMap: Map[String, Int] = Map()
-  def iterAvg: Double = iterSum.toDouble / iterMap.size
-  def iterSum: Long = _iterSum
-  def iterMap: Map[String, Int] = _iterMap
-  def recordIter(fnameOpt: Option[String], iter: Int): Unit = {
-    fnameOpt.map(fname => {
-      _iterMap += fname -> iter
-      _iterSum += iter
-    })
-  }
-  def iterMapString: String = (for {
-    (fname, iter) <- iterMap
-  } yield s"$fname: $iter").mkString(LINE_SEP)
-  def dumpIterMap(dirname: String): Unit =
-    dumpFile(iterMapString, s"$dirname/iters")
-
-  // callstack depth
-  private var _depthMap: Map[String, Int] = Map()
-  def depthSum: Int = _depthMap.toList.map(_._2).sum
-  def depthAvg: Double = depthSum.toDouble / _depthMap.size
-  def recordCallDepth(fnameOpt: Option[String], depth: Int): Unit = {
-    fnameOpt.map(fname => {
-      _depthMap += fname -> depth
-    })
-  }
-  def dumpDepthMap(dirname: String): Unit = {
-    val depthMapStr = (for {
-      (fname, depth) <- _depthMap
-    } yield s"$fname: $depth").mkString(LINE_SEP)
-    dumpFile(depthMapStr, s"$dirname/call-depths")
-  }
-
-  // summary
-  def summaryString: String = (
-    f"""- iteration:
-       |  - min   : ${iterMap.toList.map(_._2).min}
-       |  - max   : ${iterMap.toList.map(_._2).max}
-       |  - total : $iterSum
-       |  - avg.  : $iterAvg%.2f
-       |- callstack depth:
[…]

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/ir/Interp.scala

@@ -8,7 +8,7 @@ import kr.ac.kaist.jiset.parser.ESValueParser
 import kr.ac.kaist.jiset.spec.algorithm._
 import kr.ac.kaist.jiset.util.Useful._
 import kr.ac.kaist.jiset.util._
-import kr.ac.kaist.jiset.{ TEST_MODE, LOG, DEBUG, TIMEOUT, VISITED_LOG_DIR }
+import kr.ac.kaist.jiset.{ TEST_MODE, LOG, DEBUG, TIMEOUT }
 import scala.annotation.tailrec
 import scala.collection.mutable.{ Map => MMap }
 
@@ -26,33 +26,9 @@ class Interp(
   // set start time of interpreter
   val startTime: Long = System.currentTimeMillis
 
-  // file name
-  val fname = st.fnameOpt.getOrElse("UNKNOWN")
-
-  // visited nodes
-  private var nodeMap: Map[Node, (Function, Int)] = Map()
-  def nodeRecord(func: Function, node: Node) = {
-    val count = nodeMap.getOrElse(node, (func, 0))._2
-    nodeMap += (node -> (func, count + 1))
-  }
-  def visitedNode: (String, Map[Node, (Function, Int)]) =
-    (convert262(fname), nodeMap)
-  def dumpVisitJson() = {
-    import JvmUseful._, cfg.jsonProtocol._
-    val testName = convert262(fname).replace("/", ".")
-    dumpJson(visitedNode, s"$VISITED_LOG_DIR/$testName.json", true)
-  }
-
   // the number of instructions
   def getIter: Int = iter
   private var iter: Int = 0
-
-  // maximum callstack size
-  private var maxDepth: Int = 1
-  private def updateCallDepth() = {
-    val d = st.ctxtStack.size + 1
-    if (d > maxDepth) maxDepth = d
-  }
 
   // iteration period for check
   val CHECK_PERIOD = 10000
@@ -82,11 +58,8 @@ class Interp(
   final def step: Boolean = nextTarget match {
     case Terminate =>
       // stop evaluation
-      if (LOG) {
-        IRLogger.recordIter(st.fnameOpt, iter)
-        IRLogger.recordCallDepth(st.fnameOpt, maxDepth)
-        dumpVisitJson()
-      }
+      if (useHook) notify(Event.Terminate)
+
       false
     case ReturnUndef =>
       // do return
@@ -109,6 +82,9 @@ class Interp(
         case _ =>
[…]

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/ir/JsonProtocol.scala

@@ -3,12 +3,13 @@ package kr.ac.kaist.jiset.ir
 import kr.ac.kaist.jiset.ir.Parser._
 import kr.ac.kaist.jiset.util.BasicJsonProtocol
 import kr.ac.kaist.jiset.util.Useful.stringify
+import kr.ac.kaist.jiset.js._
 import io.circe._, io.circe.generic.semiauto._, io.circe.generic.auto._
 import io.circe.syntax._
 
 object JsonProtocol extends BasicJsonProtocol {
   val stringifier = new Stringifier(line = true, asite = true)
-  import stringifier._
+  import stringifier._, cfgJsonProtocol._
 
   implicit val (tyDecoder: Decoder[Ty], tyEncoder: Encoder[Ty]) =
     stringCodec[Ty](Ty.apply, stringify)
@@ -18,6 +19,10 @@ object JsonProtocol extends BasicJsonProtocol {
     stringCodec[Expr](Expr.apply, stringify)
   implicit val (instDecoder: Decoder[Inst], instEncoder: Encoder[Inst]) =
     stringCodec[Inst](Inst.apply, stringify)
+
+  // interp result
+  implicit lazy val LoggerResultDecoder: Decoder[Logger.Result] = deriveDecoder
+  implicit lazy val LoggerResultEncoder: Encoder[Logger.Result] = deriveEncoder
 
   // debugger breakpoint
   implicit lazy val AlgoBreakpointDecoder: Decoder[AlgoBreakpoint] = deriveDecoder

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/ir/Logger.scala

@@ -1,0 +1,81 @@
+package kr.ac.kaist.jiset.ir
+
+import kr.ac.kaist.jiset.LINE_SEP
+import kr.ac.kaist.jiset.cfg._
+import kr.ac.kaist.jiset.ir.JsonProtocol._
+import kr.ac.kaist.jiset.js._
+import kr.ac.kaist.jiset.util.JvmUseful._
+import scala.collection.mutable.{ Map => MMap }
+
+object Logger {
+  // result for each interp
+  case class MResult(
+    name: String,
+    var maxDepth: Int = 1,
+    touched: MMap[Node, Int] = MMap()
+  ) {
+    // update maximum call depth
+    def updateDepth(st: State): Unit = {
+      val d = st.ctxtStack.size + 1
+      if (d > maxDepth) maxDepth = d
+    }
+
+    // update touched
+    def updateTouched(st: State): Unit = {
+      val cursor = st.context.cursorOpt.get
+      cursor match {
+        case NodeCursor(node) =>
+          val count = touched.getOrElse(node, 0) + 1
+          touched += (node -> count)
+        case _ =>
+      }
+    }
+
+    // convert to fixed result object
+    def into(iter: Int): Result =
+      Result(name, iter, maxDepth, Map(touched.toSeq: _*))
+  }
+
+  // result counter
+  private var rid = 0
+  private def incRid(): Int = { val prev = rid; rid += 1; prev }
+
+  // interp result
+  case class Result(
+    name: String,
+    iter: Int,
+    maxDepth: Int,
+    touched: Map[Node, Int]
+  )
+
+  // log IR interp
+  def log(interp: Interp): Unit = {
+    // set mutable result object
+    val name = interp.st.fnameOpt.getOrElse("UNKNOWN")
+    val mresult = MResult(name)
+
+    // subscribe call, cont and update depth
+    interp.subscribe(
+      List(Interp.Event.Call, Interp.Event.Cont),
+      mresult.updateDepth
+    )
+
+    // subscribe each step and update touched
+    interp.subscribe(Interp.Event.Step, mresult.updateTouched)
+
+    // subscribe termination and dump result
+    interp.subscribe(Interp.Event.Terminate, { st =>
+      // dump result
+      val result = mresult.into(interp.getIter)
+      dumpJson(result, s"$logDir/${incRid()}.json", true)
+    })
+  }
+
+  // set base directory to dump
[…]

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/js/Test262.scala

@@ -25,6 +25,21 @@ object Test262 {
   def parseFile(filename: String): Script =
     Parser.parse(Parser.Script(Nil), fileReader(filename)).get
 
+  // load test262 test file
+  def loadTest262(jsName: String, harness: List[String]): Script = {
+    val harnessStmts = harness.foldLeft(basicStmts) {
+      case (li, s) => for {
+        x <- li
+        y <- getInclude(s)
+      } yield x ++ y
+    } match {
+      case Right(l) => l
+      case Left(msg) => throw NotSupported(msg)
+    }
+    val stmts = harnessStmts ++ flattenStmt(parseFile(jsName))
+    mergeStmt(stmts)
+  }
+
   // test262 test configuration
   lazy val config = FilterMeta.test262configSummary
 

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/package.scala

@@ -13,7 +13,6 @@ package object jiset {
   val CFG_LOG_DIR = s"$LOG_DIR/cfg"
   val CHECK_LOG_DIR = s"$LOG_DIR/check"
   val ANALYZE_LOG_DIR = s"$LOG_DIR/analyze"
-  val VISITED_LOG_DIR = s"$LOG_DIR/visited-nodes"
 
   // Specification directory
   val ECMA262_DIR = s"$BASE_DIR/ecma262"

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/util/ProgressBar.scala

@@ -6,7 +6,10 @@ import scala.concurrent.ExecutionContext.Implicits.global
 import kr.ac.kaist.jiset.LINE_SEP
 
 // progress bar
-case class ProgressBar[T](msg: String, seq: Iterable[T]) {
+case class ProgressBar[T](
+  msg: String,
+  seq: Iterable[T]
+) {
   // summary
   val summary = new Summary
 

### 2021-10-21 src/main/scala/kr/ac/kaist/jiset/util/Summary.scala

@@ -2,6 +2,7 @@ package kr.ac.kaist.jiset.util
 
 import java.io.PrintWriter
 import kr.ac.kaist.jiset.LINE_SEP
+import kr.ac.kaist.jiset.util.JvmUseful._
 
 class Summary {
   // not yet supported
@@ -22,6 +23,15 @@ class Summary {
 
   // close all print writers
   def close: Unit = { yets.close; timeouts.close; fails.close; passes.close }
+
+  // set base path of passes, fails, yets, timeouts
+  def setBase(logDir: String, name: String) = {
+    mkdir(logDir)
+    timeouts.setPath(s"$logDir/$name-timeout.log")
+    yets.setPath(s"$logDir/$name-yet.log")
+    fails.setPath(s"$logDir/$name-fail.log")
+    passes.setPath(s"$logDir/$name-pass.log")
+  }
 
   // time
   var timeMillis: Long = 0L

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/js/JSTest.scala

@@ -69,28 +69,18 @@ trait JSTest extends IRTest {
   }
 
   // tests for esparse
-  def esparseTest(jsName: String, filename: String): Unit = {
-    val answer = parseFile(jsName)
+  def esparseTest(answer: Script, jsName: String): Unit = {
     val toJsonName = changeExt("js", "json")
-    try {
-      val json = esparseFile(jsName)
+    val json = esparseFile(jsName)
 
-      // check compressed form equality
-      val comp0 = AST(answer.toJson).get
-      val comp1 = AST(json).get
-      assert(comp0.equals(comp1))
+    // check compressed form equality
+    val comp0 = AST(answer.toJson).get
+    val comp1 = AST(json).get
+    assert(comp0.equals(comp1))
 
-      // check AST equality
-      val ast = Script(comp1)
-      ASTDiff.diff(answer, ast)
-    } catch {
-      // save answer to tests/ast for debugging
-      case e: Throwable =>
-        val jsonName = toJsonName(filename)
-        dumpFile(answer.toString, s"$ESPARSE_DIR/$filename")
-        dumpFile(answer.toJson.noSpaces, s"$ESPARSE_DIR/$jsonName")
-        fail(s"esparse failed: $jsName")
-    }
+    // check AST equality
+    val ast = Script(comp1)
+    ASTDiff.diff(answer, ast)
   }
 
   // tests for JS interpreter
@@ -110,8 +100,14 @@ trait JSTest extends IRTest {
   // tests for JS analyzer
   def analyzeTestFile(filename: String): AbsSemantics =
     analyzeFile(filename, 0)
-  def analyzeTest(script: Script): AbsSemantics =
-    analyze(script, 0)
+  def analyzeTest(script: Script): AbsSemantics = {
+    val absSem = analyze(script, 0)
+    absSem.finalResult.value.isAbruptCompletion.getSingle match {
+      case FlatElem(Bool(false)) =>
+      case res => fail(s"analyze failed: $res")
+    }
+    absSem
+  }
 
   // conversion extension from .js to .ir
   val js2ir = changeExt("js", "ir")

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/AnalyzeLargeTest.scala

@@ -2,28 +2,23 @@ package kr.ac.kaist.jiset.test262
 
 import kr.ac.kaist.jiset._
 import kr.ac.kaist.jiset.js.Test262
+import kr.ac.kaist.jiset.js.ast.Script
 import kr.ac.kaist.jiset.util.Useful._
 import kr.ac.kaist.jiset.util.JvmUseful._
+import kr.ac.kaist.jiset.analyzer._
+import kr.ac.kaist.jiset.analyzer.domain._
 
 class AnalyzeLargeTest extends Test262Test {
   val name: String = "test262AnalyzeTest"
 
-  // offset and stride
-  val offset = optional(System.getenv("JSAVER_OFFSET").toInt).getOrElse(0)
-  val stride = optional(System.getenv("JSAVER_STRIDE").toInt).getOrElse(1)
-
-  // filename for analyze target names
-  val filename = s"$BASE_DIR/tests/analyze-test262"
-
   // logging
   LOG = true
 
+  // test test262 test
+  def doTest(script: Script, name: String): Unit =
+    analyzeTest(script)
+
   // registration
-  def init: Unit = check(name, {
-    val targets = readFile(filename).split(LINE_SEP).toSet
-    val tests = Test262.config.normal.filter(targets contains _.name)
-    val sliced = slice(tests, offset, stride)
-    test262Test(sliced, TestKind.Analyze)
-  })
+  def init: Unit = check(name, { test262Test("analyze") })
   init
 }

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/ESParseLargeTest.scala

@@ -2,6 +2,7 @@ package kr.ac.kaist.jiset.test262
 
 import kr.ac.kaist.jiset._
 import kr.ac.kaist.jiset.js._
+import kr.ac.kaist.jiset.js.ast.Script
 import kr.ac.kaist.jiset.phase.FilterMeta
 import kr.ac.kaist.jiset.util._
 import kr.ac.kaist.jiset.util.Useful._
@@ -10,42 +11,18 @@ import kr.ac.kaist.jiset.util.JvmUseful._
 class ESParseLargeTest extends Test262Test {
   val name: String = "test262ESParseTest"
 
-  import Test262._
-
   // parser timeout
   val PARSE_TIMEOUT = 100 // second
 
-  // progress bar
-  val progress = ProgressBar("test262 esparse test", config.normal)
+  // test test262 test
+  def doTest(script: Script, name: String): Unit =
+    esparseTest(script, s"$TEST262_TEST_DIR/$name")
 
-  // summary
-  val summary = progress.summary
+  // parse
+  override def parse(filename: String, includes: List[String]): Script =
+    parseFile(filename)
 
   // registration
-  def init: Unit = check(name, {
-    mkdir(logDir)
-
-    cleanDir(ESPARSE_DIR)
-    mkdir(ESPARSE_DIR)
-
-    dumpFile(JISETTest.spec.version, s"$logDir/ecma262-version")
-    dumpFile(currentVersion(BASE_DIR), s"$logDir/jiset-version")
-    summary.fails.setPath(s"$logDir/esparse-fail.log")
-    summary.passes.setPath(s"$logDir/esparse-pass.log")
-    for (config <- progress) {
-      val name = config.name
-      val jsName = s"$TEST262_TEST_DIR/$name"
-      val filename = name.split("/").last
-      getError {
-        timeout(esparseTest(jsName, filename), PARSE_TIMEOUT)
-        summary.passes += name
-      }.foreach(e => {
-        summary.fails += name
-      })
-    }
-    summary.close
-    dumpFile(summary, s"$logDir/esparse-summary")
-    if (summary.fail > 0) fail(s"${summary.fail} tests are failed.")
-  })
+  def init: Unit = check(name, { test262Test("esparse") })
   init
 }

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/EvalLargeTest.scala

@@ -1,7 +1,9 @@
 package kr.ac.kaist.jiset.test262
 
 import kr.ac.kaist.jiset._
+import kr.ac.kaist.jiset.ir.Logger
 import kr.ac.kaist.jiset.js.Test262
+import kr.ac.kaist.jiset.js.ast.Script
 
 class EvalLargeTest extends Test262Test {
   val name: String = "test262Test"
@@ -9,9 +11,14 @@ class EvalLargeTest extends Test262Test {
   // logging execution traces
   LOG = true
 
+  // set base directory for ir.Logger
+  Logger.setBase(s"$logDir/logger")
+
+  // test test262 test
+  def doTest(script: Script, name: String): Unit =
+    evalTest(script, name)
+
   // registration
-  def init: Unit = check(name, {
-    test262Test(Test262.config.normal, TestKind.Eval)
-  })
+  def init: Unit = check(name, { test262Test("eval") })
   init
 }

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/ManualMiddleTest.scala

@@ -1,23 +1,32 @@
 package kr.ac.kaist.jiset.test262
 
 import kr.ac.kaist.jiset._
+import kr.ac.kaist.jiset.ir.Logger
 import kr.ac.kaist.jiset.js.Test262
+import kr.ac.kaist.jiset.js.ast.Script
 import kr.ac.kaist.jiset.util.JvmUseful._
 
 class ManualMiddleTest extends Test262Test {
   val name: String = "test262ManualTest"
 
-  // filename for manual target names
-  val filename = s"$BASE_DIR/tests/manual-test262"
-
   // logging execution traces
   LOG = true
 
+  // set base directory for ir.Logger
+  Logger.setBase(s"$logDir/logger")
+
+  // filename for manual target names
+  val filename = s"$BASE_DIR/tests/manual-test262"
+
+  // eval-manual targets
+  val names = readFile(filename).split(LINE_SEP).toSet
+  override val targets = Test262.config.normal.filter(names contains _.name)
+
+  // test test262 test
+  def doTest(script: Script, name: String): Unit =
+    evalTest(script, name)
+
   // registration
-  def init: Unit = check(name, {
-    val manuals = readFile(filename).split(LINE_SEP).toSet
-    val targets = Test262.config.normal.filter(manuals contains _.name)
-    test262Test(targets, TestKind.EvalManual)
-  })
+  def init: Unit = check(name, { test262Test("eval-manual") })
   init
 }

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/ParseLargeTest.scala

@@ -2,6 +2,7 @@ package kr.ac.kaist.jiset.test262
 
 import kr.ac.kaist.jiset._
 import kr.ac.kaist.jiset.js._
+import kr.ac.kaist.jiset.js.ast.Script
 import kr.ac.kaist.jiset.phase.FilterMeta
 import kr.ac.kaist.jiset.util._
 import kr.ac.kaist.jiset.util.Useful._
@@ -10,37 +11,18 @@ import kr.ac.kaist.jiset.util.JvmUseful._
 class ParseLargeTest extends Test262Test {
   val name: String = "test262ParseTest"
 
-  import Test262._
-
   // parser timeout
   val PARSE_TIMEOUT = 100 // second
 
-  // progress bar
-  val progress = ProgressBar("test262 parse test", config.normal)
+  // test test262 test
+  def doTest(script: Script, name: String): Unit =
+    parseTest(script)
 
-  // summary
-  val summary = progress.summary
+  // parse
+  override def parse(filename: String, includes: List[String]): Script =
+    timeout(parseFile(filename), PARSE_TIMEOUT)
 
   // registration
-  def init: Unit = check(name, {
-    mkdir(logDir)
-    dumpFile(JISETTest.spec.version, s"$logDir/ecma262-version")
-    dumpFile(currentVersion(BASE_DIR), s"$logDir/jiset-version")
-    summary.fails.setPath(s"$logDir/eval-fail.log")
-    summary.passes.setPath(s"$logDir/eval-pass.log")
-    for (config <- progress) {
-      val name = config.name
-      val jsName = s"$TEST262_TEST_DIR/$name"
-      getError {
-        timeout(parseTest(parseFile(jsName)), PARSE_TIMEOUT)
-        summary.passes += name
-      }.foreach(e => {
-        summary.fails += name
-      })
-    }
-    summary.close
-    dumpFile(summary, s"$logDir/parse-summary")
-    if (summary.fail > 0) fail(s"${summary.fail} tests are failed.")
-  })
+  def init: Unit = check(name, { test262Test("parse") })
   init
 }

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/ParserBenchmarkTest.scala

@@ -1,64 +1,0 @@
-package kr.ac.kaist.jiset.test262
-
-import kr.ac.kaist.jiset._
-import kr.ac.kaist.jiset.js._
-import kr.ac.kaist.jiset.phase.FilterMeta
-import kr.ac.kaist.jiset.util._
-import kr.ac.kaist.jiset.util.Useful._
-import kr.ac.kaist.jiset.util.JvmUseful._
-
-class ParserBenchmarkTest extends Test262Test {
-  val name: String = "test262ParseBenchmarkTest"
-
-  import Test262._
-
-  // parser timeout
-  //val PARSE_TIMEOUT = 100 // second
-
-  // progress bar
-  val progress = ProgressBar("test262 paser-benchmark test", config.normal)
-
-  // summary
-  val summary = progress.summary
-
-  // registration
-  def init: Unit = check(name, {
-    mkdir(logDir)
-    dumpFile(JISETTest.spec.version, s"$logDir/ecma262-version")
-    dumpFile(currentVersion(BASE_DIR), s"$logDir/jiset-version")
-    summary.fails.setPath(s"$logDir/parser-benchmark-fail.log")
-    summary.passes.setPath(s"$logDir/parser-benchmark-pass.log")
-
-    var totalJS = 0L
-    var totalES = 0L
-
-    for (config <- progress) {
-      val name = config.name
-      val jsName = s"$TEST262_TEST_DIR/$name"
-      getError {
-        // Load file
-        var (timeLoad, file2str) = time(readFile(jsName))
-
-        // JSParse
-        var (timeJS, jsAST) = time(parse(file2str))
-
-        // ESParse
-        val shellStr = escapeJS(file2str)
-        var (timeES, esAST) = time(esparse(shellStr))
-
-        // parsed with both
-        totalES += timeES
-        totalJS += timeJS
-        summary.passes += name + "," + timeLoad + "," + timeJS + "," + timeES
-      }.foreach(e => {
-        // println(e)
-        summary.fails += name
-      })
-    }
-    val result = s"Total ${summary.pass} tests are parsed: $totalES ms took with ESParse, $totalJS ms took with JSParse"
-    println(result)
-    summary.close
-    dumpFile(result, s"$logDir/parse-benchmark-summary")
-  })
-  init
-}

### 2021-10-21 src/test/scala/kr/ac/kaist/jiset/test262/Test262Test.scala

@@ -6,150 +6,67 @@ import kr.ac.kaist.jiset.js.JSTest
 import kr.ac.kaist.jiset.ir._
 import kr.ac.kaist.jiset.js._
 import kr.ac.kaist.jiset.js.Test262._
-import kr.ac.kaist.jiset.analyzer._
-import kr.ac.kaist.jiset.analyzer.domain._
+import kr.ac.kaist.jiset.js.ast.Script
 import kr.ac.kaist.jiset.util._
 import kr.ac.kaist.jiset.util.Useful._
 import kr.ac.kaist.jiset.util.JvmUseful._
-import io.circe._, io.circe.generic.semiauto._, io.circe.generic.auto._
 
 trait Test262Test extends JSTest {
   override val category: String = "test262"
 
   // directory name
   val logDir = s"$LOG_DIR/test262_$dateStr"
+  mkdir(logDir)
 
-  // test kinds
-  type TestKind = TestKind.Value
-  object TestKind extends Enumeration {
-    val Eval, EvalManual, Analyze = Value
-    def getName(kind: Value) = kind match {
-      case Eval => "eval"
-      case EvalManual => "eval-manual"
-      case Analyze => "analyze"
-    }
-  }
+  // test262 targets
+  val targets: List[NormalTestConfig] = Test262.config.normal
 
-  type MaxIJK = AbsSemantics.MaxIJK
+  // test test262 test
+  def doTest(script: Script, name: String): Unit
 
-  // analyze result for jsaver
-  case class AnalyzeResult(test: String, jsaver: String, jsaverTime: Double)
-  implicit lazy val AnalyzeResultDecoder: Decoder[AnalyzeResult] = deriveDecoder
-  implicit lazy val AnalyzeResultEncoder: Encoder[AnalyzeResult] = deriveEncoder
+  // dump test262 test stats
+  def dumpStats(logDir: String): Unit = ()
 
-  // get analyze result
-  def getAnalyzeResult(kind: TestKind, result: String) = kind match {
-    case TestKind.Analyze => Some(result)
-    case _ => None
-  }
+  // get AST for test262 test
+  def parse(filename: String, includes: List[String]): Script =
+    loadTest262(filename, includes)
 
   // test 262 tests
-  def test262Test(
-    targets: List[NormalTestConfig],
-    kind: TestKind
-  ): Unit = {
-    val name = TestKind.getName(kind)
-    val progress = ProgressBar(s"test262 $name test", targets)
[…]

### 2021-10-22 paper/pldi22/formal.tex
More formalization in appendix

@@
 We first define $\ires$ as a specification language to describe JavaScript
-semantics.  Then, we define a function specialization in $\ires$ with two
-different source-to-source transformations: a constant propagation
-transformation and a redundancy elimination transformation.  We prove the
-semantics preservation of function specialization under an observational
-semantics.  Finally, we define the JavaScript semantics specialization with
-syntactic views using function specialization.
+semantics.  Then, we introduce a general formalization of function
+specialization in $\ires$. Finally, we define a constant propagation
+specialization as its an instance to reduce JavaScript semantics using given
+syntactic views. We also prove its semantics preservation under an observational
+semantics.
 
@@
 
-A source-to-source transformation is defined with parameteric restrictions
-$\restrictset$ and its concretization $\gamma: \restrictset \rightarrow
-\powerset{\stset \times \valset^*}$.
-\[
-  \framebox{$\transf: \funcset \times \restrictset \rightarrow \funcset$}
-\]
+A function specialization is defined with the following three components:
+\begin{itemize}
+  \item Restriction $\restrictset$
+  \item Concretization $\gamma: \restrictset \rightarrow \powerset{\stset
+    \times \valset^*}$
+  \item Transformation $\trans: \restrictset \rightarrow \funcset \rightarrow
+    \funcset$.
+\end{itemize}
 
@@
 
-\subsubsection{Constant Propagation Transformation}
+\subsubsection{Constant Propagation Specialization}
+\begin{itemize}
+  \item Restriction $\cprestrictset = (\valoptset)^* =
+    (\valset \uplus \{ \top \})^*$
+  \item Concretization $\cpgamma: (\valoptset)^* \rightarrow \powerset{\stset
+    \times \valset^*}$ s.t.
     \[
-  \begin{array}{lr@{~}c@{~}l}
-    \text{Restrictions} & (\valoptset)^* &=& (\valset \uplus \{ \top \})^*\\
-    \text{Concretization} & \gamma(\valopt_1, \cdots, \valopt_n) &=& \\
-    \multicolumn{4}{l}{\qquad \{
-      (\st, (\val_1, \cdots, \val_n)) \mid
-      \val_i \in \left\{
+      \cpgamma(\valopt_1, \cdots, \valopt_n) = \stset \times (V_1 \times \cdots
+      \times V_n)
+    \]
+    where $V_i = \left\{
       \begin{array}{ll}
@@
       \end{array}
-      \right.
-    \}}\\
+    \right.$
+  \item Transformation $\cptrans: (\valoptset)^* \rightarrow \funcset
+    \rightarrow \funcset$
+\end{itemize}
+In the constant propagation specialization, a restriction is a sequences of
+static values $\valset$ or a dynamic value $\top$.
+
+\[
+  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
+    \text{Symbolic Environments} & \senv &\in& \senvset &=&
+    \varset \finmap \svalset\\
+    \text{Symbolic Values} & \sval &\in& \svalset &=&
+    \valoptset \times \exprset\\
   \end{array}
@@
 
-In the constant propagation transformation, restrictions $(\valoptset)^*$ are
-sequences of static values $\valset$ or a dynamic value $\top$.
+\[
+  \framebox{$\cptranse: \exprset \times \senvset \rightarrow \svalset$}
+\]
 
 \[
-  \framebox{$\transcpe: \exprset \times \envset \rightarrow \exprset$}
+  \begin{array}{lcl}
+    \cptranse(\pval, \env) &=& \pval\\
+    \cptranse(\op \kwrl \expr^* \kwrr, \env) &=& \todo\\
+    \cptranse(\kwcl \kwcr, \env) &=& \todo\\
+    \cptranse(\refer, \env) &=& \todo\\
+  \end{array}
+\]
+
+\[
+  \framebox{$\cptransi: \instset \times \senvset \rightarrow \instset \times
+  \senvset$}
 \]
@@
 \[
-  \framebox{$\transcpi: \instset \times \envset \rightarrow \instset \times
-  \envset$}
+  \framebox{$\cptrans: (\valoptset)^* \rightarrow \funcset \rightarrow
+  \funcset$}
 \]
@@
 
-\[
-  \framebox{$\transcpf: \funcset \times (\valoptset)^* \rightarrow \funcset$}
-\]
-
-\todo
-
-\subsubsection{Redundancy Elimination Transformation}
-
-\todo
-
-\[
-  \begin{array}{lr@{~}c@{~}l}
-    \text{Restrictions} &\{ \top \}\\
-    \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
-  \end{array}
-\]
-
-The redundancy elimination transformation is defined without any restriction,
-which means its restriction set consists of a single element $\top$
-representing all possible cases.  Therefore, we omit the restriction part in
-this transformation for the brevity.
-
-\[
-  \framebox{$\transref: \funcset \rightarrow \funcset$}
-\]
-
-\todo
+% \subsubsection{Redundancy Elimination Transformation}
+% 
+% \[
+%   \begin{array}{lr@{~}c@{~}l}
+%     \text{Restrictions} &\{ \top \}\\
+%     \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
+%   \end{array}
+% \]
+% 
+% The redundancy elimination transformation is defined without any restriction,
+% which means its restriction set consists of a single element $\top$
+% representing all possible cases.  Therefore, we omit the restriction part in
+% this transformation for the brevity.
+% 
+% \[
+%   \framebox{$\transref: \funcset \rightarrow \funcset$}
+% \]
+% 
+% \todo
 

### 2021-10-24 paper/pldi22/formal.tex
Till semantics of instructions

@@
     \text{Functions} & \funcset &\ni& \func &::=&
-    \kwdef \; x \; \kwrl x^* \kwrr \; \kwcl [\lab: \inst]^* \kwcr\\
+    \kwdef \; \varx \; \kwrl \varx^* \kwrr \; \lab\\
 
-    \text{Variables} & \varset &\ni& x\\
+    \text{Variables} & \varset &\ni& \varx\\
 
@@
     \refer = \expr \mid
-    x = \expr \kwrl \expr^* \kwrr \mid
+    \varx = \expr \kwrl \expr^* \kwrr \mid
     \kwif \; \expr \; \lab \; \lab \mid
@@
     \text{References} & \referset &\ni& \refer &::=&
-    x \mid \refer \kwsl \expr \kwsr\\
+    \varx \mid \refer \kwsl \expr \kwsr\\
   \end{array}
@@
 
-\todo update explanation
-
-A function $\func \in \funcset$ is defined with its name, parameters, and body
-instructions with labels $\labset$.  An instruction $\inst \in \instset$ is
-a primitive value assignment $x = \pval$,
-an operation between values $x = \op \kwrl x^* \kwrr$,
-a function call $x = x \kwrl x^* \kwrr$,
-a object allocation $x = \kwcl \kwcr$,
-a field access $x = x \kwsl x \kwsr$,
-a field assignment $x \kwsl x \kwsr = x$,
-a conditional branch $\kwif \; x \; \lab \; \lab$,
-or a return instruction $\kwret \; x$.
+An $\ires$ program $\prog = (\istset, \getinst, \getnext)$ consists of initial
+states and two mappings; $\getinst: \labset \rightarrow \instset$ maps labels to
+their instructions, and $\getnext: \labset \rightarrow \labset$ maps labels to
+their next labels, where a label $\lab \in \labset$ denotes a program point.  A
+function $\func \in \funcset$ is defined with its name, parameters, and body
+label.  For presentation brevity, we assume that no global variables exist in
+this paper.  An instruction $\inst \in \instset$ is an assignment $\refer =
+\expr$, a function call $x = \expr \kwrl \expr^* \kwrr$, a branch $\kwif \;
+\expr \; \lab \; \lab$, or a return instruction $\kwret \; \expr$.  An
+invocation of an abstract algorithm in ECMAScript is compiled to a function call
+instruction with a new temporary variable.  We represent loops using branch
+instructions with cyclic pointing of labels in $\getnext$.  An expression is a
+primitive value $\pval$, an operation $\op \kwrl \expr^* \kwrr$, an object
+allocation $\kwcl \kwcr$, or a reference $\refer$.  A reference is a variable
+$x$ or an object field $\refer \kwsl \expr \kwsr$.  We write $\refer.\varf$ to
+briefly represent $\refer \kwsl \code{"f"} \kwsr$.
 
@@
 
+    \text{Objects} & \obj &\in& \objset &=&
+    \strset \finmap \valset\\
+
     \text{Environments} & \env &\in& \envset &=&
@@
     \text{Primive Values} & \pval &\in& \pvalset &=&
-    \strset \uplus \cdots\\
+    \boolset \uplus \strset \uplus \cdots\\
 
     \text{JavaScript ASTs} & \tree &\in& \treeset\\
-
-    \text{Objects} & \obj &\in& \objset &=&
-    \strset \finmap \valset\\
   \end{array}
@@
 
-\todo
-% States $\stset$ consist of heaps $\heapset$ and contexts $\ctxtset$.  A heap
-% $\heap \in \heapset$ is a finite mapping from addresses to objects.  Each object
-% allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
-% \addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
-% a triple of a label, a environment, and an optional calling context $\ctxtopt
-% \in \ctxtoptset = \ctxtset \uplus \{ \bot \}$.  An environment $\env \in
-% \envset$ is a finite mapping from variables to values. A value $\val \in
-% \valset$ is a primitive value $\pval \in \pvalset$ (e.g., a string value $\str
-% \in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree \in
-% \treeset$, or a function $f \in \funcset$.  A object $\obj \in \objset$ is a
-% finite mappings from strings to values.
+States $\stset$ consist of labels $\labset$, calling context stacks
+$\ctxtset^*$, heaps $\heapset$, and environments $\envset$.  A calling context
+$\ctxt \in \ctxtset$ consists of a label denoting the return point, a caller's
+environment, and a return variable.  A heap $\heap \in \heapset$ is a finite
+mapping from addresses to objects, and an object $\obj \in \objset$ is a finite
+mappings from strings to values.  Each object allocation $\kwcl \kwcr$ creates a
+unique address $\addr \in \addrset$ different from existing addresses.  An
+environment $\env \in \envset$ is a finite mapping from variables to values. A
+value $\val \in \valset$ is a primitive value $\pval \in \pvalset$ (e.g., a
+boolean value $\bool \in \boolset$ or a string value $\str \in \strset$), an
+address $\addr \in \addrset$, a JavaScript AST $\tree \in \treeset$, or a
+function $f \in \funcset$.
 
-\subsubsection{Concrete Semantics of Functions}
+\subsubsection{Concrete Semantics}
 
+The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset, \getinst,
+\getnext)$ is defined as follows:
 \[
-  \framebox{$\sem{\func}: \stset \times \valset^* \rightarrow \stset \times
-  \valset$}
+  \sem{\prog} = \{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}
+\]
+where $\trans^*$ denotes one or more repetition of $\trans$, and $\st \trans
+\st$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
+\st'$. Now, we define the denotational semantics of instructions $\sem{\inst}:
+\stset \rightarrow \stset$, expressions $\sem{\expr}: \stset \rightarrow \stset
+\times \valset$, and references $\sem{\refer}: \stset \rightarrow \stset \times
+\valset$.
+
+\paragraph{Instructions: $\framebox{$\sem{\inst}: \stset \rightarrow \stset$}$}
+\begin{itemize}
+  \item \underline{Variable Assignments}:
+    \[
+      \sem{\varx = \expr}(\st) =
+      (\getnext(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
+    \]
+    where
+    \[
+      \sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)
     \]
 
-\todo
-
-\subsubsection{Concrete Semantics of Instructions}
-
+  \item \underline{Field Assignments}:
     \[
-  \framebox{$\sem{\inst}: \stset \rightarrow \stset$}
+      \sem{\refer \kwsl \expr_0 \kwsr = \expr_1}(\st) =
+      (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \sem{\refer}(\st) &=& (\st', \addr) &\wedge\\
+        \sem{\expr_0}(\st') &=& (\st'', \str) &\wedge\\
+        \sem{\expr_1}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
+        \obj &=& \heap(\addr) &\wedge\\
+        \obj' &=& \obj[\str \mapsto \val]\\
+      \end{array}
     \]
 
-\todo
-% \[
-%   \begin{array}{l}
-%     \sem{x = \pval}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad (\heap, (\lab, \env[x \mapsto \pval], \ctxtopt)) \\
-%     \\
-% 
-%     \sem{x = \op \kwrl x_1, \cdots, x_n \kwrr}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad (\heap, (\lab, \env[x \mapsto \sem{\op}(x_1, \cdots, x_n)], \ctxtopt)) \\
-%     \\
-% 
-%     \sem{x = x \kwrl x^* \kwrr}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad \todo \\
-%     \\
-% 
-%     \sem{x = \kwcl \kwcr}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad \todo \\
-%     \\
-% 
-%     \sem{x = x \kwsl x \kwsr}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad \todo \\
-%     \\
-% 
-%     \sem{x \kwsl x \kwsr = x}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad \todo \\
-%     \\
-% 
-%     \sem{\kwif \; x \; \lab \; \lab}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad \todo \\
-%     \\
-% 
-%     \sem{\kwret \; x}(\heap, (\lab, \env, \ctxtopt)) =\\
-%     \qquad \todo \\
-% 
-%   \end{array}
-% \]
-
-\subsubsection{Concrete Semantics of Expressions}
-
+  \item \underline{Function Calls}:
     \[
-  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
+      \sem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
+      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \sem{\expr} &=& (\st_0, \kwdef \; \varf \; \kwrl \varp_1, \cdots,
+        \varp_n \kwrr \; \lab_\varf) &\wedge\\
+        \sem{\expr_k}(\st_{k-1}) &=& (\st_k, \val_k) \; \forall 1 \leq k \leq n
+        &\wedge\\
+        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
+        \env' &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n]
+        &\wedge\\
+        \ctxt &=& (\getnext(\lab), \env, \varx)\\
+      \end{array}
     \]
 
-\todo
-
-\subsubsection{Concrete Semantics of References}
-
+  \item \underline{Branches}:
     \[
-  \framebox{$\sem{\refer}: \stset \rightarrow \stset \times \valset$}
+      \sem{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\st) =
+      \left\{
+        \begin{array}{ll}
+          (\lab_\vart, \ctxts, \heap, \env) & \text{if} \; \val = \true\\
+          (\lab_\varf, \ctxts, \heap, \env) & \text{if} \; \val = \false\\
+        \end{array}
+      \right.
+    \]
+    where
+    \[
+      \sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)
     \]
 
-\todo
+  \item \underline{Returns}:
+    \[
+      \sem{\kwret \; \expr}(\st) = (\lab, \ctxts, \heap, \env[\varx \mapsto
+      \val])
+    \]
+    where
+    \[
+      \sem{\expr}(\st) = ((\_, (\lab, \env, \varx) :: \ctxts, \heap, \_), \val)
+    \]
+\end{itemize}
+
+\paragraph{Expressions: $\framebox{$\sem{\expr}: \stset \rightarrow \stset
+\times \valset$}$}
+\begin{itemize}
+  \item \underline{Primive Values}:
+    \[
+      \sem{\pval}(\st) = \todo
+    \]
+  \item \underline{Operations}:
+    \[
+      \sem{\op \kwrl \expr^* \kwrr}(\st) = \todo
+    \]
+  \item \underline{Object Allocations}:
+    \[
+      \sem{\kwcl \kwcr}(\st) = \todo
+    \]
+  \item \underline{References}:
+    \[
+      \sem{\refer}(\st) = \todo
+    \]
+\end{itemize}
+
+\paragraph{References: $\framebox{$\sem{\refer}: \stset \rightarrow \stset
+\times \valset$}$}
+\begin{itemize}
+  \item \underline{Variable Lookups}:
+    \[
+      \sem{\varx}(\st) = \todo
+    \]
+  \item \underline{Field Lookups}:
+    \[
+      \sem{\refer \kwsl \expr \kwsr}(\st) = \todo
+    \]
+\end{itemize}
 
@@
     \times \valset^*}$
-  \item Transformation $\trans: \restrictset \rightarrow \funcset \rightarrow
-    \funcset$.
+  \item Transformation $\transform: \restrictset \rightarrow \funcset
+    \rightarrow \funcset$.
 \end{itemize}
@@
     \right.$
-  \item Transformation $\cptrans: (\valoptset)^* \rightarrow \funcset
+  \item Transformation $\cptransform: (\valoptset)^* \rightarrow \funcset
     \rightarrow \funcset$
@@
 \[
-  \framebox{$\cptranse: \exprset \times \senvset \rightarrow \svalset$}
+  \framebox{$\cptransforme: \exprset \times \senvset \rightarrow \svalset$}
 \]
@@
   \begin{array}{lcl}
-    \cptranse(\pval, \env) &=& \pval\\
-    \cptranse(\op \kwrl \expr^* \kwrr, \env) &=& \todo\\
-    \cptranse(\kwcl \kwcr, \env) &=& \todo\\
-    \cptranse(\refer, \env) &=& \todo\\
+    \cptransforme(\pval, \env) &=& \pval\\
+    \cptransforme(\op \kwrl \expr^* \kwrr, \env) &=& \todo\\
+    \cptransforme(\kwcl \kwcr, \env) &=& \todo\\
+    \cptransforme(\refer, \env) &=& \todo\\
   \end{array}
@@
 \[
-  \framebox{$\cptransi: \instset \times \senvset \rightarrow \instset \times
+  \framebox{$\cptransformi: \instset \times \senvset \rightarrow \instset \times
   \senvset$}
@@
 \[
-  \framebox{$\cptrans: (\valoptset)^* \rightarrow \funcset \rightarrow
+  \framebox{$\cptransform: (\valoptset)^* \rightarrow \funcset \rightarrow
   \funcset$}
@@
 % \[
-%   \framebox{$\transref: \funcset \rightarrow \funcset$}
+%   \framebox{$\transformref: \funcset \rightarrow \funcset$}
 % \]

### 2021-10-24 paper/pldi22/formal.tex
Till semantics
More formalization for function specialization

@@
       \begin{array}{l@{~}c@{~}ll}
-        \sem{\expr} &=& (\st_0, \kwdef \; \varf \; \kwrl \varp_1, \cdots,
+        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \varf \; \kwrl \varp_1, \cdots,
         \varp_n \kwrr \; \lab_\varf) &\wedge\\
@@
     \[
-      \sem{\pval}(\st) = \todo
+      \sem{\pval}(\st) =
+      (\st, \pval)
     \]
@@
     \[
-      \sem{\op \kwrl \expr^* \kwrr}(\st) = \todo
+      \sem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\st) =
+      (\st_n, \op(\val_1, \cdots, \val_n))
+    \]
+    where
+    \[
+      \st_0 = \st \wedge
+      \forall 1 \leq k \leq n. \; \sem{\expr_k}(\st_{k-1}) = (\st_k, \val_k)
     \]
@@
     \[
-      \sem{\kwcl \kwcr}(\st) = \todo
+      \sem{\kwcl \kwcr}(\st) =
+      ((\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env), \addr)
     \]
-  \item \underline{References}:
+    where
     \[
-      \sem{\refer}(\st) = \todo
+      \st = (\lab, \ctxts, \heap, \env) \wedge
+      \addr \not\in \text{Domain}(\heap)
     \]
@@
     \[
-      \sem{\varx}(\st) = \todo
+      \sem{\varx}(\st) =
+      (\st, \env(\varx))
+    \]
+    where
+    \[
+      \st = (\_, \_, \_, \env)
     \]
@@
     \[
-      \sem{\refer \kwsl \expr \kwsr}(\st) = \todo
+      \sem{\refer \kwsl \expr \kwsr}(\st) =
+      (\st'', \val')
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \sem{\refer}(\st) &=& (\st', \addr) &\wedge\\
+        \sem{\expr}(\st') &=& (\st'', \str) &\wedge\\
+        \st'' &=& (\_, \_, \heap, \_) &\wedge\\
+        \obj &=& \heap(\addr) &\wedge\\
+        \val' &=& \obj(\str)\\
+      \end{array}
     \]
@@
 
-\todo
-
-A function specialization is defined with the following three components:
+A \textit{function specialization} is defined with the following three
+components:
 \begin{itemize}
@@
 \end{itemize}
-
-\todo
+We can restrict possible input states and arguments of functions by defining a
+set of restrictions $\restrictset$ with their concretization $\gamma:
+\restrictset \rightarrow \powerset{\stset \times \valset^*}$. A transformation
+$\transform: \restrictset \rightarrow \funcset \rightarrow \funcset$ is
+parameteric with such restrictions and transforms a function to another function
+by preserving observational semantics under a given restriction.
 
 \subsubsection{Constant Propagation Specialization}
+We define a \textit{constant propagation specialization} with the following
+three components:
+
 \begin{itemize}
@@
 \end{itemize}
-In the constant propagation specialization, a restriction is a sequences of
-static values $\valset$ or a dynamic value $\top$.
+The constant propagation specialization restricts specific arguments with
+concrete values with a restriction defined with a sequence of static or dynamic
+values $\valset \uplus \{ \top \}$, but it does not restrict input states.
+While a dynamic value $\top$ denotes no restriction, it restricts a specific
+argument with the static value $\val \in \valset$. To specialize functions under
+a given restriction $(\valopt_1, \cdots, \valopt_n) \in (\valoptset)^*$, we
+define a transformation $\cptransform: (\valoptset)^* \rightarrow \funcset
+\rightarrow \funcset$. To propagate constants, \todo What is a constant?
 

### 2021-10-25 paper/pldi22/formal.tex
Added example for ASTs

@@
 specialization as its an instance to reduce JavaScript semantics using given
-syntactic views. We also prove its semantics preservation under an observational
-semantics.
+syntactic views. We also prove its semantics preservation.
 
@@
     \text{References} & \referset &\ni& \refer &::=&
-    \varx \mid \refer \kwsl \expr \kwsr\\
+    \varx \mid \expr \kwsl \expr \kwsr\\
   \end{array}
@@
 allocation $\kwcl \kwcr$, or a reference $\refer$.  A reference is a variable
-$x$ or an object field $\refer \kwsl \expr \kwsr$.  We write $\refer.\varf$ to
-briefly represent $\refer \kwsl \code{"f"} \kwsr$.
+$x$ or an object field $\expr \kwsl \expr \kwsr$.  We write $\expr.\varf$ to
+briefly represent $\expr \kwsl \code{"f"} \kwsr$.
 
@@
 
-    \text{JavaScript ASTs} & \tree &\in& \treeset\\
+    \text{JavaScript ASTs} & \tree &\in& \treeset &::=& \\
   \end{array}
@@
 
+Since $\ires$ is a specification language for JavaScript, it treats JavaScript
+ASTs $\treeset$ as its values. For presentation brevity, we represent a JavaScript
+AST as follows:
+\[
+  \tree ::= \str \mid \ty_k \langle \tree^* \rangle
+\]
+A string $\str$ denotes a leaf node with a terminal symbol, and $\ty_k \langle
+\tree^* \rangle$ denotes a non-leaf node for $k$-th alternative in the syntactic
+production of nonterminal symbol $\ty$ with its subtrees $\tree^*$.  The notation
+$\ty_k.\eval$ denotes an $\ires$ function for the evaluation of $k$-th
+alternative in $\ty$, and it takes the AST itself and its nonterminal subtrees
+as arguments. For each integer $k$, the notation $\tree[k]$ denotes $k$-th
+subtree of $\tree$.  For example, Figure~\ref{fig:coalesce-prod} shows a
+syntactic production for coalesce expressions.  Consider the following coalesce
+expression:
+\begin{lstlisting}[style=JS]
+                    42 ?? true
+\end{lstlisting}
+Then, the following AST is produced as its parsing result:
+\begin{figure}[H]
+  \includegraphics[width=.8\columnwidth]{img/ast-example.png}
+\end{figure}
+\noindent Moreover, its evaluation function $\nterm{CoalesceExpression}_0.\eval$
+takes three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and
+$\tree_2$ in the AST.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.8\columnwidth]{img/coalesce-prod.png}
+  \caption{A JavaScript syntactic production for coalesce expressions}
+  \label{fig:coalesce-prod}
+\end{figure}
+
 \subsubsection{Concrete Semantics}
 
-The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset, \getinst,
-\getnext)$ is defined as follows:
+The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset,
+\getinst, \getnext)$ is defined as follows:
 \[
@@
 where $\trans^*$ denotes one or more repetition of $\trans$, and $\st \trans
-\st$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
+\st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
 \st'$. Now, we define the denotational semantics of instructions $\sem{\inst}:
-\stset \rightarrow \stset$, expressions $\sem{\expr}: \stset \rightarrow \stset
-\times \valset$, and references $\sem{\refer}: \stset \rightarrow \stset \times
-\valset$.
+\stset \rightarrow \stset$ and expressions $\sem{\expr}: \stset \rightarrow
+\stset \times \valset$.
 
-\paragraph{Instructions: $\framebox{$\sem{\inst}: \stset \rightarrow \stset$}$}
+\todo function semantics
+
+\paragraph{Instructions}
+\[
+  \framebox{$\sem{\inst}: \stset \rightarrow \stset$}
+\]
 \begin{itemize}
@@
     \[
-      \sem{\refer \kwsl \expr_0 \kwsr = \expr_1}(\st) =
+      \sem{\expr_0 \kwsl \expr_1 \kwsr = \expr_2}(\st) =
       (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
@@
       \begin{array}{l@{~}c@{~}ll}
-        \sem{\refer}(\st) &=& (\st', \addr) &\wedge\\
-        \sem{\expr_0}(\st') &=& (\st'', \str) &\wedge\\
-        \sem{\expr_1}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
+        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
+        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
+        \sem{\expr_2}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
         \obj &=& \heap(\addr) &\wedge\\
@@
 
-\paragraph{Expressions: $\framebox{$\sem{\expr}: \stset \rightarrow \stset
-\times \valset$}$}
+\paragraph{Expressions}
+\[
+  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
+\]
 \begin{itemize}
@@
     \]
+
   \item \underline{Operations}:
@@
     \]
+
   \item \underline{Object Allocations}:
@@
     \]
-\end{itemize}
 
-\paragraph{References: $\framebox{$\sem{\refer}: \stset \rightarrow \stset
-\times \valset$}$}
-\begin{itemize}
   \item \underline{Variable Lookups}:
@@
     \]
+
   \item \underline{Field Lookups}:
     \[
-      \sem{\refer \kwsl \expr \kwsr}(\st) =
+      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) =
       (\st'', \val')
@@
       \begin{array}{l@{~}c@{~}ll}
-        \sem{\refer}(\st) &=& (\st', \addr) &\wedge\\
-        \sem{\expr}(\st') &=& (\st'', \str) &\wedge\\
+        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
+        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
         \st'' &=& (\_, \_, \heap, \_) &\wedge\\
@@
 parameteric with such restrictions and transforms a function to another function
-by preserving observational semantics under a given restriction.
+by preserving semantics under a given restriction.
 
@@
 \begin{itemize}
-  \item Restriction $\cprestrictset = (\valoptset)^* =
-    (\valset \uplus \{ \top \})^*$
-  \item Concretization $\cpgamma: (\valoptset)^* \rightarrow \powerset{\stset
+  \item Restriction $\cprestrictset = \avalset^*$
+  \item Concretization $\cpgamma: \avalset^* \rightarrow \powerset{\stset
     \times \valset^*}$ s.t.
     \[
-      \cpgamma(\valopt_1, \cdots, \valopt_n) = \stset \times (V_1 \times \cdots
-      \times V_n)
+      \cpgamma(\aval_1, \cdots, \aval_n) =
+      \stset \times (\valgamma(\aval_1) \times \cdots \times \valgamma(\aval_n))
     \]
-    where $V_i = \left\{
-      \begin{array}{ll}
-        \valset & \text{if} \; \valopt_i = \top\\
-        \{ \valopt_i \} & \text{otherwise}\\
-      \end{array}
-    \right.$
-  \item Transformation $\cptransform: (\valoptset)^* \rightarrow \funcset
+  \item Transformation $\cptransform: \avalset^* \rightarrow \funcset
     \rightarrow \funcset$
@@
 argument with the static value $\val \in \valset$. To specialize functions under
-a given restriction $(\valopt_1, \cdots, \valopt_n) \in (\valoptset)^*$, we
-define a transformation $\cptransform: (\valoptset)^* \rightarrow \funcset
+a given restriction $(\aval_1, \cdots, \aval_n) \in \avalset^*$, we
+define a transformation $\cptransform: \avalset^* \rightarrow \funcset
 \rightarrow \funcset$. To propagate constants, \todo What is a constant?
+a constant is a value which is statically fixed under a given restriction.
 
@@
   \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
-    \text{Symbolic Environments} & \senv &\in& \senvset &=&
-    \varset \finmap \svalset\\
-    \text{Symbolic Values} & \sval &\in& \svalset &=&
-    \valoptset \times \exprset\\
+    \text{Abstract Environments} & \aenv &\in& \aenvset &=&
+    \varset \rightarrow \avalset\\
+    \text{Abstract Values} & \aval &\in& \avalset &=&
+    (\valset \times \exprset) \uplus \{ \bot, \top \}\\
   \end{array}
@@
 
+\todo $\envgamma, \valgamma, \join, \meet, \order$
+
+\paragraph{Expressions}
 \[
-  \framebox{$\cptransforme: \exprset \times \senvset \rightarrow \svalset$}
+  \framebox{$\asem{\expr}: \aenvset \rightarrow \avalset$}
 \]
-
+\begin{itemize}
+  \item \underline{Primive Values}:
     \[
-  \begin{array}{lcl}
-    \cptransforme(\pval, \env) &=& \pval\\
-    \cptransforme(\op \kwrl \expr^* \kwrr, \env) &=& \todo\\
-    \cptransforme(\kwcl \kwcr, \env) &=& \todo\\
-    \cptransforme(\refer, \env) &=& \todo\\
+      \asem{\pval}(\aenv) = (\pval, \pval)
+    \]
+  \item \underline{Operations}:
+    \[
+      \asem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\aenv) =
+      (\aval, \expr)
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \asem{\expr_k}(\aenv) &=& \aval_k \; \forall 1 \leq k \leq n
+        &\wedge\\
+        \aval &=& \left\{
+          \begin{array}{ll}
+            \bot & \text{if} \; \exists k. \; \aval_k = \bot\\
+            \top & \text{if} \; \exists k. \; \aval_k = \top\\
+            (\val, \expr') &
+            \text{if} \; \forall k. \; \aval_k = (\val_k, \expr'_k)\\
+          \end{array}
+        \right. &\wedge\\
+        \val &=& \op(\val_1, \cdots, \val_n) &\wedge\\
+        \expr' &=& \op(\expr'_1, \cdots, \expr'_n)\\
+      \end{array}
+    \]
+  \item \underline{Object Allocations}:
+    \[
+      \asem{\kwcl \kwcr}(\aenv) = \top
+    \]
+  \item \underline{Variable Lookups}:
+    \[
+      \asem{\varx}(\aenv) = \aenv(\varx)
+    \]
+  \item \underline{Field Lookups}:
+    \[
+      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \top
+    \]
+\end{itemize}
+\[
+  \framebox{$\cptransforme: \exprset \times \aenvset \rightarrow \exprset \times
+  \avalset$}
+\]
+\[
+  \cptransforme(\expr, \aenv) = (\expr'', \aval)
+\]
+where
+\[
+  \begin{array}{l@{~}c@{~}ll}
+    \aval &=& \asem{\expr}(\aenv) &\wedge\\
+    \expr'' &=& \left\{
+      \begin{array}{ll}
+        \pval & \text{if} \; \aval = (\pval, \_)\\
+        \expr' & \text{if} \; \aval = (\_, \expr')\\
+        \expr & \text{otherwise}\\
+      \end{array}
+    \right.\\
   \end{array}
@@
 
+\paragraph{Instructions}
 \[
-  \framebox{$\cptransformi: \instset \times \senvset \rightarrow \instset \times
-  \senvset$}
+  \framebox{$\cptransformi: \instset \times \aenvset \rightarrow \instset \times
+  \aenvset$}
+\]
+\begin{itemize}
+  \item \underline{Variable Assignments}:
+    \[
+      \cptransformi(\varx = \expr, \aenv) =
+      (\varx = \expr', \aenv[\varx \mapsto \aval])
+    \]
+    where
+    \[
+      (\expr', \aval) = \cptransforme(\expr, \aenv)
     \]
 
-\todo
+  \item \underline{Field Assignments}:
+    \[
+      \cptransformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
+      (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        (\expr'_0, \_) = \cptransforme(\expr_0, \aenv) &\wedge\\
+        (\expr'_1, \_) = \cptransforme(\expr_1, \aenv) &\wedge\\
+        (\expr'_2, \_) = \cptransforme(\expr_2, \aenv)\\
+      \end{array}
+    \]
 
+  \item \underline{Function Calls}:
     \[
-  \framebox{$\cptransform: (\valoptset)^* \rightarrow \funcset \rightarrow
+      \cptransformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
+      (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
+      \aenv[\varx \mapsto \top])
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        (\expr', \_) = \cptransforme(\expr, \aenv) &\wedge\\
+        (\expr'_k, \_) = \cptransforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
+        n\\
+      \end{array}
+    \]
+
+  \item \underline{Branches}:
+    \[
+      \cptransformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
+      (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
+    \]
+    where
+    \[
+      (\expr', \_) = \cptransforme(\expr, \aenv)
+    \]
+
+  \item \underline{Returns}:
+    \[
+      \cptransformi(\kwret \; \expr, \aenv) =
+      (\kwret \; \expr, \aenv)
+    \]
+    where
+    \[
+      (\expr', \_) = \cptransforme(\expr', \aenv)
+    \]
+\end{itemize}
+
+\paragraph{Functions}
+\[
+  \framebox{$\cptransform: (\avalset)^* \rightarrow \funcset \rightarrow
   \funcset$}
@@
 
-\subsubsection{Observational Semantics}
-
-\todo
-
 \subsection{JavaScript Semantics Specialization}
 
-\todo
+This section explains how to utilize the constant propagation specialization for
+the JavaScript semantics specialization with a user-defined syntactic view.  We
+first formally define syntactic views and their operations, then we explain how
+to decide a restriction of the constant propagation specialization based on a
+given syntactic view.
 

### 2021-10-25 paper/pldi22/formal.tex
More details in formalization

@@
     \text{Primive Values} & \pval &\in& \pvalset &=&
-    \boolset \uplus \strset \uplus \cdots\\
+    \boolset \uplus \intset \uplus \strset \uplus \cdots\\
 
-    \text{JavaScript ASTs} & \tree &\in& \treeset &::=& \\
+    \text{JavaScript ASTs} & \tree &\in& \treeset\\
   \end{array}
@@
 value $\val \in \valset$ is a primitive value $\pval \in \pvalset$ (e.g., a
-boolean value $\bool \in \boolset$ or a string value $\str \in \strset$), an
-address $\addr \in \addrset$, a JavaScript AST $\tree \in \treeset$, or a
-function $f \in \funcset$.
+boolean value $\bool \in \boolset$, an integer $k \in \intset$, or a string
+$\str \in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree
+\in \treeset$, or a function $f \in \funcset$.
 
@@
 \st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
-\st'$. Now, we define the denotational semantics of instructions $\sem{\inst}:
-\stset \rightarrow \stset$ and expressions $\sem{\expr}: \stset \rightarrow
-\stset \times \valset$.
+\st'$. Now, we define the denotational semantics of expressions, instructions,
+and functions.
 
-\todo function semantics
+\paragraph{Expressions} We define the denotational semantics of expressions with
+the following form:
+\[
+  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
+\]
+For each expression $\expr \in \exprset$, its semantics $\sem{\expr}$ takes a
+state and returns a pair of an updated state and a value as the result of
+expression. We define five different cases in the semantics of expressions as
+follows:
+\begin{itemize}
+  \item \underline{Primitive Values}:
+    \[
+      \sem{\pval}(\st) =
+      (\st, \pval)
+    \]
 
-\paragraph{Instructions}
+  \item \underline{Operations}:
+    \[
+      \sem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\st) =
+      (\st_n, \op(\val_1, \cdots, \val_n))
+    \]
+    where $\st_0 = \st \wedge \forall 1 \leq k \leq n. \;
+    \sem{\expr_k}(\st_{k-1}) = (\st_k, \val_k)$
+
+  \item \underline{Object Allocations}:
+    \[
+      \sem{\kwcl \kwcr}(\st) =
+      ((\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env), \addr)
+    \]
+    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
+    \text{Domain}(\heap)$
+
+  \item \underline{Variable Lookups}:
+    \[
+      \sem{\varx}(\st) =
+      (\st, \env(\varx))
+    \]
+    where $\st = (\_, \_, \_, \env)$
+
+  \item \underline{Field Lookups}:
+    \[
+      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) =
+      (\st'', \obj(\str))
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
+        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
+        \st'' &=& (\_, \_, \heap, \_) &\wedge\\
+        \obj &=& \heap(\addr)\\
+      \end{array}
+    \]
+\end{itemize}
+
+\paragraph{Instructions} We define the denotational semantics of instructions
+with the following form:
 \[
@@
 \]
+For each instruction $\inst \in \instset$, its semantics $\sem{\inst}$ takes a
+state and returns an updated state. We define five different cases in the
+semantics of instructions as follows:
+
 \begin{itemize}
@@
     \]
-    where
-    \[
-      \sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)
-    \]
+    where $\sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)$
 
@@
     \]
-    where
-    \[
-      \sem{\expr}(\st) = ((\_, (\lab, \env, \varx) :: \ctxts, \heap, \_), \val)
-    \]
+    where $\sem{\expr}(\st) = ((\_, (\lab, \env, \varx) :: \ctxts, \heap, \_),
+    \val)$
 \end{itemize}
 
-\paragraph{Expressions}
+\paragraph{Functions} Moreover, we define the denotational semantics of
+functions with the following form:
 \[
-  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
+  \framebox{$\sem{\func}: \heapset \times \valset^* \rightarrow \heapset \times
+  \valset$}
 \]
-\begin{itemize}
-  \item \underline{Primive Values}:
+For each function $\func \in \funcset$, its semantics $\sem{\func}$ takes a heap
+and values as arguments, and it returns a pair of an updated heap and a return
+value as follows:
 \[
-      \sem{\pval}(\st) =
-      (\st, \pval)
-    \]
-
-  \item \underline{Operations}:
-    \[
-      \sem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\st) =
-      (\st_n, \op(\val_1, \cdots, \val_n))
-    \]
-    where
-    \[
-      \st_0 = \st \wedge
-      \forall 1 \leq k \leq n. \; \sem{\expr_k}(\st_{k-1}) = (\st_k, \val_k)
-    \]
-
-  \item \underline{Object Allocations}:
-    \[
-      \sem{\kwcl \kwcr}(\st) =
-      ((\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env), \addr)
-    \]
-    where
-    \[
-      \st = (\lab, \ctxts, \heap, \env) \wedge
-      \addr \not\in \text{Domain}(\heap)
-    \]
-
-  \item \underline{Variable Lookups}:
-    \[
-      \sem{\varx}(\st) =
-      (\st, \env(\varx))
-    \]
-    where
-    \[
-      \st = (\_, \_, \_, \env)
-    \]
-
-  \item \underline{Field Lookups}:
-    \[
-      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) =
-      (\st'', \val')
+  \sem{\kwdef \; \varf \; \kwrl \varp_1, \cdots, \varp_n \kwrr \lab_\varf}
+  (\heap, (\val_1, \cdots, \val_n)) = (\heap'', \val'')
 \]
@@
   \begin{array}{l@{~}c@{~}ll}
-        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
-        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
-        \st'' &=& (\_, \_, \heap, \_) &\wedge\\
-        \obj &=& \heap(\addr) &\wedge\\
-        \val' &=& \obj(\str)\\
+    \st &=& (\lab_\varf, \epsilon, \heap, \env) &\wedge\\
+    \env &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n] &\wedge\\
+    \st \trans^* \st' &=& (\lab', \epsilon, \heap', \_) &\wedge\\
+    \getinst(\lab') &=& \kwret \; \expr' &\wedge\\
+    \sem{\expr'}(\st') &=& (\st'', \val'') &\wedge\\
+    \st'' &=& (\_, \epsilon, \heap'', \_)\\
   \end{array}
 \]
-\end{itemize}
 

### 2021-10-26 paper/pldi22/formal.tex
Transformations in formalization

@@
 We first define $\ires$ as a specification language to describe JavaScript
-semantics.  Then, we introduce a general formalization of function
-specialization in $\ires$. Finally, we define a constant propagation
-specialization as its an instance to reduce JavaScript semantics using given
-syntactic views. We also prove its semantics preservation.
+semantics.  Then, we introduce a partial evaluation in $\ires$ to reduce
+JavaScript semantics using given syntactic views. We also prove its semantics
+preservation.
 
@@
   \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
+    \text{Programs} & \progset &\ni& \prog &=& (\istset, \getinst, \getnext)\\
+
     \text{Functions} & \funcset &\ni& \func &::=&
-    \kwdef \; \varx \; \kwrl \varx^* \kwrr \; \lab\\
+    \kwdef \; \kwrl \varx^* \kwrr \; \lab\\
 
@@
 
-    \text{Labels} & \labset &\ni& \lab\\
-
     \text{Instructions} & \instset &\ni& \inst &::=&
     \refer = \expr \mid
-    \varx = \expr \kwrl \expr^* \kwrr \mid
+    \varx = \kwcl \kwcr \mid
+    \varx = \expr \kwrl \expr^* \kwrr \mid \\&&&&&
     \kwif \; \expr \; \lab \; \lab \mid
     \kwret \; \expr\\
+
+    \text{Labels} & \labset &\ni& \lab\\
 
@@
     \op \kwrl \expr^* \kwrr \mid
-    \kwcl \kwcr \mid
     \refer\\
@@
 their next labels, where a label $\lab \in \labset$ denotes a program point.  A
-function $\func \in \funcset$ is defined with its name, parameters, and body
-label.  For presentation brevity, we assume that no global variables exist in
-this paper.  An instruction $\inst \in \instset$ is an assignment $\refer =
-\expr$, a function call $x = \expr \kwrl \expr^* \kwrr$, a branch $\kwif \;
-\expr \; \lab \; \lab$, or a return instruction $\kwret \; \expr$.  An
-invocation of an abstract algorithm in ECMAScript is compiled to a function call
-instruction with a new temporary variable.  We represent loops using branch
-instructions with cyclic pointing of labels in $\getnext$.  An expression is a
-primitive value $\pval$, an operation $\op \kwrl \expr^* \kwrr$, an object
-allocation $\kwcl \kwcr$, or a reference $\refer$.  A reference is a variable
-$x$ or an object field $\expr \kwsl \expr \kwsr$.  We write $\expr.\varf$ to
+function $\func \in \funcset$ is defined with its parameters and body label.
+For presentation brevity, we assume that no global or captured variables exist
+in this paper.  An instruction $\inst \in \instset$ is an assignment $\refer =
+\expr$, an object allocation $\varx = \kwcl \kwcr$,  a function call $\varx =
+\expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \; \lab \; \lab$, or a
+return instruction $\kwret \; \expr$.  An invocation of an abstract algorithm in
+ECMAScript is compiled to a function call instruction with a new temporary
+variable.  We represent loops using branch instructions with cyclic pointing of
+labels in $\getnext$.  An expression is a primitive value $\pval$, an operation
+$\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A reference is a variable
+$\varx$ or an object field $\expr \kwsl \expr \kwsr$.  We write $\expr.\varf$ to
 briefly represent $\expr \kwsl \code{"f"} \kwsr$.
@@
 \[
-  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
+  \framebox{$\sem{\expr}: \stset \rightarrow \valset$}
 \]
 For each expression $\expr \in \exprset$, its semantics $\sem{\expr}$ takes a
-state and returns a pair of an updated state and a value as the result of
-expression. We define five different cases in the semantics of expressions as
+state and returns a value as the result of expression. We define four different
+cases in the semantics of expressions as
 follows:
@@
     \[
-      \sem{\pval}(\st) =
-      (\st, \pval)
+      \sem{\pval}(\st) = \pval
     \]
@@
       \sem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\st) =
-      (\st_n, \op(\val_1, \cdots, \val_n))
+      \op(\val_1, \cdots, \val_n)
     \]
-    where $\st_0 = \st \wedge \forall 1 \leq k \leq n. \;
-    \sem{\expr_k}(\st_{k-1}) = (\st_k, \val_k)$
-
-  \item \underline{Object Allocations}:
-    \[
-      \sem{\kwcl \kwcr}(\st) =
-      ((\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env), \addr)
-    \]
-    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
-    \text{Domain}(\heap)$
+    where $\forall 1 \leq k \leq n. \; \sem{\expr_k}(\st) = \val_k$
 
@@
     \[
-      \sem{\varx}(\st) =
-      (\st, \env(\varx))
+      \sem{\varx}(\st) = \env(\varx)
     \]
@@
     \[
-      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) =
-      (\st'', \obj(\str))
+      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) = \val
     \]
@@
       \begin{array}{l@{~}c@{~}ll}
-        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
-        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
-        \st'' &=& (\_, \_, \heap, \_) &\wedge\\
-        \obj &=& \heap(\addr)\\
+        \val_0 &=& \sem{\expr_0}(\st) &\wedge\\
+        \val_1 &=& \sem{\expr_1}(\st) &\wedge\\
+        \st &=& (\_, \_, \heap, \_) &\wedge\\
+        \val &=& \left\{
+          \begin{array}{ll}
+            \heap(\addr)(\str)
+            & \text{if} \; \val_0 = \addr \wedge \val_1 = \str\\
+            \tree[k]
+            & \text{if} \; \val_0 = \tree \wedge \val_1 = k\\
+          \end{array}
+        \right.\\
       \end{array}
@@
 For each instruction $\inst \in \instset$, its semantics $\sem{\inst}$ takes a
-state and returns an updated state. We define five different cases in the
+state and returns an updated state. We define six different cases in the
 semantics of instructions as follows:
@@
 
+  \item \underline{Object Allocations}:
+    \[
+      \sem{\varx = \kwcl \kwcr}(\st) =
+      (\lab, \ctxts, \heap[\addr \mapsto \epsilon], \env[\varx \mapsto
+      \addr])
+    \]
+    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
+    \text{Domain}(\heap)$ and $\epsilon$ denotes an empty object.
+
   \item \underline{Function Calls}:
@@
       \begin{array}{l@{~}c@{~}ll}
-        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \varf \; \kwrl \varp_1, \cdots,
-        \varp_n \kwrr \; \lab_\varf) &\wedge\\
+        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varp_1, \cdots, \varp_n
+        \kwrr \; \lab_\varf) &\wedge\\
         \sem{\expr_k}(\st_{k-1}) &=& (\st_k, \val_k) \; \forall 1 \leq k \leq n
@@
 
-\paragraph{Functions} Moreover, we define the denotational semantics of
-functions with the following form:
+% \paragraph{Functions} Moreover, we define the denotational semantics of
+% functions with the following form:
+% \[
+%   \framebox{$\sem{\func}: \heapset \times \valset^n \rightarrow \heapset \times
+%   \valset$}
+% \]
+% For each function $\func \in \funcset$, its semantics $\sem{\func}$ takes a heap
+% and values as arguments, and it returns a pair of an updated heap and a return
+% value as follows:
+% \[
+%   \sem{\kwdef \; \kwrl \varp_1, \cdots, \varp_n \kwrr \; \lab_\varf}
+%   (\heap, (\val_1, \cdots, \val_n)) = (\heap'', \val'')
+% \]
+% where
+% \[
+%   \begin{array}{l@{~}c@{~}ll}
+%     \env &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n] &\wedge\\
+%     \st &=& (\lab_\varf, \epsilon, \heap, \env) &\wedge\\
+%     \st \trans^* \st' &=& (\lab', \epsilon, \heap', \_) &\wedge\\
+%     \getinst(\lab') &=& \kwret \; \expr' &\wedge\\
+%     \sem{\expr'}(\st') &=& (\st'', \val'') &\wedge\\
+%     \st'' &=& (\_, \epsilon, \heap'', \_)\\
+%   \end{array}
+% \]
+
+\subsection{Partial Evaluation}
+
+We define a \textit{partial evaluation} in $\ires$ as a transformation
+$\transform: \funcset \times \avalset^n \rightarrow \progset$.  It takes a
+target function and abstract values $\avalset^n$ to restrict specific function
+parameters with static values, then it returns the transformed $\ires$ program
+in the given restriction.  We first define abstract domains of states,
+environments, and values as follows:
+\begin{itemize}
+  \item \underline{Abstract States}: $\aelemset = \labset \rightarrow \aenvset$
     \[
-  \framebox{$\sem{\func}: \heapset \times \valset^* \rightarrow \heapset \times
-  \valset$}
-\]
-For each function $\func \in \funcset$, its semantics $\sem{\func}$ takes a heap
-and values as arguments, and it returns a pair of an updated heap and a return
-value as follows:
-\[
-  \sem{\kwdef \; \varf \; \kwrl \varp_1, \cdots, \varp_n \kwrr \lab_\varf}
-  (\heap, (\val_1, \cdots, \val_n)) = (\heap'', \val'')
-\]
-where
-\[
-  \begin{array}{l@{~}c@{~}ll}
-    \st &=& (\lab_\varf, \epsilon, \heap, \env) &\wedge\\
-    \env &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n] &\wedge\\
-    \st \trans^* \st' &=& (\lab', \epsilon, \heap', \_) &\wedge\\
-    \getinst(\lab') &=& \kwret \; \expr' &\wedge\\
-    \sem{\expr'}(\st') &=& (\st'', \val'') &\wedge\\
-    \st'' &=& (\_, \epsilon, \heap'', \_)\\
+      \begin{array}{lcl}
+        \multicolumn{3}{l}{\elemgamma: \aelemset \rightarrow \powerset{\stset}}\\
+        \elemgamma(\aelem) &=& \{ \st \in \stset \mid \st = (\lab, \_, \_, \_)
+        \wedge \st \in \envgamma(\aelem(\lab)) \}\\
+
+        \aelem \order \aelem' &\Leftrightarrow& \forall \lab \in \labset. \;
+        \aelem(\lab) \order \aelem'(\lab)\\
+
+        \aelem \join \aelem' &=& \lambda \lab \in \labset. \; \aelem(\varx) \join
+        \aelem(\lab)\\
       \end{array}
     \]
+  \item \underline{Abstract Environments}: $\aenvset = \varset \rightarrow
+    \avalset$
+    \[
+      \begin{array}{lcl}
+        \multicolumn{3}{l}{\envgamma: \aenvset \rightarrow \powerset{\stset}}\\
+        \envgamma(\aenv) &=& \{ \st \in \stset \mid \forall \varx \in \varset.
+          \; (\aenv(\varx) = \langle \val, \expr \rangle) \Rightarrow\\ &&
+          \phantom{\{ \st \in \stset \mid} (\sem{\varx}(\st) = \sem{\expr}(\st) =
+          \val) \}\\
 
-\subsection{Function Specialization}
+        \aenv \order \env' &\Leftrightarrow& \forall \varx \in \varset. \;
+        \aenv(\varx) \order \aenv'(\varx)\\
 
-A \textit{function specialization} is defined with the following three
-components:
-\begin{itemize}
-  \item Restriction $\restrictset$
-  \item Concretization $\gamma: \restrictset \rightarrow \powerset{\stset
-    \times \valset^*}$
-  \item Transformation $\transform: \restrictset \rightarrow \funcset
-    \rightarrow \funcset$.
-\end{itemize}
-We can restrict possible input states and arguments of functions by defining a
-set of restrictions $\restrictset$ with their concretization $\gamma:
-\restrictset \rightarrow \powerset{\stset \times \valset^*}$. A transformation
-$\transform: \restrictset \rightarrow \funcset \rightarrow \funcset$ is
-parameteric with such restrictions and transforms a function to another function
-by preserving semantics under a given restriction.
-
-\subsubsection{Constant Propagation Specialization}
-We define a \textit{constant propagation specialization} with the following
-three components:
-
-\begin{itemize}
-  \item Restriction $\cprestrictset = \avalset^*$
-  \item Concretization $\cpgamma: \avalset^* \rightarrow \powerset{\stset
-    \times \valset^*}$ s.t.
-    \[
-      \cpgamma(\aval_1, \cdots, \aval_n) =
-      \stset \times (\valgamma(\aval_1) \times \cdots \times \valgamma(\aval_n))
-    \]
-  \item Transformation $\cptransform: \avalset^* \rightarrow \funcset
-    \rightarrow \funcset$
-\end{itemize}
-The constant propagation specialization restricts specific arguments with
-concrete values with a restriction defined with a sequence of static or dynamic
-values $\valset \uplus \{ \top \}$, but it does not restrict input states.
-While a dynamic value $\top$ denotes no restriction, it restricts a specific
-argument with the static value $\val \in \valset$. To specialize functions under
-a given restriction $(\aval_1, \cdots, \aval_n) \in \avalset^*$, we
-define a transformation $\cptransform: \avalset^* \rightarrow \funcset
-\rightarrow \funcset$. To propagate constants, \todo What is a constant?
-a constant is a value which is statically fixed under a given restriction.
-
-\[
-  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
-    \text{Abstract Environments} & \aenv &\in& \aenvset &=&
-    \varset \rightarrow \avalset\\
-    \text{Abstract Values} & \aval &\in& \avalset &=&
-    (\valset \times \exprset) \uplus \{ \bot, \top \}\\
+        \aenv \join \aenv' &=& \lambda \varx \in \varset. \; \aenv(\varx) \join
+        \aenv(\varx)\\
       \end{array}
     \]
+  \item \underline{Abstract Values}: $\avalset = (\valset \times \exprset)
+    \uplus \{ \top \}$
+    \[
+      \begin{array}{lcl}
+        \multicolumn{3}{l}{\valgamma: \avalset \rightarrow \powerset{\valset}}\\
+        \valgamma(\aval) &=& \left\{
+          \begin{array}{ll}
+            \{ \val \} & \aval = (\val, \expr) \\
+            \valset & \aval = \top\\
+          \end{array}
+        \right.\\
 
-\todo $\envgamma, \valgamma, \join, \meet, \order$
+        \aval \order \aval' &\Leftrightarrow&
+        \aval' = \top \vee \aval = \aval'\\
 
-\paragraph{Expressions}
+        \aval \join \aval' &=& \left\{
+          \begin{array}{ll}
+            \aval & \text{if} \; \aval = \aval'\\
+            \top & \text{otherwise}\\
+          \end{array}
+        \right.\\
+      \end{array}
+    \]
+\end{itemize}
+An abstract state $\aelem \in \aelemset$ is a mapping from labels to abstract
+environments to represent the shape of states in each label. An abstract
+environment $\aenv \in \aenvset$ is a mapping from variables to abstract values
+to describe values stored in variables.  An abstract value $\aval \in \avalset$
+is a static value $\langle \val, \expr \rangle$ or a dynamic value $\top$.
+Since non-primitive values (e.g., addresses or JavaScript ASTs) cannot be
+directly represented as expressions, each static values $\langle \val, \expr
+\rangle$ also keeps another way to represent itself as an expression. Now, we
+define transformations of expressions and instructions, and introduce an
+iterative algorithm to proceed the partial evaluation in $\ires$.
+
+\subsubsection{Expressions} Before defining a transformation of expressions, we
+first define abstract evaluation of expressions as follows:
 \[
@@
     \[
-      \asem{\pval}(\aenv) = (\pval, \pval)
+      \asem{\pval}(\aenv) = \langle \pval, \pval \rangle
     \]
@@
     \[
-      \asem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\aenv) =
-      (\aval, \expr)
+      \asem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\aenv) = \aval
     \]
@@
     \[
-      \begin{array}{l@{~}c@{~}ll}
+      \begin{array}{l@{~}c@{~}l@{~}l}
         \asem{\expr_k}(\aenv) &=& \aval_k \; \forall 1 \leq k \leq n
@@
           \begin{array}{ll}
-            \bot & \text{if} \; \exists k. \; \aval_k = \bot\\
             \top & \text{if} \; \exists k. \; \aval_k = \top\\
-            (\val, \expr') &
-            \text{if} \; \forall k. \; \aval_k = (\val_k, \expr'_k)\\
+            \langle \val, \expr' \rangle & \text{if} \; \forall k. \; \aval_k =
+            \langle \val_k, \expr'_k \rangle\\
           \end{array}
@@
       \end{array}
-    \]
-  \item \underline{Object Allocations}:
-    \[
-      \asem{\kwcl \kwcr}(\aenv) = \top
     \]
@@
     \[
-      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \top
+      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \aval
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}l@{~}l}
+        \asem{\expr_0}(\aenv) &=& \aval_0 &\wedge\\
+        \asem{\expr_1}(\aenv) &=& \aval_1 &\wedge\\
+        \aval &=& \left\{
+          \begin{array}{ll}
+            \langle \tree[k], \expr'_0 \kwsl \expr'_1 \kwsr \rangle & \text{if}
+            \; \aval_0 = \langle \tree, \expr'_0 \rangle \wedge \aval_1 =
+            \langle k, \expr'_1 \rangle\\
+            \top & \text{otherwise}\\
+          \end{array}
+        \right.\\
+      \end{array}
     \]
 \end{itemize}
+Then, we define the transformation of expressions as follows:
 \[
-  \framebox{$\cptransforme: \exprset \times \aenvset \rightarrow \exprset \times
+  \framebox{$\transforme: \exprset \times \aenvset \rightarrow \exprset \times
   \avalset$}
@@
 \[
-  \cptransforme(\expr, \aenv) = (\expr'', \aval)
+  \transforme(\expr, \aenv) = (\expr'', \aval)
 \]
@@
       \begin{array}{ll}
-        \pval & \text{if} \; \aval = (\pval, \_)\\
-        \expr' & \text{if} \; \aval = (\_, \expr')\\
+        \pval & \text{if} \; \aval = \langle \pval, \_ \rangle\\
+        \expr' & \text{if} \; \aval = \langle \_, \expr' \rangle\\
         \expr & \text{otherwise}\\
@@
 
-\paragraph{Instructions}
+\subsubsection{Instructions} Now, we define a transformation of instructions
+using the transformation of expressions as follows:
 \[
-  \framebox{$\cptransformi: \instset \times \aenvset \rightarrow \instset \times
+  \framebox{$\transformi: \instset \times \aenvset \rightarrow \instset \times
   \aenvset$}
@@
     \[
-      \cptransformi(\varx = \expr, \aenv) =
+      \transformi(\varx = \expr, \aenv) =
       (\varx = \expr', \aenv[\varx \mapsto \aval])
@@
     \[
-      (\expr', \aval) = \cptransforme(\expr, \aenv)
+      (\expr', \aval) = \transforme(\expr, \aenv)
     \]
@@
     \[
-      \cptransformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
+      \transformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
       (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
@@
       \begin{array}{l@{~}c@{~}ll}
-        (\expr'_0, \_) = \cptransforme(\expr_0, \aenv) &\wedge\\
-        (\expr'_1, \_) = \cptransforme(\expr_1, \aenv) &\wedge\\
-        (\expr'_2, \_) = \cptransforme(\expr_2, \aenv)\\
+        (\expr'_0, \_) = \transforme(\expr_0, \aenv) &\wedge\\
+        (\expr'_1, \_) = \transforme(\expr_1, \aenv) &\wedge\\
+        (\expr'_2, \_) = \transforme(\expr_2, \aenv)\\
       \end{array}
+    \]
+  \item \underline{Object Allocations}:
+    \[
+      \transformi(\varx = \kwcl \kwcr, \aenv) =
+      (\varx = \kwcl \kwcr, \aenv[\varx \mapsto \top])
     \]
@@
     \[
-      \cptransformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
+      \transformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
       (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
@@
       \begin{array}{l@{~}c@{~}ll}
-        (\expr', \_) = \cptransforme(\expr, \aenv) &\wedge\\
-        (\expr'_k, \_) = \cptransforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
+        (\expr', \_) = \transforme(\expr, \aenv) &\wedge\\
+        (\expr'_k, \_) = \transforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
         n\\
@@
     \[
-      \cptransformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
+      \transformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
       (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
@@
     \[
-      (\expr', \_) = \cptransforme(\expr, \aenv)
+      (\expr', \_) = \transforme(\expr, \aenv)
     \]
@@
     \[
-      \cptransformi(\kwret \; \expr, \aenv) =
+      \transformi(\kwret \; \expr, \aenv) =
       (\kwret \; \expr, \aenv)
@@
     \[
-      (\expr', \_) = \cptransforme(\expr', \aenv)
+      (\expr', \_) = \transforme(\expr', \aenv)
     \]
@@
 
-\paragraph{Functions}
-\[
-  \framebox{$\cptransform: (\avalset)^* \rightarrow \funcset \rightarrow
-  \funcset$}
-\]
+\subsubsection{Fixpoint of Abstract Transfer Function}
 
 \todo
-
-% \subsubsection{Redundancy Elimination Transformation}
-% 
-% \[
-%   \begin{array}{lr@{~}c@{~}l}
-%     \text{Restrictions} &\{ \top \}\\
-%     \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
-%   \end{array}
-% \]
-% 
-% The redundancy elimination transformation is defined without any restriction,
-% which means its restriction set consists of a single element $\top$
-% representing all possible cases.  Therefore, we omit the restriction part in
-% this transformation for the brevity.
-% 
-% \[
-%   \framebox{$\transformref: \funcset \rightarrow \funcset$}
-% \]
-% 
-% \todo
 

### 2021-10-26 paper/pldi22/formal.tex
Syntatic views in formalization

@@
 as arguments. For each integer $k$, the notation $\tree[k]$ denotes $k$-th
-subtree of $\tree$.  For example, Figure~\ref{fig:coalesce-prod} shows a
-syntactic production for coalesce expressions.  Consider the following coalesce
-expression:
+subtree of $\tree$. If an AST $\tree$ is a subtree of another AST $\tree'$, we
+represent it as $\tree \subtree \tree'$.  For example,
+Figure~\ref{fig:coalesce-prod} shows a syntactic production for coalesce
+expressions.  Consider the following coalesce expression:
 \begin{lstlisting}[style=JS]
@@
 \end{figure}
-\noindent Moreover, its evaluation function $\nterm{CoalesceExpression}_0.\eval$
-takes three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and
-$\tree_2$ in the AST.
+\noindent Its evaluation function $\nterm{CoalesceExpression}_0.\eval$ takes
+three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and $\tree_2$ in
+the figure. Note that $\tree_1$ and $\tree_2$ are subtrees of $\tree_0$ (i.e.,
+$\tree_1 \subtree \tree_0$ and $\tree_2 \subtree \tree_0$).
 
@@
           \begin{array}{ll}
-            \{ \val \} & \aval = (\val, \expr) \\
-            \valset & \aval = \top\\
+            \{ \val \} & \text{if} \; \aval = (\val, \expr) \\
+            \valset & \text{if} \; \aval = \top\\
           \end{array}
@@
 
-\subsubsection{Expressions} Before defining a transformation of expressions, we
-first define abstract evaluation of expressions as follows:
+\subsubsection{Transformation of Expressions} Before defining a transformation of
+expressions, we first define abstract evaluation of expressions as follows:
 \[
@@
 
-\subsubsection{Instructions} Now, we define a transformation of instructions
-using the transformation of expressions as follows:
+\subsubsection{Transformation of Instructions} Now, we define a transformation
+of instructions using the transformation of expressions as follows:
 \[
@@
 
-\subsubsection{Fixpoint of Abstract Transfer Function}
+\subsubsection{Fixpoint of Abstract Transfer Function} Finally, we define an
+abstract transfer function and its fixpoint to represent abstract semantics of a
+given function and abstract values:
+\[
+  \begin{array}{ll}
+    \text{Abstract Transfer Function} & \atransfer: \aelemset \rightarrow
+    \aelemset\\
+\end{array}
+\]
 
@@
 
-This section explains how to utilize the constant propagation specialization for
-the JavaScript semantics specialization with a user-defined syntactic view.  We
-first formally define syntactic views and their operations, then we explain how
-to decide a restriction of the constant propagation specialization based on a
-given syntactic view.
+This section explains how to utilize the partial evaluation for the JavaScript
+semantics specialization with a user-defined syntactic view.  We first formally
+define syntactic views and their operations, then we explain how to decide a
+restriction of the constant propagation specialization based on a given
+syntactic view.
 
-\subsubsection{Syntatic Views}
+\subsubsection{Syntatic Views} A syntatic view $\atree \in \atreeset$ is an
+augmented JavaScript ASTs with abstract nodes $\top$ as follows:
+\[
+  \atree ::= \str \mid \ty_k \langle \atree^* \rangle \mid \top
+\]
+\[
+  \begin{array}{lcl}
+    \multicolumn{3}{l}{\treegamma: \atreeset \rightarrow \powerset{\treeset}}\\
+    \treegamma(\atree) &=& \left\{
+      \begin{array}{ll}
+        \{ \str \} &
+        \text{if} \; \atree = \str \\
+
+        A & \text{if} \; \atree = \ty_k
+        \langle \atree_1, \cdots, \atree_n \rangle \\
+
+        \treeset & \atree = \top\\
+      \end{array}
+    \right.\\
+    A &=& \{ \ty_k \langle \tree_1, \cdots, \tree_n \rangle \mid \forall 1 \leq
+    j \leq n.  \; \tree_j \in \treegamma(\atree_j) \}
+  \end{array}
+\]
+
+\subsubsection{JavaScript Program Filtering}
+
+\[
+  \atree \subtree \tree' \iff \exists \tree \in \treegamma{\atree}. \; \tree
+  \subtree \tree'
+\]
 
@@
 
-\subsubsection{Specialization with Syntatic Views}
+\subsubsection{Semantics Specialization}
 

### 2021-10-27 paper/pldi22/formal.tex
Minor typos in formalization
Brief idea of cleanup
Writing formalization

@@
 We first define $\ires$ as a specification language to describe JavaScript
-semantics.  Then, we introduce a partial evaluation in $\ires$ to reduce
-JavaScript semantics using given syntactic views. We also prove its semantics
-preservation.
+semantics.
 
@@
   \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
-    \text{Programs} & \progset &\ni& \prog &=& (\istset, \getinst, \getnext)\\
+    \text{Programs} & \progset &\ni& \prog &=& (\istset, \getfunc, \getinst,
+    \getnext)\\
 
@@
 
-An $\ires$ program $\prog = (\istset, \getinst, \getnext)$ consists of initial
-states and two mappings; $\getinst: \labset \rightarrow \instset$ maps labels to
-their instructions, and $\getnext: \labset \rightarrow \labset$ maps labels to
-their next labels, where a label $\lab \in \labset$ denotes a program point.  A
-function $\func \in \funcset$ is defined with its parameters and body label.
-For presentation brevity, we assume that no global or captured variables exist
-in this paper.  An instruction $\inst \in \instset$ is an assignment $\refer =
-\expr$, an object allocation $\varx = \kwcl \kwcr$,  a function call $\varx =
-\expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \; \lab \; \lab$, or a
-return instruction $\kwret \; \expr$.  An invocation of an abstract algorithm in
-ECMAScript is compiled to a function call instruction with a new temporary
-variable.  We represent loops using branch instructions with cyclic pointing of
-labels in $\getnext$.  An expression is a primitive value $\pval$, an operation
-$\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A reference is a variable
-$\varx$ or an object field $\expr \kwsl \expr \kwsr$.  We write $\expr.\varf$ to
-briefly represent $\expr \kwsl \code{"f"} \kwsr$.
+An $\ires$ program $\prog = (\istset, \getfunc, \getinst, \getnext) \in \progset $
+consists of initial states and three mappings; $\getfunc: \labset \rightarrow
+\funcset$ and $\getinst: \labset \rightarrow \instset$ map labels to their
+functions and instructions, respectively, and $\getnext: \labset \rightarrow
+\labset$ maps labels to their next labels, where a label $\lab \in \labset$
+denotes a program point.  A function $\func \in \funcset$ is defined with its
+parameters and body label.  For presentation brevity, we assume that no global
+or captured variables exist in this paper.  An instruction $\inst \in \instset$
+is an assignment $\refer = \expr$, an object allocation $\varx = \kwcl \kwcr$, a
+function call $\varx = \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
+\lab \; \lab$, or a return instruction $\kwret \; \expr$.  An invocation of an
+abstract algorithm in ECMAScript is compiled to a function call instruction with
+a new temporary variable.  We represent loops using branch instructions with
+cyclic pointing of labels in $\getnext$.  An expression is a primitive value
+$\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A
+reference is a variable $\varx$ or an object field $\expr \kwsl \expr \kwsr$.
+We write $\expr.\varf$ to briefly represent $\expr \kwsl \code{"f"} \kwsr$.
 
@@
 
-    \text{Primive Values} & \pval &\in& \pvalset &=&
+    \text{Primitive Values} & \pval &\in& \pvalset &=&
     \boolset \uplus \intset \uplus \strset \uplus \cdots\\
@@
 \[
-  \tree ::= \str \mid \ty_k \langle \tree^* \rangle
+  \tree ::= \term{\str} \mid \ty_k \langle \tree^* \rangle
 \]
-A string $\str$ denotes a leaf node with a terminal symbol, and $\ty_k \langle
-\tree^* \rangle$ denotes a non-leaf node for $k$-th alternative in the syntactic
-production of nonterminal symbol $\ty$ with its subtrees $\tree^*$.  The notation
-$\ty_k.\eval$ denotes an $\ires$ function for the evaluation of $k$-th
-alternative in $\ty$, and it takes the AST itself and its nonterminal subtrees
-as arguments. For each integer $k$, the notation $\tree[k]$ denotes $k$-th
-subtree of $\tree$. If an AST $\tree$ is a subtree of another AST $\tree'$, we
-represent it as $\tree \subtree \tree'$.  For example,
+A leaf node $\term{\str}$ defined with a string $\str$ denotes a terminal
+symbol, and a non-leaf node $\ty_k \langle \tree^* \rangle$ denotes $k$-th
+alternative in the syntactic production of nonterminal symbol $\ty$ with its
+subtrees $\tree^*$.  The notation $\ty_k.\eval$ denotes an $\ires$ function for
+the evaluation of $k$-th alternative in $\ty$, and it takes the AST itself and
+its nonterminal subtrees as arguments. If an AST $\tree$ is a subtree of another
+AST $\tree'$, we represent it as $\tree \subtree \tree'$.  For example,
 Figure~\ref{fig:coalesce-prod} shows a syntactic production for coalesce
@@
     \]
-    where $\forall 1 \leq k \leq n. \; \sem{\expr_k}(\st) = \val_k$
+    where $\forall 1 \leq j \leq n. \; \sem{\expr_k}(\st) = \val_j$
 
@@
             & \text{if} \; \val_0 = \addr \wedge \val_1 = \str\\
-            \tree[k]
-            & \text{if} \; \val_0 = \tree \wedge \val_1 = k\\
+
+            \tree_j
+            & \text{if} \; \val_0 = \ty_k \langle \tree_1, \cdots, \tree_n
+            \rangle \wedge \val_1 = j\\
           \end{array}
@@
         \kwrr \; \lab_\varf) &\wedge\\
-        \sem{\expr_k}(\st_{k-1}) &=& (\st_k, \val_k) \; \forall 1 \leq k \leq n
-        &\wedge\\
+        \sem{\expr_j}(\st_{j-1}) &=& (\st_j, \val_j) \;
+        [\forall 1 \leq j \leq n] &\wedge\\
         \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
@@
 
-% \paragraph{Functions} Moreover, we define the denotational semantics of
-% functions with the following form:
-% \[
-%   \framebox{$\sem{\func}: \heapset \times \valset^n \rightarrow \heapset \times
-%   \valset$}
-% \]
-% For each function $\func \in \funcset$, its semantics $\sem{\func}$ takes a heap
-% and values as arguments, and it returns a pair of an updated heap and a return
-% value as follows:
-% \[
-%   \sem{\kwdef \; \kwrl \varp_1, \cdots, \varp_n \kwrr \; \lab_\varf}
-%   (\heap, (\val_1, \cdots, \val_n)) = (\heap'', \val'')
-% \]
-% where
-% \[
-%   \begin{array}{l@{~}c@{~}ll}
-%     \env &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n] &\wedge\\
-%     \st &=& (\lab_\varf, \epsilon, \heap, \env) &\wedge\\
-%     \st \trans^* \st' &=& (\lab', \epsilon, \heap', \_) &\wedge\\
-%     \getinst(\lab') &=& \kwret \; \expr' &\wedge\\
-%     \sem{\expr'}(\st') &=& (\st'', \val'') &\wedge\\
-%     \st'' &=& (\_, \epsilon, \heap'', \_)\\
-%   \end{array}
-% \]
+\subsection{Syntactic Views} A syntactic view $\atree \in \atreeset$ is an
+augmented JavaScript ASTs with abstract nodes $\treetop$:
+\[
+  \atree ::= \term{\str} \mid \ty_k \langle \atree^* \rangle \mid \treetop
+\]
+and its concretization is defined as follows:
+\[
+  \begin{array}{lcl}
+    \gamma(\term{\str}) &=&
+    \{ \term{\str} \}\\
+
+    \gamma(\ty_k \langle \atree_1, \cdots, \atree_n \rangle) &=&
+    \{ \ty_k \langle \tree_1, \cdots, \tree_n \rangle \mid \tree_j \in
+    \gamma(\atree_j) \}\\
+
+    \gamma(\treetop) &=& \treeset\\
+  \end{array}
+\]
+The partial order and join operator between abstract trees are defined as
+follows:
+\[
+  \begin{array}{lcl}
+    \atree \order \atree' &\Leftrightarrow& \left\{
+      \begin{array}{ll}
+        \atree = \atree' &\vee\\
+
+        \atree' = \treetop &\vee\\
+
+        \begin{array}{@{}l@{}}
+          \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
+          \atree' = \ty_k \langle \atree'_1, \cdots, \atree'_n \rangle \wedge\\
+          \forall j. \; \tree_j \order \tree'_j\\
+        \end{array}\\
+      \end{array}
+    \right.\\
+
+    \atree \join \atree' &=& \left\{
+      \begin{array}{ll}
+        \atree' & \text{if} \; \atree \order \atree'\\
+
+        \atree & \text{if} \; \atree \revorder \atree'\\
+
+        \ty_k \langle \atree''_1, \cdots, \atree''_n \rangle &
+        \text{if} \; \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle
+        \wedge\\&
+        \phantom{\text{if} \;} \atree = \ty_k \langle \atree_1, \cdots, \atree_n
+        \rangle \wedge\\&
+        \phantom{\text{if} \;} \forall j. \; \atree''_j = \atree_j
+        \join \atree'_j\\
+        \treetop & \text{otherwise}\\
+      \end{array}
+    \right.\\
+  \end{array}
+\]
+Moreover, we can filter out JavaScript programs using the subtree relation with
+syntactic views:
+\[
+  \atree \subtree \tree' \iff \exists \tree \in \gamma(\atree). \; \tree
+  \subtree \tree'
+\]
 
@@
 
-We define a \textit{partial evaluation} in $\ires$ as a transformation
-$\transform: \funcset \times \avalset^n \rightarrow \progset$.  It takes a
-target function and abstract values $\avalset^n$ to restrict specific function
-parameters with static values, then it returns the transformed $\ires$ program
-in the given restriction.  We first define abstract domains of states,
-environments, and values as follows:
+We define a \textit{partial evaluation} $\peval{-}: \progset \rightarrow
+\atreeset \rightarrow \progset$ of $\ires$ programs to specialize JavaScript
+semantics with a given syntactic view:
+\[
+  \peval{\prog}(\atree) = \transform(\prog, \asem{\prog}(\atree))
+\]
+It takes a syntactic view $\atree \in \atreeset$ to restrict arguments of the
+corresponding evaluation function. Then, it performs a static analysis
+$\asem{-}$ of a given program $\prog$ with the static part $\atree$ and
+transforms it using $\transform$ with the analysis result
+$\asem{\prog}(\atree)$ to produce a new specialized $\ires$ program.  Now, we
+define the static analysis and program transformation of $\ires$ programs and
+prove the semantics preservation of the partial evaluation consisting of them.
+
+\subsubsection{Static Analysis}
+
+To define static analysis of $\ires$ programs, we first define abstract domains
+of states, calling contexts, environments, and values as follows:
 \begin{itemize}
-  \item \underline{Abstract States}: $\aelemset = \labset \rightarrow \aenvset$
+  \item \underline{Abstract States}:
+    $\aelemset = \actxtset \times \afsenvset$
     \[
       \begin{array}{lcl}
-        \multicolumn{3}{l}{\elemgamma: \aelemset \rightarrow \powerset{\stset}}\\
-        \elemgamma(\aelem) &=& \{ \st \in \stset \mid \st = (\lab, \_, \_, \_)
-        \wedge \st \in \envgamma(\aelem(\lab)) \}\\
+        \gamma(\afsenv, \actxt) &=& \gamma(\actxt) \cap
+        \gamma(\afsenv)\\
 
-        \aelem \order \aelem' &\Leftrightarrow& \forall \lab \in \labset. \;
-        \aelem(\lab) \order \aelem'(\lab)\\
+        (\actxt, \afsenv) \order (\actxt', \afsenv') &\Leftrightarrow&
+        (\actxt \order \actxt') \wedge (\afsenv \order \afsenv')\\
 
-        \aelem \join \aelem' &=& \lambda \lab \in \labset. \; \aelem(\varx) \join
-        \aelem(\lab)\\
+        (\actxt, \afsenv) \join (\actxt', \afsenv') &=&
+        (\actxt \join \actxt', \afsenv \join \afsenv')\\
+
+        \bot &=& (\bot, \bot)\\
+
+        \top &=& (\top, \top)\\
       \end{array}
     \]
-  \item \underline{Abstract Environments}: $\aenvset = \varset \rightarrow
-    \avalset$
+
+  \item \underline{Abstract Calling Contexts}:
+    $\actxtset = \funcset \finmap \powerset{\labset \times \varset}$
+    \[
+      \todo
+      \begin{array}{lcl}
+        \gamma(\actxt) &=& \{ \st \in \stset \mid
+          \st = (\lab', (\lab, \_, \varx) :: \_, \_, \_) \wedge \\&&
+          \phantom{\{ \st \in \stset \mid} (\lab, \varx) \in
+            \actxt(\getfunc(\lab'))
+        \}\\
+
+        \actxt \order \actxt' &\Leftrightarrow&
+        \forall \func \in \funcset. \; \actxt(\func) \subseteq \actxt'(\func)\\
+
+        \actxt \join \actxt' &=&
+        \lambda \func \in \funcset. \; \actxt(\func) \cup \actxt'(\func)\\
+
+        \bot &=& \lambda \func \in \funcset. \; \bot\\
+
+        \top &=& \lambda \func \in \funcset. \; \top\\
+      \end{array}
+    \]
+
+  \item \underline{Flow-Sensitive Abstract Environments}:
+    $\afsenvset = \labset \rightarrow \aenvset$
     \[
       \begin{array}{lcl}
-        \multicolumn{3}{l}{\envgamma: \aenvset \rightarrow \powerset{\stset}}\\
-        \envgamma(\aenv) &=& \{ \st \in \stset \mid \forall \varx \in \varset.
-          \; (\aenv(\varx) = \langle \val, \expr \rangle) \Rightarrow\\ &&
-          \phantom{\{ \st \in \stset \mid} (\sem{\varx}(\st) = \sem{\expr}(\st) =
-          \val) \}\\
+        \gamma(\afsenv) &=& \{ \st \in \stset \mid
+          \st = (\lab, \_, \_, \_) \wedge \st \in \gamma(\afsenv(\lab))
+        \}\\
 
-        \aenv \order \env' &\Leftrightarrow& \forall \varx \in \varset. \;
+        \afsenv \order \afsenv' &\Leftrightarrow&
+        \forall \lab \in \labset. \; \afsenv(\lab) \order \afsenv'(\lab)\\
+
+        \afsenv \join \afsenv' &=&
+        \lambda \lab \in \labset. \; \afsenv(\lab) \join \afsenv'(\lab)\\
+
+        \bot &=& \lambda \lab \in \labset. \; \bot\\
+
+        \top &=& \lambda \lab \in \labset. \; \top\\
+      \end{array}
+    \]
+
+  \item \underline{Abstract Environments}:
+    $\aenvset = \varset \rightarrow \aenvset$
+    \[
+      \begin{array}{lcl}
+        \gamma(\aenv) &=& \{ \st \in \stset \mid
+          \forall \varx \in \varset. \;
+          \sem{\varx}(\st) \in \gamma(\aenv(\varx))
+        \}\\
+
+        \aenv \order \aenv' &\Leftrightarrow&
+        \forall \varx \in \varset. \;
         \aenv(\varx) \order \aenv'(\varx)\\
 
-        \aenv \join \aenv' &=& \lambda \varx \in \varset. \; \aenv(\varx) \join
-        \aenv(\varx)\\
+        \aenv \join \aenv' &=&
+        \lambda \varx \in \varset. \;
+        \aenv(\varx) \join \aenv'(\varx)\\
+
+        \bot &=& \lambda \varx \in \varset. \; \bot\\
+
+        \top &=& \lambda \varx \in \varset. \; \top\\
       \end{array}
     \]
-  \item \underline{Abstract Values}: $\avalset = (\valset \times \exprset)
-    \uplus \{ \top \}$
+
+  \item \underline{Abstract Values}: $\avalset = \valset \uplus \atreeset \uplus
+    \{ \bot, \top \}$
     \[
       \begin{array}{lcl}
-        \multicolumn{3}{l}{\valgamma: \avalset \rightarrow \powerset{\valset}}\\
-        \valgamma(\aval) &=& \left\{
+        \gamma(\aval) &=& \left\{
           \begin{array}{ll}
-            \{ \val \} & \text{if} \; \aval = (\val, \expr) \\
+            \{ \val \} & \text{if} \; \aval = \val\\
+            \gamma(\atree) & \text{if} \; \aval = \atree\\
+            \varnothing & \text{if} \; \aval = \bot\\
             \valset & \text{if} \; \aval = \top\\
@@
 
-        \aval \order \aval' &\Leftrightarrow&
-        \aval' = \top \vee \aval = \aval'\\
+        \aval \order \aval' &\Leftrightarrow& \left\{
+          \begin{array}{ll}
+            \aval = \bot \vee \aval' = \top \vee \aval = \aval' & \vee\\
+            \aval = \atree \wedge \aval' = \atree' \wedge
+            \atree \order \atree' &\vee\\
+            \aval = \tree \wedge \aval' = \atree' \wedge \tree \in
+            \gamma(\atree')\\
+          \end{array}
+        \right.\\
 
@@
           \begin{array}{ll}
-            \aval & \text{if} \; \aval = \aval'\\
+            \aval' & \text{if} \; \aval \order \aval'\\
+            \aval & \text{if} \; \aval \revorder \aval'\\
             \top & \text{otherwise}\\
@@
 \end{itemize}
-An abstract state $\aelem \in \aelemset$ is a mapping from labels to abstract
-environments to represent the shape of states in each label. An abstract
-environment $\aenv \in \aenvset$ is a mapping from variables to abstract values
-to describe values stored in variables.  An abstract value $\aval \in \avalset$
-is a static value $\langle \val, \expr \rangle$ or a dynamic value $\top$.
-Since non-primitive values (e.g., addresses or JavaScript ASTs) cannot be
-directly represented as expressions, each static values $\langle \val, \expr
-\rangle$ also keeps another way to represent itself as an expression. Now, we
-define transformations of expressions and instructions, and introduce an
-iterative algorithm to proceed the partial evaluation in $\ires$.
 
-\subsubsection{Transformation of Expressions} Before defining a transformation of
-expressions, we first define abstract evaluation of expressions as follows:
+An abstract state $\aelem \in \aelemset$ is a pair of an abstract calling
+context and a flow-sensitive abstract environment.  An abstract calling context
+$\actxt \in \actxtset$ is a mapping from functions to return labels and
+variables in their calling contexts. A flow-sensitive abstract environment
+$\afsenv \in \afsenvset$ is a mapping from labels to abstract environments to
+represent the shape of environments in each label. An abstract environment
+$\aenv \in \aenvset$ is a mapping from variables to abstract values to describe
+values stored in variables. An abstract value $\aval \in \avalset$ is a static
+value $\val$, a syntactic view $\atree$, a dynamic value $\top$, or nothing
+$\bot$. Now, we define abstract semantics of expressions, instructions, and
+programs.
+
+\paragraph{Expressions} We first define abstract semantics of expressions as
+follows:
 \[
@@
 \begin{itemize}
-  \item \underline{Primive Values}:
+  \item \underline{Primitive Values}:
     \[
-      \asem{\pval}(\aenv) = \langle \pval, \pval \rangle
+      \asem{\pval}(\aenv) = \pval
     \]
@@
       \begin{array}{l@{~}c@{~}l@{~}l}
-        \asem{\expr_k}(\aenv) &=& \aval_k \; \forall 1 \leq k \leq n
+        \asem{\expr_j}(\aenv) &=& \aval_j \; [\forall 1 \leq j \leq n]
         &\wedge\\
@@
           \begin{array}{ll}
-            \top & \text{if} \; \exists k. \; \aval_k = \top\\
-            \langle \val, \expr' \rangle & \text{if} \; \forall k. \; \aval_k =
-            \langle \val_k, \expr'_k \rangle\\
+            \bot & \text{if} \; \exists j. \; \aval_j = \bot\\
+
+            \op(\val_1, \cdots, \val_n) &
+            \text{if} \; \forall j. \; \aval_j = \val_j\\
+
+            \top & \text{otherwise}\\
           \end{array}
-        \right. &\wedge\\
-        \val &=& \op(\val_1, \cdots, \val_n) &\wedge\\
-        \expr' &=& \op(\expr'_1, \cdots, \expr'_n)\\
+        \right.\\
       \end{array}
@@
           \begin{array}{ll}
-            \langle \tree[k], \expr'_0 \kwsl \expr'_1 \kwsr \rangle & \text{if}
-            \; \aval_0 = \langle \tree, \expr'_0 \rangle \wedge \aval_1 =
-            \langle k, \expr'_1 \rangle\\
+            \tree_j & \text{if} \;
+            \aval_0 = \ty_k \langle \tree_1, \cdots, \tree_n \rangle \wedge
+            \aval_1 = j\\
+
+            \atree_j & \text{if} \;
+            \aval_0 = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
+            \aval_1 = j\\
+
             \top & \text{otherwise}\\
@@
 \end{itemize}
-Then, we define the transformation of expressions as follows:
+
+\paragraph{Instructions} Then, we define the abstract semantics of instructions
+using the abstract semantics of expressions as follows:
 \[
-  \framebox{$\transforme: \exprset \times \aenvset \rightarrow \exprset \times
-  \avalset$}
+  \todo
+  \framebox{$\asem{\inst}: \labset \times \aenvset \rightarrow \aelemset
+  \rightarrow \aelemset$}
 \]
+\begin{itemize}
+  \item \underline{Variable Assignments}:
     \[
-  \transforme(\expr, \aenv) = (\expr'', \aval)
+      \asem{\varx = \expr}(\lab, \aenv) =
+      (\bot[\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]], \bot)
+    \]
+    where $\aval = \asem{\expr}(\aenv)$
+
+  \item \underline{Field Assignments}:
+    \[
+      \asem{\expr_0 \kwsl \expr_1 \kwsr = \expr_2}(\lab, \aenv) =
+      (\bot[\getnext(\lab) \mapsto \aenv], \bot)
+    \]
+  \item \underline{Object Allocations}:
+    \[
+      \asem{\varx = \kwcl \kwcr}(\lab, \aenv) =
+      (\bot[\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]], \bot)
+    \]
+
+  \item \underline{Function Calls}:
+    \[
+      \asem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\lab, \aenv) =
+      \text{\todo extensible target functions}
     \]
@@
       \begin{array}{l@{~}c@{~}ll}
-    \aval &=& \asem{\expr}(\aenv) &\wedge\\
-    \expr'' &=& \left\{
-      \begin{array}{ll}
-        \pval & \text{if} \; \aval = \langle \pval, \_ \rangle\\
-        \expr' & \text{if} \; \aval = \langle \_, \expr' \rangle\\
-        \expr & \text{otherwise}\\
-      \end{array}
-    \right.\\
-  \end{array}
-\]
-
-\subsubsection{Transformation of Instructions} Now, we define a transformation
-of instructions using the transformation of expressions as follows:
-\[
-  \framebox{$\transformi: \instset \times \aenvset \rightarrow \instset \times
-  \aenvset$}
-\]
-\begin{itemize}
-  \item \underline{Variable Assignments}:
-    \[
-      \transformi(\varx = \expr, \aenv) =
-      (\varx = \expr', \aenv[\varx \mapsto \aval])
-    \]
-    where
-    \[
-      (\expr', \aval) = \transforme(\expr, \aenv)
-    \]
-
-  \item \underline{Field Assignments}:
-    \[
-      \transformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
-      (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
-    \]
-    where
-    \[
-      \begin{array}{l@{~}c@{~}ll}
-        (\expr'_0, \_) = \transforme(\expr_0, \aenv) &\wedge\\
-        (\expr'_1, \_) = \transforme(\expr_1, \aenv) &\wedge\\
-        (\expr'_2, \_) = \transforme(\expr_2, \aenv)\\
-      \end{array}
-    \]
-  \item \underline{Object Allocations}:
-    \[
-      \transformi(\varx = \kwcl \kwcr, \aenv) =
-      (\varx = \kwcl \kwcr, \aenv[\varx \mapsto \top])
-    \]
-
-  \item \underline{Function Calls}:
-    \[
-      \transformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
-      (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
-      \aenv[\varx \mapsto \top])
-    \]
-    where
-    \[
-      \begin{array}{l@{~}c@{~}ll}
-        (\expr', \_) = \transforme(\expr, \aenv) &\wedge\\
-        (\expr'_k, \_) = \transforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
-        n\\
+        \aval' = \asem{\expr}(\aenv) &\wedge\\
+        (\expr'_j, \_) = \transforme(\expr_j, \aenv) \; [\forall 1 \leq j \leq
+        n]\\
       \end{array}
@@
     \[
-      \transformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
+      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv} =
       (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
@@
     \[
-      \transformi(\kwret \; \expr, \aenv) =
+      \asem{\kwret \; \expr, \aenv} =
       (\kwret \; \expr, \aenv)
@@
 
-\subsubsection{Fixpoint of Abstract Transfer Function} Finally, we define an
-abstract transfer function and its fixpoint to represent abstract semantics of a
-given function and abstract values:
-\[
-  \begin{array}{ll}
-    \text{Abstract Transfer Function} & \atransfer: \aelemset \rightarrow
-    \aelemset\\
-\end{array}
-\]
+% \paragraph{Transformation of Programs} Finally, we define the transformation
+% of programs as the least fixed point of the abstract transfer function:
+% \[
+%   \transform(\prog, (\func, (\aval_1, \cdots, \aval_n))) = \lfp \; \atransfer =
+%   \lim_{n \rightarrow \infty}(\atransfer)^n(\prog, \iaelem)
+% \]
+% where
+% \begin{itemize}
+%   \item \underline{Abstract Transfer Function}: $\atransfer: \progset \times
+%     \aelemset \rightarrow \progset \times \aelemset$
+%     \[
+%       \atransfer(\prog, \aelem) = \lambda \lab \in \labset. \; \bigjoin_{\lab' \in
+%       \labset}{\todo}
+%     \]
+%     where
+%     \[
+%     \]
+%   \item \underline{Initial Abstract State}: $\iaelem \in \elemset$
+%     \[
+%       \iaelem = \todo
+%     \]
+% \end{itemize}
+% 
+% \todo
+
+\subsubsection{Transformations}
 
@@
 
-\subsection{Proof of Semantics Preservation}
+% \[
+%   \framebox{$\transforme: \exprset \times \aenvset \rightarrow \exprset \times
+%   \avalset$}
+% \]
+% \[
+%   \transforme(\expr, \aenv) = (\expr'', \aval)
+% \]
+% where
+% \[
+%   \begin{array}{l@{~}c@{~}ll}
+%     \aval &=& \asem{\expr}(\aenv) &\wedge\\
+%     \expr'' &=& \left\{
+%       \begin{array}{ll}
+%         \pval & \text{if} \; \aval = \langle \pval, \_ \rangle\\
+%         \expr' & \text{if} \; \aval = \langle \_, \expr' \rangle\\
+%         \expr & \text{otherwise}\\
+%       \end{array}
+%     \right.\\
+%   \end{array}
+% \]
+
+% \[
+%   \framebox{$\transformi: \instset \times \aenvset \rightarrow \instset \times
+%   \aenvset$}
+% \]
+% \begin{itemize}
+%   \item \underline{Variable Assignments}:
+%     \[
+%       \transformi(\varx = \expr, \aenv) =
+%       (\varx = \expr', \aenv[\varx \mapsto \aval])
+%     \]
+%     where
+%     \[
+%       (\expr', \aval) = \transforme(\expr, \aenv)
+%     \]
+% 
+%   \item \underline{Field Assignments}:
+%     \[
+%       \transformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
+%       (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
+%     \]
+%     where
+%     \[
+%       \begin{array}{l@{~}c@{~}ll}
+%         (\expr'_0, \_) = \transforme(\expr_0, \aenv) &\wedge\\
+%         (\expr'_1, \_) = \transforme(\expr_1, \aenv) &\wedge\\
+%         (\expr'_2, \_) = \transforme(\expr_2, \aenv)\\
+%       \end{array}
+%     \]
+%   \item \underline{Object Allocations}:
+%     \[
+%       \transformi(\varx = \kwcl \kwcr, \aenv) =
+%       (\varx = \kwcl \kwcr, \aenv[\varx \mapsto \top])
+%     \]
+% 
+%   \item \underline{Function Calls}:
+%     \[
+%       \transformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
+%       (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
+%       \aenv[\varx \mapsto \top])
+%     \]
+%     where
+%     \[
+%       \begin{array}{l@{~}c@{~}ll}
+%         (\expr', \_) = \transforme(\expr, \aenv) &\wedge\\
+%         (\expr'_k, \_) = \transforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
+%         n\\
+%       \end{array}
+%     \]
+% 
+%   \item \underline{Branches}:
+%     \[
+%       \transformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
+%       (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
+%     \]
+%     where
+%     \[
+%       (\expr', \_) = \transforme(\expr, \aenv)
+%     \]
+% 
+%   \item \underline{Returns}:
+%     \[
+%       \transformi(\kwret \; \expr, \aenv) =
+%       (\kwret \; \expr, \aenv)
+%     \]
+%     where
+%     \[
+%       (\expr', \_) = \transforme(\expr', \aenv)
+%     \]
+% \end{itemize}
+
+\subsubsection{Cleanup Algorithm}
+
+\todo
+
+\begin{itemize}
+  \item perform a syntactic def-use analysis
+  \item remove unnecessary variable assignments
+  \item remove unreachable instructions
+\end{itemize}
+
+\subsubsection{Proof of Semantics Preservation}
 
@@
 
-\subsubsection{Syntatic Views} A syntatic view $\atree \in \atreeset$ is an
-augmented JavaScript ASTs with abstract nodes $\top$ as follows:
-\[
-  \atree ::= \str \mid \ty_k \langle \atree^* \rangle \mid \top
-\]
-\[
-  \begin{array}{lcl}
-    \multicolumn{3}{l}{\treegamma: \atreeset \rightarrow \powerset{\treeset}}\\
-    \treegamma(\atree) &=& \left\{
-      \begin{array}{ll}
-        \{ \str \} &
-        \text{if} \; \atree = \str \\
-
-        A & \text{if} \; \atree = \ty_k
-        \langle \atree_1, \cdots, \atree_n \rangle \\
-
-        \treeset & \atree = \top\\
-      \end{array}
-    \right.\\
-    A &=& \{ \ty_k \langle \tree_1, \cdots, \tree_n \rangle \mid \forall 1 \leq
-    j \leq n.  \; \tree_j \in \treegamma(\atree_j) \}
-  \end{array}
-\]
-
-\subsubsection{JavaScript Program Filtering}
-
-\[
-  \atree \subtree \tree' \iff \exists \tree \in \treegamma{\atree}. \; \tree
-  \subtree \tree'
-\]
-
-\todo
-
 \subsubsection{Semantics Specialization}

### 2021-10-28 paper/pldi22/formal.tex
Target function / abstract arguments in static analysis

@@
 
-To define static analysis of $\ires$ programs, we first define abstract domains
-of states, calling contexts, environments, and values as follows:
+To define static analysis of $\ires$ programs, we first define target function
+and its abstract arguments based on a given syntactic view $\atree$.  Since only
+non-leaf nodes has single evaluation functions, we assume that $\atree = \ty_k
+\langle \atree_1, \cdots, \atree_n \rangle$.  Then, the target function and its
+abstract arguments are defined as follows:
+\[
+  \begin{array}{ll@{~}c@{~}l}
+    \text{Target Function} & \targetfunc &=& \ty_k.\eval\\
+
+    \text{Abstract Arguments} &
+    [\aval_0, \cdots, \aval_m] &=&
+    [\atree, \atree_{i_1}, \cdots, \atree_{i_m}]\\
+  \end{array}
+\]
+where $m$ denotes the number of nonterminal subtrees of $\atree$ and
+$\atree_{i_j}$ denotes $j$-th one for each $1 \leq i \leq m$.  The abstract
+domains of states, calling contexts, environments, and values are defined as
+follows:
 \begin{itemize}
@@
 
-  \item \underline{Abstract Calling Contexts}:
+  \item \todo \underline{Abstract Calling Contexts}:
+    % \powerset{\labset \times \funcset}
     $\actxtset = \funcset \finmap \powerset{\labset \times \varset}$
     \[
-      \todo
       \begin{array}{lcl}

### 2021-11-01 paper/pldi22/formal.tex
Refined formalization

--- 2021-10-27 paper/pldi22/formal.tex
@@
 
-We first define $\ires$ as a specification language to describe JavaScript
-semantics.
+In this section, we introduce a JavaScript semantics specialization with
+syntactic views.  We first introduce $\ires$ as a specification language to
+describe JavaScript semantics. To provide options to select target semantics, we
+also introduce syntactic views as an abstraction of JavaScript ASTs.  Then, we
+define a JavaScript semantics specialization with syntactic views as a partial
+evaluation of $\ires$ programs, which is a combination of static analysis and
+program transformation. Finally, we prove the semantics preservation of the
+partial evaluation.
 
@@
     \text{Instructions} & \instset &\ni& \inst &::=&
-    \refer = \expr \mid
-    \varx = \kwcl \kwcr \mid
-    \varx = \expr \kwrl \expr^* \kwrr \mid \\&&&&&
+    \refer \kweq \expr \mid
+    \varx \kweq \kwcl \kwcr \mid
+    \varx \kweq \expr \kwrl \expr^* \kwrr \mid \\&&&&&
     \kwif \; \expr \; \lab \; \lab \mid
@@
 or captured variables exist in this paper.  An instruction $\inst \in \instset$
-is an assignment $\refer = \expr$, an object allocation $\varx = \kwcl \kwcr$, a
-function call $\varx = \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
+is an assignment $\refer \kweq \expr$, an object allocation $\varx \kweq \kwcl \kwcr$, a
+function call $\varx \kweq \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
 \lab \; \lab$, or a return instruction $\kwret \; \expr$.  An invocation of an
@@
 
-Since $\ires$ is a specification language for JavaScript, it treats JavaScript
-ASTs $\treeset$ as its values. For presentation brevity, we represent a JavaScript
-AST as follows:
+$\ires$ is a specification language for JavaScript that treats JavaScript ASTs
+as its values. To handle JavaScript ASTs in $\ires$, we define them with tree
+nodes $\nodeset$ as follows:
 \[
-  \tree ::= \term{\str} \mid \ty_k \langle \tree^* \rangle
+  \begin{array}{l@{~}c@{~}l@{~}c@{~}l}
+    \treeset &\ni& \tree &::=& \ty_k \langle \node^* \rangle\\
+    \nodeset &\ni& \node &::=& \str \mid \tree\\
+  \end{array}
 \]
-A leaf node $\term{\str}$ defined with a string $\str$ denotes a terminal
-symbol, and a non-leaf node $\ty_k \langle \tree^* \rangle$ denotes $k$-th
-alternative in the syntactic production of nonterminal symbol $\ty$ with its
-subtrees $\tree^*$.  The notation $\ty_k.\eval$ denotes an $\ires$ function for
-the evaluation of $k$-th alternative in $\ty$, and it takes the AST itself and
-its nonterminal subtrees as arguments. If an AST $\tree$ is a subtree of another
-AST $\tree'$, we represent it as $\tree \subtree \tree'$.  For example,
+A JavaScript AST $\ty_k \langle \node_1, \cdots, \node_n \rangle$ denotes $k$-th
+alternative in the syntactic production of nonterminal symbol $\ty$ with
+multiple tree nodes $\node_1, \cdots, \node_n$.  A tree node is a string for a
+terminal symbol or another tree for a nonterminal symbol. We define several
+notations to easily deal with JavaScript ASTs.  The notation $\ty_k.\eval$ denotes
+an \esalg{Evaluation} function of $k$-th alternative in the production $\ty$.
+Similarly, the notation $\tree.\eval$ denotes the \esalg{Evaluation} function of
+the AST $\tree$, and it is same with $\ty_k.\eval$ when $\tree = \ty_k \langle
+\cdots \rangle$. The \esalg{Evaluation} of each AST takes the AST itself and its
+tree nodes that are nonterminals as arguments.  The notation $\getsubs(\tree)$
+denotes tree nodes that are subtrees of $\tree$.  For example,
 Figure~\ref{fig:coalesce-prod} shows a syntactic production for coalesce
-expressions.  Consider the following coalesce expression:
+expressions.  Consider the following JavaScript coalesce expression:
 \begin{lstlisting}[style=JS]
@@
 Then, the following AST is produced as its parsing result:
+\[
+  \begin{array}{lcl}
+    \tree_0 &=&
+    \essyn{CoalesceExpression}_0 \langle \tree_1, \code{"??"}, \tree_2 \rangle\\
+
+    \tree_1 &=&
+    \essyn{CoalesceExpressionHead}_1 \langle \tree_3 \rangle\\
+
+    \tree_2 &=&
+    \essyn{BitwiseORExpression}_0 \langle \cdots \rangle\\
+
+    \tree_3 &=&
+    \essyn{BitwiseORExpression}_0 \langle \cdots \rangle\\
+  \end{array}
+\]
 \begin{figure}[H]
@@
 \end{figure}
-\noindent Its evaluation function $\nterm{CoalesceExpression}_0.\eval$ takes
-three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and $\tree_2$ in
-the figure. Note that $\tree_1$ and $\tree_2$ are subtrees of $\tree_0$ (i.e.,
-$\tree_1 \subtree \tree_0$ and $\tree_2 \subtree \tree_0$).
+\noindent Its \esalg{Evaluation} function $\essyn{CoalesceExpression}_0.\eval$
+takes three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and
+$\tree_2$ in the figure. The ASTs $\tree_0$, $\tree_1$, $\tree_2$, and $\tree_3$
+are subtrees of $\tree_0$ (i.e., $\tree_0 \subtree \tree_0, \cdots, \tree_3
+\subtree \tree_0$), and $\getsubs(\tree_0) = [\tree_1, \tree_2] \wedge
+\getsubs(\tree_1) = [\tree_3]$.
 
@@
 \st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
-\st'$. Now, we define the denotational semantics of expressions, instructions,
-and functions.
+\st'$. Another way to represent the concrete semantics is to define a transfer
+function $\transfer: \powerset{\stset} \rightarrow \powerset{\stset}$:
+\[
+  \sem{\prog} = \lim_{n \rightarrow \infty}\transfer^n(\istset)
+\]
+where $\transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans \st' \}$.  Now,
+we define the denotational semantics of expressions, instructions, and
+functions.
 
@@
     \[
-      \sem{\varx = \expr}(\st) =
+      \sem{\varx \kweq \expr}(\st) =
       (\getnext(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
@@
     \[
-      \sem{\expr_0 \kwsl \expr_1 \kwsr = \expr_2}(\st) =
+      \sem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\st) =
       (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
@@
     \[
-      \sem{\varx = \kwcl \kwcr}(\st) =
-      (\lab, \ctxts, \heap[\addr \mapsto \epsilon], \env[\varx \mapsto
+      \sem{\varx \kweq \kwcl \kwcr}(\st) =
+      (\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env[\varx \mapsto
       \addr])
@@
     where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
-    \text{Domain}(\heap)$ and $\epsilon$ denotes an empty object.
+    \text{Domain}(\heap)$
 
@@
     \[
-      \sem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
+      \sem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
       (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
@@
       \begin{array}{l@{~}c@{~}ll}
-        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varp_1, \cdots, \varp_n
+        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varx_1, \cdots, \varx_n
         \kwrr \; \lab_\varf) &\wedge\\
@@
         \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
-        \env' &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n]
+        \env' &=& [\varx_1 \mapsto \val_1, \cdots, \varx_n \mapsto \val_n]
         &\wedge\\
@@
 
-\subsection{Syntactic Views} A syntactic view $\atree \in \atreeset$ is an
-augmented JavaScript ASTs with abstract nodes $\treetop$:
+\subsection{Syntactic Views}
+
+A syntactic view $\atree \in \atreeset$ is an abstract JavaScript AST with
+abstract tree nodes $\anodeset$:
 \[
-  \atree ::= \term{\str} \mid \ty_k \langle \atree^* \rangle \mid \treetop
+  \begin{array}{l@{~}c@{~}l@{~}c@{~}l}
+    \atreeset &\ni& \atree &::=& \ty_k \langle \anode^* \rangle \mid \ty\\
+    \anodeset &\ni& \anode &::=& \str \mid \atree\\
+  \end{array}
 \]
-and its concretization is defined as follows:
+where $\ty$ denotes all ASTs whose nonterminal symbol $\ty$. We define the
+concretization of abstract trees $\atreegamma: \atreeset \rightarrow
+\powerset{\treeset}$ and that of abstract nodes $\anodegamma: \anodeset
+\rightarrow \powerset{\nodeset}$ as follows:
 \[
   \begin{array}{lcl}
-    \gamma(\term{\str}) &=&
-    \{ \term{\str} \}\\
+    \atreegamma(\ty_k \langle \anode_1, \cdots, \anode_n \rangle) &=&
+    \{ \ty_k \langle \node_1, \cdots, \node_n \rangle \mid \node_j \in
+    \anodegamma(\anode_j) \}\\
 
-    \gamma(\ty_k \langle \atree_1, \cdots, \atree_n \rangle) &=&
-    \{ \ty_k \langle \tree_1, \cdots, \tree_n \rangle \mid \tree_j \in
-    \gamma(\atree_j) \}\\
+    \atreegamma(\ty) &=&
+    \{ \tree \in \treeset \mid \tree = \ty_k \langle \cdots \rangle \}\\
 
-    \gamma(\treetop) &=& \treeset\\
+    \anodegamma(\str) &=& \{ \str \}\\
+
+    \anodegamma(\atree) &=& \atreegamma(\atree)\\
   \end{array}
 \]
-The partial order and join operator between abstract trees are defined as
-follows:
+% \[
+%   \begin{array}{lcl}
+%     \anode \order \anode' &\Leftrightarrow& \left\{
+%       \begin{array}{ll}
+%         \anode = \anode' &\vee\\
+% 
+%         \anode' = \ty &\vee\\
+% 
+%         (\anode = \atree \wedge \anode' = \atree' \wedge \atree \order
+%         \atree')\\
+%       \end{array}
+%     \right.\\
+% 
+%     \atree \order \atree' &\Leftrightarrow& \left\{
+%       \begin{array}{ll}
+%         \atree = \atree' &\vee\\
+% 
+%         \atree' = \treetop &\vee\\
+% 
+%         \begin{array}{@{}l@{}}
+%           \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
+%           \atree' = \ty_k \langle \atree'_1, \cdots, \atree'_n \rangle \wedge\\
+%           \forall j. \; \tree_j \order \tree'_j\\
+%         \end{array}\\
+%       \end{array}
+%     \right.\\
+% 
+%     \atree \join \atree' &=& \left\{
+%       \begin{array}{ll}
+%         \atree' & \text{if} \; \atree \order \atree'\\
+% 
+%         \atree & \text{if} \; \atree \revorder \atree'\\
+% 
+%         \ty_k \langle \atree''_1, \cdots, \atree''_n \rangle &
+%         \text{if} \; \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle
+%         \wedge\\&
+%         \phantom{\text{if} \;} \atree = \ty_k \langle \atree_1, \cdots, \atree_n
+%         \rangle \wedge\\&
+%         \phantom{\text{if} \;} \forall j. \; \atree''_j = \atree_j
+%         \join \atree'_j\\
+%         \treetop & \text{otherwise}\\
+%       \end{array}
+%     \right.\\
+%   \end{array}
+% \]
+Moreover, we define abstract subtree relation $\asubtree \subseteq \atreeset
+\times \treeset$:
 \[
-  \begin{array}{lcl}
-    \atree \order \atree' &\Leftrightarrow& \left\{
-      \begin{array}{ll}
-        \atree = \atree' &\vee\\
-
-        \atree' = \treetop &\vee\\
-
-        \begin{array}{@{}l@{}}
-          \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
-          \atree' = \ty_k \langle \atree'_1, \cdots, \atree'_n \rangle \wedge\\
-          \forall j. \; \tree_j \order \tree'_j\\
-        \end{array}\\
-      \end{array}
-    \right.\\
-
-    \atree \join \atree' &=& \left\{
-      \begin{array}{ll}
-        \atree' & \text{if} \; \atree \order \atree'\\
-
-        \atree & \text{if} \; \atree \revorder \atree'\\
-
-        \ty_k \langle \atree''_1, \cdots, \atree''_n \rangle &
-        \text{if} \; \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle
-        \wedge\\&
-        \phantom{\text{if} \;} \atree = \ty_k \langle \atree_1, \cdots, \atree_n
-        \rangle \wedge\\&
-        \phantom{\text{if} \;} \forall j. \; \atree''_j = \atree_j
-        \join \atree'_j\\
-        \treetop & \text{otherwise}\\
-      \end{array}
-    \right.\\
-  \end{array}
+  \atree \; \asubtree \; \tree' \iff \exists \tree \in \atreegamma(\atree). \;
+  \tree \subtree \tree'
 \]
-Moreover, we can filter out JavaScript programs using the subtree relation with
-syntactic views:
-\[
-  \atree \subtree \tree' \iff \exists \tree \in \gamma(\atree). \; \tree
-  \subtree \tree'
-\]
+to filter out JavaScript programs not related to a given syntactic view.
+Similar to $\getsubs(\tree)$, an abstract helper function $\agetsubs(\atree)$
+denotes abstract tree nodes that are syntactic views when $\atree = \ty_k
+\langle \cdots \rangle$.
 
@@
 \[
-  \peval{\prog}(\atree) = \transform(\prog, \asem{\prog}(\atree))
+  \peval{\prog}(\atree) = \transform{\prog} \circ \asem{\prog} (\atree)
 \]
 It takes a syntactic view $\atree \in \atreeset$ to restrict arguments of the
-corresponding evaluation function. Then, it performs a static analysis
-$\asem{-}$ of a given program $\prog$ with the static part $\atree$ and
-transforms it using $\transform$ with the analysis result
-$\asem{\prog}(\atree)$ to produce a new specialized $\ires$ program.  Now, we
+corresponding \esalg{Evaluation} function. Then, it performs a static analysis
+$\asem{-}$ of a given program $\prog$ with the syntactic view $\atree$ and
+transforms the program using $\transform{-}$ with the analysis result
+$\asem{\prog}(\atree)$ to produce a specialized $\ires$ program.  Since the
+\esalg{Evaluation} of $\ty$ might one or more $\ires$ functions, we only define
+the partial evaluation when $\atree = \ty_k \langle \cdots \rangle$.  Now, we
 define the static analysis and program transformation of $\ires$ programs and
@@
 
-To define static analysis of $\ires$ programs, we first define abstract domains
-of states, calling contexts, environments, and values as follows:
+The static analysis $\asem{\prog}(\atree)$ performs an abstract
+interpretation~\cite{ai1977, ai1992} to abstract concrete semantics under the
+given given syntactic view $\atree$.  We first define abstract domains of
+states, calling contexts, environments, and values as follows:
 \begin{itemize}
   \item \underline{Abstract States}:
-    $\aelemset = \actxtset \times \afsenvset$
+    $\aelemset = \amctxtset \times \atctxtset \times \afsenvset$
     \[
       \begin{array}{lcl}
-        \gamma(\afsenv, \actxt) &=& \gamma(\actxt) \cap
-        \gamma(\afsenv)\\
+        \aelemgamma(\amctxt, \atctxt, \afsenv) &=&
+        \amctxtgamma(\amctxt) \cup
+        (\atctxtgamma(\atctxt) \cap \afsenvgamma(\afsenv))\\
 
-        (\actxt, \afsenv) \order (\actxt', \afsenv') &\Leftrightarrow&
-        (\actxt \order \actxt') \wedge (\afsenv \order \afsenv')\\
+        (\amctxt, \atctxt, \afsenv) \order
+        (\amctxt', \atctxt', \afsenv') &\Leftrightarrow&
+        (\amctxt \order \amctxt') \wedge
+        (\atctxt \order \atctxt') \wedge
+        (\afsenv \order \afsenv')\\
 
-        (\actxt, \afsenv) \join (\actxt', \afsenv') &=&
-        (\actxt \join \actxt', \afsenv \join \afsenv')\\
-
-        \bot &=& (\bot, \bot)\\
-
-        \top &=& (\top, \top)\\
+        (\amctxt, \atctxt, \afsenv) \join (\amctxt', \atctxt', \afsenv') &=&
+        (\amctxt \join \amctxt', \atctxt \join \atctxt', \afsenv \join \afsenv')\\
       \end{array}
@@
 
-  \item \underline{Abstract Calling Contexts}:
-    $\actxtset = \funcset \finmap \powerset{\labset \times \varset}$
+  \item \underline{Merged Calling Contexts}:
+    $\amctxtset = \powerset{\labset}$
     \[
-      \todo
       \begin{array}{lcl}
-        \gamma(\actxt) &=& \{ \st \in \stset \mid
-          \st = (\lab', (\lab, \_, \varx) :: \_, \_, \_) \wedge \\&&
-          \phantom{\{ \st \in \stset \mid} (\lab, \varx) \in
-            \actxt(\getfunc(\lab'))
+        \amctxtgamma(\amctxt) &=& \{ \st \in \stset \mid
+          \st = (\lab, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&
+
+          \phantom{\{ \st \in \stset \mid}
+          \exists 1 \leq j \leq n. \; \ctxt_j = (\lab_j, \_, \_) \wedge\\&&
+
+          \phantom{\{ \st \in \stset \mid}
+          \lab_j \in \amctxt
         \}\\
 
-        \actxt \order \actxt' &\Leftrightarrow&
-        \forall \func \in \funcset. \; \actxt(\func) \subseteq \actxt'(\func)\\
+        \amctxt \order \amctxt' &\Leftrightarrow&
+        \amctxt \subseteq \amctxt\\
 
-        \actxt \join \actxt' &=&
-        \lambda \func \in \funcset. \; \actxt(\func) \cup \actxt'(\func)\\
+        \amctxt \join \amctxt' &=&
+        \amctxt \cup \amctxt\\
+      \end{array}
+    \]
 
-        \bot &=& \lambda \func \in \funcset. \; \bot\\
+  \item \underline{Target Calling Contexts}:
+    $\atctxtset = \powerset{\labset \times \funcset}$
+    \[
+      \begin{array}{lcl}
+        \atctxtgamma(\atctxt) &=& \{ \st \in \stset \mid
+          \st = (\lab_0, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&
 
-        \top &=& \lambda \func \in \funcset. \; \top\\
+          \phantom{\{ \st \in \stset \mid}
+          \forall 1 \leq j \leq n. \; \ctxt_j = (\lab_j, \_, \_) \wedge\\&&
+
+          \phantom{\{ \st \in \stset \mid}
+          \exists 0 \leq m \leq n. \; \getfunc(\lab_m) = \ty_k.\eval \wedge\\&&
+
+          \phantom{\{ \st \in \stset \mid}
+          \forall 1 \leq j \leq m. \; (\lab_j, \getfunc{\lab_{j-1}}) \in \atctxt
+        \}\\
+
+        \atctxt \order \atctxt' &\Leftrightarrow& \atctxt \subseteq \atctxt\\
+
+        \atctxt \join \atctxt' &=& \atctxt \cup \atctxt'\\
       \end{array}
@@
       \begin{array}{lcl}
-        \gamma(\afsenv) &=& \{ \st \in \stset \mid
-          \st = (\lab, \_, \_, \_) \wedge \st \in \gamma(\afsenv(\lab))
+        \afsenvgamma(\afsenv) &=& \{ \st \in \stset \mid
+          \st = (\lab, \_, \_, \_) \wedge \st \in \aenvgamma(\afsenv(\lab))
         \}\\
@@
         \lambda \lab \in \labset. \; \afsenv(\lab) \join \afsenv'(\lab)\\
-
-        \bot &=& \lambda \lab \in \labset. \; \bot\\
-
-        \top &=& \lambda \lab \in \labset. \; \top\\
       \end{array}
@@
       \begin{array}{lcl}
-        \gamma(\aenv) &=& \{ \st \in \stset \mid
+        \aenvgamma(\aenv) &=& \{ \st \in \stset \mid
           \forall \varx \in \varset. \;
-          \sem{\varx}(\st) \in \gamma(\aenv(\varx))
+          \sem{\varx}(\st) \in \avalgamma(\aenv(\varx))
         \}\\
@@
         \aenv(\varx) \join \aenv'(\varx)\\
-
-        \bot &=& \lambda \varx \in \varset. \; \bot\\
-
-        \top &=& \lambda \varx \in \varset. \; \top\\
       \end{array}
@@
   \item \underline{Abstract Values}: $\avalset = \valset \uplus \atreeset \uplus
-    \{ \bot, \top \}$
+    \{ \top, \bot,  \}$
     \[
       \begin{array}{lcl}
-        \gamma(\aval) &=& \left\{
+        \avalgamma(\aval) &=& \left\{
           \begin{array}{ll}
             \{ \val \} & \text{if} \; \aval = \val\\
-            \gamma(\atree) & \text{if} \; \aval = \atree\\
+            \atreegamma(\atree) & \text{if} \; \aval = \atree\\
+            \valset & \text{if} \; \aval = \top\\
             \varnothing & \text{if} \; \aval = \bot\\
-            \valset & \text{if} \; \aval = \top\\
           \end{array}
@@
             \aval = \tree \wedge \aval' = \atree' \wedge \tree \in
-            \gamma(\atree')\\
+            \atreegamma(\atree')\\
           \end{array}
@@
 
-An abstract state $\aelem \in \aelemset$ is a pair of an abstract calling
-context and a flow-sensitive abstract environment.  An abstract calling context
-$\actxt \in \actxtset$ is a mapping from functions to return labels and
-variables in their calling contexts. A flow-sensitive abstract environment
-$\afsenv \in \afsenvset$ is a mapping from labels to abstract environments to
-represent the shape of environments in each label. An abstract environment
-$\aenv \in \aenvset$ is a mapping from variables to abstract values to describe
-values stored in variables. An abstract value $\aval \in \avalset$ is a static
-value $\val$, a syntactic view $\atree$, a dynamic value $\top$, or nothing
-$\bot$. Now, we define abstract semantics of expressions, instructions, and
-programs.
+An abstract state $\aelem \in \aelemset$ is a triple of a merged and target call
+edges and a flow-sensitive abstract environment.  A merged calling context
+$\amctxt \in \amctxtset$ is a set of call labels representing merged function
+calls. A target calling context $\atctxt \in \atctxtset$ is a set of possible
+static call edges from labels to function, and it represents the scope of static
+analysis. To more precisely represent states in target calling contexts, we
+define a flow-sensitive abstract environment $\afsenv \in \afsenvset$. It is
+a mapping from labels to abstract environments to represents the shape of
+environments in each label. An abstract environment $\aenv \in \aenvset$ is a
+mapping from variables to abstract values to describe values stored in
+variables. An abstract value $\aval \in \avalset$ is a static value $\val$, a
+syntactic view $\atree$, a dynamic value $\top$, or nothing $\bot$.  Now, we
+define abstract semantics of expressions, instructions, and programs.
 
@@
 \paragraph{Instructions} Then, we define the abstract semantics of instructions
-using the abstract semantics of expressions as follows:
+as follows:
 \[
-  \todo
-  \framebox{$\asem{\inst}: \labset \times \aenvset \rightarrow \aelemset
-  \rightarrow \aelemset$}
+  \framebox{$\asem{\inst}: \amctxtset \times \atctxtset \times \labset \times
+    \aenvset \rightarrow
+  \aelemset$}
 \]
@@
     \[
-      \asem{\varx = \expr}(\lab, \aenv) =
-      (\bot[\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]], \bot)
+      \asem{\varx \kweq \expr}(\amctxt, \atctxt, \lab, \aenv) =
+      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]])
     \]
@@
     \[
-      \asem{\expr_0 \kwsl \expr_1 \kwsr = \expr_2}(\lab, \aenv) =
-      (\bot[\getnext(\lab) \mapsto \aenv], \bot)
+      \asem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\amctxt, \atctxt, \lab, \aenv) =
+      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv])
     \]
+
   \item \underline{Object Allocations}:
     \[
-      \asem{\varx = \kwcl \kwcr}(\lab, \aenv) =
-      (\bot[\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]], \bot)
+      \asem{\varx \kweq \kwcl \kwcr}(\amctxt, \atctxt, \lab, \aenv) =
+      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]])
     \]
@@
     \[
-      \asem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\lab, \aenv) =
-      \text{\todo extensible target functions}
+      \asem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\amctxt,
+      \atctxt, \lab, \aenv) = (\amctxt', \atctxt', \afsenv)
     \]
@@
       \begin{array}{l@{~}c@{~}ll}
-        \aval' = \asem{\expr}(\aenv) &\wedge\\
-        (\expr'_j, \_) = \transforme(\expr_j, \aenv) \; [\forall 1 \leq j \leq
+        \aval &=& \asem{\expr}(\aenv) &\wedge\\
+        \aval_j &=& \asem{\expr_j}(\aenv) \; [\forall 1 \leq j \leq n] &\wedge\\
+        (\amctxt', \atctxt') &=& \left\{
+          \begin{array}{ll}
+            (\amctxt, \atctxt \cup \{ (\lab, \func) \} &
+            \text{if} \; \aval = \func \wedge \exists j. \; \aval_j \neq \top\\
+
+            (\amctxt \cup \{ \lab \}, \atctxt) &
+            \text{otherwise}
+          \end{array}
+        \right.\\
+        \afsenv &=& [ \lab_\func \mapsto \aenv_\func \mid
+        (\lab, \func) \in \atctxt' \wedge\\&&
+
+        \phantom{[\lab_\func \mapsto \aenv_\func \mid \;}
+        \func = \kwdef \; \kwrl \varx_1, \cdots, \varx_n \kwrr
+        \; \lab_\func \wedge\\&&
+
+        \phantom{[\lab_\func \mapsto \aenv_\func \mid \;}
+        \aenv_\func = [\varx_1 \mapsto \aval_1, \cdots,
+        \varx_n \mapsto \aval_n] ]\\
+      \end{array}
+    \]
+
+  \item \underline{Branches}:
+    \[
+      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\amctxt, \atctxt, \lab, \aenv) =
+      (\amctxt, \atctxt, \afsenv')
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aval &=& \asem{\expr}(\aenv)\\
+
+        \afsenv &=& \left\{
+          \begin{array}{ll}
+            [\lab_\vart \mapsto \aenv] & \text{if} \; \true \in
+            \avalgamma(\aval)\\
+            \varnothing & \text{otherwise}\\
+          \end{array}
+        \right.\\
+
+        \afsenv' &=& \left\{
+          \begin{array}{ll}
+            \afsenv[\lab_\varf \mapsto \aenv] & \text{if} \; \false \in
+            \avalgamma(\aval)\\
+            \afsenv & \text{otherwise}\\
+          \end{array}
+        \right.\\
+      \end{array}
+    \]
+
+  \item \underline{Returns}:
+    \[
+      \asem{\kwret \; \expr}(\amctxt, \atctxt, \lab_0, \aenv) =
+      (\amctxt, \atctxt, \afsenv)
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aval &=& \asem{\expr'}(\aenv)\\
+
+        \func &=& \getfunc(\lab_0)\\
+        R &=& \{ (\getnext(\lab), \varx) \mid
+          (\lab, \func) \in \atctxt \wedge\\
+
+          && \phantom{\{ (\getnext(\lab), \varx) \mid}
+          \getinst(\lab) = \varx \kweq \expr^\lab (\expr^\lab_1 \cdots \expr^\lab_n)
+        \}\\
+
+        \afsenv &=& \lambda \lab \in \labset. \; \left\{
+          \begin{array}{ll}
+            [\varx \mapsto \aval]
+            & \text{if} \; (\lab, \varx) \in R\\
+
+            \varnothing
+            & \text{otherwise}\\
+          \end{array}
+        \right.\\
+      \end{array}
+    \]
+\end{itemize}
+
+\paragraph{Programs} Finally, we define the abstract semantics of programs with
+a given syntactic view.  We define it as the least fixed point of the abstract
+transfer function with the target initial abstract state depending on the given
+syntactic view:
+\[
+  \asem{\prog}(\atree) = \lim_{n \rightarrow
+  \infty}(\atransfer)^n(\iaelem(\atree))
+\]
+where
+\begin{itemize}
+  \item \underline{Abstract Transfer Function}: $\atransfer: \aelemset
+    \rightarrow \aelemset$
+    \[
+      \atransfer(\aelem) = \aelem \join \sem{\amctxt} \wedge
+      \bigjoin_{\lab \in \labset}{\asem{\getinst(\lab)}(\amctxt, \atctxt, \lab,
+      \afsenv(\lab))}
+    \]
+    where $\aelem = (\amctxt, \atctxt, \afsenv)$ and $\sem{\amctxt} = (\amctxt,
+    \atctxt, [\lab \mapsto \aenv_\lab \mid \lab \in \amctxt \wedge
+    \getinst(\lab) = \varx = \expr(\cdots) \wedge \aenv_\lab = [\varx \mapsto
+    \top]])$.
+  \item \underline{Target Initial Abstract State}: $\iaelem:
+    \atreeset \rightarrow \aelemset$
+    \[
+      \iaelem(\atree) = (\varnothing, \varnothing, \afsenv)
+    \]
+    where \[
+      \begin{array}{lcl}
+        \atree &=& \ty_k \langle \cdots \rangle\\
+
+        \agetsubs(\atree) &=& [\atree_1, \cdots, \atree_n]\\
+
+        \ty_k.\eval &=& \lambda \kwdef \; \kwrl \varx_1, \cdots, \varx_n \kwrr
+        \; \lab\\
+
+        \aenv &=& [\varx_1 \mapsto \atree_1, \cdots, \varx_n \mapsto
+        \atree_n]\\
+
+        \afsenv &=& [\lab \mapsto \aenv]\\
+      \end{array}
+    \]
+\end{itemize}
+
+\subsubsection{Transformations}
+
+Using the analysis result, we define transformations for expressions,
+instructions, and programs.
+
+\paragraph{Expressions} We first define the transformation of expressions as
+follows:
+
+\[
+  \framebox{$\transform{\expr}: \aenvset \rightarrow \exprset$}
+\]
+\[
+  \transform{\expr}(\aenv) = \left\{
+    \begin{array}{ll}
+      \pval & \text{if} \; \asem{\expr}(\aenv) = \pval\\
+      \expr & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+
+\paragraph{Instructions} Then, we define the transformation of instructions
+as follows:
+\[
+  \framebox{$\transform{\inst}: \aenvset \rightarrow \instset$}
+\]
+\begin{itemize}
+  \item \underline{Variable Assignments}:
+    \[
+      \transform{\varx \kweq \expr}(\aenv) =
+      \varx \kweq \expr'
+    \]
+    where $\expr' = \transform{\expr}(\aenv)$
+
+  \item \underline{Field Assignments}:
+    \[
+      \transform{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\aenv) =
+      \expr'_0 \kwsl \expr'_1 \kwsr \kweq \expr'_2
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \expr'_0 = \transform{\expr_0}(\aenv) &\wedge\\
+        \expr'_1 = \transform{\expr_1}(\aenv) &\wedge\\
+        \expr'_2 = \transform{\expr_2}(\aenv)\\
+      \end{array}
+    \]
+  \item \underline{Object Allocations}:
+    \[
+      \transform{\varx \kweq \kwcl \kwcr}(\aenv) =
+      \varx \kweq \kwcl \kwcr
+    \]
+
+  \item \underline{Function Calls}:
+    \[
+      \transform{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\aenv) =
+      \varx \kweq \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}ll}
+        \expr' = \transform{\expr}(\aenv) &\wedge\\
+        \expr'_k = \transform{\expr_k}(\aenv) \; [\forall 1 \leq k \leq
         n]\\
@@
     \[
-      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv} =
-      (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
+      \transform{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\aenv) =
+      \kwif \; \expr' \; \lab_\vart \; \lab_\varf
     \]
-    where
-    \[
-      (\expr', \_) = \transforme(\expr, \aenv)
-    \]
+    where $\expr' = \transform{\expr}(\aenv)$
 
@@
     \[
-      \asem{\kwret \; \expr, \aenv} =
-      (\kwret \; \expr, \aenv)
+      \transform{\kwret \; \expr}(\aenv) =
+      \kwret \; \expr'
     \]
-    where
-    \[
-      (\expr', \_) = \transforme(\expr', \aenv)
-    \]
+    where $\expr' = \transform{\expr}(\aenv)$
 \end{itemize}
 
-% \paragraph{Transformation of Programs} Finally, we define the transformation
-% of programs as the least fixed point of the abstract transfer function:
-% \[
-%   \transform(\prog, (\func, (\aval_1, \cdots, \aval_n))) = \lfp \; \atransfer =
-%   \lim_{n \rightarrow \infty}(\atransfer)^n(\prog, \iaelem)
-% \]
-% where
-% \begin{itemize}
-%   \item \underline{Abstract Transfer Function}: $\atransfer: \progset \times
-%     \aelemset \rightarrow \progset \times \aelemset$
-%     \[
-%       \atransfer(\prog, \aelem) = \lambda \lab \in \labset. \; \bigjoin_{\lab' \in
-%       \labset}{\todo}
-%     \]
-%     where
-%     \[
-%     \]
-%   \item \underline{Initial Abstract State}: $\iaelem \in \elemset$
-%     \[
-%       \iaelem = \todo
-%     \]
-% \end{itemize}
-% 
-% \todo
-
-\subsubsection{Transformations}
-
-\todo
-
-% \[
-%   \framebox{$\transforme: \exprset \times \aenvset \rightarrow \exprset \times
-%   \avalset$}
-% \]
-% \[
-%   \transforme(\expr, \aenv) = (\expr'', \aval)
-% \]
-% where
-% \[
-%   \begin{array}{l@{~}c@{~}ll}
-%     \aval &=& \asem{\expr}(\aenv) &\wedge\\
-%     \expr'' &=& \left\{
-%       \begin{array}{ll}
-%         \pval & \text{if} \; \aval = \langle \pval, \_ \rangle\\
-%         \expr' & \text{if} \; \aval = \langle \_, \expr' \rangle\\
-%         \expr & \text{otherwise}\\
-%       \end{array}
-%     \right.\\
-%   \end{array}
-% \]
-
-% \[
-%   \framebox{$\transformi: \instset \times \aenvset \rightarrow \instset \times
-%   \aenvset$}
-% \]
-% \begin{itemize}
-%   \item \underline{Variable Assignments}:
-%     \[
-%       \transformi(\varx = \expr, \aenv) =
-%       (\varx = \expr', \aenv[\varx \mapsto \aval])
-%     \]
-%     where
-%     \[
-%       (\expr', \aval) = \transforme(\expr, \aenv)
-%     \]
-% 
-%   \item \underline{Field Assignments}:
-%     \[
-%       \transformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
-%       (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
-%     \]
-%     where
-%     \[
-%       \begin{array}{l@{~}c@{~}ll}
-%         (\expr'_0, \_) = \transforme(\expr_0, \aenv) &\wedge\\
-%         (\expr'_1, \_) = \transforme(\expr_1, \aenv) &\wedge\\
-%         (\expr'_2, \_) = \transforme(\expr_2, \aenv)\\
-%       \end{array}
-%     \]
-%   \item \underline{Object Allocations}:
-%     \[
-%       \transformi(\varx = \kwcl \kwcr, \aenv) =
-%       (\varx = \kwcl \kwcr, \aenv[\varx \mapsto \top])
-%     \]
-% 
-%   \item \underline{Function Calls}:
-%     \[
-%       \transformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
-%       (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
-%       \aenv[\varx \mapsto \top])
-%     \]
-%     where
-%     \[
-%       \begin{array}{l@{~}c@{~}ll}
-%         (\expr', \_) = \transforme(\expr, \aenv) &\wedge\\
-%         (\expr'_k, \_) = \transforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
-%         n\\
-%       \end{array}
-%     \]
-% 
-%   \item \underline{Branches}:
-%     \[
-%       \transformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
-%       (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
-%     \]
-%     where
-%     \[
-%       (\expr', \_) = \transforme(\expr, \aenv)
-%     \]
-% 
-%   \item \underline{Returns}:
-%     \[
-%       \transformi(\kwret \; \expr, \aenv) =
-%       (\kwret \; \expr, \aenv)
-%     \]
-%     where
-%     \[
-%       (\expr', \_) = \transforme(\expr', \aenv)
-%     \]
-% \end{itemize}
+\paragraph{Programs} Finally, we define the program transformation as follows:
+\[
+  \framebox{$\transform{\prog}: \aelemset \rightarrow \progset$}
+\]
+\[
+  \transform{\prog}(\amctxt, \atctxt, \afsenv) = (\istset, \getfunc, \getinst',
+  \getnext)
+\]
+where $\prog = (\istset, \getfunc, \getinst, \getnext)$ and $\getinst' =
+\getinst[\lab \mapsto \inst_\lab \mid \aenv = \afsenv(\lab) \neq \epsilon \wedge
+\inst_\lab = \transform{\getinst(\lab)}(\aenv)]$.
 
@@
 
-\subsubsection{Proof of Semantics Preservation}
+\subsubsection{Semantics Preservation}
+
+% We first define a helper function $\entrystset: \atreeset \rightarrow
+% \powerset{\stset}$ to define the set of entry states for a given syntactic view
+% $\atree = \ty_k \langle \cdots \rangle$:
+% \[
+%   \begin{array}{l@{~}l}
+%     \entrystset(\atree) = \{ \st \in \stset \mid &
+%       \st = (\lab, \_, \_, \env) \wedge\\&
+% 
+%       \env = [\varx_0 \mapsto \atree, \varx_1 \mapsto \atree_1, \cdots, \varx_n
+%       \mapsto \atree_n]
+%     \}\\
+%   \end{array}
+% \]
+% where $\ty_k.\eval = \kwdef \; \kwrl \varx_0, \cdots, \varx_n \kwrr \lab$ and
+% $\agetsubs(\atree) = [\atree_1, \cdots, \atree_n]$. Then, we define a restricted
+% semantics $\rsem{-}: \progset \rightarrow \atreeset \rightarrow
+% \powerset{\stset}$ as follows:
+% \[
+%   \begin{array}{l@{~}l@{~}l}
+%     \rsem{\prog}(\atree) = \{ \st \in \stset \mid&
+%       \st' \in \sem{\prog} \cap \entrystset(\atree) &\wedge\\&
+%       \st' \trans^* \st  &\wedge\\&
+%       \st' = (\_, \ctxts', \_, \_) &\wedge\\&
+%       \st = (\_, \ctxts, \_, \_) &\wedge\\&
+%       \ctxts \postfix \ctxts
+%     \}
+%   \end{array}
+% \]
+% where $x \postfix y$ denotes that a sequence $y$ is a postfix of a sequence $x$.
 
@@
 
-\subsection{JavaScript Semantics Specialization}
+\begin{theorem}[Soundness of $\asem{-}$]
+  For a given program $\prog \in \progset$ and a syntactic view $\atree \in
+  \atreeset$. Assume that $\asem{\prog}(\atree) = \aelem = (\amctxt, \atctxt,
+  \afsenv)$. Then, the following condition should be satisfied:
+  \[
+    \rsem{\prog}(\atree, \atctxt) \subseteq \gamma(\aelem)
+  \]
+\end{theorem}
+\begin{proof}
+  \todo
+\end{proof}
 
-This section explains how to utilize the partial evaluation for the JavaScript
-semantics specialization with a user-defined syntactic view.  We first formally
-define syntactic views and their operations, then we explain how to decide a
-restriction of the constant propagation specialization based on a given
-syntactic view.
+\begin{lemma}[Soundness of $\atransfer$]
+  The abstract transfer function $\atransfer$ is a sound approximation of the
+  transfer function $\transfer$ by satisfying the following condition:
+  \[
+    \forall \aelem \in \aelemset. \;
+    \transfer \circ \gamma(\aelem) \subseteq \gamma \circ \atransfer(\aelem)
+  \]
+\end{lemma}
+\begin{proof}
+  \todo
+\end{proof}
 
-\subsubsection{Semantics Specialization}
+\begin{theorem}[Semantics Preservation of $\transform{-}$]
+  \[
+    \todo
+  \]
+\end{theorem}
+\begin{proof}
+  \todo
+\end{proof}
 

### 2021-11-02 paper/pldi22/formal.tex
More formalization

@@
   \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
-    \text{Programs} & \progset &\ni& \prog &=& (\istset, \getfunc, \getinst,
-    \getnext)\\
+    \text{Programs} & \progset &\ni& \prog &=& (\initstset{\prog},
+    \getfunc{\prog}, \getinst{\prog}, \getnext{\prog})\\
 
@@
 
-An $\ires$ program $\prog = (\istset, \getfunc, \getinst, \getnext) \in \progset $
-consists of initial states and three mappings; $\getfunc: \labset \rightarrow
-\funcset$ and $\getinst: \labset \rightarrow \instset$ map labels to their
-functions and instructions, respectively, and $\getnext: \labset \rightarrow
+An $\ires$ program $\prog = (\initstset{\prog}, \getfunc{\prog},
+\getinst{\prog}, \getnext{\prog}) \in \progset $ consists of initial states and
+three mappings; $\getfunc{\prog}: \labset \rightarrow \funcset$ and
+$\getinst{\prog}: \labset \rightarrow \instset$ map labels to their functions
+and instructions, respectively, and $\getnext{\prog}: \labset \rightarrow
 \labset$ maps labels to their next labels, where a label $\lab \in \labset$
@@
 or captured variables exist in this paper.  An instruction $\inst \in \instset$
-is an assignment $\refer \kweq \expr$, an object allocation $\varx \kweq \kwcl \kwcr$, a
-function call $\varx \kweq \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
-\lab \; \lab$, or a return instruction $\kwret \; \expr$.  An invocation of an
-abstract algorithm in ECMAScript is compiled to a function call instruction with
-a new temporary variable.  We represent loops using branch instructions with
-cyclic pointing of labels in $\getnext$.  An expression is a primitive value
-$\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A
-reference is a variable $\varx$ or an object field $\expr \kwsl \expr \kwsr$.
-We write $\expr.\varf$ to briefly represent $\expr \kwsl \code{"f"} \kwsr$.
+is an assignment $\refer \kweq \expr$, an object allocation $\varx \kweq \kwcl
+\kwcr$, a function call $\varx \kweq \expr \kwrl \expr^* \kwrr$, a branch $\kwif
+\; \expr \; \lab \; \lab$, or a return instruction $\kwret \; \expr$.  An
+invocation of an abstract algorithm in ECMAScript is compiled to a function call
+instruction with a new temporary variable.  We represent loops using branch
+instructions with cyclic pointing of labels in $\getnext{\prog}$.  An expression
+is a primitive value $\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a
+reference $\refer$.  A reference is a variable $\varx$ or an object field $\expr
+\kwsl \expr \kwsr$.  We write $\expr.\varf$ to briefly represent $\expr \kwsl
+\code{"f"} \kwsr$.
 
@@
 
-The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset,
-\getinst, \getnext)$ is defined as follows:
-\[
-  \sem{\prog} = \{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}
-\]
-where $\trans^*$ denotes one or more repetition of $\trans$, and $\st \trans
-\st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
-\st'$. Another way to represent the concrete semantics is to define a transfer
-function $\transfer: \powerset{\stset} \rightarrow \powerset{\stset}$:
-\[
-  \sem{\prog} = \lim_{n \rightarrow \infty}\transfer^n(\istset)
-\]
-where $\transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans \st' \}$.  Now,
-we define the denotational semantics of expressions, instructions, and
+The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog$ is defined as
+follows:
+\[
+  \sem{\prog} = \{ \st \in \stset \mid \initst \in \initstset{\prog} \wedge
+  \initst \trans{\prog}^* \st \}
+\]
+where $\trans{\prog}^*$ denotes one or more repetition of $\trans{\prog}$, and
+$\st \trans{\prog} \st'$ if and only if $\st = (\lab, \_, \_, \_)$ and
+$\sem{\getinst{\prog}(\lab)}(\st) = \st'$. Another way to represent the concrete
+semantics is to define a transfer function $\transfer: \powerset{\stset}
+\rightarrow \powerset{\stset}$:
+\[
+  \sem{\prog} = \lim_{n \rightarrow \infty}\transfer^n(\initstset{\prog})
+\]
+where
+\begin{equation}\label{eqn:transfer}
+  \transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans{\prog} \st' \}
+\end{equation}
+Now, we define the denotational semantics of expressions, instructions, and
 functions.
@@
             \rangle \wedge \val_1 = j\\
+
+            \ty_k.\eval
+            & \text{if} \; \val_0 = \ty_k \langle \tree_1, \cdots, \tree_n
+            \rangle \wedge \val_1 = \code{"eval"}\\
           \end{array}
@@
       \sem{\varx \kweq \expr}(\st) =
-      (\getnext(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
+      (\getnext{\prog}(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
     \]
@@
       \sem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\st) =
-      (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
+      (\getnext{\prog}(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
     \]
@@
       \sem{\varx \kweq \kwcl \kwcr}(\st) =
-      (\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env[\varx \mapsto
+      (\lab, \ctxts, \heap[\addr \mapsto \epsilon], \env[\varx \mapsto
       \addr])
@@
         &\wedge\\
-        \ctxt &=& (\getnext(\lab), \env, \varx)\\
+        \ctxt &=& (\getnext{\prog}(\lab), \env, \varx)\\
       \end{array}
@@
 
-We define a \textit{partial evaluation} $\peval{-}: \progset \rightarrow
-\atreeset \rightarrow \progset$ of $\ires$ programs to specialize JavaScript
-semantics with a given syntactic view:
+We define a \textit{partial evaluation} $\peval{\prog}: \atreeset \rightarrow
+\progset$ of $\ires$ programs to specialize JavaScript semantics with a given
+syntactic view:
 \[
@@
 corresponding \esalg{Evaluation} function. Then, it performs a static analysis
-$\asem{-}$ of a given program $\prog$ with the syntactic view $\atree$ and
-transforms the program using $\transform{-}$ with the analysis result
-$\asem{\prog}(\atree)$ to produce a specialized $\ires$ program.  Since the
-\esalg{Evaluation} of $\ty$ might one or more $\ires$ functions, we only define
-the partial evaluation when $\atree = \ty_k \langle \cdots \rangle$.  Now, we
-define the static analysis and program transformation of $\ires$ programs and
-prove the semantics preservation of the partial evaluation consisting of them.
+$\asem{\prog}$ of a given program $\prog$ with the syntactic view $\atree$, and
+transforms the program to a specialized program using $\transform{\prog}$ with
+the analysis result $\asem{\prog}(\atree)$.  Since the \esalg{Evaluation} of
+$\ty$ might one or more $\ires$ functions, we only define the partial evaluation
+when $\atree = \ty_k \langle \cdots \rangle$.  Now, we define the static
+analysis and program transformation of $\ires$ programs and prove the semantics
+preservation of the partial evaluation consisting of them.
 
@@
 given given syntactic view $\atree$.  We first define abstract domains of
-states, calling contexts, environments, and values as follows:
+states, call edges, environments, and values as follows:
 \begin{itemize}
-  \item \underline{Abstract States}:
-    $\aelemset = \amctxtset \times \atctxtset \times \afsenvset$
-    \[
-      \begin{array}{lcl}
-        \aelemgamma(\amctxt, \atctxt, \afsenv) &=&
-        \amctxtgamma(\amctxt) \cup
-        (\atctxtgamma(\atctxt) \cap \afsenvgamma(\afsenv))\\
-
-        (\amctxt, \atctxt, \afsenv) \order
-        (\amctxt', \atctxt', \afsenv') &\Leftrightarrow&
-        (\amctxt \order \amctxt') \wedge
-        (\atctxt \order \atctxt') \wedge
-        (\afsenv \order \afsenv')\\
-
-        (\amctxt, \atctxt, \afsenv) \join (\amctxt', \atctxt', \afsenv') &=&
-        (\amctxt \join \amctxt', \atctxt \join \atctxt', \afsenv \join \afsenv')\\
-      \end{array}
-    \]
-
-  \item \underline{Merged Calling Contexts}:
-    $\amctxtset = \powerset{\labset}$
-    \[
-      \begin{array}{lcl}
-        \amctxtgamma(\amctxt) &=& \{ \st \in \stset \mid
+  \item \underline{Abstract States}: $\aelemset$
+    \[
+      \begin{array}{lcl}
+        \aelemset &=& \adcallset \times \ascallset \times \afsenvset\\
+
+        \aelemgamma &:& \atreeset \rightarrow \aelemset \rightarrow
+        \powerset{\stset}\\
+
+        \aelemgamma(\atree)(\aelem) &=&
+        (\adcallgamma(\atree)(\adcall) \setminus C) \uplus
+        (C \cap \afsenvgamma(\afsenv))\\
+        \multicolumn{3}{r}{\text{where} \; C = \ascallgamma(\atree)(\ascall)}\\
+
+        \aelem \order \aelem' &\Leftrightarrow&
+        \adcall \order \adcall' \wedge
+        \ascall \order \ascall' \wedge
+        \afsenv \order \afsenv'\\
+
+        \aelem \join \aelem' &=&
+        (\adcall \join \adcall', \ascall \join \ascall', \afsenv \join \afsenv')\\
+      \end{array}
+    \]
+    where $\atree = \ty_k \langle \cdots \rangle$, $\aelem = (\adcall, \ascall,
+    \afsenv)$ and $\aelem' = (\adcall', \ascall', \afsenv')$
+
+  \item \underline{Dynamic Call Sets}: $\adcallset$
+    \[
+      \begin{array}{lcl}
+        \adcallset &=& \powerset{\labset}\\
+
+        \adcallgamma &:& \atreeset \rightarrow \adcallset \rightarrow
+        \powerset{\stset}\\
+
+        \adcallgamma(\atree)(\adcall) &=& \{ \st \in \stset \mid
           \st = (\lab, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&
@@
           \phantom{\{ \st \in \stset \mid}
-          \lab_j \in \amctxt
+          \lab_j \in \adcall
         \}\\
 
-        \amctxt \order \amctxt' &\Leftrightarrow&
-        \amctxt \subseteq \amctxt\\
-
-        \amctxt \join \amctxt' &=&
-        \amctxt \cup \amctxt\\
-      \end{array}
-    \]
-
-  \item \underline{Target Calling Contexts}:
-    $\atctxtset = \powerset{\labset \times \funcset}$
-    \[
-      \begin{array}{lcl}
-        \atctxtgamma(\atctxt) &=& \{ \st \in \stset \mid
+        \adcall \order \adcall' &\Leftrightarrow&
+        \adcall \subseteq \adcall\\
+
+        \adcall \join \adcall' &=&
+        \adcall \cup \adcall\\
+      \end{array}
+    \]
+    where $\atree = \ty_k \langle \cdots \rangle$
+
+  \item \underline{Static Call Sets}: $\ascallset$
+    \[
+      \begin{array}{lcl}
+        \ascallset &=& \powerset{\labset \times \funcset}\\
+
+        \ascallgamma &:& \atreeset \rightarrow \ascallset \rightarrow
+        \powerset{\stset}\\
+
+        \ascallgamma(\atree)(\ascall) &=& \{ \st \in \stset \mid
           \st = (\lab_0, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&
@@
           \phantom{\{ \st \in \stset \mid}
-          \exists 0 \leq m \leq n. \; \getfunc(\lab_m) = \ty_k.\eval \wedge\\&&
+          \exists 0 \leq m \leq n. \; \getfunc{\prog}(\lab_m) = \ty_k.\eval
+          \wedge\\&&
 
           \phantom{\{ \st \in \stset \mid}
-          \forall 1 \leq j \leq m. \; (\lab_j, \getfunc{\lab_{j-1}}) \in \atctxt
+          \forall 1 \leq j \leq m. \; (\lab_j, \getfunc{\prog}{\lab_{j-1}}) \in
+          \ascall
         \}\\
 
-        \atctxt \order \atctxt' &\Leftrightarrow& \atctxt \subseteq \atctxt\\
-
-        \atctxt \join \atctxt' &=& \atctxt \cup \atctxt'\\
-      \end{array}
-    \]
-
-  \item \underline{Flow-Sensitive Abstract Environments}:
-    $\afsenvset = \labset \rightarrow \aenvset$
-    \[
-      \begin{array}{lcl}
+        \ascall \order \ascall' &\Leftrightarrow& \ascall \subseteq \ascall\\
+
+        \ascall \join \ascall' &=& \ascall \cup \ascall'\\
+      \end{array}
+    \]
+    where $\atree = \ty_k \langle \cdots \rangle$
+
+  \item \underline{Flow-Sensitive Abstract Environments}: $\afsenvset$
+    \[
+      \begin{array}{lcl}
+        \afsenvset &=& \labset \rightarrow \aenvset\\
+
+        \afsenvgamma &:& \afsenvset \rightarrow \powerset{\stset}\\
+
         \afsenvgamma(\afsenv) &=& \{ \st \in \stset \mid
@@
 
-  \item \underline{Abstract Environments}:
-    $\aenvset = \varset \rightarrow \aenvset$
-    \[
-      \begin{array}{lcl}
+  \item \underline{Abstract Environments}: $\aenvset$
+    \[
+      \begin{array}{lcl}
+        \aenvset &=& \varset \rightarrow \aenvset\\
+
+        \aenvgamma &:& \aenvset \rightarrow \powerset{\stset}\\
+
         \aenvgamma(\aenv) &=& \{ \st \in \stset \mid
@@
 
-  \item \underline{Abstract Values}: $\avalset = \valset \uplus \atreeset \uplus
-    \{ \top, \bot,  \}$
-    \[
-      \begin{array}{lcl}
+  \item \underline{Abstract Values}: $\avalset$
+    \[
+      \begin{array}{lcl}
+        \avalset &=& \valset \uplus \atreeset \uplus \{ \top, \bot,  \}\\
+
+        \avalgamma &:& \avalset \rightarrow \powerset{\valset}\\
+
         \avalgamma(\aval) &=& \left\{
@@
 
-An abstract state $\aelem \in \aelemset$ is a triple of a merged and target call
-edges and a flow-sensitive abstract environment.  A merged calling context
-$\amctxt \in \amctxtset$ is a set of call labels representing merged function
-calls. A target calling context $\atctxt \in \atctxtset$ is a set of possible
-static call edges from labels to function, and it represents the scope of static
-analysis. To more precisely represent states in target calling contexts, we
-define a flow-sensitive abstract environment $\afsenv \in \afsenvset$. It is
-a mapping from labels to abstract environments to represents the shape of
-environments in each label. An abstract environment $\aenv \in \aenvset$ is a
-mapping from variables to abstract values to describe values stored in
-variables. An abstract value $\aval \in \avalset$ is a static value $\val$, a
-syntactic view $\atree$, a dynamic value $\top$, or nothing $\bot$.  Now, we
-define abstract semantics of expressions, instructions, and programs.
+An abstract state $\aelem \in \aelemset$ is a triple of a dynamic call set, a
+static call set, and a flow-sensitive abstract environment.  A dynamic call set
+$\adcall \in \adcallset$ is a set of call labels representing function calls
+with multiple functions or no static arguments. A static call set $\ascall \in
+\ascallset$ is a set of possible static call edges from labels to function, and
+it represent a set of \textit{static calling contexts} $\ascallgamma(\ascall)$
+used as the scope of program transformations.  To more precisely in the static
+calling contexts, we define a flow-sensitive abstract environment $\afsenv \in
+\afsenvset$. It is a mapping from labels to abstract environments to represents
+the shape of environments in each label. An abstract environment $\aenv \in
+\aenvset$ is a mapping from variables to abstract values to describe values
+stored in variables. An abstract value $\aval \in \avalset$ is a static value
+$\val$, a syntactic view $\atree$, a dynamic value $\top$, or nothing $\bot$.
+Now, we define abstract semantics of expressions, instructions, and programs.
 
@@
     \[
-      \begin{array}{l@{~}c@{~}l@{~}l}
-        \asem{\expr_0}(\aenv) &=& \aval_0 &\wedge\\
-        \asem{\expr_1}(\aenv) &=& \aval_1 &\wedge\\
+      \begin{array}{lcl}
+        \asem{\expr_0}(\aenv) &=& \aval_0\\
+        \asem{\expr_1}(\aenv) &=& \aval_1\\
         \aval &=& \left\{
           \begin{array}{ll}
-            \tree_j & \text{if} \;
-            \aval_0 = \ty_k \langle \tree_1, \cdots, \tree_n \rangle \wedge
-            \aval_1 = j\\
-
             \atree_j & \text{if} \;
@@
 
+            \ty_k.\eval & \text{if} \;
+            \aval_0 = \ty_k \langle \cdots \rangle \wedge
+            \aval_1 = \code{"eval"}\\
+
             \top & \text{otherwise}\\
@@
 \[
-  \framebox{$\asem{\inst}: \amctxtset \times \atctxtset \times \labset \times
-    \aenvset \rightarrow
-  \aelemset$}
+  \framebox{$\asem{\inst}: \labset \times \aelemset \rightarrow \aelemset$}
 \]
@@
     \[
-      \asem{\varx \kweq \expr}(\amctxt, \atctxt, \lab, \aenv) =
-      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]])
-    \]
-    where $\aval = \asem{\expr}(\aenv)$
+      \asem{\varx \kweq \expr}(\lab, \aelem) =
+      (\adcall, \ascall, [\getnext{\prog}(\lab) \mapsto \aenv[\varx
+      \mapsto \aval]])
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aelem &=& (\adcall, \ascall, \afsenv)\\
+        \aenv &=& \afsenv(\lab)\\
+        \aval &=& \asem{\expr}(\aenv)\\
+      \end{array}
+    \]
 
@@
     \[
-      \asem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\amctxt, \atctxt, \lab, \aenv) =
-      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv])
+      \asem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}
+      (\lab, \aelem) =
+      (\adcall, \ascall, [\getnext{\prog}(\lab) \mapsto \aenv])
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aelem &=& (\adcall, \ascall, \afsenv)\\
+        \aenv &=& \afsenv(\lab)\\
+      \end{array}
     \]
@@
     \[
-      \asem{\varx \kweq \kwcl \kwcr}(\amctxt, \atctxt, \lab, \aenv) =
-      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]])
+      \asem{\varx \kweq \kwcl \kwcr}(\lab, \aelem) =
+      (\adcall, \ascall, [\getnext{\prog}(\lab) \mapsto \aenv[\varx
+      \mapsto \top]])
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aelem &=& (\adcall, \ascall, \afsenv)\\
+        \aenv &=& \afsenv(\lab)\\
+      \end{array}
     \]
@@
     \[
-      \asem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\amctxt,
-      \atctxt, \lab, \aenv) = (\amctxt', \atctxt', \afsenv)
-    \]
-    where
-    \[
-      \begin{array}{l@{~}c@{~}ll}
-        \aval &=& \asem{\expr}(\aenv) &\wedge\\
-        \aval_j &=& \asem{\expr_j}(\aenv) \; [\forall 1 \leq j \leq n] &\wedge\\
-        (\amctxt', \atctxt') &=& \left\{
+      \asem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\lab, \aelem)
+      = (\adcall', \ascall', \afsenv')
+    \]
+    where
+    \[
+      \begin{array}{l@{~}c@{~}l}
+        \aelem &=& (\adcall, \ascall, \afsenv)\\
+        \aenv &=& \afsenv(\lab)\\
+        \aval &=& \asem{\expr}(\aenv)\\
+        \aval_j &=& \asem{\expr_j}(\aenv) \; [\forall 1 \leq j \leq n]\\
+        (\adcall', \ascall') &=& \left\{
           \begin{array}{ll}
-            (\amctxt, \atctxt \cup \{ (\lab, \func) \} &
+            (\adcall, \ascall \cup \{ (\lab, \func) \} &
             \text{if} \; \aval = \func \wedge \exists j. \; \aval_j \neq \top\\
 
-            (\amctxt \cup \{ \lab \}, \atctxt) &
+            (\adcall \cup \{ \lab \}, \ascall) &
             \text{otherwise}
@@
         \right.\\
-        \afsenv &=& [ \lab_\func \mapsto \aenv_\func \mid
-        (\lab, \func) \in \atctxt' \wedge\\&&
+        \afsenv' &=& [ \lab_\func \mapsto \aenv_\func \mid
+        (\lab, \func) \in \ascall' \wedge\\&&
 
@@
     \[
-      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\amctxt, \atctxt, \lab, \aenv) =
-      (\amctxt, \atctxt, \afsenv')
-    \]
-    where
-    \[
-      \begin{array}{lcl}
+      \asem{\kwif \; \expr \; \lab_\vart \; \lab_\varf}(\lab, \aelem) =
+      (\adcall, \ascall, \afsenv'')
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aelem &=& (\adcall, \ascall, \afsenv)\\
+        \aenv &=& \afsenv(\lab)\\
         \aval &=& \asem{\expr}(\aenv)\\
 
-        \afsenv &=& \left\{
+        \afsenv' &=& \left\{
           \begin{array}{ll}
@@
             \avalgamma(\aval)\\
-            \varnothing & \text{otherwise}\\
+            \epsilon & \text{otherwise}\\
           \end{array}
@@
 
-        \afsenv' &=& \left\{
+        \afsenv'' &=& \left\{
           \begin{array}{ll}
-            \afsenv[\lab_\varf \mapsto \aenv] & \text{if} \; \false \in
+            \afsenv'[\lab_\varf \mapsto \aenv] & \text{if} \; \false \in
             \avalgamma(\aval)\\
-            \afsenv & \text{otherwise}\\
+            \afsenv' & \text{otherwise}\\
           \end{array}
@@
     \[
-      \asem{\kwret \; \expr}(\amctxt, \atctxt, \lab_0, \aenv) =
-      (\amctxt, \atctxt, \afsenv)
-    \]
-    where
-    \[
-      \begin{array}{lcl}
+      \asem{\kwret \; \expr}(\lab_0, \aelem) =
+      (\adcall, \ascall, \afsenv')
+    \]
+    where
+    \[
+      \begin{array}{lcl}
+        \aelem &=& (\adcall, \ascall, \afsenv)\\
+        \aenv &=& \afsenv(\lab)\\
         \aval &=& \asem{\expr'}(\aenv)\\
 
-        \func &=& \getfunc(\lab_0)\\
-        R &=& \{ (\getnext(\lab), \varx) \mid
-          (\lab, \func) \in \atctxt \wedge\\
-
-          && \phantom{\{ (\getnext(\lab), \varx) \mid}
-          \getinst(\lab) = \varx \kweq \expr^\lab (\expr^\lab_1 \cdots \expr^\lab_n)
+        \func &=& \getfunc{\prog}(\lab_0, \aelem)\\
+        R &=& \{ (\getnext{\prog}(\lab), \varx) \mid
+          (\lab, \func) \in \ascall \wedge\\&&
+
+          \phantom{\{ (\getnext{\prog}(\lab), \varx) \mid}
+          \getinst{\prog}(\lab) = \varx \kweq \expr^\lab (\expr^\lab_1 \cdots
+          \expr^\lab_n)
         \}\\
 
-        \afsenv &=& \lambda \lab \in \labset. \; \left\{
+        \afsenv' &=& \lambda \lab \in \labset. \; \left\{
           \begin{array}{ll}
@@
 
-            \varnothing
+            \epsilon
             & \text{otherwise}\\
@@
 
-\paragraph{Programs} Finally, we define the abstract semantics of programs with
-a given syntactic view.  We define it as the least fixed point of the abstract
-transfer function with the target initial abstract state depending on the given
-syntactic view:
-\[
-  \asem{\prog}(\atree) = \lim_{n \rightarrow
-  \infty}(\atransfer)^n(\iaelem(\atree))
-\]
-where
+\paragraph{Programs} Finally, we define the abstract semantics $\asem{\prog}:
+\atreeset \rightarrow \aelemset$ of a program $\prog$ with a given syntactic
+view:
+\[
+  \asem{\prog}(\atree) = \lim_{n \rightarrow \infty}(\atransfer)^n \circ
+  \entryaelem(\atree)
+\]
+It is the least fixed point of the abstract transfer function $\atransfer$ with
+an abstract entry state $\entryaelem$ depending on the given syntactic view
+$\atree$:
 \begin{itemize}
@@
     \[
-      \atransfer(\aelem) = \aelem \join \sem{\amctxt} \wedge
-      \bigjoin_{\lab \in \labset}{\asem{\getinst(\lab)}(\amctxt, \atctxt, \lab,
-      \afsenv(\lab))}
-    \]
-    where $\aelem = (\amctxt, \atctxt, \afsenv)$ and $\sem{\amctxt} = (\amctxt,
-    \atctxt, [\lab \mapsto \aenv_\lab \mid \lab \in \amctxt \wedge
-    \getinst(\lab) = \varx = \expr(\cdots) \wedge \aenv_\lab = [\varx \mapsto
-    \top]])$.
-  \item \underline{Target Initial Abstract State}: $\iaelem:
+      \atransfer(\aelem) = \aelem \join \sem{\adcall} \wedge
+      \bigjoin_{\lab \in \labset}{\asem{\getinst{\prog}(\lab)}(\lab, \aelem)}
+    \]
+    where $\aelem = (\adcall, \ascall, \afsenv)$ and $\sem{\adcall} = (\adcall,
+    \ascall, [\lab \mapsto \aenv_\lab \mid \lab \in \adcall \wedge
+    \getinst{\prog}(\lab) = \varx = \expr(\cdots) \wedge \aenv_\lab = [\varx
+    \mapsto \top]])$.
+  \item \underline{Abstract Entry States}: $\entryaelem:
     \atreeset \rightarrow \aelemset$
     \[
-      \iaelem(\atree) = (\varnothing, \varnothing, \afsenv)
+      \entryaelem(\atree) = (\varnothing, \varnothing, \afsenv)
     \]
@@
         \ty_k.\eval &=& \lambda \kwdef \; \kwrl \varx_1, \cdots, \varx_n \kwrr
-        \; \lab\\
+        \; \entrylab\\
 
@@
 
-        \afsenv &=& [\lab \mapsto \aenv]\\
+        \afsenv &=& [\entrylab \mapsto \aenv]\\
       \end{array}
@@
 \[
-  \transform{\prog}(\amctxt, \atctxt, \afsenv) = (\istset, \getfunc, \getinst',
-  \getnext)
-\]
-where $\prog = (\istset, \getfunc, \getinst, \getnext)$ and $\getinst' =
-\getinst[\lab \mapsto \inst_\lab \mid \aenv = \afsenv(\lab) \neq \epsilon \wedge
-\inst_\lab = \transform{\getinst(\lab)}(\aenv)]$.
+  \transform{\prog}(\adcall, \ascall, \afsenv) = (\initstset{\prog},
+  \getfunc{\prog}, \getinst{\prog'}, \getnext{\prog})
+\]
+where
+\[
+  \begin{array}{lcl}
+    \prog &=&
+    (\initstset{\prog}, \getfunc{\prog}, \getinst{\prog}, \getnext{\prog})\\
+
+    \getinst{\prog'} &=&
+    \getinst{\prog}[\lab \mapsto \inst_\lab \mid
+    \lab \in \labset \wedge \aenv = \afsenv(\lab) \wedge\\&&
+
+    \phantom{\getinst{\prog}[\lab \mapsto \inst_\lab \mid}
+    \inst_\lab = \transform{\getinst{\prog}(\lab)}(\aenv)]\\
+  \end{array}
+\]
 
@@
 
-% We first define a helper function $\entrystset: \atreeset \rightarrow
-% \powerset{\stset}$ to define the set of entry states for a given syntactic view
-% $\atree = \ty_k \langle \cdots \rangle$:
-% \[
-%   \begin{array}{l@{~}l}
-%     \entrystset(\atree) = \{ \st \in \stset \mid &
-%       \st = (\lab, \_, \_, \env) \wedge\\&
-% 
-%       \env = [\varx_0 \mapsto \atree, \varx_1 \mapsto \atree_1, \cdots, \varx_n
-%       \mapsto \atree_n]
-%     \}\\
-%   \end{array}
-% \]
-% where $\ty_k.\eval = \kwdef \; \kwrl \varx_0, \cdots, \varx_n \kwrr \lab$ and
-% $\agetsubs(\atree) = [\atree_1, \cdots, \atree_n]$. Then, we define a restricted
-% semantics $\rsem{-}: \progset \rightarrow \atreeset \rightarrow
-% \powerset{\stset}$ as follows:
-% \[
-%   \begin{array}{l@{~}l@{~}l}
-%     \rsem{\prog}(\atree) = \{ \st \in \stset \mid&
-%       \st' \in \sem{\prog} \cap \entrystset(\atree) &\wedge\\&
-%       \st' \trans^* \st  &\wedge\\&
-%       \st' = (\_, \ctxts', \_, \_) &\wedge\\&
-%       \st = (\_, \ctxts, \_, \_) &\wedge\\&
-%       \ctxts \postfix \ctxts
-%     \}
-%   \end{array}
-% \]
-% where $x \postfix y$ denotes that a sequence $y$ is a postfix of a sequence $x$.
-
-\todo
-
-\begin{theorem}[Soundness of $\asem{-}$]
-  For a given program $\prog \in \progset$ and a syntactic view $\atree \in
-  \atreeset$. Assume that $\asem{\prog}(\atree) = \aelem = (\amctxt, \atctxt,
-  \afsenv)$. Then, the following condition should be satisfied:
-  \[
-    \rsem{\prog}(\atree, \atctxt) \subseteq \gamma(\aelem)
+To prove the semantics preservation of the partial evaluation for each syntactic
+view $\atree$, we first define a restricted semantics depending on the given
+syntactic view. Then, we prove the soundness of the static analysis
+$\asem{\prog}$ of the program. Finally, we prove the semantics preservation of
+the program transformation $\transform{\prog}$.
+
+\paragraph{Restricted Semantics} We first define a \textit{restricted semantics}
+$\rsem{\prog}: \atreeset \rightarrow \powerset{\stset}$ with a syntactic view:
+\[
+  \rsem{\prog}(\atree) = \lim_{n \rightarrow \infty}\transfer^n \circ
+  \entrystset(\atree)
+\]
+It is the least fixed point of a transfer function $\transfer: \powerset{\stset}
+\rightarrow \powerset{\stset}$ defined in Equation~\ref{eqn:transfer} with the
+following entry states $\entrystset: \atreeset \rightarrow \powerset{\stset}$
+depending on the given syntactic view $\atree$:
+\[
+  \begin{array}{lcl}
+    \entrystset &:& \atreeset \rightarrow \powerset{\stset}\\
+
+    \entrystset(\atree) &=& \{ \st \in \stset \mid
+      \st = (\entrylab, \_, \_, \env) \wedge\\&&
+
+      \phantom{\{ \st \in \stset \mid}
+        \tree \in \atreegamma(\atree) \wedge \forall 1 \leq j \leq n. \;
+      \tree_j \in \atreegamma(\atree_j) \wedge\\&&
+
+      \phantom{\{ \st \in \stset \mid}
+        \env = [\varx_0 \mapsto \tree, \varx_1 \mapsto \tree_1, \cdots,
+        \varx_n \mapsto \tree_n]
+      \}\\
+    \end{array}
+  \]
+where
+\[
+  \begin{array}{lcl}
+    \atree &=& \ty_k \langle \cdots \rangle\\
+    \ty_k.\eval &=& \kwdef \; \kwrl \varx_0, \cdots, \varx_n \kwrr \entrylab\\
+    \agetsubs(\atree) &=& [\atree_1, \cdots, \atree_n]\\
+  \end{array}
+\]
+
+\paragraph{Proof of Soundness} We formally define the soundness of the static
+analysis $\asem{\prog}$ in Theorem~\ref{thm:sound-prog} and prove it using
+several lemmas.
+
+\begin{theorem}[Soundness of $\asem{\prog}$]\label{thm:sound-prog}
+  For a given syntactic view $\atree \in \atreeset$, the static analysis
+  $\asem{\prog}(\atree)$ is sound by satisfying the following condition:
+  \[
+    \rsem{\prog}(\atree) \subseteq \aelemgamma \circ \asem{\prog}(\atree)
   \]
@@
 
-\begin{lemma}[Soundness of $\atransfer$]
-  The abstract transfer function $\atransfer$ is a sound approximation of the
-  transfer function $\transfer$ by satisfying the following condition:
-  \[
-    \forall \aelem \in \aelemset. \;
-    \transfer \circ \gamma(\aelem) \subseteq \gamma \circ \atransfer(\aelem)
+\begin{lemma}[Soundness of $\entryaelem$]\label{thm:sound-entryaelem}
+  For a given syntactic view $\atree \in \atreeset$, the abstract entry state
+  $\entryaelem(\atree)$ is a sound approximation of the entry states
+  $\entrystset(\atree)$ by satisfying the following condition:
+  \[
+    \entrystset(\atree) \subseteq \aelemgamma \circ \entryaelem(\atree) 
   \]
@@
 
-\begin{theorem}[Semantics Preservation of $\transform{-}$]
-  \[
+\begin{lemma}[Soundness of $\atransfer$]\label{thm:sound-atransfer}
+  The abstract transfer function $\atransfer$ is a sound approximation of the
+  transfer function $\transfer$ by satisfying the following condition:
+  \[
+    \forall \aelem \in \aelemset. \;
+    \transfer \circ \aelemgamma(\aelem) \subseteq
+    \aelemgamma \circ \atransfer(\aelem)
+  \]
+\end{lemma}
+\begin{proof}
   \todo
+\end{proof}
+
+\begin{lemma}[Soundness of $\asem{\inst}$]\label{thm:sound-inst}
+  For a given label $\lab \in \labset$ and its instruction $\inst =
+  \getinst{\prog}(\lab)$, the abstract semantics $\asem{\inst}$ of the
+  instruction is a sound approximation of its concrete semantics $\sem{\inst}$:
+  \[
+    \forall \aelem \in \aelemset. \;
+    \st \in \aelemgamma(\aelem) \wedge \st = (\lab, \_, \_, \_) \Rightarrow
+    \sem{\inst}(\st) \in \aelemgamma \circ \asem{\inst}(\lab, \aelem)
+  \]
+\end{lemma}
+\begin{proof}
+  \todo
+\end{proof}
+
+\begin{lemma}[Soundness of $\asem{\expr}$]\label{thm:sound-inst}
+  The abstract semantics $\asem{\inst}$ of an expression $\expr$ is a sound
+  approximation of its concrete semantics $\sem{\expr}$:
+  \[
+    \forall \aenv \in \aenvset. \;
+    \st \in \aenvgamma(\aenv) \Rightarrow
+    \sem{\expr}(\st) \in \avalgamma \circ \asem{\expr}(\aenv)
+  \]
+\end{lemma}
+\begin{proof}
+  \todo
+\end{proof}
+
+\paragraph{Proof of Semantics Preservation} Finally, we prove the semantics
+prservation of the program transformation $\transform{\prog}$ in
+Theorem~\ref{thm:preserve-prog} with several lemmas.
+
+\begin{theorem}[Semantics Preservation of $\transform{\prog}$]
+  \label{thm:preserve-prog}
+  For a given syntactic view $\atree \in \atreeset$, a transformed program
+  $\prog' = \transform{\prog}(\aelem)$ with an abstract state $\aelem =
+  (\adcall, \ascall, \afsenv) \in \aelemset$ preserves the restricted semantics
+  $\rsem{\prog}(\atree)$ under the static calling contexts
+  $\ascallgamma(\ascall)$ if $\aelem$ is sound:
+  \[
+    \todo
+    % \rsem{\prog}(\atree) \subseteq \aelemgamma(\aelem) \Rightarrow
+    % \forall \st \in \rsem{\prog}(\atree) \cap \ascallgamma(\ascall). \;
+    % (\st \trans{\prog} \st' \wedge \st \trans{\prog'} \st'') \Rightarrow (\st' =
+    % \st'')
   \]
@@
 \end{proof}
-
-\todo

### 2021-11-02 paper/pldi22/formal.tex
Minor update
More proof

@@
 \[
-  \sem{\prog} = \{ \st \in \stset \mid \initst \in \initstset{\prog} \wedge
+  \sem{\prog} = \{ \st \in \stset \mid \exists \initst \in \initstset{\prog}. \;
   \initst \trans{\prog}^* \st \}
@@
 \begin{equation}\label{eqn:transfer}
-  \transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans{\prog} \st' \}
+  \transfer(S) = \{ \st' \in \stset \mid \exists \st \in S. \; \st \trans{\prog}
+  \st' \}
 \end{equation}
@@
 \ascallset$ is a set of possible static call edges from labels to function, and
-it represent a set of \textit{static calling contexts} $\ascallgamma(\ascall)$
-used as the scope of program transformations.  To more precisely in the static
+it represent a set of \textit{static calling contexts}
+$\ascallgamma(\ascall)(\atree)$ with a given syntactic view $\atree$ to
+determine the scope of program transformations.  To more precisely in the static
 calling contexts, we define a flow-sensitive abstract environment $\afsenv \in
@@
     \[
-      \atransfer(\aelem) = \aelem \join \sem{\adcall} \wedge
+      \atransfer(\aelem) = \aelem \join \sem{\adcall} \join
       \bigjoin_{\lab \in \labset}{\asem{\getinst{\prog}(\lab)}(\lab, \aelem)}
@@
 
-        \ty_k.\eval &=& \lambda \kwdef \; \kwrl \varx_1, \cdots, \varx_n \kwrr
+        \ty_k.\eval &=& \kwdef \; \kwrl \varx_1, \cdots, \varx_n \kwrr
         \; \entrylab\\
@@
 \begin{proof}
-  \todo
+  We use an induction on $n$.  Lemma~\ref{lem:sound-entryaelem} proves the base
+  case, $n=0$. Then, we can prove the inductive case using
+  Lemma~\ref{lem:sound-atransfer}.
 \end{proof}
 
-\begin{lemma}[Soundness of $\entryaelem$]\label{thm:sound-entryaelem}
+\begin{lemma}[Soundness of $\entryaelem$]\label{lem:sound-entryaelem}
   For a given syntactic view $\atree \in \atreeset$, the abstract entry state
@@
     \entrystset(\atree) \subseteq \aelemgamma \circ \entryaelem(\atree)
+  \]
+\end{lemma}
+\begin{proof}
+  Since all the conditions described in the definition $\entrystset$ and
+  $\entryaelem$ are exactly same with a given syntactic view $\atree$, this
+  lemma is trivially proved.
+\end{proof}
+
+\begin{lemma}[Soundness of $\atransfer$]\label{lem:sound-atransfer}
+  The abstract transfer function $\atransfer$ is a sound approximation of the
+  transfer function $\transfer$ by satisfying the following condition:
+  \[
+    \forall \aelem \in \aelemset. \;
+    \transfer \circ \aelemgamma(\aelem) \subseteq
+    \aelemgamma \circ \atransfer(\aelem)
   \]
@@
 
-\begin{lemma}[Soundness of $\atransfer$]\label{thm:sound-atransfer}
-  The abstract transfer function $\atransfer$ is a sound approximation of the
-  transfer function $\transfer$ by satisfying the following condition:
-  \[
-    \forall \aelem \in \aelemset. \;
-    \transfer \circ \aelemgamma(\aelem) \subseteq
-    \aelemgamma \circ \atransfer(\aelem)
-  \]
+\begin{lemma}[Soundness of $\asem{\inst}$]\label{lem:sound-inst}
+  \todo
+  % For a given label $\lab \in \labset$ and its instruction $\inst =
+  % \getinst{\prog}(\lab)$, the abstract semantics $\asem{\inst}$ of the
+  % instruction is a sound approximation of its concrete semantics $\sem{\inst}$:
+  % \[
+  %   \forall \aelem = \in \aelemset. \;
+  %   \st \in \aelemgamma(\aelem) \wedge \st = (\lab, \_, \_, \_) \Rightarrow
+  %   \sem{\inst}(\st) \in \aelemgamma \circ \asem{\inst}(\lab, \aelem)
+  % \]
 \end{lemma}
@@
 
-\begin{lemma}[Soundness of $\asem{\inst}$]\label{thm:sound-inst}
-  For a given label $\lab \in \labset$ and its instruction $\inst =
-  \getinst{\prog}(\lab)$, the abstract semantics $\asem{\inst}$ of the
-  instruction is a sound approximation of its concrete semantics $\sem{\inst}$:
-  \[
-    \forall \aelem \in \aelemset. \;
-    \st \in \aelemgamma(\aelem) \wedge \st = (\lab, \_, \_, \_) \Rightarrow
-    \sem{\inst}(\st) \in \aelemgamma \circ \asem{\inst}(\lab, \aelem)
-  \]
-\end{lemma}
-\begin{proof}
-  \todo
-\end{proof}
-
-\begin{lemma}[Soundness of $\asem{\expr}$]\label{thm:sound-inst}
+\begin{lemma}[Soundness of $\asem{\expr}$]\label{lem:sound-inst}
   The abstract semantics $\asem{\inst}$ of an expression $\expr$ is a sound
@@
   $\rsem{\prog}(\atree)$ under the static calling contexts
-  $\ascallgamma(\ascall)$ if $\aelem$ is sound:
+  $\ascallgamma(\ascall)(\atree)$ if $\aelem$ is sound:
   \[

### 2021-11-04 paper/pldi22/abstract.tex
Revised abstract

--- 2021-10-13 paper/pldi22/abstract.tex
@@
   process to adapt users' demands to the language quickly. In this fast-evolving
-  nature of JavaScript, the need for \textit{language design assistants} has
-  grown to understand target semantics and to synchronize three language
-  components: specifications, conformance tests, and language-based tools.
-  Unfortunately, while several language design assistants for JavaScript have
-  been proposed in academia and industry, they have two limitations: 1) no
-  functionalities to focus the target semantics and 2) manual or slow updates of
-  language components.
+  nature of JavaScript, developers and even language designers often suffer from
+  complex semantics in newly introduced language features and desire to
+  understand them correctly.  To meet the demand, researchers have proposed
+  several tools that enhance the understanding of JavaScript semantics. However,
+  existing tools 1) require manual updates for new specifications or 2) do not
+  provide any automatic ways to focus on specific semantics.
 
-  To alleviate this problem, we present $\tool$, a \textit{live} language design
-  assistant for JavaScript with \textit{syntactic views}. First, our tool
-  provides a way to focus on target semantics using syntactic views, abstract
-  syntax trees with abstracted nodes. It automatically reduces semantics and
-  filters out conformance tests depending on user-defined syntactic views.
-  Second, $\tool$ automatically and quickly synchronizes language components in
-  the language design process. It detects which parts of semantics are revised
-  and partially updates specifications and conformance tests. For evaluation, we
-  demonstrate the effectiveness of $\tool$ with randomly selected syntactic
-  views and randomly modified semantics. With randomly selected syntactic views,
-  it reduces the \inred{XX.X}\% of semantics and filters out \inred{XX.X}\% of
-  conformance tests on average. With randomly modified semantics, it shortens
-  the time to synchronize three language components by \inred{XX.X}\%.
+  To alleviate this problem, we present $\tool$, a JavaScript interactive
+  specification. First, it provides step-by-step program execution automatically
+  synchronized with a given version of JavaScript specification. Second, our
+  tool offers two approaches to focus on target semantics: 1) reducing semantics
+  with a user-defined \textit{syntactic view} and 2) providing a small-sized
+  program related to a selected algorithm step with automatically inferred
+  assertions. For evaluation, we experimentally demonstrate the effectiveness of
+  $\tool$ with the latest ECMAScript (ES12, 2021), \inred{177} syntactic views,
+  and \inred{19,839} programs. Our tool successfully reduces \inred{18.9}\%
+  algorithm steps for each syntactic view on average. For each algorithm step,
+  it provides \inred{2.3} lines (\inred{152.3} bytes) of a program with
+  automatically inferred assertions on average.
 \end{abstract}

### 2021-11-04 paper/pldi22/abstract.tex
Revised abstract

@@
   nature of JavaScript, developers and even language designers often suffer from
-  complex semantics in newly introduced language features and desire to
-  understand them correctly.  To meet the demand, researchers have proposed
-  several tools that enhance the understanding of JavaScript semantics. However,
-  existing tools 1) require manual updates for new specifications or 2) do not
-  provide any automatic ways to focus on specific semantics.
+  complex semantics in newly introduced language features and want to
+  \textit{understand} them correctly.  To meet the demand, researchers have
+  proposed several tools that enhance the understanding of JavaScript semantics.
+  However, existing tools 1) require manual updates for new specifications or 2)
+  do not provide additional information when users desire to understand specific
+  parts of semantics.
 
@@
   synchronized with a given version of JavaScript specification. Second, our
-  tool offers two approaches to focus on target semantics: 1) reducing semantics
-  with a user-defined \textit{syntactic view} and 2) providing a small-sized
-  program related to a selected algorithm step with automatically inferred
-  assertions. For evaluation, we experimentally demonstrate the effectiveness of
+  tool offers two different kinds of additional information for target semantics
+  selected by users: 1) reduced semantics for a selected \textit{syntactic view}
+  using \textit{partial evaluation} and 2) a small-sized program related to a
+  selected algorithm step using \textit{delta debugging} with a given set of
+  programs. For evaluation, we experimentally demonstrate the effectiveness of
   $\tool$ with the latest ECMAScript (ES12, 2021), \inred{177} syntactic views,

### 2021-11-04 src/main/scala/kr/ac/kaist/jiset/editor/mutator/RandomMutator.scala
Minor

@@ -10,7 +10,7 @@ import kr.ac.kaist.jiset.util.Useful._
 // random mutator
 case class RandomMutator(program: JsProgram, nids: Set[Int]) extends Mutator with ASTTransformer {
   // handle stmts
-  var transformed :Boolean = false
+  var transformed: Boolean = false
   override def transform(ast: StatementList): StatementList = if (!transformed) {
     val stmts = flattenStmtList(ast)
     val length = stmts.length
@@ -25,7 +25,7 @@ case class RandomMutator(program: JsProgram, nids: Set[Int]) extends Mutator wit
   val name: String = "random"
   val retryMax = 10
   def _mutate: Option[Script] = {
-   val removed = transform(program.script)
-   Some(removed)
+    val removed = transform(program.script)
+    Some(removed)
   }
 }

### 2021-11-04 paper/pldi22/abstract.tex
Revised intro

--- 2021-11-04 paper/pldi22/abstract.tex
@@
 \begin{abstract}\label{sec:abstract}
-  JavaScript is a widely-used programming language in various fields. Recently,
-  it has rapidly evolved with a yearly release cadence and open development
-  process to adapt users' demands to the language quickly. In this fast-evolving
-  nature of JavaScript, developers and even language designers often suffer from
-  complex semantics in newly introduced language features and desire to
-  understand them correctly.  To meet the demand, researchers have proposed
-  several tools that enhance the understanding of JavaScript semantics. However,
-  existing tools 1) require manual updates for new specifications or 2) do not
-  provide any automatic ways to focus on specific semantics.
+  JavaScript is a widely-used programming language in various fields.
+  Unfortunately, developers and even language designers often suffer from
+  complex semantics in JavaScript and desire to \textit{understand} them
+  correctly. Therefore, researchers have presented several tools for a better
+  understanding of JavaScript semantics. However, existing tools 1) require
+  manual updates for new specifications while JavaScript has rapidly evolved
+  with various language features and 2) do not support user interactions to
+  select target semantics to get additional information.
 
@@
   synchronized with a given version of JavaScript specification. Second, our
-  tool offers two approaches to focus on target semantics: 1) reducing semantics
-  with a user-defined \textit{syntactic view} and 2) providing a small-sized
-  program related to a selected algorithm step with automatically inferred
-  assertions. For evaluation, we experimentally demonstrate the effectiveness of
-  $\tool$ with the latest ECMAScript (ES12, 2021), \inred{177} syntactic views,
-  and \inred{19,839} programs. Our tool successfully reduces \inred{18.9}\%
-  algorithm steps for each syntactic view on average. For each algorithm step,
-  it provides \inred{2.3} lines (\inred{152.3} bytes) of a program with
-  automatically inferred assertions on average.
+  tool supports two different types of user interactions to select target
+  semantics: 1) a \textit{syntactic view selection} to reduce abstract
+  algorithms using \textit{partial evaluation} and 2) an \textit{algorithm step
+  selection} to get a small-sized JavaScript program related to the step using
+  \textit{delta debugging} with a given set of programs. For evaluation, we
+  experimentally demonstrate the effectiveness of $\tool$ with the latest
+  ECMAScript (ES12, 2021), \inred{177} syntactic views, and \inred{19,839}
+  programs. Our tool successfully supports step-by-step program execution in
+  ES12. It reduces \inred{18.9}\% algorithm steps for each syntactic view and
+  provides \inred{2.3} lines (\inred{152.3} bytes) of a program for each step on
+  average.
 \end{abstract}

### 2021-11-04 paper/pldi22/intro.tex
Revised intro

--- 2021-10-12 paper/pldi22/intro.tex
@@
 hack. However, it has become a de facto Web standard and eventually becomes one
-of the dominating programming languages in various fields. For example, Node.js
-introduced full-stack JavaScript by supporting server-side programming, and
-JavaScript has recently begun to be used even in embedded systems and
-microcontrollers for the Internet of Things (IoT). Furthermore, according to the
-annual report of GitHub\footnote{\url{https://octoverse.github.com/}},
-JavaScript has consistently been the most popular programming language based on
-the number of contributors to GitHub projects.
+of the dominating programming languages in various fields. For example,
+Node.js\footnote{https://nodejs.org/} introduced full-stack JavaScript by
+supporting server-side programming, and JavaScript has recently begun to be used
+even in embedded systems and microcontrollers for the Internet of
+Things\footnote{https://www.espruino.com/}. Furthermore, according to the annual
+report of GitHub\footnote{\url{https://octoverse.github.com/}}, JavaScript has
+consistently been the most popular programming language based on the number of
+contributors to GitHub projects.
 
-Recently, JavaScript has rapidly evolved with a yearly release cadence and open
-development process. In 2015, The Ecma Technical Committee 39 (TC39) decided to
-annually release ECMAScript, the standard specification for JavaScript, with a
-massive update in ECMAScript 2015 (ES6, 2015)~\cite{es6}. Moreover, they
-published the specification as an open-source project in a GitHub repository to
-quickly adapt users' demands to the language.
+Unfortunately, developers and even language designers often suffer from complex
+semantics in new language features and desire to understand them correctly.
+ECMAScript is the standard specification for JavaScript maintained by Ecma
+Technical Committee 39 (TC39). It describes the language semantics in abstract
+algorithms consisting of English sentences. However, it is infeasible to know
+all the detailed complex semantics by reading the specification even to language
+designers. For example, consider a JavaScript logical nullish assignment
+\jscode{x ??= y} newly introduced in the latest ECMAScript (ES12,
+2021)~\cite{es12}. Its basic semantics is to assign \jscode{y} to \jscode{x}
+only if \jscode{x} is nullish (\jscode{undefined} or \jscode{null}). Therefore,
+it seems to have exactly same semantics with an assignment \jscode{x = x ?? y}
+with a nullish coalescing operator \jscode{??}.  However, it is not true because
+of the short-circuiting for assignments:
+\begin{lstlisting}[style=JS]
+       const x = 0;  x ??= 1;    // x === 0
+       const y = 0;  y = y ?? 1; // TypeError
+\end{lstlisting}
+and the named evaluation for anonymous functions:
+\begin{lstlisting}[style=JS]
+   let f;  f ??= () => {};      // f.name === "f"
+   let g;  g = g ?? (() => {}); // g.name === ""
+\end{lstlisting}
+Such misunderstanding of complex semantics in various language features causes
+the wrong implementation of JavaScript applications or even JavaScript engines.
 
-In this fast-evolving nature of JavaScript, the need for language design
-assistants (LDAs)~\cite{lda} has grown to understand original or revised
-semantics correctly in the revision process. Historically, researchers have
-proposed several language design assistants, such as LISA~\cite{lisa} and
-$\asfsdf$~\cite{asf-sdf, meta-env}, with semantics editors and the generators
-for language-based tools, such as parsers, compilers, interpreters, and so on.
-However, only small-size domain-specific languages are their targets due to
-their low expressive power. On the other hand, there are several attempts to
-develop language design assistants for JavaScript in the academy and industry.
-For example, in the academy, \citet{jsexplain} presented JSExplain, a JavaScript
-reference interpreter written in OCaml that closely follows ECMAScript and
-produces execution traces for debugging both ECMAScript and a given program. In
-the industry, Mozilla and several contributors introduced JavaScript
-interpreters written in pure JavaScript, such as Narcissus~\cite{narcissus} and
-engine262~\cite{engine262}, to aid the development of new features in
-JavaScript.
+Thus, researchers have presented several tools for a better understanding of
+JavaScript semantics. For example, JSExplain~\cite{jsexplain} is a reference
+interpreter that provides step-by-step execution of a given JavaScript program
+by closely following the English sentences of the specification. Several
+JavaScript language designers accept the concept of reference interpreters and
+implement Narcissus~\cite{narcissus} and engine262~\cite{engine262} to use in
+the language design process. On the other hand, TC39 feels the need for type
+information in ECMAScript to enhance its readability and has started internal
+discussions on manual type annotations for each abstract
+algorithm\footnote{https://github.com/tc39/ecmarkup/issues/173}. To meet the
+demand of type information, \citet{jstar} presents a tool named $\jstar$ to
+perform a type analysis for a given ECMAScript. Besides, they detect
+type-related specification bugs in ES12 using the type analysis result. Finally,
+$\jest$~\cite{jest} is another tool that synthesizes JavaScript conformance
+tests from a given ECMAScript. Thus, it allows users to understand language
+semantics using test programs instead of English sentences in the specification.
 
-However, existing language design assistants for JavaScript have two
-limitations: \textit{manual updates} and \textit{lack of connection with
-conformance tests}. First, all existing assistants are developed manually; thus,
-developers should manually update them for each frequent evolution of
-ECMAScript. This manual approach is a tedious, labor-intensive, and even
-error-prone process. Moreover, they lack information about the relationship
-between specific semantics with conformance tests. When a language designer
-desires to understand specific language semantics, one possible approach is to
-learn them from related conformance tests. Fortunately, TC39 provides Test262,
-an official conformance test suite for the latest version of ECMAScript.
-However, existing assistants do not utilize them to give a better comprehension
-of language semantics.
+However, existing tools have two limitations: 1) manual update for evolving
+language specification and 2) no user interactions to select target semantics.
+Among existing tools, JavaScript reference interpreters require manual updates
+when ECMAScript evolves. Until 2015, it was not a critical problem because
+ECMAScript had rarely evolved. However, TC39 decided to annually release the
+specification with a massive update in ECMAScript 6 (ES6, 2015)~\cite{es6} in
+2015. Moreover, they published the specification as an open-source project in a
+GitHub repository to quickly adapt users' demands to the language. For example,
+JSExplain also requires manual updates for new specifications. Thus, it still
+supports only ECMAScript 5.1 (ES5.1, 2011)~\cite{es5}, while already seven more
+versions from ES6 to ES12 have been released. Another limitation is that
+existing tools do not support user interactions to select target semantics to
+get additional information. For example, $\jstar$ and $\jest$ do not interact
+with users to give more information helpful for semantics understanding.
+Instead, they only extract type information and conformance tests for a given
+ECMAScript. On the other hand, while JSExplain supports step-by-step execution
+as user interaction with several debugger-like features, it can deal with only
+the execution trace of a single JavaScript program.
 
-In this paper, we present $\tool$, a \textit{live} language design assistant for
-JavaScript, which automatically synchronizes with a given language specification
-and shows related conformance tests in the revision process. To synchronize our
-tool with ECMAScript, we utilize another tool $\jiset$~\cite{jiset}, which
-automatically extracts a mechanized specification from a given version of
-ECMAScript. Note that a specification is mechanized if and only if it is both
-executable and formalized.
-\todo
+In this paper, we present $\tool$, a \textbf{J}ava\textbf{S}cript
+\textbf{I}nteractive \textbf{S}pecification. It is the first reference
+interpreter automatically synchronized with a given ECMAScript supporting
+step-by-step program execution. Fortunately, \citet{jiset} presents a tool named
+$\jiset$ that extracts a mechanized specification from a given specification.
+The extracted mechanized specification is written in a specification language
+$\ires$ and executable with a JavaScript program. Thus, we implement our tool
+using $\jiset$ and design debugger-like features: stepping controls, state
+visualization, and breakpoints with algorithm names or JavaScript program
+points. Moreover, our tool supports two different types of user interactions to
+select target semantics: \textit{syntactic view selection} and \textit{algorithm
+step selection}. First, we introduce a way to reduce abstract algorithms using a
+partial evaluation~\cite{peval, peval-survey, trans-ai} with a \textit{syntactic
+view}. A syntactic view is a JavaScript Abstract Syntax Tree (AST) defined with
+abstracted nodes. We formally define a partial evaluation with syntactic views
+and prove its semantics preservation under the given syntactic view. Second, we
+also present a way to extract a small-sized program for each algorithm step
+using delta debugging~\cite{delta-debugging} with a given set of programs. For
+the f first step, we execute each program using $\tool$ to compute semantics
+coverage in ECMAScript and filter out unnecessary programs. Then, we perform
+delta debugging for each program to reduce program sizes without loss of
+semantics coverage.
+
+Our contributions are as follows:
+\begin{itemize}
+  \item We present $\tool$, a JavaScript interactive specification. It is the
+    first reference interpreter automatically synchronized with a given
+    ECMAScript supporting step-by-step program execution.
+
+  \item We introduce two different types of user interactions to select target
+    semantics and implement them in $\tool$: 1) a \textit{syntactic view
+    selection} to reduce abstract algorithms using \textit{partial evaluation}
+    and 2) an \textit{algorithm step selection} to extract a small-sized
+    JavaScript program related to the selected step using \textit{delta
+    debugging} with a given set of programs.
+
+  \item We evaluate $\tool$ with the latest ECMAScript, ES12, and experimentally
+    show the effectiveness of two different target semantics selections with
+    \inred{177} syntactic views and \inred{19,839} programs. Our tool
+    successfully supports step-by-step program execution in ES12. It reduces
+    \inred{18.9}\% algorithm steps for each syntactic view and provides
+    \inred{2.3} lines (\inred{152.3} bytes) of a program for each step on
+    average.
+\end{itemize}
